### 2019-10-28 lloveras_2020.tex
iniciando paper

%% Template.tex; Solar Physics
%% 
\documentclass[namedreferences]{solarphysics}
%
% spr-sola-addons available options:
%  hyperref      -- loads hyperref.sty with options (pdfborder={0 0 0 },urlcolor=blue,breaklinks)
%  nonatbib      -- do not load natbib.sty (style loads it by default)
%  solaromanenum -- makes enumerated list with roman numerals and a single right-bracket
%  linksfromyear -- puts a link on a year citation (hyperref must be loaded). Loaded by default
%  nolinksfromyear -- suppress  linksfromyear
%  optionalrh    -- for optional running title/author
%  showbiblabels -- to show bibitem label at end of bibitem (via \endbibitem command)
%
\usepackage[hyperref,optionalrh,solaromanenum]{spr-sola-addons} % For Solar Physics 
%\usepackage{epsfig}                     % For eps figures, old commands
\usepackage{graphicx}                    % For eps figures, newer & more powerfull
%\usepackage{courier}                    % Change the \texttt command to courier style
\usepackage{amssymb}                    % useful mathematical symbols
\usepackage{color}                       % For color text: \color command
\usepackage{breakurl}                         % For breaking URLs easily trough lines
\def\UrlFont{\sf}                        % define the fonts for the URLs
\usepackage{comment}
\usepackage{setspace}

%% Local definitions
%% please place your own definitions here and don't use \def but
%% \newcommand{}{} or 
%% \renewcommand{}{} if it is already defined in LaTeX
\renewcommand{\deg}{$^\circ$}
\newcommand{\mdeg}{^\circ}
\newcommand{\rsun}{R{$_\odot$}}
\renewcommand{\l}{\lambda_{\rm N}}%\lambda_
\newcommand{\mrsun}{{\rm R_\odot}}
\newcommand{\med}{{\rm Md}}
\newcommand{\avgTe}{\left<T_\textrm{m}\right>}
\newcommand{\MK}{{\rm MK}}
\newcommand{\cm}{{\rm cm}}
\newcommand{\sdev}{{\rm SD}}
\newcommand{\mean}{{\rm Mn}}
\newcommand{\deltat}{$\delta$}
\newcommand{\LDEM}{{\rm LDEM}}
\newcommand{\FBE}{{\rm FBE}}
\newcommand{\TRF}{{\rm TRF}}
\newcommand{\lN}{\lambda_N}
\newcommand{\NCB}{N_{\rm CB}}
\newcommand{\aTm}{\left< T_\textrm{m}\right>}
\newcommand{\Nqi}{N_{\rm QI}}

\newcommand{\Tefit}{T_{e,{\rm fit}}}

\newcommand{\BibTeX}{\textsc{Bib}\TeX}
\newcommand{\etal}{{\it et al.}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{article}

\begin{opening}

\title{Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Authors Names
%
% \author[addressref={},corref,email={}]{\inits{}\fnm{}\lnm{}\orcid{}}
\author[addressref={aff1,aff2},corref,email={dlloveras@iafe.uba.ar}]{\inits{D.G.}\fnm{Diego G.}~\lnm{Lloveras}\orcid{0000-0003-1402-0398}}

\author[addressref={aff1,aff3,aff2},corref,email={albert@iafe.uba.ar}]{\inits{A.M.}\fnm{Alberto M.}~\lnm{V\'asquez}\orcid{0000-0003-3401-6409}}

\author[addressref={aff1,aff2},corref,email={federico@iafe.uba.ar}]{\inits{F.A.}\fnm{Federico A.}~\lnm{Nuevo}\orcid{0000-0003-2355-5853}}

\author[addressref={},corref,email={nishthas@umich.edu}]{\inits{N.}\fnm{Nishtha}\lnm{Sachdeva}\orcid{1}}

\author[addressref={},corref,email={chipm@umich.edu}]{\inits{W.}\fnm{Ward}\lnm{Manchester IV}\orcid{2}}

\author[addressref={},corref,email={bartvand@umich.edu}]{\inits{B.}\fnm{Bartholomeus}\lnm{Van der Holst}\orcid{3}}

\author[addressref={aff4},corref,email={rfrazin@umich.edu}]{\inits{R.A.}\fnm{Richard A.}~\lnm{Frazin}\orcid{0000-0002-0281-7677}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Runningheads
%
\runningauthor{D.G.~Lloveras~\etal}
%\runningtitle{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Affilations 
%% id shold be the same with \author addressref value.
%\address[id={}]{}
\address[id=aff1]{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (IAFE), CONICET-UBA, CC 67 - Suc 28,  (C1428ZAA) Ciudad Aut\'onoma de Buenos Aires, Argentina}

\address[id=aff2]{Departamento de F\'{\i}sica, Facultad de Ciencias Exactas y Naturales (FCEN), Universidad de Buenos Aires (UBA), Pabell\'on I, Ciudad Universitaria, (C1428ZAA) Ciudad Aut\'onoma de Buenos Aires, Argentina}

\address[id=aff3]{Departamento de Ciencia y Tecnolog\'{\i}a, Universidad Nacional de Tres de Febrero (UNTREF), Valent\'{\i}n G\'omez 4752, (B1678ABH) Caseros, Provincia de Buenos Aires, Argentina}

\address[id=aff4]{Department of Climate and Space Sciences and Engineering (CLaSP), University of Michigan, 2455 Hayward Street, Ann Arbor, MI 48109-2143, USA}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Abstract 
\begin{abstract}
Observational tools play an essential role in advancing our understanding of the physics of the solar corona. They provide validation data to improve three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, key to enhance their space weather forecasting capabilities. Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of fundamental plasma parameters of the solar corona at a global scale. Based on EUV data of space borne instruments, SRT allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun. We carry out a study of the corona combining tomographic reconstructions with MHD simulations of the latest version of the Alfvén Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF). Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24. Tomographic reconstructions and results of the model are analyzed in distinct coronal magnetic structures. We study magnetically closed structures associated with the equatorial streamer belt, as well as magnetically open regions enclosing it. We report on the tomographic results in the different structures, their implications for the physics of the solar corona, and the capability of the AWSoM model to reproduce the tomographic reconstructions in different regions.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Keywords
%
\keywords{Solar Cycle, Observations; Corona,E; Corona, Structures}

\end{opening}
%-------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Sections
\section{Introduction}\label{intro}

\section{Methodology}\label{meto}   
\subsection{DEMT reconstructions}\label{demt} 
\subsection{AWSoM simulations}\label{awsom} 
\subsection{Tracing results along fieldlines}\label{trace}

\section{Results}\label{resu} 
\subsection{Tomographic Results}\label{demt_res} 
A) Carrington (Lat/Lon) maps of the DEMT products Ne and Te at selected heights 1.025, 1.105, 1.205 Rsun, over plotting the Open/Closed (O/C) boundary from the AWSoM model. This plot gives initial CONTEXT.

B) Carrington maps of the Lat/Lon location at 1.105 Rs of the field lines I (in blue), II (in red), and III (in green). This shows in a very graphical way which regions of the corona are probed by the three classes of selected field lines.

C) A plot of the average DEMT Ne(r) along all field lines of type I (in solid-blue), of type II (in solid-red and of type III (in solid-green). Over plotted in the same color code but in dashed-line style the AWSoM results along the same three statistical sample of field-lines. In particular, this shows the global 3D agreement between AWSoM and DEMT in distinct magnetic structures and carefully tracing along field lines

D) Same as C) but for Te.

C) and D) will be complemented with companion histograms showing in a statistical fashion how AWSoM and DEMT results compare.

E) As the two rotations are strongly axis-symmetric we want to show the longitude-averaged results of DEMT at a low height, say 1.105 Rsun, along with AWSoM results. In the attached plot we show the DEMT and AWSoM longitude-averaged results at 1.105 Rsun in the top two panels (one for each rotation). The vertical lines indicate the longitude-averaged latitudes of the North and South OC boundary. The LOW panels show the longitude-averaged AWSoM wind speed Vr at 6 Rsun, where all field lines are open. The HCS location is indicated by the minimum of the speed curve. Everything to the South of the HCS maps down to the Southern OPEN region in the top panels, and the same for the Northern hemisphere. It is pretty obvious the ANTI-CORRELATION between the tomographic Ne at low heights (coronal source region of the wind) and the Vr.

This plot (E) has never been shown before and I believe it is a very nice result. There are of course previous studies on this, but this would be the first time this is evaluated with tomography. It is not the terminal speed, but it already shows the fast/slow components. We can show this, or we can go for more. Diego can QUANTIFY the correlation by carefully mapping all open field lines at 6 Rsun down to the DEMT region. He needs to code a bit more to achieve this goal, but we believe it is worth. With that tool done Diego can explore other terminal values of quantities of the AWSoM model and the DEMT results below (expansion factor maybe?). This will be nice to do also for the July-2-2019 Eclipse rotation that we will analyze after this paper.

\subsection{Tomography and Models}\label{awsom_res} 
Same as A but for AWSoM model.
Same as B but for AWSoM model

\section{Discussion}\label{discu} 
%% Figure 
%
% \begin{figure} 
% \centerline{\includegraphics[width=0.5\textwidth,clip=]{<fig.eps>}}
% \caption{}%\label{fig:?}
% \end{figure}

%% Table
%
% \begin{table}
% \caption{}%\label{tbl:?}
% \begin{tabular}{}     
% \hline
% \multicolumn{2}{c}{<>}
% <data>
% \hline
% \end{tabular}
% \end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Appendix
%
% \appendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Acknowledgements
%
% \begin{acks}
%
% \end{acks}

%%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Bibliography
%
% Using BibTeX
%
% \bibliographystyle{spr-mp-sola}
% \bibliography{<bib file>}  
%
% Without BibTeX 
% \begin{thebibliography}{}
% \bibitem[\protect\citeauthoryear{Author}{Year}]{key}
%   <bibliographical entry>
%
% \bibitem[\protect\citeauthoryear{}{}]{}
%   
%  
% \end{thebibliography}

\end{article} 
\end{document}

### 2019-11-12 lloveras_2020.tex
primeros graficos

@@
 
+\begin{figure}%[ht!]
+\begin{center}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
+\caption{Carrington maps of DEMT results: $N_e$ (left panels) and $T_\textrm{m}$ (right panels) for CR-2082.
+Top, middle and bottom panels show the results at three heliocentric heights, $1.025$ ,$1.065$ $1.105\,\mrsun$, respectively.
+Black voxels correspond to non-reconstructed regions and thick-black curves indicate the open/closed boundaries.}
+\label{carmaps_demt_2082}
+\end{center}
+\end{figure}
+
+\begin{figure}%[ht!]
+\begin{center}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
+\caption{Same as Figure \ref{carmaps_demt_2082} but for CR-2208.}
+\label{carmaps_demt_2208}
+\end{center}
+\end{figure}
+
+\begin{figure}%[ht!]
+\begin{center}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1105_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1105_Rsun.pdf}
+\caption{Same as Figure \ref{carmaps_demt_2082} but for AWSoM results.}
+\label{carmaps_awsom_2082}
+\end{center}
+\end{figure}
+
+\begin{figure}%[ht!]
+\begin{center}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1105_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1105_Rsun.pdf}
+\caption{Same as Figure \ref{carmaps_demt_2208} but for AWSoM results.}
+\label{carmaps_awsom_2208}
+\end{center}
+\end{figure}
+
 B) Carrington maps of the Lat/Lon location at 1.105 Rs of the field lines I (in blue), II (in red), and III (in green).

### 2019-11-13 ejemplo/dlloveras_2020.tex
agregando midpoints

\documentclass[namedreferences]{solarphysics}

\usepackage[hyperref,optionalrh]{spr-sola-addons} % For Solar Physics 
%\usepackage[optionalrh]{spr-sola-addons} % For Solar Physics 
%\usepackage{epsfig}          % For eps figures, old commands
\usepackage{graphicx}        % For eps figures, newer & more powerfull
%\usepackage{courier}         % Change the \texttt command to courier style
%\usepackage{amssymb}        % useful mathematical symbols
\usepackage{color}           % For color text: \color command
\usepackage{breakurl}        % For breaking URLs easily trough lines
\def\UrlFont{\sf}            % define the fonts for the URLs

% General definitions
% please place your own definitions here and don't use \def but
% \newcommand{}{} or 
% \renewcommand{}{} if it is already defined in LaTeX

\newcommand{\BibTeX}{\textsc{Bib}\TeX}
\newcommand{\etal}{{\it et al.}}

% Definitions for equations
\renewcommand{\vec}[1]{{\mathbfit #1}}
\newcommand{\deriv}[2]{\frac{{\mathrm d} #1}{{\mathrm d} #2}}
\newcommand{\rmd}{ {\ \mathrm d} }
\newcommand{\uvec}[1]{ \hat{\mathbf #1} }
\newcommand{\pder}[2]{ \f{\partial #1}{\partial #2} }
\newcommand{\grad}{ {\bf \nabla } }
\newcommand{\curl}{ {\bf \nabla} \times}
\newcommand{\vol}{ {\mathcal V} }
\newcommand{\bndry}{ {\mathcal S} }
\newcommand{\dv}{~{\mathrm d}^3 x}
\newcommand{\da}{~{\mathrm d}^2 x}
\newcommand{\dl}{~{\mathrm d} l}
\newcommand{\dt}{~{\mathrm d}t}
\newcommand{\intv}{\int_{\vol}^{}}
\newcommand{\inta}{\int_{\bndry}^{}}
\newcommand{\avec}{ \vec A}
\newcommand{\ap}{ \vec A_p}

\newcommand{\bb}{\vec B}
\newcommand{\jj}{ \vec j}
\newcommand{\rr}{ \vec r}
\newcommand{\xx}{ \vec x}

% Definitions for the journal names
\newcommand{\adv}{    {\it Adv. Space Res.}} 
\newcommand{\annG}{   {\it Ann. Geophys.}} 
\newcommand{\aap}{    {\it Astron. Astrophys.}}
\newcommand{\aaps}{   {\it Astron. Astrophys. Suppl.}}
\newcommand{\aapr}{   {\it Astron. Astrophys. Rev.}}
\newcommand{\ag}{     {\it Ann. Geophys.}}
\newcommand{\aj}{     {\it Astron. J.}} 
\newcommand{\apj}{    {\it Astrophys. J.}}
\newcommand{\apjl}{   {\it Astrophys. J. Lett.}}
\newcommand{\apss}{   {\it Astrophys. Space Sci.}} 
\newcommand{\cjaa}{   {\it Chin. J. Astron. Astrophys.}} 
\newcommand{\gafd}{   {\it Geophys. Astrophys. Fluid Dyn.}}
\newcommand{\grl}{    {\it Geophys. Res. Lett.}}
\newcommand{\ijga}{   {\it Int. J. Geomagn. Aeron.}}
\newcommand{\jastp}{  {\it J. Atmos. Solar-Terr. Phys.}} 
\newcommand{\jgr}{    {\it J. Geophys. Res.}}
\newcommand{\mnras}{  {\it Mon. Not. Roy. Astron. Soc.}}
\newcommand{\nat}{    {\it Nature}}
\newcommand{\pasp}{   {\it Pub. Astron. Soc. Pac.}}
\newcommand{\pasj}{   {\it Pub. Astron. Soc. Japan}}
\newcommand{\pre}{    {\it Phys. Rev. E}}
\newcommand{\solphys}{{\it Solar Phys.}}
\newcommand{\sovast}{ {\it Soviet  Astron.}} 
\newcommand{\ssr}{    {\it Space Sci. Rev.}} 
\chardef\us=`\_

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{article}
\begin{opening}

\title{Article preparation guidelines\\ {\it Solar Physics}}

\author[addressref={aff1,aff2,aff3},corref,email={e-mail.a@mail.com}]{\inits{F.N.}\fnm{F. Name}~\lnm{Author-a}}%\sep
\author[addressref=aff1,email={e-mail.b@mail.com}]{\inits{F.}\fnm{Fisrt}~\lnm{Author-b}}%\sep
\author[corref,email={e-mail.c@mail.com}]{\inits{S.}\fnm{Second}~\lnm{Author-c}}%\sep
\author{\inits{T.}\fnm{Third}~\lnm{Author-x}}
%\author{\inits{}\fnm{}~\lnm{}\orcid{}}
%\author{P.~\surname{Author-a}$^{1}$\sep
%        E.~\surname{Author-b}$^{1}$\sep
%        M.~\surname{Author-c}$^{2}$      
%       }

%   \institute{$^{1}$ First affiliation
%                     email: \url{e.mail-a} email: \url{e.mail-b}\\ 
%              $^{2}$ Second affiliation
%                     email: \url{e.mail-c} \\
%             }
\address[id=aff1]{First very very very very very very very very very
 very very very very very very very very very very very very very very very very very very long affiliation}
\address[id=aff2]{Second affiliation}
\address[id=aff3]{Third affiliation}

\runningauthor{Author-a et al.}
\runningtitle{Example paper}

\begin{abstract}
0- Title / Abstract

1- Introduction. Aquí se da contexto, se anuncian las técnicas y los targets.

2- Methodology
   2.1 DEMT reconstructions.
   2.2 AWSoM simulations.
   2.3 Tracing results along fieldlines.

3- Results
   3.1 Tomographic Results. Aquí se analizan los resultados DEMT per se y también trazados a lo largo de las lineas. Se comparan las dos rotaciones entre si e incluso con tu paper previo.
   3.2 Tomography and Models

4- Discussion

Con respecto a que mostrar en la sección 3.1. Hay varias cosas. Una que Fede propone es repetir quizá de arranque la misma Figura de Rona a una altura dada versus latitudes. Eso exige saber la latitud promedio de la frontera O/C. A discutir, debo mirar el paper de Rona.
Fede, te parece que lo de arriba luce bien? Otra idea?

\end{abstract}
\keywords{Flares, Dynamics; Helicity, Magnetic; Magnetic fields, Corona}
\end{opening}
%-------------------------------------------------

\section{Introduction}
     \label{S-Introduction}

This file describes the use of special \LaTeX\ features,
useful to format an article for {\it Solar Physics}.  It is only a complement
to the \LaTeX\ and \BibTeX\ documentation.  
It is designed to be used as an example
article giving the general commands. When compiled with \LaTeX\ 
(see Section~\ref{S-BibTeX} for \BibTeX\ compilation), it provides
some practical guidance on the main useful features. More information
is included within this file, but commented out (with a \%).
Un-commenting the \LaTeX\ commands permits one to show their 
results in the compiled file.

  %{\S}{\bf --- Road map of the paper} \\
    % When writing a paper, it is worth to define a title for each paragraph:
    %   gives a roadmap for the paper logic.
    % Replacing automatically all the ``%{\S}{\bf'' by ``{\S}{\bf'' 
    % brings these titles in the typeset of the paper.
 Section~\ref{S-general} gives examples and some general information
to aid writing text with citations (Section~\ref{S-text})
and defining labels (Section~\ref{S-labels}).
Section~\ref{S-features} gives examples of equations 
(Section~\ref{S-equations}), figures (Section~\ref{S-figures}), and 
tables (Section~\ref{S-tables}).
It continues by describing the inclusion of labeled references
(Section~\ref{S-references}) and suggestions for an easy construction 
of a list of references (Section~\ref{S-BibTeX}). 
An appendix is shown as a particular section (Appendix~\ref{S-appendix}),
which can contain figures and tables (Figure~\ref{F-appendix}, 
Table~\ref{T-appendix}).
There is a list of abbreviations used for the main journals (see the
beginning of this \texttt{.tex} file, or the companion 
 \verb+SOLA_example_labels.tex+ 
file, for the definition of the \LaTeX\ commands.
Our conclusions are given in Section~\ref{S-Conclusion}.

\section{Authors, emails and affiliations}
\label{S-aug}
Authors, their emails and affiliations should be typsed with \verb+\author[key=val,key,..]{}+ and \verb+\address[key=val]{}+ commands.

Command \verb+\author+  has an optional parameter with available keys: 
\begin{itemize}
\item \verb+addressref=<address_id1,address_id2,..>+ -- makes numbered marks of affiliations with the same \texttt{id}.
\item \verb+email=<authors_email>+ -- outputs author and email in the footnotes area.
\item \verb+corref+ -- marks this author as a corresponding one and outputs him (and his email) in the footnotes area with envelope icon in front. 
\end{itemize}
Mandatory parameter -- authors name, which should be tagged in three commands:
\begin{itemize}
\item \verb+\inits+ -- is used for author's initials (will be outputed before author's name in the footnotes area).
\item \verb+\fnm+ -- is used for author's first name.
\item \verb+\lnm+ -- is used for author's last name.
\item \verb+\orcid+ -- is used for author's ORCID identifier (will be outputed orcid.eps(pdf) image with a link to \verb+http://orcid.org/+\textit{identifier}.
\end{itemize}

Command \verb+\address+ has optional parameter  with one key -- \texttt{id}, which is used to combine author and affiliation with the same mark.
All affiliations are outputed in footnotes area right after the emails.

\section{General Text} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \label{S-general}

\subsection{Text with Citations} %%%%%%%%%%%%%%
  \label{S-text}
This section gives an example of text with references 
included with the \verb+\citep{}+ and \verb+\citealp{}+ commands
(see Section~\ref{S-references} about citation commands).

   %{\S}{\bf --- Introduction of H.  What is it ?} \\
Magnetic helicity quantifies how the magnetic field is sheared
and/or twisted compared to its lowest energy state (potential
field). Observations of sheared, and even helical, magnetic
structures in the photosphere, corona and solar wind have
attracted considerable attention, with the consequent interest in
magnetic helicity studies (see reviews by \citealp{Brown99}, and,
\citealp{Berger03}). Stressed magnetic fields are often observed
in association with flares, eruptive filaments, and coronal mass
ejections (CMEs), but the precise role of magnetic helicity in
such activity events still needs to be clarified.

   %{\S}{\bf --- Theoretical use of H} \\
Magnetic helicity plays a key role in magnetohydrodynamics (MHD)
because it is almost preserved on a timescale less than the global
diffusion timescale (\citealp{Berger84}, \citeyear{Berger03}).  
Its conservation defines a
constraint on the magnetic field evolution; in particular a
stressed magnetic field with finite total helicity cannot relax to
a potential field.  Thus magnetic helicity is at the heart of
several MHD relaxation theories, for example of coronal heating
\citep{Heyvaerts84} but also of flares \citep{Kusano04,Melrose04}.
The permanent accumulation of helicity in the corona could be
vital to the origin of CMEs \citep{Rust94,Low97}.  In the
convection zone, the accumulation of helicity in large scales
limits the efficiency of the dynamo, thus the conservation of
magnetic helicity is responsible for dynamo saturation, the
so-called $\alpha$-effect quenching \citep{Brandenburg01}.

\subsection{Importance of Using Labels} %%%%%%%%%%%%%%
  \label{S-labels}

  %{\S}{\bf --- Why using labels ?} \\
    \LaTeX\ defines labels for many features like sections, 
equations, figures, tables, and citations.  The systematic use
of these labels greatly facilitates the writing of a scientific
article (even if it may appear as more extra work at the beginning).
Indeed, it permits one to re-number or re-order automatically the
features during the compilation ({\it e.g.} when adding or moving a 
section).  It also permits one to
cross check automatically whether the citations have been included
in the bibliography list.

  %{\S}{\bf --- How to use labels} \\
    Labels are powerful but their use can be cumbersome if some
clear logic is not used in defining them since one can easily
forget the exact defined label ({\it e.g.} case sensitive).
A label should be simple
while reflecting precisely what it refers to. It is very helpful
to create a small auxiliary file where all these labels are
kept (see the \verb+SOLA_example_labels.tex+ 
accompanying the present file).   
It also provides a roadmap of the paper with the list
of the sections and subsections with the equations introduced in each.     
Including the full command ({\it e.g.} \verb+Section~\ref{S-labels}+)
permits one to do a simple copy/paste when needed (rather than moving
through the \texttt{.tex} file looking for the definition of the label). 
It is also useful that  
\verb+SOLA_example_labels.tex+   file contains the copy of the 
new commands, as well as the citation commands. For references,
the simple convention of concatenating the first author's name and the year
(and eventually a letter), is simple enough to be easily remembered.

\section{Including Special Features} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \label{S-features}

\subsection{Examples of Equations} %%%%%%%%%%%%%%
  \label{S-equations}
Here are a few examples of equations. It is useful to define
a new command when a combination of symbols is present at several 
locations, for example:\\
  \verb+ \renewcommand{\vec}[1]{{\mathbfit #1}} + 
(see the beginning of present \texttt{.tex} file for more examples). 
The mathematics style is to set operators such as ``d'', ``ln'', ``log'', 
``curl'', \textit{etc.} in roman, not italic.
The following math fonts should be used:
\begin{itemize}
\item Scalar: slant \verb+\mathit+
\item Vector: bold slant \verb+\mathbfit+
\item Matrix: bold \verb+\mathbf+
\item Tensor: calligraphic \verb+\mathcal+
\end{itemize}

\subsubsection{Simple Equations} %%%%%%%%%%%%%%
  \label{S-simple-equations}
 The magnetic helicity of the magnetic field ($\vec{B}$) fully contained 
within a volume $\vol $ is \citep{Elsasser56}:
   \begin{equation}  \label{Eq-H-def}
     H^{\rm closed} = \intv \avec \cdot \bb \dv \,.
   \end{equation}

\subsubsection{Array of Equations} %%%%%%%%%%%%%%
  \label{S-array-equations}
The vector potential ($\avec$) can be written as a function of $\bb$
within the Coulomb gauge:
   \begin{eqnarray}   
     \avec (\xx) &=& \mu_{0}\intv \frac{\jj (\xx  ^\prime)}
                     { | \xx - \xx  ^\prime |} \dv ^\prime          
                       \nonumber \\      % \\ indicates the equation end
                 &=& \frac{1}{4\pi} \int \bb (\xx ^\prime ) \times
                     \frac{(\xx  - \xx ^\prime)}{\,\, |\xx - \xx ^\prime |^3}  
                                           \dv ^\prime   \,. 
                       \label{Eq-A-B}    % No ``\\'' for the last equation
   \end{eqnarray}

Then the magnetic helicity can be written as a function of $\bb$
alone \citep{Moffatt69}. An approximation of this double integral 
can be realized by splitting
the magnetic field in $N$ flux tubes \citep{BergerF84}:
   \begin{eqnarray}   
    H^{\rm closed} &=& \frac{1}{4\pi} \intv \intv
                      \bb (\xx ) \times \bb (\xx ^\prime )
                      \cdot \frac{(\xx  - \xx ^\prime)}{\,\, |\xx - \xx ^\prime |^3}
                      \dv \dv ^\prime \,,                     \label{Eq-H-B} \\      
                  &\approx & \sum_{i=1}^N T_i^{\rm closed} \Phi_i^2
                           + \sum_{i=1}^N \sum_{j=1,j \neq i}^N
                             {\mathcal L}^{\rm closed}_{i,j} \Phi_i \Phi_j  \,.
                       \label{Eq-H-N}     % No ``\\'' for the last equation
   \end{eqnarray}
where $\Phi_i$ and $T_i^{\rm closed}$ are the magnetic flux and the
self helicity of flux tube $i$ respectively ($T_i^{\rm closed}$
includes both twist and writhe), and ${\mathcal L}^{\rm
closed}_{i,j}$ is the mutual helicity between flux tubes $i$ and
$j$.

\subsubsection{Long Equations} %%%%%%%%%%%%%%
  \label{S-long-equations}
 A long equation is broken into several lines:
      \begin{eqnarray}
      \deriv{H}{t} &=& 
                    \frac{1}{2 \pi} \int_{\Phi } \int_{\Phi }
                    \left(   \deriv{ \theta (\xx _{c_-} -\xx _{a_+}) }{t}
                           + \deriv{ \theta (\xx _{c_+} -\xx _{a_-}) }{t}
                    \right.                            \nonumber  \\
       && \qquad \qquad \;
                    \left. - \deriv{ \theta (\xx _{c_+} -\xx _{a_+}) }{t}
                         -\, \deriv{ \theta (\xx _{c_-} -\xx _{a_-}) }{t}
                    \right) 
                    \rmd \Phi_{a} \rmd \Phi_{c}  \,. \label{Eq-dH-Phi}
      \end{eqnarray}
A fine tuning of the positions can be obtained with the following spacing commands
(\verb+\!+ is a negative thin space):
     \begin{eqnarray} 
     \verb+\! + |\!| \,\  \qquad &    \! \verb+  \, + |\,|    
                          & \qquad    \verb+    \: + |\:|       \nonumber \\
     \verb+\ + |\ |       \qquad &    \verb+\quad + |\quad| 
                          & \qquad    \verb+\qquad + |\qquad|   \nonumber  
     \end{eqnarray}

  \begin{figure}    %%%%%%%%%%%%%%%%%% FIGURE 1 
   \centerline{\includegraphics[width=0.5\textwidth,clip=]{fig1a.eps}
              }
              \caption{Example of a simple figure with only one panel. 
Relative units (here \texttt{$\backslash$textwidth}) are preferred
so that the figure adapts automatically to the text width (this command is very useful
in more complex figures such as Figures~\ref{F-4panels} and~\ref{F-rotate-cut}).
The use of the command \texttt{$\backslash$includegraphics} requires the 
inclusion of \texttt{$\backslash$usepackage\{graphicx\}} at the beginning of the
\LaTeX\ file.
                      }
   \label{F-simple}
   \end{figure}

  \begin{figure}    %%%%%%%%%%%%%%%%%% FIGURE 2
                                % includes the two top panels 
   \centerline{\hspace*{0.015\textwidth}
               \includegraphics[width=0.515\textwidth,clip=]{fig1a.eps}
               \hspace*{-0.03\textwidth}
               \includegraphics[width=0.515\textwidth,clip=]{fig1b.eps}
              }
     \vspace{-0.35\textwidth}   % Shift close to the panel top 
     \centerline{\Large \bf     % Includes the labels (here needs the color 
                                %   package, see beginning of this file)
      \hspace{0.0 \textwidth}  \color{white}{(a)}
      \hspace{0.415\textwidth}  \color{white}{(b)}
         \hfill}
     \vspace{0.31\textwidth}    % Shift back to the panel bottom 
%           
   \centerline{\hspace*{0.015\textwidth}
               \includegraphics[width=0.515\textwidth,clip=]{fig1c.eps}
               \hspace*{-0.03\textwidth}
               \includegraphics[width=0.515\textwidth,clip=]{fig1d.eps}
              }
     \vspace{-0.35\textwidth}   % Shift close to the panel top 
     \centerline{\Large \bf     % Includes the labels (here needs the color package)
      \hspace{0.0 \textwidth} \color{white}{(c)}
      \hspace{0.415\textwidth}  \color{white}{(d)}
         \hfill}
     \vspace{0.31\textwidth}    % Shift back to the panel bottom

\caption{Example of a figure with four panels (constructed with 
four \texttt{.eps} files).  
The labels of the panels are included with \LaTeX\ commands 
so that each panel can be referred to unambiguously in the text.
The position of the panels
is fine-tuned with the \texttt{$\backslash$hspace} and 
\texttt{$\backslash$vspace} commands.
        }
   \label{F-4panels}
   \end{figure}

%% The following show the use of the epsfig package.   
%%    Un-comment the relevant parts if needed
%%    Un-comment the \usepackage{epsfig} line at the top of this file
%  \begin{figure}    %%%%%%%%%%%%%%%%%% FIGURE 2 bis
%   \centerline{\epsfig{file=fig1a.eps,width=0.51\textwidth,clip=}
%               \hspace*{-0.03\textwidth}
%               \epsfig{file=fig1b.eps,width=0.51\textwidth,clip=}
%              }
%    \vspace*{0.003\textwidth}
%   \centerline{\epsfig{file=fig1c.eps,width=0.51\textwidth,clip=}
%               \hspace*{-0.03\textwidth}
%               \epsfig{file=fig1d.eps,width=0.51\textwidth,clip=}
%              }
%  \centerline{\includegraphics[width=\textwidth,clip=]{fig1.eps} }                 
%\caption{Example of figure with four panels.}
%   \label{F-4panels-bis}
%   \end{figure}

  \begin{figure}    %%%%%%%%%%%%%%%%%% FIGURE 3   rotation + cut
% Original BoundingBox (in the .eps files) : 54 360 558 720
%   corresponds to the coordinates of: left, bottom, right, top   (unrotated)
   \centerline{\includegraphics[width=0.4\textwidth,clip=,
                 bb=54 440 488 660,angle=-90]{fig1a.eps}
               \includegraphics[width=0.4\textwidth,clip=,
                 bb=54 440 488 660,angle=-90]{fig1b.eps}
               \includegraphics[width=0.4\textwidth,clip=,
                 bb=54 440 488 660,angle=-90]{fig1c.eps}
               \includegraphics[width=0.4\textwidth,clip=,
                 bb=54 440 488 660,angle=-90]{fig1d.eps}
              }
     \vspace{-0.39\textwidth}   % Shift close to the panel top 
     \centerline{\Large \bf     % Includes the labels (here needs the color package)
      \hspace{0.07\textwidth}   \color{white}{(a)}
      \hspace{0.122\textwidth}  \color{black}{(b)}
      \hspace{0.122\textwidth}  \color{white}{(c)}
      \hspace{0.122\textwidth}  \color{white}{(d)}
         \hfill}
     \vspace{0.36\textwidth}    % Shift back to the panel bottom 
\caption{Example of a figure with panels smaller
than the original and rotated clockwise by 90$^{\circ}$ 
(compare with Figure~\ref{F-4panels}). The \texttt{clip=} 
command is important to include only the selected part of the figure 
by changing the \texttt{BoundingBox}. 
The labels of the panels are included using \LaTeX\ commands. 
        }
   \label{F-rotate-cut}
   \end{figure}

\subsection{Examples of Figures} %%%%%%%%%%%%%%
  \label{S-figures}
  %{\S}{\bf --- Main features} \\
 A simple figure is presented as Figure~\ref{F-simple}. When more
than one panel is present, one should add labels for those individual panels.
One can add labels to a figure by using \LaTeX\ as done
in Figures~\ref{F-4panels} and~\ref{F-rotate-cut}. 
The package \verb+\usepackage{color}+
can be used to write text ({\it e.g.} labels) in white or in color. 
Figures can be rotated and their position fine tuned 
(Figures~\ref{F-4panels} and~\ref{F-rotate-cut}).

  %{\S}{\bf --- Cutting a figure in the .eps file} \\
  Cutting a figure can be made by editing the \texttt{.eps} 
file with a text editor, and changing the \texttt{BoundingBox}, 
then saving the file (do not use a text editor designed for \LaTeX\ since 
it could open the file as a figure, and not as a text file).
An \texttt{.eps} file has typically the command
\verb+ %%BoundingBox: 54 360 558 720 + 
at the beginning, where the numbers are the left, bottom, right, and top
coordinates of the graphic (in units of ``pt'').  
Changing these numbers is a way to reduce the part of the image shown. 
The \texttt{GhostView} application gives the coordinates
of the cursor (in units of ``pt''), so it permits one to locate the 
coordinates of the cropping. 
The result of the changes can be checked using \texttt{GhostView}. 
 Note that, depending on the software used to create the \texttt{.eps} file, 
the \texttt{BoundingBox} can be repeated at several places in the
\texttt{.eps} file ({\it e.g.} with \texttt{PageBoundingBox}). 
Also, with some software,
the \texttt{BoundingBox} is defined only close to the end of the file
(the file has at the beginning: \texttt{BoundingBox: (atend)}).
The \texttt{BoundingBox} can still be changed
in place, or defined at the beginning of the \texttt{.eps} file. 
   Finally, this method provides a figure with a reduced size, when
included in \LaTeX\ (do not forget the \texttt{clip=} 
in the command including the \texttt{.eps} file!).     
The advantage of this method is that the correct \texttt{BoundingBox}
is easily determined.

  %{\S}{\bf --- Cutting a figure with \LaTeX } \\
   An alternative way to crop figures is to include the \texttt{BoundingBox}
in the\linebreak \verb+\includegraphics+ command, for example:\\
\verb+ \includegraphics[width=\textwidth,bb=54 440 488 660, clip=]+ \\
  The advantage
is that it can be made within \LaTeX . The initial value is given
by the \texttt{BoundingBox} found in the \texttt{.eps} file.
It may be better to process the
figure in a separate \texttt{.tex} file, since it will require several 
iterations to get the right \texttt{BoundingBox}.

\begin{table}
\caption{ A simple table. Each column is aligned by one of the letters:
l: left, c: center, r: right. 
Using two \$s permits one to insert equation-like features (see last column). 
The inclusion of $\sim$ adds a blank to approximately align the numbers
of the last two columns (see the \LaTeX\ file).
}
\label{T-simple}
\begin{tabular}{ccclc}     % define the column alignment
                           % l: left, c: center, r: right
  \hline                   % horizontal line
Rot. & Date & CMEs & CMEs~ & $\alpha$ \\
     &      & obs. & ~cor. & $10^{-2}$Mm$^{-1}$\\
  \hline
1\tabnote{First table line.} & 02--Nov--97 & 16  & 24.1~ & -1.26 \\
2 & 29--Nov--97 & --  & ~2.53 & ~0.94 \\
3 & 27--Dec--97 & 06  & 11.7~ & ~0.82 \\
4 & 23--Jan--98 & 09  & 16.82 & ~0.94 \\
5 & 20--Feb--98 & 04  & ~9.6~ & ~1.00 \\
total&          & 35  & 64.75 &       \\
  \hline
\end{tabular}
\end{table}

  \begin{table}
\caption{ A more complex table with multi-columns labels. The command 
\texttt{$\backslash$multicolumn\{4\}\{c\}\{Flares (GOES)\}} permits
writing the title ``Flares (GOES)'' over four columns. The alignment
of the decimal points is made by defining two columns separated with an
inter-column replaced by a ``.'' with the command \texttt{r@\{.\}l}  
(see the \LaTeX\ file).
}
\label{T-complex}
\begin{tabular}{lcccccc r@{.}l c} % define the column alignment
                                  % l: left, c: center, r: right
                                  % @{.} replace the inter-column by a .
  \hline
Rot. & Date & \multicolumn{4}{c}{Flares (GOES)}& CMEs 
     & \multicolumn{2}{c}{CMEs} & $\alpha$ \\
     &      &   X & M & C & B                  & obs. 
     & \multicolumn{2}{c}{cor.} & $10^{-2}$Mm$^{-1}$\\
  \hline
1 & 02--Nov--97 & 02 & 04 & 24 & 05 & 16  & ~24&1 & -1.26 \\
2 & 29--Nov--97 & -- & -- & 03 & 04 & --  &   2&53& ~0.94 \\
3 & 27--Dec--97 & -- & 01 & 07 & 08 & 06  &  11&7 & ~0.82 \\
4 & 23--Jan--98 & -- & -- & 03 & 03 & 09  &  16&82& ~0.94 \\
5 & 20--Feb--98 & -- & -- & -- & -- & 04  &   9&6 & ~1.00 \\
total&          & 02 & 05 & 37 & 20 & 35  &  64&75&       \\
  \hline
\end{tabular}
\end{table}

\subsection{Examples of Tables} %%%%%%%%%%%%%%
  \label{S-tables}
   Tables are easy to write provided one keeps the alignment 
with the column separator \texttt{\&} when entering the table 
in the \LaTeX\ file 
(even if it is not required by \LaTeX). Examples of a simple table,
Table~\ref{T-simple}, and a more complex table, Table~\ref{T-complex},
are given.

\subsection{Including References in the Text} %%%%%%%%%%%%%%
  \label{S-references}
  The classical way to input references in the text is with the 
\verb+\cite{label-ref}+ command where \verb+label-ref+ is a label
unique for each reference.  It is defined in the environment
\verb+\begin{thebibliography}{} ... +, or in the \BibTeX\ file
(see Section~\ref{S-BibTeX}). 
Style uses \texttt{natbib} package to handle all the issues with citations.
The natbib package is a reimplementation of the \LaTeX\ \verb+\cite+ command, 
to work with both author-year and numerical citations.

\texttt{natbib} provides a lot of different citation commands. So you can manage the output of citation by yourself.
For example:\\
\verb+\defcitealias{Dupont07}{DSK}+: \defcitealias{Dupont07}{DSK}alias text for citation \texttt{Dupont07}\\
\verb+(\citealp{Dupont07}: hereafter \citetalias{Dupont07})+ will output:\linebreak 
                                  (\citealp{Dupont07}: hereafter \citetalias{Dupont07})

For more valid citation commands see the \texttt{natbib} package documentation.

%The main citation commands, and their
%compilation results, are:\\
%\verb+\cite{Kusano04}          +: (Kusano \etal, 2004)\\
%\verb+\cite{Kusano04,Berger03} +: (Kusano \etal, 2004; Berger, 2003)\\
%\verb+\inlinecite{Brown99}     +: Brown, Canfield, and Pevtsov (1999)\\
%\verb+\opencite{Brown99}       +: Brown, Canfield, and Pevtsov, 1999\\
%\verb+\citeauthor{Brown99}     +: Brown, Canfield, and Pevtsov\\
%\verb+\shortcite{Brown99}      +: (1999)\\
%\verb+\citeyear{Brown99}       +: 1999\\
%\verb+(\opencite{Berger84}, \citeyear{Berger03}) +: 
%                                  (\opencite{Berger84}, \citeyear{Berger03})

\subsection{Using \BibTeX} %%%%%%%%%%%%%%
  \label{S-BibTeX}
  %{\S}{\bf --- Why using \BibTeX ? } \\
  The use of \BibTeX\ simplifies the inclusion of references. Only the 
references cited and labeled in the text are included at compilation, 
and an error message appears if some references
are missing.  Any new reference will automatically be written at the correct 
location in the reference list after compilation. 
Moreover the references are stored, in any order, in a separate file
(with the \texttt{.bib} extension) in the \BibTeX\ format, so independently of 
the journal format. Such a personal reference file can be re-used with any journal.
The formatting of the references and their listing order are made automatically
at compilation (using the information given in the \texttt{.bst} file).

  %{\S}{\bf --- Downloading references} \\
  The references in \BibTeX\ format can be downloaded from the 
Astrophysics Data System (ADS), then stored
in \verb+sola_bibliography_example.bib+  (file name of the present example).
The main extra work is to define a proper and easy label for each citation
(a convenient one is simply first-author-name-year).  Furthermore, it is better
to have the journal names defined by commands (for example 
\texttt{$\backslash$solphys)}, as defined at the beginning of 
this \texttt{.tex} file.
This provides an homogeneity in the reference list and permits flexibility
when changing for journals.   Some caution should be taken for some journals
since ADS does not necessarily provide a uniform format for the
journal names. This is the case for \jgr\  Moreover since
\jgr\ has a new way to refer to an article 
(since 2002 it has no page number), then the ADS references need to be corrected. 
More generally, it is worth verifying
each reference from the original publication (independently of \BibTeX\ use).

  %{\S}{\bf --- Compilation: general} \\
   The full \LaTeX\ and \BibTeX\ compilation is made in four steps: 
\begin{tabbing}
1) {\tt latex filename}\qquad\qquad\=(stores the labels in the {\tt .aux} file)\\
2) {\tt bibtex filename}\>(loads the bibliography in the {\tt .bbl} file)\\
3) {\tt latex filename}\>(reads the .bbl, stores in the {\tt .aux})\\
4) {\tt latex filename}\>(replaces all labels)  
\end{tabbing}
   where \texttt{filename} is the name of your \LaTeX\ file (for example, 
the present file) {\bf without} typing its \texttt{.tex} extension.
If a \texttt{(?)} is still present in the output (at the place of a label),
it means that this label has not been properly defined. 
 (for example, \LaTeX\ labels are case sensitive).
Any undefined label has a warning written in the \texttt{console window}
(it is better to have this window open by default, since \LaTeX\ warning and 
error messages are very useful to localize the problem).

  %{\S}{\bf --- Compilation: simple} \\
  When the references are not changed, it is unnecessary to re-run \BibTeX .
When no new labels are added, running latex once is sufficient to refresh
the \LaTeX\ output. So, except for
the first, and the final time (safest), running \LaTeX\ once is sufficient
in most cases to update the \LaTeX\ output, if the compilation files 
created are not erased! For example \BibTeX\ keeps the bibliography in the usual 
environment,\\
  \verb+ \begin{thebibliography}{} ... \end{thebibliography}+\\
in the file with the \verb+.bbl+ extension.

\subsection{Miscellaneous Other Features} %%%%%%%%%%%%%%
      \label{S-Miscellaneous} 
Long URL's can be quite messy when broken across lines
\texttt{ http://gong.nso.edu/data/magmap/} as normal text,
however the \texttt{breakurl} package does a nice job of this, \textit{e.g.}% \linebreak
\url{http://gong.nso.edu/data/magmap/}.

\section{Conclusion} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \label{S-Conclusion} 
      We hope authors of {\it Solar Physics} will find this guide useful.
Please send us feedback on how to improve it.

  \LaTeX\ is very convenient to write a scientific text, in particular
with the use of labels for figures, tables, and references. Moreover, the labels and list of references are checked by the software against
one another, and, the formatting should be effortless with \BibTeX.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acks}
 The authors thank ... ({\it note the reduced point size})
\end{acks}

\noindent To change a title use an optional parameter:\par
\verb+\begin{acks}[Acknowledgements]...\end{acks}+

%\acknowledgment US spelling: \verb+\acknowledgment+
%\acknowledgement British  spelling: \verb+\acknowledgement+

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix

 After the \verb+\appendix+ command, the sections are referenced with 
capital letters. 
The numbering of equations, figures and labels is 
is just the same as with classical sections.

  \begin{figure}    %%%%%%%%%%%%%%%%%% FIGURE 1 
   \centerline{\includegraphics[width=0.3\textwidth,clip=]{fig1a.eps}
              }
   \caption{Example of a simple figure in an appendix.}
    \label{F-appendix}
  \end{figure}

  \begin{table}
   \caption{ A simple table in an appendix. }
   \label{T-appendix}
    \begin{tabular}{ccclc}     % define the column alignment
                               % l: left, c: center, r: right
      \hline                   % horizontal line
    Rot. & Date & CMEs & CMEs~ & $\alpha$ \\
         &      & obs. & ~cor. & $10^{-2}$Mm$^{-1}$\\
      \hline
    1 & 02--Nov--97 & 16  & 24.1  & -1.26 \\
    2 & 29--Nov--97 & --  & ~2.53 & ~0.94 \\
      \hline
    \end{tabular}
   \end{table}

\section{Abbreviations of some Journal Names} %%%%%%%%%
    \label{S-appendix}
Journal names are abbreviated in {\it Solar Physics} with the IAU
convention (IAU Style Book
published in Transactions of the IAU XXB, 1988, pp. Si-S3.
\url{www.iau.org/Abbreviations.235.0.html}).  Here are a few journals with their \LaTeX\ 
commands (see the beginning of this \texttt{.tex} file).\\
  \verb+\aap     + \aap \\
  \verb+\apj     + \apj \\
  \verb+\jgr     + \jgr \\
  \verb+\mnras   + \mnras \\
  \verb+\pasj    + \pasj \\
  \verb+\pasp    + \pasp \\
  \verb+\solphys +~ \solphys

%%% BIBLIOGRAPHY %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Bibliography Included with \BibTeX } 
      % more powerful
  With \BibTeX\ the formatting will be done automatically for all 
the references cited with one
of the \verb+\cite+ commands (Section~\ref{S-references}).
Besides the usual items, it includes the title of the article 
and the concluding page number.

There is an option \texttt{showbiblabels} which adds a \verb+\bibitem+ 
label at the end of every bibliography item. Label output is made on \verb+\endbibitem+ command.
This option should be used 
just for compatibility while citing a document (see the references below). 
Don't forget to remove the option when document will be finished.

     % format of references provided by the journal (.bst)
\bibliographystyle{spr-mp-sola}
     % name your Bibtex file containing your references (.bib)
\bibliography{sola_bibliography_example}

     % Checking: look if the file containing the ``\bibitem'' exits
     %           so check if the .bbl file exist (bibTeX compilation)
\IfFileExists{\jobname.bbl}{} {\typeout{}
\typeout{****************************************************}
\typeout{****************************************************}
\typeout{** Please run "bibtex \jobname" to obtain} \typeout{**
the bibliography and then re-run LaTeX} \typeout{** twice to fix
the references !}
\typeout{****************************************************}
\typeout{****************************************************}
\typeout{}}

\section*{Bibliography included manually }
     % Require more work
  The articles can be entered, formatted, and ordered  
by the author with the command \verb+\bibitem+.  ADS provides
references in the {\it Solar Physics} format by selecting
the format \verb+SoPh format+ under the menu 
\verb+Select short list format+.    Including the article title
and the concluding page number are optional;
however, we require consistency in the author's choice.
That is, all of the references should have the article title, or none,
and similarly for ending page numbers.

\begin{thebibliography}{}
  \bibitem[\protect\citeauthoryear{{Berger}}{2003}]{Berger03b}
Berger,~M.A.: 
2003, in Ferriz-Mas, A., N{\'u}{\~n}ez, M. (eds.),
    \textit{Advances in Nonlinear Dynamics}, Taylor and Francis Group, 
    London, 345.
  \bibitem[\protect\citeauthoryear{{Berger} and {Field}}{1984}]{BergerF84b}
Berger,~M.A., Field,~G.B.: 
1984, \textit{J. Fluid. Mech.} \textbf{147}, 133.
  \bibitem[\protect\citeauthoryear{{Brown}, {Canfield}, and
                                   {Pevtsov}}{1999}]{Brown99b}
Brown,~M., Canfield,~R., Pevtsov,~A.:
1999, Magnetic Helicity in Space and Laboratory Plasmas, Geophys. Mon. 
      Ser. 111, AGU.
 \bibitem[\protect\citeauthoryear{{Dupont}, {Schmidt}, and {Koutny}}{2007}]{Dupont07}
Dupont, J.-C., Schmidt, F., Koutny, P.: 2007, \solphys{} \textbf{323}, 965. 
\end{thebibliography}

\end{article}

\end{document}

### 2019-11-13 lloveras_2020.tex
agregando midpoints

@@
 \section{Methodology}\label{meto}
+
 \subsection{DEMT reconstructions}\label{demt}
+
 \subsection{AWSoM simulations}\label{awsom}
+
 \subsection{Tracing results along fieldlines}\label{trace}
@@
 
-\begin{figure}%[ht!]
+B)    I - Small-closed field lines.
+Small meaning with apex within the DEMT range of heights.
+This class thoroughly probes the inner core of the Streamer belt, where most of the DOWN loops showed up before, and will show up now.
+
+  II - Large-closed field lines.
+Large meaning their apex surpasses the DEMT range of heights.
+This class is mostly populated by very large trans-equatorial field lines forming the "envelope" of the Streamer belt.
+
+ III - Open field lines.
+
+Carrington maps of the Lat/Lon location at 1.105 Rs of the field lines I (in blue), II (in red), and III (in green).
+This shows in a very graphical way which regions of the corona are probed by the three classes of selected field lines.
+
+\begin{figure}%[h]
 \begin{center}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1105_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1105_Rsun.pdf}
-\caption{Same as Figure \ref{carmaps_demt_2082} but for AWSoM results.}
-\label{carmaps_awsom_2082}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_Rpoint-map.eps}
+%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_Rpoint-map.eps}
+%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
+\caption{Latitude-longitude location of field lines meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082(left panel) and CR-2208 (right panel).
+Different colors identify diverse thermodynamical and magnetic structures, as described in the text.}
+\label{rpoint}
 \end{center}
 \end{figure}
-
-\begin{figure}%[ht!]
-\begin{center}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1105_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1105_Rsun.pdf}
-\caption{Same as Figure \ref{carmaps_demt_2208} but for AWSoM results.}
-\label{carmaps_awsom_2208}
-\end{center}
-\end{figure}
-
-B) Carrington maps of the Lat/Lon location at 1.105 Rs of the field lines I (in blue), II (in red), and III (in green).
-This shows in a very graphical way which regions of the corona are probed by the three classes of selected field lines.
 
@@
 \subsection{Tomography and Models}\label{awsom_res}
-Same as A but for AWSoM model.
-Same as B but for AWSoM model
+
+\begin{figure}%[ht!]
+\begin{center}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1105_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1105_Rsun.pdf}
+\caption{Same as Figure \ref{carmaps_demt_2082} but for AWSoM results.}
+\label{carmaps_awsom_2082}
+\end{center}
+\end{figure}
+
+\begin{figure}%[ht!]
+\begin{center}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1105_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1105_Rsun.pdf}
+\caption{Same as Figure \ref{carmaps_demt_2208} but for AWSoM results.}
+\label{carmaps_awsom_2208}
+\end{center}
+\end{figure}
+
+\begin{figure}%[h]
+\begin{center}
+%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_Rpoint-map.eps}
+%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_Rpoint-map.eps}
+\caption{Same as \ref{rpoint_demt} but for AWSoM loops.}
+\label{rpoint_awsom}
+\end{center}
+\end{figure}
 

### 2019-11-15 lloveras_2020.tex
agregado de plots de perfiles radiales de ne y te

@@
 
+\begin{figure}%[h]
+\begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_cr2082_ne.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_cr2082_te.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_cr2208_ne.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_cr2208_te.eps}
+\caption{Latitude-longitude location of field lines meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082(left panel) and CR-2208 (right panel).
+Different colors identify diverse thermodynamical and magnetic structures, as described in the text.}
+\label{rpoint}
+\end{center}
+\end{figure}
+
 D) Same as C) but for Te.
@@
 C) and D) will be complemented with companion histograms showing in a statistical fashion how AWSoM and DEMT results compare.
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{test_comp_lowlat_ncb.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{test_comp_midlat_S_ncb.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{test_comp_lowlat_lambda.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{test_comp_midlat_S_lambda.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{test_comp_lowlat_tm.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{test_comp_midlat_S_tm.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{test_comp_lowlat_bcb.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{test_comp_midlat_S_bcb.pdf}
+\caption{
+{Comparative statistical distributions of (from top to bottom): the coronal base electron density $\NCB\equiv N_e(r=1.025\,\mrsun)$, the electron density scale height $\lN$, the average electron mean temperature $\aTm$, and the coronal base magnetic field strength $B_{\rm CB}$, along all field lines traced in the low-latitudes of the equatorial streamer (region ES-Ll, left panels) and the southern mid-latitudes of the equatorial streamer (region ES-Sm, right panels), for CR-2081 (solid-blue) and CR-1915 (dashed-red).
+In each panel the median $m$, mean $\mu$, fractional standard deviation $\sigma/\mu$, and number of traced loops $N$, are indicated.}
+}
+\label{compES}
+\end{center}
+\end{figure}
+
+For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were separated into the coronal {regions described in Section \ref{regions} and summarized in Table \ref{tabregions}}.
+For each field line, the data points of electron density and electron mean temperature versus height were fitted to the functions given by Equations 5 and 6 of Section \ref{trace}.
+As a result, the footpoint electron density $N_0$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $a=\textrm{d}T_m/\textrm{d}r$, and the height-averaged (along the loop) electron mean temperature $\aTm$.
+As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data versus height was used to compute the {coronal base electron density} here defined as $\NCB\equiv N_e(r=1.025\,\mrsun)$.
+Also, for each field line the coronal base magnetic field strength $B_{\rm CB}\equiv B(r=1.025\,\mrsun)$ and its height-averaged value along the loop $\left<B\right>$ were also computed.
+
+\begin{figure}[ht!]
+\begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{test_comp_open_S_L_ncb.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{test_comp_open_S_H_ncb.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{test_comp_open_S_L_lambda.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{test_comp_open_S_H_lambda.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{test_comp_open_S_L_tm.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{test_comp_open_S_H_tm.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{test_comp_open_S_L_bcb.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{test_comp_open_S_H_bcb.pdf}
+\caption{Same as Figure \ref{compES} but for all field lines traced in the low-latitudes of the southern coronal hole (region CH-Sl, left panels) and the high-latitudes of the southern coronal hole (region CH-Sh, right panels).}
+\label{compCH}
+\end{center}
+\end{figure}
 

### 2019-11-19 lloveras_2020.tex
nuevas imagenes

--- 2019-11-13 lloveras_2020.tex
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_Rpoint-map.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_Rpoint-map.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
@@
 
+\begin{figure}%[h]
+\begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
+\caption{A plot of the average $N_e(r)$ and $T_e(r)$ along all field lines of type I (in blue), of type II (in red) and of type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082(top panel) and CR-2208 (bottom panel).
+In solid lines DEMT traced data and in dashed lines AWSoM data.}
+\label{rpoint}
+\end{center}
+\end{figure}
+
 D) Same as C) but for Te.
@@
 C) and D) will be complemented with companion histograms showing in a statistical fashion how AWSoM and DEMT results compare.
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
+\caption{
+{Comparative statistical distributions of (from left to right): the coronal base electron density $\NCB\equiv N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type I, top panels), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels) for CR-2082.
+In blue the data of DEMT are shown while those of AWSoM in red.
+In each panel the median $m$ is indicated.}
+}
+\label{histos_2082}
+\end{center}
+\end{figure}
+
+For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were separated into the coronal {regions described in Section \ref{regions} and summarized in Table \ref{tabregions}}.
+For each field line, the data points of electron density and electron mean temperature versus height were fitted to the functions given by Equations 5 and 6 of Section \ref{trace}.
+As a result, the footpoint electron density $N_0$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $a=\textrm{d}T_m/\textrm{d}r$, and the height-averaged (along the loop) electron mean temperature $\aTm$.
+As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data versus height was used to compute the {coronal base electron density} here defined as $\NCB\equiv N_e(r=1.025\,\mrsun)$.
+Also, for each field line the coronal base magnetic field strength $B_{\rm CB}\equiv B(r=1.025\,\mrsun)$ and its height-averaged value along the loop $\left<B\right>$ were also computed.
+
+\begin{figure}[ht!]
+\begin{center}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_Tm.eps}\\
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_Tm.eps}\\
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_Tm.eps}
+\caption{Same as Figure \ref{histos_2082} but for CR2208.}
+\label{histos_2208}
+\end{center}
+\end{figure}
 
@@
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_Rpoint-map.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.eps}
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_Rpoint-map.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.eps}
 \caption{Same as \ref{rpoint_demt} but for AWSoM loops.}

### 2019-11-21 lloveras_2020.tex
nuevos graficos

@@
 
-\author[addressref={},corref,email={nishthas@umich.edu}]{\inits{N.}\fnm{Nishtha}\lnm{Sachdeva}\orcid{1}}
+\author[addressref={aff1,aff3,aff2},corref,email={cmaccormack@iafe.uba.ar}]{\inits{C.}\fnm{Cecilia}~\lnm{Mac Cormack}}
 
-\author[addressref={},corref,email={chipm@umich.edu}]{\inits{W.}\fnm{Ward}\lnm{Manchester IV}\orcid{2}}
+\author[addressref={aff4},corref,email={nishthas@umich.edu}]{\inits{N.}\fnm{Nishtha}~\lnm{Sachdeva}\orcid{1}}
 
-\author[addressref={},corref,email={bartvand@umich.edu}]{\inits{B.}\fnm{Bartholomeus}\lnm{Van der Holst}\orcid{3}}
+\author[addressref={aff4},corref,email={chipm@umich.edu}]{\inits{W.}\fnm{Ward}~\lnm{Manchester IV}\orcid{2}}
+
+\author[addressref={aff4},corref,email={bartvand@umich.edu}]{\inits{B.}\fnm{Bartholomeus}~\lnm{Van der Holst}\orcid{3}}
 
@@
 Different colors identify diverse thermodynamical and magnetic structures, as described in the text.}
-\label{rpoint}
+\label{rpoint_demt}
 \end{center}
@@
 
-For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were separated into the coronal {regions described in Section \ref{regions} and summarized in Table \ref{tabregions}}.
+%For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were separated into the coronal {regions described in Section \ref{regions} and summarized in Table \ref{tabregions}}.
 For each field line, the data points of electron density and electron mean temperature versus height were fitted to the functions given by Equations 5 and 6 of Section \ref{trace}.
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.eps}
-\caption{Same as \ref{rpoint_demt} but for AWSoM loops.}
+\caption{Same as Figure \ref{rpoint_demt} but for AWSoM loops.}
 \label{rpoint_awsom}
+\end{center}
+\end{figure}
+
+\begin{figure}%[ht!]
+\begin{center}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105.eps}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
+\caption{Longitude-averaged of DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$.
+On the left CR2082 and on the right CR2208, the vertical black lines indicates the longitude-averaged latitudes of the open/close magnetic boundaries.}
+\label{perf_lon_ne}
+\end{center}
+\end{figure}
+
+\begin{figure}%[ht!]
+\begin{center}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995.eps}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
+\caption{Longitude-averaged of radial wind speed at $6\,\mrsun$ given by AWSoM.}
+\label{perf_lon_vr}
 \end{center}

### 2019-11-24 lloveras_2020.tex
acomodando graficos

@@
 
+For both rotations, the DEMT AWSoM 3D maps of electron density $N_e$ and electron mean temperature $T_\textrm{m}$ were traced along the magnetic field lines modeled with AWSoM as described at the end of Section \ref{awsom}.
+In the case of closed loops, results were separated into their two {legs}, defined as the two segments that go from the coronal base up to the apex.
+
+Se eligen loops con $abs(person_temp) mayor a .5$ lo cual nos permite descartar loops QI.
+OBS: Esto es valido para hasta la fig 7 inclusive.
+
+For each open field line, and for each leg of the closed ones, an exponential fit was then applied to the $N_e(r)$ data points, and a linear fit applied to the $T_m(r)$ data points, as described by
+
+\begin{eqnarray}
+N_e &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]},\label{Nfit}\\
+T_\textrm{m} &=& a\,r\,+\,b,\label{Tfit}
+\end{eqnarray}
+
+\noindent
+where $h \equiv r - 1\,\mrsun$, and $a$ and $b$ are constants.
+
+In the case of the electron density, the fitted function corresponds to the isothermal hydrostatic equilibrium solution, allowing for variation of the solar gravitational acceleration with height.
+After computing the footpoint ($r=1.0\,\mrsun$) electron density $N_{0}\,[\cm^{-3}]$ and scale height $\lN\,[\mrsun]$, this choice of function provides a straightforward means to directly evaluate how compatible is the observed coronal thermodynamical state with the hydrostatic solution, as analyzed in Section \ref{qi}.
+In the case of the DEMT electron mean temperature, the linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $a = \textrm{d}T_m/\textrm{d}r\,[\MK/\mrsun]$ along each leg/loop.
+
+*Nos quedamos con los fiteos que cumplen test de hipotesis chi cuadrado en temp y densidad.
+OBS: Esta es la seleccion para las figuras 8 en adelante.
+
+*Types of field lines
+ I - Small-closed field lines.
+Small meaning with apex within the DEMT range of heights.
+This class thoroughly probes the inner core of the Streamer belt, where most of the DOWN loops showed up before, and will show up now.
+
+  II - Large-closed field lines.
+Large meaning their apex surpasses the DEMT range of heights.
+This class is mostly populated by very large trans-equatorial field lines forming the "envelope" of the Streamer belt.
+
+ III - Open field lines.
+
 \section{Results}\label{resu} 
 \subsection{Tomographic Results}\label{demt_res}
-A) Carrington (Lat/Lon) maps of the DEMT products Ne and Te at selected heights 1.025, 1.105, 1.205 Rsun, over plotting the Open/Closed (O/C) boundary from the AWSoM model.
-This plot gives initial CONTEXT.
 
-\begin{figure}%[ht!]
+\begin{figure}[h!]
 \begin{center}
@@
 \caption{Carrington maps of DEMT results: $N_e$ (left panels) and $T_\textrm{m}$ (right panels) for CR-2082.
-Top, middle and bottom panels show the results at three heliocentric heights, $1.025$ ,$1.065$ $1.105\,\mrsun$, respectively.
+Top, middle and bottom panels show the results at three heliocentric heights, $1.025$ ,$1.065$ and $1.105\,\mrsun$, respectively.
 Black voxels correspond to non-reconstructed regions and thick-black curves indicate the open/closed boundaries.}
@@
 
-\begin{figure}%[ht!]
+\begin{figure}[h!]
 \begin{center}
@@
 
-B)    I - Small-closed field lines.
-Small meaning with apex within the DEMT range of heights.
-This class thoroughly probes the inner core of the Streamer belt, where most of the DOWN loops showed up before, and will show up now.
-
-  II - Large-closed field lines.
-Large meaning their apex surpasses the DEMT range of heights.
-This class is mostly populated by very large trans-equatorial field lines forming the "envelope" of the Streamer belt.
-
- III - Open field lines.
-
-Carrington maps of the Lat/Lon location at 1.105 Rs of the field lines I (in blue), II (in red), and III (in green).
-This shows in a very graphical way which regions of the corona are probed by the three classes of selected field lines.
-
-\begin{figure}%[h]
+\begin{figure}[h!]
 \begin{center}
@@
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
-\caption{Latitude-longitude location of field lines meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082(left panel) and CR-2208 (right panel).
-Different colors identify diverse thermodynamical and magnetic structures, as described in the text.}
+\caption{Latitude-longitude location of each leg of type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082 (left panel) and CR-2208 (right panel).}
 \label{rpoint_demt}
@@
 
-C) A plot of the average DEMT Ne(r) along all field lines of type I (in solid-blue), of type II (in solid-red and of type III (in solid-green).
-Over plotted in the same color code but in dashed-line style the AWSoM results along the same three statistical sample of field-lines.
-In particular, this shows the global 3D agreement between AWSoM and DEMT in distinct magnetic structures and carefully tracing along field lines
+\subsection{Tomography and Models}\label{awsom_res}
 
-\begin{figure}%[h]
+\begin{figure}%[ht!]
+\begin{center}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1105_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1105_Rsun.pdf}
+\caption{Same as Figure \ref{carmaps_demt_2082} but for AWSoM results.}
+\label{carmaps_awsom_2082}
+\end{center}
+\end{figure}
+
+\begin{figure}%[ht!]
+\begin{center}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1105_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1105_Rsun.pdf}
+\caption{Same as Figure \ref{carmaps_demt_2208} but for AWSoM results.}
+\label{carmaps_awsom_2208}
+\end{center}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.eps}
+%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.eps}
+\caption{Same as Figure \ref{rpoint_demt} but for AWSoM loops.}
+\label{rpoint_awsom}
+\end{center}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_updowntriple_gradt.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_updowntriple_gradt.eps}
+\caption{Frequency histogram of the temperature radial gradient of along each leg of type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (left panel) and CR-2208 (right panel).
+In solid lines DEMT traced data and in dashed lines AWSoM data.}
+\label{gradientes}
+\end{center}
+\end{figure}
+
+\begin{figure}[h!]
 \begin{center}
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
-\caption{A plot of the average $N_e(r)$ and $T_e(r)$ along all field lines of type I (in blue), of type II (in red) and of type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082(top panel) and CR-2208 (bottom panel).
-In solid lines DEMT traced data and in dashed lines AWSoM data.}
-\label{rpoint}
+\caption{Average fitted of $N_e(r)$ and $T_e(r)$ along all field lines of type I (in blue), of type II (in red) and of type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082(top panel) and CR-2208 (bottom panel).
+In solid lines DEMT traced results and in dashed lines AWSoM results.}
+\label{perfiles_promedio}
 \end{center}
@@
 
-D) Same as C) but for Te.
-
-C) and D) will be complemented with companion histograms showing in a statistical fashion how AWSoM and DEMT results compare.
-
-\begin{figure}[h]
+\begin{figure}[h!]
 \begin{center}
@@
 \includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
-\caption{
-{Comparative statistical distributions of (from left to right): the coronal base electron density $\NCB\equiv N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type I, top panels), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels) for CR-2082.
+\caption{Comparative statistical distributions of (from left to right): the coronal base electron density $\NCB\equiv N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type I, top panels), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels) for CR-2082.
 In blue the data of DEMT are shown while those of AWSoM in red.
 In each panel the median $m$ is indicated.}
-}
+
 \label{histos_2082}
@@
 
-\begin{figure}[ht!]
+\begin{figure}[h!]
 \begin{center}
@@
 
-\subsection{Tomography and Models}\label{awsom_res}
-
-\begin{figure}%[ht!]
-\begin{center}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1105_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1105_Rsun.pdf}
-\caption{Same as Figure \ref{carmaps_demt_2082} but for AWSoM results.}
-\label{carmaps_awsom_2082}
-\end{center}
-\end{figure}
-
-\begin{figure}%[ht!]
-\begin{center}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1105_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1105_Rsun.pdf}
-\caption{Same as Figure \ref{carmaps_demt_2208} but for AWSoM results.}
-\label{carmaps_awsom_2208}
-\end{center}
-\end{figure}
-
-\begin{figure}%[h]
-\begin{center}
-%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.eps}
-%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.eps}
-\caption{Same as Figure \ref{rpoint_demt} but for AWSoM loops.}
-\label{rpoint_awsom}
-\end{center}
-\end{figure}
-
-\begin{figure}%[ht!]
+\begin{figure}[h!]
 \begin{center}

### 2019-11-25 lloveras_2020.tex
nuevas figuras

@@
 
+Once the LDEM is determined at each voxel, the average {squared electron density $N_e^2$} and the electron mean temperature $T_\textrm{m}$ in the voxel can be computed by taking its zeroth and first moments over temperature.
+More specifically, at the $i$-th voxel,
+\begin{eqnarray}\label{momento1}
+ N_{e,i}^2 &=& \int\,\textrm{d}T\,\LDEM_i(T),\label{Ne} \\ 
+\label{momento2}
+ T_{\textrm{m},i}   &=& \frac{1}{N_{e,i}^2}\,\int\,\textrm{d}T\,T\,\LDEM_i(T),\label{Tm} 
+\end{eqnarray}
+
+so that the final product of DEMT is in the form of 3D maps of the electron density and mean temperature.
+{Once again, these relationships (derived in detail in \citealt{frazin_2009}, see Appendix C) are similar to those in standard DEM analysis, in which the line-of-sight DEM appears instead of the voxel's LDEM, and the EM appears instead of the squared electron density.}
+
 \subsection{AWSoM simulations}\label{awsom}
@@
 
-Se eligen loops con $abs(person_temp) mayor a .5$ lo cual nos permite descartar loops QI.
-OBS: Esto es valido para hasta la fig 7 inclusive.
+\textcolor{red}{Se eligen loops con abs(person temp) mayor a .5 lo cual nos permite descartar loops QI.
+OBS: Esto es valido para hasta la fig 7 inclusive.}
 
@@
 
-\begin{eqnarray}
-N_e &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]},\label{Nfit}\\
-T_\textrm{m} &=& a\,r\,+\,b,\label{Tfit}
+\begin{eqnarray}\label{Nfit}
+N_e &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]}\\
+\label{Tfit}
+T_\textrm{m} &=& a\,r\,+\,b
 \end{eqnarray}
@@
 In the case of the electron density, the fitted function corresponds to the isothermal hydrostatic equilibrium solution, allowing for variation of the solar gravitational acceleration with height.
-After computing the footpoint ($r=1.0\,\mrsun$) electron density $N_{0}\,[\cm^{-3}]$ and scale height $\lN\,[\mrsun]$, this choice of function provides a straightforward means to directly evaluate how compatible is the observed coronal thermodynamical state with the hydrostatic solution, as analyzed in Section \ref{qi}.
+After computing the footpoint ($r=1.0\,\mrsun$) electron density $N_{0}\,[\cm^{-3}]$ and scale height $\lN\,[\mrsun]$, this choice of function provides a straightforward means to directly evaluate how compatible is the observed coronal thermodynamical state with the hydrostatic solution.
 In the case of the DEMT electron mean temperature, the linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $a = \textrm{d}T_m/\textrm{d}r\,[\MK/\mrsun]$ along each leg/loop.
 
-*Nos quedamos con los fiteos que cumplen test de hipotesis chi cuadrado en temp y densidad.
-OBS: Esta es la seleccion para las figuras 8 en adelante.
+\textcolor{red}{*Nos quedamos con los fiteos que cumplen test de hipotesis chi cuadrado en temp y densidad.
+OBS: Esta es la seleccion para las figuras 8 en adelante.}
 
-*Types of field lines
+*Types of field lines\\
  I - Small-closed field lines.
@@
 \section{Results}\label{resu}
+
 \subsection{Tomographic Results}\label{demt_res}
+
+Once the LDEM was determined for each rotation, the electron density $N_e$ and electron mean temperature $T_\textrm{m}$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}.
+As an example, Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show the results for both rotations at $r=1.025, 1.065 and 1.105\,\mrsun$.
+Black voxels correspond to non-reconstructed regions.
 
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
-\caption{Longitude-averaged of DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$.
+\caption{Longitude-averaged of electron density for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$.
 On the left CR2082 and on the right CR2208, the vertical black lines indicates the longitude-averaged latitudes of the open/close magnetic boundaries.}

### 2019-11-26 lloveras_2020.tex
algo de texto

@@
 \textcolor{red}{*Nos quedamos con los fiteos que cumplen test de hipotesis chi cuadrado en temp y densidad.
-OBS: Esta es la seleccion para las figuras 8 en adelante.}
+OBS: Esta es la seleccion para las figuras 8 en adelante. Citar numerical recipes seccion 15.2}
 
@@
 Black voxels correspond to non-reconstructed regions.
+
+\textcolor{red}{
+*Comentarios descriptivos sobre las rotaciones:
+-Simetria
+-CH
+-Matcheo entre open-closed boundaries y las estructuras termodinamicas.
+}
 
@@
 
+\textcolor{red}{
+*Para las piernas trazadas que cumplen  |pearson de temp| > 0.5 se calcularon los gradientes de temp que cumplen test de hipotesis.
+Estos gradientes se muestran en la Figura \ref{gradientes} para las 3 regiones definidas para ambas rotaciones.
+Esto muestra up y down loops.
+OBS: esto da pie a hablar y proponer mejoras en la conversion de modos de alfven. citar paper fede.
+*Como el modelo awsom no presenta down loops, se selecciona de ahora en mas los loops con pearson de temp > 0.5
+}
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_updowntriple_gradt.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_updowntriple_gradt.eps}
+\caption{Frequency histogram of the temperature radial gradient of along each leg of type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (left panel) and CR-2208 (right panel).
+In solid lines DEMT traced data and in dashed lines AWSoM data.}
+\label{gradientes}
+\end{center}
+\end{figure}
+
+\textcolor{red}{
+For the two analyzed rotations, Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of all field lines that meet the criteria listed in Section \ref{trace} at $1.105\,\mrsun$.
+}
+
 \begin{figure}[h!]
@@
 
-\begin{figure}%[ht!]
+\textcolor{red}{Se presentan los resultados de Ne y Te del modelo AWSoM}
+
+\begin{figure}[h!]
 \begin{center}
@@
 \end{figure}
+
+\textcolor{red}{Se presentan los midpoints para awsom que lucen mas rellenos xq no hay down loops y todo es super suave.}
 
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_updowntriple_gradt.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_updowntriple_gradt.eps}
-\caption{Frequency histogram of the temperature radial gradient of along each leg of type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (left panel) and CR-2208 (right panel).
-In solid lines DEMT traced data and in dashed lines AWSoM data.}
-\label{gradientes}
-\end{center}
-\end{figure}
-
-\begin{figure}[h!]
-\begin{center}
 \includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
-\caption{Average fitted of $N_e(r)$ and $T_e(r)$ along all field lines of type I (in blue), of type II (in red) and of type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082(top panel) and CR-2208 (bottom panel).
+\caption{Average fitted of $N_e(r)$ and $T_e(r)$ along all field lines of type I (in blue), of type II (in red) and of type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (top panel) and CR-2208 (bottom panel).
 In solid lines DEMT traced results and in dashed lines AWSoM results.}
@@
 \end{figure}
+
+\textcolor{red}{
+As way of example, Figure \ref{histos_2082} and \ref{histos_2208} shows the statistical results of both rotations for the three types of field lines traced with DEMT (blue) and AWSoM results (red).
+From left to right the panels show the statistical distribution of $\NCB$, $\lN$, $\aTm$ and $B_{\rm CB}$.
+}
 
@@
 In each panel the median $m$ is indicated.}
-
 \label{histos_2082}
@@
 
-E) As the two rotations are strongly axis-symmetric we want to show the longitude-averaged results of DEMT at a low height, say 1.105 Rsun, along with AWSoM results.
+%E) As the two rotations are strongly axis-symmetric we want to show the longitude-averaged results of DEMT at a low height, say 1.105 Rsun, along with AWSoM results.
 In the attached plot we show the DEMT and AWSoM longitude-averaged results at 1.105 Rsun in the top two panels (one for each rotation).
@@
 
-This plot (E) has never been shown before and I believe it is a very nice result.
+%This plot (E) has never been shown before and I believe it is a very nice result.
 There are of course previous studies on this, but this would be the first time this is evaluated with tomography.

### 2019-11-26 lloveras_2020.tex
mas texto

@@
 
+Being the place where the solar atmosphere is heated and the solar wind accelerated, and where impulsive events such as solar flares and coronal mass ejections are energized, observation and modeling of the solar corona are tasks of great relevance to improve our understanding of the Sun-Earth environment.
+To advance our knowledge of the physics of the solar corona, as well as to improve its three-dimensional (3D) models, information derived from observational data plays a key role.
+Solar rotational tomography is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar corona at a global scale.
+
 \section{Methodology}\label{meto}
@@
 
-Once the LDEM is determined at each voxel, the average {squared electron density $N_e^2$} and the electron mean temperature $T_\textrm{m}$ in the voxel can be computed by taking its zeroth and first moments over temperature.
+Once the LDEM is determined at each voxel, the average squared electron density $\langle N_e^2 \rangle$ and the electron mean temperature $T_\textrm{m}$ in the voxel can be computed by taking its zeroth and first moments over temperature.
 More specifically, at the $i$-th voxel,
@@
 
-so that the final product of DEMT is in the form of 3D maps of the electron density and mean temperature.
-{Once again, these relationships (derived in detail in \citealt{frazin_2009}, see Appendix C) are similar to those in standard DEM analysis, in which the line-of-sight DEM appears instead of the voxel's LDEM, and the EM appears instead of the squared electron density.}
+so that the final product of DEMT is in the form of 3D maps of the electron density and mean temperature. These relationships was derived in detail in \citealt{frazin_2009} (see Appendix C).
+
+\textcolor{red}{aclarar que consideramos Ne como $\sqrt{<N_e ^2>}$.}
 
@@
 
-For both rotations, the DEMT AWSoM 3D maps of electron density $N_e$ and electron mean temperature $T_\textrm{m}$ were traced along the magnetic field lines modeled with AWSoM as described at the end of Section \ref{awsom}.
-In the case of closed loops, results were separated into their two {legs}, defined as the two segments that go from the coronal base up to the apex.
+For both rotations, the DEMT and AWSoM 3D maps of electron density $N_e$, electron mean temperature $T_\textrm{m}$ and electron temperature $T_\textrm{e}$ respectively were traced along the magnetic field lines modeled using AWSoM as described at the end of Section \ref{awsom}.
+In the case of closed loops, results were separated into their two legs, defined as the two segments that go from the coronal base up to the apex.
 
@@
 In the case of the electron density, the fitted function corresponds to the isothermal hydrostatic equilibrium solution, allowing for variation of the solar gravitational acceleration with height.
-After computing the footpoint ($r=1.0\,\mrsun$) electron density $N_{0}\,[\cm^{-3}]$ and scale height $\lN\,[\mrsun]$, this choice of function provides a straightforward means to directly evaluate how compatible is the observed coronal thermodynamical state with the hydrostatic solution.
-In the case of the DEMT electron mean temperature, the linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $a = \textrm{d}T_m/\textrm{d}r\,[\MK/\mrsun]$ along each leg/loop.
+After computing the footpoint ($r=1.0\,\mrsun$) electron density $N_{0}\,[\cm^{-3}]$ and scale height $\lN\,[\mrsun]$\textcolor{blue}{, this choice of function provides a straightforward means to directly evaluate how compatible is the observed coronal thermodynamical state with the hydrostatic solution}.
+The linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $a = \textrm{d}T_m/\textrm{d}r\,[\MK/\mrsun]$ along each leg.
+
+\textcolor{red}{Podriamos comentar acá las mejoras hechas a la tomo desde la ultima publicacion.}
+DEMT has been improved since the previously published work.
+We now perform hollow-tomography with the EUV images, \textcolor{red}{definir hollow-tom} and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.
 
@@
 
-*Types of field lines\\
+For the two targeted rotations, DEMT and AWSoM resuls were traced along the AWSoM field lines, which provides a way to characterize the global thermodynamic state of the inner solar corona and to compare them.
+To that end three different types of magnetic lines corresponding with three different types of magnetic structures where selected:
+
   I - Small-closed field lines.
 Small meaning with apex within the DEMT range of heights.
-This class thoroughly probes the inner core of the Streamer belt, where most of the DOWN loops showed up before, and will show up now.
+%This class thoroughly probes the inner core of the Streamer belt, where most of the DOWN loops showed up before, and will show up now.
 
@@
 \includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1105_Rsun.pdf}
-\caption{Same as Figure \ref{carmaps_demt_2082} but for AWSoM results.}
+\caption{Same as Figure \ref{carmaps_awsom_2082} but for AWSoM results.}
 \label{carmaps_awsom_2082}
@@
 \includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1105_Rsun.pdf}
-\caption{Same as Figure \ref{carmaps_demt_2208} but for AWSoM results.}
+\caption{Same as Figure \ref{carmaps_awsom_2208} but for AWSoM results.}
 \label{carmaps_awsom_2208}
@@
 
-%E) As the two rotations are strongly axis-symmetric we want to show the longitude-averaged results of DEMT at a low height, say 1.105 Rsun, along with AWSoM results.
-In the attached plot we show the DEMT and AWSoM longitude-averaged results at 1.105 Rsun in the top two panels (one for each rotation).
-The vertical lines indicate the longitude-averaged latitudes of the North and South OC boundary.
-The LOW panels show the longitude-averaged AWSoM wind speed Vr at 6 Rsun, where all field lines are open.
-The HCS location is indicated by the minimum of the speed curve.
-Everything to the South of the HCS maps down to the Southern OPEN region in the top panels, and the same for the Northern hemisphere.
-It is pretty obvious the ANTI-CORRELATION between the tomographic Ne at low heights (coronal source region of the wind) and the Vr.
-
 %This plot (E) has never been shown before and I believe it is a very nice result.
@@
 This will be nice to do also for the July-2-2019 Eclipse rotation that we will analyze after this paper.
+
+Visual inspection of the results for CR-2082 in Figure \ref{carmaps_demt_2082} and \ref{carmaps_awsom_2082} reveals two clearly distinct thermodynamical states between the streamer (closed field lines) and the coronal holes (open lines).
+\\
+
+Figure \ref{perf_lon_ne} shows for both rotations the DEMT and AWSoM longitude-averaged variation of the electron density at the height $r=1.105\,\mrsun$.
+Density shows higher values in the low-latitudes of the streamer and a nearly monotonic decrease towards the poles.
+The vertical black lines indicates the longitude-averaged latitudes of the open/close magnetic boundaries (excluding the AR in the case of CR-2082)
 
@@
 
+Figure \ref{perf_lon_vr} show the longitude-averaged AWSoM radial wind speed $V_r$ at $6\,\mrsun$, where all field lines are open.
+The heliocentric current sheet (HCS) location is indicated by the minimum of the speed curve.\\
+
+Everything to the south of the HCS maps down to the southern open region in the Figures \ref{perf_lon_ne}, and the same for the northern hemisphere, showing an anti-correlation between $N_e$ at low heights and $V_r$.
+
 \begin{figure}[h!]
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
-\caption{Longitude-averaged of radial wind speed at $6\,\mrsun$ given by AWSoM.}
+\caption{Longitude-averaged of radial wind speed at $6\,\mrsun$ given by AWSoM for both rotations.}
 \label{perf_lon_vr}
@@
 %
-% \bibliographystyle{spr-mp-sola}
-% \bibliography{<bib file>}  
+\bibliographystyle{spr-mp-sola}
+\bibliography{solphys_dglloveras}  
 %

### 2019-11-27 lloveras_2020.tex
cambio de graficos, uno nuevo agregado, otro eliminado

@@
 \begin{eqnarray}\label{momento1}
- N_{e,i}^2 &=& \int\,\textrm{d}T\,\LDEM_i(T),\label{Ne} \\ 
+ \langle N_{e,i}^2 \rangle &=& \int\,\textrm{d}T\,\LDEM_i(T),\label{Ne} \\ 
 \label{momento2}
- T_{\textrm{m},i}   &=& \frac{1}{N_{e,i}^2}\,\int\,\textrm{d}T\,T\,\LDEM_i(T),\label{Tm} 
+ T_{\textrm{m},i}   &=& \frac{1}{\langle N_{e,i}^2 \rangle}\,\int\,\textrm{d}T\,T\,\LDEM_i(T),\label{Tm} 
 \end{eqnarray}
@@
 
+\textcolor{red}{que quede claro que de ahora en mas solo consideramos ajustes de loops up, es decir pearson temp > 0.5 debido a que awsom solo tiene up.}
+
 \section{Results}\label{resu}
@@
 OBS: esto da pie a hablar y proponer mejoras en la conversion de modos de alfven. citar paper fede.
-*Como el modelo awsom no presenta down loops, se selecciona de ahora en mas los loops con pearson de temp > 0.5
+%*Como el modelo awsom no presenta down loops, se selecciona de ahora en mas los loops con pearson de temp > 0.5
 }
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_updowntriple_gradt.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_updowntriple_gradt.eps}
-\caption{Frequency histogram of the temperature radial gradient of along each leg of type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (left panel) and CR-2208 (right panel).
+%\begin{figure}[h!]
+%\begin{center}
+%\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_updowntriple_gradt.eps}
+%\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_updowntriple_gradt.eps}
+%\caption{Frequency histogram of the temperature radial gradient of along each leg of type I (in blue), type II %(in red) and type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (left panel) and CR-2208 (right panel).
 In solid lines DEMT traced data and in dashed lines AWSoM data.}
-\label{gradientes}
-\end{center}
-\end{figure}
+%\label{gradientes}
+%\end{center}
+%\end{figure}
 
@@
 \label{rpoint_demt}
+\end{center}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
+\caption{Comparative statistical distributions of (from left to right): the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type I, top panels), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels).
+for CR-2082.
+DEMT results of CR2082 are shown in blue while those of CR2208 in red.
+In each panel the median $m$ is indicated.}
+\label{histos_fulldemt}
 \end{center}
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
-\caption{Average fitted of $N_e(r)$ and $T_e(r)$ along all field lines of type I (in blue), of type II (in red) and of type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (top panel) and CR-2208 (bottom panel).
+\caption{Average fits of $N_e(r)$ and $T_e(r)$ along all field lines of type I (in blue), of type II (in red) and of type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (top panel) and CR-2208 (bottom panel).
 In solid lines DEMT traced results and in dashed lines AWSoM results.}
@@
 \includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
-\caption{Comparative statistical distributions of (from left to right): the coronal base electron density $\NCB\equiv N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type I, top panels), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels) for CR-2082.
+\caption{Comparative statistical distributions of (from left to right): the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type I, top panels), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels) for CR-2082.
 In blue the data of DEMT are shown while those of AWSoM in red.

### 2019-12-03 lloveras_2020.tex
muchos cambios en figuras

@@
 \begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.eps}
+%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.eps}
+%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
-\caption{Latitude-longitude location of each leg of type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082 (left panel) and CR-2208 (right panel).}
+\caption{Latitude-longitude location of each leg of type 0 (in cyan), type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082 (left panel) and CR-2208 (right panel).}
 \label{rpoint_demt}
@@
 \begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_fulltriple_gradt.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
+\caption{Histogram of the temperature radial gradient along each leg of type 0 (in cyan), type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082 (left panel) and CR-2208 (right panel).}
+\label{gradt_demt}
+\end{center}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
 \includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
@@
 \includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
-\caption{Comparative statistical distributions of (from left to right): the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type I, top panels), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels).
+\caption{Comparative statistical distributions of (from left to right): the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type 0 - down loops and type I - up loops), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels).
 for CR-2082.
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105.eps}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105.eps}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105.eps}
+\caption{Longitude-averaged, in both rotations, of electron density (top) and electron temperature (bottom) for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$.
+On the left CR2082 and on the right CR2208, the vertical black lines indicates the longitude-averaged latitudes of the open/close magnetic boundaries.}
+\label{perf_lon_ne}
+\end{center}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up_short.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up_short.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up_short.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_short.eps}
 \caption{Average fits of $N_e(r)$ and $T_e(r)$ along all field lines of type I (in blue), of type II (in red) and of type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (top panel) and CR-2208 (bottom panel).
@@
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105.eps}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
-\caption{Longitude-averaged of electron density for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$.
-On the left CR2082 and on the right CR2208, the vertical black lines indicates the longitude-averaged latitudes of the open/close magnetic boundaries.}
-\label{perf_lon_ne}
-\end{center}
-\end{figure}
-
 Figure \ref{perf_lon_vr} show the longitude-averaged AWSoM radial wind speed $V_r$ at $6\,\mrsun$, where all field lines are open.

### 2019-12-03 lloveras_2020.tex
graficos de energia

@@
 
-  I - Small-closed field lines.
-Small meaning with apex within the DEMT range of heights.
+  0 - Small-closed field lines footlat $<30$ y gradt neg. where most of the DOWN loops showed up before
+
+  I - Small-closed field lines. Small meaning with apex within the DEMT range of heights. gradt pos
    %This class thoroughly probes the inner core of the Streamer belt, where most of the DOWN loops showed up before, and will show up now.
@@
 This class is mostly populated by very large trans-equatorial field lines forming the "envelope" of the Streamer belt.
+footlat $>30$ y gradt pos
 
- III - Open field lines.
+ III - Open field lines. footlat $>60$ y gradt pos
 
@@
 \label{histos_fulldemt}
+\end{center}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccenergia.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_cgenergia.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccenergia.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
+\caption{Statistical results of the loop integrated energy flux quantities $\phi_r,\phi_c, and \phi_h$ for CR2082 (top) and CR2208 (bottom).
+Left/right panels correspond to the type 0-1 and type 2 respectively \textcolor{red}{el tipo 2 tmb tiene down!
+Aca hay que tomar una desicion para no marear al lector!
+Pero lo dejo asi internamente para compararlo con figura 5 y 6 del aper de Mac Cormack}}
+\label{gradt_demt}
 \end{center}

### 2019-12-04 lloveras_2020.tex
retoques a captions, sugerencias Fede

@@
 Based on EUV data of space borne instruments, SRT allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun.
-We carry out a study of the corona combining tomographic reconstructions with MHD simulations of the latest version of the Alfvén Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF).
+We carry out a study of the corona combining tomographic reconstructions with MHD simulations of the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF).
 Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24.
@@
 \subsection{DEMT reconstructions}\label{demt} 
+\textcolor{red}{*Tratado de imagenes}
+\textcolor{red}{*FBE}
+\textcolor{red}{*LDEM}
 
@@
 
-\textcolor{red}{aclarar que consideramos Ne como $\sqrt{<N_e ^2>}$.}
+\textcolor{red}{*aclarar que consideramos Ne como $\sqrt{<N_e ^2>}$.}
+
+\textcolor{red}{*Mejoras de la tecnica con respecto a trabajos previos}
 
 \subsection{AWSoM simulations}\label{awsom} 
+\textcolor{red}{*Que es, que modela, que datos usa, y que se obtiene en general y en particular para este trabajo}
 
@@
 
-\textcolor{red}{Podriamos comentar acá las mejoras hechas a la tomo desde la ultima publicacion.}
 DEMT has been improved since the previously published work.
@@
 Once the LDEM was determined for each rotation, the electron density $N_e$ and electron mean temperature $T_\textrm{m}$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}.
-As an example, Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show the results for both rotations at $r=1.025, 1.065 and 1.105\,\mrsun$.
+As an example, Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show the results for both rotations at $r=1.025, 1.065$ and $1.105\,\mrsun$.
 Black voxels correspond to non-reconstructed regions.
@@
 \textcolor{red}{
+*explicar voxel negros
 *Comentarios descriptivos sobre las rotaciones:
@@
 \caption{Carrington maps of DEMT results: $N_e$ (left panels) and $T_\textrm{m}$ (right panels) for CR-2082.
-Top, middle and bottom panels show the results at three heliocentric heights, $1.025$ ,$1.065$ and $1.105\,\mrsun$, respectively.
-Black voxels correspond to non-reconstructed regions and thick-black curves indicate the open/closed boundaries.}
+Top, middle and bottom panels show the results at three heliocentric heights, $1.025$, $1.065$ and $1.105\,\mrsun$ respectively.
+Black voxels correspond to non-reconstructed regions (see text in Section \ref{demt_res}) and thick-black curves indicate the open/closed boundaries.}
 \label{carmaps_demt_2082}
@@
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
-\caption{Latitude-longitude location of each leg of type 0 (in cyan), type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082 (left panel) and CR-2208 (right panel).}
+\caption{Latitude-longitude location of each leg of type 0 (in cyan), type I (in blue), type II (in red) and type III (in green) at $1.105\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).
+See Section \ref{trace} for a definition of the different types of legs.}
 \label{rpoint_demt}
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
-\caption{Histogram of the temperature radial gradient along each leg of type 0 (in cyan), type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082 (left panel) and CR-2208 (right panel).}
+\caption{Frequency histograms of the temperature radial gradient for the different types of legs shown in Figure \ref{rpoint_demt} (same colour code) for CR-2082 (left panel) and CR-2208 (right panel).}
 \label{gradt_demt}
@@
 \includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
-\caption{Comparative statistical distributions of (from left to right): the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type 0 - down loops and type I - up loops), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels).
-for CR-2082.
-DEMT results of CR2082 are shown in blue while those of CR2208 in red.
+\caption{Comparative statistical distributions of DEMT reults.
+From left to right: the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all types of legs defined in Section \ref{trace}.
+Results of CR2082 are shown in blue while those of CR-2208 in red.
 In each panel the median $m$ is indicated.}
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
-\caption{Statistical results of the loop integrated energy flux quantities $\phi_r,\phi_c, and \phi_h$ for CR2082 (top) and CR2208 (bottom).
+\caption{Statistical results of the loop integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ for CR-2082 (top) and CR-2208 (bottom).
 Left/right panels correspond to the type 0-1 and type 2 respectively \textcolor{red}{el tipo 2 tmb tiene down!
 Aca hay que tomar una desicion para no marear al lector!
-Pero lo dejo asi internamente para compararlo con figura 5 y 6 del aper de Mac Cormack}}
+Pero lo dejo asi internamente para compararlo con figura 5 y 6 del paper de Mac Cormack.
+Fede sugiere 6 graf, uno para cada tipo de linea (0, 1, 2).}}
 \label{gradt_demt}
@@
 \includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1105_Rsun.pdf}
-\caption{Same as Figure \ref{carmaps_awsom_2082} but for AWSoM results.}
+\caption{Carrington maps of density (left panels) and temperature (right panels)) obtained with AWSoM model for the three heights shown in Figure \ref{carmaps_awsom_2082}.}
 \label{carmaps_awsom_2082}
@@
 \includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1105_Rsun.pdf}
-\caption{Same as Figure \ref{carmaps_awsom_2208} but for AWSoM results.}
+\caption{Same as Figure \ref{carmaps_awsom_2208} for CR-2208.}
 \label{carmaps_awsom_2208}
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.eps}
-\caption{Same as Figure \ref{rpoint_demt} but for AWSoM loops.}
+\caption{Same as Figure \ref{rpoint_demt}, using the density and temperature of AWSoM model to classify legs in type 1, 2 and 3.}
 \label{rpoint_awsom}
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105.eps}
-\caption{Longitude-averaged, in both rotations, of electron density (top) and electron temperature (bottom) for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$.
-On the left CR2082 and on the right CR2208, the vertical black lines indicates the longitude-averaged latitudes of the open/close magnetic boundaries.}
+\caption{Longitude-averaged electron density (top) and temperature (bottom) for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$.
+The left (right) panels correspond to CR-2082 (CR2208).
+The vertical black line indicates the longitude-averaged latitudes of the open/close magnetic boundary.}
 \label{perf_lon_ne}
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_short.eps}
-\caption{Average fits of $N_e(r)$ and $T_e(r)$ along all field lines of type I (in blue), of type II (in red) and of type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (top panel) and CR-2208 (bottom panel).
-In solid lines DEMT traced results and in dashed lines AWSoM results.}
+\caption{Average fits of $N_e(r)$ and $T_e(r)$ for all legs of type I (blue), type II (red) and type III (green) for CR-2082 (top panel) and CR-2208 (bottom panel) using DEMT (solid) and AWSoM (dashed) results.}
 \label{perfiles_promedio}
@@
 \includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
-\caption{Comparative statistical distributions of (from left to right): the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type I, top panels), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels) for CR-2082.
-In blue the data of DEMT are shown while those of AWSoM in red.
-In each panel the median $m$ is indicated.}
+\caption{Comparative statistical distributions for CR-2082 between DEMT (blue) and AWSoM (red).
+From left to right: the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average $\aTm$ along the four types of legs considered in Section \ref{trace}.
+In each panel the median ($m$) is indicated.}
 \label{histos_2082}
@@
 \includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_Tm.eps}
-\caption{Same as Figure \ref{histos_2082} but for CR2208.}
+\caption{Same as Figure \ref{histos_2082} for CR-2208.}
 \label{histos_2208}

### 2019-12-04 lloveras_2020.tex
algo de texto

@@
 
+*Paso 1: obtencion de FBE
+*Paso 2: obtencion LDEM
+\begin{equation}\label{fbeldem}
+\FBE_i^{(k)}  = \int\,\textrm{d}T\,\LDEM_i(T)\,{\TRF}^{(k)}(T), \ \ \ {k=1,...,K}
+\end{equation}
+
 Once the LDEM is determined at each voxel, the average squared electron density $\langle N_e^2 \rangle$ and the electron mean temperature $T_\textrm{m}$ in the voxel can be computed by taking its zeroth and first moments over temperature.
@@
 
+*Una medida del grado de acuerdo de la reconstruccion
+\begin{equation}\label{R}
+R_i \, \equiv \ (1/K) \, \sum_{k=1}^K \left| \, 1 - \FBE^{(k)}_{i,\rm syn} / \,\FBE^{(k)}_{i,\rm tom}\, \right| \,,
+\end{equation}
+
 so that the final product of DEMT is in the form of 3D maps of the electron density and mean temperature. These relationships was derived in detail in \citealt{frazin_2009} (see Appendix C).
@@
 \textcolor{red}{*Mejoras de la tecnica con respecto a trabajos previos}
+
+\textcolor{red}{DEMT has been improved since the previously published work.
+We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.}
 
@@
 In the case of closed loops, results were separated into their two legs, defined as the two segments that go from the coronal base up to the apex.
-
-\textcolor{red}{Se eligen loops con abs(person temp) mayor a .5 lo cual nos permite descartar loops QI.
-OBS: Esto es valido para hasta la fig 7 inclusive.}
 
@@
 
-DEMT has been improved since the previously published work.
-We now perform hollow-tomography with the EUV images, \textcolor{red}{definir hollow-tom} and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.
+\textcolor{red}{*Nos quedamos con los fiteos que cumplen test de hipotesis chi cuadrado en temp y densidad.
+OBS: SE usan los errores en temp y densidad. Citar numerical recipes seccion 15.2}
 
-\textcolor{red}{*Nos quedamos con los fiteos que cumplen test de hipotesis chi cuadrado en temp y densidad.
-OBS: Esta es la seleccion para las figuras 8 en adelante. Citar numerical recipes seccion 15.2}
+\textcolor{red}{Se eligen loops con abs(person temp) mayor a .5 lo cual nos permite descartar loops QI. gradT suficientemente grandes.}
 
 For the two targeted rotations, DEMT and AWSoM resuls were traced along the AWSoM field lines, which provides a way to characterize the global thermodynamic state of the inner solar corona and to compare them.
-To that end three different types of magnetic lines corresponding with three different types of magnetic structures where selected:
+To that end four different types of legs corresponding with four different types of magnetic structures where selected:
 
-  0 - Small-closed field lines footlat $<30$ y gradt neg. where most of the DOWN loops showed up before
+  0 - Small (meaning with apex within the DEMT range of heights) closed field lines in the latitudes range $[-30\mdeg,+30\mdeg]$ and $\nabla_r T_m < 0$.
+This class thoroughly populates the equator of the Streamer belt during a minimum solar rotation.
 
-  I - Small-closed field lines. Small meaning with apex within the DEMT range of heights. gradt pos
-   %This class thoroughly probes the inner core of the Streamer belt, where most of the DOWN loops showed up before, and will show up now.
+  I - Small closed field lines in all latitudes, with $\nabla_r T_m > 0$. This class thoroughly populates the inner of the Streamer belt.
 
-  II - Large-closed field lines.
-Large meaning their apex surpasses the DEMT range of heights.
-This class is mostly populated by very large trans-equatorial field lines forming the "envelope" of the Streamer belt.
-footlat $>30$ y gradt pos
+  II - Large (meaning their apex surpasses the DEMT range of heights) closed field lines in the latitudes range $[-90\mdeg,-30\mdeg] \cup [+30\mdeg,+90\mdeg]$ and $\nabla_r T_m > 0$.
+This class is mostly populated by very large trans-equatorial field lines forming the envelope of the Streamer belt.
 
- III - Open field lines. footlat $>60$ y gradt pos
+ III - Open (meaning with apex out the DEMT range of heights) field lines in the latitudes range $[-90\mdeg,-60\mdeg] \cup [+60\mdeg,+90\mdeg]$ and $\nabla_r T_m > 0$.
 
-\textcolor{red}{que quede claro que de ahora en mas solo consideramos ajustes de loops up, es decir pearson temp > 0.5 debido a que awsom solo tiene up.}
+\textcolor{red}{Hice las definiciones con gradiente de temperatura para que quede mas claro, pero en realidad uso el pearson.} 
+%\textcolor{red}{que quede claro que de ahora en mas solo consideramos ajustes de loops up, es decir pearson temp > 0.5 debido a que awsom solo tiene up.}
 
@@
 }
+
+While CR-2082 was highly axisymmetric and showed virtually no ARs\textcolor{red}{(ver si en lat 50 y long 70 hay una.)}, CR-2208 showed an AR around latitude $+10\mdeg$ and longitude $300\mdeg$ \textcolor{red}{(ver la region open en lat 0 y long 200)}.
+Except for this AR, in both rotations the open-closed boundaries derived from the respective AWSoM model match the shape of the contour levels of the tomographic maps of both the electron density and the electron mean temperature.
+In these regions, there is a lack of match between the open-closed boundaries and the tomographic reconstructions of density and temperature.
+This range of longitudes was excluded from the analysis.
+Closed regions are characterized by relatively larger values of density and temperature in comparison to the open regions.
 
@@
 \end{figure}
+
+\textcolor{blue}{seccion 3.5 del otro paper}
 

### 2019-12-06 lloveras_2020.tex
mas texto

@@
 
-While CR-2082 was highly axisymmetric and showed virtually no ARs\textcolor{red}{(ver si en lat 50 y long 70 hay una.)}, CR-2208 showed an AR around latitude $+10\mdeg$ and longitude $300\mdeg$ \textcolor{red}{(ver la region open en lat 0 y long 200)}.
-Except for this AR, in both rotations the open-closed boundaries derived from the respective AWSoM model match the shape of the contour levels of the tomographic maps of both the electron density and the electron mean temperature.
-In these regions, there is a lack of match between the open-closed boundaries and the tomographic reconstructions of density and temperature.
-This range of longitudes was excluded from the analysis.
+While CR-2082 was highly axisymmetric and showed virtually no ARs (active region) \textcolor{red}{(ver si en lat 50 y long 70 hay una.)}, CR-2208 showed an AR around latitude $+10\mdeg$ and longitude $300\mdeg$ \textcolor{red}{(ver la region open en lat 0 y long 200)}.
+Except for these ARs, in both rotations the open-closed boundaries derived from the respective AWSoM model match the shape of the contour levels of the tomographic maps of both the electron density and the electron mean temperature.
+In the AR, there is a lack of match between the open-closed boundaries and the tomographic reconstructions of density and temperature, that is why those ranges were excluded from the analysis.
 Closed regions are characterized by relatively larger values of density and temperature in comparison to the open regions.
+
+\textcolor{red}{A visual inspection of Figures \ref{momento1} and \ref{momento2} suggest/indicates:
+PARRAFO CORTO DE OBSERVACIONES QUE LUEGO SERAN CORROBORADAS CON HISTOGRAMAS.
+*that the streamer region of CR-2082 was denser and colder than CR-2208. 
+*a diminishing of the temperatures conform the height increase in the the most equatorial latitudes in both rotations, asociated with the type 0 lines.
+*}
+
+\textcolor{red}{Esto me suena a un indicador de mas actividad en 2208, pero deberia justificarlo.
+Y podria ser una buena idea asi queda un parrafito que compare los mapas de carrington de ambas rotaciones.}
 
@@
 
-\textcolor{red}{
-*Para las piernas trazadas que cumplen  |pearson de temp| > 0.5 se calcularon los gradientes de temp que cumplen test de hipotesis.
-Estos gradientes se muestran en la Figura \ref{gradientes} para las 3 regiones definidas para ambas rotaciones.
-Esto muestra up y down loops.
-OBS: esto da pie a hablar y proponer mejoras en la conversion de modos de alfven. citar paper fede.
-%*Como el modelo awsom no presenta down loops, se selecciona de ahora en mas los loops con pearson de temp > 0.5
-}
-%\begin{figure}[h!]
-%\begin{center}
-%\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_updowntriple_gradt.eps}
-%\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_updowntriple_gradt.eps}
-%\caption{Frequency histogram of the temperature radial gradient of along each leg of type I (in blue), type II %(in red) and type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (left panel) and CR-2208 (right panel).
-In solid lines DEMT traced data and in dashed lines AWSoM data.}
-%\label{gradientes}
-%\end{center}
-%\end{figure}
+For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected.
+For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{momento1} and \ref{momento2}.
+\textcolor{red}{aca los highpoints, comentar los colores y enunciar que cada uno puebla una regino termodinamica diferente}
 
-\textcolor{red}{
-For the two analyzed rotations, Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of all field lines that meet the criteria listed in Section \ref{trace} at $1.105\,\mrsun$.
-}
+ As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $\nabla_r T_m$, and the height-averaged (along the loop) electron mean temperature $\aTm$.
+As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height was used to compute the coronal base electron density here defined as $\NCB\equiv N_e(r=1.025\,\mrsun)$.
+
+\textcolor{red}{the temperature gradient $\nabla_r T_m$ fue computada}\\
+Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of the selected lines.
+In cyan the type 0 lines are indicated, populating the most equatorial latitudes.
+In blue the type 1, populating mostly the mid latitudes  of the streamer.
+In red the type 2, populating the edge that assemble the envelope arround the streamer, and in green dots the type 3 lines, populating the coronal holes.
 
@@
 
+Figure \ref{gradt_demt} is a frequency histogram normalized to the total amount of legs concidered of $\nabla_r T_m$ for every type of legs for both rotations.
+\textcolor{red}{Aun no se que decir sobre esto, sobre los downs se puede citar nuevo et al 2013 y decir algo sobre hay menos cantidad en cr2208 haciendo enfoque en que podria ser un indicador de que aun no esta en un minimo}
+
 \begin{figure}[h!]
@@
 \end{figure}
+
+As an example of the traced magnitudes, Figure \ref{histos_fulldemt} shows the statistical results of both rotations for all field lines traced.
+From top to bottom type 0 to type 4.
+From left to right the panels show the statistical distribution of $\NCB$, $\lN$, $\aTm$, in each panel the median $m$ is indicated.
+
+\textcolor{red}{Podria ir una tabla resumiendo las comparaciones y luego un parrafo que indique brevemente que la densidad a 1.055 de CR2208 fué en general mas grande, que la escala de altura es casi la misma y que ademas cr2208 fue mas caliente.}
 

### 2019-12-06 lloveras_2020.tex
nuevos graficos energeticos

@@
 % \author[addressref={},corref,email={}]{\inits{}\fnm{}\lnm{}\orcid{}}
-\author[addressref={aff1,aff2},corref,email={dlloveras@iafe.uba.ar}]{\inits{D.G.}\fnm{Diego G.}~\lnm{Lloveras}\orcid{0000-0003-1402-0398}}
+\author[addressref={aff1},corref,email={dlloveras@iafe.uba.ar}]{\inits{D.G.}\fnm{Diego G.}~\lnm{Lloveras}\orcid{0000-0003-1402-0398}}
 
-\author[addressref={aff1,aff3,aff2},corref,email={albert@iafe.uba.ar}]{\inits{A.M.}\fnm{Alberto M.}~\lnm{V\'asquez}\orcid{0000-0003-3401-6409}}
+\author[addressref={aff1,aff3},corref,email={albert@iafe.uba.ar}]{\inits{A.M.}\fnm{Alberto M.}~\lnm{V\'asquez}\orcid{0000-0003-3401-6409}}
 
-\author[addressref={aff1,aff2},corref,email={federico@iafe.uba.ar}]{\inits{F.A.}\fnm{Federico A.}~\lnm{Nuevo}\orcid{0000-0003-2355-5853}}
+\author[addressref={aff1},corref,email={federico@iafe.uba.ar}]{\inits{F.A.}\fnm{Federico A.}~\lnm{Nuevo}\orcid{0000-0003-2355-5853}}
 
-\author[addressref={aff1,aff3,aff2},corref,email={cmaccormack@iafe.uba.ar}]{\inits{C.}\fnm{Cecilia}~\lnm{Mac Cormack}}
+\author[addressref={aff1,aff3},corref,email={cmaccormack@iafe.uba.ar}]{\inits{C.}\fnm{Cecilia}~\lnm{Mac Cormack}}
 
@@
 
-\address[id=aff2]{Departamento de F\'{\i}sica, Facultad de Ciencias Exactas y Naturales (FCEN), Universidad de Buenos Aires (UBA), Pabell\'on I, Ciudad Universitaria, (C1428ZAA) Ciudad Aut\'onoma de Buenos Aires, Argentina}
+%\address[id=aff2]{Departamento de F\'{\i}sica, Facultad de Ciencias Exactas y Naturales (FCEN), Universidad de Buenos Aires (UBA), Pabell\'on I, Ciudad Universitaria, (C1428ZAA) Ciudad Aut\'onoma de Buenos Aires, Argentina}
 
@@
 
+\textcolor{red}{Aca vienen quizas 1 o 2 parrafos introduciendo y explicando los phi, los resultados de la Figura \ref{energia_demt} y un parrafo comentando esos resultados.}
+
 \begin{figure}[h!]
 \begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccdownenergia.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccdownenergia.eps}
 \includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccenergia.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccenergia.eps}
 \includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_cgenergia.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccenergia.eps}
 \includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
-\caption{Statistical results of the loop integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ for CR-2082 (top) and CR-2208 (bottom).
-Left/right panels correspond to the type 0-1 and type 2 respectively \textcolor{red}{el tipo 2 tmb tiene down!
-Aca hay que tomar una desicion para no marear al lector!
-Pero lo dejo asi internamente para compararlo con figura 5 y 6 del paper de Mac Cormack.
-Fede sugiere 6 graf, uno para cada tipo de linea (0, 1, 2).}}
-\label{gradt_demt}
+\caption{Statistical results of the loop integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colours blu, red and green, respectively for CR-2082 (left) and CR-2208 (right).
+From top to left the type 0, 1 and 2 field of lines defined in Section \ref{trace}.
+}
+\label{energia_demt}
 \end{center}

### 2019-12-07 lloveras_2020.tex
sigue la milonga

@@
 
-*Paso 1: obtencion de FBE
+*Paso 1: obtencion de FBE\\
 *Paso 2: obtencion LDEM
@@
 \end{equation}
+
+\textcolor{red}{
+Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}.
+{These non-reconstructed voxels are indicated in black in the Carrington maps of reconstructed FBE}.
+}
 

### 2019-12-09 lloveras_2020.tex
tesxto en la seccion 3.1 y 3.2

@@
 \newcommand{\etal}{{\it et al.}}
+
+\def\Pl{\texttt{+}}
+\def\Mi{\texttt{-}}
+
+% Definitions for the journal names
+\newcommand{\adv}{    {\it Adv. Space Res.}} 
+\newcommand{\annG}{   {\it Ann. Geophys.}} 
+\newcommand{\aap}{    {\it Astron. Astrophys.}}
+\newcommand{\aaps}{   {\it Astron. Astrophys. Suppl.}}
+\newcommand{\aapr}{   {\it Astron. Astrophys. Rev.}}
+\newcommand{\ag}{     {\it Ann. Geophys.}}
+\newcommand{\aj}{     {\it Astron. J.}} 
+\newcommand{\apj}{    {\it Astrophys. J.}}
+\newcommand{\apjs}{   {\it Astrophys. J. Suppl.}}
+\newcommand{\apjl}{   {\it Astrophys. J. Lett.}}
+\newcommand{\apss}{   {\it Astrophys. Space Sci.}} 
+\newcommand{\cjaa}{   {\it Chin. J. Astron. Astrophys.}} 
+\newcommand{\gafd}{   {\it Geophys. Astrophys. Fluid Dyn.}}
+\newcommand{\grl}{    {\it Geophys. Res. Lett.}}
+\newcommand{\ijga}{   {\it Int. J. Geomagn. Aeron.}}
+\newcommand{\jastp}{  {\it J. Atmos. Solar-Terr. Phys.}} 
+\newcommand{\jgr}{    {\it J. Geophys. Res.}}
+\newcommand{\mnras}{  {\it Mon. Not. Roy. Astron. Soc.}}
+\newcommand{\nat}{    {\it Nature}}
+\newcommand{\pasp}{   {\it Pub. Astron. Soc. Pac.}}
+\newcommand{\pasj}{   {\it Pub. Astron. Soc. Japan}}
+\newcommand{\pre}{    {\it Phys. Rev. E}}
+\newcommand{\solphys}{{\it Solar Phys.}}
+\newcommand{\sovast}{ {\it Soviet  Astron.}} 
+\newcommand{\ssr}{    {\it Space Sci. Rev.}}
 
@@
 Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}.
-{These non-reconstructed voxels are indicated in black in the Carrington maps of reconstructed FBE}.
+These non-reconstructed voxels are indicated as black voxels in the Carrington maps of the reconstructed DEMT reults in Section \ref{resu}.
 }
@@
 Once the LDEM was determined for each rotation, the electron density $N_e$ and electron mean temperature $T_\textrm{m}$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}.
-As an example, Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show the results for both rotations at $r=1.025, 1.065$ and $1.105\,\mrsun$.
-Black voxels correspond to non-reconstructed regions.
-
-\textcolor{red}{
-*explicar voxel negros
-*Comentarios descriptivos sobre las rotaciones:
--Simetria
--CH
--Matcheo entre open-closed boundaries y las estructuras termodinamicas.
-}
+As an example, Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} shows the latitude-longitude maps for both tomographic results for CR-2082 and CR-2208 at $r=1.025, 1.065$ and $1.105\,\mrsun$.
+Black voxels correspond to non-reconstructed regions (explained in Section \ref{demt}).
 
@@
 
-\textcolor{red}{A visual inspection of Figures \ref{momento1} and \ref{momento2} suggest/indicates:
-PARRAFO CORTO DE OBSERVACIONES QUE LUEGO SERAN CORROBORADAS CON HISTOGRAMAS.
-*that the streamer region of CR-2082 was denser and colder than CR-2208. 
-*a diminishing of the temperatures conform the height increase in the the most equatorial latitudes in both rotations, asociated with the type 0 lines.
-*}
-
-\textcolor{red}{Esto me suena a un indicador de mas actividad en 2208, pero deberia justificarlo.
-Y podria ser una buena idea asi queda un parrafito que compare los mapas de carrington de ambas rotaciones.}
+\textcolor{red}{PARRAFO CORTO DE OBSERVACIONES QUE LUEGO SERAN CORROBORADAS CON HISTOGRAMAS.}
+A visual inspection of Figures \ref{momento1} and \ref{momento2} suggest/indicates that the streamer region of CR-2082 was denser and colder than CR-2208.
+In both rotations, but specifically in CR-2082 the temperature in the equatorial latitudes tend to decrease with height while the latitudes between the open-close boundaries and the equatorial latitudes tend to increase.
+These thermodynamic structures have been reported for other rotations in previous works \citep{lloveras_2017}.
 
@@
 
-\textcolor{blue}{seccion 3.5 del otro paper}
-
 For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected.
-For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{momento1} and \ref{momento2}.
+For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.
 \textcolor{red}{aca los highpoints, comentar los colores y enunciar que cada uno puebla una regino termodinamica diferente}
@@
  As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $\nabla_r T_m$, and the height-averaged (along the loop) electron mean temperature $\aTm$.
-As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height was used to compute the coronal base electron density here defined as $\NCB\equiv N_e(r=1.025\,\mrsun)$.
+As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height may be used to compute the tomographic basal electron density at $ N_e(r=1.025\,\mrsun)$ as in previous articles.
+In this case, for an further comparison analysis with the AWSoM results, we selected the lowest height where the results of the MHD model are reliable, that is $1,065\,\mrsun)$.
 
-\textcolor{red}{the temperature gradient $\nabla_r T_m$ fue computada}\\
-Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of the selected lines.
-In cyan the type 0 lines are indicated, populating the most equatorial latitudes.
-In blue the type 1, populating mostly the mid latitudes  of the streamer.
-In red the type 2, populating the edge that assemble the envelope arround the streamer, and in green dots the type 3 lines, populating the coronal holes.
+\textcolor{red}{Aca una linea que linkee la definicion del tipo de lineas en la seccion anterior con las regiones que se ven en la figura que se describe a continuacion}
+Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations.
+In cyan the type 0 lines are indicated, populating the most equatorial latitudes (dominated mostly by down loops).
+In blue the type 1 lines, populating mostly the mid latitudes of the streamer.
+In red the type 2 lines, populating the edge that assemble the envelope around the streamer, and in green dots the type 3 lines, populating the coronal holes.
+
+This selection of the types of lines automatically leads to thermodynamic regions arranged along all longitudes with good symmetry in both rotations, this is because the rotations are at a minimum of activity and the static corona is a good approximation.
 
@@
 
-Figure \ref{gradt_demt} is a frequency histogram normalized to the total amount of legs concidered of $\nabla_r T_m$ for every type of legs for both rotations.
-\textcolor{red}{Aun no se que decir sobre esto, sobre los downs se puede citar nuevo et al 2013 y decir algo sobre hay menos cantidad en cr2208 haciendo enfoque en que podria ser un indicador de que aun no esta en un minimo}
+Figure \ref{gradt_demt} shows histograms (normalized to the total amount of field lines) of the temperature radial gradients ($\nabla_r T_m$) for every type of line and for both rotations.
+The lack of population around values close to zero is due to the strict condition $|\rho_t| > 0.5$ that discards possible isothermal values.
+
+\textcolor{red}{Aun no se que decir sobre esto, sobre los downs se puede citar nuevo et al 2013 y decir algo sobre hay menos cantidad en cr2208 haciendo enfoque en que podria ser un indicador de que aun no esta en un minimo.
+Por otro lado mostrar los gradientes negativos va a ser util en los parrafos posteriores que expliquen porque en las lineas tipo 0 hay valores de $\phi_c$ negativos.}
+\textcolor{blue}{Quizas sea un buen lugar para comentar el paper up down de Fede, y el de shift y cramer, para decir un poco sobre los down, xq en la prox seccion voy a decir que no hay lineas tipo 0 justamente xq el modelo es incapaz de reproducir los down}
 
@@
 
-As an example of the traced magnitudes, Figure \ref{histos_fulldemt} shows the statistical results of both rotations for all field lines traced.
+As an example of the traced magnitudes, Figure \ref{histos_fulldemt} shows the statistical results of both rotations for all field lines types.
 From top to bottom type 0 to type 4.
 From left to right the panels show the statistical distribution of $\NCB$, $\lN$, $\aTm$, in each panel the median $m$ is indicated.
-
-\textcolor{red}{Podria ir una tabla resumiendo las comparaciones y luego un parrafo que indique brevemente que la densidad a 1.055 de CR2208 fué en general mas grande, que la escala de altura es casi la misma y que ademas cr2208 fue mas caliente.}
 
@@
 
-\textcolor{red}{Aca vienen quizas 1 o 2 parrafos introduciendo y explicando los phi, los resultados de la Figura \ref{energia_demt} y un parrafo comentando esos resultados.}
+\begin{table}
+\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
+% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
+\hline
+Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
+       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
+\hline
+0  & 0&93 &(\Mi&12&9\%)  &   7&4 &(\Pl&~3&9\%) &   1&11 &(\Pl&20&7\%) \\
+1  & 0&84 &(\Mi&11&3\%)  &   8&3 &(\Pl&15&3\%) &   1&30 &(\Pl&16&1\%) \\
+2  & 0&69 &(\Mi&10&1\%)  &   8&9 &(\Pl&19&1\%) &   1&33 &(\Pl&14&2\%) \\
+3  & 0&48 &(\Mi&12&5\%)  &   7&7 &(\Pl&10&5\%) &   0&98 &(\Pl&~5&7\%) \\
+\hline          
+\end{tabular}
+\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
+For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
+\label{tabla_demt}
+\end{table}
+
+Table \ref{tabla_demt} summarize the quantitative comparative analysis between the results of the two target rotations sampling both minima.
+The following major results concerning the structure of each rotation individually and their comparison can be drawn.
+
+In the equatorial streamer of both rotations, increasing latitudes show decreasing \textcolor{red}{coronal base (1.055)} density, and increasing density scale height and electron temperature.
+In both rotations the CH regions are characterized sub-MK temperatures, and coronal base densities of order $\approx 1/2$ of the equatorial streamer.
+Histograms with sharp populations indicates that for both rotations the values of all physical quantities exhibit a strong symmetry between both hemispheres.
+
+A comparison of the results between the two rotations within the closed field lines \textcolor{red}{equatorial streamer belt} shows that CR-2208 is characterized by lower values of electron density and larger of temperature compared to CR-2082, as well as larger values of the density scale height.
+\textcolor{red}{Comentario sobre la estimacion de errores del paper pasado?}
+
+In the coronal hole region, \textcolor{red}{No se si se puede aclarar algo en particular, quizas decir que ahora que tomamos una gran region abierta (en comparacion con el paper pasado) la seleccion toma lineas en la transicion de viento lento y rapido y eso genera que el histograma de Tm sea tan disperso}
+
+%To establish if the differences in the results between the two rotations are significant, Section \ref{uncertainties} estimates the error bars due the dominating systematic uncertainties.
+
+%{Also, within the streamer belt the magnetic field strength is similar in both rotations in the northern hemisphere, while in the southern hemisphere CR-1915 exhibits $10-80\%$ larger values compared to CR-2081, with increasing difference for larger latitudes.
+In the coronal holes, the magnetic field strength of CR-1915 is much larger than for CR-2081, exhibiting values up to 50\% larger in the northern hemisphere and more than twice larger in the southern hemisphere.}
+
+\textcolor{red}{Aca vienen quizas 1 o 2 parrafos introduciendo y explicando los phi, los resultados de la Figura \ref{energia_demt} y un parrafo comentando esos resultados.
+Este parrafo va escrito por Ceci.}
 
@@
 
-\textcolor{red}{Se presentan los resultados de Ne y Te del modelo AWSoM}
+\textcolor{red}{Parrafo introductorio}
+
+As an example of the AWSoM results, Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} shows the latitude-longitude maps for $N_e$ and $T_e$ modeled for CR-2082 and CR-2208 at $r=1.025, 1.065$ and $1.105\,\mrsun$.
+The black curve denotes the open-close boundary.
+
+\textcolor{red}{No pondría los mapas de 1.025 y diria algo asi como:\\}
+In the transition region, the plasma heats up and becomes less dense in several orders of magnitude in a short distance.
+Modeling this region correctly requires a high computational cost.
+For this reason the model uses a extended transition region and not real initial conditions of contour in density and electronic temperature.
+Consequently, the results below $1.065\,\mrsun$ were not taken into account in this article.
+
+A visual inspection of the AWSoM results shows that both reconstruction are very axysimmetric for $N_e$ and $T_e$ as well.
+The closed region is denser and hotter than the open region.
+The density and temperature gradients are maximum in the open-close boundary.
+The open field regions in low latitudes maintain thermodynamic values associated with open regions.
+CR-2208 shows a well reconstruction of the AR around latitude $+10\mdeg$ and longitude $300\mdeg$ and a slight temperature difference between the poles \textcolor{red}{estoy asumiento que es una AR}.
+In both rotations the open-closed boundaries derived from the respective AWSoM model match the shape of the contour levels of the tomographic maps of both the electron density and the electron mean temperature.
 
@@
 \includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1105_Rsun.pdf}
-\caption{Carrington maps of density (left panels) and temperature (right panels)) obtained with AWSoM model for the three heights shown in Figure \ref{carmaps_awsom_2082}.}
+\caption{Carrington maps of density (left panels) and temperature (right panels) obtained with AWSoM model for the same three heights shown in Figure \ref{carmaps_demt_2082}.}
 \label{carmaps_awsom_2082}
@@
 
+In the same way as in Section \ref{demt_res}, the model results were traced along the magnetic lines obtained with it.
+This allowed to obtain $N_e(r)$ and $T_e(r)$ along the magnetic lines and fit them to the Equations \ref{Nfit} and \ref{Tfit}.
+
+Due to the inability of the model to reproduce down legs, in this section we only use lines type 1, 2 and 3 and only select those that meet the chi square hypothesis test.
+
+Figure \ref{rpoint_awsom} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations.
+In blue the type 1 lines, populating mostly the entire streamer.
+In red the type 2 lines, populating the edge that assemble the envelope around the streamer, and in green dots the type 3 lines, populating the coronal holes.
+
+The fact that Figure \ref{rpoint_awsom} looks much fuller than Figure \ref{rpoint_demt} is because giving the model smoother results, fewer fitted lines are filtered.
+
+The reader may notice that these structures are the same as those in Figure \ref{rpoint_demt} but more filled, this is because the same magnetic result was used to trace both DEMT and AWSoM results.
+
 \begin{figure}[h!]
@@
 
+To highlight the latitudinal structures, Figure \ref{perf_lat} shows for both rotations the latitudinal variation  of both the electron density and the electron mean temperature at the height $r=1.105\,\mrsun$, averaged over all longitudes (excluding the AR).
+DEMT results are shown in blue lines while AWSoM results in red.
+While the temperature shows a maximum in each hemisphere, the density has a simpler behavior, with higher values in the low-latitudes of the streamer and a nearly monotonic decrease towards larger latitudes.
+The vertical black lines denotes the average of the open-close boundary in both hemispheres to each rotation.
+
+\textcolor{red}{
+*awsom da valores mas altos en los polos\\
+*Parece haber una buena coincidencia en CR2082 en Te yen CR2208 en Ne.
+*En CR2082 en Ne demt es 20 \% mas grande que awsom en la zona cerrada.
+*En cr2208 en Te, en la zona polar awsom es 30\% mas grande y awsom es 25\% mas grande en la region cerrada.
+}
+
 \begin{figure}[h!]
@@
 The vertical black line indicates the longitude-averaged latitudes of the open/close magnetic boundary.}
-\label{perf_lon_ne}
+\label{perf_lat}
 \end{center}
 \end{figure}
+
+To summarize the comparison between both results during both rotations at full height, it is shown in Figure \ref{perfiles_promedio} the average fits of $N_e(r)$ and $T_e(r)$ for every type of legs.
+
+\textcolor{red}{Explicar lo que se observa}
 
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_short.eps}
-\caption{Average fits of $N_e(r)$ and $T_e(r)$ for all legs of type I (blue), type II (red) and type III (green) for CR-2082 (top panel) and CR-2208 (bottom panel) using DEMT (solid) and AWSoM (dashed) results.}
+\caption{Average fits of $N_e(r)$ and $T_e(r)$ for legs of type I (blue), type II (red) and type III (green) for CR-2082 (top panel) and CR-2208 (bottom panel) using DEMT (solid) and AWSoM (dashed) results.}
 \label{perfiles_promedio}
@@
 This will be nice to do also for the July-2-2019 Eclipse rotation that we will analyze after this paper.
-
-Visual inspection of the results for CR-2082 in Figure \ref{carmaps_demt_2082} and \ref{carmaps_awsom_2082} reveals two clearly distinct thermodynamical states between the streamer (closed field lines) and the coronal holes (open lines).
-\\
 

### 2019-12-09 lloveras_2020.tex
cambios en lois graficos energeticos
detalles

@@
 
+\textcolor{red}{Se debe aclarar que solo produce resultados razonables arriba de 1.065}
+
 \subsection{Tracing results along fieldlines}\label{trace}
@@
 \textcolor{red}{*Nos quedamos con los fiteos que cumplen test de hipotesis chi cuadrado en temp y densidad.
-OBS: SE usan los errores en temp y densidad. Citar numerical recipes seccion 15.2}
+OBS: SE usan los errores en temp y densidad. Citar numerical recipes seccion 15.2 \citet{recipes}}
 
@@
 To that end four different types of legs corresponding with four different types of magnetic structures where selected:
-
+\textcolor{red}{Hacer explicacion de los tipos de lineas bien secos, luego en fig 3 hacer notar que implica cada una en cuanto a estructura magnetica}
   0 - Small (meaning with apex within the DEMT range of heights) closed field lines in the latitudes range $[-30\mdeg,+30\mdeg]$ and $\nabla_r T_m < 0$.
@@
 %\textcolor{red}{que quede claro que de ahora en mas solo consideramos ajustes de loops up, es decir pearson temp > 0.5 debido a que awsom solo tiene up.}
+
+\subsection{Energy flux ?}\label{energia} 
+\textcolor{red}{Aca se introduce la seccion de energia con sus ecuaciones etc}
 
@@
 Por otro lado mostrar los gradientes negativos va a ser util en los parrafos posteriores que expliquen porque en las lineas tipo 0 hay valores de $\phi_c$ negativos.}
-\textcolor{blue}{Quizas sea un buen lugar para comentar el paper up down de Fede, y el de shift y cramer, para decir un poco sobre los down, xq en la prox seccion voy a decir que no hay lineas tipo 0 justamente xq el modelo es incapaz de reproducir los down}
+\textcolor{blue}{Quizas sea un buen lugar para comentar el paper up down de Fede, diciendo que estas estructuras ya se han visto antes, etc., suena bien que les de algo de importancia xq en la prox seccion voy a decir que no hay lineas tipo 0 justamente xq el modelo es incapaz de reproducir los down}
+
+\textcolor{red}{ Comentar en la discusion el paper de shift y cramer, para decir un poco sobre los down y la incapacidad del modelo en reproducirlos}
 
@@
 \section{Discussion}\label{discu}
+
+*Down loops, shiff y cranmer comentarios.
+
 %% Figure 

### 2019-12-11 lloveras_2020.tex
graficos de histogramas arreglados y mas texto

@@
 \usepackage{setspace}
+
+\usepackage{xcolor}
 
@@
 \newcommand{\ssr}{    {\it Space Sci. Rev.}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% temporales
+\definecolor{mygray}{gray}{0.6}
+
+\def\diego#1{\textcolor{red}{DIEGO: #1}}
+\def\albert#1{\textcolor{blue}{ALBERT: #1}}
+\def\fede#1{\textcolor{green}{FEDE: #1}}
+
+\def\temp#1{\textcolor{mygray}{TEMPORAL: #1}}
 
@@
 \subsection{DEMT reconstructions}\label{demt} 
-\textcolor{red}{*Tratado de imagenes}
-\textcolor{red}{*FBE}
-\textcolor{red}{*LDEM}
+\temp{*Tratado de imagenes}
+\temp{*FBE}
+\temp{*LDEM}
 
@@
 
-\textcolor{red}{
+\temp{
 Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}.
@@
 
-\textcolor{red}{*aclarar que consideramos Ne como $\sqrt{<N_e ^2>}$.}
+\temp{*aclarar que consideramos Ne como $\sqrt{<N_e ^2>}$.}
 
-\textcolor{red}{*Mejoras de la tecnica con respecto a trabajos previos}
+\temp{red}{*Mejoras de la tecnica con respecto a trabajos previos}
 
-\textcolor{red}{DEMT has been improved since the previously published work.
+\temp{DEMT has been improved since the previously published work.
 We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.}
@@
 \subsection{AWSoM simulations}\label{awsom} 
-\textcolor{red}{*Que es, que modela, que datos usa, y que se obtiene en general y en particular para este trabajo}
+\temp{*Que es, que modela, que datos usa, y que se obtiene en general y en particular para este trabajo}
 
-\textcolor{red}{Se debe aclarar que solo produce resultados razonables arriba de 1.065}
+\temp{Se debe aclarar que solo produce resultados razonables arriba de 1.065}
+
+\temp{No pondría los mapas de 1.025 y diria algo asi como:\\}
+In the transition region, the plasma heats up and becomes less dense in several orders of magnitude in a short distance.
+Modeling this region correctly requires a high computational cost.
+For this reason the model uses a extended transition region and not real initial conditions of contour in density and electronic temperature.
+Consequently, the results below $1.065\,\mrsun$ were not taken into account in this article.
 
@@
 
-For both rotations, the DEMT and AWSoM 3D maps of electron density $N_e$, electron mean temperature $T_\textrm{m}$ and electron temperature $T_\textrm{e}$ respectively were traced along the magnetic field lines modeled using AWSoM as described at the end of Section \ref{awsom}.
+\diego{Abajo una copia del paper anterior, esta seccion debe ser reescrita.}
+
+For both rotations, the DEMT and AWSoM 3D maps of electron density $N_e$, electron mean temperature $T_\textrm{m}$ and electron temperature $T_\textrm{e}$ respectively were traced along the magnetic field lines modeled using AWSoM as described at the end of Section \ref{demt}.
 In the case of closed loops, results were separated into their two legs, defined as the two segments that go from the coronal base up to the apex.
@@
 \label{Tfit}
-T_\textrm{m} &=& a\,r\,+\,b
+T_\textrm{m} &=&  \nabla_r T_m \,r\,+\,T_\textrm{0}
 \end{eqnarray}
@@
 In the case of the electron density, the fitted function corresponds to the isothermal hydrostatic equilibrium solution, allowing for variation of the solar gravitational acceleration with height.
-After computing the footpoint ($r=1.0\,\mrsun$) electron density $N_{0}\,[\cm^{-3}]$ and scale height $\lN\,[\mrsun]$\textcolor{blue}{, this choice of function provides a straightforward means to directly evaluate how compatible is the observed coronal thermodynamical state with the hydrostatic solution}.
-The linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $a = \textrm{d}T_m/\textrm{d}r\,[\MK/\mrsun]$ along each leg.
+After computing the footpoint ($r=1.0\,\mrsun$) electron density $N_{0}\,[\cm^{-3}]$ and scale height $\lN\,[\mrsun]$\temp{, this choice of function provides a straightforward means to directly evaluate how compatible is the observed coronal thermodynamical state with the hydrostatic solution}.
 
-\textcolor{red}{*Nos quedamos con los fiteos que cumplen test de hipotesis chi cuadrado en temp y densidad.
+\temp{
+La temperatura en funcion de la altura a lo largo de lineas muestra comportamientos lineales.
+En el presente trabajo nos focalizamos en lineas con temperaturas crecientes y decrecientes en foma lineal.
+Es decir nos quedamos con aquellas piernas donde el coeficiente de pearson entre la temperatura y la altura (rho) cumple rho mayor 0.5 (con p-value 0.05) y de esta forma se descartan aquellas piernas en las que los resultados DEMT no pueden asegurar un cambio notable de temperatura entre la base y el apice (asi no uso la palabra isotermico y evado ese problema)
+}
+
+The linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $\nabla_r T_m\,[\MK/\mrsun]$ along each leg.
+\diego{ambos fiteos utilizan los errores del paper anterior!!}
+
+\temp{
+*to measure how good the quality of the exponential fit to the electron density and the linear fit to the temperature data are, a chi-square merit function was used \temp{eq 15.2.2}.
+The errors were estimated in lloveras-2017 $tanto y tanto \%$ and the lesg with p-value $>0.005$ were rejected.
+*aplicamos un test de hipotesis chi cuadrado asumiendo como hipotesis nula que los valores ajustados a cada pierna corresponden al valor esperado de la funcion distribucion chi cuadrado Df,E.
+Donde DF es la cantidad de datos en cada linea-2 y E
+2) el p-valor es un concepto estadístico, no veo xq deberia ser explicado. Lo que si, en el paper explicare bien las hipotesis nulas y de esa forma el p-valor queda bien claro.
+El p-valor es una cuantificacion de con cuanta probabilidad de exito estas rechazando o aceptando una hipotesis en particular que se la suele denominar hipotesis nula.
+En este caso, con 95$\%$ de seguridad estas rechazando las piernas que tienen un $pearson_x,y = 0$. Es decir te estarias quedando con aquellas que tienen una dependencia lineal entre x e y.
+En el segundo caso, el test de hipotesis seria sobre la hip nula de que los datos provienen una funcion distribucion donde la recta fiteada de esos datos es el valor esperado de la distribucion.
+Con lo cual hacerle un test chi cuadrado te da una idea de cuan acertado o no es el ajuste.
+En este caso la hipotesis nula es que los datos provienen de esa distrib, con lo cual el chi deberia dar bajo y descartas los que dan valores altos con un 95$\%$ de seguridad.
+Eso es lo que representa el p-valor =0.05 en este caso (el area bajo la funcion distribucion, es decir, probabilidad).
+}
+
+\temp{*Nos quedamos con los fiteos que cumplen test de hipotesis chi cuadrado en temp y densidad.
 OBS: SE usan los errores en temp y densidad. Citar numerical recipes seccion 15.2 \citet{recipes}}
 
-\textcolor{red}{Se eligen loops con abs(person temp) mayor a .5 lo cual nos permite descartar loops QI. gradT suficientemente grandes.}
+\temp{Se eligen loops con abs(person temp) mayor a .5 lo cual nos permite descartar loops QI. gradT suficientemente grandes.}
 
@@
 To that end four different types of legs corresponding with four different types of magnetic structures where selected:
-\textcolor{red}{Hacer explicacion de los tipos de lineas bien secos, luego en fig 3 hacer notar que implica cada una en cuanto a estructura magnetica}
+\temp{Hacer explicacion de los tipos de lineas bien secos, luego en fig 3 hacer notar que implica cada una en cuanto a estructura magnetica}\\
   0 - Small (meaning with apex within the DEMT range of heights) closed field lines in the latitudes range $[-30\mdeg,+30\mdeg]$ and $\nabla_r T_m < 0$.
@@
 
-\textcolor{red}{Hice las definiciones con gradiente de temperatura para que quede mas claro, pero en realidad uso el pearson.} 
-%\textcolor{red}{que quede claro que de ahora en mas solo consideramos ajustes de loops up, es decir pearson temp > 0.5 debido a que awsom solo tiene up.}
+\temp{Hice las definiciones con gradiente de temperatura para que quede mas claro, pero en realidad uso el pearson.} 
+%\temp{que quede claro que de ahora en mas solo consideramos ajustes de loops up, es decir pearson temp > 0.5 debido a que awsom solo tiene up.}
 
 \subsection{Energy flux ?}\label{energia} 
-\textcolor{red}{Aca se introduce la seccion de energia con sus ecuaciones etc}
-
+\temp{Aca se introduce la seccion de energia con sus ecuaciones etc}
+\diego{sugerencias para el nombre?}
 \section{Results}\label{resu}
@@
 
-While CR-2082 was highly axisymmetric and showed virtually no ARs (active region) \textcolor{red}{(ver si en lat 50 y long 70 hay una.)}, CR-2208 showed an AR around latitude $+10\mdeg$ and longitude $300\mdeg$ \textcolor{red}{(ver la region open en lat 0 y long 200)}.
+While CR-2082 was highly axisymmetric and showed virtually no ARs (active region) \temp{(ver si en lat 50 y long 70 hay una.)}, CR-2208 showed an AR around latitude $+10\mdeg$ and longitude $300\mdeg$ \temp{(ver la region open en lat 0 y long 200)}.
 Except for these ARs, in both rotations the open-closed boundaries derived from the respective AWSoM model match the shape of the contour levels of the tomographic maps of both the electron density and the electron mean temperature.
@@
 
-\textcolor{red}{PARRAFO CORTO DE OBSERVACIONES QUE LUEGO SERAN CORROBORADAS CON HISTOGRAMAS.}
+\temp{PARRAFO CORTO DE OBSERVACIONES QUE LUEGO SERAN CORROBORADAS CON HISTOGRAMAS.}
 A visual inspection of Figures \ref{momento1} and \ref{momento2} suggest/indicates that the streamer region of CR-2082 was denser and colder than CR-2208.
@@
 For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.
-\textcolor{red}{aca los highpoints, comentar los colores y enunciar que cada uno puebla una regino termodinamica diferente}
+\temp{aca los highpoints, comentar los colores y enunciar que cada uno puebla una regino termodinamica diferente}
 
@@
 
-\textcolor{red}{Aca una linea que linkee la definicion del tipo de lineas en la seccion anterior con las regiones que se ven en la figura que se describe a continuacion}
+\temp{Aca una linea que linkee la definicion del tipo de lineas en la seccion anterior con las regiones que se ven en la figura que se describe a continuacion}
 Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations.
@@
 
-\textcolor{red}{Aun no se que decir sobre esto, sobre los downs se puede citar nuevo et al 2013 y decir algo sobre hay menos cantidad en cr2208 haciendo enfoque en que podria ser un indicador de que aun no esta en un minimo.
+\temp{Aun no se que decir sobre esto, sobre los downs se puede citar nuevo et al 2013 y decir algo sobre hay menos cantidad en cr2208 haciendo enfoque en que podria ser un indicador de que aun no esta en un minimo.
 Por otro lado mostrar los gradientes negativos va a ser util en los parrafos posteriores que expliquen porque en las lineas tipo 0 hay valores de $\phi_c$ negativos.}
@@
 
-\textcolor{red}{ Comentar en la discusion el paper de shift y cramer, para decir un poco sobre los down y la incapacidad del modelo en reproducirlos}
+\temp{ Comentar en la discusion el paper de shift y cramer, para decir un poco sobre los down y la incapacidad del modelo en reproducirlos}
 
@@
 
+For all type of lines, Table \ref{tabla_demt} summarize the quantitative comparative analysis between the results of the two target rotations sampling both minima.
+For CR-2082 quantities are expressed as absoulte values, qhile for CR-2208 they are informed relative to the corresponding results for CR-2082.
+The following major results concerning the structure of each rotation individually and their comparison can be drawn.
+
 \begin{table}
@@
 1  & 0&84 &(\Mi&11&3\%)  &   8&3 &(\Pl&15&3\%) &   1&30 &(\Pl&16&1\%) \\
-2  & 0&69 &(\Mi&10&1\%)  &   8&9 &(\Pl&19&1\%) &   1&33 &(\Pl&14&2\%) \\
+2  & 0&74 &(\Mi&16&1\%)  &   8&9 &(\Pl&19&1\%) &   1&33 &(\Pl&14&2\%) \\
 3  & 0&48 &(\Mi&12&5\%)  &   7&7 &(\Pl&10&5\%) &   0&98 &(\Pl&~5&7\%) \\
@@
 
-Table \ref{tabla_demt} summarize the quantitative comparative analysis between the results of the two target rotations sampling both minima.
-The following major results concerning the structure of each rotation individually and their comparison can be drawn.
-
-In the equatorial streamer of both rotations, increasing latitudes show decreasing \textcolor{red}{coronal base (1.055)} density, and increasing density scale height and electron temperature.
+In the equatorial streamer of both rotations, increasing latitudes show decreasing \temp{coronal base (1.055)} density, and increasing density scale height and electron temperature.
 In both rotations the CH regions are characterized sub-MK temperatures, and coronal base densities of order $\approx 1/2$ of the equatorial streamer.
@@
 
-A comparison of the results between the two rotations within the closed field lines \textcolor{red}{equatorial streamer belt} shows that CR-2208 is characterized by lower values of electron density and larger of temperature compared to CR-2082, as well as larger values of the density scale height.
-\textcolor{red}{Comentario sobre la estimacion de errores del paper pasado?}
+A comparison of the results between the two rotations within the closed field lines \temp{equatorial streamer belt} shows that CR-2208 is characterized by lower values of electron density and larger of temperature compared to CR-2082, as well as larger values of the density scale height.
+\temp{Comentario sobre la estimacion de errores del paper pasado?}
 
-In the coronal hole region, \textcolor{red}{No se si se puede aclarar algo en particular, quizas decir que ahora que tomamos una gran region abierta (en comparacion con el paper pasado) la seleccion toma lineas en la transicion de viento lento y rapido y eso genera que el histograma de Tm sea tan disperso}
+In the coronal hole region, \temp{No se si se puede aclarar algo en particular, quizas decir que ahora que tomamos una gran region abierta (en comparacion con el paper pasado) la seleccion toma lineas en la transicion de viento lento y rapido y eso genera que el histograma de Tm sea tan disperso}
 
@@
 
-\textcolor{red}{Aca vienen quizas 1 o 2 parrafos introduciendo y explicando los phi, los resultados de la Figura \ref{energia_demt} y un parrafo comentando esos resultados.
-Este parrafo va escrito por Ceci.}
+\temp{Aca vienen quizas 1 o 2 parrafos introduciendo y explicando los phi, los resultados de la Figura \ref{energia_demt} y un parrafo comentando esos resultados. Este parrafo va escrito por Ceci.}
 
@@
 
-\textcolor{red}{Parrafo introductorio}
+\temp{Parrafo introductorio?}
 
@@
 The black curve denotes the open-close boundary.
-
-\textcolor{red}{No pondría los mapas de 1.025 y diria algo asi como:\\}
-In the transition region, the plasma heats up and becomes less dense in several orders of magnitude in a short distance.
-Modeling this region correctly requires a high computational cost.
-For this reason the model uses a extended transition region and not real initial conditions of contour in density and electronic temperature.
-Consequently, the results below $1.065\,\mrsun$ were not taken into account in this article.
 
@@
 The open field regions in low latitudes maintain thermodynamic values associated with open regions.
-CR-2208 shows a well reconstruction of the AR around latitude $+10\mdeg$ and longitude $300\mdeg$ and a slight temperature difference between the poles \textcolor{red}{estoy asumiento que es una AR}.
+CR-2208 shows a well reconstruction of the AR around latitude $+10\mdeg$ and longitude $300\mdeg$ and a slight temperature difference between the poles \temp{estoy asumiento que es una AR}.
 In both rotations the open-closed boundaries derived from the respective AWSoM model match the shape of the contour levels of the tomographic maps of both the electron density and the electron mean temperature.
@@
 
-\textcolor{red}{Se presentan los midpoints para awsom que lucen mas rellenos xq no hay down loops y todo es super suave.}
+\temp{Se presentan los midpoints para awsom que lucen mas rellenos xq no hay down loops y todo es super suave.}
 
@@
 
-Due to the inability of the model to reproduce down legs, in this section we only use lines type 1, 2 and 3 and only select those that meet the chi square hypothesis test.
+Due to the inability of the model to reproduce down legs, in this section we only used lines type 1, 2 and 3 and only were selected those that meet the chi square hypothesis test.
 
@@
 
-To highlight the latitudinal structures, Figure \ref{perf_lat} shows for both rotations the latitudinal variation  of both the electron density and the electron mean temperature at the height $r=1.105\,\mrsun$, averaged over all longitudes (excluding the AR).
+To highlight the latitudinal structures observed in Figures \ref{carmaps_demt_2082} and \ref{carmaps_awsom_2082} for CR-2082 as well as Figures \ref{carmaps_demt_2208} and \ref{carmaps_awsom_2208} for CR-2208, Figure \ref{perf_lat} shows for both rotations the latitudinal variation  of both the electron density and the electron mean temperature at the height $r=1.105\,\mrsun$, averaged over all longitudes (excluding the AR).
 DEMT results are shown in blue lines while AWSoM results in red.
@@
 
-\textcolor{red}{
+\diego{Me gustaria hacer un comentario de cierre para esta figura que refiera las Figuras 3 y 9, como la linea de abajo, y que conecte con los histogramas que vienen a continuacion.
+Si no queda bien, hay que mover esta figura entre la actual figura 8 y 9.}
+
+This longitude-averaged behaviors match well with the physical locations of the legs shown in Figures \ref{rpoint_awsom} and \ref{rpoint_demt}.
+
+\diego{
 *awsom da valores mas altos en los polos\\
-*Parece haber una buena coincidencia en CR2082 en Te yen CR2208 en Ne.
-*En CR2082 en Ne demt es 20 \% mas grande que awsom en la zona cerrada.
+*Parece haber una buena coincidencia en CR2082 en Te yen CR2208 en Ne.\\
+*En CR2082 en Ne demt es 20 \% mas grande que awsom en la zona cerrada.\\
 *En cr2208 en Te, en la zona polar awsom es 30\% mas grande y awsom es 25\% mas grande en la region cerrada.
@@
 
-\textcolor{red}{Explicar lo que se observa}
+\diego{Explicar lo que se observa:
+- Ne 1.65 awsom menor que la de demt en CR2082 y mayor que la de CR2208 y debido a que decaen esponencialmente, el hecho que tiendan a valores similares conforme aumenta la altura implica escalas de altura similares.
+\\
+- Las temperaturas a 1.065 difieren en ambas rotaciones y en todas las regiones/tipos de lineas siendo siempre menor la de awsom, sin embargo las pendientes son similares en todas la regiones.
+Excepto que los gradientes de cr2208 en CH son mayores demt consistente con la fig de grad de temp, me preg si esto es por AIA.}
 
@@
 
-\textcolor{red}{
 As way of example, Figure \ref{histos_2082} and \ref{histos_2208} shows the statistical results of both rotations for the three types of field lines traced with DEMT (blue) and AWSoM results (red).
-From left to right the panels show the statistical distribution of $\NCB$, $\lN$, $\aTm$ and $B_{\rm CB}$.
-}
+From left to right the panels show the statistical distribution of $\NCB$, $\lN$ and $\aTm$.
+For all types of lines, Table \ref{tabla_comp} summarizes the median value of the statidtical distribution of each physical quantity derived from the analysis.
+The DEMT quantities are expressed as absoulte values, while for ASWSoM they are informed relative to the corresponding result for DEMT.
+
+\diego{comentar lo que se desprende de los graficos y la tabla.}
 
@@
 \end{figure}
+
+\begin{table}
+\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
+% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
+\hline
+Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
+       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
+\hline
+CR-2082\\
+1  & 0&84 &(\Mi&14&4\%)  &   8&3 &(\Mi&~2&5\%) &   1&30 &(\Mi&10&8\%) \\
+2  & 0&74 &(\Mi&21&9\%)  &   8&9 &(\Pl&~1&0\%) &   1&33 &(\Mi&~4&5\%) \\
+3  & 0&82 &(\Mi&17&9\%)  &   7&7 &(\Mi&~8&9\%) &   0&98 &(\Mi&~9&5\%) \\
+\hline          
+CR-2208\\
+1  & 0&74 &(\Pl&~6&4\%)  &   9&8 &(\Mi&~7&1\%) &   1&55 &(\Mi&12&3\%) \\
+2  & 0&62 &(\Pl&~8&2\%)  &  11&6 &(\Mi&17&2\%) &   1&55 &(\Mi&~9&7\%) \\
+3  & 0&42 &(\Mi&~4&8\%)  &   8&6 &(\Mi&~8&4\%) &   1&04 &(\Mi&~9&7\%) \\
+\end{tabular}
+\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
+FDEMT values are expressed in absolute terms, while for AWSoM they are informed as a percentual variation relative to the DEMT value.}
+\label{tabla_comp}
+\end{table}
 
@@
 
-Figure \ref{perf_lon_ne} shows for both rotations the DEMT and AWSoM longitude-averaged variation of the electron density at the height $r=1.105\,\mrsun$.
-Density shows higher values in the low-latitudes of the streamer and a nearly monotonic decrease towards the poles.
-The vertical black lines indicates the longitude-averaged latitudes of the open/close magnetic boundaries (excluding the AR in the case of CR-2082)
-
 Figure \ref{perf_lon_vr} show the longitude-averaged AWSoM radial wind speed $V_r$ at $6\,\mrsun$, where all field lines are open.
 The heliocentric current sheet (HCS) location is indicated by the minimum of the speed curve.\\
+\diego{can we say something without having traced the lines?}
 
-Everything to the south of the HCS maps down to the southern open region in the Figures \ref{perf_lon_ne}, and the same for the northern hemisphere, showing an anti-correlation between $N_e$ at low heights and $V_r$.
+For each rotation, everything to the south of the HCS maps down to the southern open region in the Figures \ref{perf_lat}, and the same for the northern hemisphere, showing an anti-correlation between $N_e$ at low heights and high $V_r$ at $6\,\mrsun$.
+
+\diego{Voy a intentar jugar con las lineas tipo 3 aumentando su cota inferior de latitud para ver si los histogramas de temp media dejan de ser tan dispersos y se vuelven mas sub-1MK. }
 

### 2019-12-11 lloveras_2020.tex
nuevo texto en seccion trace

@@
 
-\diego{Abajo una copia del paper anterior, esta seccion debe ser reescrita.}
+\diego{Falta explicar que todos los resultados pasamos a tenerlos en la grilla demt, y que en esa grilla se traza el campo.}
 
@@
 
-\temp{
-La temperatura en funcion de la altura a lo largo de lineas muestra comportamientos lineales.
+%La temperatura en funcion de la altura a lo largo de lineas muestra comportamientos lineales.
 En el presente trabajo nos focalizamos en lineas con temperaturas crecientes y decrecientes en foma lineal.
 Es decir nos quedamos con aquellas piernas donde el coeficiente de pearson entre la temperatura y la altura (rho) cumple rho mayor 0.5 (con p-value 0.05) y de esta forma se descartan aquellas piernas en las que los resultados DEMT no pueden asegurar un cambio notable de temperatura entre la base y el apice (asi no uso la palabra isotermico y evado ese problema)
-}
+
+%The temperature as a function of height along legs shows linear behaviors. 
+In the present work we focus on lines with increasing and decreasing temperatures in linear form.
+In other words, we selected those legs where the pearson coefficient between temperature and height ($\rho_{T,r}$) meets $|\rho_{T,r}| > 0.5$ \temp{(with p-value less than 0.05)}.
+In this way, those legs in which the DEMT results cannot ensure a noticeable change in temperature between the base and the apex, are discarded.
 
 The linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $\nabla_r T_m\,[\MK/\mrsun]$ along each leg.
-\diego{ambos fiteos utilizan los errores del paper anterior!!}
+\diego{En realidad esta regresion lineal utiliza de por si los errores, pero luego tmb los uso para el test de hipotesis, quizas vale la pena ponerlo solo ahi.}
 
-\temp{
-*to measure how good the quality of the exponential fit to the electron density and the linear fit to the temperature data are, a chi-square merit function was used \temp{eq 15.2.2}.
-The errors were estimated in lloveras-2017 $tanto y tanto \%$ and the lesg with p-value $>0.005$ were rejected.
-*aplicamos un test de hipotesis chi cuadrado asumiendo como hipotesis nula que los valores ajustados a cada pierna corresponden al valor esperado de la funcion distribucion chi cuadrado Df,E.
-Donde DF es la cantidad de datos en cada linea-2 y E
-2) el p-valor es un concepto estadístico, no veo xq deberia ser explicado. Lo que si, en el paper explicare bien las hipotesis nulas y de esa forma el p-valor queda bien claro.
-El p-valor es una cuantificacion de con cuanta probabilidad de exito estas rechazando o aceptando una hipotesis en particular que se la suele denominar hipotesis nula.
-En este caso, con 95$\%$ de seguridad estas rechazando las piernas que tienen un $pearson_x,y = 0$. Es decir te estarias quedando con aquellas que tienen una dependencia lineal entre x e y.
-En el segundo caso, el test de hipotesis seria sobre la hip nula de que los datos provienen una funcion distribucion donde la recta fiteada de esos datos es el valor esperado de la distribucion.
+To measure how good the quality of the exponential fit to the electron density and the linear fit to the temperature data are, a chi-square merit function was used (see Section 15.2 \citet{recipes}).
+The errors were estimated in \citet{lloveras_2017}, $0.07$ MK for $T_m$ and $0.04 10^8 cm^{-3}$ for $N_e$ and legs with p-value $>0.005$ were rejected.
+
+%el p-valor es un concepto estadístico, no veo xq deberia ser explicado. Lo que si, en el paper explicare bien las hipotesis nulas y de esa forma el p-valor queda bien claro.
+%El p-valor es una cuantificacion de con cuanta probabilidad de exito estas rechazando o aceptando una hipotesis en particular que se la suele denominar hipotesis nula.
+%En este caso, con 95$\%$ de seguridad estas rechazando las piernas que tienen un $pearson_x,y = 0$. Es decir te estarias quedando con aquellas que tienen una dependencia lineal entre x e y.
+%En el segundo caso, el test de hipotesis seria sobre la hip nula de que los datos provienen una funcion distribucion donde la recta fiteada de esos datos es el valor esperado de la distribucion.
 Con lo cual hacerle un test chi cuadrado te da una idea de cuan acertado o no es el ajuste.
@@
 Eso es lo que representa el p-valor =0.05 en este caso (el area bajo la funcion distribucion, es decir, probabilidad).
-}
 
-\temp{*Nos quedamos con los fiteos que cumplen test de hipotesis chi cuadrado en temp y densidad.
-OBS: SE usan los errores en temp y densidad. Citar numerical recipes seccion 15.2 \citet{recipes}}
+To be selected a loop must meet all following conditions.
 
-\temp{Se eligen loops con abs(person temp) mayor a .5 lo cual nos permite descartar loops QI. gradT suficientemente grandes.}
+\begin{enumerate}
+
+\item 
+Each leg of the loop must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the loop.
+
+\item 
+The pearson value must comply $|\rho_{T,r}| > 0.5$.
+
+\item 
+The p-value of both the exponential and linear fit must be less than 0.05.
+
+\end{enumerate}
 
@@
 To that end four different types of legs corresponding with four different types of magnetic structures where selected:
-\temp{Hacer explicacion de los tipos de lineas bien secos, luego en fig 3 hacer notar que implica cada una en cuanto a estructura magnetica}\\
-  0 - Small (meaning with apex within the DEMT range of heights) closed field lines in the latitudes range $[-30\mdeg,+30\mdeg]$ and $\nabla_r T_m < 0$.
-This class thoroughly populates the equator of the Streamer belt during a minimum solar rotation.
+%\temp{Hacer explicacion de los tipos de lineas bien secos, luego en fig 3 hacer notar que implica cada una en cuanto a estructura magnetica}\\
 
-  I - Small closed field lines in all latitudes, with $\nabla_r T_m > 0$. This class thoroughly populates the inner of the Streamer belt.
+\begin{itemize}
+ \item Type 0 - Small (meaning with apex within the DEMT range of heights) closed field lines in the latitudes range $[-30\mdeg,+30\mdeg]$ and $\nabla_r T_m < 0$.
+%This class thoroughly populates the equator of the Streamer belt during a minimum solar rotation.
 
-  II - Large (meaning their apex surpasses the DEMT range of heights) closed field lines in the latitudes range $[-90\mdeg,-30\mdeg] \cup [+30\mdeg,+90\mdeg]$ and $\nabla_r T_m > 0$.
-This class is mostly populated by very large trans-equatorial field lines forming the envelope of the Streamer belt.
+\item  Type I - Small closed field lines in all latitudes, with $\nabla_r T_m > 0$. %This class thoroughly populates the inner of the Streamer belt.
 
- III - Open (meaning with apex out the DEMT range of heights) field lines in the latitudes range $[-90\mdeg,-60\mdeg] \cup [+60\mdeg,+90\mdeg]$ and $\nabla_r T_m > 0$.
+\item  Type II - Large closed field lines (meaning their apex surpasses the DEMT range of heights) in the latitudes range $[-90\mdeg,-30\mdeg] \cup [+30\mdeg,+90\mdeg]$ and $\nabla_r T_m > 0$.
+%This class is mostly populated by very large trans-equatorial field lines forming the envelope of the Streamer belt.
 
-\temp{Hice las definiciones con gradiente de temperatura para que quede mas claro, pero en realidad uso el pearson.} 
-%\temp{que quede claro que de ahora en mas solo consideramos ajustes de loops up, es decir pearson temp > 0.5 debido a que awsom solo tiene up.}
+\item Type III - Open field lines (meaning with apex out the DEMT range of heights) in the latitudes range $[-90\mdeg,-60\mdeg] \cup [+60\mdeg,+90\mdeg]$ and $\nabla_r T_m > 0$.
+
+\end{itemize}
+\diego{Hice las definiciones con gradiente de temperatura para que quede mas claro, pero en realidad uso el pearson.}
 
@@
 \diego{sugerencias para el nombre?}
+
 \section{Results}\label{resu}
@@
 As an example, Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} shows the latitude-longitude maps for both tomographic results for CR-2082 and CR-2208 at $r=1.025, 1.065$ and $1.105\,\mrsun$.
-Black voxels correspond to non-reconstructed regions (explained in Section \ref{demt}).
+Black voxels correspond to non-reconstructed voxels (explained in Section \ref{demt}).
 

### 2019-12-12 lloveras_2020.tex
editado por A.

@@
 
-\usepackage{xcolor}
+\usepackage[dvipsnames]{xcolor}
 
@@
 \newcommand{\Nqi}{N_{\rm QI}}
+\newcommand{\sqravgN}{\sqrt{\langle N_{e,i}^2 \rangle}}
 
@@
 
-\def\Pl{\texttt{+}}
-\def\Mi{\texttt{-}}
+\newcommand{\Pl}{\texttt{+}}
+\newcommand{\Mi}{\texttt{-}}
 
@@
 
+%---------REMOVE DEFs BEFORE SUMBISSION----------------
 \def\diego#1{\textcolor{red}{DIEGO: #1}}
-\def\albert#1{\textcolor{blue}{ALBERT: #1}}
-\def\fede#1{\textcolor{green}{FEDE: #1}}
-
-\def\temp#1{\textcolor{mygray}{TEMPORAL: #1}}
+\def\albert#1{\textcolor{blue}{#1}}
+\def\fede#1{\textcolor{ForestGreen}{FEDE: #1}}
+\def\temp#1{\textcolor{mygray}{#1}}
+\def\edit#1{\textcolor{Apricot}{#1}}
+%------------------------------------------------------
 
@@
 \begin{abstract}
-Observational tools play an essential role in advancing our understanding of the physics of the solar corona.
-They provide validation data to improve three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, key to enhance their space weather forecasting capabilities.
-Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of fundamental plasma parameters of the solar corona at a global scale.
+Observational \albert{techniques} play an essential role in advancing our understanding of the physics of the solar corona.
+They provide validation data to improve three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, \albert{enhancing} their space weather forecasting capabilities.
+Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of some \albert{of the fundamental} plasma parameters of the solar corona at a global scale.
 Based on EUV data of space borne instruments, SRT allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun.
-We carry out a study of the corona combining tomographic reconstructions with MHD simulations of the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF).
+We carry out a study of the corona combining tomographic reconstructions with MHD simulations \albert{using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF).
 Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24.
@@
 \subsection{DEMT reconstructions}\label{demt}
-\temp{*Tratado de imagenes}
-\temp{*FBE}
-\temp{*LDEM}
-
+\temp{* Procesado de imagenes}\\
+\temp{* FBE}\\
+\temp{* LDEM}\\
 *Paso 1: obtencion de FBE\\
@@
 More specifically, at the $i$-th voxel,
+
 \begin{eqnarray}\label{momento1}
@@
 
-*Una medida del grado de acuerdo de la reconstruccion
+\albert{We define next a measure of the average relative difference between the tomographic and the synthetic FBE in each voxel, as}
+
 \begin{equation}\label{R}
-R_i \, \equiv \ (1/K) \, \sum_{k=1}^K \left| \, 1 - \FBE^{(k)}_{i,\rm syn} / \,\FBE^{(k)}_{i,\rm tom}\, \right| \,,
+R_i \, \equiv \ (1/K) \, \sum_{k=1}^K \left| \, 1 - \FBE^{(k)}_{i,\rm syn}\,/\,\FBE^{(k)}_{i,\rm tom}\, \right| \,,
 \end{equation}
 
-so that the final product of DEMT is in the form of 3D maps of the electron density and mean temperature. These relationships was derived in detail in \citealt{frazin_2009} (see Appendix C).
-
-\temp{*aclarar que consideramos Ne como $\sqrt{<N_e ^2>}$.}
-
-\temp{red}{*Mejoras de la tecnica con respecto a trabajos previos}
+so that the final product of DEMT is in the form of 3D maps of the electron density and mean temperature.
+These relationships \albert{were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
+\temp{* Aclarar que consideramos Ne como $\sqrt{<N_e ^2>}$.} \albert{ALBERT: Yo creo que es mejor simplemente hablar de $\sqravgN$}\\
+\temp{* Mejoras de la DEMT con respecto a trabajos previos}.
 
@@
 \subsection{AWSoM simulations}\label{awsom} 
-\temp{*Que es, que modela, que datos usa, y que se obtiene en general y en particular para este trabajo}
-
-\temp{Se debe aclarar que solo produce resultados razonables arriba de 1.065}
-
-\temp{No pondría los mapas de 1.025 y diria algo asi como:\\}
-In the transition region, the plasma heats up and becomes less dense in several orders of magnitude in a short distance.
-Modeling this region correctly requires a high computational cost.
-For this reason the model uses a extended transition region and not real initial conditions of contour in density and electronic temperature.
-Consequently, the results below $1.065\,\mrsun$ were not taken into account in this article.
+\temp{* Qué es, qué modela, qué datos usa, y qué se obtiene en general y en particular para este trabajo}\\
+\temp{* Se debe aclarar que solo produce resultados razonables arriba de 1.065}\\
+\temp{No pondría los mapas de 1.025 y diria algo asi como:}\\
+In the transition region \albert{(TR)}, the plasma heats up and becomes less dense \albert{by} several orders of magnitude \albert{over} a short distance.
+Modeling this region \albert{realistically has a very high computational cost}.
+For this \albert{reason,} the model uses \albert{an artificially} extended \albert{TR about $\approx 0.05\,\mrsun$ thick, as well as artificially high boundary conditions for the electronic density and temperature}.
+Consequently, model results below \albert{$\approx 1.05\,\mrsun$} were not taken into account in this article.
 

### 2019-12-12 lloveras_2020.tex
editado por Albert 12/Dic/2019 - 18:44 hs

@@
 \usepackage{setspace}
-
+\usepackage[utf8]{inputenc}
 \usepackage[dvipsnames]{xcolor}
@@
 \newcommand{\med}{{\rm Md}}
-\newcommand{\avgTe}{\left<T_\textrm{m}\right>}
+\newcommand{\avgTe}{\left<\Tm\right>}
 \newcommand{\MK}{{\rm MK}}
@@
 \newcommand{\NCB}{N_{\rm CB}}
-\newcommand{\aTm}{\left< T_\textrm{m}\right>}
+\newcommand{\aTm}{\left< \Tm\right>}
 \newcommand{\Nqi}{N_{\rm QI}}
 \newcommand{\sqravgN}{\sqrt{\langle N_{e,i}^2 \rangle}}
-
+\newcommand{\dr}{\triangledown_r}
+\newcommand{\er}{\mathbf{e}_r}
+\newcommand{\Te}{T_{\rm e}}
+\newcommand{\Tm}{T_{\rm m}}
+\newcommand{\Ne}{N_{\rm e}}
+\newcommand{\rhoTr}{\rho(T,r)}
 \newcommand{\Tefit}{T_{e,{\rm fit}}}
@@
 
-Once the LDEM is determined at each voxel, the average squared electron density $\langle N_e^2 \rangle$ and the electron mean temperature $T_\textrm{m}$ in the voxel can be computed by taking its zeroth and first moments over temperature.
+Once the LDEM is determined at each voxel, the average squared electron density $\langle \Ne^2 \rangle$ and the electron mean temperature $\Tm$ in the voxel can be computed by taking its zeroth and first moments over temperature.
 More specifically, at the $i$-th voxel,
@@
 These relationships \albert{were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
-\temp{* Aclarar que consideramos Ne como $\sqrt{<N_e ^2>}$.} \albert{ALBERT: Yo creo que es mejor simplemente hablar de $\sqravgN$}\\
+\temp{* Aclarar que consideramos Ne como $\sqrt{<\Ne ^2>}$.} \albert{ALBERT: Yo creo que es mejor simplemente hablar de $\sqravgN$}\\
 \temp{* Mejoras de la DEMT con respecto a trabajos previos}.
@@
 
-For both rotations, the DEMT and AWSoM 3D maps of electron density $N_e$, electron mean temperature $T_\textrm{m}$ and electron temperature $T_\textrm{e}$ respectively were traced along the magnetic field lines modeled using AWSoM as described at the end of Section \ref{demt}.
+For both rotations, the DEMT and AWSoM 3D maps of electron density $\Ne$, electron mean temperature $\Tm$ and electron temperature $\Te$ respectively were traced along the magnetic field lines modeled using AWSoM as described at the end of Section \ref{demt}.
 In the case of closed loops, results were separated into their two legs, defined as the two segments that go from the coronal base up to the apex.
 
-For each open field line, and for each leg of the closed ones, an exponential fit was then applied to the $N_e(r)$ data points, and a linear fit applied to the $T_m(r)$ data points, as described by
+For each open field line, and for each leg of the closed ones, an exponential fit was then applied to the $\Ne(r)$ data points, and a linear fit applied to the $\Tm(r)$ data points, as described by
 
 \begin{eqnarray}\label{Nfit}
-N_e &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]}\\
+\Ne &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]}\\
 \label{Tfit}
-T_\textrm{m} &=&  \nabla_r T_m \,r\,+\,T_\textrm{0}
+\albert{\Tm} &=& \albert{\dr \Tm(r) \ r\,+\,T_0}
 \end{eqnarray}
@@
 \noindent
-where $h \equiv r - 1\,\mrsun$, and $a$ and $b$ are constants.
+\albert{where $\l$ is the electron density scale height, $h \equiv r - 1\,\mrsun$ is the coronal height measured from the photosphere, $\dr\equiv\er\cdot\nabla$ is the radial derivative operator (being $\er$ the heliocentric radial unit vector), and $T_0$ and $N_0$ are constants.}
 
@@
 In the present work we focus on lines with increasing and decreasing temperatures in linear form.
-In other words, we selected those legs where the pearson coefficient between temperature and height ($\rho_{T,r}$) meets $|\rho_{T,r}| > 0.5$ \temp{(with p-value less than 0.05)}.
+In other words, we selected those legs where the \albert{Pearson correlation coefficient $\rho$ between temperature $T$ and radius $r$ meets $|\rhoTr| > 0.5$}.
+\temp{(with p-value less than 0.05)}.
 In this way, those legs in which the DEMT results cannot ensure a noticeable change in temperature between the base and the apex, are discarded.
 
-The linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $\nabla_r T_m\,[\MK/\mrsun]$ along each leg.
+The linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg.
 \diego{En realidad esta regresion lineal utiliza de por si los errores, pero luego tmb los uso para el test de hipotesis, quizas vale la pena ponerlo solo ahi.}
@@
 To measure how good the quality of the exponential fit to the electron density and the linear fit to the temperature data are, a chi-square merit function was used (see Section 15.2 \citet{recipes}).
-The errors were estimated in \citet{lloveras_2017}, $0.07$ MK for $T_m$ and $0.04 10^8 cm^{-3}$ for $N_e$ and legs with p-value $>0.005$ were rejected.
+The errors were estimated in \citet{lloveras_2017}, $0.07$ MK for $\Tm$ and $0.04 10^8 cm^{-3}$ for $\Ne$ and legs with p-value $>0.005$ were rejected.
 
@@
 \item 
-The pearson value must comply $|\rho_{T,r}| > 0.5$.
+The \albert{value of the Pearson correation coefficient meets $|\rhoTr| > 0.5$.}
 
@@
 \begin{itemize}
- \item Type 0 - Small (meaning with apex within the DEMT range of heights) closed field lines in the latitudes range $[-30\mdeg,+30\mdeg]$ and $\nabla_r T_m < 0$.
+ \item Type 0 - Small (meaning with apex within the DEMT range of heights) closed field lines in the latitudes range $[-30\mdeg,+30\mdeg]$ and $\dr \Tm < 0$.
 %This class thoroughly populates the equator of the Streamer belt during a minimum solar rotation.
 
-\item  Type I - Small closed field lines in all latitudes, with $\nabla_r T_m > 0$. %This class thoroughly populates the inner of the Streamer belt.
+\item  Type I - Small closed field lines in all latitudes, with $\dr \Tm > 0$. %This class thoroughly populates the inner of the Streamer belt.
 
-\item  Type II - Large closed field lines (meaning their apex surpasses the DEMT range of heights) in the latitudes range $[-90\mdeg,-30\mdeg] \cup [+30\mdeg,+90\mdeg]$ and $\nabla_r T_m > 0$.
+\item  Type II - Large closed field lines (meaning their apex surpasses the DEMT range of heights) in the latitudes range $[-90\mdeg,-30\mdeg] \cup [+30\mdeg,+90\mdeg]$ and $\dr \Tm > 0$.
 %This class is mostly populated by very large trans-equatorial field lines forming the envelope of the Streamer belt.
 
-\item Type III - Open field lines (meaning with apex out the DEMT range of heights) in the latitudes range $[-90\mdeg,-60\mdeg] \cup [+60\mdeg,+90\mdeg]$ and $\nabla_r T_m > 0$.
+\item Type III - Open field lines (meaning with apex out the DEMT range of heights) in the latitudes range $[-90\mdeg,-60\mdeg] \cup [+60\mdeg,+90\mdeg]$ and $\dr \Tm > 0$.
 
@@
 
-Once the LDEM was determined for each rotation, the electron density $N_e$ and electron mean temperature $T_\textrm{m}$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}.
+Once the LDEM was determined for each rotation, the electron density $\Ne$ and electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}.
 As an example, Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} shows the latitude-longitude maps for both tomographic results for CR-2082 and CR-2208 at $r=1.025, 1.065$ and $1.105\,\mrsun$.
@@
 \includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
-\caption{Carrington maps of DEMT results: $N_e$ (left panels) and $T_\textrm{m}$ (right panels) for CR-2082.
+\caption{Carrington maps of DEMT results: $\Ne$ (left panels) and $\Tm$ (right panels) for CR-2082.
 Top, middle and bottom panels show the results at three heliocentric heights, $1.025$, $1.065$ and $1.105\,\mrsun$ respectively.
@@
 
- As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $\nabla_r T_m$, and the height-averaged (along the loop) electron mean temperature $\aTm$.
-As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height may be used to compute the tomographic basal electron density at $ N_e(r=1.025\,\mrsun)$ as in previous articles.
+ As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $\dr \Tm$, and the height-averaged (along the loop) electron mean temperature $\aTm$.
+As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height may be used to compute the tomographic basal electron density at $ \Ne(r=1.025\,\mrsun)$ as in previous articles.
 In this case, for an further comparison analysis with the AWSoM results, we selected the lowest height where the results of the MHD model are reliable, that is $1,065\,\mrsun)$.
@@
 
-Figure \ref{gradt_demt} shows histograms (normalized to the total amount of field lines) of the temperature radial gradients ($\nabla_r T_m$) for every type of line and for both rotations.
+Figure \ref{gradt_demt} shows histograms (normalized to the total amount of field lines) of the temperature radial gradients ($\dr \Tm$) for every type of line and for both rotations.
 The lack of population around values close to zero is due to the strict condition $|\rho_t| > 0.5$ that discards possible isothermal values.
@@
 \caption{Comparative statistical distributions of DEMT reults.
-From left to right: the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all types of legs defined in Section \ref{trace}.
+From left to right: the coronal base electron density $\Ne(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all types of legs defined in Section \ref{trace}.
 Results of CR2082 are shown in blue while those of CR-2208 in red.
@@
 
-As an example of the AWSoM results, Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} shows the latitude-longitude maps for $N_e$ and $T_e$ modeled for CR-2082 and CR-2208 at $r=1.025, 1.065$ and $1.105\,\mrsun$.
+As an example of the AWSoM results, Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} shows the latitude-longitude maps for $\Ne$ and $T_e$ modeled for CR-2082 and CR-2208 at $r=1.025, 1.065$ and $1.105\,\mrsun$.
 The black curve denotes the open-close boundary.
 
-A visual inspection of the AWSoM results shows that both reconstruction are very axysimmetric for $N_e$ and $T_e$ as well.
+A visual inspection of the AWSoM results shows that both reconstruction are very axysimmetric for $\Ne$ and $T_e$ as well.
 The closed region is denser and hotter than the open region.
@@
 In the same way as in Section \ref{demt_res}, the model results were traced along the magnetic lines obtained with it.
-This allowed to obtain $N_e(r)$ and $T_e(r)$ along the magnetic lines and fit them to the Equations \ref{Nfit} and \ref{Tfit}.
+This allowed to obtain $\Ne(r)$ and $T_e(r)$ along the magnetic lines and fit them to the Equations \ref{Nfit} and \ref{Tfit}.
 
@@
 
-To summarize the comparison between both results during both rotations at full height, it is shown in Figure \ref{perfiles_promedio} the average fits of $N_e(r)$ and $T_e(r)$ for every type of legs.
+To summarize the comparison between both results during both rotations at full height, it is shown in Figure \ref{perfiles_promedio} the average fits of $\Ne(r)$ and $T_e(r)$ for every type of legs.
 
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_short.eps}
-\caption{Average fits of $N_e(r)$ and $T_e(r)$ for legs of type I (blue), type II (red) and type III (green) for CR-2082 (top panel) and CR-2208 (bottom panel) using DEMT (solid) and AWSoM (dashed) results.}
+\caption{Average fits of $\Ne(r)$ and $T_e(r)$ for legs of type I (blue), type II (red) and type III (green) for CR-2082 (top panel) and CR-2208 (bottom panel) using DEMT (solid) and AWSoM (dashed) results.}
 \label{perfiles_promedio}
@@
 \caption{Comparative statistical distributions for CR-2082 between DEMT (blue) and AWSoM (red).
-From left to right: the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average $\aTm$ along the four types of legs considered in Section \ref{trace}.
+From left to right: the coronal base electron density $\Ne(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average $\aTm$ along the four types of legs considered in Section \ref{trace}.
 In each panel the median ($m$) is indicated.}
@@
 For each field line, the data points of electron density and electron mean temperature versus height were fitted to the functions given by Equations 5 and 6 of Section \ref{trace}.
-As a result, the footpoint electron density $N_0$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $a=\textrm{d}T_m/\textrm{d}r$, and the height-averaged (along the loop) electron mean temperature $\aTm$.
-As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data versus height was used to compute the {coronal base electron density} here defined as $\NCB\equiv N_e(r=1.025\,\mrsun)$.
+As a result, the footpoint electron density $N_0$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $a=\textrm{d}\Tm/\textrm{d}r$, and the height-averaged (along the loop) electron mean temperature $\aTm$.
+As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data versus height was used to compute the {coronal base electron density} here defined as $\NCB\equiv \Ne(r=1.025\,\mrsun)$.
 Also, for each field line the coronal base magnetic field strength $B_{\rm CB}\equiv B(r=1.025\,\mrsun)$ and its height-averaged value along the loop $\left<B\right>$ were also computed.
@@
 
-For each rotation, everything to the south of the HCS maps down to the southern open region in the Figures \ref{perf_lat}, and the same for the northern hemisphere, showing an anti-correlation between $N_e$ at low heights and high $V_r$ at $6\,\mrsun$.
+For each rotation, everything to the south of the HCS maps down to the southern open region in the Figures \ref{perf_lat}, and the same for the northern hemisphere, showing an anti-correlation between $\Ne$ at low heights and high $V_r$ at $6\,\mrsun$.
 

### 2019-12-13 lloveras_2020.tex
editado por Albert 12/Dic/2019 - 19:22 hs
mergeo con cambios de albert y agregado de texto en seccion 3.1

@@
 \newcommand{\NCB}{N_{\rm CB}}
-\newcommand{\aTm}{\left< \Tm\right>}
+\newcommand{\aTm}{\left<\Tm\right>}
 \newcommand{\Nqi}{N_{\rm QI}}
-\newcommand{\sqravgN}{\sqrt{\langle N_{e,i}^2 \rangle}}
+
 \newcommand{\dr}{\triangledown_r}
@@
 \newcommand{\Tm}{T_{\rm m}}
+\newcommand{\Tmi}{T_{{\rm m},i}}
 \newcommand{\Ne}{N_{\rm e}}
+\newcommand{\Nm}{N_{\rm m}}
+\newcommand{\Nsqmi}{N^2_{{\rm m},i}}
 \newcommand{\rhoTr}{\rho(T,r)}
 \newcommand{\Tefit}{T_{e,{\rm fit}}}
+\newcommand{\sqravgN}{\sqrt{\Nsqmi}}
 
@@
 
+\albert{
 \begin{eqnarray}\label{momento1}
-\langle N_{e,i}^2 \rangle &=& \int\,\textrm{d}T\,\LDEM_i(T),\label{Ne} \\ 
+ \Nsqmi = \langle \Ne^2 \rangle_i &=& \int\,\textrm{d}T\,\LDEM_i(T),\label{Ne} \\ 
 \label{momento2}
- T_{\textrm{m},i}   &=& \frac{1}{\langle N_{e,i}^2 \rangle}\,\int\,\textrm{d}T\,T\,\LDEM_i(T),\label{Tm} 
+ \Tmi  = \langle \Te \rangle_i &=& \frac{1}{\langle \Ne^2 \rangle_i}\,\int\,\textrm{d}T\,T\,\LDEM_i(T),\label{Tm} 
 \end{eqnarray}
+}
 
@@
 Modeling this region \albert{realistically has a very high computational cost}.
-For this \albert{reason,} the model uses \albert{an artificially} extended \albert{TR about $\approx 0.05\,\mrsun$ thick, as well as artificially high boundary conditions for the electronic density and temperature}.
-Consequently, model results below \albert{$\approx 1.05\,\mrsun$} were not taken into account in this article.
+For this \albert{reason,} the model uses \albert{an artificially} extended \albert{TR about $\approx 0.05\,\mrsun$ thick, as well as artificially large values for the electronic density and temperature as boundary conditions in $r=1\,\mrsun$.} Consequently, model results below \albert{$\approx 1.05\,\mrsun$} were not taken into account in this article.
 
@@
 To measure how good the quality of the exponential fit to the electron density and the linear fit to the temperature data are, a chi-square merit function was used (see Section 15.2 \citet{recipes}).
-The errors were estimated in \citet{lloveras_2017}, $0.07$ MK for $\Tm$ and $0.04 10^8 cm^{-3}$ for $\Ne$ and legs with p-value $>0.005$ were rejected.
+The errors were estimated in \citet{lloveras_2017}, $0.07$ MK for $\Tm$ and $0.04\,10^8 cm^{-3}$ for $\Ne$ and legs with p-value $>0.005$ were rejected.
 
@@
 \item 
-The \albert{value of the Pearson correation coefficient meets $|\rhoTr| > 0.5$.}
+The \albert{value of the Pearson correlation coefficient meets $|\rhoTr| > 0.5$.}
 
@@
 Black voxels correspond to non-reconstructed voxels (explained in Section \ref{demt}).
+Thick-black curves indicate the open/closed boundaries based on the AWSoM model.
 
@@
 In the AR, there is a lack of match between the open-closed boundaries and the tomographic reconstructions of density and temperature, that is why those ranges were excluded from the analysis.
-Closed regions are characterized by relatively larger values of density and temperature in comparison to the open regions.
 
@@
 These thermodynamic structures have been reported for other rotations in previous works \citep{lloveras_2017}.
+Closed regions are characterized by relatively larger values of density and temperature in comparison to the open regions.
+\diego{que mas se puede agregar?}
 
@@
 For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.
-\temp{aca los highpoints, comentar los colores y enunciar que cada uno puebla una regino termodinamica diferente}
+
+\temp{aca se defininen los highpoints, se comentan los colores y enunciar que cada uno puebla una regino termodinamica diferente}
 
@@
 As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height may be used to compute the tomographic basal electron density at $ \Ne(r=1.025\,\mrsun)$ as in previous articles.
-In this case, for an further comparison analysis with the AWSoM results, we selected the lowest height where the results of the MHD model are reliable, that is $1,065\,\mrsun)$.
+In this case, for further comparison analysis with the AWSoM results, we selected the lowest height where the results of the MHD model are reliable, that is $1,065\,\mrsun$.
 
-\temp{Aca una linea que linkee la definicion del tipo de lineas en la seccion anterior con las regiones que se ven en la figura que se describe a continuacion}
-Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations.
+\temp{Aca una linea que linkea la definicion del tipo de lineas en la seccion anterior con las regiones que se ven en la figura que se describe a continuacion}
+
+As a way of knowing the physical position of the types of lines defined in Section \ref{trace}, the Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations.
 In cyan the type 0 lines are indicated, populating the most equatorial latitudes (dominated mostly by down loops).
-In blue the type 1 lines, populating mostly the mid latitudes of the streamer.
-In red the type 2 lines, populating the edge that assemble the envelope around the streamer, and in green dots the type 3 lines, populating the coronal holes.
+This kind of structures has been informed in previous works, \citet{lloveras_2017} observed down loops in a rotation during the solar minima of 1996 and for the previous rotation CR-2081.
+The amount of down loops in the equatorial latitudes.
+A decrease in the amount of down loops in equatorial latitudes could be an indicator of increased coronal activity \citet{nuevo_2013}.
+In blue the type 1 lines, populating all the streamer but mostly the mid latitudes.
+In red the type 2 lines, are mostly very large trans-equatorial field lines forming the envelope of the Streamer belt, and in green dots the type 3 lines, populating the coronal holes.
 
-This selection of the types of lines automatically leads to thermodynamic regions arranged along all longitudes with good symmetry in both rotations, this is because the rotations are at a minimum of activity and the static corona is a good approximation.
+Of the 45000 legs selected in 2082, 14\% are type 0, 38\% are type 1, 23\% are type 3 and 25\% type 4, on the other hand of the 59000 legs selected in 2208, 8\% are type 0, 43\% are type 1, 22\% are type 3 and 30\% type 4.
+
+This selection of types of lines automatically leads to specific regions arranged along all longitudes associated with different thermodynamic, with good symmetry between both hemispheres in both rotations.%, this is because the rotations are at a minimum of activity and the static corona is a good approximation.
 
@@
 
-Figure \ref{gradt_demt} shows histograms (normalized to the total amount of field lines) of the temperature radial gradients ($\dr \Tm$) for every type of line and for both rotations.
-The lack of population around values close to zero is due to the strict condition $|\rho_t| > 0.5$ that discards possible isothermal values.
+To compare the results obtained with the traced results in both rotations and for each type of lines (associated with differents types of regions), Figure \ref{gradt_demt} shows histograms (normalized to the total amount of the field lines selected) of the temperature radial gradients ($\dr \Tm$) for every type of line and for both rotations.
+The lack of population around values close to zero is due to the strict condition $|\rho_t| > 0.5$ that discards possible isothermal values, according to DEMT results.
 
-\temp{Aun no se que decir sobre esto, sobre los downs se puede citar nuevo et al 2013 y decir algo sobre hay menos cantidad en cr2208 haciendo enfoque en que podria ser un indicador de que aun no esta en un minimo.
-Por otro lado mostrar los gradientes negativos va a ser util en los parrafos posteriores que expliquen porque en las lineas tipo 0 hay valores de $\phi_c$ negativos.}
-\textcolor{blue}{Quizas sea un buen lugar para comentar el paper up down de Fede, diciendo que estas estructuras ya se han visto antes, etc., suena bien que les de algo de importancia xq en la prox seccion voy a decir que no hay lineas tipo 0 justamente xq el modelo es incapaz de reproducir los down}
+Both rotations are characterized by lines of type 0 with mean values of $-2.5\, \rm MK/\mrsun$, mean values of $2.3\, \rm MK/\mrsun$ in type 1 and $2.4\, \rm MK/\mrsun$ in type 2.
+The only notable difference is the smaller number of type 0 lines in CR-2208 and the mean value of $4.5\, \rm MK/\mrsun$ in type 3 for CR-2208 which is twice that for the other rotation.
 
-\temp{ Comentar en la discusion el paper de shift y cramer, para decir un poco sobre los down y la incapacidad del modelo en reproducirlos}
+\temp{mostrar los gradientes negativos va a ser util en los parrafos posteriores que expliquen porque en las lineas tipo 0 hay valores de $\phi_c$ negativos.}
+
+%\temp{ Comentar en la discusion el paper de shift y cramer, para decir un poco sobre los down y la incapacidad del modelo en reproducirlos}
 
@@
 
+\temp{este inicio de linea se repite del anterior}\\
 As an example of the traced magnitudes, Figure \ref{histos_fulldemt} shows the statistical results of both rotations for all field lines types.
@@
 
-In the equatorial streamer of both rotations, increasing latitudes show decreasing \temp{coronal base (1.055)} density, and increasing density scale height and electron temperature.
+\diego{si queda una asociacion directa entre los tipos de lineas y las estructuras de streamer, CH etc entonces usaria esos nombres a continuacion.}\\
+From the equatorial streamer of both rotations, increasing latitudes show decreasing \temp{coronal base (1.055)} density, and increasing density scale height and electron temperature.
 In both rotations the CH regions are characterized sub-MK temperatures, and coronal base densities of order $\approx 1/2$ of the equatorial streamer.
 Histograms with sharp populations indicates that for both rotations the values of all physical quantities exhibit a strong symmetry between both hemispheres.
+\diego{no se si decir sharp queda bien.}
 
-A comparison of the results between the two rotations within the closed field lines \temp{equatorial streamer belt} shows that CR-2208 is characterized by lower values of electron density and larger of temperature compared to CR-2082, as well as larger values of the density scale height.
-\temp{Comentario sobre la estimacion de errores del paper pasado?}
-
-In the coronal hole region, \temp{No se si se puede aclarar algo en particular, quizas decir que ahora que tomamos una gran region abierta (en comparacion con el paper pasado) la seleccion toma lineas en la transicion de viento lento y rapido y eso genera que el histograma de Tm sea tan disperso}
+A comparison of the results between the two rotations shows that CR-2208 is characterized by lower values (between $11\%\, \rm and\, 16\%$) of electron density than CR-2082, higher values of density scale height (between $4\%\, \rm and\,19\%$) and higher values of electron temperature (between $6\%\, \rm and\,21\%$).
 
 %To establish if the differences in the results between the two rotations are significant, Section \ref{uncertainties} estimates the error bars due the dominating systematic uncertainties.
-
+\diego{Vale la pena introducir alguna comparacion sobre el campo magnetico????}
 %{Also, within the streamer belt the magnetic field strength is similar in both rotations in the northern hemisphere, while in the southern hemisphere CR-1915 exhibits $10-80\%$ larger values compared to CR-2081, with increasing difference for larger latitudes.
@@
 
-\temp{Aca vienen quizas 1 o 2 parrafos introduciendo y explicando los phi, los resultados de la Figura \ref{energia_demt} y un parrafo comentando esos resultados. Este parrafo va escrito por Ceci.}
+\diego{Aca vienen quizas 1 o 2 parrafos  explicando los resultados de la Figura \ref{energia_demt}. Este parrafo va escrito por Ceci.}
 

### 2019-12-13 lloveras_2020.tex
Version Dec-13-2019 20:51

@@
 \usepackage[utf8]{inputenc}
-\usepackage[dvipsnames]{xcolor}
 
@@
 \newcommand{\cm}{{\rm cm}}
+\newcommand{\cminvc}{\cm^{-3}}
+\newcommand{\cminvs}{\cm^{-2}}
 \newcommand{\sdev}{{\rm SD}}
@@
 \newcommand{\NCB}{N_{\rm CB}}
-\newcommand{\aTm}{\left<\Tm\right>}
 \newcommand{\Nqi}{N_{\rm QI}}
@@
 \newcommand{\Tm}{T_{\rm m}}
+\newcommand{\aTm}{\left<\Tm\right>}
 \newcommand{\Tmi}{T_{{\rm m},i}}
@@
 \newcommand{\Nsqmi}{N^2_{{\rm m},i}}
+\newcommand{\Nsqm}{N^2_{{\rm m}}}
 \newcommand{\rhoTr}{\rho(T,r)}
 \newcommand{\Tefit}{T_{e,{\rm fit}}}
-\newcommand{\sqravgN}{\sqrt{\Nsqmi}}
+\newcommand{\sqravgNi}{\sqrt{\Nsqmi}}
+\newcommand{\sqravgN}{\sqrt{\Nsqm}}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% temporales
-\definecolor{mygray}{gray}{0.6}
+%---------REMOVE THESE OPTIONS AND DEFs BEFORE SUMBISSION---------------------------------------
+\usepackage[usenames,dvipsnames]{xcolor} % Las opciones: [USENAMES,DVIPSNAMES] 
+                                         % ponen a disposición los colores ejemplificados aquí:
+                                         % https://en.wikibooks.org/wiki/LaTeX/Colors
+\def\diego#1{\textcolor{red}{#1}}
+\def\albert#1{\textcolor{blue}{#1}}
+\def\fede#1{\textcolor{ForestGreen}{#1}}
+\def\temp#1{\textcolor{gray}{#1}}
+\def\notebyalbert#1{\textcolor{blue}{NOTE: #1}}
+%-----------------------------------------------------------------------------------------------
 
-%---------REMOVE DEFs BEFORE SUMBISSION----------------
-\def\diego#1{\textcolor{red}{DIEGO: #1}}
-\def\albert#1{\textcolor{blue}{#1}}
-\def\fede#1{\textcolor{ForestGreen}{FEDE: #1}}
-\def\temp#1{\textcolor{mygray}{#1}}
-\def\edit#1{\textcolor{Apricot}{#1}}
-%------------------------------------------------------
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
@@
 
-\title{Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling}
+\title{Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling\\
+      \notebyalbert{\small Corregí filiación UNTREF, agregué segunda filiación para Fede (creo que no es preciso poner CBC, Fede?). Diego, ORCID IDs faltantes sacalos de {\tt orcid.org}}}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Authors Names
-%
-% \author[addressref={},corref,email={}]{\inits{}\fnm{}\lnm{}\orcid{}}
 \author[addressref={aff1},corref,email={dlloveras@iafe.uba.ar}]{\inits{D.G.}\fnm{Diego G.}~\lnm{Lloveras}\orcid{0000-0003-1402-0398}}
 
-\author[addressref={aff1,aff3},corref,email={albert@iafe.uba.ar}]{\inits{A.M.}\fnm{Alberto M.}~\lnm{V\'asquez}\orcid{0000-0003-3401-6409}}
+\author[addressref={aff1,aff2},corref,email={albert@iafe.uba.ar}]{\inits{A.M.}\fnm{Alberto M.}~\lnm{V\'asquez}\orcid{0000-0003-3401-6409}}
 
-\author[addressref={aff1},corref,email={federico@iafe.uba.ar}]{\inits{F.A.}\fnm{Federico A.}~\lnm{Nuevo}\orcid{0000-0003-2355-5853}}
+\author[addressref={aff1,aff3},corref,email={federico@iafe.uba.ar}]{\inits{F.A.}\fnm{Federico A.}~\lnm{Nuevo}\orcid{0000-0003-2355-5853}}
 
-\author[addressref={aff1,aff3},corref,email={cmaccormack@iafe.uba.ar}]{\inits{C.}\fnm{Cecilia}~\lnm{Mac Cormack}}
+\author[addressref={aff1,aff2},corref,email={cmaccormack@iafe.uba.ar}]{\inits{C.}\fnm{Cecilia}~\lnm{Mac Cormack}\orcid{0000-0003-1173-503X}}
 
@@
 
-%\address[id=aff2]{Departamento de F\'{\i}sica, Facultad de Ciencias Exactas y Naturales (FCEN), Universidad de Buenos Aires (UBA), Pabell\'on I, Ciudad Universitaria, (C1428ZAA) Ciudad Aut\'onoma de Buenos Aires, Argentina}
+\address[id=aff2]{Universidad Nacional de Tres de Febrero (UNTREF), Valent\'{\i}n G\'omez 4752, (B1678ABH) Caseros, Provincia de Buenos Aires, Argentina}
 
-\address[id=aff3]{Departamento de Ciencia y Tecnolog\'{\i}a, Universidad Nacional de Tres de Febrero (UNTREF), Valent\'{\i}n G\'omez 4752, (B1678ABH) Caseros, Provincia de Buenos Aires, Argentina}
+\address[id=aff3]{Facultad de Ciencias Exactas y Naturales (FCEN), Universidad de Buenos Aires (UBA), Pabell\'on II, Ciudad Universitaria, (C1428ZAA) Ciudad Aut\'onoma de Buenos Aires, Argentina}
 
 \address[id=aff4]{Department of Climate and Space Sciences and Engineering (CLaSP), University of Michigan, 2455 Hayward Street, Ann Arbor, MI 48109-2143, USA}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% Abstract 
+
 \begin{abstract}
-Observational \albert{techniques} play an essential role in advancing our understanding of the physics of the solar corona.
-They provide validation data to improve three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, \albert{enhancing} their space weather forecasting capabilities.
-Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of some \albert{of the fundamental} plasma parameters of the solar corona at a global scale.
+Observational {techniques} play an essential role in advancing our understanding of the physics of the solar corona.
+They provide validation data \albert{for} three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, \albert{key to improve} their space weather forecasting capabilities.
+Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale.
 Based on EUV data of space borne instruments, SRT allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun.
-We carry out a study of the corona combining tomographic reconstructions with MHD simulations \albert{using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF).
+We carry out a study of the corona combining tomographic reconstructions with MHD simulations {using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF).
 Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24.
@@
 We study magnetically closed structures associated with the equatorial streamer belt, as well as magnetically open regions enclosing it.
-We report on the tomographic results in the different structures, their implications for the physics of the solar corona, and the capability of the AWSoM model to reproduce the tomographic reconstructions in different regions.
+We report on the tomographic results in the different structures, their implications for the physics of the solar corona, and the \albert{current} capability of the AWSoM model to reproduce the tomographic reconstructions in different regions.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Keywords
-%
 \keywords{Solar Cycle, Observations; Corona,E; Corona, Structures}
@@
 \end{opening}
-%-------------------------------------------------
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Sections
 \section{Introduction}\label{intro}
@@
 
+\noindent\notebyalbert{Here we will put in a couple of paragraphs summarizing what SRT and DEMT are, including references and defining the accronyms in the process.
+We should refer to minima in particular.
+We should mention the instruments and missions we use as data for DEMT, and define their accronyms too.
+Also, a couple of paragraphs on the AWSoM model and the SWMF, including references and defining the accronyms in the process.}
+
 \section{Methodology}\label{meto}
@@
 \subsection{DEMT reconstructions}\label{demt}
-\temp{* Procesado de imagenes}\\
-\temp{* FBE}\\
-\temp{* LDEM}\\
-*Paso 1: obtencion de FBE\\
-*Paso 2: obtencion LDEM
+
+\noindent\notebyalbert{This section will summarize DEMT's main aspects and equations, only those needed to understand the paper.
+Nothing not needed to read this paper is provided.
+Also, no derivation of equations are provided.
+References are given so that the reader can dig deeper if so desires.
+Points to cover are:
+\begin{itemize}
+  \item Selected targets, instruments used. One paragraph.
+  \item Characteristics of the data (specific time series, dates, bands, etc.), SolarSoft software version used for their processing. One paragraph.
+  \item Technical aspects of DEMT (grid, regularization, off-limb data is only used) and how these differ from previous versions (rereferences). One paragraph.
+  \item What is FBE, what is LDEM, what is R.
+Why we care about these three quantities and what is their physical meaning should be clear.
+Then the final products $\Nm$ and $\Tm$, and what is their physical meaning.
+\end{itemize}
+}
+
 \begin{equation}\label{fbeldem}
@@
 
-\albert{
+{
 \begin{eqnarray}\label{momento1}
@@
 
-\albert{We define next a measure of the average relative difference between the tomographic and the synthetic FBE in each voxel, as}
+{We define next a measure of the average relative difference between the tomographic and the synthetic FBE in each voxel, as}
 
@@
 
-so that the final product of DEMT is in the form of 3D maps of the electron density and mean temperature.
-These relationships \albert{were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
-\temp{* Aclarar que consideramos Ne como $\sqrt{<\Ne ^2>}$.} \albert{ALBERT: Yo creo que es mejor simplemente hablar de $\sqravgN$}\\
-\temp{* Mejoras de la DEMT con respecto a trabajos previos}.
+so that the final product of DEMT is in the form of 3D maps of the electron density and mean temperature. These relationships {were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
+\temp{Aclarar que consideramos Ne como $\sqrt{<\Ne ^2>}$.} {ALBERT: Yo creo que es mejor hablar de $\sqravgN$}
 
 \temp{DEMT has been improved since the previously published work.
-We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.}
+We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.} \albert{NOTA de Albert: Explicá que hacés sin justificarte.
+Luego aclará como se hizo eso en trabajos previos, y cual es el impacto esperado.
+Puedo proveer un párrafo de ejemplo, pero creo que será mejor que vos escribas como te salga y yo luego edito.
+Algo muy importante para todo el paper: proponete escribir ``párrafos modulares".
+Es decir que, con las razonables limitaciones, puedan moverse de lugar, de orden, y sigan funcionando.
+No definiría hollow-tomography, es un término coloquial interno nuestro.
+Lo correcto es que al hablar de datos mucho más arribas expliques que los datos del disco no se utilizan, pero no le des un nombre a la tomografía.}
 
 \subsection{AWSoM simulations}\label{awsom}
-\temp{* Qué es, qué modela, qué datos usa, y qué se obtiene en general y en particular para este trabajo}\\
-\temp{* Se debe aclarar que solo produce resultados razonables arriba de 1.065}\\
-\temp{No pondría los mapas de 1.025 y diria algo asi como:}\\
-In the transition region \albert{(TR)}, the plasma heats up and becomes less dense \albert{by} several orders of magnitude \albert{over} a short distance.
-Modeling this region \albert{realistically has a very high computational cost}.
-For this \albert{reason,} the model uses \albert{an artificially} extended \albert{TR about $\approx 0.05\,\mrsun$ thick, as well as artificially large values for the electronic density and temperature as boundary conditions in $r=1\,\mrsun$.} Consequently, model results below \albert{$\approx 1.05\,\mrsun$} were not taken into account in this article.
 
-\subsection{Tracing results along fieldlines}\label{trace}
+\noindent\notebyalbert{This section will summarize the AWSoM model. After a first version is written we will surely require some input from the Michigan friends. Points to cover:
+\begin{itemize}
+  \item Data input. Link with the data input for DEMT in terms of dates, etc. One paragraph.
+  \item Main physical and technical aspects (grid in particular) of the model.  One paragraph. 
+  \item Explain the artificially extended TR. One paragraph.
+  \item What are the products of the model we care about in this paper. One paragraph.
+\end{itemize}
+}
 
-\diego{Falta explicar que todos los resultados pasamos a tenerlos en la grilla demt, y que en esa grilla se traza el campo.}
+In the transition region {(TR)}, the plasma heats up and becomes less dense {by} several orders of magnitude {over} a short distance.
+Modeling this region {realistically has a very high computational cost}.
+For this {reason,} the model uses {an artificially} extended {TR about $\approx 0.05\,\mrsun$ thick, as well as artificially large values for the electronic density and temperature as boundary conditions in $r=1\,\mrsun$.} Consequently, model results below {$\approx 1.05\,\mrsun$} were not taken into account in this article.
+
+\subsection{Tracing of results along fieldlines}\label{trace}
+
+\noindent\notebyalbert{This section will explain how the AWSoM magnetic model is used to trace the thermodynamic products of both DEMT and AWSoM along the fieldlines of AWSoM.
+This requires covering the following points:
+\begin{itemize}
+  \item A first paragraph qualitatively describing the process. This includes mentioning that the AWSoM products are first interpolated into the DEMT grid.
+  \item A short paragraph describing the numerical method used to trace field lines.
+We have a nice version of this in your previous paper.
+At this point the reader should understand that for each field line we have its geometry $\mathbf{r}(s)$ as a function of the distance $s$ along the loop, with $s(1\,\mrsun)\equiv 0$.
+  \item Explain very simply how then that for each voxel the middle point of the field line is selected and assigned the DEMT and AWSoM products of that cell.
+At this point the reader should understand that for each field line we have: $Q[r(s)]$, where $Q$ is any given quantity from either the DEMT model (specifically $\sqravgN$ and $\Tm$) or the AWSoM model (specifically $\Ne$ and $\Te$).
+  \item Explain fits to the DEMT results  $\sqravgN(r)$, $\Tm(r)$.
+  \item Explain then the classification of field lines.
+\end{itemize}
+}
 
@@
 
-For each open field line, and for each leg of the closed ones, an exponential fit was then applied to the $\Ne(r)$ data points, and a linear fit applied to the $\Tm(r)$ data points, as described by
+For each open field line, and for each leg of the closed ones, an exponential fit was then applied to \albert{the $\sqravgN(r)$ data points, and a linear fit applied to the $\Tm(r)$ data points}, as described by
 
+\albert{
 \begin{eqnarray}\label{Nfit}
-\Ne &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]}\\
+\sqravgN &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]}\\
 \label{Tfit}
-\albert{\Tm} &=& \albert{\dr \Tm(r) \ r\,+\,T_0}
+\Tm &=& T_0\,+\,m\,h
 \end{eqnarray}
-
 \noindent
-\albert{where $\l$ is the electron density scale height, $h \equiv r - 1\,\mrsun$ is the coronal height measured from the photosphere, $\dr\equiv\er\cdot\nabla$ is the radial derivative operator (being $\er$ the heliocentric radial unit vector), and $T_0$ and $N_0$ are constants.}
+where $h \equiv r - 1\,\mrsun$ is the coronal height measured from the photosphere.
+In the electron density fit, $\l\,[\mrsun]$ is the density scale height and $N_0\,[\cminvc]$ is the electron density at the footpoint ($h=0$) of the loop.
+In the electron temperature fit, $m\,[\MK/\mrsun]$ is the slope and $T_0\,[\MK]$ is the electron temperature at the footpoint of the loop.
+The slope $m$ is the radial gradient of the electron temperature along the loop, which we denote as $m = \dr\Tm$ hereafter, being $\dr\equiv\er\cdot\nabla$ the radial derivative operator, where $\er$ is the heliocentric radial unit vector.}
 
 In the case of the electron density, the fitted function corresponds to the isothermal hydrostatic equilibrium solution, allowing for variation of the solar gravitational acceleration with height.
-After computing the footpoint ($r=1.0\,\mrsun$) electron density $N_{0}\,[\cm^{-3}]$ and scale height $\lN\,[\mrsun]$\temp{, this choice of function provides a straightforward means to directly evaluate how compatible is the observed coronal thermodynamical state with the hydrostatic solution}.
+This choice of function provides a straightforward means to directly evaluate how compatible is the observed coronal thermodynamical state with the hydrostatic solution.
 
@@
 In the present work we focus on lines with increasing and decreasing temperatures in linear form.
-In other words, we selected those legs where the \albert{Pearson correlation coefficient $\rho$ between temperature $T$ and radius $r$ meets $|\rhoTr| > 0.5$}.
+In other words, we selected those legs where the {Pearson correlation coefficient $\rho$ between temperature $T$ and radius $r$ meets $|\rhoTr| > 0.5$}.
 \temp{(with p-value less than 0.05)}.
@@
 \item 
-The \albert{value of the Pearson correlation coefficient meets $|\rhoTr| > 0.5$.}
+The {value of the Pearson correlation coefficient meets $|\rhoTr| > 0.5$.}
 
@@
 \end{itemize}
-\diego{Hice las definiciones con gradiente de temperatura para que quede mas claro, pero en realidad uso el pearson.}
+\diego{Hice las definiciones con gradiente de temperatura para que quede mas claro, pero en realidad uso el pearson.} \notebyalbert{Charlemos los tres en persona de esto.}
 
-\subsection{Energy flux ?}\label{energia} 
-\temp{Aca se introduce la seccion de energia con sus ecuaciones etc}
-\diego{sugerencias para el nombre?}
+\subsection{\albert{Energy input flux}}\label{energia}
+
+\noindent\notebyalbert{This section will summarize how loop integrated energy quantities are computed from the DEMT products and the AWSoM magetic model alone.
+The summary will not include any derivation and will refer to Cecilia's paper.
+Only the results that are relevant are to be explicited.
+Start by explaining the model and assumptions, and end up summarizing the loop-integrated products (radiative and conductive fluxes).
+At the end the reader should understand that their sum is the enery input flux required at the coronal base to maintain the loop stable.
+This should be a very short section, as it is a summary of one previous paper alone.}
 
@@
 \subsection{Tomographic Results}\label{demt_res}
+
+\noindent\notebyalbert{This section will show first the DEMT products in the form of Carrington maps at three heights, for the two target rotations.
+It will then show the latitude/longitude location of the four types of  magnetic loops (defined in Section 2.3) at a sample height.
+Then, for the each type of loop, we will show histograms of the values of different DEMT products traced along them, charerizing in a quantitative fashion the DEMT results in distinct magnetic structures.
+It will also include a quantitative comparison between the two target rotations of the median values of the DEMT products in each type of loop.}
 
@@
 \includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
-\caption{Carrington maps of DEMT results: $\Ne$ (left panels) and $\Tm$ (right panels) for CR-2082.
+\caption{Carrington maps of DEMT \albert{products $\sqravgN$} (left panels) and $\Tm$ (right panels) for CR-2082.
 Top, middle and bottom panels show the results at three heliocentric heights, $1.025$, $1.065$ and $1.105\,\mrsun$ respectively.
@@
 
- As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $\dr \Tm$, and the height-averaged (along the loop) electron mean temperature $\aTm$.
+As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $\dr \Tm$, and the height-averaged (along the loop) \albert{electron temperature} $\aTm$.
 As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height may be used to compute the tomographic basal electron density at $ \Ne(r=1.025\,\mrsun)$ as in previous articles.
@@
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
-\caption{Latitude-longitude location of each leg of type 0 (in cyan), type I (in blue), type II (in red) and type III (in green) at $1.105\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).
-See Section \ref{trace} for a definition of the different types of legs.}
+\caption{Latitude-longitude location of each leg of \albert{loops of type 0 (cyan), I (blue), II (red) and III (green)} at $1.105\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).
+See Section \ref{trace} for a definition of the different types of \albert{loops}.
+\notebyalbert{(by ALBERT) This Figure is great, but I do not quite like the choice of colors.
+I suggest these changes: cyan$\rightarrow$blue, blue$\rightarrow$red, red$\rightarrow$violet.
+In this way, blue will be DOWN loops and red will be UP loops, as in previous papers.
+The same change applies to Figure 4.
+Also, how about making Figures 3 and 4 a single Figure of four panels?
+Just an idea.}}
 \label{rpoint_demt}
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_fulltriple_gradt.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
-\caption{Frequency histograms of the temperature radial gradient for the different types of legs shown in Figure \ref{rpoint_demt} (same colour code) for CR-2082 (left panel) and CR-2208 (right panel).}
+\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2082_fulltriple_gradt.eps}
+\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
+\caption{Frequency histograms of the temperature radial gradient for the different \albert{four types of loops} shown in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
 \label{gradt_demt}
@@
 From top to bottom type 0 to type 4.
-From left to right the panels show the statistical distribution of $\NCB$, $\lN$, $\aTm$, in each panel the median $m$ is indicated.
+From left to right the panels show the statistical distribution of \albert{$\NCB\equiv\sqravgN(r=1.055\,\mrsun)$}, $\lN$, $\aTm$, in each panel the median $m$ is indicated.
 
@@
 \begin{center}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
-\caption{Comparative statistical distributions of DEMT reults.
-From left to right: the coronal base electron density $\Ne(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all types of legs defined in Section \ref{trace}.
-Results of CR2082 are shown in blue while those of CR-2208 in red.
-In each panel the median $m$ is indicated.}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
+\caption{\albert{Statistical distribution of DEMT results traced along the type of loops 0, I, II and III (from top to bottom), as defined in Section \ref{trace}.
+From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$.
+Results for target rotations CR2082 and CR2208 are shown in blue and red color, respectively.
+In each panel the median value $m$ is indicated.} \notebyalbert{The histogram Figures in this draft need to be improved, in particular font size-and-type need to be optimized for a clear reading.}}
 \label{histos_fulldemt}
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
-\caption{Statistical results of the loop integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colours blu, red and green, respectively for CR-2082 (left) and CR-2208 (right).
+\caption{Statistical results of the loop integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blu, red and green, respectively for CR-2082 (left) and CR-2208 (right).
 From top to left the type 0, 1 and 2 field of lines defined in Section \ref{trace}.
-}
+\notebyalbert{Utilizar los colores del paper de Cecilia, notar que el conductivo debe ser el verde y el energy input flux (h) debe ser el rojo.
+De paso, haría el verde un poco menos chillón, como en el paper de Ceci, se verá mejor.
+En el XYOUTS podés poner la letra griega $\phi$,  y para que te salga r,c,h como subíndice pero no pequeño usá: ``!Dp!N", donde p=r,c,h.}}
 \label{energia_demt}
@@
 \begin{center}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
 \caption{Comparative statistical distributions for CR-2082 between DEMT (blue) and AWSoM (red).
@@
 \begin{center}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_Tm.eps}\\
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_Tm.eps}\\
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_Tm.eps}\\
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_Tm.eps}\\
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_Tm.eps}
 \caption{Same as Figure \ref{histos_2082} for CR-2208.}

### 2019-12-14 lloveras_2020.tex
Edited by Albert 13/Dec/2019 - 23:28 hs.

@@
 
-As a way of knowing the physical position of the types of lines defined in Section \ref{trace}, the Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations.
+\albert{En las discusiones usás type 1, 2 y 3, pero son I, II y III.} As a way of knowing the physical position of the types of lines defined in Section \ref{trace}, the Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations.
 In cyan the type 0 lines are indicated, populating the most equatorial latitudes (dominated mostly by down loops).
@@
 See Section \ref{trace} for a definition of the different types of \albert{loops}.
-\notebyalbert{(by ALBERT) This Figure is great, but I do not quite like the choice of colors.
+\notebyalbert{(by ALBERT) The population of DOWN loops in CR-2008 is negligible.
+These are VERY SMALL loops, I am pretty sure but you and Ceci shoudl check it.}  \notebyalbert{(by ALBERT) This Figure is great, but I do not quite like the choice of colors.
 I suggest these changes: cyan$\rightarrow$blue, blue$\rightarrow$red, red$\rightarrow$violet.
@@
 Also, how about making Figures 3 and 4 a single Figure of four panels?
-Just an idea.}}
+Just an idea.} }
 \label{rpoint_demt}
@@
 \includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
-\caption{\albert{Statistical distribution of DEMT results traced along the type of loops 0, I, II and III (from top to bottom), as defined in Section \ref{trace}.
+\caption{\albert{Statistical distribution of DEMT results traced along loops of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}.
 From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$.
 Results for target rotations CR2082 and CR2208 are shown in blue and red color, respectively.
-In each panel the median value $m$ is indicated.} \notebyalbert{The histogram Figures in this draft need to be improved, in particular font size-and-type need to be optimized for a clear reading.}}
+In each panel the median value $m$ is indicated.} \notebyalbert{The histogram Figures in this draft need to be improved, in particular font size-and-type need to be optimized for clear reading.
+Also, we need to improve their X/Y ratio, here I stretched the Y size a bit in the LaTeX source.}}
 \label{histos_fulldemt}
@@
 From top to left the type 0, 1 and 2 field of lines defined in Section \ref{trace}.
-\notebyalbert{Utilizar los colores del paper de Cecilia, notar que el conductivo debe ser el verde y el energy input flux (h) debe ser el rojo.
+\notebyalbert{The type-0 population in CR-22208 is negligible.
+These are VERY SMALL loops, I am pretty sure but you and Ceci shoudl check it.
+This can explain the non-physical $\phi_h<0$ population.} \notebyalbert{Utilizar los colores del paper de Cecilia, notar que el conductivo debe ser el verde y el energy input flux (h) debe ser el rojo.
 De paso, haría el verde un poco menos chillón, como en el paper de Ceci, se verá mejor.
@@
 
-\temp{Parrafo introductorio?}
+\noindent\notebyalbert{This section will show the results of AWSoM for $N_e$ and $T_e$, and how they compare with the corresponding results of DEMT ($\sqravgN$ and $\Tm$).
+It will first show the Carrington maps of $N_e$ and $T_e$ at the same three heights we showed the same maps for the DEMT results.
+Then it will show the lat/lon location of loops of type I, II and III at a middle height, just loke for DEMT results.
+As the two targets are highly axis-symmetric, a first quantitative comparison between AWSoM and DEMT will be shown as longitude-averaged latitudinal profiles of the results of both models at a sample height.
+To make comparisons in distinct magnetic structures, we will also show the average radial dependence of results for loops of type I, II and III, overplotting the AWSoM and the DEMT results.
+For the tree types of loops we will show histograms of the DEMT and AWSoM products along field lines.
+This is a LOT of information from which and we need to pull out a few clear conlcusions.}
 
-As an example of the AWSoM results, Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} shows the latitude-longitude maps for $\Ne$ and $T_e$ modeled for CR-2082 and CR-2208 at $r=1.025, 1.065$ and $1.105\,\mrsun$.
+As an example of the AWSoM results, Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} shows the latitude-longitude maps for $\Ne$ and $T_e$ modeled for CR-2082 and CR-2208 at $r=1.025$, $1.065$ and $1.105\,\mrsun$.
 The black curve denotes the open-close boundary.
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.eps}
-\caption{Same as Figure \ref{rpoint_demt}, using the density and temperature of AWSoM model to classify legs in type 1, 2 and 3.}
+\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify \albert{its loops in types I, II and III. The model does not exhibit loops of type 0.}}
 \label{rpoint_awsom}
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105.eps}
-\caption{Longitude-averaged electron density (top) and temperature (bottom) for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$.
+\caption{Longitude-averaged latitudinal dependence of the electron density (top) and temperature (bottom) for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$.
 The left (right) panels correspond to CR-2082 (CR2208).
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_short.eps}
-\caption{Average fits of $\Ne(r)$ and $T_e(r)$ for legs of type I (blue), type II (red) and type III (green) for CR-2082 (top panel) and CR-2208 (bottom panel) using DEMT (solid) and AWSoM (dashed) results.}
+\caption{\albert{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (blue), II (red), and III (green), for CR-2082 (top panel) and CR-2208 (bottom panel).
+Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
 \label{perfiles_promedio}
@@
 \includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
-\caption{Comparative statistical distributions for CR-2082 between DEMT (blue) and AWSoM (red).
-From left to right: the coronal base electron density $\Ne(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average $\aTm$ along the four types of legs considered in Section \ref{trace}.
-In each panel the median ($m$) is indicated.}
+\caption{\albert{Statistical distribution of DEMT (blue) and AWSoM (red) results traced along loops of type I, II and III (from top to bottom), as defined in Section 2.3.
+From left to right: electron density at the coronal base $\NCB\equiv \Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$.
+In each panel the median value $m$ is indicated.}}
 \label{histos_2082}
@@
 \caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
-FDEMT values are expressed in absolute terms, while for AWSoM they are informed as a percentual variation relative to the DEMT value.}
+DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
 \label{tabla_comp}
@@
 The heliocentric current sheet (HCS) location is indicated by the minimum of the speed curve.\\
-\diego{can we say something without having traced the lines?}
+\diego{can we say something without having traced the lines?} \notebyalbert{(by ALBERT) Todo el punto de la última Figura es precisamente decir algo.
+La comparación con la Figura 10 muestra una anti-correlación entre la densidad basal de DEMT y la velocidad terminal de AWSoM.}
 
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
-\caption{Longitude-averaged of radial wind speed at $6\,\mrsun$ given by AWSoM for both rotations.}
+\caption{\albert{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).}}
 \label{perf_lon_vr}
@@
 \section{Discussion}\label{discu}
+
+\noindent\notebyalbert{Antes de enviar esto a Michigan se precisa un conjunto de conclusiones compacto y claro.
+Creo que yo las pondría en tres grupos: a) conclusiones DEMT solas (esto incluye estructura termodinámica, up/down loops, energía), b) comparación AWSoM/DEMT (la clobal, es decir promedio longitudinal, y la que difernecia estructuras magnéticas), c) Wind Speed y Densidad basal.}
 

### 2019-12-16 lloveras_2020.tex
Mergeo de Diego + comentarios albert + cosas de fede + energi a de ceci, cosas varias.

@@
 
-\title{Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling\\
-      \notebyalbert{\small Corregí filiación UNTREF, agregué segunda filiación para Fede (creo que no es preciso poner CBC, Fede?). Diego, ORCID IDs faltantes sacalos de {\tt orcid.org}}}
+\title{Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling}
 
@@
 
-\author[addressref={aff4},corref,email={nishthas@umich.edu}]{\inits{N.}\fnm{Nishtha}~\lnm{Sachdeva}\orcid{1}}
+\author[addressref={aff4},corref,email={nishthas@umich.edu}]{\inits{N.}\fnm{Nishtha}~\lnm{Sachdeva}\orcid{0000-0001-9114-6133}}
 
-\author[addressref={aff4},corref,email={chipm@umich.edu}]{\inits{W.}\fnm{Ward}~\lnm{Manchester IV}\orcid{2}}
+\author[addressref={aff4},corref,email={chipm@umich.edu}]{\inits{W.}\fnm{Ward}~\lnm{Manchester IV}\orcid{0000-0003-0472-9408}}
 
-\author[addressref={aff4},corref,email={bartvand@umich.edu}]{\inits{B.}\fnm{Bartholomeus}~\lnm{Van der Holst}\orcid{3}}
+\author[addressref={aff4},corref,email={bartvand@umich.edu}]{\inits{B.}\fnm{Bartholomeus}~\lnm{Van der Holst}\orcid{0000-0001-5260-3944}}
 
@@
 Observational {techniques} play an essential role in advancing our understanding of the physics of the solar corona.
-They provide validation data \albert{for} three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, \albert{key to improve} their space weather forecasting capabilities.
+They provide validation data {for} three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, {key to improve} their space weather forecasting capabilities.
 Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale.
@@
 We study magnetically closed structures associated with the equatorial streamer belt, as well as magnetically open regions enclosing it.
-We report on the tomographic results in the different structures, their implications for the physics of the solar corona, and the \albert{current} capability of the AWSoM model to reproduce the tomographic reconstructions in different regions.
+We report on the tomographic results in the different structures, their implications for the physics of the solar corona, and the {current} capability of the AWSoM model to reproduce the tomographic reconstructions in different regions.
 
@@
 
-For each open field line, and for each leg of the closed ones, an exponential fit was then applied to \albert{the $\sqravgN(r)$ data points, and a linear fit applied to the $\Tm(r)$ data points}, as described by
+For each open field line, and for each leg of the closed ones, an exponential fit was then applied to {the $\sqravgN(r)$ data points, and a linear fit applied to the $\Tm(r)$ data points}, as described by
 
-\albert{
 \begin{eqnarray}\label{Nfit}
@@
 In the electron temperature fit, $m\,[\MK/\mrsun]$ is the slope and $T_0\,[\MK]$ is the electron temperature at the footpoint of the loop.
-The slope $m$ is the radial gradient of the electron temperature along the loop, which we denote as $m = \dr\Tm$ hereafter, being $\dr\equiv\er\cdot\nabla$ the radial derivative operator, where $\er$ is the heliocentric radial unit vector.}
+The slope $m$ is the radial gradient of the electron temperature along the loop, which we denote as $m = \dr\Tm$ hereafter, being $\dr\equiv\er\cdot\nabla$ the radial derivative operator, where $\er$ is the heliocentric radial unit vector.
 
@@
 To measure how good the quality of the exponential fit to the electron density and the linear fit to the temperature data are, a chi-square merit function was used (see Section 15.2 \citet{recipes}).
-The errors were estimated in \citet{lloveras_2017}, $0.07$ MK for $\Tm$ and $0.04\,10^8 cm^{-3}$ for $\Ne$ and legs with p-value $>0.005$ were rejected.
+The errors were estimated in \citet{lloveras_2017}, $0.07$ MK for $\Tm$ and $4.0\,10^6 cm^{-3}$ for $\Ne$ and legs with p-value $>0.005$ were rejected.
 
@@
 
-To be selected a loop must meet all following conditions.
+{To be selected a leg must meet all following conditions.}
 
@@
 \item 
-Each leg of the loop must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the loop.
+The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg.
 
@@
 
-For the two targeted rotations, DEMT and AWSoM resuls were traced along the AWSoM field lines, which provides a way to characterize the global thermodynamic state of the inner solar corona and to compare them.
-To that end four different types of legs corresponding with four different types of magnetic structures where selected:
+For the two targeted rotations, DEMT and AWSoM results were traced along the AWSoM field lines, which provides a way to characterize the global thermodynamic state of the inner solar corona and to compare them.
+To that end four different types of {legs} corresponding with four different types of magnetic structures were selected:
 %\temp{Hacer explicacion de los tipos de lineas bien secos, luego en fig 3 hacer notar que implica cada una en cuanto a estructura magnetica}\\
@@
 
-\subsection{\albert{Energy input flux}}\label{energia}
+\subsection{{Energy input flux}}\label{energia}
 
@@
 This should be a very short section, as it is a summary of one previous paper alone.}
+
+Due the difference between temperatures of transition region and solar corona, there must to be a heating mechanism that compensate all the losses present in the atmosphere and maintain stable the plasma temperature.
+Previous works have studied this mechanism by observations and modeling, but mostly for active regions.
+\citet{maccormack_2017} have developed a technique that estimate the heating injected into the loops during a period of minima activity.
+Using DEMT combined with an extrapolation of magnetic field, as we detailed before, they obtain the different plasma parameters along each magnetic loop, and therefore, compute the energy input flux required to maintain them stable.
+The model assume a simple energy balance for each magnetic flux tube, where the losses by radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated by some coronal heating power($E_h$) \citep{aschwanden_2004}:
+
+\begin{equation}\label{Balance}
+E_h(s) = E_r(s)+ E_c(s),
+\end{equation}
+
+\noindent
+where $s$ is the position along each magnetic flux tube and the powers are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.
+
+Thermal conduction power is calculated by the Spitzer model \citep{spitzer_1962}, which describes coronal plasma regime properly.
+The thermal conduction power is obtained by taking the divergence of the conductive loss function $F_c(s)=-\kappa_0\,{T(s)}^{5/2}\,\frac{dT}{ds}(s)$, where $\kappa_0 = 9.2 \times 10^{-7}  {\rm erg\,sec^{-1}\,K^{-7/2}}$ is the Spitzer thermal conductivity.
+Due in coronal regime, the plasma is confined to the magnetic field, thus conduction is also predominately in the magnetic field direction.
+Thus, divergence is only the derivative along the position $s$:
+
+\begin{equation}\label{Ec}
+E_c(s)=\frac{1}{A(s)}\,\frac{d}{ds}\left[A(s)\,F_c(s)\right].
+\end{equation}
+
+\noindent
+where $A(s)$ represent the magnetic flux tube area along the position $s$.
+
+Radiative power depends on the amount of plasma in certain temperatures that can radiate.
+The model estimate it by integrating the squared density multiplied by a radiative loss function $\Lambda(T)$.
+This function depends on plasma temperature and is calculated by the atomic database and the plasma emission model from CHIANTI \citep{delzanna_2015}.
+Then, the expression for radiative power obtained is:
+
+\begin{equation}\label{Er}
+E_r = \int\,\Lambda(T)\,dN_e^2(T).
+\end{equation}
+
+Taking into acount the null divergence condition of magnetic field, the model integrate, between tomographic limits, each power quantities over magnetic flux tube independently of its area.
+Therefore, a loop-integrated equation for the energy flux balance is obtained ($[\rm{erg\,sec^{-1}\,cm^{-2}}]$):
+
+\begin{equation}\label{FluxBalance}
+\phi_h = \phi_r + \phi_c.
+\end{equation}
+
+\noindent
+where $\phi_{h,r,c}$ are the loop-integrated energy input flux, radiative flux and conductive flux for each magnetic field line at 1.025 $R_{\odot}$.
+
+For a complete description of the energy balance model, the reader can refer to \citet{maccormack_2017}.
+We compute the loop-integrated energy quantities for both rotation analyzed in this work. 
+\\
 
@@
 
-Once the LDEM was determined for each rotation, the electron density $\Ne$ and electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}.
-As an example, Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} shows the latitude-longitude maps for both tomographic results for CR-2082 and CR-2208 at $r=1.025, 1.065$ and $1.105\,\mrsun$.
+{To perform a comparative study of the thermodynamic structure of the inner corona in different solar cycles
+we carry out a DEMT reconstruction for two rotations: CR-2082, using STEREO/EUVI data and CR-2208, using SDO/AIA data.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared $\sqravgN$ and the electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}.} As an example, Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show the latitude-longitude maps of DEMT results for both rotations at {three different heights of interest.
+The lowest height where the tomography gives results, the lowest height where the AWSoM model results are reliable and a representative average height were selected, that is $r=$1.025, 1.065 and 1.105, $\mrsun$ respectively}.
 Black voxels correspond to non-reconstructed voxels (explained in Section \ref{demt}).
-Thick-black curves indicate the open/closed boundaries based on the AWSoM model.
+Thick-black curve indicates the magnetic open/closed boundary based on the magnetic field of AWSoM model.
 
@@
 \includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
-\caption{Carrington maps of DEMT \albert{products $\sqravgN$} (left panels) and $\Tm$ (right panels) for CR-2082.
+\caption{Carrington maps of DEMT {products $\sqravgN$} (left panels) and $\Tm$ (right panels) for CR-2082.
 Top, middle and bottom panels show the results at three heliocentric heights, $1.025$, $1.065$ and $1.105\,\mrsun$ respectively.
@@
 
-For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected.
+{To study the variation of the DEMT results in different magnetic structures we traced $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.} For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected.
 For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.
@@
 
-As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $\dr \Tm$, and the height-averaged (along the loop) \albert{electron temperature} $\aTm$.
-As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height may be used to compute the tomographic basal electron density at $ \Ne(r=1.025\,\mrsun)$ as in previous articles.
-In this case, for further comparison analysis with the AWSoM results, we selected the lowest height where the results of the MHD model are reliable, that is $1,065\,\mrsun$.
+As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr \Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.
+As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height may be used to compute the tomographic basal electron density at $\sqravgN(r=1.025\,\mrsun)$ as in previous articles.
+In this case, for further comparison analysis with the AWSoM results, we selected the lowest height where the results of the MHD model are reliable, that is $1,055\,\mrsun$.
 
@@
 
-\albert{En las discusiones usás type 1, 2 y 3, pero son I, II y III.} As a way of knowing the physical position of the types of lines defined in Section \ref{trace}, the Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations.
+As a way of knowing the physical position of the types of lines defined in Section \ref{trace}, the Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations.
 In cyan the type 0 lines are indicated, populating the most equatorial latitudes (dominated mostly by down loops).
-This kind of structures has been informed in previous works, \citet{lloveras_2017} observed down loops in a rotation during the solar minima of 1996 and for the previous rotation CR-2081.
-The amount of down loops in the equatorial latitudes.
+This kind of structures has been informed in previous works, \citet{lloveras_2017} observed down {loops} in a rotation during the solar minima of 1996 and for the previous rotation CR-2081.
 A decrease in the amount of down loops in equatorial latitudes could be an indicator of increased coronal activity \citet{nuevo_2013}.
@@
 
-Of the 45000 legs selected in 2082, 14\% are type 0, 38\% are type 1, 23\% are type 3 and 25\% type 4, on the other hand of the 59000 legs selected in 2208, 8\% are type 0, 43\% are type 1, 22\% are type 3 and 30\% type 4.
+Of the 45000 legs selected in 2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III, on the other hand of the 59000 legs selected in 2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.
 
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
 %\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
 %\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
-\caption{Latitude-longitude location of each leg of \albert{loops of type 0 (cyan), I (blue), II (red) and III (green)} at $1.105\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).
-See Section \ref{trace} for a definition of the different types of \albert{loops}.
-\notebyalbert{(by ALBERT) The population of DOWN loops in CR-2008 is negligible.
+\caption{Latitude-longitude location of each leg of type 0 (cyan), I (blue), II (red) and III (green) at $1.105\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).
+See Section \ref{trace} for a definition of the different types of {legs}.
+\notebyalbert{(by ALBERT) The population of DOWN LEGS in CR-2008 is negligible.
 These are VERY SMALL loops, I am pretty sure but you and Ceci shoudl check it.}  \notebyalbert{(by ALBERT) This Figure is great, but I do not quite like the choice of colors.
@@
 
-To compare the results obtained with the traced results in both rotations and for each type of lines (associated with differents types of regions), Figure \ref{gradt_demt} shows histograms (normalized to the total amount of the field lines selected) of the temperature radial gradients ($\dr \Tm$) for every type of line and for both rotations.
+To compare obtained traced results in both rotations and for each type of lines (associated with differents types of regions), Figure \ref{gradt_demt} shows histograms (normalized to the total amount of the field lines selected) of the temperature radial gradients ($\dr \Tm$).
 The lack of population around values close to zero is due to the strict condition $|\rho_t| > 0.5$ that discards possible isothermal values, according to DEMT results.
 
-Both rotations are characterized by lines of type 0 with mean values of $-2.5\, \rm MK/\mrsun$, mean values of $2.3\, \rm MK/\mrsun$ in type 1 and $2.4\, \rm MK/\mrsun$ in type 2.
-The only notable difference is the smaller number of type 0 lines in CR-2208 and the mean value of $4.5\, \rm MK/\mrsun$ in type 3 for CR-2208 which is twice that for the other rotation.
+Both rotations are characterized by lines of type 0 with mean values of $-2.5\, \rm MK/\mrsun$, mean values of $2.3\, \rm MK/\mrsun$ in type I and $2.4\, \rm MK/\mrsun$ in type II.
+The only notable difference is the smaller number of type 0 lines in CR-2208 and the mean value of $4.5\, \rm MK/\mrsun$ in type III for CR-2208 which is twice that for the other rotation.
 
-\temp{mostrar los gradientes negativos va a ser util en los parrafos posteriores que expliquen porque en las lineas tipo 0 hay valores de $\phi_c$ negativos.}
+%\temp{mostrar los gradientes negativos va a ser util en los parrafos posteriores que expliquen porque en las lineas tipo 0 hay valores de $\phi_c$ negativos.}
 
@@
 \includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
-\caption{Frequency histograms of the temperature radial gradient for the different \albert{four types of loops} shown in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
+\caption{Frequency histograms of the temperature radial gradient for the different {four types of legs} shown in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
 \label{gradt_demt}
@@
 
-\temp{este inicio de linea se repite del anterior}\\
 As an example of the traced magnitudes, Figure \ref{histos_fulldemt} shows the statistical results of both rotations for all field lines types.
-From top to bottom type 0 to type 4.
-From left to right the panels show the statistical distribution of \albert{$\NCB\equiv\sqravgN(r=1.055\,\mrsun)$}, $\lN$, $\aTm$, in each panel the median $m$ is indicated.
+From top to bottom type 0 to type III.
+From left to right the panels show the statistical distribution of $\NCB$, $\lN$, $\aTm$, in each panel the median $m$ is indicated.
 
@@
 \includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
-\caption{\albert{Statistical distribution of DEMT results traced along loops of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}.
+\caption{{Statistical distribution of DEMT results traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}.
 From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$.
@@
 \diego{si queda una asociacion directa entre los tipos de lineas y las estructuras de streamer, CH etc entonces usaria esos nombres a continuacion.}\\
-From the equatorial streamer of both rotations, increasing latitudes show decreasing \temp{coronal base (1.055)} density, and increasing density scale height and electron temperature.
+From the equatorial streamer of both rotations, increasing latitudes show decreasing {coronal base} density, and increasing density scale height and electron temperature.
 In both rotations the CH regions are characterized sub-MK temperatures, and coronal base densities of order $\approx 1/2$ of the equatorial streamer.
 Histograms with sharp populations indicates that for both rotations the values of all physical quantities exhibit a strong symmetry between both hemispheres.
-\diego{no se si decir sharp queda bien.}
 
-A comparison of the results between the two rotations shows that CR-2208 is characterized by lower values (between $11\%\, \rm and\, 16\%$) of electron density than CR-2082, higher values of density scale height (between $4\%\, \rm and\,19\%$) and higher values of electron temperature (between $6\%\, \rm and\,21\%$).
+A comparison of the results between the two rotations shows that CR-2208 is characterized by lower values (between $11\%\, \rm and\, 16\%$) of coronal base electron density than CR-2082, higher values of density scale height (between $4\%\, \rm and\,19\%$) and higher values of electron temperature (between $6\%\, \rm and\,21\%$).
 
 %To establish if the differences in the results between the two rotations are significant, Section \ref{uncertainties} estimates the error bars due the dominating systematic uncertainties.
-\diego{Vale la pena introducir alguna comparacion sobre el campo magnetico????}
+%\diego{quizas vale la pena introducir alguna comparacion sobre el campo magnetico, veremos como quedan los comentarios de ceci.}
 %{Also, within the streamer belt the magnetic field strength is similar in both rotations in the northern hemisphere, while in the southern hemisphere CR-1915 exhibits $10-80\%$ larger values compared to CR-2081, with increasing difference for larger latitudes.
@@
 
-\diego{Aca vienen quizas 1 o 2 parrafos  explicando los resultados de la Figura \ref{energia_demt}. Este parrafo va escrito por Ceci.}
+\diego{Comienza la energia}\\
 
-\begin{figure}[h!]
+%Previous works have found magnetic loops which temperature decrease with height, most generally in equatorial latitudes \citep{huang_2012,nuevo_2013}.
+This type of loops with negative gradients produce a negative conductive flux that contribute to the heating in the corona.
+In this work, we compute the loop-integrated energy quantities separately in three different populations of loops.
+
+To compare integrated quantities along loops, we select those close loops where both legs meet the requirements of Section \ref{trace}.
+In an analogous way to the legs definition, we will refer to them as loops of type 0, I or II.
+
+\begin{figure}[ht]
 \begin{center}
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
-\caption{Statistical results of the loop integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blu, red and green, respectively for CR-2082 (left) and CR-2208 (right).
-From top to left the type 0, 1 and 2 field of lines defined in Section \ref{trace}.
-\notebyalbert{The type-0 population in CR-22208 is negligible.
+\caption{\diego{Statistical results of the loop integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right).
+From top to left loops of type 0, I and II where both legs meets the criteria from Section \ref{trace}.} \notebyalbert{The type-0 population in CR-22208 is negligible.
 These are VERY SMALL loops, I am pretty sure but you and Ceci shoudl check it.
@@
 \end{figure}
+
+The frequency histograms of Figure \ref{energia_demt} shows the loops-integrated energy quantities: $\phi_h$, $\phi_r$ and $\phi_c$ in green, blue, and red lines respectively, for both rotations.
+
+The type I loops show a loop-integrated positive conductive for each loop in both rotations consistent with positive gradients of temperatures.
+\diego{We found larger temperature gradients for CR2208 than CR2082 (SI?)}, but for the most population of loops, the conductive flux have values around 0.3 $10^{5}[\rm{erg\,sec^{-1}\,cm^{-2}}]$ in both rotations.
+Similar results have been found for loop-integrated radiative flux and energy input flux for both rotations.
+
+Type 0 loops present larger gradients than type I.
+Therefore, type 0 present bigger amount, in modulus, of loop-integrated conductive flux.
+Due conductive flux negative can not be assumed as a loss but it can be contributing to the coronal heating.
+Thus, to compensate the radiative losses, a lower loop-integrated energy input flux is required.
+
+We can see, on type 0 loops, a median value of energy input flux for CR2082 twice bigger than CR2208.
+Also, in both rotations, we observe a negative population of loop integrated energy input flux.
+This can refer to some loops where loop-integrated radiative flux is too small in comparison with the larger gradients of negative conductive flux, resulting in negative energy input flux.
+
+\diego{No son los mismos colores que el paper de ceci, tmb quizas podriamos poner la cant de LOOPS y los valores medianos, ceci insiste.}
 
@@
 
-As an example of the AWSoM results, Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} shows the latitude-longitude maps for $\Ne$ and $T_e$ modeled for CR-2082 and CR-2208 at $r=1.025$, $1.065$ and $1.105\,\mrsun$.
-The black curve denotes the open-close boundary.
+The thermodynamic results of AWSoM are shown in Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208}.
+That is latitude-longitude maps for $\Ne$ and $\Te$ modeled for CR-2082 and CR-2208 at $r=1.025, 1.065$ and $1.105\,\mrsun$.
+The black curve denotes the same open-close boundary showed in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} respectively.
 
-A visual inspection of the AWSoM results shows that both reconstruction are very axysimmetric for $\Ne$ and $T_e$ as well.
+%$r=1.025, 1.065$ and $1.105\,\mrsun$. The black curve denotes the open-close boundary.
+
+A visual inspection of these maps shows that both reconstructions are very axysimmetric for $\Ne$ and $\Te$ as well.
 The closed region is denser and hotter than the open region.
@@
 CR-2208 shows a well reconstruction of the AR around latitude $+10\mdeg$ and longitude $300\mdeg$ and a slight temperature difference between the poles \temp{estoy asumiento que es una AR}.
-In both rotations the open-closed boundaries derived from the respective AWSoM model match the shape of the contour levels of the tomographic maps of both the electron density and the electron mean temperature.
+In both rotations the open-closed boundaries derived from the AWSoM model match the shape of the contour levels of both the electron density and the electron temperature.
+
+%\diego{comparacion visual entre estas dos figuras y als dos de DEMT.}
+
+The same intensity scales in both density and temperature can be observed between the tomographic results and those of AWSoM in both rotations, as well as the same thermodinamic structures.
+That is, equatorial latitudes, mid laditudes and the open regions.
 
@@
 
-Due to the inability of the model to reproduce down legs, in this section we only used lines type 1, 2 and 3 and only were selected those that meet the chi square hypothesis test.
-
-Figure \ref{rpoint_awsom} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations.
+The actual version of the AWSoM model can not reproduce down loops, so for a further comparison we only select lines of type 1, 2 and 3 of those meeting the criteria described in Section \ref{trace}.
+As a way to understand the distribution of the selected lines, Figure \ref{rpoint_awsom} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations.
 In blue the type 1 lines, populating mostly the entire streamer.
@@
 
-The fact that Figure \ref{rpoint_awsom} looks much fuller than Figure \ref{rpoint_demt} is because giving the model smoother results, fewer fitted lines are filtered.
-
-The reader may notice that these structures are the same as those in Figure \ref{rpoint_demt} but more filled, this is because the same magnetic result was used to trace both DEMT and AWSoM results.
+The reader may notice that these structures are the same as those in Figure \ref{rpoint_demt} but more filled, the cause is twofold.
+On the one hand the same magnetic model was used to trace both DEMT and AWSoM results, on the other hand is because giving the model smoother results, fewer fitted lines are filtered.
 
@@
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.pdf}
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.eps}
-\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify \albert{its loops in types I, II and III. The model does not exhibit loops of type 0.}}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.pdf}
+\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its loops in types I, II and III. The model does not exhibit loops of type 0.}}
 \label{rpoint_awsom}
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_short.eps}
-\caption{\albert{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (blue), II (red), and III (green), for CR-2082 (top panel) and CR-2208 (bottom panel).
+\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (blue), II (red), and III (green), for CR-2082 (top panel) and CR-2208 (bottom panel).
 Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
@@
 \includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
-\caption{\albert{Statistical distribution of DEMT (blue) and AWSoM (red) results traced along loops of type I, II and III (from top to bottom), as defined in Section 2.3.
+\caption{{Statistical distribution of DEMT (blue) and AWSoM (red) results traced along legs of type I, II and III (from top to bottom), as defined in Section 2.3.
 From left to right: electron density at the coronal base $\NCB\equiv \Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$.
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
-\caption{\albert{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).}}
+\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).}}
 \label{perf_lon_vr}
@@
 *Down loops, shiff y cranmer comentarios.
+
+*Energia DEMT\\
+We can see, on type 0 loops, a median value of energy input flux for CR2082 twice bigger than CR2208.
+Also, in both rotations, we observe a negative population of loop integrated energy input flux.
+This can refer to some loops where loop-integrated radiative flux is too small in comparison with the larger gradients of negative conductive flux, resulting in negative energy input flux.
+
+This effect can be due a subestimation of the density present in the loop or the limited range of temperature used to reconstruct tomographic parameters, that can affect the compute of radiative power.
+Nevertheless, this population represent lower than the \diego{ALGÚN PORCENTAJE$\%$} of total population in both cases.
+Bottom panels show the comparison for larger type I loops.
+We observe similar median values for the three loop-integrated energy quantities for both rotations.
 

### 2019-12-17 lloveras_2020.tex
mas texto, correcciones por aca y por alla

@@
 
-\address[id=aff3]{Facultad de Ciencias Exactas y Naturales (FCEN), Universidad de Buenos Aires (UBA), Pabell\'on II, Ciudad Universitaria, (C1428ZAA) Ciudad Aut\'onoma de Buenos Aires, Argentina}
+\address[id=aff3]{Ciclo Básico Común (CBC), Universidad de Buenos Aires (UBA), Buenos Aires, Argentina}
 
@@
 
+%correcciones a hacer! DIEGO
+%Los términos de la Eq (10) requieren ser explicados.
+La explicación a conituación no es clara, y de hecho está mal escrita.
+La Eq.
+(7) se integra en el VOLUMEN CORONAL COMPLETO de cada tubo de flujo y se divide por el área basal del mismo.
+Utilizando la condición solenoidal de B se llega a la Eq.
+(7), dónde...
+y ahí deberían darse las expresiones de Phir y Phic porque no pertenecen a la literatura estandard, y explicar a continuación como todos los elementos de esas dos expresiones surgen de los fits de DEMT y del modelo magnético de AWSoM.
+Donde si se puede ahorrar mucho espacio es en lo previo, la Eq (8) podría no incluirse por ejemplo.
+Creo que ahora lo mejor es que trates de completar la explicación dando las expresiones de Phir y Phic, y luego vemos de como limarla, probablemente eliminando la ec.
+(8).
+y además el texto puede compactarse, corregirse y reordenarse mucho.
+Poné las unidades de las cantidades Phi entre paréntesis a continuación de $\Phi_{h,r,c}$.
+
 Due the difference between temperatures of transition region and solar corona, there must to be a heating mechanism that compensate all the losses present in the atmosphere and maintain stable the plasma temperature.
@@
 \begin{equation}\label{Er}
-E_r = \int\,\Lambda(T)\,dN_e^2(T).
+E_r = \int\,\textrm{d}T\,T\,\LDEM(T)\,\Lambda(T)
 \end{equation}
@@
 As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr \Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.
-As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height may be used to compute the tomographic basal electron density at $\sqravgN(r=1.025\,\mrsun)$ as in previous articles.
+As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height may be used to compute the tomographic electron density at the coronal base $\sqravgN(r=1.025\,\mrsun)$ as in previous articles.
 In this case, for further comparison analysis with the AWSoM results, we selected the lowest height where the results of the MHD model are reliable, that is $1,055\,\mrsun$.
@@
 A decrease in the amount of down loops in equatorial latitudes could be an indicator of increased coronal activity \citet{nuevo_2013}.
-In blue the type 1 lines, populating all the streamer but mostly the mid latitudes.
-In red the type 2 lines, are mostly very large trans-equatorial field lines forming the envelope of the Streamer belt, and in green dots the type 3 lines, populating the coronal holes.
+In blue the type I lines, populating all the streamer but mostly the mid latitudes.
+In red the type II lines, are mostly very large trans-equatorial field lines forming the envelope of the Streamer belt, and in green dots the type III lines, populating the coronal holes.
 
@@
 To compare obtained traced results in both rotations and for each type of lines (associated with differents types of regions), Figure \ref{gradt_demt} shows histograms (normalized to the total amount of the field lines selected) of the temperature radial gradients ($\dr \Tm$).
-The lack of population around values close to zero is due to the strict condition $|\rho_t| > 0.5$ that discards possible isothermal values, according to DEMT results.
+The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs.
 
@@
 From top to bottom type 0 to type III.
-From left to right the panels show the statistical distribution of $\NCB$, $\lN$, $\aTm$, in each panel the median $m$ is indicated.
+From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$, $\lN$, $\aTm$, in each panel the median $m$ is indicated.
 
@@
 To compare integrated quantities along loops, we select those close loops where both legs meet the requirements of Section \ref{trace}.
-In an analogous way to the legs definition, we will refer to them as loops of type 0, I or II.
+In an analogous way to the legs definition, we will refer to them as loops of type 0, I or II to those whose both legs meeting the criteria.
+Now the type 0 loops are down loops.
 
@@
 
-The type I loops show a loop-integrated positive conductive for each loop in both rotations consistent with positive gradients of temperatures.
-\diego{We found larger temperature gradients for CR2208 than CR2082 (SI?)}, but for the most population of loops, the conductive flux have values around 0.3 $10^{5}[\rm{erg\,sec^{-1}\,cm^{-2}}]$ in both rotations.
-Similar results have been found for loop-integrated radiative flux and energy input flux for both rotations.
-
-Type 0 loops present larger gradients than type I.
+Type 0 loops present slightly larger gradients than type I.
 Therefore, type 0 present bigger amount, in modulus, of loop-integrated conductive flux.
 Due conductive flux negative can not be assumed as a loss but it can be contributing to the coronal heating.
-Thus, to compensate the radiative losses, a lower loop-integrated energy input flux is required.
+Thus, to compensate the radiative losses, a lower loop-integrated energy input flux ($\phi_h$) is required.
 
@@
 This can refer to some loops where loop-integrated radiative flux is too small in comparison with the larger gradients of negative conductive flux, resulting in negative energy input flux.
+
+The type I loops show a loop-integrated positive conductive for each loop in both rotations consistent with positive gradients of temperatures. The differences
+
+We found larger temperature gradients for CR2208 than CR2082, but for the most population of loops, the conductive flux have values around 0.3 $10^{5}[\rm{erg\,sec^{-1}\,cm^{-2}}]$ in both rotations.
+Similar results have been found for loop-integrated radiative flux and energy input flux for both rotations.
 
@@
 
-The actual version of the AWSoM model can not reproduce down loops, so for a further comparison we only select lines of type 1, 2 and 3 of those meeting the criteria described in Section \ref{trace}.
+The actual version of the AWSoM model can not reproduce down loops, so for a further comparison we only select lines of type I, II and III of those meeting the criteria described in Section \ref{trace}.
 As a way to understand the distribution of the selected lines, Figure \ref{rpoint_awsom} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations.
-In blue the type 1 lines, populating mostly the entire streamer.
-In red the type 2 lines, populating the edge that assemble the envelope around the streamer, and in green dots the type 3 lines, populating the coronal holes.
+In blue the type I lines, populating mostly the entire streamer.
+In red the type II lines, populating the edge that assemble the envelope around the streamer, and in green dots the type III lines, populating the coronal holes.
 
-The reader may notice that these structures are the same as those in Figure \ref{rpoint_demt} but more filled, the cause is twofold.
-On the one hand the same magnetic model was used to trace both DEMT and AWSoM results, on the other hand is because giving the model smoother results, fewer fitted lines are filtered.
+The reader may notice that these structures are the same as those in Figure \ref{rpoint_demt} but more filled.
+The cause is twofold, on the one hand the same magnetic model was used to trace both DEMT and AWSoM results, on the other hand is because giving the model smoother results, fewer fitted lines are filtered.
 
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.pdf}
-\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its loops in types I, II and III. The model does not exhibit loops of type 0.}}
+\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its legs in types I, II and III. The model does not exhibit legs of type 0.}}
 \label{rpoint_awsom}
@@
 
-\diego{
-*awsom da valores mas altos en los polos\\
-*Parece haber una buena coincidencia en CR2082 en Te yen CR2208 en Ne.\\
-*En CR2082 en Ne demt es 20 \% mas grande que awsom en la zona cerrada.\\
-*En cr2208 en Te, en la zona polar awsom es 30\% mas grande y awsom es 25\% mas grande en la region cerrada.
-}
+According to the visual inspection on the maps of carrington, the latitudinal profiles comparing both DEMT and AWSoM results are on the same scale.
+Little difference in density is observed in CR-2208 and in temperature in CR-2082, while DEMT in CR-2082 was $20\%$ denser.
+Finally, DEMT results for CR-2208 were $25\%$ hotter in the streamer and $30\%$ colder in the polar zone than AWSoM.
+Density profiles on AWSoM show an increase around the polar zone, which seems like an artifice.
 
@@
 
-To summarize the comparison between both results during both rotations at full height, it is shown in Figure \ref{perfiles_promedio} the average fits of $\Ne(r)$ and $T_e(r)$ for every type of legs.
+To summarize the comparison between both results during both rotations at full height, it is shown in Figure \ref{perfiles_promedio} the average fits of $\Ne(r)$ and $T_e(r)$ for legs of type I (blue), II (red), and III (green) for both rotations.
 
-\diego{Explicar lo que se observa:
-- Ne 1.65 awsom menor que la de demt en CR2082 y mayor que la de CR2208 y debido a que decaen esponencialmente, el hecho que tiendan a valores similares conforme aumenta la altura implica escalas de altura similares.
-\\
-- Las temperaturas a 1.065 difieren en ambas rotaciones y en todas las regiones/tipos de lineas siendo siempre menor la de awsom, sin embargo las pendientes son similares en todas la regiones.
-Excepto que los gradientes de cr2208 en CH son mayores demt consistente con la fig de grad de temp, me preg si esto es por AIA.}
+In average all temperature and density behavior from both results are on the same scale.
+The coronal base densities of AWSoM were lower than those of DEMT in CR-2082 and higher in CR-2208.
+The fact that the density decays to similar values between both results suggests a similar height scale.
+Onthe other hand basal temperature of AWSoM was lower in both rotations, but the temperature gradients are very similar en each type of legs, showing a very similar increase of temperature with height.
 
@@
 
-As way of example, Figure \ref{histos_2082} and \ref{histos_2208} shows the statistical results of both rotations for the three types of field lines traced with DEMT (blue) and AWSoM results (red).
+Tu summary the statistical comparison, Figure \ref{histos_2082} and \ref{histos_2208} shows the statistical results of both rotations for the three types of field lines traced with DEMT (blue) and AWSoM results (red).
 From left to right the panels show the statistical distribution of $\NCB$, $\lN$ and $\aTm$.
@@
 The DEMT quantities are expressed as absoulte values, while for ASWSoM they are informed relative to the corresponding result for DEMT.
-
-\diego{comentar lo que se desprende de los graficos y la tabla.}
 
@@
 \caption{{Statistical distribution of DEMT (blue) and AWSoM (red) results traced along legs of type I, II and III (from top to bottom), as defined in Section 2.3.
-From left to right: electron density at the coronal base $\NCB\equiv \Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$.
+From left to right: electron density at the coronal base $\NCB\equiv \Ne(r=1.055\,\mrsun)$\diego{en realidad Ncb se define distinto para awsom que demt.}, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
 In each panel the median value $m$ is indicated.}}
@@
 \end{figure}
-
-\begin{table}
-\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
-% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
-\hline
-Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
-       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
-\hline
-CR-2082\\
-1  & 0&84 &(\Mi&14&4\%)  &   8&3 &(\Mi&~2&5\%) &   1&30 &(\Mi&10&8\%) \\
-2  & 0&74 &(\Mi&21&9\%)  &   8&9 &(\Pl&~1&0\%) &   1&33 &(\Mi&~4&5\%) \\
-3  & 0&82 &(\Mi&17&9\%)  &   7&7 &(\Mi&~8&9\%) &   0&98 &(\Mi&~9&5\%) \\
-\hline          
-CR-2208\\
-1  & 0&74 &(\Pl&~6&4\%)  &   9&8 &(\Mi&~7&1\%) &   1&55 &(\Mi&12&3\%) \\
-2  & 0&62 &(\Pl&~8&2\%)  &  11&6 &(\Mi&17&2\%) &   1&55 &(\Mi&~9&7\%) \\
-3  & 0&42 &(\Mi&~4&8\%)  &   8&6 &(\Mi&~8&4\%) &   1&04 &(\Mi&~9&7\%) \\
-\end{tabular}
-\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
-DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
-\label{tabla_comp}
-\end{table}
-
-%For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were separated into the coronal {regions described in Section \ref{regions} and summarized in Table \ref{tabregions}}.
-For each field line, the data points of electron density and electron mean temperature versus height were fitted to the functions given by Equations 5 and 6 of Section \ref{trace}.
-As a result, the footpoint electron density $N_0$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $a=\textrm{d}\Tm/\textrm{d}r$, and the height-averaged (along the loop) electron mean temperature $\aTm$.
-As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data versus height was used to compute the {coronal base electron density} here defined as $\NCB\equiv \Ne(r=1.025\,\mrsun)$.
-Also, for each field line the coronal base magnetic field strength $B_{\rm CB}\equiv B(r=1.025\,\mrsun)$ and its height-averaged value along the loop $\left<B\right>$ were also computed.
 
@@
 This will be nice to do also for the July-2-2019 Eclipse rotation that we will analyze after this paper.
+
+\begin{table}
+\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
+% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
+\hline
+Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
+       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
+\hline
+CR-2082\\
+1  & 0&84 &(\Mi&14&4\%)  &   8&3 &(\Mi&~2&5\%) &   1&30 &(\Mi&10&8\%) \\
+2  & 0&74 &(\Mi&21&9\%)  &   8&9 &(\Pl&~1&0\%) &   1&33 &(\Mi&~4&5\%) \\
+3  & 0&82 &(\Mi&17&9\%)  &   7&7 &(\Mi&~8&9\%) &   0&98 &(\Mi&~9&5\%) \\
+\hline          
+CR-2208\\
+1  & 0&74 &(\Pl&~6&4\%)  &   9&8 &(\Mi&~7&1\%) &   1&55 &(\Mi&12&3\%) \\
+2  & 0&62 &(\Pl&~8&2\%)  &  11&6 &(\Mi&17&2\%) &   1&55 &(\Mi&~9&7\%) \\
+3  & 0&42 &(\Mi&~4&8\%)  &   8&6 &(\Mi&~8&4\%) &   1&04 &(\Mi&~9&7\%) \\
+\end{tabular}
+\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
+DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
+\label{tabla_comp}
+\end{table}
 
@@
 Bottom panels show the comparison for larger type I loops.
-We observe similar median values for the three loop-integrated energy quantities for both rotations.
 

### 2019-12-20 lloveras_2020.tex
tablas acomodadas.

@@
 
-While CR-2082 was highly axisymmetric and showed virtually no ARs (active region) \temp{(ver si en lat 50 y long 70 hay una.)}, CR-2208 showed an AR around latitude $+10\mdeg$ and longitude $300\mdeg$ \temp{(ver la region open en lat 0 y long 200)}.
+While CR-2082 was highly axisymmetric and showed virtually no ARs (active region) \temp{(ver si en lat 50 y long 70 hay una.)}, CR-2208 showed an AR around latitude $+10\mdeg$ and longitude $310\mdeg$ \diego{and }.
 Except for these ARs, in both rotations the open-closed boundaries derived from the respective AWSoM model match the shape of the contour levels of the tomographic maps of both the electron density and the electron mean temperature.
@@
 \hline
-0  & 0&93 &(\Mi&12&9\%)  &   7&4 &(\Pl&~3&9\%) &   1&11 &(\Pl&20&7\%) \\
-1  & 0&84 &(\Mi&11&3\%)  &   8&3 &(\Pl&15&3\%) &   1&30 &(\Pl&16&1\%) \\
-2  & 0&74 &(\Mi&16&1\%)  &   8&9 &(\Pl&19&1\%) &   1&33 &(\Pl&14&2\%) \\
-3  & 0&48 &(\Mi&12&5\%)  &   7&7 &(\Pl&10&5\%) &   0&98 &(\Pl&~5&7\%) \\
+0    & 1&26 &(\Mi&17&4\%)  &   7&3 &(\Pl&13&6\%) &   1&09 &(\Pl&24&7\%) \\
+I    & 1&13 &(\Mi&14&1\%)  &   8&3 &(\Pl&18&1\%) &   1&29 &(\Pl&20&1\%) \\
+II   & 0&97 &(\Mi&20&6\%)  &   8&9 &(\Pl&29&1\%) &   1&33 &(\Pl&16&5\%) \\
+III  & 0&66 &(\Mi&16&2\%)  &   7&7 &(\Pl&11&4\%) &   0&98 &(\Pl&~6&1\%) \\
 \hline          
@@
 CR-2082\\
-1  & 0&84 &(\Mi&14&4\%)  &   8&3 &(\Mi&~2&5\%) &   1&30 &(\Mi&10&8\%) \\
-2  & 0&74 &(\Mi&21&9\%)  &   8&9 &(\Pl&~1&0\%) &   1&33 &(\Mi&~4&5\%) \\
-3  & 0&82 &(\Mi&17&9\%)  &   7&7 &(\Mi&~8&9\%) &   0&98 &(\Mi&~9&5\%) \\
+I  & 1&13 &(\Mi&11&9\%)  &   8&3 &(\Mi&~2&4\%) &   1&29 &(\Mi&10&8\%) \\
+II  & 0&97 &(\Mi&22&5\%)  &   8&9 &(\Pl&~2&2\%) &   1&33 &(\Mi&~4&5\%) \\
+III  & 0&66 &(\Mi&16&8\%)  &   7&7 &(\Mi&~9&1\%) &   0&98 &(\Mi&~9&2\%) \\
 \hline          
 CR-2208\\
-1  & 0&74 &(\Pl&~6&4\%)  &   9&8 &(\Mi&~7&1\%) &   1&55 &(\Mi&12&3\%) \\
-2  & 0&62 &(\Pl&~8&2\%)  &  11&6 &(\Mi&17&2\%) &   1&55 &(\Mi&~9&7\%) \\
-3  & 0&42 &(\Mi&~4&8\%)  &   8&6 &(\Mi&~8&4\%) &   1&04 &(\Mi&~9&7\%) \\
+I  & 0&97 &(\Pl&~9&3\%)  &   9&8 &(\Mi&~7&1\%) &   1&55 &(\Mi&14&2\%) \\
+II  & 0&77 &(\Pl&11&7\%)  &  11&6 &(\Mi&17&2\%) &   1&55 &(\Mi&~9&7\%) \\
+III  & 0&56 &(\Mi&~1&9\%)  &   8&6 &(\Mi&16&3\%) &   1&04 &(\Mi&~9&6\%) \\
 \end{tabular}

### 2019-12-20 lloveras_2020.tex
cambiando cosas

@@
 \begin{equation}\label{Er}
-E_r = \int\,\textrm{d}T\,T\,\LDEM(T)\,\Lambda(T)
+E_r = \int\,\textrm{d}T\,\LDEM(T)\,\Lambda(T)
 \end{equation}
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up_short.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up_short.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up_short.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_short.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
 \caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (blue), II (red), and III (green), for CR-2082 (top panel) and CR-2208 (bottom panel).
@@
 
+In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI.
+In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, analyzed a single target using both instruments independently.
+They found that while the density product is essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e.
+$\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$.
+Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was $\approx 10-15\%$ hotter than CR-2082 throughout the streamer belt region.
+As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region.
+These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\lesssim 5\%$ and $\approx 2\%$ for the electron temperature and density, respectively.
+
 *Down loops, shiff y cranmer comentarios.

### 2019-12-23 lloveras_2020.tex
cambios varios en figuras y texto

@@
 
-\address[id=aff2]{Universidad Nacional de Tres de Febrero (UNTREF), Valent\'{\i}n G\'omez 4752, (B1678ABH) Caseros, Provincia de Buenos Aires, Argentina}
+\address[id=aff2]{Universidad Nacional de Tres de Febrero (UNTREF). Departamento de Ciencia y Tecnolog\'{\i}a, Sáenz Peña, Argentina.}
 
@@
 
-While CR-2082 was highly axisymmetric and showed virtually no ARs (active region) \temp{(ver si en lat 50 y long 70 hay una.)}, CR-2208 showed an AR around latitude $+10\mdeg$ and longitude $310\mdeg$ \diego{and }.
+While CR-2082 was highly axisymmetric and showed two ARs (active region) in latitude $+30\mdeg$ and longitude $50\mdeg$ and $120\mdeg$.
+CR-2208 showed two AR, one around latitude $+5\mdeg$ and longitude $140\mdeg$ and the other around latitude-longitud $+5\mdeg$, $300\mdeg$.
 Except for these ARs, in both rotations the open-closed boundaries derived from the respective AWSoM model match the shape of the contour levels of the tomographic maps of both the electron density and the electron mean temperature.
@@
 
-\temp{aca se defininen los highpoints, se comentan los colores y enunciar que cada uno puebla una regino termodinamica diferente}
-
 As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr \Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.
@@
 
-\temp{Aca una linea que linkea la definicion del tipo de lineas en la seccion anterior con las regiones que se ven en la figura que se describe a continuacion}
-
-As a way of knowing the physical position of the types of lines defined in Section \ref{trace}, the Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations.
-In cyan the type 0 lines are indicated, populating the most equatorial latitudes (dominated mostly by down loops).
-This kind of structures has been informed in previous works, \citet{lloveras_2017} observed down {loops} in a rotation during the solar minima of 1996 and for the previous rotation CR-2081.
-A decrease in the amount of down loops in equatorial latitudes could be an indicator of increased coronal activity \citet{nuevo_2013}.
-In blue the type I lines, populating all the streamer but mostly the mid latitudes.
-In red the type II lines, are mostly very large trans-equatorial field lines forming the envelope of the Streamer belt, and in green dots the type III lines, populating the coronal holes.
+\diego{
+As a way of knowing the physical position of all traced lines, Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of all open and closed file lines traced in gray scale at $1.105\,\mrsun$ for both rotations, where the ARs where excluded.
+At top, all traced legs with enaugh tomographic data are shown.
+In black all legs corresponding to closed lines and in grey corresponding to open lines.
+This traced lines were divided into four types as explained in Section \ref{trace} and the fit in density and temperature was applied, selecting only those legs that met the criteria.
+The bottom figure shows the latitudinal-longitudinal location of this selected lines at same height.
+In blue the type 0 lines are indicated, populating the most equatorial latitudes (dominated mostly by down legs).
+This kind of structures has been informed in previous works, \citet{lloveras_2017} observed down legs in a rotation during the solar minima of 1996 and for the previous rotation CR-2081.
+A decrease in the amount of down legs in equatorial latitudes could be an indicator of increased coronal activity \citet{nuevo_2013}.
+In red the type I lines, populating all the streamer but mostly the mid latitudes.
+In violet the type II lines, which are mostly very large trans-equatorial field lines forming the envelope of the Streamer belt, and in green dots the type III lines, populating the coronal holes.
+}
 
@@
 \begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
 \includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
@@
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
-\caption{Latitude-longitude location of each leg of type 0 (cyan), I (blue), II (red) and III (green) at $1.105\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).
-See Section \ref{trace} for a definition of the different types of {legs}.
-\notebyalbert{(by ALBERT) The population of DOWN LEGS in CR-2008 is negligible.
-These are VERY SMALL loops, I am pretty sure but you and Ceci shoudl check it.}  \notebyalbert{(by ALBERT) This Figure is great, but I do not quite like the choice of colors.
-I suggest these changes: cyan$\rightarrow$blue, blue$\rightarrow$red, red$\rightarrow$violet.
-In this way, blue will be DOWN loops and red will be UP loops, as in previous papers.
-The same change applies to Figure 4.
-Also, how about making Figures 3 and 4 a single Figure of four panels?
-Just an idea.} }
+\caption{\diego{At the top, latitude-longitude location of all open (grey) and closed (black) lines traced.
+At the bottom, latitude-longitude location of each leg that was traced and that meets the criteria listed in Section \ref{trace}.
+Type 0, I, II and III are shown in blue, red, violet and green respectively at $1.105\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).
+See Section \ref{trace} for a definition of the different types of {legs}.} \notebyalbert{(by ALBERT) The population of DOWN LEGS in CR-2008 is negligible.
+These are VERY SMALL loops, I am pretty sure but you and Ceci shoudl check it.} }
 \label{rpoint_demt}
@@
 
-\diego{Comienza la energia}\\
-
 %Previous works have found magnetic loops which temperature decrease with height, most generally in equatorial latitudes \citep{huang_2012,nuevo_2013}.
@@
 In an analogous way to the legs definition, we will refer to them as loops of type 0, I or II to those whose both legs meeting the criteria.
-Now the type 0 loops are down loops.
+When two legs of the same loop have a decreasing temperature with height (type 0), they are called down loops.
 
@@
 
-The type I loops show a loop-integrated positive conductive for each loop in both rotations consistent with positive gradients of temperatures. The differences
-
-We found larger temperature gradients for CR2208 than CR2082, but for the most population of loops, the conductive flux have values around 0.3 $10^{5}[\rm{erg\,sec^{-1}\,cm^{-2}}]$ in both rotations.
+The type I loops show a loop-integrated positive conductive for each loop in both rotations consistent with positive gradients of temperatures.
+The conductive flux have values around 0.3 $10^{5}[\rm{erg\,sec^{-1}\,cm^{-2}}]$ in both rotations.
 Similar results have been found for loop-integrated radiative flux and energy input flux for both rotations.
@@
 The open field regions in low latitudes maintain thermodynamic values associated with open regions.
-CR-2208 shows a well reconstruction of the AR around latitude $+10\mdeg$ and longitude $300\mdeg$ and a slight temperature difference between the poles \temp{estoy asumiento que es una AR}.
+The reconstruction of CR-2082 does not show clear the ARs, while CR-2208 shows a well reconstruction of both AR around latitude-longitud $+5\mdeg$, $140\mdeg$ and $+5\mdeg$, $300\mdeg$.
 In both rotations the open-closed boundaries derived from the AWSoM model match the shape of the contour levels of both the electron density and the electron temperature.
@@
 
-\temp{Se presentan los midpoints para awsom que lucen mas rellenos xq no hay down loops y todo es super suave.}
+%\temp{Se presentan los midpoints para awsom que lucen mas rellenos xq no hay down loops y todo es super suave.}
 
@@
 
-The actual version of the AWSoM model can not reproduce down loops, so for a further comparison we only select lines of type I, II and III of those meeting the criteria described in Section \ref{trace}.
-As a way to understand the distribution of the selected lines, Figure \ref{rpoint_awsom} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations.
-In blue the type I lines, populating mostly the entire streamer.
-In red the type II lines, populating the edge that assemble the envelope around the streamer, and in green dots the type III lines, populating the coronal holes.
+The actual version of the AWSoM model can not reproduce down legs, so for a further comparison we only select lines of type I, II and III of those meeting the criteria described in Section \ref{trace}.
+
+As a way to understand the distribution of legs, Figure \ref{rpoint_awsom} shows the latitudinal-longitudinal location of the traced legs at top and the selected fitted legs meeting the criteria at $1.105\,\mrsun$ for both rotations, in the same way as in Section \ref{demt_res}.
+In red the type I lines, populating mostly the entire streamer.
+In violet the type II lines, populating the edge that assemble the envelope around the streamer, and in green dots the type III lines, populating the coronal holes.
 
@@
 \begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_awsom_paper_test_Rpoint-map.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_awsom_paper_test_Rpoint-map.pdf}
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
-\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (blue), II (red), and III (green), for CR-2082 (top panel) and CR-2208 (bottom panel).
+\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (red), II (violet), and III (green), for CR-2082 (top panel) and CR-2208 (bottom panel).
 Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
@@
 The DEMT quantities are expressed as absoulte values, while for ASWSoM they are informed relative to the corresponding result for DEMT.
+
+\diego{aca podria ir un pequeño parrafo que resuma las diferencias.
+Pero justo a continuacion empiezan las conclusiones y uno tiende a repetir, no se como encararlo para que no quede dos veces lo mismo y tan pegado uno de lo otro.}
 
@@
 
-In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI.
+\diego{NOTE: Here is a paragraph describing the empirical successes in the reconstruction of both rotations.}
+
+*In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI.
 In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, analyzed a single target using both instruments independently.
@@
 
-*Down loops, shiff y cranmer comentarios.
+*Coronal magnetic structures for which the temperature increases/decreases with height in the range of heights covered by DEMT, $1.02–1.22\,\mrsun$, have been dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first observed their presence by means of DEMT.
+As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
+Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}.
+In a recent study by \citet{schiff_2016}, down and up loops have been successfully reproduced by a numerical implementation of a 1D steady-state model that considers time-averaged heating rates.
 
-*Energia DEMT\\
-We can see, on type 0 loops, a median value of energy input flux for CR2082 twice bigger than CR2208.
-Also, in both rotations, we observe a negative population of loop integrated energy input flux.
-This can refer to some loops where loop-integrated radiative flux is too small in comparison with the larger gradients of negative conductive flux, resulting in negative energy input flux.
+We found down legs in the DEMT reconstructions mainly in the equatorial latitudes, being a greater quantity and better distribution along longitudes in CR-2082 than in CR-2208.
+\citet{nuevo_2013} showed a decrease in the amount of down loops as the solar activity increases, which is consistent with the results shown in this article.
+
+*We can see, on type 0 loops, a median value of energy input flux ($\phi_h$) for CR-2082 twice bigger than CR-2208.
+In both rotations this magnitude has negative values, this can refer to some loops where loop-integrated radiative flux $\phi_r$) is too small in comparison with the larger gradients of negative conductive flux $\phi_c$), resulting in negative energy input flux.
 
@@
 Nevertheless, this population represent lower than the \diego{ALGÚN PORCENTAJE$\%$} of total population in both cases.
-Bottom panels show the comparison for larger type I loops.
+
+Consistent that the density in CR-2082 was higher, the $\phi_r$ was also higher.
+In both rotations the magnitudes in the temperature gradients are similar, but the temperatures in CR-2208 were consistently higher at all heights, resulting in a larger $\phi_c$ in module.
+This results are in agree with the observations of \citet{maccormack_2017}.
+
+\diego{THE AR of CR-2082 wasn't well modeled by AWSoM.}
+
+In both rotations, AWSoM and DEMT resutls shows same termodynamic structures along latitude and longitude with very comparable values between $1.055 - 1.25\,\mrsun$
+
+Figure \ref{histos_2082} and Table \ref{tabla_comp} indicate that AWSoM reconstruction of CR-2082 was found to be less dense $\approx 11-22\%$ and colder $\approx 5-10\%$.
+
+Both reconstructions of CR-2208 reconstructed the ARs with very similare values and in almost the same latitude-longitude location.
+Figure \ref{histos_2208} and Table \ref{tabla_comp} indicate that AWSoM reconstruction of CR-2208 was found to be denser $\approx 0-10\%$ and colder $\approx 10-15\%$.
+
+CR-2208 was $\approx 10-15\%$ hotter than CR-2082 throughout the streamer belt region.
+As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region.
+These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\lesssim 5\%$ and $\approx 2\%$ for the electron temperature and density, respectively.
+
+\diego{I would like to say something about FIgure 10. Maybe the weird tale in AWSoM Ne in the poles. Ideas?}\\
+
+\diego{We could say something about the anti correlation between speed and density and not get into the trace because issues do always appear and we don't have much time, and we all want to be happy in january.
+Unless the collaborators find easy to make this part.}
 

### 2019-12-23 lloveras_2020.tex
..

@@
 \def\diego#1{\textcolor{red}{#1}}
-\def\albert#1{\textcolor{blue}{#1}}
+\def\albert#1{\textcolor{orange}{#1}}
 \def\fede#1{\textcolor{ForestGreen}{#1}}
@@
 \temp{DEMT has been improved since the previously published work.
-We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.} \albert{NOTA de Albert: Explicá que hacés sin justificarte.
+We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.} \notebyalbert{NOTA de Albert: Explicá que hacés sin justificarte.
 Luego aclará como se hizo eso en trabajos previos, y cual es el impacto esperado.
@@
 
-Thermal conduction power is calculated by the Spitzer model \citep{spitzer_1962}, which describes coronal plasma regime properly.
-The thermal conduction power is obtained by taking the divergence of the conductive loss function $F_c(s)=-\kappa_0\,{T(s)}^{5/2}\,\frac{dT}{ds}(s)$, where $\kappa_0 = 9.2 \times 10^{-7}  {\rm erg\,sec^{-1}\,K^{-7/2}}$ is the Spitzer thermal conductivity.
-Due in coronal regime, the plasma is confined to the magnetic field, thus conduction is also predominately in the magnetic field direction.
-Thus, divergence is only the derivative along the position $s$:
+\noindent\notebyalbert{Trabajé todo lo naranja.
+Primero decidí que es mejor no numerar $E_c$ sino $F_c$.
+Eso te quedará claro cuando agregues las ecuaciones (11) y (12) que te indico más abajo y leas el último párrafo naranja de abajo, ahí cierra todo.
+Además describí que son los $\phi$ en forma correcta.
+El texto previo estaba muy flojón, entre otras cosas se hablaba de una (inexistente) ``conductive loss function" y de una (incorrectamente denominada) ``area along the loop".
+Obviamente luego de chequear este texto naranja borrá esta nota azul en particular.}
 
-\begin{equation}\label{Ec}
-E_c(s)=\frac{1}{A(s)}\,\frac{d}{ds}\left[A(s)\,F_c(s)\right].
+\albert{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, i.e.
+$E_c(s)=[1/A(s)]\,{\rm d}[A(s)\,F_c(s)]/{\rm d}s$, where $A(s)$ is the transversal area of the magnetic flux tube at position $s$.
+Under a quiescent solar corona plasma regime, the conductive flux is assumed to be dominated by the electron thermal conduction, described by the usual Spitzer model \citep{spitzer_1962}
+\begin{equation}\label{Fc}
+F_c(s)=-\kappa_0\,{T(s)}^{5/2}\,\frac{dT}{ds}(s),
 \end{equation}
-
-\noindent
-where $A(s)$ represent the magnetic flux tube area along the position $s$.
+where $\kappa_0 = 9.2 \times 10^{-7}  {\rm erg\,sec^{-1}\,K^{-7/2}}$ is the Spitzer thermal conductivity.}
 
@@
 
-Taking into acount the null divergence condition of magnetic field, the model integrate, between tomographic limits, each power quantities over magnetic flux tube independently of its area.
-Therefore, a loop-integrated equation for the energy flux balance is obtained ($[\rm{erg\,sec^{-1}\,cm^{-2}}]$):
-
+\albert{The energy balance given by Equation (\ref{Balance}) is then integrated in the volume of any given coronal magnetic flux tube.
+Dividing the result by the flux tube ara at the coronal base, and making use of the soleidonal conditon of the magnetic field, a field-line integrated version of that energy balance is found,
 \begin{equation}\label{FluxBalance}
@@
 \end{equation}
+\noindent
+where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},}\\
+\notebyalbert{Diego, please include here Equations (11) and (12) of that paper, which incredibly enough will have the same numbers here.}
 
-\noindent
-where $\phi_{h,r,c}$ are the loop-integrated energy input flux, radiative flux and conductive flux for each magnetic field line at 1.025 $R_{\odot}$.
-
-For a complete description of the energy balance model, the reader can refer to \citet{maccormack_2017}.
-We compute the loop-integrated energy quantities for both rotation analyzed in this work. 
-\\
+\albert{Note that, for any given field line, all quantities in these two expresions can be computed from the DEMT and AWSoM models through Equations (\ref{Fc})-(\ref{Er}).
+Once computed, the quantity $\phi_h$ can be calculated, which is the enery input flux required at the coronal base of each coronal field-line required to mantain a stable coronal structure.}
 
@@
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
-\caption{\diego{At the top, latitude-longitude location of all open (grey) and closed (black) lines traced.
-At the bottom, latitude-longitude location of each leg that was traced and that meets the criteria listed in Section \ref{trace}.
-Type 0, I, II and III are shown in blue, red, violet and green respectively at $1.105\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).
-See Section \ref{trace} for a definition of the different types of {legs}.} \notebyalbert{(by ALBERT) The population of DOWN LEGS in CR-2008 is negligible.
-These are VERY SMALL loops, I am pretty sure but you and Ceci shoudl check it.} }
+\caption{\albert{\emph{Top panels:} latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey) and closed (black) traced field lines for which there are along at least five DEMT data points, for both CR2082 (left) and CR2208 (right).
+\emph{Bottom panels}, latitude-longitude location (at the same height) of each traced leg that meets the criteria listed in Section \ref{trace}.
+Type 0, I, II and III legs (see text) are shown in blue, red, violet and green, respectively, for CR-2082 (left) and CR-2208 (right).}}
 \label{rpoint_demt}
@@
 Results for target rotations CR2082 and CR2208 are shown in blue and red color, respectively.
-In each panel the median value $m$ is indicated.} \notebyalbert{The histogram Figures in this draft need to be improved, in particular font size-and-type need to be optimized for clear reading.
-Also, we need to improve their X/Y ratio, here I stretched the Y size a bit in the LaTeX source.}}
+In each panel the median value $m$ is indicated.} \notebyalbert{ (by Albert) The histogram Figures in this draft need to be improved, in particular font size-and-type need to be optimized for clear reading.
+Also, we need to improve their X/Y ratio, here I stretched the Y size a bit in the LaTeX source.} \albert{Also, I believe you should use a FIXED x-range for each quantity (one for $\NCB$, one for $\lambda_N$ and one for $\aTm$) accross all Figures 5, 12, and 13, as that will visually highlinght how meadians and standard deviations compare, both between targets (CR2082 versus CR2208, this Figure) as well as between models (DEMT versus AWSoM, Figures 12 and 13).}}
 \label{histos_fulldemt}
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
-\caption{\diego{Statistical results of the loop integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right).
-From top to left loops of type 0, I and II where both legs meets the criteria from Section \ref{trace}.} \notebyalbert{The type-0 population in CR-22208 is negligible.
-These are VERY SMALL loops, I am pretty sure but you and Ceci shoudl check it.
-This can explain the non-physical $\phi_h<0$ population.} \notebyalbert{Utilizar los colores del paper de Cecilia, notar que el conductivo debe ser el verde y el energy input flux (h) debe ser el rojo.
-De paso, haría el verde un poco menos chillón, como en el paper de Ceci, se verá mejor.
-En el XYOUTS podés poner la letra griega $\phi$,  y para que te salga r,c,h como subíndice pero no pequeño usá: ``!Dp!N", donde p=r,c,h.}}
+\caption{\albert{Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right).
+From top to bottom, panels show the results for loops of type 0, I and II, which are loops for which both legs meet the criteria from Section \ref{trace}.} \notebyalbert{(by Albert) En el XYOUTS podés poner la letra griega $\phi$ usando los comandos ``!4" y ``!3",  y para que te salga r,c,h como subíndice pero no tan pequeño usá: ``!Dp!N", dónde p=r,c,h.}}
 \label{energia_demt}
@@
 
-The frequency histograms of Figure \ref{energia_demt} shows the loops-integrated energy quantities: $\phi_h$, $\phi_r$ and $\phi_c$ in green, blue, and red lines respectively, for both rotations.
+\albert{For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities $\phi_h$, $\phi_r$ and $\phi_c$ in green, blue and red color, respectively.}
 
@@
 The left (right) panels correspond to CR-2082 (CR2208).
-The vertical black line indicates the longitude-averaged latitudes of the open/close magnetic boundary.}
+The vertical black line indicates the longitude-averaged latitudes of the open/close magnetic boundary in both hemispheres.
+\notebyalbert{(by Albert): The idea of this Figure is to show how DEMT and AWSoM compare AS A FUNCTION OF LATITUDE at an intermediate height of the DMET grid, averaged in longitude (excluding zones with ARs).}}
 \label{perf_lat}
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
-\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (red), II (violet), and III (green), for CR-2082 (top panel) and CR-2208 (bottom panel).
-Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
+\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (red), II (violet), and III (green), for CR-2082 (top panels) and CR-2208 (bottom panels).
+Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.} \notebyalbert{(by Albert): The idea of this Figure is to show how DEMT and AWSoM compare AS A FUNCTION OF HEIGHT, in three distinct types of magnetic structures, and for both rotations.}}
 \label{perfiles_promedio}
@@
 \caption{{Statistical distribution of DEMT (blue) and AWSoM (red) results traced along legs of type I, II and III (from top to bottom), as defined in Section 2.3.
-From left to right: electron density at the coronal base $\NCB\equiv \Ne(r=1.055\,\mrsun)$\diego{en realidad Ncb se define distinto para awsom que demt.}, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
+From left to right: electron density at the lowest coronal height of the AWSoM model $\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
 In each panel the median value $m$ is indicated.}}
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
-\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).}}
+\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6.0\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).} \notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the abslute minimum indicates the location of the HCS at this height.
+I believe it is interesting to compare these two curves with Figure 10.
+Note that while in this Figure all latitudes are magnetically open, in Figure 10 only the part at latitudes larger than the vertical black lines are open.
+Note that DEMT shows that in the open low corona $N_e$ dereases from the O/C boundary towards the poles, anti-correlating with the AWSoM terminal speed, which is nice.
+In order to quantify this anti-correlation we need to trace the termnal speed and the DEMT $N_e$, which we may need to do with the help of Chip and Nishtha.
+Chip, we can discuss this idea over Skype after Xmas if you are around.}}
 \label{perf_lon_vr}
@@
 
-\noindent\notebyalbert{Antes de enviar esto a Michigan se precisa un conjunto de conclusiones compacto y claro.
-Creo que yo las pondría en tres grupos: a) conclusiones DEMT solas (esto incluye estructura termodinámica, up/down loops, energía), b) comparación AWSoM/DEMT (la clobal, es decir promedio longitudinal, y la que difernecia estructuras magnéticas), c) Wind Speed y Densidad basal.}
+\noindent\notebyalbert{(by Albert) This section will discuss and summarize some main conclusions, possibly in three groups: a) DEMT analysis alone (including thermodynamical structure, up/down loops, energy considerations, etc.), b) Comparison AWSoM/DEMT (longitude-averaged latitudinal profiles, height-dependence profiles in different magnetic structures, etc), and c) Correlation betweem AWSoM terminal wind speed and DEMT basal density, I will expand on this later this week as this may require help from Michigan).}
 

### 2019-12-26 lloveras_2020.tex
mas texto y algunas imagenes

@@
 
+To perform the comparison two specific rotations were selected, CR-2082 (2009, 05 April through 03 May), a deep minimum period between solar cycles (SCs) 23 and 24 characterized by virtually no ARs, and CR-2208 (2018, 02 September through 29 September), a rotation during the early declining fase of SC 24.
+
+To determine the thermodynamical structure of both rotations, the DEMT technique was applied to respective time series of EUV images covering each first half rotation.
+To study CR-2082 and CR-2208 data taken by the EUVI/STEREO and AIA/SDO instruments was used, respectively.
+
+In DEMT, the low corona in the height range $1.0$ to $1.25\,\mrsun$ is discretized in a spherical computational grid.
+The size of the tomographic cell (or voxel) is set to 0.01 \rsun \ in the radial direction, while is set 2\deg\ in both the latitudinal and longitudinal directions.
+We carried out a reconstruction using half of a solar rotation blocking the lines-of-sight comming from the disk (i.e.
+only using off-limb data).
+With this angular resolution one image every 6 hours is the cadence needed to fully constrain the inversion problem, for a total of about 55 images to cover a half solar rotation.
+We refer the reader to \citet{frazin_2009} for a detailed description of the technique, and to \citet{vasquez_2016} for a recent review on all published work based on it.
+Here we summarize the key points.
+The technique involves two consecutive procedures.
+
+ \diego{creo que es la primera vez que exploramos con hollow, vale la pena explicar la diferencia en detalle?}
+
+In a first step, the time series of EUV images is used to solve a SRT problem, for each EUV band independently.
+As a result, the 3D distribution of the so called {filter band emissivity} (FBE) is determined for each band separately.
+The FBE, {an emissivity-type quantity}, is defined as the wavelength integral of the coronal EUV spectral emissivity and the telescope's passband function of each EUV channel.
+Line-of-sight (LOS) integration of the FBE provides synthetic images that can be quantitatively compared to the real data in the time series.
+To find the FBE, the tomographic problem is posed a global optimization problem in which the quadratic norm of the difference between all pairs of synthetic and real images is minimized.
+Spatial regularization terms are also included in the objective function as to minimize high frequency spurious artifacts that are due to the specific characteristics of the SRT sparse projection matrix \citep{frazin_2009,frazin_2000}.
+{Due to optical depth issues that may affect LOSs} passing very close to the limb, and to the decay of intensity with radii, the 3D maps produced by DEMT analysis typically cover the height range 1.02 to 1.23 \rsun \ \citep{frazin_2009}.
+
+{In a second step, the FBE values obtained for all bands in each voxel are used to constrain the determination of a {local differential emission measure} (LDEM) distribution, which describes the temperature distribution of the electron plasma contained in each individual tomographic grid voxel.
+Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}
+
 \begin{equation}\label{fbeldem}
@@
 
-\temp{
+{
 Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}.
@@
 
-\albert{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, i.e.
+{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, i.e.
 $E_c(s)=[1/A(s)]\,{\rm d}[A(s)\,F_c(s)]/{\rm d}s$, where $A(s)$ is the transversal area of the magnetic flux tube at position $s$.
@@
 
-\albert{The energy balance given by Equation (\ref{Balance}) is then integrated in the volume of any given coronal magnetic flux tube.
-Dividing the result by the flux tube ara at the coronal base, and making use of the soleidonal conditon of the magnetic field, a field-line integrated version of that energy balance is found,
+{The energy balance given by Equation (\ref{Balance}) is then integrated in the volume of any given coronal magnetic flux tube.
+Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a field-line integrated version of that energy balance is found,
 \begin{equation}\label{FluxBalance}
@@
 \noindent
-where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},}\\
-\notebyalbert{Diego, please include here Equations (11) and (12) of that paper, which incredibly enough will have the same numbers here.}
+where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\
 
-\albert{Note that, for any given field line, all quantities in these two expresions can be computed from the DEMT and AWSoM models through Equations (\ref{Fc})-(\ref{Er}).
-Once computed, the quantity $\phi_h$ can be calculated, which is the enery input flux required at the coronal base of each coronal field-line required to mantain a stable coronal structure.}
+\begin{equation}\label{phi_r}
+\phi_r = \left( \frac{B_0 \ B_L}{B_0 + B_L} \right) \int_{0}^{L} ds \ \frac{E_r(s)}{B(s)}
+\end{equation}
+
+\begin{equation}\label{phi_c}
+\phi_c = \left( \frac{B_0 \ F_{c,L} - B_L \ F_{c,0}}{B_0 + B_L} \right) 
+\end{equation}
+
+{Note that, for any given field line, all quantities in these two expresions can be computed from the DEMT and AWSoM models through Equations (\ref{Fc})-(\ref{Er}).
+Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line required to mantain a stable coronal structure.}
 
@@
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
-\caption{\albert{\emph{Top panels:} latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey) and closed (black) traced field lines for which there are along at least five DEMT data points, for both CR2082 (left) and CR2208 (right).
-\emph{Bottom panels}, latitude-longitude location (at the same height) of each traced leg that meets the criteria listed in Section \ref{trace}.
+\caption{{\emph{Top panels:} latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey) and closed (black) traced field lines for which there are along at least five DEMT data points, for both CR2082 (left) and CR2208 (right).
+\emph{Bottom panels}: latitude-longitude location (at the same height) of each traced leg that meets the criteria listed in Section \ref{trace}.
 Type 0, I, II and III legs (see text) are shown in blue, red, violet and green, respectively, for CR-2082 (left) and CR-2208 (right).}}
@@
 In each panel the median value $m$ is indicated.} \notebyalbert{ (by Albert) The histogram Figures in this draft need to be improved, in particular font size-and-type need to be optimized for clear reading.
-Also, we need to improve their X/Y ratio, here I stretched the Y size a bit in the LaTeX source.} \albert{Also, I believe you should use a FIXED x-range for each quantity (one for $\NCB$, one for $\lambda_N$ and one for $\aTm$) accross all Figures 5, 12, and 13, as that will visually highlinght how meadians and standard deviations compare, both between targets (CR2082 versus CR2208, this Figure) as well as between models (DEMT versus AWSoM, Figures 12 and 13).}}
+Also, we need to improve their X/Y ratio, here I stretched the Y size a bit in the LaTeX source.} }
 \label{histos_fulldemt}
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
-\caption{\albert{Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right).
+\caption{{Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right).
 From top to bottom, panels show the results for loops of type 0, I and II, which are loops for which both legs meet the criteria from Section \ref{trace}.} \notebyalbert{(by Albert) En el XYOUTS podés poner la letra griega $\phi$ usando los comandos ``!4" y ``!3",  y para que te salga r,c,h como subíndice pero no tan pequeño usá: ``!Dp!N", dónde p=r,c,h.}}
@@
 
-\albert{For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities $\phi_h$, $\phi_r$ and $\phi_c$ in green, blue and red color, respectively.}
+{For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities $\phi_h$, $\phi_r$ and $\phi_c$ in green, blue and red color, respectively.}
 
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
-\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6.0\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).} \notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the abslute minimum indicates the location of the HCS at this height.
+\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6.0\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).} \notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the absolute minimum indicates the location of the HCS at this height.
 I believe it is interesting to compare these two curves with Figure 10.
 Note that while in this Figure all latitudes are magnetically open, in Figure 10 only the part at latitudes larger than the vertical black lines are open.
-Note that DEMT shows that in the open low corona $N_e$ dereases from the O/C boundary towards the poles, anti-correlating with the AWSoM terminal speed, which is nice.
-In order to quantify this anti-correlation we need to trace the termnal speed and the DEMT $N_e$, which we may need to do with the help of Chip and Nishtha.
+Note that DEMT shows that in the open low corona $N_e$ decreases from the O/C boundary towards the poles, anti-correlating with the AWSoM terminal speed, which is nice.
+In order to quantify this anti-correlation we need to trace the terminal speed and the DEMT $N_e$, which we may need to do with the help of Chip and Nishtha.
 Chip, we can discuss this idea over Skype after Xmas if you are around.}}
@@
 
-\diego{We could say something about the anti correlation between speed and density and not get into the trace because issues do always appear and we don't have much time, and we all want to be happy in january.
+%\diego{We could say something about the anti correlation between speed and density and not get into the trace because issues do always appear and we don't have much time, and we all want to be happy in january.
 Unless the collaborators find easy to make this part.}

### 2019-12-26 lloveras_2020_Albert.tex
unas sugerencias

--- 2019-12-26 lloveras_2020.tex
@@
 
-{We define next a measure of the average relative difference between the tomographic and the synthetic FBE in each voxel, as}
+\albert{We define next a measure of the accuracy of the LDEM model to predict the tomographic FBEs in each voxel, as}
 
 \begin{equation}\label{R}
-R_i \, \equiv \ (1/K) \, \sum_{k=1}^K \left| \, 1 - \FBE^{(k)}_{i,\rm syn}\,/\,\FBE^{(k)}_{i,\rm tom}\, \right| \,,
+R_i \, \equiv \ (1/K) \, \sum_{k=1}^K \left| \, 1 - \FBE^{(k)}_{i,\rm syn}\,/\,\FBE^{(k)}_{i,\rm tom}\, \right| \, ,
 \end{equation}
 
-so that the final product of DEMT is in the form of 3D maps of the electron density and mean temperature. These relationships {were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
+\noindent
+\albert{being the average relative difference between the tomographic and the synthetic FBEs.
+The final product} of DEMT is in the form of 3D maps of the electron density and mean temperature.
+These relationships {were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
 \temp{Aclarar que consideramos Ne como $\sqrt{<\Ne ^2>}$.} {ALBERT: Yo creo que es mejor hablar de $\sqravgN$}
-
 \temp{DEMT has been improved since the previously published work.
@@
 
-{Note that, for any given field line, all quantities in these two expresions can be computed from the DEMT and AWSoM models through Equations (\ref{Fc})-(\ref{Er}).
-Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line required to mantain a stable coronal structure.}
+Note that, for any given field line, all quantities in these two expresions can be computed from the DEMT and AWSoM models through Equations (\ref{Fc})-(\ref{Er}).
+Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux \albert{required at the coronal base of each coronal field-line to mantain a stable coronal structure.}
 
@@
 
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
+\caption{\albert{Carrington maps of the measure $R$ defined by Equation (\ref{R}), for CR2082 (left panels) and CR2208 (right panels), at heights $1.025$, $1.065$ and $1.105\,\mrsun$, from top to bottom}.
+\notebyalbert{Aquí deberían ir los seis mapas de $R$ correspondientes.
+Quizá los saquemos, pero a esta altura es importante que los veamos nosotros para evaluar la precisión de predicción de las reconstrucciones de los resultados LDEM en la zona abierta.
+Quizá terminemos haciendo el comentario adecuado y sacamos la Figura, o quizá la dejamos, pero veamos esa info aquí.
+Noten el cambio en NARANJA que hice en torno de la Ecuación (4) más adelante.}}
+\label{carmaps_R_2082_2208}
+\end{center}
+\end{figure}
 {To study the variation of the DEMT results in different magnetic structures we traced $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.} For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected.
@@
 \caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
-For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
+For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.
+\albert{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
+Doy dos ejemplos para no dejar dudas.
+Para $\NCB$ de Type-II: $1.0\,(-21\%)$.
+Para $\aTm$ de Type-III: $1.0\,(+6\%)$.}}
 \label{tabla_demt}
@@
 \caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
-DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
+DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.
+\albert{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
+Ejemplo para CR-2082 $\NCB$ de Type-II: $1.0\,(-23\%)$.
+Ejemplo para CR-2208 $\lambda_N$ de Type-II: $12.0\,(-17\%)$.
+Ejemplo para CR-2208 $\aTm$ de Type-II: $1.6\,(-10\%)$.}}
 \label{tabla_comp}

### 2019-12-26 lloveras_2020.tex
nueva figura y mas texto

@@
 To determine the thermodynamical structure of both rotations, the DEMT technique was applied to respective time series of EUV images covering each first half rotation.
-To study CR-2082 and CR-2208 data taken by the EUVI/STEREO and AIA/SDO instruments was used, respectively.
+To study CR-2082 and CR-2208 data taken by the EUVI-B/STEREO and AIA/SDO instruments was used, respectively.
+
+EUV images are affected by instrumental stray light contamination, which can be corrected by deconvolution of the point spread function (PSF).
+While in the case of AIA images there is no reliable determination of its PSF, it has been well determined for EUVI-B by \citet{shearer_2012}.
+For this article, all EUVI images were stray-light corrected.
+For the details of impact in $\Nm$ and $\Tm$, refer to \citet{lloveras_ba2017}.
 
@@
 only using off-limb data).
-With this angular resolution one image every 6 hours is the cadence needed to fully constrain the inversion problem, for a total of about 55 images to cover a half solar rotation.
+
+Using the high cadence of data available, one image every 10 minutes were used.
+The selected images were averaged in 6-hour intervals.
+Which, given the angular resolution, is the cadence needed to fully constrain the inversion problem, for a total of about 55 images to cover a half solar rotation.
+For both rotations, the first 14 days of data were used.
+
+\diego{
+Some technical improvements were applied in this work, a 3D regularization scheme was used instead of the latitude-longitude regularization scheme used in previous DEMT reconstructions.
+This implies that the results of the tomography are now more reliable at lower heights and limit-induced artifacts are minimized.
+For each instrument, the DEMT analysis involves a cross-validation study to determine the optimal level of regularization.
+This level is different for each wavelength band and is sensitive to}
+
 We refer the reader to \citet{frazin_2009} for a detailed description of the technique, and to \citet{vasquez_2016} for a recent review on all published work based on it.
@@
 The technique involves two consecutive procedures.
-
- \diego{creo que es la primera vez que exploramos con hollow, vale la pena explicar la diferencia en detalle?}
 
@@
 
-{We define next a measure of the average relative difference between the tomographic and the synthetic FBE in each voxel, as}
+We define next a measure of the accuracy of the LDEM model to predict the tomographic FBEs in each voxel, as
 
@@
 
-so that the final product of DEMT is in the form of 3D maps of the electron density and mean temperature. These relationships {were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
-\temp{Aclarar que consideramos Ne como $\sqrt{<\Ne ^2>}$.} {ALBERT: Yo creo que es mejor hablar de $\sqravgN$}
-
-\temp{DEMT has been improved since the previously published work.
+being the average relative difference between the tomographic and the synthetic FBEs.
+The final product of DEMT is in the form of 3D maps of the electron density and mean temperature.
+These relationships {were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
+%\temp{Aclarar que consideramos Ne como $\sqrt{<\Ne ^2>}$.} {ALBERT: Yo creo que es mejor hablar de $\sqravgN$}
+
+%\temp{DEMT has been improved since the previously published work.
 We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.} \notebyalbert{NOTA de Albert: Explicá que hacés sin justificarte.
@@
 {Note that, for any given field line, all quantities in these two expresions can be computed from the DEMT and AWSoM models through Equations (\ref{Fc})-(\ref{Er}).
-Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line required to mantain a stable coronal structure.}
+Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to mantain a stable coronal structure.}
 
@@
 \label{carmaps_demt_2208}
+\end{center}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
+\caption{{Carrington maps of the measure $R$ defined by Equation (\ref{R}), for CR-2082 (left panels) and CR-2208 (right panels), at heights $1.025$, $1.065$ and $1.105\,\mrsun$, from top to bottom}.
+}
+\label{carmaps_R_2082_2208}
 \end{center}

### 2019-12-27 lloveras_2020.tex
nueva figura3 y retoques

@@
 Using the high cadence of data available, one image every 10 minutes were used.
-The selected images were averaged in 6-hour intervals.
-Which, given the angular resolution, is the cadence needed to fully constrain the inversion problem, for a total of about 55 images to cover a half solar rotation.
+The selected images were averaged in 6-hour intervals which, given the angular resolution, is the cadence needed to fully constrain the inversion problem, for a total of about 55 images to cover a half solar rotation.
 For both rotations, the first 14 days of data were used.
 
-\diego{
-Some technical improvements were applied in this work, a 3D regularization scheme was used instead of the latitude-longitude regularization scheme used in previous DEMT reconstructions.
-This implies that the results of the tomography are now more reliable at lower heights and limit-induced artifacts are minimized.
-For each instrument, the DEMT analysis involves a cross-validation study to determine the optimal level of regularization.
-This level is different for each wavelength band and is sensitive to}
+\diego{ DONDE QUEDA MEJOR COMENTAR ESTA MEJORA?
+Unlike in previous works, a 3D regularization scheme was applied, thus spurious artifacts (nduced by the previous longitude latitude regularization schemei) were minimized in the first two heights of the tomographic grid.}
 
@@
 {Due to optical depth issues that may affect LOSs} passing very close to the limb, and to the decay of intensity with radii, the 3D maps produced by DEMT analysis typically cover the height range 1.02 to 1.23 \rsun \ \citep{frazin_2009}.
+
+\diego{COMO INTRODUZCO EL NIVEL DE REGULARIZACION? For each instrument, the DEMT analysis involves a cross-validation study to determine the optimal level of regularization.}
 
@@
 
-\diego{
 As a way of knowing the physical position of all traced lines, Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of all open and closed file lines traced in gray scale at $1.105\,\mrsun$ for both rotations, where the ARs where excluded.
@@
 In violet the type II lines, which are mostly very large trans-equatorial field lines forming the envelope of the Streamer belt, and in green dots the type III lines, populating the coronal holes.
-}
 
@@
 \caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
-For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
+For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.\albert{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
+Doy dos ejemplos para no dejar dudas.
+Para $\NCB$ de Type-II: $1.0\,(-21\%)$.
+Para $\aTm$ de Type-III: $1.0\,(+6\%)$.}}
 \label{tabla_demt}
@@
 Similar results have been found for loop-integrated radiative flux and energy input flux for both rotations.
-
-\diego{No son los mismos colores que el paper de ceci, tmb quizas podriamos poner la cant de LOOPS y los valores medianos, ceci insiste.}
 

### 2019-12-27 lloveras_2020_Albert.tex
Ediciones por ALBERT del VIERNES 27

--- 2019-12-26 lloveras_2020.tex
@@
 \newcommand{\cminvs}{\cm^{-2}}
+\newcommand{\erg}{{\rm erg}}
+\newcommand{\s}{{\rm s}}
 \newcommand{\sdev}{{\rm SD}}
@@
 \newcommand{\sqravgN}{\sqrt{\Nsqm}}
+\newcommand{\Tc}{T_{\rm c}}
 
@@
 only using off-limb data).
-With this angular resolution one image every 6 hours is the cadence needed to fully constrain the inversion problem, for a total of about 55 images to cover a half solar rotation.
+
+Using the high cadence of data available, one image every 10 minutes were used.
+The selected images were averaged in 6-hour intervals which, given the angular resolution, is the cadence needed to fully constrain the inversion problem, for a total of about 55 images to cover a half solar rotation.
+For both rotations, the first 14 days of data were used.
+
+\diego{ DONDE QUEDA MEJOR COMENTAR ESTA MEJORA?
+Unlike in previous works, a 3D regularization scheme was applied, thus spurious artifacts (nduced by the previous longitude latitude regularization schemei) were minimized in the first two heights of the tomographic grid.}
+
 We refer the reader to \citet{frazin_2009} for a detailed description of the technique, and to \citet{vasquez_2016} for a recent review on all published work based on it.
@@
 
+\diego{COMO INTRODUZCO EL NIVEL DE REGULARIZACION? For each instrument, the DEMT analysis involves a cross-validation study to determine the optimal level of regularization.}
+
 {In a second step, the FBE values obtained for all bands in each voxel are used to constrain the determination of a {local differential emission measure} (LDEM) distribution, which describes the temperature distribution of the electron plasma contained in each individual tomographic grid voxel.
@@
 Under a quiescent solar corona plasma regime, the conductive flux is assumed to be dominated by the electron thermal conduction, described by the usual Spitzer model \citep{spitzer_1962}
+
 \begin{equation}\label{Fc}
@@
 {To perform a comparative study of the thermodynamic structure of the inner corona in different solar cycles
-we carry out a DEMT reconstruction for two rotations: CR-2082, using STEREO/EUVI data and CR-2208, using SDO/AIA data.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared $\sqravgN$ and the electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}.} As an example, Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show the latitude-longitude maps of DEMT results for both rotations at {three different heights of interest.
-The lowest height where the tomography gives results, the lowest height where the AWSoM model results are reliable and a representative average height were selected, that is $r=$1.025, 1.065 and 1.105, $\mrsun$ respectively}.
-Black voxels correspond to non-reconstructed voxels (explained in Section \ref{demt}).
-Thick-black curve indicates the magnetic open/closed boundary based on the magnetic field of AWSoM model.
-
-While CR-2082 was highly axisymmetric and showed two ARs (active region) in latitude $+30\mdeg$ and longitude $50\mdeg$ and $120\mdeg$.
-CR-2208 showed two AR, one around latitude $+5\mdeg$ and longitude $140\mdeg$ and the other around latitude-longitud $+5\mdeg$, $300\mdeg$.
-Except for these ARs, in both rotations the open-closed boundaries derived from the respective AWSoM model match the shape of the contour levels of the tomographic maps of both the electron density and the electron mean temperature.
-In the AR, there is a lack of match between the open-closed boundaries and the tomographic reconstructions of density and temperature, that is why those ranges were excluded from the analysis.
-
-\temp{PARRAFO CORTO DE OBSERVACIONES QUE LUEGO SERAN CORROBORADAS CON HISTOGRAMAS.}
-A visual inspection of Figures \ref{momento1} and \ref{momento2} suggest/indicates that the streamer region of CR-2082 was denser and colder than CR-2208.
-In both rotations, but specifically in CR-2082 the temperature in the equatorial latitudes tend to decrease with height while the latitudes between the open-close boundaries and the equatorial latitudes tend to increase.
-These thermodynamic structures have been reported for other rotations in previous works \citep{lloveras_2017}.
-Closed regions are characterized by relatively larger values of density and temperature in comparison to the open regions.
-\diego{que mas se puede agregar?}
+we carry out a DEMT reconstruction for two rotations: CR-2082, using STEREO/EUVI data and CR-2208, using SDO/AIA data.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared $\sqravgN$ and the electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}.}
+
+\albert{As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show \albert{latitude-longitude} maps of DEMT results for both \albert{rotations.
+Three different heights of interest were selected here, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic results ($1.025\,\mrsun$), one of the lowest heights where the AWSoM results are consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
+Black voxels correspond to non-reconstructed voxels (\albert{see} Section \ref{demt}).
+Thick-black \albert{curves indicate} the magnetic open/closed \albert{boundaries} based on the magnetic field of \albert{the} AWSoM model.
+
+\albert{Target} CR-2082 was highly axisymmetric \albert{(i.e, a high azymuthal symmetry)} and showed two ARs (active region) in latitude $+30\mdeg$ and longitude $50\mdeg$ and $120\mdeg$.
+\albert{Target CR-2208 was much less axisymmetric and it} showed two AR, one around latitude $+5\mdeg$ and longitude $140\mdeg$ and the other around latitude-longitud $+5\mdeg$, $300\mdeg$.
+\albert{In both rotations the open/closed} boundaries derived from the respective AWSoM model \albert{very accurately} match the shape of \albert{contour levels} of the tomographic maps of both the \albert{electron density and temperature.
+The magneticlly open regions of the AWSoM model are those associated to CHs, and the magnetically closed ones to the equatorial streamer belt.}
+
+\albert{Visual inspection of Figures \ref{momento1} and \ref{momento2} indicates} that the streamer belt region of CR-2082 was denser and colder than CR-2208.
+\albert{In the case of CR-2082, which belongs to the deep minimum epoch between SC2 24/25, the temperature in the equatorial latitudes tends to decrease with height while in the mid-latitudes tends to increase.
+A similar behabiour is seen in CR-2208, belonmging to the declining phase of SC25, but being a much less axisymmetric target this behaviour is not so obvious.
+This structure of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.} Closed regions are characterized by relatively larger values of density and temperature in comparison to the open regions.
 
@@
 
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
+\caption{{Carrington maps of the measure $R$ defined by Equation (\ref{R}), for CR-2082 (left panels) and CR-2208 (right panels), at heights $1.025$, $1.065$ and $1.105\,\mrsun$, from top to bottom}.
+}
+\label{carmaps_R_2082_2208}
+\end{center}
+\end{figure}
+
 {To study the variation of the DEMT results in different magnetic structures we traced $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.} For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected.
 For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.
-
-As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr \Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.
-As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height may be used to compute the tomographic electron density at the coronal base $\sqravgN(r=1.025\,\mrsun)$ as in previous articles.
-In this case, for further comparison analysis with the AWSoM results, we selected the lowest height where the results of the MHD model are reliable, that is $1,055\,\mrsun$.
-
-\diego{
-As a way of knowing the physical position of all traced lines, Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of all open and closed file lines traced in gray scale at $1.105\,\mrsun$ for both rotations, where the ARs where excluded.
-At top, all traced legs with enaugh tomographic data are shown.
-In black all legs corresponding to closed lines and in grey corresponding to open lines.
-This traced lines were divided into four types as explained in Section \ref{trace} and the fit in density and temperature was applied, selecting only those legs that met the criteria.
-The bottom figure shows the latitudinal-longitudinal location of this selected lines at same height.
-In blue the type 0 lines are indicated, populating the most equatorial latitudes (dominated mostly by down legs).
-This kind of structures has been informed in previous works, \citet{lloveras_2017} observed down legs in a rotation during the solar minima of 1996 and for the previous rotation CR-2081.
-A decrease in the amount of down legs in equatorial latitudes could be an indicator of increased coronal activity \citet{nuevo_2013}.
-In red the type I lines, populating all the streamer but mostly the mid latitudes.
-In violet the type II lines, which are mostly very large trans-equatorial field lines forming the envelope of the Streamer belt, and in green dots the type III lines, populating the coronal holes.
-}
-
-Of the 45000 legs selected in 2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III, on the other hand of the 59000 legs selected in 2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.
-
-This selection of types of lines automatically leads to specific regions arranged along all longitudes associated with different thermodynamic, with good symmetry between both hemispheres in both rotations.%, this is because the rotations are at a minimum of activity and the static corona is a good approximation.
+\albert{As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}
+
+\noindent\notebyalbert{Quiero destactar el siguiente ejemplo de corrección, todo el párrafo.
+Comparalo con el texto previo para ver cuanto cambió.
+No solo estaba mal escrito sintácticamente, sino que no se conectaba adecuadamente con cada aspecto puntual de la Sección 2.3.
+Fijate que quedó mucho mejor explicado y conectando bien puntualmete con elementos previos de tu paper, lo cual es importante.
+Quizá te sirve para mejorar párrafos puntuales.
+Moví al fin de este párrafo el detalle de los porcentajes de cada población.}
+
+\albert{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
+Open legs are indicated in grey color and closed ones in black color.
+For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}).
+Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
+Using a four-color code, type 0, I, II and III legs are shown in blue, red, violet and green color, respectively.} \albert{Of the 45000 legs selected for CR-2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III.
+On the other hand, of the 59000 legs selected for CR-2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.}
+
+\albert{Type 0 (small down) legs mainly populate the equatorial latitudes.
+This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the SC 24/25 solar minimum by \citet{nuevo_2013}.
+Later on, \citet{lloveras_2017} showed how equatorial down loops in streamers were also to be found in the deep minimum between SCs 23/24.
+Here, we verify the existence of this type of structuire for the two target rotations.
+The relatively smaller population of down loops seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}.
+Type I (small up) mainly populate the mid-latitudes, while type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt.
+Finally, type III (open) legs populate of course the CHs.}
+
+\notebyalbert{No comprendo esta frase:} \emph{This classification of types of lines automatically leads to specific regions arranged along all longitudes associated with different thermodynamic, with good symmetry between both hemispheres in both rotations.}
 
@@
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
-\caption{{\emph{Top panels:} latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey) and closed (black) traced field lines for which there are along at least five DEMT data points, for both CR2082 (left) and CR2208 (right).
-\emph{Bottom panels}: latitude-longitude location (at the same height) of each traced leg that meets the criteria listed in Section \ref{trace}.
-Type 0, I, II and III legs (see text) are shown in blue, red, violet and green, respectively, for CR-2082 (left) and CR-2208 (right).}}
+\caption{\emph{Top panels:} \albert{latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR2082 (left) and CR2208 (right).
+\emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
+Using a four-color code, type 0, I, II and III legs (see text) are shown in blue, red, violet and green color, respectively.}}
 \label{rpoint_demt}
@@
 
-To compare obtained traced results in both rotations and for each type of lines (associated with differents types of regions), Figure \ref{gradt_demt} shows histograms (normalized to the total amount of the field lines selected) of the temperature radial gradients ($\dr \Tm$).
-The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs.
-
-Both rotations are characterized by lines of type 0 with mean values of $-2.5\, \rm MK/\mrsun$, mean values of $2.3\, \rm MK/\mrsun$ in type I and $2.4\, \rm MK/\mrsun$ in type II.
-The only notable difference is the smaller number of type 0 lines in CR-2208 and the mean value of $4.5\, \rm MK/\mrsun$ in type III for CR-2208 which is twice that for the other rotation.
+\albert{Figure \ref{gradt_demt} shows frequency histograms (normalized to the total amount of selected field lines ) of the temperature radial gradient ($\dr\Tm$) for legs of type 0, I, II and III.} The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs.
+\albert{For both rotations, the median value of $\dr\Tm$ is very similar for each type of leg, being  $\approx -2.5$, $2.3$ and $2.4\,\MK/\mrsun$ for legs of type 0, I and II, respectively.
+The only notable difference between both rotations is the characteristic value $\dr\Tm\approx 4.5\,\MK/\mrsun$ for legs of type III for CR-2208, which is about half that for CR-2082.} \notebyalbert{Estos vaores que informas son medianas o modas?
+(yo especifiqué ``medianas".
+Son efectivamente tan iguales?}
 
@@
 
-As an example of the traced magnitudes, Figure \ref{histos_fulldemt} shows the statistical results of both rotations for all field lines types.
-From top to bottom type 0 to type III.
-From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$, $\lN$, $\aTm$, in each panel the median $m$ is indicated.
+\albert{Figure \ref{histos_fulldemt} shows} the statistical results of both rotations for all field lines types.
+From top to bottom \albert{results are shown for} type 0 to type III \albert{field lines}.
+From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$ \albert{(the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ \albert{and} $\aTm$, \albert{with the median value $m$ indicated in each plot}.
 
@@
 
-For all type of lines, Table \ref{tabla_demt} summarize the quantitative comparative analysis between the results of the two target rotations sampling both minima.
-For CR-2082 quantities are expressed as absoulte values, qhile for CR-2208 they are informed relative to the corresponding results for CR-2082.
+For all type of lines, Table \ref{tabla_demt} \albert{summarizes a} quantitative comparative analysis between the results of the two \albert{target rotations}.
+For CR-2082 quantities are expressed as absoulte values, \albert{while} for CR-2208 they are informed \albert{as a precentual variation} relative to the corresponding results for CR-2082.
 The following major results concerning the structure of each rotation individually and their comparison can be drawn.
@@
 
-\diego{si queda una asociacion directa entre los tipos de lineas y las estructuras de streamer, CH etc entonces usaria esos nombres a continuacion.}\\
-From the equatorial streamer of both rotations, increasing latitudes show decreasing {coronal base} density, and increasing density scale height and electron temperature.
-In both rotations the CH regions are characterized sub-MK temperatures, and coronal base densities of order $\approx 1/2$ of the equatorial streamer.
-Histograms with sharp populations indicates that for both rotations the values of all physical quantities exhibit a strong symmetry between both hemispheres.
-
-A comparison of the results between the two rotations shows that CR-2208 is characterized by lower values (between $11\%\, \rm and\, 16\%$) of coronal base electron density than CR-2082, higher values of density scale height (between $4\%\, \rm and\,19\%$) and higher values of electron temperature (between $6\%\, \rm and\,21\%$).
+%\noindent\diego{Si queda una asociacion directa entre los tipos de lineas y las estructuras de streamer, CH etc entonces usaria esos nombres a continuacion.}\\
+\albert{Throughout} the equatorial streamer of both rotations, \albert{type 0, I and II legs, which are associated to progressively} increasing latitudes, \albert{progressively exhibit} decreasing {coronal base} density, \albert{increasing density scale height, and increasing electron temperature}.
+In both rotations the CH regions are characterized sub-MK temperatures, and coronal base densities of order $\approx 1/2$ of \albert{those observed for the type 0 lines in the core of} the equatorial streamer.
+\notebyalbert{No estoy seguro de entender y acordar con la siguiente frase.} \emph{Histograms with sharp populations indicates that for both rotations the values of all physical quantities exhibit a strong symmetry between both hemispheres.}
+
+\notebyalbert{A continuación modifiqué la sintaxis en que esto se explica (creo que para mejor), y puse números acordes a los de la Tabla-1, los que estaban no eran consistentes con ella.} \albert{A comparison of the results between the two rotations shows that compared to CR-2082, target rotation CR-2208 was characterized by $\approx 15-20\%$ lower values of the electron density at the coronal base, $\approx 10-30\%$ larger values of density scale height, and $\approx 15-25\%$ larger values of the electron temperature.}
 
@@
 
-To compare integrated quantities along loops, we select those close loops where both legs meet the requirements of Section \ref{trace}.
-In an analogous way to the legs definition, we will refer to them as loops of type 0, I or II to those whose both legs meeting the criteria.
-When two legs of the same loop have a decreasing temperature with height (type 0), they are called down loops.
+\notebyalbert{Cambié este párrafo.} \albert{To analyze the loop-integrated energy flux quantities, we selected closed loops where both legs meet the requirements of Section \ref{trace}, and both posses the same sign of the radial gradient of the electron temperature $\dr\Tm$.
+In this way, according to the clasification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).}
 
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
-\caption{{Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right).
+\caption{\albert{Sugiero fuertemente que el histograpma de Type 0 tenga xr=[-1,+3] como el resto, creo que quedará claro por qué cuando lean el análisis que hice de esta Figura en el texto.} {Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right).
 From top to bottom, panels show the results for loops of type 0, I and II, which are loops for which both legs meet the criteria from Section \ref{trace}.} \notebyalbert{(by Albert) En el XYOUTS podés poner la letra griega $\phi$ usando los comandos ``!4" y ``!3",  y para que te salga r,c,h como subíndice pero no tan pequeño usá: ``!Dp!N", dónde p=r,c,h.}}
@@
 
-{For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities $\phi_h$, $\phi_r$ and $\phi_c$ in green, blue and red color, respectively.}
-
-Type 0 loops present slightly larger gradients than type I.
+For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities \albert{$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.
+\notebyalbert{Notá que puse las cosas en el orden que las cosas se calculan: Eq.
+11, 12, y 10.
+Sugiero que en los histogramas listes los $\phi$ y sus medianas de arriba a abajo en este orden, ya que igual los deberás re-hacer para poner la letra griega $\phi$ (y otros cambios requeridos).}
+
+\notebyalbert{El análisis que había de los $\phi$ no me pareció adecuado, y lo comenté (no lo borré por si querés revisarlo y si ves que se pasó algo).
+Lo que sigue hasta el fin de la sección lo escribí yo mirando el paper de Cecilia y tu Figura, destacando lo que considero más importante.
+Lo hice medio apurato, y requerirá más trabajo.
+Pero para mi esta es la línea.}
+
+\albert{For both rotations it is readily seen that the integrated radiative loss of the loops, measured by the quantity $\phi_r$, is largest for loops of type 0, smaller for loops of type I, and smalest for loops of type II .
+This is mainly due to the fact that in the range of sensitivity of the AUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$.
+Indeed, according to Table 1, loops of type 0 have the lowest temperature of them all and closest to $\Tc$, for both rotations.}
+
+\albert{In the case of the quantity $\phi_c$, its sign depends on that of the conductive flux $F_c$.
+As shown in \citet{maccormack_2017}, down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, which is verified in Figure \ref{energia_demt}.}
+
+\albert{The characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.0 \times 10^5\,\erg\cminvs\s^{-1}$, depending on the rotatin and the type of loop.
+These values are consistent with those reported by \citet{maccormack_2017}.}
+
+%Type 0 loops present slightly larger gradients than type I.
 Therefore, type 0 present bigger amount, in modulus, of loop-integrated conductive flux.
@@
 
-We can see, on type 0 loops, a median value of energy input flux for CR2082 twice bigger than CR2208.
+%We can see, on type 0 loops, a median value of energy input flux for CR2082 twice bigger than CR2208.
 Also, in both rotations, we observe a negative population of loop integrated energy input flux.
@@
 
-The type I loops show a loop-integrated positive conductive for each loop in both rotations consistent with positive gradients of temperatures.
+%The type I loops show a loop-integrated positive conductive for each loop in both rotations consistent with positive gradients of temperatures.
 The conductive flux have values around 0.3 $10^{5}[\rm{erg\,sec^{-1}\,cm^{-2}}]$ in both rotations.
 Similar results have been found for loop-integrated radiative flux and energy input flux for both rotations.
-
-\diego{No son los mismos colores que el paper de ceci, tmb quizas podriamos poner la cant de LOOPS y los valores medianos, ceci insiste.}
 

### 2019-12-28 lloveras_2020_Albert.tex
Edits by Albert, Viernes 27/Dic

@@
 
-\albert{For both rotations it is readily seen that the integrated radiative loss of the loops, measured by the quantity $\phi_r$, is largest for loops of type 0, smaller for loops of type I, and smalest for loops of type II .
+\albert{For both rotations it is readily seen that the integrated radiative loss, measured by the quantity $\phi_r$, is largest for loops of type 0, smaller for loops of type I, and smallest for loops of type II .
 This is mainly due to the fact that in the range of sensitivity of the AUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$.
@@
 
-\albert{The characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.0 \times 10^5\,\erg\cminvs\s^{-1}$, depending on the rotatin and the type of loop.
-These values are consistent with those reported by \citet{maccormack_2017}.}
+\albert{The characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.0 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of loop.
+These values are similar to those reported by \citet{maccormack_2017}.}
 

### 2019-12-28 lloveras_2020_Albert.tex
Nuevo texto de PHIs por Albert

@@
 
-\albert{For both rotations it is readily seen that the integrated radiative loss, measured by the quantity $\phi_r$, is largest for loops of type 0, smaller for loops of type I, and smallest for loops of type II .
-This is mainly due to the fact that in the range of sensitivity of the AUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$.
-Indeed, according to Table 1, loops of type 0 have the lowest temperature of them all and closest to $\Tc$, for both rotations.}
+\albert{For both rotations, the value of the integrated radiative power $E_r$, measured by the quantity $\phi_r$, progressively decreaces for loops of type 0, I and II.
+This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors cooperating to maximize $E_r$ for loops of type 0 and minimize it for loops of type II.
+As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0, I and II are characterised by progressively decreasing electron density for both rotations.
+Also, in the range of sensitivity of the AUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$.
+According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterised by progressively larger electron temperature, and progressively farther from the value $\Tc$, for both rotations.}
 
@@
 
-\albert{The characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.0 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of loop.
+\albert{As a result of the radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of loop.
 These values are similar to those reported by \citet{maccormack_2017}.}

### 2019-12-30 lloveras_2020.tex
cambio de figuras

@@
 
-For both rotations, the DEMT and AWSoM 3D maps of electron density $\Ne$, electron mean temperature $\Tm$ and electron temperature $\Te$ respectively were traced along the magnetic field lines modeled using AWSoM as described at the end of Section \ref{demt}.
-In the case of closed loops, results were separated into their two legs, defined as the two segments that go from the coronal base up to the apex.
-
-For each open field line, and for each leg of the closed ones, an exponential fit was then applied to {the $\sqravgN(r)$ data points, and a linear fit applied to the $\Tm(r)$ data points}, as described by
+Aiming determination of the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid.
+Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = r{\rm d}\theta/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point.
+In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, for a total of $96,000$ starting points.
+Each traced field line is classified as ``open" if it intersects the source surface, set in this work at $r=6\,\mrsun$ (where lines become radial), or as ``closed" otherwise.
+In the case of closed magnetic field lines, loops {are} further classified as ``small" and ``large" upon their apex height being within or beyond the range of heights studied by DEMT, respectively.
+
+At this stage, all DEMT and AWSoM products, electron density and mean temperature in particular, can be traced along open and closed magnetic field lines.
+Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one).
+To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it.
+As a result, for each field line one data point per tomographic cell is obtained.
+This allows to analyze how density and temperature, comming from both models, vary with height along each individual field line.
+This approach was firstly used by \citet{huang_2012} to study inverted temperature structures in the solar minimum corona, and later on applied by \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.
+
+\diego{aca estoy haciendo la distincion entre la densidad y temp obtenida por demt y awsom}
+For each open field line, and for each leg of the closed ones, an exponential fit was then applied to the electron density and a linear fit applied to the electron temperature.
+For DEMT results, the data points used were $\sqravgN(r)$ and $\Tm(r)$, in case of AWSoM the data points were $\Ne(r)$ and $\Te(r)$.
+The exponential and linear fit equations are described by
 
@@
 {To perform a comparative study of the thermodynamic structure of the inner corona in different solar cycles
-we carry out a DEMT reconstruction for two rotations: CR-2082, using STEREO/EUVI data and CR-2208, using SDO/AIA data.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared $\sqravgN$ and the electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}.} As an example, Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show the latitude-longitude maps of DEMT results for both rotations at {three different heights of interest.
-The lowest height where the tomography gives results, the lowest height where the AWSoM model results are reliable and a representative average height were selected, that is $r=$1.025, 1.065 and 1.105, $\mrsun$ respectively}.
-Black voxels correspond to non-reconstructed voxels (explained in Section \ref{demt}).
-Thick-black curve indicates the magnetic open/closed boundary based on the magnetic field of AWSoM model.
-
-While CR-2082 was highly axisymmetric and showed two ARs (active region) in latitude $+30\mdeg$ and longitude $50\mdeg$ and $120\mdeg$.
-CR-2208 showed two AR, one around latitude $+5\mdeg$ and longitude $140\mdeg$ and the other around latitude-longitud $+5\mdeg$, $300\mdeg$.
-Except for these ARs, in both rotations the open-closed boundaries derived from the respective AWSoM model match the shape of the contour levels of the tomographic maps of both the electron density and the electron mean temperature.
-In the AR, there is a lack of match between the open-closed boundaries and the tomographic reconstructions of density and temperature, that is why those ranges were excluded from the analysis.
-
-\temp{PARRAFO CORTO DE OBSERVACIONES QUE LUEGO SERAN CORROBORADAS CON HISTOGRAMAS.}
-A visual inspection of Figures \ref{momento1} and \ref{momento2} suggest/indicates that the streamer region of CR-2082 was denser and colder than CR-2208.
-In both rotations, but specifically in CR-2082 the temperature in the equatorial latitudes tend to decrease with height while the latitudes between the open-close boundaries and the equatorial latitudes tend to increase.
-These thermodynamic structures have been reported for other rotations in previous works \citep{lloveras_2017}.
-Closed regions are characterized by relatively larger values of density and temperature in comparison to the open regions.
-\diego{que mas se puede agregar?}
+we carry out a DEMT reconstruction for two rotations: CR-2082, using STEREO/EUVI data and CR-2208, using SDO/AIA data.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared $\sqravgN$ and the electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}.}
+
+{As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations.
+Three different heights of interest were selected here, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic results ($1.025\,\mrsun$), one of the lowest heights where the AWSoM results are consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
+Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}).
+Thick-black {curves indicate} the magnetic open/closed {boundaries} based on the magnetic field of {the} AWSoM model.
+
+{Target} CR-2082 was highly axisymmetric {(i.e, a high azymuthal symmetry)} and showed two ARs (active region) in latitude $+30\mdeg$ and longitude $50\mdeg$ and $120\mdeg$.
+{Target CR-2208 was much less axisymmetric and it} showed two AR, one around latitude $+5\mdeg$ and longitude $140\mdeg$ and the other around latitude-longitud $+5\mdeg$, $300\mdeg$.
+{In both rotations the open/closed} boundaries derived from the respective AWSoM model {very accurately} match the shape of {contour levels} of the tomographic maps of both the {electron density and temperature.
+The magneticlly open regions of the AWSoM model are those associated to CHs, and the magnetically closed ones to the equatorial streamer belt.}
+
+{Visual inspection of Figures \ref{momento1} and \ref{momento2} indicates} that the streamer belt region of CR-2082 was denser and colder than CR-2208.
+{In the case of CR-2082, which belongs to the deep minimum epoch between SC2 24/25, the temperature in the equatorial latitudes tends to decrease with height while in the mid-latitudes tends to increase.
+A similar behaviour is seen in CR-2208, belonging to the declining phase of SC25, but being a much less axisymmetric target this behaviour is not so obvious.
+This structure of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.} Closed regions are characterized by relatively larger values of density and temperature in comparison to the open regions.
 
@@
 For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.
-
-As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr \Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.
-As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height may be used to compute the tomographic electron density at the coronal base $\sqravgN(r=1.025\,\mrsun)$ as in previous articles.
-In this case, for further comparison analysis with the AWSoM results, we selected the lowest height where the results of the MHD model are reliable, that is $1,055\,\mrsun$.
-
-As a way of knowing the physical position of all traced lines, Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of all open and closed file lines traced in gray scale at $1.105\,\mrsun$ for both rotations, where the ARs where excluded.
-At top, all traced legs with enaugh tomographic data are shown.
-In black all legs corresponding to closed lines and in grey corresponding to open lines.
-This traced lines were divided into four types as explained in Section \ref{trace} and the fit in density and temperature was applied, selecting only those legs that met the criteria.
-The bottom figure shows the latitudinal-longitudinal location of this selected lines at same height.
-In blue the type 0 lines are indicated, populating the most equatorial latitudes (dominated mostly by down legs).
-This kind of structures has been informed in previous works, \citet{lloveras_2017} observed down legs in a rotation during the solar minima of 1996 and for the previous rotation CR-2081.
-A decrease in the amount of down legs in equatorial latitudes could be an indicator of increased coronal activity \citet{nuevo_2013}.
-In red the type I lines, populating all the streamer but mostly the mid latitudes.
-In violet the type II lines, which are mostly very large trans-equatorial field lines forming the envelope of the Streamer belt, and in green dots the type III lines, populating the coronal holes.
-
-Of the 45000 legs selected in 2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III, on the other hand of the 59000 legs selected in 2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.
-
-This selection of types of lines automatically leads to specific regions arranged along all longitudes associated with different thermodynamic, with good symmetry between both hemispheres in both rotations.%, this is because the rotations are at a minimum of activity and the static corona is a good approximation.
+{As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}
+
+\noindent\notebyalbert{Quiero destactar el siguiente ejemplo de corrección, todo el párrafo.
+Comparalo con el texto previo para ver cuanto cambió.
+No solo estaba mal escrito sintácticamente, sino que no se conectaba adecuadamente con cada aspecto puntual de la Sección 2.3.
+Fijate que quedó mucho mejor explicado y conectando bien puntualmete con elementos previos de tu paper, lo cual es importante.
+Quizá te sirve para mejorar párrafos puntuales.
+Moví al fin de este párrafo el detalle de los porcentajes de cada población.}
+
+{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
+Open legs are indicated in grey color and closed ones in black color.
+For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}).
+Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
+Using a four-color code, type 0, I, II and III legs are shown in blue, red, violet and green color, respectively.} {Of the 45000 legs selected for CR-2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III.
+On the other hand, of the 59000 legs selected for CR-2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.}
+
+{Type 0 (small down) legs mainly populate the equatorial latitudes.
+This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the SC 24/25 solar minimum by \citet{nuevo_2013}.
+Later on, \citet{lloveras_2017} showed how equatorial down loops in streamers were also to be found in the deep minimum between SCs 23/24.
+Here, we verify the existence of this type of structure for the two target rotations.
+The relatively smaller population of down loops seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}.
+Type I (small up) mainly populate the mid-latitudes, while type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt.
+Finally, type III (open) legs populate of course the CHs.}
+
+%\notebyalbert{No comprendo esta frase:} \emph{This classification of types of lines automatically leads to specific regions arranged along all longitudes associated with different thermodynamic, with good symmetry between both hemispheres in both rotations.}
 
@@
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
-\caption{{\emph{Top panels:} latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey) and closed (black) traced field lines for which there are along at least five DEMT data points, for both CR2082 (left) and CR2208 (right).
-\emph{Bottom panels}: latitude-longitude location (at the same height) of each traced leg that meets the criteria listed in Section \ref{trace}.
-Type 0, I, II and III legs (see text) are shown in blue, red, violet and green, respectively, for CR-2082 (left) and CR-2208 (right).}}
+\caption{\emph{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR2082 (left) and CR2208 (right).
+\emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
+Using a four-color code, type 0, I, II and III legs (see text) are shown in blue, red, violet and green color, respectively.}}
 \label{rpoint_demt}
@@
 
-To compare obtained traced results in both rotations and for each type of lines (associated with differents types of regions), Figure \ref{gradt_demt} shows histograms (normalized to the total amount of the field lines selected) of the temperature radial gradients ($\dr \Tm$).
-The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs.
-
-Both rotations are characterized by lines of type 0 with mean values of $-2.5\, \rm MK/\mrsun$, mean values of $2.3\, \rm MK/\mrsun$ in type I and $2.4\, \rm MK/\mrsun$ in type II.
-The only notable difference is the smaller number of type 0 lines in CR-2208 and the mean value of $4.5\, \rm MK/\mrsun$ in type III for CR-2208 which is twice that for the other rotation.
+{Figure \ref{gradt_demt} shows frequency histograms (normalized to the total amount of selected field lines ) of the temperature radial gradient ($\dr\Tm$) for legs of type 0, I, II and III.} The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs.
+{For both rotations, the median value of $\dr\Tm$ is very similar for each type of leg, being  $\approx -2.5$, $2.3$ and $2.4\,\MK/\mrsun$ for legs of type 0, I and II, respectively.
+The only notable difference between both rotations is the characteristic value $\dr\Tm\approx 4.5\,\MK/\mrsun$ for legs of type III for CR-2208, which is about half that for CR-2082.} \notebyalbert{Estos vaores que informas son medianas o modas?
+(yo especifiqué ``medianas".
+Son efectivamente tan iguales?}\diego{si, las medianas tienen esos valores.}
 
@@
 
-As an example of the traced magnitudes, Figure \ref{histos_fulldemt} shows the statistical results of both rotations for all field lines types.
-From top to bottom type 0 to type III.
-From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$, $\lN$, $\aTm$, in each panel the median $m$ is indicated.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
+{Figure \ref{histos_fulldemt} shows} the statistical results of both rotations for all field lines types.
+From top to bottom {results are shown for} type 0 to type III {field lines}.
+From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$ {(the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
 \caption{{Statistical distribution of DEMT results traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}.
 From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$.
-Results for target rotations CR2082 and CR2208 are shown in blue and red color, respectively.
+Results for target rotations CR-2082 and CR-2208 are shown in blue and red color, respectively.
 In each panel the median value $m$ is indicated.} \notebyalbert{ (by Albert) The histogram Figures in this draft need to be improved, in particular font size-and-type need to be optimized for clear reading.
@@
 
-For all type of lines, Table \ref{tabla_demt} summarize the quantitative comparative analysis between the results of the two target rotations sampling both minima.
-For CR-2082 quantities are expressed as absoulte values, qhile for CR-2208 they are informed relative to the corresponding results for CR-2082.
+For all type of lines, Table \ref{tabla_demt} {summarizes a} quantitative comparative analysis between the results of the two {target rotations}.
+For CR-2082 quantities are expressed as absoulte values, {while} for CR-2208 they are informed {as a precentual variation} relative to the corresponding results for CR-2082.
 The following major results concerning the structure of each rotation individually and their comparison can be drawn.
@@
 \caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
-For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.\albert{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
+For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.
+{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
 Doy dos ejemplos para no dejar dudas.
@@
 
-\diego{si queda una asociacion directa entre los tipos de lineas y las estructuras de streamer, CH etc entonces usaria esos nombres a continuacion.}\\
-From the equatorial streamer of both rotations, increasing latitudes show decreasing {coronal base} density, and increasing density scale height and electron temperature.
-In both rotations the CH regions are characterized sub-MK temperatures, and coronal base densities of order $\approx 1/2$ of the equatorial streamer.
-Histograms with sharp populations indicates that for both rotations the values of all physical quantities exhibit a strong symmetry between both hemispheres.
-
-A comparison of the results between the two rotations shows that CR-2208 is characterized by lower values (between $11\%\, \rm and\, 16\%$) of coronal base electron density than CR-2082, higher values of density scale height (between $4\%\, \rm and\,19\%$) and higher values of electron temperature (between $6\%\, \rm and\,21\%$).
+%\noindent\diego{Si queda una asociacion directa entre los tipos de lineas y las estructuras de streamer, CH etc entonces usaria esos nombres a continuacion.}\\
+{Throughout} the equatorial streamer of both rotations, {type 0, I and II legs, which are associated to progressively} increasing latitudes, {progressively exhibit} decreasing {coronal base} density, {increasing density scale height, and increasing electron temperature}.
+In both rotations the CH regions are characterized sub-MK temperatures, and coronal base densities of order $\approx 1/2$ of {those observed for the type 0 lines in the core of} the equatorial streamer.
+
+{A comparison of the results between the two rotations shows that compared to CR-2082, target rotation CR-2208 was characterized by $\approx 15-20\%$ lower values of the electron density at the coronal base, $\approx 10-30\%$ larger values of density scale height, and $\approx 15-25\%$ larger values of the electron temperature.}
 
@@
 
-To compare integrated quantities along loops, we select those close loops where both legs meet the requirements of Section \ref{trace}.
-In an analogous way to the legs definition, we will refer to them as loops of type 0, I or II to those whose both legs meeting the criteria.
-When two legs of the same loop have a decreasing temperature with height (type 0), they are called down loops.
+\notebyalbert{Cambié este párrafo.} {To analyze the loop-integrated energy flux quantities, we selected closed loops where both legs meet the requirements of Section \ref{trace}, and both posses the same sign of the radial gradient of the electron temperature $\dr\Tm$.
+In this way, according to the clasification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).}
 
@@
 
-{For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities $\phi_h$, $\phi_r$ and $\phi_c$ in green, blue and red color, respectively.}
-
-Type 0 loops present slightly larger gradients than type I.
+For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.
+\notebyalbert{Notá que puse las cosas en el orden que las cosas se calculan: Eq.
+11, 12, y 10.
+Sugiero que en los histogramas listes los $\phi$ y sus medianas de arriba a abajo en este orden, ya que igual los deberás re-hacer para poner la letra griega $\phi$ (y otros cambios requeridos).}
+
+\notebyalbert{El análisis que había de los $\phi$ no me pareció adecuado, y lo comenté (no lo borré por si querés revisarlo y si ves que se pasó algo).
+Lo que sigue hasta el fin de la sección lo escribí yo mirando el paper de Cecilia y tu Figura, destacando lo que considero más importante.
+Lo hice medio apurato, y requerirá más trabajo.
+Pero para mi esta es la línea.}
+
+{For both rotations, the value of the integrated radiative power $E_r$, measured by the quantity $\phi_r$, progressively decreaces for loops of type 0, I and II.
+This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors cooperating to maximize $E_r$ for loops of type 0 and minimize it for loops of type II.
+As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0, I and II are characterised by progressively decreasing electron density for both rotations.
+Also, in the range of sensitivity of the EUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$.
+According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterised by progressively larger electron temperature, and progressively farther from the value $\Tc$, for both rotations.}
+
+{In the case of the quantity $\phi_c$, its sign depends on that of the conductive flux $F_c$.
+As shown in \citet{maccormack_2017}, down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, which is verified in Figure \ref{energia_demt}.}
+
+{As a result of the radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of loop.
+These values are similar to those reported by \citet{maccormack_2017}.}
+
+%Type 0 loops present slightly larger gradients than type I.
 Therefore, type 0 present bigger amount, in modulus, of loop-integrated conductive flux.
@@
 
-The type I loops show a loop-integrated positive conductive for each loop in both rotations consistent with positive gradients of temperatures.
+%The type I loops show a loop-integrated positive conductive for each loop in both rotations consistent with positive gradients of temperatures.
 The conductive flux have values around 0.3 $10^{5}[\rm{erg\,sec^{-1}\,cm^{-2}}]$ in both rotations.
@@
 \begin{center}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
 \caption{{Statistical distribution of DEMT (blue) and AWSoM (red) results traced along legs of type I, II and III (from top to bottom), as defined in Section 2.3.
@@
 \begin{center}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_Tm.eps}\\
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_Tm.eps}\\
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_Tm.eps}\\
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_Tm.eps}\\
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_Tm.eps}
 \caption{Same as Figure \ref{histos_2082} for CR-2208.}

### 2020-01-02 lloveras_2020_Albert.tex

@@
 
-\albert{As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show \albert{latitude-longitude} maps of DEMT results for both \albert{rotations.
+{As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations.
 Three different heights of interest were selected here, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic results ($1.025\,\mrsun$), one of the lowest heights where the AWSoM results are consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
-Black voxels correspond to non-reconstructed voxels (\albert{see} Section \ref{demt}).
-Thick-black \albert{curves indicate} the magnetic open/closed \albert{boundaries} based on the magnetic field of \albert{the} AWSoM model.
-
-\albert{Target} CR-2082 was highly axisymmetric \albert{(i.e, a high azymuthal symmetry)} and showed two ARs (active region) in latitude $+30\mdeg$ and longitude $50\mdeg$ and $120\mdeg$.
-\albert{Target CR-2208 was much less axisymmetric and it} showed two AR, one around latitude $+5\mdeg$ and longitude $140\mdeg$ and the other around latitude-longitud $+5\mdeg$, $300\mdeg$.
-\albert{In both rotations the open/closed} boundaries derived from the respective AWSoM model \albert{very accurately} match the shape of \albert{contour levels} of the tomographic maps of both the \albert{electron density and temperature.
+Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}).
+Thick-black {curves indicate} the magnetic open/closed {boundaries} based on the magnetic field of {the} AWSoM model.
+
+{Target} CR-2082 was highly axisymmetric {(i.e, a high azymuthal symmetry)} and showed two ARs (active region) in latitude $+30\mdeg$ and longitude $50\mdeg$ and $120\mdeg$.
+{Target CR-2208 was much less axisymmetric and it} showed two AR, one around latitude $+5\mdeg$ and longitude $140\mdeg$ and the other around latitude-longitud $+5\mdeg$, $300\mdeg$.
+{In both rotations the open/closed} boundaries derived from the respective AWSoM model {very accurately} match the shape of {contour levels} of the tomographic maps of both the {electron density and temperature.
 The magneticlly open regions of the AWSoM model are those associated to CHs, and the magnetically closed ones to the equatorial streamer belt.}
 
-\albert{Visual inspection of Figures \ref{momento1} and \ref{momento2} indicates} that the streamer belt region of CR-2082 was denser and colder than CR-2208.
-\albert{In the case of CR-2082, which belongs to the deep minimum epoch between SC2 24/25, the temperature in the equatorial latitudes tends to decrease with height while in the mid-latitudes tends to increase.
-A similar behabiour is seen in CR-2208, belonmging to the declining phase of SC25, but being a much less axisymmetric target this behaviour is not so obvious.
+{Visual inspection of Figures \ref{momento1} and \ref{momento2} indicates} that the streamer belt region of CR-2082 was denser and colder than CR-2208.
+{In the case of CR-2082, which belongs to the deep minimum epoch between SC2 24/25, the temperature in the equatorial latitudes tends to decrease with height while in the mid-latitudes tends to increase.
+A similar behaviour is seen in CR-2208, belonging to the declining phase of SC25, but being a much less axisymmetric target this behaviour is not so obvious.
 This structure of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.} Closed regions are characterized by relatively larger values of density and temperature in comparison to the open regions.
@@
 For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.
-\albert{As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}
+{As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}
 
@@
 
-\albert{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
+{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
 Open legs are indicated in grey color and closed ones in black color.
@@
 Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs are shown in blue, red, violet and green color, respectively.} \albert{Of the 45000 legs selected for CR-2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III.
+Using a four-color code, type 0, I, II and III legs are shown in blue, red, violet and green color, respectively.} {Of the 45000 legs selected for CR-2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III.
 On the other hand, of the 59000 legs selected for CR-2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.}
 
-\albert{Type 0 (small down) legs mainly populate the equatorial latitudes.
+{Type 0 (small down) legs mainly populate the equatorial latitudes.
 This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the SC 24/25 solar minimum by \citet{nuevo_2013}.
 Later on, \citet{lloveras_2017} showed how equatorial down loops in streamers were also to be found in the deep minimum between SCs 23/24.
-Here, we verify the existence of this type of structuire for the two target rotations.
+Here, we verify the existence of this type of structure for the two target rotations.
 The relatively smaller population of down loops seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}.
@@
 
-\notebyalbert{No comprendo esta frase:} \emph{This classification of types of lines automatically leads to specific regions arranged along all longitudes associated with different thermodynamic, with good symmetry between both hemispheres in both rotations.}
+%\notebyalbert{No comprendo esta frase:} \emph{This classification of types of lines automatically leads to specific regions arranged along all longitudes associated with different thermodynamic, with good symmetry between both hemispheres in both rotations.}
 
@@
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
-\caption{\emph{Top panels:} \albert{latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR2082 (left) and CR2208 (right).
+\caption{\emph{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR2082 (left) and CR2208 (right).
 \emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs (see text) are shown in blue, red, violet and green color, respectively.}}
+Using a four-color code, type 0, I, II and III legs (see text) are shown in blue, red, violet and green color, respectively.} \notebyalbert{ (by Albert) The violet color is not distinguishable from the blue one really, they gonna claim this so you better change it now.
+How about ORANGE?
+You can try a light-shade of orange, something that VERY clearly contrasts with the RED.
+Also, ORANGE is better suited, as these type-II loops are also of class UP (while violet suggests DOWN).
+Use then the same color for Figure 5.}}
 \label{rpoint_demt}
@@
 
-\albert{Figure \ref{gradt_demt} shows frequency histograms (normalized to the total amount of selected field lines ) of the temperature radial gradient ($\dr\Tm$) for legs of type 0, I, II and III.} The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs.
-\albert{For both rotations, the median value of $\dr\Tm$ is very similar for each type of leg, being  $\approx -2.5$, $2.3$ and $2.4\,\MK/\mrsun$ for legs of type 0, I and II, respectively.
+{Figure \ref{gradt_demt} shows frequency histograms (normalized to the total amount of selected field lines ) of the temperature radial gradient ($\dr\Tm$) for legs of type 0, I, II and III.} The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs.
+{For both rotations, the median value of $\dr\Tm$ is very similar for each type of leg, being  $\approx -2.5$, $2.3$ and $2.4\,\MK/\mrsun$ for legs of type 0, I and II, respectively.
 The only notable difference between both rotations is the characteristic value $\dr\Tm\approx 4.5\,\MK/\mrsun$ for legs of type III for CR-2208, which is about half that for CR-2082.} \notebyalbert{Estos vaores que informas son medianas o modas?
 (yo especifiqué ``medianas".
-Son efectivamente tan iguales?}
+Son efectivamente tan iguales?}\diego{si, las medianas tienen esos valores.}
 
@@
 \includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
-\caption{Frequency histograms of the temperature radial gradient for the different {four types of legs} shown in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
+\caption{Frequency histograms of the temperature radial gradient for the different {four types of legs} shown in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).
+\notebyalbert{This Figure is still stretched in LaTeX, i.e.
+you are forcing the height and the width.
+Do not do that.
+Set only the width.}}
 \label{gradt_demt}
@@
 
-\albert{Figure \ref{histos_fulldemt} shows} the statistical results of both rotations for all field lines types.
-From top to bottom \albert{results are shown for} type 0 to type III \albert{field lines}.
-From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$ \albert{(the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ \albert{and} $\aTm$, \albert{with the median value $m$ indicated in each plot}.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
+{Figure \ref{histos_fulldemt} shows} the statistical results of both rotations for all field lines types.
+From top to bottom {results are shown for} type 0 to type III {field lines}.
+From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$ {(the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
 \caption{{Statistical distribution of DEMT results traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}.
 From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$.
-Results for target rotations CR2082 and CR2208 are shown in blue and red color, respectively.
-In each panel the median value $m$ is indicated.} \notebyalbert{ (by Albert) The histogram Figures in this draft need to be improved, in particular font size-and-type need to be optimized for clear reading.
-Also, we need to improve their X/Y ratio, here I stretched the Y size a bit in the LaTeX source.} }
+Results for target rotations CR-2082 and CR-2208 are shown in blue and red color, respectively.
+In each panel the median value $m$ is indicated.}}
 \label{histos_fulldemt}
@@
 
-For all type of lines, Table \ref{tabla_demt} \albert{summarizes a} quantitative comparative analysis between the results of the two \albert{target rotations}.
-For CR-2082 quantities are expressed as absoulte values, \albert{while} for CR-2208 they are informed \albert{as a precentual variation} relative to the corresponding results for CR-2082.
+For all type of lines, Table \ref{tabla_demt} {summarizes a} quantitative comparative analysis between the results of the two {target rotations}.
+For CR-2082 quantities are expressed as absoulte values, {while} for CR-2208 they are informed {as a precentual variation} relative to the corresponding results for CR-2082.
 The following major results concerning the structure of each rotation individually and their comparison can be drawn.
@@
 For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.
-\albert{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
+\notebyalbert{ (by Albert) Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
 Doy dos ejemplos para no dejar dudas.
@@
 %\noindent\diego{Si queda una asociacion directa entre los tipos de lineas y las estructuras de streamer, CH etc entonces usaria esos nombres a continuacion.}\\
-\albert{Throughout} the equatorial streamer of both rotations, \albert{type 0, I and II legs, which are associated to progressively} increasing latitudes, \albert{progressively exhibit} decreasing {coronal base} density, \albert{increasing density scale height, and increasing electron temperature}.
-In both rotations the CH regions are characterized sub-MK temperatures, and coronal base densities of order $\approx 1/2$ of \albert{those observed for the type 0 lines in the core of} the equatorial streamer.
-\notebyalbert{No estoy seguro de entender y acordar con la siguiente frase.} \emph{Histograms with sharp populations indicates that for both rotations the values of all physical quantities exhibit a strong symmetry between both hemispheres.}
-
-\notebyalbert{A continuación modifiqué la sintaxis en que esto se explica (creo que para mejor), y puse números acordes a los de la Tabla-1, los que estaban no eran consistentes con ella.} \albert{A comparison of the results between the two rotations shows that compared to CR-2082, target rotation CR-2208 was characterized by $\approx 15-20\%$ lower values of the electron density at the coronal base, $\approx 10-30\%$ larger values of density scale height, and $\approx 15-25\%$ larger values of the electron temperature.}
+{Throughout} the equatorial streamer of both rotations, {type 0, I and II legs, which are associated to progressively} increasing latitudes, {progressively exhibit} decreasing {coronal base} density, {increasing density scale height, and increasing electron temperature}.
+In both rotations the CH regions are characterized sub-MK temperatures, and coronal base densities of order $\approx 1/2$ of {those observed for the type 0 lines in the core of} the equatorial streamer.
+
+{A comparison of the results between the two rotations shows that compared to CR-2082, target rotation CR-2208 was characterized by $\approx 15-20\%$ lower values of the electron density at the coronal base, $\approx 10-30\%$ larger values of density scale height, and $\approx 15-25\%$ larger values of the electron temperature.}
 
@@
 
-\notebyalbert{Cambié este párrafo.} \albert{To analyze the loop-integrated energy flux quantities, we selected closed loops where both legs meet the requirements of Section \ref{trace}, and both posses the same sign of the radial gradient of the electron temperature $\dr\Tm$.
+\notebyalbert{Cambié este párrafo.} {To analyze the loop-integrated energy flux quantities, we selected closed loops where both legs meet the requirements of Section \ref{trace}, and both posses the same sign of the radial gradient of the electron temperature $\dr\Tm$.
 In this way, according to the clasification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).}
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
-\caption{\albert{Sugiero fuertemente que el histograpma de Type 0 tenga xr=[-1,+3] como el resto, creo que quedará claro por qué cuando lean el análisis que hice de esta Figura en el texto.} {Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right).
-From top to bottom, panels show the results for loops of type 0, I and II, which are loops for which both legs meet the criteria from Section \ref{trace}.} \notebyalbert{(by Albert) En el XYOUTS podés poner la letra griega $\phi$ usando los comandos ``!4" y ``!3",  y para que te salga r,c,h como subíndice pero no tan pequeño usá: ``!Dp!N", dónde p=r,c,h.}}
+\caption{{Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right).
+From top to bottom, panels show the results for loops of type 0, I and II, which are loops for which both legs meet the criteria from Section \ref{trace}.} \notebyalbert{(by Albert) Very nice, but it needs slightly larger fonts, they are very tiny.
+You should work out all histograms at the same time and understand what is going on.
+TITLE here is PERFECT, but  XYOUTS and LABELS here are SLIGHTLY small.
+One comment, did you use "!Dp!N", where p=r,c,h, for the XYOUTS?
+Or did you use a "subscript" command.
+If the latter, then try !D instead.}}
 \label{energia_demt}
@@
 
-For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities \albert{$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.
+For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.
 \notebyalbert{Notá que puse las cosas en el orden que las cosas se calculan: Eq.
@@
 
-\albert{For both rotations, the value of the integrated radiative power $E_r$, measured by the quantity $\phi_r$, progressively decreaces for loops of type 0, I and II.
+{For both rotations, the value of the integrated radiative power $E_r$, measured by the quantity $\phi_r$, progressively decreaces for loops of type 0, I and II.
 This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors cooperating to maximize $E_r$ for loops of type 0 and minimize it for loops of type II.
 As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0, I and II are characterised by progressively decreasing electron density for both rotations.
-Also, in the range of sensitivity of the AUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$.
+Also, in the range of sensitivity of the EUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$.
 According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterised by progressively larger electron temperature, and progressively farther from the value $\Tc$, for both rotations.}
 
-\albert{In the case of the quantity $\phi_c$, its sign depends on that of the conductive flux $F_c$.
+{In the case of the quantity $\phi_c$, its sign depends on that of the conductive flux $F_c$.
 As shown in \citet{maccormack_2017}, down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, which is verified in Figure \ref{energia_demt}.}
 
-\albert{As a result of the radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of loop.
+{As a result of the radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of loop.
 These values are similar to those reported by \citet{maccormack_2017}.}
@@
 
-The thermodynamic results of AWSoM are shown in Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208}.
-That is latitude-longitude maps for $\Ne$ and $\Te$ modeled for CR-2082 and CR-2208 at $r=1.025, 1.065$ and $1.105\,\mrsun$.
-The black curve denotes the same open-close boundary showed in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} respectively.
-
-%$r=1.025, 1.065$ and $1.105\,\mrsun$. The black curve denotes the open-close boundary.
-
-A visual inspection of these maps shows that both reconstructions are very axysimmetric for $\Ne$ and $\Te$ as well.
-The closed region is denser and hotter than the open region.
-The density and temperature gradients are maximum in the open-close boundary.
+\albert{Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature, for both rotations.
+These Figures show the results at the same three heights selected for visualisation of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}.
+As in those, thick-black curves indicate the magnetic open/closed boundaries based on the magnetic field of the AWSoM model.
+Visual inspection of these maps shows that the AWSoM model for both rotations is highly axysimmetric, as the tomographic model.}
+
+The density and temperature gradients are maximum in the open-close boundary \albert{Esto no está bien expresado, debés aclarar que te referís a gradientes latitudinales.
+Pero además, no es cierto!, como lo muestra claramente tu Figura 11.
+Esto es interesante.
+Si vos mirás la Figura 11 verás que la O/C boundary si coincide para AMBAS rotaciones y AMBOS hemisferios con el gradiente latitudinal máximo de $\sqravgN$ (i.e., la densidad electrónica de DEMT)!!
+Pero NO con el de ASWoM, coincide co el MINIMO de $N_e$!!
+Primero pensé que podrías haber promediado mal, pero cuando uno hace un ZOOM de los mapas de Carrington de AWSoM se ve clarito que así es.}.
 The open field regions in low latitudes maintain thermodynamic values associated with open regions.
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.pdf}
-\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its legs in types I, II and III. The model does not exhibit legs of type 0.}}
+\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its legs in types I, II and III.
+The model does not exhibit legs of type 0.} \notebyalbert{ (by Albert) Aquí el font-type de paneles superiores e inferiores difieren.
+Deben ser los mismos, y los mismos que en la Figure 4.}}
 \label{rpoint_awsom}
@@
 \caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (red), II (violet), and III (green), for CR-2082 (top panels) and CR-2208 (bottom panels).
-Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.} \notebyalbert{(by Albert): The idea of this Figure is to show how DEMT and AWSoM compare AS A FUNCTION OF HEIGHT, in three distinct types of magnetic structures, and for both rotations.}}
+Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.} \notebyalbert{(by Albert): The idea of this Figure is to show how DEMT and AWSoM compare AS A FUNCTION OF HEIGHT, in three distinct types of magnetic structures, and for both rotations.} \notebyalbert{Las leyendas DEMT y AWSoM están muy pegadas entre sí y muy pegadas al borde superior.
+Además deben decir: 'DEMT: solid-lines', 'AWSoM: dashed-lines'.
+Insisto en usar el mismo Y/X ratio de los perfiles latitudinales.
+Vos podés preferir  que los perfiles (radiales y latitudinales) no tengan igual Y/X ratio que histogramas (yo creo que lucirán mejor de esa forma), pero lo haría algo más cuadrado.}}
 \label{perfiles_promedio}
@@
 DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.
-\albert{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
+\notebyalbert{ (by Albert) Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
 Ejemplo para CR-2082 $\NCB$ de Type-II: $1.0\,(-23\%)$.
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
-\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6.0\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).} \notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the absolute minimum indicates the location of the HCS at this height.
+\caption{Longitude-averaged latitudinal dependence of the AWSoM model wind \albert{speed $V_r$} at $6.0\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).
+\albert{No compendo si es $V$ ó $V_r$, sospecho lo primero, es lo que yo graficaría.
+Además, podés eliminar el XYOUTS en estos.} \notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the absolute minimum indicates the location of the HCS at this height.
 I believe it is interesting to compare these two curves with Figure 10.

### 2020-01-02 lloveras_2020.tex
nuevos graficos

@@
 For the tree types of loops we will show histograms of the DEMT and AWSoM products along field lines.
-This is a LOT of information from which and we need to pull out a few clear conlcusions.}
-
-The thermodynamic results of AWSoM are shown in Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208}.
-That is latitude-longitude maps for $\Ne$ and $\Te$ modeled for CR-2082 and CR-2208 at $r=1.025, 1.065$ and $1.105\,\mrsun$.
-The black curve denotes the same open-close boundary showed in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} respectively.
-
-%$r=1.025, 1.065$ and $1.105\,\mrsun$. The black curve denotes the open-close boundary.
-
-A visual inspection of these maps shows that both reconstructions are very axysimmetric for $\Ne$ and $\Te$ as well.
+This is a LOT of information from which and we need to pull out a few clear conclusions.}
+
+Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature, for both rotations.
+These Figures show the results at the same three heights selected for visualisation of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}.
+As in those, thick-black curves indicate the magnetic open/closed boundaries based on the magnetic field of the AWSoM model.
+Visual inspection of these maps shows that the AWSoM model for both rotations is highly axysimmetric, as the tomographic model.
+
+\diego{A visual inspection of these maps shows that both reconstructions are very axysimmetric for $\Ne$ and $\Te$ as well.
 The closed region is denser and hotter than the open region.
 The density and temperature gradients are maximum in the open-close boundary.
-The open field regions in low latitudes maintain thermodynamic values associated with open regions.
-The reconstruction of CR-2082 does not show clear the ARs, while CR-2208 shows a well reconstruction of both AR around latitude-longitud $+5\mdeg$, $140\mdeg$ and $+5\mdeg$, $300\mdeg$.
+The open field regions in low latitudes maintain thermodynamic values associated with open regions.} The reconstruction of CR-2082 does not show clear the ARs, while CR-2208 shows a well reconstruction of both AR around latitude-longitud $+5\mdeg$, $140\mdeg$ and $+5\mdeg$, $300\mdeg$.
 In both rotations the open-closed boundaries derived from the AWSoM model match the shape of the contour levels of both the electron density and the electron temperature.

### 2020-01-06 lloveras_2020.tex
cambio grande de figuras y seleccion de legs cerrados grandes y chicos

@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_sinfiltro_Rpoint-map.pdf}
 %\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_sinfiltro_Rpoint-map.pdf}
 %\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
@@
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_sinfiltro_Rpoint-map.pdf}
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_sinfiltro_Rpoint-map.pdf}
 \caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its legs in types I, II and III. The model does not exhibit legs of type 0.}}

### 2020-01-07 lloveras_2020.tex
otros cambios imag

--- 2020-01-02 lloveras_2020.tex
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccdownenergia.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccdownenergia.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccenergia.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccenergia.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_cgenergia.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
+\includegraphics[width=0.495\textwidth]{figs/histocr2082_ccdownenergia.eps}
+\includegraphics[width=0.495\textwidth]{figs/histocr2208_ccdownenergia.eps}
+\includegraphics[width=0.495\textwidth]{figs/histocr2082_ccenergia.eps}
+\includegraphics[width=0.495\textwidth]{figs/histocr2208_ccenergia.eps}
+\includegraphics[width=0.495\textwidth]{figs/histocr2082_cgenergia.eps}
+\includegraphics[width=0.495\textwidth]{figs/histocr2208_cgenergia.eps}
 \caption{\albert{Sugiero fuertemente que el histograpma de Type 0 tenga xr=[-1,+3] como el resto, creo que quedará claro por qué cuando lean el análisis que hice de esta Figura en el texto.} {Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right).

### 2020-01-07 lloveras_2020_Albert.tex
..

@@
 
-{To perform a comparative study of the thermodynamic structure of the inner corona in different solar cycles
-we carry out a DEMT reconstruction for two rotations: CR-2082, using STEREO/EUVI data and CR-2208, using SDO/AIA data.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared $\sqravgN$ and the electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}.}
+\albert{As described in Section \ref{demt}, we carried out DEMT reconstructions of the coronal structure for target rotations CR-2082 and CR-2208 using STEREO/EUVI and SDO/AIA data, respectively.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared $\sqravgN$ and the electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}\albert{, and the measure $R$ was calculated by means of Equation (\ref{R}).}}
 
 {As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations.
-Three different heights of interest were selected here, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic results ($1.025\,\mrsun$), one of the lowest heights where the AWSoM results are consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
+Three different heights \albert{of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic results ($1.025\,\mrsun$), \albert{the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
 Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}).
-Thick-black {curves indicate} the magnetic open/closed {boundaries} based on the magnetic field of {the} AWSoM model.
-
-{Target} CR-2082 was highly axisymmetric {(i.e, a high azymuthal symmetry)} and showed two ARs (active region) in latitude $+30\mdeg$ and longitude $50\mdeg$ and $120\mdeg$.
-{Target CR-2208 was much less axisymmetric and it} showed two AR, one around latitude $+5\mdeg$ and longitude $140\mdeg$ and the other around latitude-longitud $+5\mdeg$, $300\mdeg$.
-{In both rotations the open/closed} boundaries derived from the respective AWSoM model {very accurately} match the shape of {contour levels} of the tomographic maps of both the {electron density and temperature.
-The magneticlly open regions of the AWSoM model are those associated to CHs, and the magnetically closed ones to the equatorial streamer belt.}
-
-{Visual inspection of Figures \ref{momento1} and \ref{momento2} indicates} that the streamer belt region of CR-2082 was denser and colder than CR-2208.
-{In the case of CR-2082, which belongs to the deep minimum epoch between SC2 24/25, the temperature in the equatorial latitudes tends to decrease with height while in the mid-latitudes tends to increase.
-A similar behaviour is seen in CR-2208, belonging to the declining phase of SC25, but being a much less axisymmetric target this behaviour is not so obvious.
-This structure of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.} Closed regions are characterized by relatively larger values of density and temperature in comparison to the open regions.
+Thick-black {curves indicate} the \albert{open/closed boundaries of the magnetic field of the} AWSoM model.
 
@@
 
+Target CR-2082 was highly axisymmetric (i.e, \albert{characterized by} a high azymuthal symmetry) and showed two \albert{small} ARs (active \albert{regions), both near latitude} $+30\mdeg$ and \albert{around longitudes} $50\mdeg$ and $120\mdeg$\albert{, respectively}.
+Target CR-2208 was \albert{considerably less axisymmetric and} showed two \albert{ARs, both near latitude} $+5\mdeg$ and \albert{around longitudes $140\mdeg$ and $300\mdeg$, respectively.}
+
+\albert{The magnetically open and closed regions of the AWSoM model are associated to CHs and the the equatorial streamer belt, respectively.
+Consistently with that, the open/closed boundaries derived from the respective AWSoM model quite accurately match the regions which exhibit the strongest latitudinal gradient in the DEMT maps of both the electron density and temperature.}
+
 \begin{figure}[h!]
@@
 \end{figure}
+
+\albert{Visual inspection of Figures \ref{momento1} and \ref{momento2} shows that the DEMT reconstruction of the streamer belt is characterized by relatively larger values of density and temperature in comparison to the CHs.
+They also that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between \albert{SCs 24 and 25}, the temperature in the equatorial latitudes tends to decrease with height while in the mid-latitudes tends to \albert{increase with height}.
+A similar behaviour is seen in CR-2208, belonging to the declining phase of \albert{SC 25, but having a much less axisymmetric structure this characteristic is not so obvious.
+This thermodynamic structure} of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
+
+\albert{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of DEMT measure $R$ defined by Equation (\ref{R}), at the same three heighs shown in Figures \ref{momento1} and \ref{momento2}.
+In most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$.
+The notable exception is to be found in the CHs of the target rotation analyzed based on AIA data.
+A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}.
+This point is further discussed below.}
 
@@
 
-{To study the variation of the DEMT results in different magnetic structures we traced $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.} For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected.
+\albert{To characterize the DEMT results in different magnetic structures, we traced} $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.
+For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected.
 For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.
 {As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}
-
-\noindent\notebyalbert{Quiero destactar el siguiente ejemplo de corrección, todo el párrafo.
-Comparalo con el texto previo para ver cuanto cambió.
-No solo estaba mal escrito sintácticamente, sino que no se conectaba adecuadamente con cada aspecto puntual de la Sección 2.3.
-Fijate que quedó mucho mejor explicado y conectando bien puntualmete con elementos previos de tu paper, lo cual es importante.
-Quizá te sirve para mejorar párrafos puntuales.
-Moví al fin de este párrafo el detalle de los porcentajes de cada población.}
-
-{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
-Open legs are indicated in grey color and closed ones in black color.
-For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}).
-Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs are shown in blue, red, violet and green color, respectively.} {Of the 45000 legs selected for CR-2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III.
-On the other hand, of the 59000 legs selected for CR-2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.}
-
-{Type 0 (small down) legs mainly populate the equatorial latitudes.
-This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the SC 24/25 solar minimum by \citet{nuevo_2013}.
-Later on, \citet{lloveras_2017} showed how equatorial down loops in streamers were also to be found in the deep minimum between SCs 23/24.
-Here, we verify the existence of this type of structure for the two target rotations.
-The relatively smaller population of down loops seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}.
-Type I (small up) mainly populate the mid-latitudes, while type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt.
-Finally, type III (open) legs populate of course the CHs.}
-
-%\notebyalbert{No comprendo esta frase:} \emph{This classification of types of lines automatically leads to specific regions arranged along all longitudes associated with different thermodynamic, with good symmetry between both hemispheres in both rotations.}
 
@@
 \emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs (see text) are shown in blue, red, violet and green color, respectively.} \notebyalbert{ (by Albert) The violet color is not distinguishable from the blue one really, they gonna claim this so you better change it now.
-How about ORANGE?
-You can try a light-shade of orange, something that VERY clearly contrasts with the RED.
-Also, ORANGE is better suited, as these type-II loops are also of class UP (while violet suggests DOWN).
-Use then the same color for Figure 5.}}
+Using a four-color code, type 0, I, II and III legs (see text) are shown in blue, red, violet and green color, respectively.}}
 \label{rpoint_demt}
@@
 
-{Figure \ref{gradt_demt} shows frequency histograms (normalized to the total amount of selected field lines ) of the temperature radial gradient ($\dr\Tm$) for legs of type 0, I, II and III.} The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs.
-{For both rotations, the median value of $\dr\Tm$ is very similar for each type of leg, being  $\approx -2.5$, $2.3$ and $2.4\,\MK/\mrsun$ for legs of type 0, I and II, respectively.
-The only notable difference between both rotations is the characteristic value $\dr\Tm\approx 4.5\,\MK/\mrsun$ for legs of type III for CR-2208, which is about half that for CR-2082.} \notebyalbert{Estos vaores que informas son medianas o modas?
-(yo especifiqué ``medianas".
-Son efectivamente tan iguales?}\diego{si, las medianas tienen esos valores.}
-
-%\temp{mostrar los gradientes negativos va a ser util en los parrafos posteriores que expliquen porque en las lineas tipo 0 hay valores de $\phi_c$ negativos.}
-
-%\temp{ Comentar en la discusion el paper de shift y cramer, para decir un poco sobre los down y la incapacidad del modelo en reproducirlos}
+{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
+Open legs are indicated in grey color and closed ones in black color.
+For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}).
+Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
+Using a four-color code, type 0, I, II and III legs are shown in blue, red, \albert{magenta and cyan} color, respectively.} {Of the 45000 legs selected for CR-2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III.
+On the other hand, of the 59000 legs selected for CR-2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.} \notebyalbert{Los números deben ser actualizados, o la frase eliminada.}
+
+{Type 0 (small down) legs mainly populate the equatorial latitudes.
+This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level \albert{around the solar minimum beween SCs 24 and 25} by \citet{nuevo_2013}.
+Later on, \citet{lloveras_2017} showed \albert{that} equatorial down loops in streamers were also to be found in the deep minimum between SCs \albert{23 and 24}.
+Here, we verify the existence of this type of structure for the two target rotations.
+The relatively smaller population of down loops seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}.
+Type I (small up) mainly populate the mid-latitudes, while type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt.
+Finally, type III (open) legs populate of course the CHs.}
+
+%\notebyalbert{No comprendo esta frase:} \emph{This classification of types of lines automatically leads to specific regions arranged along all longitudes associated with different thermodynamic, with good symmetry between both hemispheres in both rotations.}
 
@@
 \includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
-\caption{Frequency histograms of the temperature radial gradient for the different {four types of legs} shown in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).
-\notebyalbert{This Figure is still stretched in LaTeX, i.e.
-you are forcing the height and the width.
-Do not do that.
-Set only the width.}}
+\caption{Frequency histograms of the temperature radial gradient for the different {four types of legs} shown in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
 \label{gradt_demt}
@@
 
-{Figure \ref{histos_fulldemt} shows} the statistical results of both rotations for all field lines types.
-From top to bottom {results are shown for} type 0 to type III {field lines}.
-From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$ {(the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.
+Figure \ref{gradt_demt} shows frequency histograms (normalized to the total amount of selected field lines ) of the temperature radial gradient ($\dr\Tm$) for legs of type 0, I, II and III.
+The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs.
+For both rotations, \albert{the median value of the temperature radial gradient is ${\rm Md}\left(\dr\Tm\right) \approx -2.5$, $+2.3$ and $+2.4\,\MK/\mrsun$} for legs of type 0, I and II, respectively.
+
+\albert{The notable difference between both rotations is the characteristic \albert{value ${\rm Md}\left(\dr\Tm\right)\approx +4.5\,\MK/\mrsun$} for legs of type III for CR-2208.
+This is related to the much larger $R$ score for the DEMT results along CH legs for CR-2208.
+In this case, DEMT performs poorly in modeling a LDEM that predicts the tomographic FBEs with reasonable accuracy.
+Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, shows that in most of the CH region the results for $\Tm$ below height $1.105\,\mrsun$ are quite uniform and artificially low.
+As it turns out, around and above height this height the score $R$ is lower and the temperature results are more reliable.
+As a result, the temperature gradient along these legs is artificially larger, with the linear fit trying to simultaneously fit the artificially low values of $\Tm$ at lower heights.
+In general, the DEMT results in the CH region based on AIA data are thus much less reliable than in the rest of the analysis.
+We will return to this point in the conclusion section.}
+
+%\temp{mostrar los gradientes negativos va a ser util en los parrafos posteriores que expliquen porque en las lineas tipo 0 hay valores de $\phi_c$ negativos.}
+
+%\temp{ Comentar en la discusion el paper de shift y cramer, para decir un poco sobre los down y la incapacidad del modelo en reproducirlos}
 
@@
 Results for target rotations CR-2082 and CR-2208 are shown in blue and red color, respectively.
-In each panel the median value $m$ is indicated.}}
+In each panel the median value $m$ is indicated.} }
 \label{histos_fulldemt}
@@
 
-For all type of lines, Table \ref{tabla_demt} {summarizes a} quantitative comparative analysis between the results of the two {target rotations}.
+\albert{For both rotations, Figure \ref{histos_fulldemt} shows, in a statistical fashion, the DEMT results traced along field lines discriminated by field line type}.
+From top to bottom {results are shown for} type 0 to type III {field lines}\albert{, respectively}.
+From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$ {(the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.
+
+\albert{Table \ref{tabla_demt} summarizes a} quantitative comparative analysis between the results of the two {target rotations}.
 For CR-2082 quantities are expressed as absoulte values, {while} for CR-2208 they are informed {as a precentual variation} relative to the corresponding results for CR-2082.
-The following major results concerning the structure of each rotation individually and their comparison can be drawn.
-
-\begin{table}
+\albert{The following major results, both concerning the structure of each rotation individually as well as their comparison, can be drawn.}
+
+\begin{table}[h!]
 \begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
@@
 For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.
-\notebyalbert{ (by Albert) Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
+\notebyalbert{Propongo que para todas las cantidades absolutas de la Tabla 1 informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
 Doy dos ejemplos para no dejar dudas.
@@
 
-%\noindent\diego{Si queda una asociacion directa entre los tipos de lineas y las estructuras de streamer, CH etc entonces usaria esos nombres a continuacion.}\\
-{Throughout} the equatorial streamer of both rotations, {type 0, I and II legs, which are associated to progressively} increasing latitudes, {progressively exhibit} decreasing {coronal base} density, {increasing density scale height, and increasing electron temperature}.
-In both rotations the CH regions are characterized sub-MK temperatures, and coronal base densities of order $\approx 1/2$ of {those observed for the type 0 lines in the core of} the equatorial streamer.
-
-{A comparison of the results between the two rotations shows that compared to CR-2082, target rotation CR-2208 was characterized by $\approx 15-20\%$ lower values of the electron density at the coronal base, $\approx 10-30\%$ larger values of density scale height, and $\approx 15-25\%$ larger values of the electron temperature.}
+\albert{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer regions of the equatorial streamer belt, progressively exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature.
+In both rotations also, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.}
+
+{A comparison of the results between the two rotations shows that, compared to CR-2082, target rotation CR-2208 was characterized by $\approx 15-20\%$ lower values of the electron density at the coronal base, $\approx 10-30\%$ larger values of density scale height, and $\approx 15-25\%$ larger values of the electron temperature.} \notebyalbert{Los números de esta frase deben ser consistentes con los que finalmente informe la Table 1, redondeando los rangos característicos observados para los diversos tipos de línea (consultame!).
+La Table 1 debe a su vez resumir lo que muestra la Figure 6.
+Destacalo en tu color cuando lo hayas hecho así le presto atención.}
 
@@
 
-\notebyalbert{Cambié este párrafo.} {To analyze the loop-integrated energy flux quantities, we selected closed loops where both legs meet the requirements of Section \ref{trace}, and both posses the same sign of the radial gradient of the electron temperature $\dr\Tm$.
-In this way, according to the clasification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).}
+\albert{To analyze the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the clasification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).
+\albert{For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.}
 
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccdownenergia.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccdownenergia.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccenergia.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccenergia.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_cgenergia.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
+\includegraphics[width=0.495\textwidth]{figs/histocr2082_ccdownenergia.eps}
+\includegraphics[width=0.495\textwidth]{figs/histocr2208_ccdownenergia.eps}
+\includegraphics[width=0.495\textwidth]{figs/histocr2082_ccenergia.eps}
+\includegraphics[width=0.495\textwidth]{figs/histocr2208_ccenergia.eps}
+\includegraphics[width=0.495\textwidth]{figs/histocr2082_cgenergia.eps}
+\includegraphics[width=0.495\textwidth]{figs/histocr2208_cgenergia.eps}
 \caption{{Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right).
-From top to bottom, panels show the results for loops of type 0, I and II, which are loops for which both legs meet the criteria from Section \ref{trace}.} \notebyalbert{(by Albert) Very nice, but it needs slightly larger fonts, they are very tiny.
-You should work out all histograms at the same time and understand what is going on.
-TITLE here is PERFECT, but  XYOUTS and LABELS here are SLIGHTLY small.
-One comment, did you use "!Dp!N", where p=r,c,h, for the XYOUTS?
-Or did you use a "subscript" command.
-If the latter, then try !D instead.}}
+From top to bottom, panels show the results for loops of type 0, I and II, which are loops for which both legs meet the criteria from Section \ref{trace}.}}
 \label{energia_demt}
@@
 
-For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.
-\notebyalbert{Notá que puse las cosas en el orden que las cosas se calculan: Eq.
-11, 12, y 10.
-Sugiero que en los histogramas listes los $\phi$ y sus medianas de arriba a abajo en este orden, ya que igual los deberás re-hacer para poner la letra griega $\phi$ (y otros cambios requeridos).}
-
-\notebyalbert{El análisis que había de los $\phi$ no me pareció adecuado, y lo comenté (no lo borré por si querés revisarlo y si ves que se pasó algo).
-Lo que sigue hasta el fin de la sección lo escribí yo mirando el paper de Cecilia y tu Figura, destacando lo que considero más importante.
-Lo hice medio apurato, y requerirá más trabajo.
-Pero para mi esta es la línea.}
-
-{For both rotations, the value of the integrated radiative power $E_r$, measured by the quantity $\phi_r$, progressively decreaces for loops of type 0, I and II.
-This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors cooperating to maximize $E_r$ for loops of type 0 and minimize it for loops of type II.
-As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0, I and II are characterised by progressively decreasing electron density for both rotations.
+\albert{For both rotations, the value of the integrated radiative power $E_r$, measured by the quantity $\phi_r$, is largest for loops of type 0.
+This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors contributing to maximize $E_r$ for loops of type 0.
+As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0 are characterised by the relatively largest values of electron density.
 Also, in the range of sensitivity of the EUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$.
-According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterised by progressively larger electron temperature, and progressively farther from the value $\Tc$, for both rotations.}
+According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterised by \albert{values of temperature that are progressively larger and farther} from the value $\Tc$, for both rotations.}
 
@@
 
-{As a result of the radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of loop.
-These values are similar to those reported by \citet{maccormack_2017}.}
+\albert{As a result of the radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of loop.
+These values are similar to those reported by \citet{maccormack_2017}.
+Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$.
+As shown by \citet{maccormack_2017}, this result affects only the smallest loops (a subset of the type 0 class) and it is due to the limited temperature sensitivity of the instrumental passbands.
+The radiative loss term is calculated based on plasma emission detected by the three coronal bands of EUVI and the three bands of AIA used.
+Though this should account for most of the coronal plasma, there surely is additional emission that is out of the range of sensitivity of the instruments used.
+Thus, the positive term $\phi_r$ is most liekly understimated, leading to values $\phi_h<0$ in loops of type 0, which are characterized by $\phi_c<0$.}
 
@@
 For the tree types of loops we will show histograms of the DEMT and AWSoM products along field lines.
-This is a LOT of information from which and we need to pull out a few clear conlcusions.}
-
-\albert{Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature, for both rotations.
+This is a LOT of information from which and we need to pull out a few clear conclusions.}
+
+Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature, for both rotations.
 These Figures show the results at the same three heights selected for visualisation of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}.
 As in those, thick-black curves indicate the magnetic open/closed boundaries based on the magnetic field of the AWSoM model.
-Visual inspection of these maps shows that the AWSoM model for both rotations is highly axysimmetric, as the tomographic model.}
-
-The density and temperature gradients are maximum in the open-close boundary \albert{Esto no está bien expresado, debés aclarar que te referís a gradientes latitudinales.
-Pero además, no es cierto!, como lo muestra claramente tu Figura 11.
-Esto es interesante.
-Si vos mirás la Figura 11 verás que la O/C boundary si coincide para AMBAS rotaciones y AMBOS hemisferios con el gradiente latitudinal máximo de $\sqravgN$ (i.e., la densidad electrónica de DEMT)!!
-Pero NO con el de ASWoM, coincide co el MINIMO de $N_e$!!
-Primero pensé que podrías haber promediado mal, pero cuando uno hace un ZOOM de los mapas de Carrington de AWSoM se ve clarito que así es.}.
-The open field regions in low latitudes maintain thermodynamic values associated with open regions.
-The reconstruction of CR-2082 does not show clear the ARs, while CR-2208 shows a well reconstruction of both AR around latitude-longitud $+5\mdeg$, $140\mdeg$ and $+5\mdeg$, $300\mdeg$.
+Visual inspection of these maps shows that the AWSoM model for both rotations is highly axysimmetric, as the tomographic model.
+
+\diego{A visual inspection of these maps shows that both reconstructions are very axysimmetric for $\Ne$ and $\Te$ as well.
+The closed region is denser and hotter than the open region.
+The density and temperature gradients are maximum in the open-close boundary.
+The open field regions in low latitudes maintain thermodynamic values associated with open regions.} The reconstruction of CR-2082 does not show clear the ARs, while CR-2208 shows a well reconstruction of both AR around latitude-longitud $+5\mdeg$, $140\mdeg$ and $+5\mdeg$, $300\mdeg$.
 In both rotations the open-closed boundaries derived from the AWSoM model match the shape of the contour levels of both the electron density and the electron temperature.
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.pdf}
-\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its legs in types I, II and III.
-The model does not exhibit legs of type 0.} \notebyalbert{ (by Albert) Aquí el font-type de paneles superiores e inferiores difieren.
-Deben ser los mismos, y los mismos que en la Figure 4.}}
+\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its legs in types I, II and III. The model does not exhibit legs of type 0.}}
 \label{rpoint_awsom}
@@
 \caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (red), II (violet), and III (green), for CR-2082 (top panels) and CR-2208 (bottom panels).
-Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.} \notebyalbert{(by Albert): The idea of this Figure is to show how DEMT and AWSoM compare AS A FUNCTION OF HEIGHT, in three distinct types of magnetic structures, and for both rotations.} \notebyalbert{Las leyendas DEMT y AWSoM están muy pegadas entre sí y muy pegadas al borde superior.
-Además deben decir: 'DEMT: solid-lines', 'AWSoM: dashed-lines'.
-Insisto en usar el mismo Y/X ratio de los perfiles latitudinales.
-Vos podés preferir  que los perfiles (radiales y latitudinales) no tengan igual Y/X ratio que histogramas (yo creo que lucirán mejor de esa forma), pero lo haría algo más cuadrado.}}
+Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.} \notebyalbert{(by Albert): The idea of this Figure is to show how DEMT and AWSoM compare AS A FUNCTION OF HEIGHT, in three distinct types of magnetic structures, and for both rotations.}}
 \label{perfiles_promedio}
@@
 DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.
-\notebyalbert{ (by Albert) Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
+\albert{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
 Ejemplo para CR-2082 $\NCB$ de Type-II: $1.0\,(-23\%)$.
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
-\caption{Longitude-averaged latitudinal dependence of the AWSoM model wind \albert{speed $V_r$} at $6.0\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).
-\albert{No compendo si es $V$ ó $V_r$, sospecho lo primero, es lo que yo graficaría.
-Además, podés eliminar el XYOUTS en estos.} \notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the absolute minimum indicates the location of the HCS at this height.
+\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6.0\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).} \notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the absolute minimum indicates the location of the HCS at this height.
 I believe it is interesting to compare these two curves with Figure 10.

### 2020-01-08 lloveras_2020.tex
lloveras_2020.tex

@@
 
-{To perform a comparative study of the thermodynamic structure of the inner corona in different solar cycles
-we carry out a DEMT reconstruction for two rotations: CR-2082, using STEREO/EUVI data and CR-2208, using SDO/AIA data.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared $\sqravgN$ and the electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}.}
+{As described in Section \ref{demt}, we carried out DEMT reconstructions of the coronal structure for target rotations CR-2082 and CR-2208 using STEREO/EUVI and SDO/AIA data, respectively.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared $\sqravgN$ and the electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}{, and the measure $R$ was calculated by means of Equation (\ref{R}).}}
 
 {As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations.
-Three different heights of interest were selected here, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic results ($1.025\,\mrsun$), one of the lowest heights where the AWSoM results are consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
+Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic results ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
 Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}).
-Thick-black {curves indicate} the magnetic open/closed {boundaries} based on the magnetic field of {the} AWSoM model.
-
-{Target} CR-2082 was highly axisymmetric {(i.e, a high azymuthal symmetry)} and showed two ARs (active region) in latitude $+30\mdeg$ and longitude $50\mdeg$ and $120\mdeg$.
-{Target CR-2208 was much less axisymmetric and it} showed two AR, one around latitude $+5\mdeg$ and longitude $140\mdeg$ and the other around latitude-longitud $+5\mdeg$, $300\mdeg$.
-{In both rotations the open/closed} boundaries derived from the respective AWSoM model {very accurately} match the shape of {contour levels} of the tomographic maps of both the {electron density and temperature.
-The magneticlly open regions of the AWSoM model are those associated to CHs, and the magnetically closed ones to the equatorial streamer belt.}
-
-{Visual inspection of Figures \ref{momento1} and \ref{momento2} indicates} that the streamer belt region of CR-2082 was denser and colder than CR-2208.
-{In the case of CR-2082, which belongs to the deep minimum epoch between SC2 24/25, the temperature in the equatorial latitudes tends to decrease with height while in the mid-latitudes tends to increase.
-A similar behaviour is seen in CR-2208, belonging to the declining phase of SC25, but being a much less axisymmetric target this behaviour is not so obvious.
-This structure of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.} Closed regions are characterized by relatively larger values of density and temperature in comparison to the open regions.
+Thick-black {curves indicate} the {open/closed boundaries of the magnetic field of the} AWSoM model.
 
@@
 
+Target CR-2082 was highly axisymmetric (i.e, {characterized by} a high azymuthal symmetry) and showed two {small} ARs (active {regions), both near latitude} $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg${, respectively}.
+Target CR-2208 was {considerably less axisymmetric and} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$, respectively.}
+
+{The magnetically open and closed regions of the AWSoM model are associated to CHs and the the equatorial streamer belt, respectively.
+Consistently with that, the open/closed boundaries derived from the respective AWSoM model quite accurately match the regions which exhibit the strongest latitudinal gradient in the DEMT maps of both the electron density and temperature.}
+
 \begin{figure}[h!]
@@
 \end{figure}
+
+{Visual inspection of Figures \ref{momento1} and \ref{momento2} shows that the DEMT reconstruction of the streamer belt is characterized by relatively larger values of density and temperature in comparison to the CHs.
+They also that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 24 and 25}, the temperature in the equatorial latitudes tends to decrease with height while in the mid-latitudes tends to {increase with height}.
+A similar behaviour is seen in CR-2208, belonging to the declining phase of {SC 25, but having a much less axisymmetric structure this characteristic is not so obvious.
+This thermodynamic structure} of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
+
+{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of DEMT measure $R$ defined by Equation (\ref{R}), at the same three heighs shown in Figures \ref{momento1} and \ref{momento2}.
+In most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$.
+The notable exception is to be found in the CHs of the target rotation analyzed based on AIA data.
+A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}.
+This point is further discussed below.}
 
@@
 
-{To study the variation of the DEMT results in different magnetic structures we traced $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.} For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected.
+{To characterize the DEMT results in different magnetic structures, we traced} $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.
+For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected.
 For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.
 {As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}
-
-\noindent\notebyalbert{Quiero destactar el siguiente ejemplo de corrección, todo el párrafo.
-Comparalo con el texto previo para ver cuanto cambió.
-No solo estaba mal escrito sintácticamente, sino que no se conectaba adecuadamente con cada aspecto puntual de la Sección 2.3.
-Fijate que quedó mucho mejor explicado y conectando bien puntualmete con elementos previos de tu paper, lo cual es importante.
-Quizá te sirve para mejorar párrafos puntuales.
-Moví al fin de este párrafo el detalle de los porcentajes de cada población.}
-
-{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
-Open legs are indicated in grey color and closed ones in black color.
-For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}).
-Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs are shown in blue, red, violet and green color, respectively.} {Of the 45000 legs selected for CR-2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III.
-On the other hand, of the 59000 legs selected for CR-2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.}
-
-{Type 0 (small down) legs mainly populate the equatorial latitudes.
-This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the SC 24/25 solar minimum by \citet{nuevo_2013}.
-Later on, \citet{lloveras_2017} showed how equatorial down loops in streamers were also to be found in the deep minimum between SCs 23/24.
-Here, we verify the existence of this type of structure for the two target rotations.
-The relatively smaller population of down loops seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}.
-Type I (small up) mainly populate the mid-latitudes, while type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt.
-Finally, type III (open) legs populate of course the CHs.}
-
-%\notebyalbert{No comprendo esta frase:} \emph{This classification of types of lines automatically leads to specific regions arranged along all longitudes associated with different thermodynamic, with good symmetry between both hemispheres in both rotations.}
 
@@
 
-{Figure \ref{gradt_demt} shows frequency histograms (normalized to the total amount of selected field lines ) of the temperature radial gradient ($\dr\Tm$) for legs of type 0, I, II and III.} The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs.
-{For both rotations, the median value of $\dr\Tm$ is very similar for each type of leg, being  $\approx -2.5$, $2.3$ and $2.4\,\MK/\mrsun$ for legs of type 0, I and II, respectively.
-The only notable difference between both rotations is the characteristic value $\dr\Tm\approx 4.5\,\MK/\mrsun$ for legs of type III for CR-2208, which is about half that for CR-2082.} \notebyalbert{Estos vaores que informas son medianas o modas?
-(yo especifiqué ``medianas".
-Son efectivamente tan iguales?}\diego{si, las medianas tienen esos valores.}
-
-%\temp{mostrar los gradientes negativos va a ser util en los parrafos posteriores que expliquen porque en las lineas tipo 0 hay valores de $\phi_c$ negativos.}
-
-%\temp{ Comentar en la discusion el paper de shift y cramer, para decir un poco sobre los down y la incapacidad del modelo en reproducirlos}
+{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
+Open legs are indicated in grey color and closed ones in black color.
+For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}).
+Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
+Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} {Of the 45000 legs selected for CR-2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III.
+On the other hand, of the 59000 legs selected for CR-2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.} \notebyalbert{Los números deben ser actualizados, o la frase eliminada.}
+
+{Type 0 (small down) legs mainly populate the equatorial latitudes.
+This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level {around the solar minimum beween SCs 24 and 25} by \citet{nuevo_2013}.
+Later on, \citet{lloveras_2017} showed {that} equatorial down loops in streamers were also to be found in the deep minimum between SCs {23 and 24}.
+Here, we verify the existence of this type of structure for the two target rotations.
+The relatively smaller population of down loops seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}.
+Type I (small up) mainly populate the mid-latitudes, while type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt.
+Finally, type III (open) legs populate of course the CHs.}
+
+%\notebyalbert{No comprendo esta frase:} \emph{This classification of types of lines automatically leads to specific regions arranged along all longitudes associated with different thermodynamic, with good symmetry between both hemispheres in both rotations.}
 
@@
 
-{Figure \ref{histos_fulldemt} shows} the statistical results of both rotations for all field lines types.
-From top to bottom {results are shown for} type 0 to type III {field lines}.
-From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$ {(the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.
+Figure \ref{gradt_demt} shows frequency histograms (normalized to the total amount of selected field lines ) of the temperature radial gradient ($\dr\Tm$) for legs of type 0, I, II and III.
+The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs.
+For both rotations, {the median value of the temperature radial gradient is ${\rm Md}\left(\dr\Tm\right) \approx -2.5$, $+2.3$ and $+2.4\,\MK/\mrsun$} for legs of type 0, I and II, respectively.
+
+{The notable difference between both rotations is the characteristic {value ${\rm Md}\left(\dr\Tm\right)\approx +4.5\,\MK/\mrsun$} for legs of type III for CR-2208.
+This is related to the much larger $R$ score for the DEMT results along CH legs for CR-2208.
+In this case, DEMT performs poorly in modeling a LDEM that predicts the tomographic FBEs with reasonable accuracy.
+Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, shows that in most of the CH region the results for $\Tm$ below height $1.105\,\mrsun$ are quite uniform and artificially low.
+As it turns out, around and above height this height the score $R$ is lower and the temperature results are more reliable.
+As a result, the temperature gradient along these legs is artificially larger, with the linear fit trying to simultaneously fit the artificially low values of $\Tm$ at lower heights.
+In general, the DEMT results in the CH region based on AIA data are thus much less reliable than in the rest of the analysis.
+We will return to this point in the conclusion section.}
+
+%\temp{mostrar los gradientes negativos va a ser util en los parrafos posteriores que expliquen porque en las lineas tipo 0 hay valores de $\phi_c$ negativos.}
+
+%\temp{ Comentar en la discusion el paper de shift y cramer, para decir un poco sobre los down y la incapacidad del modelo en reproducirlos}
 
@@
 Results for target rotations CR-2082 and CR-2208 are shown in blue and red color, respectively.
-In each panel the median value $m$ is indicated.} \notebyalbert{ (by Albert) The histogram Figures in this draft need to be improved, in particular font size-and-type need to be optimized for clear reading.
-Also, we need to improve their X/Y ratio, here I stretched the Y size a bit in the LaTeX source.} }
+In each panel the median value $m$ is indicated.} }
 \label{histos_fulldemt}
@@
 
-For all type of lines, Table \ref{tabla_demt} {summarizes a} quantitative comparative analysis between the results of the two {target rotations}.
+{For both rotations, Figure \ref{histos_fulldemt} shows, in a statistical fashion, the DEMT results traced along field lines discriminated by field line type}.
+From top to bottom {results are shown for} type 0 to type III {field lines}{, respectively}.
+From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$ {(the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.
+
+{Table \ref{tabla_demt} summarizes a} quantitative comparative analysis between the results of the two {target rotations}.
 For CR-2082 quantities are expressed as absoulte values, {while} for CR-2208 they are informed {as a precentual variation} relative to the corresponding results for CR-2082.
-The following major results concerning the structure of each rotation individually and their comparison can be drawn.
-
-\begin{table}
+{The following major results, both concerning the structure of each rotation individually as well as their comparison, can be drawn.}
+
+\begin{table}[h!]
 \begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
@@
 For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.
-{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
+\notebyalbert{Propongo que para todas las cantidades absolutas de la Tabla 1 informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
 Doy dos ejemplos para no dejar dudas.
@@
 
-%\noindent\diego{Si queda una asociacion directa entre los tipos de lineas y las estructuras de streamer, CH etc entonces usaria esos nombres a continuacion.}\\
-{Throughout} the equatorial streamer of both rotations, {type 0, I and II legs, which are associated to progressively} increasing latitudes, {progressively exhibit} decreasing {coronal base} density, {increasing density scale height, and increasing electron temperature}.
-In both rotations the CH regions are characterized sub-MK temperatures, and coronal base densities of order $\approx 1/2$ of {those observed for the type 0 lines in the core of} the equatorial streamer.
-
-{A comparison of the results between the two rotations shows that compared to CR-2082, target rotation CR-2208 was characterized by $\approx 15-20\%$ lower values of the electron density at the coronal base, $\approx 10-30\%$ larger values of density scale height, and $\approx 15-25\%$ larger values of the electron temperature.}
+{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer regions of the equatorial streamer belt, progressively exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature.
+In both rotations also, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.}
+
+{A comparison of the results between the two rotations shows that, compared to CR-2082, target rotation CR-2208 was characterized by $\approx 15-20\%$ lower values of the electron density at the coronal base, $\approx 10-30\%$ larger values of density scale height, and $\approx 15-25\%$ larger values of the electron temperature.} \notebyalbert{Los números de esta frase deben ser consistentes con los que finalmente informe la Table 1, redondeando los rangos característicos observados para los diversos tipos de línea (consultame!).
+La Table 1 debe a su vez resumir lo que muestra la Figure 6.
+Destacalo en tu color cuando lo hayas hecho así le presto atención.}
 
@@
 
-\notebyalbert{Cambié este párrafo.} {To analyze the loop-integrated energy flux quantities, we selected closed loops where both legs meet the requirements of Section \ref{trace}, and both posses the same sign of the radial gradient of the electron temperature $\dr\Tm$.
-In this way, according to the clasification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).}
+{To analyze the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the clasification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).
+{For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.}
 
@@
 \includegraphics[width=0.495\textwidth]{figs/histocr2208_cgenergia.eps}
-\caption{\albert{Sugiero fuertemente que el histograpma de Type 0 tenga xr=[-1,+3] como el resto, creo que quedará claro por qué cuando lean el análisis que hice de esta Figura en el texto.} {Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right).
-From top to bottom, panels show the results for loops of type 0, I and II, which are loops for which both legs meet the criteria from Section \ref{trace}.} \notebyalbert{(by Albert) En el XYOUTS podés poner la letra griega $\phi$ usando los comandos ``!4" y ``!3",  y para que te salga r,c,h como subíndice pero no tan pequeño usá: ``!Dp!N", dónde p=r,c,h.}}
+\caption{{Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right).
+From top to bottom, panels show the results for loops of type 0, I and II, which are loops for which both legs meet the criteria from Section \ref{trace}.}}
 \label{energia_demt}
@@
 
-For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.
-\notebyalbert{Notá que puse las cosas en el orden que las cosas se calculan: Eq.
-11, 12, y 10.
-Sugiero que en los histogramas listes los $\phi$ y sus medianas de arriba a abajo en este orden, ya que igual los deberás re-hacer para poner la letra griega $\phi$ (y otros cambios requeridos).}
-
-\notebyalbert{El análisis que había de los $\phi$ no me pareció adecuado, y lo comenté (no lo borré por si querés revisarlo y si ves que se pasó algo).
-Lo que sigue hasta el fin de la sección lo escribí yo mirando el paper de Cecilia y tu Figura, destacando lo que considero más importante.
-Lo hice medio apurato, y requerirá más trabajo.
-Pero para mi esta es la línea.}
-
-{For both rotations, the value of the integrated radiative power $E_r$, measured by the quantity $\phi_r$, progressively decreaces for loops of type 0, I and II.
-This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors cooperating to maximize $E_r$ for loops of type 0 and minimize it for loops of type II.
-As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0, I and II are characterised by progressively decreasing electron density for both rotations.
+{For both rotations, the value of the integrated radiative power $E_r$, measured by the quantity $\phi_r$, is largest for loops of type 0.
+This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors contributing to maximize $E_r$ for loops of type 0.
+As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0 are characterised by the relatively largest values of electron density.
 Also, in the range of sensitivity of the EUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$.
-According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterised by progressively larger electron temperature, and progressively farther from the value $\Tc$, for both rotations.}
+According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterised by {values of temperature that are progressively larger and farther} from the value $\Tc$, for both rotations.}
 
@@
 {As a result of the radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of loop.
-These values are similar to those reported by \citet{maccormack_2017}.}
+These values are similar to those reported by \citet{maccormack_2017}.
+Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$.
+As shown by \citet{maccormack_2017}, this result affects only the smallest loops (a subset of the type 0 class) and it is due to the limited temperature sensitivity of the instrumental passbands.
+The radiative loss term is calculated based on plasma emission detected by the three coronal bands of EUVI and the three bands of AIA used.
+Though this should account for most of the coronal plasma, there surely is additional emission that is out of the range of sensitivity of the instruments used.
+Thus, the positive term $\phi_r$ is most liekly understimated, leading to values $\phi_h<0$ in loops of type 0, which are characterized by $\phi_c<0$.}
 

### 2020-01-10 lloveras_2020_Albert.tex
Nueva Section 2.3, 3.1 y 3.2, by Albert

@@
 Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24.
-Tomographic reconstructions and results of the model are analyzed in distinct coronal magnetic structures.
+Tomographic reconstructions and results of the model are \albert{analysed} in distinct coronal magnetic structures.
 We study magnetically closed structures associated with the equatorial streamer belt, as well as magnetically open regions enclosing it.
@@
 
-For the two targeted rotations, DEMT and AWSoM results were traced along the AWSoM field lines, which provides a way to characterize the global thermodynamic state of the inner solar corona and to compare them.
-To that end four different types of {legs} corresponding with four different types of magnetic structures were selected:
-%\temp{Hacer explicacion de los tipos de lineas bien secos, luego en fig 3 hacer notar que implica cada una en cuanto a estructura magnetica}\\
+\albert{Coronal magnetic structures for which their temperature increases/decreases with height (in the inner corona) have been dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies.
+As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
+Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}.
+In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}
+
+\albert{To characterize the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model.
+Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types in this work:}
+
+\diego{Hice las definiciones con gradiente de temperatura para que quede mas claro, pero en realidad uso el pearson.} \notebyalbert{Charlemos los tres en persona de esto.}
 
@@
 \end{itemize}
-\diego{Hice las definiciones con gradiente de temperatura para que quede mas claro, pero en realidad uso el pearson.} \notebyalbert{Charlemos los tres en persona de esto.}
+
+\albert{In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed.}
 
@@
 
-\albert{As described in Section \ref{demt}, we carried out DEMT reconstructions of the coronal structure for target rotations CR-2082 and CR-2208 using STEREO/EUVI and SDO/AIA data, respectively.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared $\sqravgN$ and the electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}\albert{, and the measure $R$ was calculated by means of Equation (\ref{R}).}}
+{As described in Section \ref{demt}, we carried out DEMT reconstructions of the coronal structure for target rotations CR-2082 and CR-2208 using STEREO/EUVI and SDO/AIA data, respectively.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared $\sqravgN$ and the electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}{, and the measure $R$ was calculated by means of Equation (\ref{R}).}}
 
 {As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations.
-Three different heights \albert{of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic results ($1.025\,\mrsun$), \albert{the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
+Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic results ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
 Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}).
-Thick-black {curves indicate} the \albert{open/closed boundaries of the magnetic field of the} AWSoM model.
+Thick-black {curves indicate} the {open/closed boundaries of the magnetic field of the} AWSoM model.
 
@@
 
-Target CR-2082 was highly axisymmetric (i.e, \albert{characterized by} a high azymuthal symmetry) and showed two \albert{small} ARs (active \albert{regions), both near latitude} $+30\mdeg$ and \albert{around longitudes} $50\mdeg$ and $120\mdeg$\albert{, respectively}.
-Target CR-2208 was \albert{considerably less axisymmetric and} showed two \albert{ARs, both near latitude} $+5\mdeg$ and \albert{around longitudes $140\mdeg$ and $300\mdeg$, respectively.}
-
-\albert{The magnetically open and closed regions of the AWSoM model are associated to CHs and the the equatorial streamer belt, respectively.
-Consistently with that, the open/closed boundaries derived from the respective AWSoM model quite accurately match the regions which exhibit the strongest latitudinal gradient in the DEMT maps of both the electron density and temperature.}
+\albert{Both target rotations are highly axisymmetric, i.e.
+characterized by a high azymuthal symmetry.
+Rotation CR-2082} showed two {small} ARs (active {regions), both near latitude} $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg${, respectively}.
+\albert{Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$, respectively.}
+
+{The magnetically open and closed regions of the AWSoM model are associated to CHs and the the equatorial streamer belt, respectively.
+Consistently with that, the \albert{location of the} open/closed boundaries derived from the respective AWSoM model quite accurately match \albert{the regions of the DEMT maps which exhibit the strongest latitudinal gradient of both the electron density and temperature.}}
 
@@
 
-\albert{Visual inspection of Figures \ref{momento1} and \ref{momento2} shows that the DEMT reconstruction of the streamer belt is characterized by relatively larger values of density and temperature in comparison to the CHs.
-They also that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between \albert{SCs 24 and 25}, the temperature in the equatorial latitudes tends to decrease with height while in the mid-latitudes tends to \albert{increase with height}.
-A similar behaviour is seen in CR-2208, belonging to the declining phase of \albert{SC 25, but having a much less axisymmetric structure this characteristic is not so obvious.
+{\albert{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively larger values of density and temperature in comparison to the CHs.
+They also that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 24 and 25}, the \albert{the low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behaviour is seen in CR-2208, belonging to the declining phase of {SC 25, but having a \albert{somewhat less axisymmetric} structure this characteristic is not so obvious.
 This thermodynamic structure} of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
 
-\albert{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of DEMT measure $R$ defined by Equation (\ref{R}), at the same three heighs shown in Figures \ref{momento1} and \ref{momento2}.
+{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of \albert{the DEMT} measure $R$ defined by Equation (\ref{R}), at the same three heighs shown in Figures \ref{momento1} and \ref{momento2}.
 In most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$.
-The notable exception is to be found in the CHs of the target rotation analyzed based on AIA data.
+The notable exception is to be found in the CHs of the target rotation \albert{analysed} based on AIA data.
 A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}.
@@
 
-\albert{To characterize the DEMT results in different magnetic structures, we traced} $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.
+{To characterize the DEMT results in different magnetic structures, we traced} $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.
 For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected.
@@
 \emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs (see text) are shown in blue, red, violet and green color, respectively.}}
+\albert{The location of} type 0, I, II and III legs \albert{is shown} in blue, red, \albert{magenta and cyan} color, respectively.}}
 \label{rpoint_demt}
@@
 Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs are shown in blue, red, \albert{magenta and cyan} color, respectively.} {Of the 45000 legs selected for CR-2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III.
+Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} {Of the 45000 legs selected for CR-2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III.
 On the other hand, of the 59000 legs selected for CR-2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.} \notebyalbert{Los números deben ser actualizados, o la frase eliminada.}
@@
 {Type 0 (small down) legs mainly populate the equatorial latitudes.
-This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level \albert{around the solar minimum beween SCs 24 and 25} by \citet{nuevo_2013}.
-Later on, \citet{lloveras_2017} showed \albert{that} equatorial down loops in streamers were also to be found in the deep minimum between SCs \albert{23 and 24}.
+This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level {around the solar minimum beween SCs 24 and 25} by \citet{nuevo_2013}.
+Later on, \citet{lloveras_2017} showed {that} equatorial down loops in streamers were also to be found in the deep minimum between SCs {23 and 24}.
 Here, we verify the existence of this type of structure for the two target rotations.
@@
 
-%\notebyalbert{No comprendo esta frase:} \emph{This classification of types of lines automatically leads to specific regions arranged along all longitudes associated with different thermodynamic, with good symmetry between both hemispheres in both rotations.}
-
 \begin{figure}[h!]
@@
 \includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
-\caption{Frequency histograms of the temperature radial gradient for the different {four types of legs} shown in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
+\caption{Frequency histograms of the temperature radial gradient for \albert{the four types of legs} in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
 \label{gradt_demt}
@@
 The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs.
-For both rotations, \albert{the median value of the temperature radial gradient is ${\rm Md}\left(\dr\Tm\right) \approx -2.5$, $+2.3$ and $+2.4\,\MK/\mrsun$} for legs of type 0, I and II, respectively.
-
-\albert{The notable difference between both rotations is the characteristic \albert{value ${\rm Md}\left(\dr\Tm\right)\approx +4.5\,\MK/\mrsun$} for legs of type III for CR-2208.
+For both rotations, {the median value of the temperature radial gradient is ${\rm Md}\left(\dr\Tm\right) \approx -2.5$, $+2.3$ and $+2.4\,\MK/\mrsun$} for legs of type 0, I and II, respectively.
+
+{The notable difference between both rotations is the characteristic {value ${\rm Md}\left(\dr\Tm\right)\approx +4.5\,\MK/\mrsun$} for legs of type III for CR-2208.
 This is related to the much larger $R$ score for the DEMT results along CH legs for CR-2208.
 In this case, DEMT performs poorly in modeling a LDEM that predicts the tomographic FBEs with reasonable accuracy.
-Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, shows that in most of the CH region the results for $\Tm$ below height $1.105\,\mrsun$ are quite uniform and artificially low.
+Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, \albert{reveals that in most of the CH region the result for $\Tm$ below height $1.105\,\mrsun$ is quite uniform and artificially low}.
 As it turns out, around and above height this height the score $R$ is lower and the temperature results are more reliable.
@@
 We will return to this point in the conclusion section.}
-
-%\temp{mostrar los gradientes negativos va a ser util en los parrafos posteriores que expliquen porque en las lineas tipo 0 hay valores de $\phi_c$ negativos.}
-
-%\temp{ Comentar en la discusion el paper de shift y cramer, para decir un poco sobre los down y la incapacidad del modelo en reproducirlos}
 
@@
 \includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
-\caption{{Statistical distribution of DEMT results traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}.
-From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$.
-Results for target rotations CR-2082 and CR-2208 are shown in blue and red color, respectively.
-In each panel the median value $m$ is indicated.} }
+\caption{{Statistical distribution of \albert{DEMT results for rotations CR-2082 (blue) and CR-2208 (red)} traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}.
+From left to right: \albert{electron density $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$,} electron density scale height $\lN$, \albert{and loop-averaged temperature $\aTm$.
+In each panel} the median value $m$ is indicated.} }
 \label{histos_fulldemt}
@@
 
-\albert{For both rotations, Figure \ref{histos_fulldemt} shows, in a statistical fashion, the DEMT results traced along field lines discriminated by field line type}.
-From top to bottom {results are shown for} type 0 to type III {field lines}\albert{, respectively}.
+{For both rotations, Figure \ref{histos_fulldemt} shows, in a statistical fashion, the DEMT results traced along field lines discriminated by field line type}.
+From top to bottom {results are shown for} type 0 to type III {field lines}{, respectively}.
 From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$ {(the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.
 
-\albert{Table \ref{tabla_demt} summarizes a} quantitative comparative analysis between the results of the two {target rotations}.
+{Table \ref{tabla_demt} summarizes a} quantitative comparative analysis between the results of the two {target rotations}.
 For CR-2082 quantities are expressed as absoulte values, {while} for CR-2208 they are informed {as a precentual variation} relative to the corresponding results for CR-2082.
-\albert{The following major results, both concerning the structure of each rotation individually as well as their comparison, can be drawn.}
+{The following major results, both concerning the structure of each rotation individually as well as their comparison, can be drawn.}
 
@@
 
-\albert{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer regions of the equatorial streamer belt, progressively exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature.
+{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer regions of the equatorial streamer belt, progressively exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature.
 In both rotations also, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.}
@@
 
-%To establish if the differences in the results between the two rotations are significant, Section \ref{uncertainties} estimates the error bars due the dominating systematic uncertainties.
-%\diego{quizas vale la pena introducir alguna comparacion sobre el campo magnetico, veremos como quedan los comentarios de ceci.}
-%{Also, within the streamer belt the magnetic field strength is similar in both rotations in the northern hemisphere, while in the southern hemisphere CR-1915 exhibits $10-80\%$ larger values compared to CR-2081, with increasing difference for larger latitudes.
-In the coronal holes, the magnetic field strength of CR-1915 is much larger than for CR-2081, exhibiting values up to 50\% larger in the northern hemisphere and more than twice larger in the southern hemisphere.}
-
-%Previous works have found magnetic loops which temperature decrease with height, most generally in equatorial latitudes \citep{huang_2012,nuevo_2013}.
-This type of loops with negative gradients produce a negative conductive flux that contribute to the heating in the corona.
-In this work, we compute the loop-integrated energy quantities separately in three different populations of loops.
-
-\albert{To analyze the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the clasification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).
-\albert{For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.}
+{To analyze the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the clasification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).
+{For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.}
 
@@
 
-\albert{For both rotations, the value of the integrated radiative power $E_r$, measured by the quantity $\phi_r$, is largest for loops of type 0.
+{For both rotations, the value of the \albert{loop-integrated} radiative power $E_r$, measured by the quantity $\phi_r$, is largest for loops of type 0.
 This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors contributing to maximize $E_r$ for loops of type 0.
-As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0 are characterised by the relatively largest values of electron density.
+As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0 are characterised by \albert{the largest} values of electron density.
 Also, in the range of sensitivity of the EUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$.
-According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterised by \albert{values of temperature that are progressively larger and farther} from the value $\Tc$, for both rotations.}
-
-{In the case of the quantity $\phi_c$, its sign depends on that of the conductive flux $F_c$.
-As shown in \citet{maccormack_2017}, down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, which is verified in Figure \ref{energia_demt}.}
-
-\albert{As a result of the radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of loop.
-These values are similar to those reported by \citet{maccormack_2017}.
+According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterised by {values of temperature that are progressively larger and farther} from the value $\Tc$, for both rotations.}
+
+{\albert{The sign of the quantity $\phi_c$ depends on that of the conductive flux $F_c$.
+Equations (\ref{Fc}) and (\ref{phi_c}) imply that } down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, \albert{as verified} in Figure \ref{energia_demt}.}
+
+{\albert{Adding the} radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of \albert{loop, matching the values reported by} \citet{maccormack_2017}.
 Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$.
-As shown by \citet{maccormack_2017}, this result affects only the smallest loops (a subset of the type 0 class) and it is due to the limited temperature sensitivity of the instrumental passbands.
-The radiative loss term is calculated based on plasma emission detected by the three coronal bands of EUVI and the three bands of AIA used.
-Though this should account for most of the coronal plasma, there surely is additional emission that is out of the range of sensitivity of the instruments used.
-Thus, the positive term $\phi_r$ is most liekly understimated, leading to values $\phi_h<0$ in loops of type 0, which are characterized by $\phi_c<0$.}
-
-%Type 0 loops present slightly larger gradients than type I.
-Therefore, type 0 present bigger amount, in modulus, of loop-integrated conductive flux.
-Due conductive flux negative can not be assumed as a loss but it can be contributing to the coronal heating.
-Thus, to compensate the radiative losses, a lower loop-integrated energy input flux ($\phi_h$) is required.
-
-%We can see, on type 0 loops, a median value of energy input flux for CR2082 twice bigger than CR2208.
-Also, in both rotations, we observe a negative population of loop integrated energy input flux.
-This can refer to some loops where loop-integrated radiative flux is too small in comparison with the larger gradients of negative conductive flux, resulting in negative energy input flux.
-
-%The type I loops show a loop-integrated positive conductive for each loop in both rotations consistent with positive gradients of temperatures.
-The conductive flux have values around 0.3 $10^{5}[\rm{erg\,sec^{-1}\,cm^{-2}}]$ in both rotations.
-Similar results have been found for loop-integrated radiative flux and energy input flux for both rotations.
+As shown by \citet{maccormack_2017}, \albert{this affects only the smallest sized loops of the type 0}, and it is \albert{most probably} due to the limited temperature sensitivity of the instrumental passbands.
+The radiative loss term is \albert{here calculated based on plasma emission detected by three coronal bands of EUVI or AIA.
+Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range.
+As a result,} the positive term $\phi_r$ is most likely understimated, leading to values $\phi_h<0$ in loops of type 0, \albert{being characterized} by $\phi_c<0$.}
 
@@
 
-\noindent\notebyalbert{This section will show the results of AWSoM for $N_e$ and $T_e$, and how they compare with the corresponding results of DEMT ($\sqravgN$ and $\Tm$).
+%\noindent\notebyalbert{This section will show the results of AWSoM for $N_e$ and $T_e$, and how they compare with the corresponding results of DEMT ($\sqravgN$ and $\Tm$).
 It will first show the Carrington maps of $N_e$ and $T_e$ at the same three heights we showed the same maps for the DEMT results.
-Then it will show the lat/lon location of loops of type I, II and III at a middle height, just loke for DEMT results.
 As the two targets are highly axis-symmetric, a first quantitative comparison between AWSoM and DEMT will be shown as longitude-averaged latitudinal profiles of the results of both models at a sample height.
-To make comparisons in distinct magnetic structures, we will also show the average radial dependence of results for loops of type I, II and III, overplotting the AWSoM and the DEMT results.
+Then we will show the lat/lon location of loops of type I, II and III at a middle height, just loke for DEMT results.
+To make comparisons in distinct magnetic structures, we will show the average radial dependence of results for loops of type I, II and III, overplotting the AWSoM and the DEMT results.
 For the tree types of loops we will show histograms of the DEMT and AWSoM products along field lines.
@@
 
-Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature, for both rotations.
-These Figures show the results at the same three heights selected for visualisation of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}.
-As in those, thick-black curves indicate the magnetic open/closed boundaries based on the magnetic field of the AWSoM model.
-Visual inspection of these maps shows that the AWSoM model for both rotations is highly axysimmetric, as the tomographic model.
-
-\diego{A visual inspection of these maps shows that both reconstructions are very axysimmetric for $\Ne$ and $\Te$ as well.
-The closed region is denser and hotter than the open region.
-The density and temperature gradients are maximum in the open-close boundary.
-The open field regions in low latitudes maintain thermodynamic values associated with open regions.} The reconstruction of CR-2082 does not show clear the ARs, while CR-2208 shows a well reconstruction of both AR around latitude-longitud $+5\mdeg$, $140\mdeg$ and $+5\mdeg$, $300\mdeg$.
-In both rotations the open-closed boundaries derived from the AWSoM model match the shape of the contour levels of both the electron density and the electron temperature.
-
-%\diego{comparacion visual entre estas dos figuras y als dos de DEMT.}
-
-The same intensity scales in both density and temperature can be observed between the tomographic results and those of AWSoM in both rotations, as well as the same thermodinamic structures.
-That is, equatorial latitudes, mid laditudes and the open regions.
+\albert{For both target rotations,} Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature.
+\albert{Maps are shown} at the same three heights selected for visualisation of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}.
+\albert{Thick-black curves} indicate the magnetic open/closed boundaries based on the magnetic field of the AWSoM model.
+Visual inspection of these maps shows that the AWSoM model for both rotations is highly \albert{axisymetric}, as the tomographic model.
 
@@
 
+\albert{As described in Section \ref{awsom}, the AWSoM model includes an artificially thick TR, achieving coronal conditions above height $\approx 1.06\,\mrsun$.
+Indeed, the top panels in Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208}, at height $1.025\,\mrsun$, clearly do not represent coronal conditions (altough we include them here for completness).
+When compared to DEMT results (Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}), the latitude-longitude maps of the AWSoM model for heights $1.065$ and $1.105\,\mrsun$ capture well the denser and hotter equatorial streamer belt surrounded by the less dense and colder CHs.
+Furthermore, for both target rotations, the temperature maps show the low latitudes of the equatorial streamer belt to be characterised by lower temperatures than its mid-latitudes, as also seen in the DEMT results.
+The latitude-longitude maps of the AWSoM and DEMT results are shown in the same units and scales, so that a visual comparison among them already reveals similar values of electron density and temperature in both models.}
+
 \begin{figure}[h!]
@@
 
-%\temp{Se presentan los midpoints para awsom que lucen mas rellenos xq no hay down loops y todo es super suave.}
-
-In the same way as in Section \ref{demt_res}, the model results were traced along the magnetic lines obtained with it.
-This allowed to obtain $\Ne(r)$ and $T_e(r)$ along the magnetic lines and fit them to the Equations \ref{Nfit} and \ref{Tfit}.
-
-The actual version of the AWSoM model can not reproduce down legs, so for a further comparison we only select lines of type I, II and III of those meeting the criteria described in Section \ref{trace}.
-
-As a way to understand the distribution of legs, Figure \ref{rpoint_awsom} shows the latitudinal-longitudinal location of the traced legs at top and the selected fitted legs meeting the criteria at $1.105\,\mrsun$ for both rotations, in the same way as in Section \ref{demt_res}.
-In red the type I lines, populating mostly the entire streamer.
-In violet the type II lines, populating the edge that assemble the envelope around the streamer, and in green dots the type III lines, populating the coronal holes.
-
-The reader may notice that these structures are the same as those in Figure \ref{rpoint_demt} but more filled.
-The cause is twofold, on the one hand the same magnetic model was used to trace both DEMT and AWSoM results, on the other hand is because giving the model smoother results, fewer fitted lines are filtered.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_awsom_paper_test_Rpoint-map.pdf}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_awsom_paper_test_Rpoint-map.pdf}
-%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.pdf}
-%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.pdf}
-\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its legs in types I, II and III. The model does not exhibit legs of type 0.}}
-\label{rpoint_awsom}
-\end{center}
-\end{figure}
-
-To highlight the latitudinal structures observed in Figures \ref{carmaps_demt_2082} and \ref{carmaps_awsom_2082} for CR-2082 as well as Figures \ref{carmaps_demt_2208} and \ref{carmaps_awsom_2208} for CR-2208, Figure \ref{perf_lat} shows for both rotations the latitudinal variation  of both the electron density and the electron mean temperature at the height $r=1.105\,\mrsun$, averaged over all longitudes (excluding the AR).
-DEMT results are shown in blue lines while AWSoM results in red.
-While the temperature shows a maximum in each hemisphere, the density has a simpler behavior, with higher values in the low-latitudes of the streamer and a nearly monotonic decrease towards larger latitudes.
-The vertical black lines denotes the average of the open-close boundary in both hemispheres to each rotation.
-
-\diego{Me gustaria hacer un comentario de cierre para esta figura que refiera las Figuras 3 y 9, como la linea de abajo, y que conecte con los histogramas que vienen a continuacion.
-Si no queda bien, hay que mover esta figura entre la actual figura 8 y 9.}
-
-This longitude-averaged behaviors match well with the physical locations of the legs shown in Figures \ref{rpoint_awsom} and \ref{rpoint_demt}.
-
-According to the visual inspection on the maps of carrington, the latitudinal profiles comparing both DEMT and AWSoM results are on the same scale.
-Little difference in density is observed in CR-2208 and in temperature in CR-2082, while DEMT in CR-2082 was $20\%$ denser.
-Finally, DEMT results for CR-2208 were $25\%$ hotter in the streamer and $30\%$ colder in the polar zone than AWSoM.
-Density profiles on AWSoM show an increase around the polar zone, which seems like an artifice.
+\albert{Being highly axisymmtric target rotations, the longitude-averaged latitudinal variation of the results of both models is an informative way to compare their large-scale structure.
+Such comprison is shown in Figure \ref{perf_lat} at height $1.105\,\mrsun$, with top panels comparing electron density and lower panels electron temperature.
+In these longitude-averaged profiles, longitudes containing ARs or low latitude CHs were excluded.
+In each panel the averaged latitudinal variation for the DEMT model is shown in solid-linestyle, while the result for the AWSoM model is shown in dashed-linesyle.
+Left panels show the comparison for CR-2082 (in blue) and right panels for CR-2208 (in red).
+In each panel the vertical black lines denote the corresponding longitude-averaged latitude of the open-close boundary in both hemispheres.}
+
+\notebyalbert{Diego: debés estar seguro que sacaste ARs y low-latitude CHs de los promedios en longitud.
+Cuando más te esmeres la comparación es más justa, y podés revelar algo que de otra manera no se vería.
+Si promediaste longitudes con ARs o CHs, rehacelo, vale la pena.
+Por supuesto debes promediar idéntidas longitudes en DEMT, AWSoM y en la O/C.}
 
@@
 The left (right) panels correspond to CR-2082 (CR2208).
-The vertical black line indicates the longitude-averaged latitudes of the open/close magnetic boundary in both hemispheres.
-\notebyalbert{(by Albert): The idea of this Figure is to show how DEMT and AWSoM compare AS A FUNCTION OF LATITUDE at an intermediate height of the DMET grid, averaged in longitude (excluding zones with ARs).}}
+The vertical black line indicates the longitude-averaged latitudes of the open/close magnetic boundary in both hemispheres.}
 \label{perf_lat}
@@
 
-To summarize the comparison between both results during both rotations at full height, it is shown in Figure \ref{perfiles_promedio} the average fits of $\Ne(r)$ and $T_e(r)$ for legs of type I (blue), II (red), and III (green) for both rotations.
-
-In average all temperature and density behavior from both results are on the same scale.
-The coronal base densities of AWSoM were lower than those of DEMT in CR-2082 and higher in CR-2208.
-The fact that the density decays to similar values between both results suggests a similar height scale.
-Onthe other hand basal temperature of AWSoM was lower in both rotations, but the temperature gradients are very similar en each type of legs, showing a very similar increase of temperature with height.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
-\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (red), II (violet), and III (green), for CR-2082 (top panels) and CR-2208 (bottom panels).
-Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.} \notebyalbert{(by Albert): The idea of this Figure is to show how DEMT and AWSoM compare AS A FUNCTION OF HEIGHT, in three distinct types of magnetic structures, and for both rotations.}}
-\label{perfiles_promedio}
-\end{center}
-\end{figure}
-
-Tu summary the statistical comparison, Figure \ref{histos_2082} and \ref{histos_2208} shows the statistical results of both rotations for the three types of field lines traced with DEMT (blue) and AWSoM results (red).
-From left to right the panels show the statistical distribution of $\NCB$, $\lN$ and $\aTm$.
-For all types of lines, Table \ref{tabla_comp} summarizes the median value of the statidtical distribution of each physical quantity derived from the analysis.
-The DEMT quantities are expressed as absoulte values, while for ASWSoM they are informed relative to the corresponding result for DEMT.
-
-\diego{aca podria ir un pequeño parrafo que resuma las diferencias.
-Pero justo a continuacion empiezan las conclusiones y uno tiende a repetir, no se como encararlo para que no quede dos veces lo mismo y tan pegado uno de lo otro.}
+\albert{Several details from Figure \ref{perf_lat} are worth being highlighted.
+Firstly, for CR-2082 the electron density of both models agree within $\approx 20\%$ at all latitudes, and for CR-2208 the agreement is within $\approx5\%$.
+In the case of the electron temperature both models agree within $\approx 10-15\%$ at all latitudes for both target rotations.
+Secondly, for both target rotations, and for both models, these plots clearly show the relatively lower temperatures characterising the low-latitudes of the equatorial streamel belt compared to its mid-latitudes.
+Thirdly, for both target rotations, the latitude of the open/close magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density.
+Note this is not the case for the AWSoM model, that shows a minimum densityat the open/closed boundary.
+Last, note that the DEMT electron density decreases from the open/close boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend.}
+
+\albert{To characterize the results of the AWSoM model in distinct magnetic structures, its results for electron density and temperature were traced along its magnetic field lines.
+For each field line leg, the results were then fit to Equations (\ref{Nfit}) and (\ref{Tfit}).
+In its current implementation, the AWSoM model can not simulate down loops, a point we will discuss in the next section.
+We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_awsom_paper_test_Rpoint-map.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_awsom_paper_test_Rpoint-map.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.pdf}
+\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its legs in types I, II and III. The model does not exhibit legs of type 0.}}
+\label{rpoint_awsom}
+\end{center}
+\end{figure}
+
+\albert{For both target rotations, the top panels of Figure \ref{rpoint_awsom} show the latitude-longitude location (at heliocentric height $1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
+That criterion is adapted here, requiring that at least five voxels of the tomographic grid are threaded by the leg.
+Open legs are indicated in grey color and closed ones in black color.
+For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit} and \ref{Tfit}.
+Considering the AWSoM data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_awsom} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
+Using a three-color code, type I, II and III legs are shown in red, magenta and cyan color, respectively.
+This figure is to be compared with the corresponding Figure \ref{rpoint_demt} for DEMT results.
+It is readily seen that the AWSoM maps are more populated than those of DEMT.
+This is due to the 3D MHD model having electron density and temperature fields spatially smoother than those of DEMT.}
+
+\albert{For target rotation CR-2082, Figure \ref{histos_2082} shows the statistical distribution of the results of the DEMT (solid line-style) and AWSoM (dashed line-style) models traced along legs of type I, II and III (from top to bottom), as defined in Section \ref{trace}.
+From left to right: electron density at the lowest coronal height of the AWSoM model $\NCB\equiv\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
+In each panel the median values $m$ are indicated.
+Figure \ref{histos_2208} shows the same analysis for target rotation CR-2208.}
 
@@
 \includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
-\caption{{Statistical distribution of DEMT (blue) and AWSoM (red) results traced along legs of type I, II and III (from top to bottom), as defined in Section 2.3.
-From left to right: electron density at the lowest coronal height of the AWSoM model $\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
-In each panel the median value $m$ is indicated.}}
+\caption{{Statistical distribution \albert{of the results of the DEMT (solid line-style) and AWSoM (dashed-linestyle) models} traced along legs of type I, II and III (from top to bottom), as defined in \albert{Section \ref{trace}.} From left to right: electron density at the lowest coronal height of the AWSoM model $\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
+In each panel the median \albert{values $m$ are} indicated.}}
 \label{histos_2082}
@@
 \end{figure}
+
+\albert{For the two target rotations, Table \ref{tabla_comp} summarizes a quantitative comparative analysis between the results of the DEMT and AWSoM models.
+The DEMT results are expressed as absolute values, while the ASWSoM results are informed as a percentual variation relative to the corresponding result for DEMT.
+the following major results can be drawn.}
 
@@
 
-%This plot (E) has never been shown before and I believe it is a very nice result.
-There are of course previous studies on this, but this would be the first time this is evaluated with tomography.
-It is not the terminal speed, but it already shows the fast/slow components.
-We can show this, or we can go for more.
-Diego can QUANTIFY the correlation by carefully mapping all open field lines at 6 Rsun down to the DEMT region.
-He needs to code a bit more to achieve this goal, but we believe it is worth.
-With that tool done Diego can explore other terminal values of quantities of the AWSoM model and the DEMT results below (expansion factor maybe?).
-This will be nice to do also for the July-2-2019 Eclipse rotation that we will analyze after this paper.
+\albert{For target rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, depending of the type of leg, while the median value of the scale height $\lN$ agree within $\approx 10\%$.
+The leg-averaged electron temperature $\aTm$ of both models also agree within $10\%$.
+For target rotation CR-2208 the agreement of the median value of $\NCB$ and $\lN$ of both models is within $5\%$, while median values of $\aTm$ agree within $15\%$.
+These detailed results informed per magnetic structure are fully consistent with the large-scale comparison provided in Figure \ref{perf_lat}.}
 
@@
 DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.
-\albert{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
+{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
 Ejemplo para CR-2082 $\NCB$ de Type-II: $1.0\,(-23\%)$.
@@
 
-Figure \ref{perf_lon_vr} show the longitude-averaged AWSoM radial wind speed $V_r$ at $6\,\mrsun$, where all field lines are open.
-The heliocentric current sheet (HCS) location is indicated by the minimum of the speed curve.\\
-\diego{can we say something without having traced the lines?} \notebyalbert{(by ALBERT) Todo el punto de la última Figura es precisamente decir algo.
-La comparación con la Figura 10 muestra una anti-correlación entre la densidad basal de DEMT y la velocidad terminal de AWSoM.}
-
-For each rotation, everything to the south of the HCS maps down to the southern open region in the Figures \ref{perf_lat}, and the same for the northern hemisphere, showing an anti-correlation between $\Ne$ at low heights and high $V_r$ at $6\,\mrsun$.
-
-\diego{Voy a intentar jugar con las lineas tipo 3 aumentando su cota inferior de latitud para ver si los histogramas de temp media dejan de ser tan dispersos y se vuelven mas sub-1MK. }
+\albert{Finally, to provide a graphical comparison of both models accross the full range of heliocentric heights covered by the DEMT results, Figure \ref{perfiles_promedio} shows the average fits of $\Ne(r)$ and $T_e(r)$ for legs of type I (red), II (magenta), and III (cyan) for both target rotations.
+In each panel the DEMT and AWSoM results are plotted in solid and dashed linestyles, respectively.}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
+\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of \albert{type I (red), II (magenta), and III (cyan)}, for CR-2082 (top panels) and CR-2208 (bottom panels).
+Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
+\label{perfiles_promedio}
+\end{center}
+\end{figure}
+
+\albert{As discusssed above, Figure \ref{perf_lat} shows that the logitude-averaged latitudinal profile of the DEMT electron density in the CHs decreases towards the poles.
+Figure \ref{perf_lon_vr} below shows the longitude-averaged AWSoM radial wind speed $V_r$ at $6\,\mrsun$, where all field lines are open.
+The heliocentric current sheet (HCS) location is indicated by the minimum of the speed curve.
+For each rotation, all velocity data points to the south of the HCS position map down to the southern CH in Figures \ref{perf_lat}.
+Similarly, all velocity data points to the north of the HCS position map down to the northern CH in Figures \ref{perf_lat}.
+This clearly shows an anti-correlation between the DEMT electron density at low heights and the AWSoM wind speed at larger heghts.}
+
+\notebyalbert{We could quantify the anti-correlation between the AWSoM terminal speed and the DEMT electron density at the coronal base in the following fashion.
+We can set up starting points at, say, $20\,\mrsun$, every one degree, both in latitude and longitude.
+This would mean setting up $180\times 360$ strating points.
+We trace then the (open) field lines from each of those starting points down to $1.0\,\mrsun$ to find out the DEMT results at those lower heights for each field line.
+Now, to do this we need to develop some codes and have no time for this paper.
+We can postpone it for a next effort, or...
+Chip: do you think you could do this with your present tools?
+Do you think it is intersting?
+I think so.
+Our submission deadline is end-of-January.}
 
@@
 *In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI.
-In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, analyzed a single target using both instruments independently.
+In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, \albert{analysed} a single target using both instruments independently.
 They found that while the density product is essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e.
@@
 These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\lesssim 5\%$ and $\approx 2\%$ for the electron temperature and density, respectively.
-
-*Coronal magnetic structures for which the temperature increases/decreases with height in the range of heights covered by DEMT, $1.02–1.22\,\mrsun$, have been dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first observed their presence by means of DEMT.
-As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
-Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}.
-In a recent study by \citet{schiff_2016}, down and up loops have been successfully reproduced by a numerical implementation of a 1D steady-state model that considers time-averaged heating rates.
 

### 2020-01-10 lloveras_2020.tex
graficos

@@
 
-EUV images are affected by instrumental stray light contamination, which can be corrected by deconvolution of the point spread function (PSF).
-While in the case of AIA images there is no reliable determination of its PSF, it has been well determined for EUVI-B by \citet{shearer_2012}.
-For this article, all EUVI images were stray-light corrected.
-For the details of impact in $\Nm$ and $\Tm$, refer to \citet{lloveras_ba2017}.
-
 In DEMT, the low corona in the height range $1.0$ to $1.25\,\mrsun$ is discretized in a spherical computational grid.
@@
 
-\diego{ DONDE QUEDA MEJOR COMENTAR ESTA MEJORA?
+EUV images are affected by instrumental stray light contamination, which can be corrected by deconvolution of the point spread function (PSF).
+While in the case of AIA images there is no reliable determination of its PSF, it has been well determined for EUVI-B by \citet{shearer_2012}.
+For this article, all EUVI images were stray-light corrected.
+For details of the impact on the tomographic results, refer to \citet{lloveras_ba2017}.
+
+\diego{
 Unlike in previous works, a 3D regularization scheme was applied, thus spurious artifacts (nduced by the previous longitude latitude regularization schemei) were minimized in the first two heights of the tomographic grid.}
@@
 We refer the reader to \citet{frazin_2009} for a detailed description of the technique, and to \citet{vasquez_2016} for a recent review on all published work based on it.
-Here we summarize the key points.
-The technique involves two consecutive procedures.
-
-In a first step, the time series of EUV images is used to solve a SRT problem, for each EUV band independently.
+Here we summarize the key points of the technique that involves two consecutive procedures.
+
+In a first step, the time series of EUV images is used to solve a solar rotational tomography (SRT) problem, for each EUV band independently.
 As a result, the 3D distribution of the so called {filter band emissivity} (FBE) is determined for each band separately.
@@
 Each traced field line is classified as ``open" if it intersects the source surface, set in this work at $r=6\,\mrsun$ (where lines become radial), or as ``closed" otherwise.
-In the case of closed magnetic field lines, loops {are} further classified as ``small" and ``large" upon their apex height being within or beyond the range of heights studied by DEMT, respectively.
+In the case of closed magnetic lines, they are separated in two ``legs", from the base to the apex.
+
+%\diego{Of these legs, those whose size $L$ are smaller than the average lengths $\langle L \rangle$ are called small, and those with $L > \langle L \rangle$ ar called large.}
+\diego{
+In the case of closed magnetic field lines, legs {are} further classified as ``small" and ``large" upon their apex height being within or beyond the heigh average of the closed legs, respectively.
+}
 
@@
 
-\diego{aca estoy haciendo la distincion entre la densidad y temp obtenida por demt y awsom}
 For each open field line, and for each leg of the closed ones, an exponential fit was then applied to the electron density and a linear fit applied to the electron temperature.
-For DEMT results, the data points used were $\sqravgN(r)$ and $\Tm(r)$, in case of AWSoM the data points were $\Ne(r)$ and $\Te(r)$.
+For DEMT results the data points used were $\sqravgN(r)$ and $\Tm(r)$, and in case of AWSoM the data points used were $\Ne(r)$ and $\Te(r)$.
 The exponential and linear fit equations are described by
@@
 
-%La temperatura en funcion de la altura a lo largo de lineas muestra comportamientos lineales.
-En el presente trabajo nos focalizamos en lineas con temperaturas crecientes y decrecientes en foma lineal.
-Es decir nos quedamos con aquellas piernas donde el coeficiente de pearson entre la temperatura y la altura (rho) cumple rho mayor 0.5 (con p-value 0.05) y de esta forma se descartan aquellas piernas en las que los resultados DEMT no pueden asegurar un cambio notable de temperatura entre la base y el apice (asi no uso la palabra isotermico y evado ese problema)
-
-%The temperature as a function of height along legs shows linear behaviors. 
-In the present work we focus on lines with increasing and decreasing temperatures in linear form.
-In other words, we selected those legs where the {Pearson correlation coefficient $\rho$ between temperature $T$ and radius $r$ meets $|\rhoTr| > 0.5$}.
-\temp{(with p-value less than 0.05)}.
+In the present work we focus on legs with increasing and decreasing temperatures in linear form.
+In other words, we selected those legs where the {Pearson correlation coefficient $\rho$ between temperature $T$ and radius $r$ meets $|\rhoTr| > 0.5$} {(with 95\% confidence level)}.
 In this way, those legs in which the DEMT results cannot ensure a noticeable change in temperature between the base and the apex, are discarded.
@@
 The linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg.
-\diego{En realidad esta regresion lineal utiliza de por si los errores, pero luego tmb los uso para el test de hipotesis, quizas vale la pena ponerlo solo ahi.}
-
-To measure how good the quality of the exponential fit to the electron density and the linear fit to the temperature data are, a chi-square merit function was used (see Section 15.2 \citet{recipes}).
-The errors were estimated in \citet{lloveras_2017}, $0.07$ MK for $\Tm$ and $4.0\,10^6 cm^{-3}$ for $\Ne$ and legs with p-value $>0.005$ were rejected.
+Both fits consider tomographic systematic uncertainty estimated in \citet{lloveras_2017}, i.e.
+$0.07$ MK for $\Tm$ and $4.0\,10^6 cm^{-3}$ for $\Ne$.
+
+To measure how good the quality of the fit are, a chi-square merit function was used (Section 15.2 \citet{recipes}).%, selecting only legs with 95\% confidence level.
 
@@
 
+\diego{
 \begin{enumerate}
-
 \item 
 The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg.
-
 \item 
 The {value of the Pearson correlation coefficient meets $|\rhoTr| > 0.5$.}
-
 \item 
-The p-value of both the exponential and linear fit must be less than 0.05.
-
+The coefficient level of both the exponential and linear fit must be grater than \%90.
 \end{enumerate}
+}
 
@@
 %\temp{Hacer explicacion de los tipos de lineas bien secos, luego en fig 3 hacer notar que implica cada una en cuanto a estructura magnetica}\\
-
+\diego{
 \begin{itemize}
- \item Type 0 - Small (meaning with apex within the DEMT range of heights) closed field lines in the latitudes range $[-30\mdeg,+30\mdeg]$ and $\dr \Tm < 0$.
+\item Type 0 - Small legs (coming from closed field) in the latitudes range $[-50\mdeg,+50\mdeg]$, and $\rhoTr < -0.5$. 
  %This class thoroughly populates the equator of the Streamer belt during a minimum solar rotation.
-
-\item  Type I - Small closed field lines in all latitudes, with $\dr \Tm > 0$. %This class thoroughly populates the inner of the Streamer belt.
-
-\item  Type II - Large closed field lines (meaning their apex surpasses the DEMT range of heights) in the latitudes range $[-90\mdeg,-30\mdeg] \cup [+30\mdeg,+90\mdeg]$ and $\dr \Tm > 0$.
+\item Type I - Small legs (coming from closed field) in the latitudes range $[-50\mdeg,+50\mdeg]$, and $\rhoTr > 0.5$. 
+%This class thoroughly populates the inner of the Streamer belt.
+\item Type II - Large legs (coming from closed field) in the latitudes range $[-90\mdeg,-40\mdeg] \cup [+40\mdeg,+90\mdeg]$, and $\rhoTr > 0.5$. 
 %This class is mostly populated by very large trans-equatorial field lines forming the envelope of the Streamer belt. 
-
-\item Type III - Open field lines (meaning with apex out the DEMT range of heights) in the latitudes range $[-90\mdeg,-60\mdeg] \cup [+60\mdeg,+90\mdeg]$ and $\dr \Tm > 0$.
-
+\item Type III - Open field lines in the latitudes range $[-90\mdeg,-60\mdeg] \cup [+60\mdeg,+90\mdeg]$, and $\rhoTr > 0.5$.
 \end{itemize}
-\diego{Hice las definiciones con gradiente de temperatura para que quede mas claro, pero en realidad uso el pearson.} \notebyalbert{Charlemos los tres en persona de esto.}
+}
 

### 2020-01-10 left_out_text.tex

--- 2020-01-10 lloveras_2020.tex
@@
-%% Template.tex; Solar Physics
-%% 
-\documentclass[namedreferences]{solarphysics}
-%
-% spr-sola-addons available options:
-%  hyperref      -- loads hyperref.sty with options (pdfborder={0 0 0 },urlcolor=blue,breaklinks)
-%  nonatbib      -- do not load natbib.sty (style loads it by default)
-%  solaromanenum -- makes enumerated list with roman numerals and a single right-bracket
-%  linksfromyear -- puts a link on a year citation (hyperref must be loaded). Loaded by default
-%  nolinksfromyear -- suppress  linksfromyear
-%  optionalrh    -- for optional running title/author
-%  showbiblabels -- to show bibitem label at end of bibitem (via \endbibitem command)
-%
-\usepackage[hyperref,optionalrh,solaromanenum]{spr-sola-addons} % For Solar Physics 
-%\usepackage{epsfig}                     % For eps figures, old commands
-\usepackage{graphicx}                    % For eps figures, newer & more powerfull
-%\usepackage{courier}                    % Change the \texttt command to courier style
-\usepackage{amssymb}                     % useful mathematical symbols
-\usepackage{color}                       % For color text: \color command
-\usepackage{breakurl}                    % For breaking URLs easily trough lines
-\def\UrlFont{\sf}                        % define the fonts for the URLs
-\usepackage{comment}
-\usepackage{setspace}
-\usepackage[utf8]{inputenc}
-
-%% Local definitions
-%% please place your own definitions here and don't use \def but
-%% \newcommand{}{} or 
-%% \renewcommand{}{} if it is already defined in LaTeX
-\renewcommand{\deg}{$^\circ$}
-\newcommand{\mdeg}{^\circ}
-\newcommand{\rsun}{R{$_\odot$}}
-\renewcommand{\l}{\lambda_{\rm N}}%\lambda_
-\newcommand{\mrsun}{{\rm R_\odot}}
-\newcommand{\med}{{\rm Md}}
-\newcommand{\avgTe}{\left<\Tm\right>}
-\newcommand{\MK}{{\rm MK}}
-\newcommand{\cm}{{\rm cm}}
-\newcommand{\cminvc}{\cm^{-3}}
-\newcommand{\cminvs}{\cm^{-2}}
-\newcommand{\erg}{{\rm erg}}
-\newcommand{\s}{{\rm s}}
-\newcommand{\sdev}{{\rm SD}}
-\newcommand{\mean}{{\rm Mn}}
-\newcommand{\deltat}{$\delta$}
-\newcommand{\LDEM}{{\rm LDEM}}
-\newcommand{\FBE}{{\rm FBE}}
-\newcommand{\TRF}{{\rm TRF}}
-\newcommand{\lN}{\lambda_N}
-\newcommand{\NCB}{N_{\rm CB}}
-\newcommand{\Nqi}{N_{\rm QI}}
-
-\newcommand{\dr}{\triangledown_r}
-\newcommand{\er}{\mathbf{e}_r}
-\newcommand{\Te}{T_{\rm e}}
-\newcommand{\Tm}{T_{\rm m}}
-\newcommand{\aTm}{\left<\Tm\right>}
-\newcommand{\Tmi}{T_{{\rm m},i}}
-\newcommand{\Ne}{N_{\rm e}}
-\newcommand{\Nm}{N_{\rm m}}
-\newcommand{\Nsqmi}{N^2_{{\rm m},i}}
-\newcommand{\Nsqm}{N^2_{{\rm m}}}
-\newcommand{\rhoTr}{\rho(T,r)}
-\newcommand{\Tefit}{T_{e,{\rm fit}}}
-\newcommand{\sqravgNi}{\sqrt{\Nsqmi}}
-\newcommand{\sqravgN}{\sqrt{\Nsqm}}
-\newcommand{\Tc}{T_{\rm c}}
-
-\newcommand{\BibTeX}{\textsc{Bib}\TeX}
-\newcommand{\etal}{{\it et al.}}
-
-\newcommand{\Pl}{\texttt{+}}
-\newcommand{\Mi}{\texttt{-}}
-
-% Definitions for the journal names
-\newcommand{\adv}{    {\it Adv. Space Res.}} 
-\newcommand{\annG}{   {\it Ann. Geophys.}} 
-\newcommand{\aap}{    {\it Astron. Astrophys.}}
-\newcommand{\aaps}{   {\it Astron. Astrophys. Suppl.}}
-\newcommand{\aapr}{   {\it Astron. Astrophys. Rev.}}
-\newcommand{\ag}{     {\it Ann. Geophys.}}
-\newcommand{\aj}{     {\it Astron. J.}} 
-\newcommand{\apj}{    {\it Astrophys. J.}}
-\newcommand{\apjs}{   {\it Astrophys. J. Suppl.}}
-\newcommand{\apjl}{   {\it Astrophys. J. Lett.}}
-\newcommand{\apss}{   {\it Astrophys. Space Sci.}} 
-\newcommand{\cjaa}{   {\it Chin. J. Astron. Astrophys.}} 
-\newcommand{\gafd}{   {\it Geophys. Astrophys. Fluid Dyn.}}
-\newcommand{\grl}{    {\it Geophys. Res. Lett.}}
-\newcommand{\ijga}{   {\it Int. J. Geomagn. Aeron.}}
-\newcommand{\jastp}{  {\it J. Atmos. Solar-Terr. Phys.}} 
-\newcommand{\jgr}{    {\it J. Geophys. Res.}}
-\newcommand{\mnras}{  {\it Mon. Not. Roy. Astron. Soc.}}
-\newcommand{\nat}{    {\it Nature}}
-\newcommand{\pasp}{   {\it Pub. Astron. Soc. Pac.}}
-\newcommand{\pasj}{   {\it Pub. Astron. Soc. Japan}}
-\newcommand{\pre}{    {\it Phys. Rev. E}}
-\newcommand{\solphys}{{\it Solar Phys.}}
-\newcommand{\sovast}{ {\it Soviet  Astron.}} 
-\newcommand{\ssr}{    {\it Space Sci. Rev.}}
-
-%---------REMOVE THESE OPTIONS AND DEFs BEFORE SUMBISSION---------------------------------------
-\usepackage[usenames,dvipsnames]{xcolor} % Las opciones: [USENAMES,DVIPSNAMES] 
-                                         % ponen a disposición los colores ejemplificados aquí:
-                                         % https://en.wikibooks.org/wiki/LaTeX/Colors
-\def\diego#1{\textcolor{red}{#1}}
-\def\albert#1{\textcolor{orange}{#1}}
-\def\fede#1{\textcolor{ForestGreen}{#1}}
-\def\temp#1{\textcolor{gray}{#1}}
-\def\notebyalbert#1{\textcolor{blue}{NOTE: #1}}
-%-----------------------------------------------------------------------------------------------
-
-\begin{document}
-
-\begin{article}
-
-\begin{opening}
-
-\title{Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling}
-
-\author[addressref={aff1},corref,email={dlloveras@iafe.uba.ar}]{\inits{D.G.}\fnm{Diego G.}~\lnm{Lloveras}\orcid{0000-0003-1402-0398}}
-
-\author[addressref={aff1,aff2},corref,email={albert@iafe.uba.ar}]{\inits{A.M.}\fnm{Alberto M.}~\lnm{V\'asquez}\orcid{0000-0003-3401-6409}}
-
-\author[addressref={aff1,aff3},corref,email={federico@iafe.uba.ar}]{\inits{F.A.}\fnm{Federico A.}~\lnm{Nuevo}\orcid{0000-0003-2355-5853}}
-
-\author[addressref={aff1,aff2},corref,email={cmaccormack@iafe.uba.ar}]{\inits{C.}\fnm{Cecilia}~\lnm{Mac Cormack}\orcid{0000-0003-1173-503X}}
-
-\author[addressref={aff4},corref,email={nishthas@umich.edu}]{\inits{N.}\fnm{Nishtha}~\lnm{Sachdeva}\orcid{0000-0001-9114-6133}}
-
-\author[addressref={aff4},corref,email={chipm@umich.edu}]{\inits{W.}\fnm{Ward}~\lnm{Manchester IV}\orcid{0000-0003-0472-9408}}
-
-\author[addressref={aff4},corref,email={bartvand@umich.edu}]{\inits{B.}\fnm{Bartholomeus}~\lnm{Van der Holst}\orcid{0000-0001-5260-3944}}
-
-\author[addressref={aff4},corref,email={rfrazin@umich.edu}]{\inits{R.A.}\fnm{Richard A.}~\lnm{Frazin}\orcid{0000-0002-0281-7677}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Runningheads
-%
-\runningauthor{D.G.~Lloveras~\etal}
-%\runningtitle{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Affilations 
-%% id shold be the same with \author addressref value.
-%\address[id={}]{}
-\address[id=aff1]{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (IAFE), CONICET-UBA, CC 67 - Suc 28,  (C1428ZAA) Ciudad Aut\'onoma de Buenos Aires, Argentina}
-
-\address[id=aff2]{Universidad Nacional de Tres de Febrero (UNTREF). Departamento de Ciencia y Tecnolog\'{\i}a, Sáenz Peña, Argentina.}
-
-\address[id=aff3]{Ciclo Básico Común (CBC), Universidad de Buenos Aires (UBA), Buenos Aires, Argentina}
-
-\address[id=aff4]{Department of Climate and Space Sciences and Engineering (CLaSP), University of Michigan, 2455 Hayward Street, Ann Arbor, MI 48109-2143, USA}
-
-\begin{abstract}
-Observational {techniques} play an essential role in advancing our understanding of the physics of the solar corona.
-They provide validation data {for} three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, {key to improve} their space weather forecasting capabilities.
-Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale.
-Based on EUV data of space borne instruments, SRT allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun.
-We carry out a study of the corona combining tomographic reconstructions with MHD simulations {using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF).
-Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24.
-Tomographic reconstructions and results of the model are analyzed in distinct coronal magnetic structures.
-We study magnetically closed structures associated with the equatorial streamer belt, as well as magnetically open regions enclosing it.
-We report on the tomographic results in the different structures, their implications for the physics of the solar corona, and the {current} capability of the AWSoM model to reproduce the tomographic reconstructions in different regions.
-
-\end{abstract}
-
-\keywords{Solar Cycle, Observations; Corona,E; Corona, Structures}
-
-\end{opening}
-
-\section{Introduction}\label{intro}
-
-Being the place where the solar atmosphere is heated and the solar wind accelerated, and where impulsive events such as solar flares and coronal mass ejections are energized, observation and modeling of the solar corona are tasks of great relevance to improve our understanding of the Sun-Earth environment.
-To advance our knowledge of the physics of the solar corona, as well as to improve its three-dimensional (3D) models, information derived from observational data plays a key role.
-Solar rotational tomography is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar corona at a global scale.
-
-\noindent\notebyalbert{Here we will put in a couple of paragraphs summarizing what SRT and DEMT are, including references and defining the accronyms in the process.
-We should refer to minima in particular.
-We should mention the instruments and missions we use as data for DEMT, and define their accronyms too.
-Also, a couple of paragraphs on the AWSoM model and the SWMF, including references and defining the accronyms in the process.}
-
-\section{Methodology}\label{meto}
-
-\subsection{DEMT reconstructions}\label{demt}
-
-\noindent\notebyalbert{This section will summarize DEMT's main aspects and equations, only those needed to understand the paper.
-Nothing not needed to read this paper is provided.
-Also, no derivation of equations are provided.
-References are given so that the reader can dig deeper if so desires.
-Points to cover are:
-\begin{itemize}
-  \item Selected targets, instruments used. One paragraph.
-  \item Characteristics of the data (specific time series, dates, bands, etc.), SolarSoft software version used for their processing. One paragraph.
-  \item Technical aspects of DEMT (grid, regularization, off-limb data is only used) and how these differ from previous versions (rereferences). One paragraph.
-  \item What is FBE, what is LDEM, what is R.
-Why we care about these three quantities and what is their physical meaning should be clear.
-Then the final products $\Nm$ and $\Tm$, and what is their physical meaning.
-\end{itemize}
-}
-
-To perform the comparison two specific rotations were selected, CR-2082 (2009, 05 April through 03 May), a deep minimum period between solar cycles (SCs) 23 and 24 characterized by virtually no ARs, and CR-2208 (2018, 02 September through 29 September), a rotation during the early declining fase of SC 24.
-
-To determine the thermodynamical structure of both rotations, the DEMT technique was applied to respective time series of EUV images covering each first half rotation.
-To study CR-2082 and CR-2208 data taken by the EUVI-B/STEREO and AIA/SDO instruments was used, respectively.
-
-In DEMT, the low corona in the height range $1.0$ to $1.25\,\mrsun$ is discretized in a spherical computational grid.
-The size of the tomographic cell (or voxel) is set to 0.01 \rsun \ in the radial direction, while is set 2\deg\ in both the latitudinal and longitudinal directions.
-We carried out a reconstruction using half of a solar rotation blocking the lines-of-sight comming from the disk (i.e.
-only using off-limb data).
-
-Using the high cadence of data available, one image every 10 minutes were used.
-The selected images were averaged in 6-hour intervals which, given the angular resolution, is the cadence needed to fully constrain the inversion problem, for a total of about 55 images to cover a half solar rotation.
-For both rotations, the first 14 days of data were used.
-
-EUV images are affected by instrumental stray light contamination, which can be corrected by deconvolution of the point spread function (PSF).
-While in the case of AIA images there is no reliable determination of its PSF, it has been well determined for EUVI-B by \citet{shearer_2012}.
-For this article, all EUVI images were stray-light corrected.
-For details of the impact on the tomographic results, refer to \citet{lloveras_ba2017}.
-
-\diego{
-Unlike in previous works, a 3D regularization scheme was applied, thus spurious artifacts (nduced by the previous longitude latitude regularization schemei) were minimized in the first two heights of the tomographic grid.}
-
-We refer the reader to \citet{frazin_2009} for a detailed description of the technique, and to \citet{vasquez_2016} for a recent review on all published work based on it.
-Here we summarize the key points of the technique that involves two consecutive procedures.
-
-In a first step, the time series of EUV images is used to solve a solar rotational tomography (SRT) problem, for each EUV band independently.
-As a result, the 3D distribution of the so called {filter band emissivity} (FBE) is determined for each band separately.
-The FBE, {an emissivity-type quantity}, is defined as the wavelength integral of the coronal EUV spectral emissivity and the telescope's passband function of each EUV channel.
-Line-of-sight (LOS) integration of the FBE provides synthetic images that can be quantitatively compared to the real data in the time series.
-To find the FBE, the tomographic problem is posed a global optimization problem in which the quadratic norm of the difference between all pairs of synthetic and real images is minimized.
-Spatial regularization terms are also included in the objective function as to minimize high frequency spurious artifacts that are due to the specific characteristics of the SRT sparse projection matrix \citep{frazin_2009,frazin_2000}.
-{Due to optical depth issues that may affect LOSs} passing very close to the limb, and to the decay of intensity with radii, the 3D maps produced by DEMT analysis typically cover the height range 1.02 to 1.23 \rsun \ \citep{frazin_2009}.
-
-\diego{COMO INTRODUZCO EL NIVEL DE REGULARIZACION? For each instrument, the DEMT analysis involves a cross-validation study to determine the optimal level of regularization.}
-
-{In a second step, the FBE values obtained for all bands in each voxel are used to constrain the determination of a {local differential emission measure} (LDEM) distribution, which describes the temperature distribution of the electron plasma contained in each individual tomographic grid voxel.
-Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}
-
-\begin{equation}\label{fbeldem}
-\FBE_i^{(k)}  = \int\,\textrm{d}T\,\LDEM_i(T)\,{\TRF}^{(k)}(T), \ \ \ {k=1,...,K}
-\end{equation}
-
-{
-Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}.
-These non-reconstructed voxels are indicated as black voxels in the Carrington maps of the reconstructed DEMT reults in Section \ref{resu}.
-}
-
-Once the LDEM is determined at each voxel, the average squared electron density $\langle \Ne^2 \rangle$ and the electron mean temperature $\Tm$ in the voxel can be computed by taking its zeroth and first moments over temperature.
-More specifically, at the $i$-th voxel,
-
-{
-\begin{eqnarray}\label{momento1}
- \Nsqmi = \langle \Ne^2 \rangle_i &=& \int\,\textrm{d}T\,\LDEM_i(T),\label{Ne} \\ 
-\label{momento2}
- \Tmi  = \langle \Te \rangle_i &=& \frac{1}{\langle \Ne^2 \rangle_i}\,\int\,\textrm{d}T\,T\,\LDEM_i(T),\label{Tm} 
-\end{eqnarray}
-}
-
-We define next a measure of the accuracy of the LDEM model to predict the tomographic FBEs in each voxel, as
-
-\begin{equation}\label{R}
-R_i \, \equiv \ (1/K) \, \sum_{k=1}^K \left| \, 1 - \FBE^{(k)}_{i,\rm syn}\,/\,\FBE^{(k)}_{i,\rm tom}\, \right| \,,
-\end{equation}
-
-being the average relative difference between the tomographic and the synthetic FBEs.
-The final product of DEMT is in the form of 3D maps of the electron density and mean temperature.
-These relationships {were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
-%\temp{Aclarar que consideramos Ne como $\sqrt{<\Ne ^2>}$.} {ALBERT: Yo creo que es mejor hablar de $\sqravgN$}
-
-%\temp{DEMT has been improved since the previously published work.
-We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.} \notebyalbert{NOTA de Albert: Explicá que hacés sin justificarte.
-Luego aclará como se hizo eso en trabajos previos, y cual es el impacto esperado.
-Puedo proveer un párrafo de ejemplo, pero creo que será mejor que vos escribas como te salga y yo luego edito.
-Algo muy importante para todo el paper: proponete escribir ``párrafos modulares".
-Es decir que, con las razonables limitaciones, puedan moverse de lugar, de orden, y sigan funcionando.
-No definiría hollow-tomography, es un término coloquial interno nuestro.
-Lo correcto es que al hablar de datos mucho más arribas expliques que los datos del disco no se utilizan, pero no le des un nombre a la tomografía.}
-
-\subsection{AWSoM simulations}\label{awsom}
-
-\noindent\notebyalbert{This section will summarize the AWSoM model. After a first version is written we will surely require some input from the Michigan friends. Points to cover:
-\begin{itemize}
-  \item Data input. Link with the data input for DEMT in terms of dates, etc. One paragraph.
-  \item Main physical and technical aspects (grid in particular) of the model.  One paragraph. 
-  \item Explain the artificially extended TR. One paragraph.
-  \item What are the products of the model we care about in this paper. One paragraph.
-\end{itemize}
-}
-
-In the transition region {(TR)}, the plasma heats up and becomes less dense {by} several orders of magnitude {over} a short distance.
-Modeling this region {realistically has a very high computational cost}.
-For this {reason,} the model uses {an artificially} extended {TR about $\approx 0.05\,\mrsun$ thick, as well as artificially large values for the electronic density and temperature as boundary conditions in $r=1\,\mrsun$.} Consequently, model results below {$\approx 1.05\,\mrsun$} were not taken into account in this article.
-
-\subsection{Tracing of results along fieldlines}\label{trace}
-
-\noindent\notebyalbert{This section will explain how the AWSoM magnetic model is used to trace the thermodynamic products of both DEMT and AWSoM along the fieldlines of AWSoM.
-This requires covering the following points:
-\begin{itemize}
-  \item A first paragraph qualitatively describing the process. This includes mentioning that the AWSoM products are first interpolated into the DEMT grid.
-  \item A short paragraph describing the numerical method used to trace field lines.
-We have a nice version of this in your previous paper.
-At this point the reader should understand that for each field line we have its geometry $\mathbf{r}(s)$ as a function of the distance $s$ along the loop, with $s(1\,\mrsun)\equiv 0$.
-  \item Explain very simply how then that for each voxel the middle point of the field line is selected and assigned the DEMT and AWSoM products of that cell.
-At this point the reader should understand that for each field line we have: $Q[r(s)]$, where $Q$ is any given quantity from either the DEMT model (specifically $\sqravgN$ and $\Tm$) or the AWSoM model (specifically $\Ne$ and $\Te$).
-  \item Explain fits to the DEMT results  $\sqravgN(r)$, $\Tm(r)$.
-  \item Explain then the classification of field lines.
-\end{itemize}
-}
-
-Aiming determination of the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid.
-Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = r{\rm d}\theta/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point.
-In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, for a total of $96,000$ starting points.
-Each traced field line is classified as ``open" if it intersects the source surface, set in this work at $r=6\,\mrsun$ (where lines become radial), or as ``closed" otherwise.
-In the case of closed magnetic lines, they are separated in two ``legs", from the base to the apex.
-
-%\diego{Of these legs, those whose size $L$ are smaller than the average lengths $\langle L \rangle$ are called small, and those with $L > \langle L \rangle$ ar called large.}
-\diego{
-In the case of closed magnetic field lines, legs {are} further classified as ``small" and ``large" upon their apex height being within or beyond the heigh average of the closed legs, respectively.
-}
-
-At this stage, all DEMT and AWSoM products, electron density and mean temperature in particular, can be traced along open and closed magnetic field lines.
-Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one).
-To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it.
-As a result, for each field line one data point per tomographic cell is obtained.
-This allows to analyze how density and temperature, comming from both models, vary with height along each individual field line.
-This approach was firstly used by \citet{huang_2012} to study inverted temperature structures in the solar minimum corona, and later on applied by \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.
-
-For each open field line, and for each leg of the closed ones, an exponential fit was then applied to the electron density and a linear fit applied to the electron temperature.
-For DEMT results the data points used were $\sqravgN(r)$ and $\Tm(r)$, and in case of AWSoM the data points used were $\Ne(r)$ and $\Te(r)$.
-The exponential and linear fit equations are described by
-
-\begin{eqnarray}\label{Nfit}
-\sqravgN &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]}\\
-\label{Tfit}
-\Tm &=& T_0\,+\,m\,h
-\end{eqnarray}
-\noindent
-where $h \equiv r - 1\,\mrsun$ is the coronal height measured from the photosphere.
-In the electron density fit, $\l\,[\mrsun]$ is the density scale height and $N_0\,[\cminvc]$ is the electron density at the footpoint ($h=0$) of the loop.
-In the electron temperature fit, $m\,[\MK/\mrsun]$ is the slope and $T_0\,[\MK]$ is the electron temperature at the footpoint of the loop.
-The slope $m$ is the radial gradient of the electron temperature along the loop, which we denote as $m = \dr\Tm$ hereafter, being $\dr\equiv\er\cdot\nabla$ the radial derivative operator, where $\er$ is the heliocentric radial unit vector.
-
-In the case of the electron density, the fitted function corresponds to the isothermal hydrostatic equilibrium solution, allowing for variation of the solar gravitational acceleration with height.
-This choice of function provides a straightforward means to directly evaluate how compatible is the observed coronal thermodynamical state with the hydrostatic solution.
-
-In the present work we focus on legs with increasing and decreasing temperatures in linear form.
-In other words, we selected those legs where the {Pearson correlation coefficient $\rho$ between temperature $T$ and radius $r$ meets $|\rhoTr| > 0.5$} {(with 95\% confidence level)}.
-In this way, those legs in which the DEMT results cannot ensure a noticeable change in temperature between the base and the apex, are discarded.
-
-The linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg.
-Both fits consider tomographic systematic uncertainty estimated in \citet{lloveras_2017}, i.e.
-$0.07$ MK for $\Tm$ and $4.0\,10^6 cm^{-3}$ for $\Ne$.
-
-To measure how good the quality of the fit are, a chi-square merit function was used (Section 15.2 \citet{recipes}).%, selecting only legs with 95\% confidence level.
-
-%el p-valor es un concepto estadístico, no veo xq deberia ser explicado. Lo que si, en el paper explicare bien las hipotesis nulas y de esa forma el p-valor queda bien claro.
-%El p-valor es una cuantificacion de con cuanta probabilidad de exito estas rechazando o aceptando una hipotesis en particular que se la suele denominar hipotesis nula.
-%En este caso, con 95$\%$ de seguridad estas rechazando las piernas que tienen un $pearson_x,y = 0$. Es decir te estarias quedando con aquellas que tienen una dependencia lineal entre x e y.
-%En el segundo caso, el test de hipotesis seria sobre la hip nula de que los datos provienen una funcion distribucion donde la recta fiteada de esos datos es el valor esperado de la distribucion.
-Con lo cual hacerle un test chi cuadrado te da una idea de cuan acertado o no es el ajuste.
-En este caso la hipotesis nula es que los datos provienen de esa distrib, con lo cual el chi deberia dar bajo y descartas los que dan valores altos con un 95$\%$ de seguridad.
-Eso es lo que representa el p-valor =0.05 en este caso (el area bajo la funcion distribucion, es decir, probabilidad).
-
-{To be selected a leg must meet all following conditions.}
-
-\diego{
-\begin{enumerate}
-\item 
-The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg.
-\item 
-The {value of the Pearson correlation coefficient meets $|\rhoTr| > 0.5$.}
-\item 
-The coefficient level of both the exponential and linear fit must be grater than \%90.
-\end{enumerate}
-}
-
-For the two targeted rotations, DEMT and AWSoM results were traced along the AWSoM field lines, which provides a way to characterize the global thermodynamic state of the inner solar corona and to compare them.
-To that end four different types of {legs} corresponding with four different types of magnetic structures were selected:
-%\temp{Hacer explicacion de los tipos de lineas bien secos, luego en fig 3 hacer notar que implica cada una en cuanto a estructura magnetica}\\
-\diego{
-\begin{itemize}
-\item Type 0 - Small legs (coming from closed field) in the latitudes range $[-50\mdeg,+50\mdeg]$, and $\rhoTr < -0.5$. 
- %This class thoroughly populates the equator of the Streamer belt during a minimum solar rotation.
-\item Type I - Small legs (coming from closed field) in the latitudes range $[-50\mdeg,+50\mdeg]$, and $\rhoTr > 0.5$. 
-%This class thoroughly populates the inner of the Streamer belt.
-\item Type II - Large legs (coming from closed field) in the latitudes range $[-90\mdeg,-40\mdeg] \cup [+40\mdeg,+90\mdeg]$, and $\rhoTr > 0.5$. 
-%This class is mostly populated by very large trans-equatorial field lines forming the envelope of the Streamer belt. 
-\item Type III - Open field lines in the latitudes range $[-90\mdeg,-60\mdeg] \cup [+60\mdeg,+90\mdeg]$, and $\rhoTr > 0.5$.
-\end{itemize}
-}
-
-\subsection{{Energy input flux}}\label{energia}
-
-\noindent\notebyalbert{This section will summarize how loop integrated energy quantities are computed from the DEMT products and the AWSoM magetic model alone.
-The summary will not include any derivation and will refer to Cecilia's paper.
-Only the results that are relevant are to be explicited.
-Start by explaining the model and assumptions, and end up summarizing the loop-integrated products (radiative and conductive fluxes).
-At the end the reader should understand that their sum is the enery input flux required at the coronal base to maintain the loop stable.
-This should be a very short section, as it is a summary of one previous paper alone.}
-
-%correcciones a hacer! DIEGO
-%Los términos de la Eq (10) requieren ser explicados.
-La explicación a conituación no es clara, y de hecho está mal escrita.
-La Eq.
-(7) se integra en el VOLUMEN CORONAL COMPLETO de cada tubo de flujo y se divide por el área basal del mismo.
-Utilizando la condición solenoidal de B se llega a la Eq.
-(7), dónde...
-y ahí deberían darse las expresiones de Phir y Phic porque no pertenecen a la literatura estandard, y explicar a continuación como todos los elementos de esas dos expresiones surgen de los fits de DEMT y del modelo magnético de AWSoM.
-Donde si se puede ahorrar mucho espacio es en lo previo, la Eq (8) podría no incluirse por ejemplo.
-Creo que ahora lo mejor es que trates de completar la explicación dando las expresiones de Phir y Phic, y luego vemos de como limarla, probablemente eliminando la ec.
-(8).
-y además el texto puede compactarse, corregirse y reordenarse mucho.
-Poné las unidades de las cantidades Phi entre paréntesis a continuación de $\Phi_{h,r,c}$.
-
-Due the difference between temperatures of transition region and solar corona, there must to be a heating mechanism that compensate all the losses present in the atmosphere and maintain stable the plasma temperature.
-Previous works have studied this mechanism by observations and modeling, but mostly for active regions.
-\citet{maccormack_2017} have developed a technique that estimate the heating injected into the loops during a period of minima activity.
-Using DEMT combined with an extrapolation of magnetic field, as we detailed before, they obtain the different plasma parameters along each magnetic loop, and therefore, compute the energy input flux required to maintain them stable.
-The model assume a simple energy balance for each magnetic flux tube, where the losses by radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated by some coronal heating power($E_h$) \citep{aschwanden_2004}:
-
-\begin{equation}\label{Balance}
-E_h(s) = E_r(s)+ E_c(s),
-\end{equation}
-
-\noindent
-where $s$ is the position along each magnetic flux tube and the powers are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.
-
-\noindent\notebyalbert{Trabajé todo lo naranja.
-Primero decidí que es mejor no numerar $E_c$ sino $F_c$.
-Eso te quedará claro cuando agregues las ecuaciones (11) y (12) que te indico más abajo y leas el último párrafo naranja de abajo, ahí cierra todo.
-Además describí que son los $\phi$ en forma correcta.
-El texto previo estaba muy flojón, entre otras cosas se hablaba de una (inexistente) ``conductive loss function" y de una (incorrectamente denominada) ``area along the loop".
-Obviamente luego de chequear este texto naranja borrá esta nota azul en particular.}
-
-{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, i.e.
-$E_c(s)=[1/A(s)]\,{\rm d}[A(s)\,F_c(s)]/{\rm d}s$, where $A(s)$ is the transversal area of the magnetic flux tube at position $s$.
-Under a quiescent solar corona plasma regime, the conductive flux is assumed to be dominated by the electron thermal conduction, described by the usual Spitzer model \citep{spitzer_1962}
-
-\begin{equation}\label{Fc}
-F_c(s)=-\kappa_0\,{T(s)}^{5/2}\,\frac{dT}{ds}(s),
-\end{equation}
-where $\kappa_0 = 9.2 \times 10^{-7}  {\rm erg\,sec^{-1}\,K^{-7/2}}$ is the Spitzer thermal conductivity.}
-
-Radiative power depends on the amount of plasma in certain temperatures that can radiate.
-The model estimate it by integrating the squared density multiplied by a radiative loss function $\Lambda(T)$.
-This function depends on plasma temperature and is calculated by the atomic database and the plasma emission model from CHIANTI \citep{delzanna_2015}.
-Then, the expression for radiative power obtained is:
-
-\begin{equation}\label{Er}
-E_r = \int\,\textrm{d}T\,\LDEM(T)\,\Lambda(T)
-\end{equation}
-
-{The energy balance given by Equation (\ref{Balance}) is then integrated in the volume of any given coronal magnetic flux tube.
-Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a field-line integrated version of that energy balance is found,
-\begin{equation}\label{FluxBalance}
-\phi_h = \phi_r + \phi_c.
-\end{equation}
-\noindent
-where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\
-
-\begin{equation}\label{phi_r}
-\phi_r = \left( \frac{B_0 \ B_L}{B_0 + B_L} \right) \int_{0}^{L} ds \ \frac{E_r(s)}{B(s)}
-\end{equation}
-
-\begin{equation}\label{phi_c}
-\phi_c = \left( \frac{B_0 \ F_{c,L} - B_L \ F_{c,0}}{B_0 + B_L} \right) 
-\end{equation}
-
-{Note that, for any given field line, all quantities in these two expresions can be computed from the DEMT and AWSoM models through Equations (\ref{Fc})-(\ref{Er}).
-Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to mantain a stable coronal structure.}
-
-\section{Results}\label{resu}
-
-\subsection{Tomographic Results}\label{demt_res}
-
-\noindent\notebyalbert{This section will show first the DEMT products in the form of Carrington maps at three heights, for the two target rotations.
-It will then show the latitude/longitude location of the four types of  magnetic loops (defined in Section 2.3) at a sample height.
-Then, for the each type of loop, we will show histograms of the values of different DEMT products traced along them, charerizing in a quantitative fashion the DEMT results in distinct magnetic structures.
-It will also include a quantitative comparison between the two target rotations of the median values of the DEMT products in each type of loop.}
-
-{As described in Section \ref{demt}, we carried out DEMT reconstructions of the coronal structure for target rotations CR-2082 and CR-2208 using STEREO/EUVI and SDO/AIA data, respectively.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared $\sqravgN$ and the electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}{, and the measure $R$ was calculated by means of Equation (\ref{R}).}}
-
-{As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations.
-Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic results ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
-Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}).
-Thick-black {curves indicate} the {open/closed boundaries of the magnetic field of the} AWSoM model.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
-\caption{Carrington maps of DEMT {products $\sqravgN$} (left panels) and $\Tm$ (right panels) for CR-2082.
-Top, middle and bottom panels show the results at three heliocentric heights, $1.025$, $1.065$ and $1.105\,\mrsun$ respectively.
-Black voxels correspond to non-reconstructed regions (see text in Section \ref{demt_res}) and thick-black curves indicate the open/closed boundaries.}
-\label{carmaps_demt_2082}
-\end{center}
-\end{figure}
-
-Target CR-2082 was highly axisymmetric (i.e, {characterized by} a high azymuthal symmetry) and showed two {small} ARs (active {regions), both near latitude} $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg${, respectively}.
-Target CR-2208 was {considerably less axisymmetric and} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$, respectively.}
-
-{The magnetically open and closed regions of the AWSoM model are associated to CHs and the the equatorial streamer belt, respectively.
-Consistently with that, the open/closed boundaries derived from the respective AWSoM model quite accurately match the regions which exhibit the strongest latitudinal gradient in the DEMT maps of both the electron density and temperature.}
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
-\caption{Same as Figure \ref{carmaps_demt_2082} but for CR-2208.}
-\label{carmaps_demt_2208}
-\end{center}
-\end{figure}
-
-{Visual inspection of Figures \ref{momento1} and \ref{momento2} shows that the DEMT reconstruction of the streamer belt is characterized by relatively larger values of density and temperature in comparison to the CHs.
-They also that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 24 and 25}, the temperature in the equatorial latitudes tends to decrease with height while in the mid-latitudes tends to {increase with height}.
-A similar behaviour is seen in CR-2208, belonging to the declining phase of {SC 25, but having a much less axisymmetric structure this characteristic is not so obvious.
-This thermodynamic structure} of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
-
-{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of DEMT measure $R$ defined by Equation (\ref{R}), at the same three heighs shown in Figures \ref{momento1} and \ref{momento2}.
-In most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$.
-The notable exception is to be found in the CHs of the target rotation analyzed based on AIA data.
-A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}.
-This point is further discussed below.}
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
-\caption{{Carrington maps of the measure $R$ defined by Equation (\ref{R}), for CR-2082 (left panels) and CR-2208 (right panels), at heights $1.025$, $1.065$ and $1.105\,\mrsun$, from top to bottom}.
-}
-\label{carmaps_R_2082_2208}
-\end{center}
-\end{figure}
-
-{To characterize the DEMT results in different magnetic structures, we traced} $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.
-For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected.
-For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.
-{As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
-%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
-%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
-%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
-%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
-\caption{\emph{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR2082 (left) and CR2208 (right).
-\emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs (see text) are shown in blue, red, violet and green color, respectively.}}
-\label{rpoint_demt}
-\end{center}
-\end{figure}
-
-{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
-Open legs are indicated in grey color and closed ones in black color.
-For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}).
-Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} {Of the 45000 legs selected for CR-2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III.
-On the other hand, of the 59000 legs selected for CR-2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.} \notebyalbert{Los números deben ser actualizados, o la frase eliminada.}
-
-{Type 0 (small down) legs mainly populate the equatorial latitudes.
-This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level {around the solar minimum beween SCs 24 and 25} by \citet{nuevo_2013}.
-Later on, \citet{lloveras_2017} showed {that} equatorial down loops in streamers were also to be found in the deep minimum between SCs {23 and 24}.
-Here, we verify the existence of this type of structure for the two target rotations.
-The relatively smaller population of down loops seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}.
-Type I (small up) mainly populate the mid-latitudes, while type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt.
-Finally, type III (open) legs populate of course the CHs.}
-
 %\notebyalbert{No comprendo esta frase:} \emph{This classification of types of lines automatically leads to specific regions arranged along all longitudes associated with different thermodynamic, with good symmetry between both hemispheres in both rotations.}
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2082_fulltriple_gradt.eps}
-\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
-\caption{Frequency histograms of the temperature radial gradient for the different {four types of legs} shown in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
-\label{gradt_demt}
-\end{center}
-\end{figure}
-
-Figure \ref{gradt_demt} shows frequency histograms (normalized to the total amount of selected field lines ) of the temperature radial gradient ($\dr\Tm$) for legs of type 0, I, II and III.
-The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs.
-For both rotations, {the median value of the temperature radial gradient is ${\rm Md}\left(\dr\Tm\right) \approx -2.5$, $+2.3$ and $+2.4\,\MK/\mrsun$} for legs of type 0, I and II, respectively.
-
-{The notable difference between both rotations is the characteristic {value ${\rm Md}\left(\dr\Tm\right)\approx +4.5\,\MK/\mrsun$} for legs of type III for CR-2208.
-This is related to the much larger $R$ score for the DEMT results along CH legs for CR-2208.
-In this case, DEMT performs poorly in modeling a LDEM that predicts the tomographic FBEs with reasonable accuracy.
-Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, shows that in most of the CH region the results for $\Tm$ below height $1.105\,\mrsun$ are quite uniform and artificially low.
-As it turns out, around and above height this height the score $R$ is lower and the temperature results are more reliable.
-As a result, the temperature gradient along these legs is artificially larger, with the linear fit trying to simultaneously fit the artificially low values of $\Tm$ at lower heights.
-In general, the DEMT results in the CH region based on AIA data are thus much less reliable than in the rest of the analysis.
-We will return to this point in the conclusion section.}
+----------------------------------------------------
 
@@
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
-\caption{{Statistical distribution of DEMT results traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}.
-From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$.
-Results for target rotations CR-2082 and CR-2208 are shown in blue and red color, respectively.
-In each panel the median value $m$ is indicated.} }
-\label{histos_fulldemt}
-\end{center}
-\end{figure}
-
-{For both rotations, Figure \ref{histos_fulldemt} shows, in a statistical fashion, the DEMT results traced along field lines discriminated by field line type}.
-From top to bottom {results are shown for} type 0 to type III {field lines}{, respectively}.
-From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$ {(the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.
-
-{Table \ref{tabla_demt} summarizes a} quantitative comparative analysis between the results of the two {target rotations}.
-For CR-2082 quantities are expressed as absoulte values, {while} for CR-2208 they are informed {as a precentual variation} relative to the corresponding results for CR-2082.
-{The following major results, both concerning the structure of each rotation individually as well as their comparison, can be drawn.}
-
-\begin{table}[h!]
-\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
-% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
-\hline
-Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
-       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
-\hline
-0    & 1&26 &(\Mi&17&4\%)  &   7&3 &(\Pl&13&6\%) &   1&09 &(\Pl&24&7\%) \\
-I    & 1&13 &(\Mi&14&1\%)  &   8&3 &(\Pl&18&1\%) &   1&29 &(\Pl&20&1\%) \\
-II   & 0&97 &(\Mi&20&6\%)  &   8&9 &(\Pl&29&1\%) &   1&33 &(\Pl&16&5\%) \\
-III  & 0&66 &(\Mi&16&2\%)  &   7&7 &(\Pl&11&4\%) &   0&98 &(\Pl&~6&1\%) \\
-\hline          
-\end{tabular}
-\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
-For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.
-\notebyalbert{Propongo que para todas las cantidades absolutas de la Tabla 1 informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
-Doy dos ejemplos para no dejar dudas.
-Para $\NCB$ de Type-II: $1.0\,(-21\%)$.
-Para $\aTm$ de Type-III: $1.0\,(+6\%)$.}}
-\label{tabla_demt}
-\end{table}
-
-{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer regions of the equatorial streamer belt, progressively exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature.
-In both rotations also, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.}
-
-{A comparison of the results between the two rotations shows that, compared to CR-2082, target rotation CR-2208 was characterized by $\approx 15-20\%$ lower values of the electron density at the coronal base, $\approx 10-30\%$ larger values of density scale height, and $\approx 15-25\%$ larger values of the electron temperature.} \notebyalbert{Los números de esta frase deben ser consistentes con los que finalmente informe la Table 1, redondeando los rangos característicos observados para los diversos tipos de línea (consultame!).
-La Table 1 debe a su vez resumir lo que muestra la Figure 6.
-Destacalo en tu color cuando lo hayas hecho así le presto atención.}
+----------------------------------------------------
 
@@
 
-{To analyze the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the clasification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).
-{For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.}
-
-\begin{figure}[ht]
-\begin{center}
-\includegraphics[width=0.495\textwidth]{figs/histocr2082_ccdownenergia.eps}
-\includegraphics[width=0.495\textwidth]{figs/histocr2208_ccdownenergia.eps}
-\includegraphics[width=0.495\textwidth]{figs/histocr2082_ccenergia.eps}
-\includegraphics[width=0.495\textwidth]{figs/histocr2208_ccenergia.eps}
-\includegraphics[width=0.495\textwidth]{figs/histocr2082_cgenergia.eps}
-\includegraphics[width=0.495\textwidth]{figs/histocr2208_cgenergia.eps}
-\caption{{Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right).
-From top to bottom, panels show the results for loops of type 0, I and II, which are loops for which both legs meet the criteria from Section \ref{trace}.}}
-\label{energia_demt}
-\end{center}
-\end{figure}
-
-{For both rotations, the value of the integrated radiative power $E_r$, measured by the quantity $\phi_r$, is largest for loops of type 0.
-This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors contributing to maximize $E_r$ for loops of type 0.
-As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0 are characterised by the relatively largest values of electron density.
-Also, in the range of sensitivity of the EUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$.
-According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterised by {values of temperature that are progressively larger and farther} from the value $\Tc$, for both rotations.}
-
-{In the case of the quantity $\phi_c$, its sign depends on that of the conductive flux $F_c$.
-As shown in \citet{maccormack_2017}, down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, which is verified in Figure \ref{energia_demt}.}
-
-{As a result of the radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of loop.
-These values are similar to those reported by \citet{maccormack_2017}.
-Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$.
-As shown by \citet{maccormack_2017}, this result affects only the smallest loops (a subset of the type 0 class) and it is due to the limited temperature sensitivity of the instrumental passbands.
-The radiative loss term is calculated based on plasma emission detected by the three coronal bands of EUVI and the three bands of AIA used.
-Though this should account for most of the coronal plasma, there surely is additional emission that is out of the range of sensitivity of the instruments used.
-Thus, the positive term $\phi_r$ is most liekly understimated, leading to values $\phi_h<0$ in loops of type 0, which are characterized by $\phi_c<0$.}
+----------------------------------------------------
 
@@
 
-\subsection{Tomography and Models}\label{awsom_res}
+----------------------------------------------------
 
-\noindent\notebyalbert{This section will show the results of AWSoM for $N_e$ and $T_e$, and how they compare with the corresponding results of DEMT ($\sqravgN$ and $\Tm$).
-It will first show the Carrington maps of $N_e$ and $T_e$ at the same three heights we showed the same maps for the DEMT results.
-Then it will show the lat/lon location of loops of type I, II and III at a middle height, just loke for DEMT results.
-As the two targets are highly axis-symmetric, a first quantitative comparison between AWSoM and DEMT will be shown as longitude-averaged latitudinal profiles of the results of both models at a sample height.
-To make comparisons in distinct magnetic structures, we will also show the average radial dependence of results for loops of type I, II and III, overplotting the AWSoM and the DEMT results.
-For the tree types of loops we will show histograms of the DEMT and AWSoM products along field lines.
-This is a LOT of information from which and we need to pull out a few clear conclusions.}
-
-Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature, for both rotations.
-These Figures show the results at the same three heights selected for visualisation of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}.
-As in those, thick-black curves indicate the magnetic open/closed boundaries based on the magnetic field of the AWSoM model.
-Visual inspection of these maps shows that the AWSoM model for both rotations is highly axysimmetric, as the tomographic model.
-
-\diego{A visual inspection of these maps shows that both reconstructions are very axysimmetric for $\Ne$ and $\Te$ as well.
-The closed region is denser and hotter than the open region.
-The density and temperature gradients are maximum in the open-close boundary.
+ with latitudinal gradients of both density and temperature  maximum in the open-close boundary.
 The open field regions in low latitudes maintain thermodynamic values associated with open regions.} The reconstruction of CR-2082 does not show clear the ARs, while CR-2208 shows a well reconstruction of both AR around latitude-longitud $+5\mdeg$, $140\mdeg$ and $+5\mdeg$, $300\mdeg$.
 In both rotations the open-closed boundaries derived from the AWSoM model match the shape of the contour levels of both the electron density and the electron temperature.
-
-%\diego{comparacion visual entre estas dos figuras y als dos de DEMT.}
-
-The same intensity scales in both density and temperature can be observed between the tomographic results and those of AWSoM in both rotations, as well as the same thermodinamic structures.
-That is, equatorial latitudes, mid laditudes and the open regions.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1105_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1105_Rsun.pdf}
-\caption{Carrington maps of density (left panels) and temperature (right panels) obtained with AWSoM model for the same three heights shown in Figure \ref{carmaps_demt_2082}.}
-\label{carmaps_awsom_2082}
-\end{center}
-\end{figure}
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1105_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1105_Rsun.pdf}
-\caption{Same as Figure \ref{carmaps_awsom_2208} for CR-2208.}
-\label{carmaps_awsom_2208}
-\end{center}
-\end{figure}
-
-%\temp{Se presentan los midpoints para awsom que lucen mas rellenos xq no hay down loops y todo es super suave.}
-
-In the same way as in Section \ref{demt_res}, the model results were traced along the magnetic lines obtained with it.
-This allowed to obtain $\Ne(r)$ and $T_e(r)$ along the magnetic lines and fit them to the Equations \ref{Nfit} and \ref{Tfit}.
-
-The actual version of the AWSoM model can not reproduce down legs, so for a further comparison we only select lines of type I, II and III of those meeting the criteria described in Section \ref{trace}.
-
-As a way to understand the distribution of legs, Figure \ref{rpoint_awsom} shows the latitudinal-longitudinal location of the traced legs at top and the selected fitted legs meeting the criteria at $1.105\,\mrsun$ for both rotations, in the same way as in Section \ref{demt_res}.
-In red the type I lines, populating mostly the entire streamer.
-In violet the type II lines, populating the edge that assemble the envelope around the streamer, and in green dots the type III lines, populating the coronal holes.
-
-The reader may notice that these structures are the same as those in Figure \ref{rpoint_demt} but more filled.
-The cause is twofold, on the one hand the same magnetic model was used to trace both DEMT and AWSoM results, on the other hand is because giving the model smoother results, fewer fitted lines are filtered.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_awsom_paper_test_Rpoint-map.pdf}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_awsom_paper_test_Rpoint-map.pdf}
-%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.pdf}
-%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.pdf}
-\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its legs in types I, II and III. The model does not exhibit legs of type 0.}}
-\label{rpoint_awsom}
-\end{center}
-\end{figure}
-
-To highlight the latitudinal structures observed in Figures \ref{carmaps_demt_2082} and \ref{carmaps_awsom_2082} for CR-2082 as well as Figures \ref{carmaps_demt_2208} and \ref{carmaps_awsom_2208} for CR-2208, Figure \ref{perf_lat} shows for both rotations the latitudinal variation  of both the electron density and the electron mean temperature at the height $r=1.105\,\mrsun$, averaged over all longitudes (excluding the AR).
-DEMT results are shown in blue lines while AWSoM results in red.
-While the temperature shows a maximum in each hemisphere, the density has a simpler behavior, with higher values in the low-latitudes of the streamer and a nearly monotonic decrease towards larger latitudes.
-The vertical black lines denotes the average of the open-close boundary in both hemispheres to each rotation.
-
-\diego{Me gustaria hacer un comentario de cierre para esta figura que refiera las Figuras 3 y 9, como la linea de abajo, y que conecte con los histogramas que vienen a continuacion.
-Si no queda bien, hay que mover esta figura entre la actual figura 8 y 9.}
-
-This longitude-averaged behaviors match well with the physical locations of the legs shown in Figures \ref{rpoint_awsom} and \ref{rpoint_demt}.
-
-According to the visual inspection on the maps of carrington, the latitudinal profiles comparing both DEMT and AWSoM results are on the same scale.
-Little difference in density is observed in CR-2208 and in temperature in CR-2082, while DEMT in CR-2082 was $20\%$ denser.
-Finally, DEMT results for CR-2208 were $25\%$ hotter in the streamer and $30\%$ colder in the polar zone than AWSoM.
-Density profiles on AWSoM show an increase around the polar zone, which seems like an artifice.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105.eps}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105.eps}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105.eps}
-\caption{Longitude-averaged latitudinal dependence of the electron density (top) and temperature (bottom) for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$.
-The left (right) panels correspond to CR-2082 (CR2208).
-The vertical black line indicates the longitude-averaged latitudes of the open/close magnetic boundary in both hemispheres.
-\notebyalbert{(by Albert): The idea of this Figure is to show how DEMT and AWSoM compare AS A FUNCTION OF LATITUDE at an intermediate height of the DMET grid, averaged in longitude (excluding zones with ARs).}}
-\label{perf_lat}
-\end{center}
-\end{figure}
-
-To summarize the comparison between both results during both rotations at full height, it is shown in Figure \ref{perfiles_promedio} the average fits of $\Ne(r)$ and $T_e(r)$ for legs of type I (blue), II (red), and III (green) for both rotations.
-
-In average all temperature and density behavior from both results are on the same scale.
-The coronal base densities of AWSoM were lower than those of DEMT in CR-2082 and higher in CR-2208.
-The fact that the density decays to similar values between both results suggests a similar height scale.
-Onthe other hand basal temperature of AWSoM was lower in both rotations, but the temperature gradients are very similar en each type of legs, showing a very similar increase of temperature with height.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
-\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (red), II (violet), and III (green), for CR-2082 (top panels) and CR-2208 (bottom panels).
-Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.} \notebyalbert{(by Albert): The idea of this Figure is to show how DEMT and AWSoM compare AS A FUNCTION OF HEIGHT, in three distinct types of magnetic structures, and for both rotations.}}
-\label{perfiles_promedio}
-\end{center}
-\end{figure}
-
-Tu summary the statistical comparison, Figure \ref{histos_2082} and \ref{histos_2208} shows the statistical results of both rotations for the three types of field lines traced with DEMT (blue) and AWSoM results (red).
-From left to right the panels show the statistical distribution of $\NCB$, $\lN$ and $\aTm$.
-For all types of lines, Table \ref{tabla_comp} summarizes the median value of the statidtical distribution of each physical quantity derived from the analysis.
-The DEMT quantities are expressed as absoulte values, while for ASWSoM they are informed relative to the corresponding result for DEMT.
-
-\diego{aca podria ir un pequeño parrafo que resuma las diferencias.
-Pero justo a continuacion empiezan las conclusiones y uno tiende a repetir, no se como encararlo para que no quede dos veces lo mismo y tan pegado uno de lo otro.}
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
-\caption{{Statistical distribution of DEMT (blue) and AWSoM (red) results traced along legs of type I, II and III (from top to bottom), as defined in Section 2.3.
-From left to right: electron density at the lowest coronal height of the AWSoM model $\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
-In each panel the median value $m$ is indicated.}}
-\label{histos_2082}
-\end{center}
-\end{figure}
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_Tm.eps}\\
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_Tm.eps}\\
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_Tm.eps}
-\caption{Same as Figure \ref{histos_2082} for CR-2208.}
-\label{histos_2208}
-\end{center}
-\end{figure}
-
-%This plot (E) has never been shown before and I believe it is a very nice result.
-There are of course previous studies on this, but this would be the first time this is evaluated with tomography.
-It is not the terminal speed, but it already shows the fast/slow components.
-We can show this, or we can go for more.
-Diego can QUANTIFY the correlation by carefully mapping all open field lines at 6 Rsun down to the DEMT region.
-He needs to code a bit more to achieve this goal, but we believe it is worth.
-With that tool done Diego can explore other terminal values of quantities of the AWSoM model and the DEMT results below (expansion factor maybe?).
-This will be nice to do also for the July-2-2019 Eclipse rotation that we will analyze after this paper.
-
-\begin{table}
-\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
-% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
-\hline
-Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
-       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
-\hline
-CR-2082\\
-I  & 1&13 &(\Mi&11&9\%)  &   8&3 &(\Mi&~2&4\%) &   1&29 &(\Mi&10&8\%) \\
-II  & 0&97 &(\Mi&22&5\%)  &   8&9 &(\Pl&~2&2\%) &   1&33 &(\Mi&~4&5\%) \\
-III  & 0&66 &(\Mi&16&8\%)  &   7&7 &(\Mi&~9&1\%) &   0&98 &(\Mi&~9&2\%) \\
-\hline          
-CR-2208\\
-I  & 0&97 &(\Pl&~9&3\%)  &   9&8 &(\Mi&~7&1\%) &   1&55 &(\Mi&14&2\%) \\
-II  & 0&77 &(\Pl&11&7\%)  &  11&6 &(\Mi&17&2\%) &   1&55 &(\Mi&~9&7\%) \\
-III  & 0&56 &(\Mi&~1&9\%)  &   8&6 &(\Mi&16&3\%) &   1&04 &(\Mi&~9&6\%) \\
-\end{tabular}
-\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
-DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.
-\albert{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
-Ejemplo para CR-2082 $\NCB$ de Type-II: $1.0\,(-23\%)$.
-Ejemplo para CR-2208 $\lambda_N$ de Type-II: $12.0\,(-17\%)$.
-Ejemplo para CR-2208 $\aTm$ de Type-II: $1.6\,(-10\%)$.}}
-\label{tabla_comp}
-\end{table}
-
-Figure \ref{perf_lon_vr} show the longitude-averaged AWSoM radial wind speed $V_r$ at $6\,\mrsun$, where all field lines are open.
-The heliocentric current sheet (HCS) location is indicated by the minimum of the speed curve.\\
-\diego{can we say something without having traced the lines?} \notebyalbert{(by ALBERT) Todo el punto de la última Figura es precisamente decir algo.
-La comparación con la Figura 10 muestra una anti-correlación entre la densidad basal de DEMT y la velocidad terminal de AWSoM.}
-
-For each rotation, everything to the south of the HCS maps down to the southern open region in the Figures \ref{perf_lat}, and the same for the northern hemisphere, showing an anti-correlation between $\Ne$ at low heights and high $V_r$ at $6\,\mrsun$.
-
-\diego{Voy a intentar jugar con las lineas tipo 3 aumentando su cota inferior de latitud para ver si los histogramas de temp media dejan de ser tan dispersos y se vuelven mas sub-1MK. }
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995.eps}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
-\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6.0\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).} \notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the absolute minimum indicates the location of the HCS at this height.
-I believe it is interesting to compare these two curves with Figure 10.
-Note that while in this Figure all latitudes are magnetically open, in Figure 10 only the part at latitudes larger than the vertical black lines are open.
-Note that DEMT shows that in the open low corona $N_e$ decreases from the O/C boundary towards the poles, anti-correlating with the AWSoM terminal speed, which is nice.
-In order to quantify this anti-correlation we need to trace the terminal speed and the DEMT $N_e$, which we may need to do with the help of Chip and Nishtha.
-Chip, we can discuss this idea over Skype after Xmas if you are around.}}
-\label{perf_lon_vr}
-\end{center}
-\end{figure}
-
-\section{Discussion}\label{discu}
-
-\noindent\notebyalbert{(by Albert) This section will discuss and summarize some main conclusions, possibly in three groups: a) DEMT analysis alone (including thermodynamical structure, up/down loops, energy considerations, etc.), b) Comparison AWSoM/DEMT (longitude-averaged latitudinal profiles, height-dependence profiles in different magnetic structures, etc), and c) Correlation betweem AWSoM terminal wind speed and DEMT basal density, I will expand on this later this week as this may require help from Michigan).}
-
-\diego{NOTE: Here is a paragraph describing the empirical successes in the reconstruction of both rotations.}
-
-*In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI.
-In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, analyzed a single target using both instruments independently.
-They found that while the density product is essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e.
-$\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$.
-Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was $\approx 10-15\%$ hotter than CR-2082 throughout the streamer belt region.
-As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region.
-These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\lesssim 5\%$ and $\approx 2\%$ for the electron temperature and density, respectively.
-
-*Coronal magnetic structures for which the temperature increases/decreases with height in the range of heights covered by DEMT, $1.02–1.22\,\mrsun$, have been dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first observed their presence by means of DEMT.
-As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
-Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}.
-In a recent study by \citet{schiff_2016}, down and up loops have been successfully reproduced by a numerical implementation of a 1D steady-state model that considers time-averaged heating rates.
-
-We found down legs in the DEMT reconstructions mainly in the equatorial latitudes, being a greater quantity and better distribution along longitudes in CR-2082 than in CR-2208.
-\citet{nuevo_2013} showed a decrease in the amount of down loops as the solar activity increases, which is consistent with the results shown in this article.
-
-*We can see, on type 0 loops, a median value of energy input flux ($\phi_h$) for CR-2082 twice bigger than CR-2208.
-In both rotations this magnitude has negative values, this can refer to some loops where loop-integrated radiative flux $\phi_r$) is too small in comparison with the larger gradients of negative conductive flux $\phi_c$), resulting in negative energy input flux.
-
-This effect can be due a subestimation of the density present in the loop or the limited range of temperature used to reconstruct tomographic parameters, that can affect the compute of radiative power.
-Nevertheless, this population represent lower than the \diego{ALGÚN PORCENTAJE$\%$} of total population in both cases.
-
-Consistent that the density in CR-2082 was higher, the $\phi_r$ was also higher.
-In both rotations the magnitudes in the temperature gradients are similar, but the temperatures in CR-2208 were consistently higher at all heights, resulting in a larger $\phi_c$ in module.
-This results are in agree with the observations of \citet{maccormack_2017}.
-
-\diego{THE AR of CR-2082 wasn't well modeled by AWSoM.}
-
-In both rotations, AWSoM and DEMT resutls shows same termodynamic structures along latitude and longitude with very comparable values between $1.055 - 1.25\,\mrsun$
-
-Figure \ref{histos_2082} and Table \ref{tabla_comp} indicate that AWSoM reconstruction of CR-2082 was found to be less dense $\approx 11-22\%$ and colder $\approx 5-10\%$.
-
-Both reconstructions of CR-2208 reconstructed the ARs with very similare values and in almost the same latitude-longitude location.
-Figure \ref{histos_2208} and Table \ref{tabla_comp} indicate that AWSoM reconstruction of CR-2208 was found to be denser $\approx 0-10\%$ and colder $\approx 10-15\%$.
-
-CR-2208 was $\approx 10-15\%$ hotter than CR-2082 throughout the streamer belt region.
-As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region.
-These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\lesssim 5\%$ and $\approx 2\%$ for the electron temperature and density, respectively.
-
-\diego{I would like to say something about FIgure 10. Maybe the weird tale in AWSoM Ne in the poles. Ideas?}\\
-
-%\diego{We could say something about the anti correlation between speed and density and not get into the trace because issues do always appear and we don't have much time, and we all want to be happy in january.
-Unless the collaborators find easy to make this part.}
-
-%% Figure 
-%
-% \begin{figure} 
-% \centerline{\includegraphics[width=0.5\textwidth,clip=]{<fig.eps>}}
-% \caption{}%\label{fig:?}
-% \end{figure}
-
-%% Table
-%
-% \begin{table}
-% \caption{}%\label{tbl:?}
-% \begin{tabular}{}     
-% \hline
-% \multicolumn{2}{c}{<>}
-% <data>
-% \hline
-% \end{tabular}
-% \end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Appendix
-%
-% \appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Acknowledgements
-%
-% \begin{acks}
-%
-% \end{acks}
-
-%%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Bibliography
-%
-% Using BibTeX
-%
-\bibliographystyle{spr-mp-sola}
-\bibliography{solphys_dglloveras}  
-%
-% Without BibTeX 
-% \begin{thebibliography}{}
-% \bibitem[\protect\citeauthoryear{Author}{Year}]{key}
-%   <bibliographical entry>
-%
-% \bibitem[\protect\citeauthoryear{}{}]{}
-%   
-%  
-% \end{thebibliography}
-
-\end{article} 
-\end{document}

### 2020-01-11 lloveras_2020.tex
modificaciones

@@
 Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24.
-Tomographic reconstructions and results of the model are analyzed in distinct coronal magnetic structures.
+Tomographic reconstructions and results of the model are {analysed} in distinct coronal magnetic structures.
 We study magnetically closed structures associated with the equatorial streamer belt, as well as magnetically open regions enclosing it.
@@
 For this article, all EUVI images were stray-light corrected.
-For details of the impact on the tomographic results, refer to \citet{lloveras_ba2017}.
+For the details of impact in $\Nm$ and $\Tm$, refer to \citet{lloveras_ba2017}.
 
@@
 We refer the reader to \citet{frazin_2009} for a detailed description of the technique, and to \citet{vasquez_2016} for a recent review on all published work based on it.
-Here we summarize the key points of the technique that involves two consecutive procedures.
+Here we summarize the key points.
+The technique involves two consecutive procedures.
 
@@
 \diego{
-In the case of closed magnetic field lines, legs {are} further classified as ``small" and ``large" upon their apex height being within or beyond the heigh average of the closed legs, respectively.
+In the case of closed magnetic field lines, legs {are} further classified as ``small" and ``large" upon their apex height being within or beyond the lenght average of the closed legs, respectively.
 }
@@
 As a result, for each field line one data point per tomographic cell is obtained.
-This allows to analyze how density and temperature, comming from both models, vary with height along each individual field line.
+This allows to analyze how density and temperature, coming from both models, vary with height along each individual field line.
 This approach was firstly used by \citet{huang_2012} to study inverted temperature structures in the solar minimum corona, and later on applied by \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.
@@
 
-For the two targeted rotations, DEMT and AWSoM results were traced along the AWSoM field lines, which provides a way to characterize the global thermodynamic state of the inner solar corona and to compare them.
-To that end four different types of {legs} corresponding with four different types of magnetic structures were selected:
-%\temp{Hacer explicacion de los tipos de lineas bien secos, luego en fig 3 hacer notar que implica cada una en cuanto a estructura magnetica}\\
+{Coronal magnetic structures for which their temperature increases/decreases with height (in the inner corona) have been dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies.
+As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
+Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}.
+In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}
+
+{To characterize the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model.
+Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types in this work:}
+
 \diego{
@@
 }
+{In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed.}
 
@@
 
-Target CR-2082 was highly axisymmetric (i.e, {characterized by} a high azymuthal symmetry) and showed two {small} ARs (active {regions), both near latitude} $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg${, respectively}.
-Target CR-2208 was {considerably less axisymmetric and} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$, respectively.}
-
-{The magnetically open and closed regions of the AWSoM model are associated to CHs and the the equatorial streamer belt, respectively.
-Consistently with that, the open/closed boundaries derived from the respective AWSoM model quite accurately match the regions which exhibit the strongest latitudinal gradient in the DEMT maps of both the electron density and temperature.}
+{Both target rotations are highly axisymmetric, i.e.
+characterized by a high azymuthal symmetry.
+Rotation CR-2082} showed two {small} ARs (active {regions), both near latitude} $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg${, respectively}.
+{Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$, respectively.}
+
+{The magnetically open and closed regions of the AWSoM model are associated to CHs and the equatorial streamer belt, respectively.
+Consistently with that, the {location of the} open/closed boundaries derived from the respective AWSoM model quite accurately match {the regions of the DEMT maps which exhibit the strongest latitudinal gradient of both the electron density and temperature.}}
 
@@
 
-{Visual inspection of Figures \ref{momento1} and \ref{momento2} shows that the DEMT reconstruction of the streamer belt is characterized by relatively larger values of density and temperature in comparison to the CHs.
-They also that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 24 and 25}, the temperature in the equatorial latitudes tends to decrease with height while in the mid-latitudes tends to {increase with height}.
-A similar behaviour is seen in CR-2208, belonging to the declining phase of {SC 25, but having a much less axisymmetric structure this characteristic is not so obvious.
+{{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively larger values of density and temperature in comparison to the CHs.
+They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 24 and 25}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the declining phase of {SC 25, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious.
 This thermodynamic structure} of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
 
-{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of DEMT measure $R$ defined by Equation (\ref{R}), at the same three heighs shown in Figures \ref{momento1} and \ref{momento2}.
+{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of {the DEMT} measure $R$ defined by Equation (\ref{R}), at the same three heights shown in Figures \ref{momento1} and \ref{momento2}.
 In most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$.
-The notable exception is to be found in the CHs of the target rotation analyzed based on AIA data.
+The notable exception is to be found in the CHs of the target rotation {analysed} based on AIA data.
 A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}.
@@
 \emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs (see text) are shown in blue, red, violet and green color, respectively.}}
+{The location of} type 0, I, II and III legs {is shown} in blue, red, {magenta and cyan} color, respectively.}}
 \label{rpoint_demt}
@@
 {For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
-Open legs are indicated in grey color and closed ones in black color.
+Open legs are indicated in gray color and closed ones in black color.
 For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}).
 Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} {Of the 45000 legs selected for CR-2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III.
-On the other hand, of the 59000 legs selected for CR-2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.} \notebyalbert{Los números deben ser actualizados, o la frase eliminada.}
+Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} \diego{Of the 48000 legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III.
+On the other hand, of the 57000 legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III.
+(NOTA: Estos numeros estan actualizados,  pensaba en ponerlos solo porque en ningun momento hablamos de la proporcion, solo se muestran los histos de gradT)}
 
 {Type 0 (small down) legs mainly populate the equatorial latitudes.
-This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level {around the solar minimum beween SCs 24 and 25} by \citet{nuevo_2013}.
+This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level {around the solar minimum between SCs 24 and 25} by \citet{nuevo_2013}.
 Later on, \citet{lloveras_2017} showed {that} equatorial down loops in streamers were also to be found in the deep minimum between SCs {23 and 24}.
@@
 \includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
-\caption{Frequency histograms of the temperature radial gradient for the different {four types of legs} shown in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
+\caption{Frequency histograms of the temperature radial gradient for {the four types of legs} in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
 \label{gradt_demt}
@@
 Figure \ref{gradt_demt} shows frequency histograms (normalized to the total amount of selected field lines ) of the temperature radial gradient ($\dr\Tm$) for legs of type 0, I, II and III.
-The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs.
+The lack of population around values close to zero is due to the requirement $|\rhoTr| > 0.5$ which discards quasi-isothermal legs.
 For both rotations, {the median value of the temperature radial gradient is ${\rm Md}\left(\dr\Tm\right) \approx -2.5$, $+2.3$ and $+2.4\,\MK/\mrsun$} for legs of type 0, I and II, respectively.
@@
 In this case, DEMT performs poorly in modeling a LDEM that predicts the tomographic FBEs with reasonable accuracy.
-Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, shows that in most of the CH region the results for $\Tm$ below height $1.105\,\mrsun$ are quite uniform and artificially low.
+Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, {reveals that in most of the CH region the result for $\Tm$ below height $1.105\,\mrsun$ is quite uniform and artificially low}.
 As it turns out, around and above height this height the score $R$ is lower and the temperature results are more reliable.
@@
 \includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
-\caption{{Statistical distribution of DEMT results traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}.
-From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$.
-Results for target rotations CR-2082 and CR-2208 are shown in blue and red color, respectively.
-In each panel the median value $m$ is indicated.} }
+\caption{{Statistical distribution of {DEMT results for rotations CR-2082 (blue) and CR-2208 (red)} traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}.
+From left to right: {electron density $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$,} electron density scale height $\lN$, {and loop-averaged temperature $\aTm$.
+In each panel} the median value $m$ is indicated.} }
 \label{histos_fulldemt}
@@
 {Table \ref{tabla_demt} summarizes a} quantitative comparative analysis between the results of the two {target rotations}.
-For CR-2082 quantities are expressed as absoulte values, {while} for CR-2208 they are informed {as a precentual variation} relative to the corresponding results for CR-2082.
+For CR-2082 quantities are expressed as absolute values, {while} for CR-2208 they are informed {as a percentual variation} relative to the corresponding results for CR-2082.
 {The following major results, both concerning the structure of each rotation individually as well as their comparison, can be drawn.}
@@
 \begin{table}[h!]
-\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
-% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
+\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
 \hline
-Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
-       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
+Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
+        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
 \hline
-0    & 1&26 &(\Mi&17&4\%)  &   7&3 &(\Pl&13&6\%) &   1&09 &(\Pl&24&7\%) \\
-I    & 1&13 &(\Mi&14&1\%)  &   8&3 &(\Pl&18&1\%) &   1&29 &(\Pl&20&1\%) \\
-II   & 0&97 &(\Mi&20&6\%)  &   8&9 &(\Pl&29&1\%) &   1&33 &(\Pl&16&5\%) \\
-III  & 0&66 &(\Mi&16&2\%)  &   7&7 &(\Pl&11&4\%) &   0&98 &(\Pl&~6&1\%) \\
+0    & 1&24 &(\Mi&19\%)  &   7&4 &(\Pl&~3\%) &   1&09 &(\Pl&24\%) \\
+I    & 1&15 &(\Mi&10\%)  &   7&5 &(\Pl&29\%) &   1&25 &(\Pl&24\%) \\
+II   & 0&98 &(\Mi&20\%)  &   9&9 &(\Pl&19\%) &   1&36 &(\Pl&16\%) \\
+III  & 0&65 &(\Mi&15\%)  &   7&6 &(\Pl&12\%) &   0&97 &(\Pl&~7\%) \\
 \hline          
@@
 Para $\NCB$ de Type-II: $1.0\,(-21\%)$.
-Para $\aTm$ de Type-III: $1.0\,(+6\%)$.}}
+Para $\aTm$ de Type-III: $1.0\,(+6\%)$.}\diego{Si aca redondeo, Ncb de type 0 y I toman el mismo valor 1.2, y si no redondeo la temp en type III se ve lindo que sea sub-MK.
+}}
 \label{tabla_demt}
@@
 
-{A comparison of the results between the two rotations shows that, compared to CR-2082, target rotation CR-2208 was characterized by $\approx 15-20\%$ lower values of the electron density at the coronal base, $\approx 10-30\%$ larger values of density scale height, and $\approx 15-25\%$ larger values of the electron temperature.} \notebyalbert{Los números de esta frase deben ser consistentes con los que finalmente informe la Table 1, redondeando los rangos característicos observados para los diversos tipos de línea (consultame!).
-La Table 1 debe a su vez resumir lo que muestra la Figure 6.
-Destacalo en tu color cuando lo hayas hecho así le presto atención.}
-
-%To establish if the differences in the results between the two rotations are significant, Section \ref{uncertainties} estimates the error bars due the dominating systematic uncertainties.
-%\diego{quizas vale la pena introducir alguna comparacion sobre el campo magnetico, veremos como quedan los comentarios de ceci.}
-%{Also, within the streamer belt the magnetic field strength is similar in both rotations in the northern hemisphere, while in the southern hemisphere CR-1915 exhibits $10-80\%$ larger values compared to CR-2081, with increasing difference for larger latitudes.
-In the coronal holes, the magnetic field strength of CR-1915 is much larger than for CR-2081, exhibiting values up to 50\% larger in the northern hemisphere and more than twice larger in the southern hemisphere.}
-
-%Previous works have found magnetic loops which temperature decrease with height, most generally in equatorial latitudes \citep{huang_2012,nuevo_2013}.
-This type of loops with negative gradients produce a negative conductive flux that contribute to the heating in the corona.
-In this work, we compute the loop-integrated energy quantities separately in three different populations of loops.
-
-{To analyze the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the clasification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).
+\diego{A comparison of the results between the two rotations shows that, compared to CR-2082, target rotation CR-2208 was characterized by $\approx 15-20\%$ lower values of the electron density at the coronal base, $\approx 5-30\%$ larger values of density scale height, and $\approx 10-25\%$ larger values of the electron temperature.}
+
+{To analyze the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the classification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).
 {For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.}
@@
 
-{For both rotations, the value of the integrated radiative power $E_r$, measured by the quantity $\phi_r$, is largest for loops of type 0.
+{For both rotations, the value of the {loop-integrated} radiative power $E_r$, measured by the quantity $\phi_r$, is largest for loops of type 0.
 This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors contributing to maximize $E_r$ for loops of type 0.
-As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0 are characterised by the relatively largest values of electron density.
+As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0 are characterized by {the largest} values of electron density.
 Also, in the range of sensitivity of the EUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$.
-According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterised by {values of temperature that are progressively larger and farther} from the value $\Tc$, for both rotations.}
-
-{In the case of the quantity $\phi_c$, its sign depends on that of the conductive flux $F_c$.
-As shown in \citet{maccormack_2017}, down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, which is verified in Figure \ref{energia_demt}.}
-
-{As a result of the radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of loop.
-These values are similar to those reported by \citet{maccormack_2017}.
+According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterized by {values of temperature that are progressively larger and farther} from the value $\Tc$, for both rotations.}
+
+{{The sign of the quantity $\phi_c$ depends on that of the conductive flux $F_c$.
+Equations (\ref{Fc}) and (\ref{phi_c}) imply that } down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, {as verified} in Figure \ref{energia_demt}.}
+
+{{Adding the} radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}.
 Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$.
-As shown by \citet{maccormack_2017}, this result affects only the smallest loops (a subset of the type 0 class) and it is due to the limited temperature sensitivity of the instrumental passbands.
-The radiative loss term is calculated based on plasma emission detected by the three coronal bands of EUVI and the three bands of AIA used.
-Though this should account for most of the coronal plasma, there surely is additional emission that is out of the range of sensitivity of the instruments used.
-Thus, the positive term $\phi_r$ is most liekly understimated, leading to values $\phi_h<0$ in loops of type 0, which are characterized by $\phi_c<0$.}
-
-%Type 0 loops present slightly larger gradients than type I.
-Therefore, type 0 present bigger amount, in modulus, of loop-integrated conductive flux.
-Due conductive flux negative can not be assumed as a loss but it can be contributing to the coronal heating.
-Thus, to compensate the radiative losses, a lower loop-integrated energy input flux ($\phi_h$) is required.
-
-%We can see, on type 0 loops, a median value of energy input flux for CR2082 twice bigger than CR2208.
-Also, in both rotations, we observe a negative population of loop integrated energy input flux.
-This can refer to some loops where loop-integrated radiative flux is too small in comparison with the larger gradients of negative conductive flux, resulting in negative energy input flux.
-
-%The type I loops show a loop-integrated positive conductive for each loop in both rotations consistent with positive gradients of temperatures.
-The conductive flux have values around 0.3 $10^{5}[\rm{erg\,sec^{-1}\,cm^{-2}}]$ in both rotations.
-Similar results have been found for loop-integrated radiative flux and energy input flux for both rotations.
+As shown by \citet{maccormack_2017}, {this affects only the smallest sized loops of the type 0}, and it is {most probably} due to the limited temperature sensitivity of the instrumental passbands.
+The radiative loss term is {here calculated based on plasma emission detected by three coronal bands of EUVI or AIA.
+Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range.
+As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized} by $\phi_c<0$.}
 
@@
 
-Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature, for both rotations.
-These Figures show the results at the same three heights selected for visualisation of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}.
-As in those, thick-black curves indicate the magnetic open/closed boundaries based on the magnetic field of the AWSoM model.
-Visual inspection of these maps shows that the AWSoM model for both rotations is highly axysimmetric, as the tomographic model.
-
-\diego{A visual inspection of these maps shows that both reconstructions are very axysimmetric for $\Ne$ and $\Te$ as well.
-The closed region is denser and hotter than the open region.
-The density and temperature gradients are maximum in the open-close boundary.
-The open field regions in low latitudes maintain thermodynamic values associated with open regions.} The reconstruction of CR-2082 does not show clear the ARs, while CR-2208 shows a well reconstruction of both AR around latitude-longitud $+5\mdeg$, $140\mdeg$ and $+5\mdeg$, $300\mdeg$.
-In both rotations the open-closed boundaries derived from the AWSoM model match the shape of the contour levels of both the electron density and the electron temperature.
-
-%\diego{comparacion visual entre estas dos figuras y als dos de DEMT.}
-
-The same intensity scales in both density and temperature can be observed between the tomographic results and those of AWSoM in both rotations, as well as the same thermodinamic structures.
-That is, equatorial latitudes, mid laditudes and the open regions.
+{For both target rotations,} Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature.
+{Maps are shown} at the same three heights selected for visualization of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}.
+{Thick-black curves} indicate the magnetic open/closed boundaries based on the magnetic field of the AWSoM model.
+Visual inspection of these maps shows that the AWSoM model for both rotations is highly {axisymetric}, as the tomographic model.
 
@@
 
+{As described in Section \ref{awsom}, the AWSoM model includes an artificially thick TR, achieving coronal conditions above height $\approx 1.06\,\mrsun$.
+Indeed, the top panels in Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208}, at height $1.025\,\mrsun$, clearly do not represent coronal conditions (although we include them here for completeness).
+When compared to DEMT results (Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}), the latitude-longitude maps of the AWSoM model for heights $1.065$ and $1.105\,\mrsun$ capture well the denser and hotter equatorial streamer belt surrounded by the less dense and colder CHs.
+Furthermore, for both target rotations, the temperature maps show the low latitudes of the equatorial streamer belt to be characterized by lower temperatures than its mid-latitudes, as also seen in the DEMT results.
+The latitude-longitude maps of the AWSoM and DEMT results are shown in the same units and scales, so that a visual comparison among them already reveals similar values of electron density and temperature in both models.}
+
 \begin{figure}[h!]
@@
 
-%\temp{Se presentan los midpoints para awsom que lucen mas rellenos xq no hay down loops y todo es super suave.}
-
-In the same way as in Section \ref{demt_res}, the model results were traced along the magnetic lines obtained with it.
-This allowed to obtain $\Ne(r)$ and $T_e(r)$ along the magnetic lines and fit them to the Equations \ref{Nfit} and \ref{Tfit}.
-
-The actual version of the AWSoM model can not reproduce down legs, so for a further comparison we only select lines of type I, II and III of those meeting the criteria described in Section \ref{trace}.
-
-As a way to understand the distribution of legs, Figure \ref{rpoint_awsom} shows the latitudinal-longitudinal location of the traced legs at top and the selected fitted legs meeting the criteria at $1.105\,\mrsun$ for both rotations, in the same way as in Section \ref{demt_res}.
-In red the type I lines, populating mostly the entire streamer.
-In violet the type II lines, populating the edge that assemble the envelope around the streamer, and in green dots the type III lines, populating the coronal holes.
-
-The reader may notice that these structures are the same as those in Figure \ref{rpoint_demt} but more filled.
-The cause is twofold, on the one hand the same magnetic model was used to trace both DEMT and AWSoM results, on the other hand is because giving the model smoother results, fewer fitted lines are filtered.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_awsom_paper_test_Rpoint-map.pdf}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_awsom_paper_test_Rpoint-map.pdf}
-%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.pdf}
-%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.pdf}
-\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its legs in types I, II and III. The model does not exhibit legs of type 0.}}
-\label{rpoint_awsom}
-\end{center}
-\end{figure}
-
-To highlight the latitudinal structures observed in Figures \ref{carmaps_demt_2082} and \ref{carmaps_awsom_2082} for CR-2082 as well as Figures \ref{carmaps_demt_2208} and \ref{carmaps_awsom_2208} for CR-2208, Figure \ref{perf_lat} shows for both rotations the latitudinal variation  of both the electron density and the electron mean temperature at the height $r=1.105\,\mrsun$, averaged over all longitudes (excluding the AR).
-DEMT results are shown in blue lines while AWSoM results in red.
-While the temperature shows a maximum in each hemisphere, the density has a simpler behavior, with higher values in the low-latitudes of the streamer and a nearly monotonic decrease towards larger latitudes.
-The vertical black lines denotes the average of the open-close boundary in both hemispheres to each rotation.
-
-\diego{Me gustaria hacer un comentario de cierre para esta figura que refiera las Figuras 3 y 9, como la linea de abajo, y que conecte con los histogramas que vienen a continuacion.
-Si no queda bien, hay que mover esta figura entre la actual figura 8 y 9.}
-
-This longitude-averaged behaviors match well with the physical locations of the legs shown in Figures \ref{rpoint_awsom} and \ref{rpoint_demt}.
-
-According to the visual inspection on the maps of carrington, the latitudinal profiles comparing both DEMT and AWSoM results are on the same scale.
-Little difference in density is observed in CR-2208 and in temperature in CR-2082, while DEMT in CR-2082 was $20\%$ denser.
-Finally, DEMT results for CR-2208 were $25\%$ hotter in the streamer and $30\%$ colder in the polar zone than AWSoM.
-Density profiles on AWSoM show an increase around the polar zone, which seems like an artifice.
+{Being highly axisymmtric target rotations, the longitude-averaged latitudinal variation of the results of both models is an informative way to compare their large-scale structure.
+Such comparison is shown in Figure \ref{perf_lat} at height $1.105\,\mrsun$, with top panels comparing electron density and lower panels electron temperature.
+In these longitude-averaged profiles, longitudes containing ARs or low latitude CHs were excluded.
+In each panel the averaged latitudinal variation for the DEMT model is shown in solid-linestyle, while the result for the AWSoM model is shown in dashed-linesyle.
+Left panels show the comparison for CR-2082 (in blue) and right panels for CR-2208 (in red).
+In each panel the vertical black lines denote the corresponding longitude-averaged latitude of the open-close boundary in both hemispheres.}
+
+\notebyalbert{Diego: debés estar seguro que sacaste ARs y low-latitude CHs de los promedios en longitud.
+Cuando más te esmeres la comparación es más justa, y podés revelar algo que de otra manera no se vería.
+Si promediaste longitudes con ARs o CHs, rehacelo, vale la pena.
+Por supuesto debes promediar idéntidas longitudes en DEMT, AWSoM y en la O/C.}\\
+\diego{NOTA: Saqué todo desde un principio, incluso las selcciones donde hay regiones abiertas dentro del streamer.}
 
@@
 
-To summarize the comparison between both results during both rotations at full height, it is shown in Figure \ref{perfiles_promedio} the average fits of $\Ne(r)$ and $T_e(r)$ for legs of type I (blue), II (red), and III (green) for both rotations.
-
-In average all temperature and density behavior from both results are on the same scale.
-The coronal base densities of AWSoM were lower than those of DEMT in CR-2082 and higher in CR-2208.
-The fact that the density decays to similar values between both results suggests a similar height scale.
-Onthe other hand basal temperature of AWSoM was lower in both rotations, but the temperature gradients are very similar en each type of legs, showing a very similar increase of temperature with height.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
-\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (red), II (violet), and III (green), for CR-2082 (top panels) and CR-2208 (bottom panels).
-Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.} \notebyalbert{(by Albert): The idea of this Figure is to show how DEMT and AWSoM compare AS A FUNCTION OF HEIGHT, in three distinct types of magnetic structures, and for both rotations.}}
-\label{perfiles_promedio}
-\end{center}
-\end{figure}
-
-Tu summary the statistical comparison, Figure \ref{histos_2082} and \ref{histos_2208} shows the statistical results of both rotations for the three types of field lines traced with DEMT (blue) and AWSoM results (red).
-From left to right the panels show the statistical distribution of $\NCB$, $\lN$ and $\aTm$.
-For all types of lines, Table \ref{tabla_comp} summarizes the median value of the statidtical distribution of each physical quantity derived from the analysis.
-The DEMT quantities are expressed as absoulte values, while for ASWSoM they are informed relative to the corresponding result for DEMT.
-
-\diego{aca podria ir un pequeño parrafo que resuma las diferencias.
-Pero justo a continuacion empiezan las conclusiones y uno tiende a repetir, no se como encararlo para que no quede dos veces lo mismo y tan pegado uno de lo otro.}
+{Several details from Figure \ref{perf_lat} are worth being highlighted.
+Firstly, for CR-2082 the electron density of both models agree within $\approx 20\%$ at all latitudes, and for CR-2208 the agreement is within $\approx5\%$.
+In the case of the electron temperature both models agree within $\approx 10-15\%$ at all latitudes for both target rotations.
+Secondly, for both target rotations, and for both models, these plots clearly show the relatively lower temperatures characterising the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
+Thirdly, for both target rotations, the latitude of the open/close magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density.
+Note this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
+Last, note that the DEMT electron density decreases from the open/close boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend.}
+
+{To characterize the results of the AWSoM model in distinct magnetic structures, its results for electron density and temperature were traced along its magnetic field lines.
+For each field line leg, the results were then fit to Equations (\ref{Nfit}) and (\ref{Tfit}).
+\diego{In case of AWSoM, only data above $1.055\,\mrsun$ were fitted.} In its current implementation, the AWSoM model can not simulate down loops, a point we will discuss in the next section.
+We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_awsom_paper_test_Rpoint-map.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_awsom_paper_test_Rpoint-map.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.pdf}
+\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its legs in types I, II and III. The model does not exhibit legs of type 0.}}
+\label{rpoint_awsom}
+\end{center}
+\end{figure}
+
+{For both target rotations, the top panels of Figure \ref{rpoint_awsom} show the latitude-longitude location (at heliocentric height $1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
+That criterion is adapted here, requiring that at least five voxels of the tomographic grid are threaded by the leg.
+Open legs are indicated in gray color and closed ones in black color.
+For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit} and \ref{Tfit}.
+Considering the AWSoM data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_awsom} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
+Using a three-color code, type I, II and III legs are shown in red, magenta and cyan color, respectively.
+This figure is to be compared with the corresponding Figure \ref{rpoint_demt} for DEMT results.
+It is readily seen that the AWSoM maps are more populated than those of DEMT.
+This is due to the 3D MHD model having electron density and temperature fields spatially smoother than those of DEMT.}
+
+{For target rotation CR-2082, Figure \ref{histos_2082} shows the statistical distribution of the results of the DEMT (solid line-style) and AWSoM (dashed line-style) models traced along legs of type I, II and III (from top to bottom), as defined in Section \ref{trace}.
+From left to right: electron density at the lowest coronal height of the AWSoM model $\NCB\equiv\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
+In each panel the median values $m$ are indicated.
+Figure \ref{histos_2208} shows the same analysis for target rotation CR-2208.}
 
@@
 \includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
-\caption{{Statistical distribution of DEMT (blue) and AWSoM (red) results traced along legs of type I, II and III (from top to bottom), as defined in Section 2.3.
-From left to right: electron density at the lowest coronal height of the AWSoM model $\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
-In each panel the median value $m$ is indicated.}}
+\caption{{Statistical distribution {of the results of the DEMT (solid line-style) and AWSoM (dashed-linestyle) models} traced along legs of type I, II and III (from top to bottom), as defined in {Section \ref{trace}.} From left to right: electron density at the lowest coronal height of the AWSoM model $\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
+In each panel the median {values $m$ are} indicated.}}
 \label{histos_2082}
@@
 \end{figure}
+
+{For the two target rotations, Table \ref{tabla_comp} summarizes a quantitative comparative analysis between the results of the DEMT and AWSoM models.
+The DEMT results are expressed as absolute values, while the ASWSoM results are informed as a percentual variation relative to the corresponding result for DEMT.
+The following major results can be drawn.}
 
@@
 
-%This plot (E) has never been shown before and I believe it is a very nice result.
-There are of course previous studies on this, but this would be the first time this is evaluated with tomography.
-It is not the terminal speed, but it already shows the fast/slow components.
-We can show this, or we can go for more.
-Diego can QUANTIFY the correlation by carefully mapping all open field lines at 6 Rsun down to the DEMT region.
-He needs to code a bit more to achieve this goal, but we believe it is worth.
-With that tool done Diego can explore other terminal values of quantities of the AWSoM model and the DEMT results below (expansion factor maybe?).
-This will be nice to do also for the July-2-2019 Eclipse rotation that we will analyze after this paper.
+{For target rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, depending of the type of leg, while the median value of the scale height $\lN$ agree within $\approx 10\%$.
+The leg-averaged electron temperature $\aTm$ of both models also agree within $10\%$.
+For target rotation CR-2208 the agreement of the median value of $\NCB$ and $\lN$ of both models is within $5\%$, while median values of $\aTm$ agree within $15\%$.
+These detailed results informed per magnetic structure are fully consistent with the large-scale comparison provided in Figure \ref{perf_lat}.}
 
 \begin{table}
-\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
-% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
+\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
 \hline
-Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
-       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
+Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
+        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
 \hline
 CR-2082\\
-I  & 1&13 &(\Mi&11&9\%)  &   8&3 &(\Mi&~2&4\%) &   1&29 &(\Mi&10&8\%) \\
-II  & 0&97 &(\Mi&22&5\%)  &   8&9 &(\Pl&~2&2\%) &   1&33 &(\Mi&~4&5\%) \\
-III  & 0&66 &(\Mi&16&8\%)  &   7&7 &(\Mi&~9&1\%) &   0&98 &(\Mi&~9&2\%) \\
+I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&~9\%) \\
+II   & 0&99 &(\Mi&25\%)  &   8&9 &(\Mi&~2\%) &   1&36 &(\Mi&~2\%) \\
+III  & 0&65 &(\Mi&15\%)  &   7&6 &(\Mi&~8\%) &   0&97 &(\Mi&~9\%) \\
 \hline          
 CR-2208\\
-I  & 0&97 &(\Pl&~9&3\%)  &   9&8 &(\Mi&~7&1\%) &   1&55 &(\Mi&14&2\%) \\
-II  & 0&77 &(\Pl&11&7\%)  &  11&6 &(\Mi&17&2\%) &   1&55 &(\Mi&~9&7\%) \\
-III  & 0&56 &(\Mi&~1&9\%)  &   8&6 &(\Mi&16&3\%) &   1&04 &(\Mi&~9&6\%) \\
+I    & 1&03 &(\Pl&~6\%)  &   9&7 &(\Mi&~8\%) &   1&55 &(\Mi&17\%) \\
+II   & 0&79 &(\Pl&~9\%)  &  11&8 &(\Mi&14\%) &   1&58 &(\Mi&~8\%) \\
+III  & 0&55 &(\Pl&~1\%)  &   8&6 &(\Mi&16\%) &   1&04 &(\Mi&11\%) \\
 \end{tabular}
@@
 Ejemplo para CR-2208 $\lambda_N$ de Type-II: $12.0\,(-17\%)$.
-Ejemplo para CR-2208 $\aTm$ de Type-II: $1.6\,(-10\%)$.}}
+Ejemplo para CR-2208 $\aTm$ de Type-II: $1.6\,(-10\%)$.} \diego{Hay 6 valores que terminan en 5, con lo cual al redondearlos se pierde bastante informacion, lo dejé así como lo vez por eso.
+Si aún asi te parece buena idea redondearlo, lo hacemos.}}
 \label{tabla_comp}
@@
 
-Figure \ref{perf_lon_vr} show the longitude-averaged AWSoM radial wind speed $V_r$ at $6\,\mrsun$, where all field lines are open.
-The heliocentric current sheet (HCS) location is indicated by the minimum of the speed curve.\\
-\diego{can we say something without having traced the lines?} \notebyalbert{(by ALBERT) Todo el punto de la última Figura es precisamente decir algo.
-La comparación con la Figura 10 muestra una anti-correlación entre la densidad basal de DEMT y la velocidad terminal de AWSoM.}
-
-For each rotation, everything to the south of the HCS maps down to the southern open region in the Figures \ref{perf_lat}, and the same for the northern hemisphere, showing an anti-correlation between $\Ne$ at low heights and high $V_r$ at $6\,\mrsun$.
-
-\diego{Voy a intentar jugar con las lineas tipo 3 aumentando su cota inferior de latitud para ver si los histogramas de temp media dejan de ser tan dispersos y se vuelven mas sub-1MK. }
+{Finally, to provide a graphical comparison of both models across the full range of heliocentric heights covered by the DEMT results, Figure \ref{perfiles_promedio} shows the average fits of $\Ne(r)$ and $T_e(r)$ for legs of type I (red), II (magenta), and III (cyan) for both target rotations.
+In each panel the DEMT and AWSoM results are plotted in solid and dashed linestyles, respectively.}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
+\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of {type I (red), II (magenta), and III (cyan)}, for CR-2082 (top panels) and CR-2208 (bottom panels).
+Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
+\label{perfiles_promedio}
+\end{center}
+\end{figure}
+
+{As discussed above, Figure \ref{perf_lat} shows that the logitude-averaged latitudinal profile of the DEMT electron density in the CHs decreases towards the poles.
+Figure \ref{perf_lon_vr} below shows the longitude-averaged AWSoM radial wind speed $V_r$ at $6\,\mrsun$, where all field lines are open.
+The heliocentric current sheet (HCS) location is indicated by the minimum of the speed curve.
+For each rotation, all velocity data points to the south of the HCS position map down to the southern CH in Figures \ref{perf_lat}.
+Similarly, all velocity data points to the north of the HCS position map down to the northern CH in Figures \ref{perf_lat}.
+This clearly shows an anti-correlation between the DEMT electron density at low heights and the AWSoM wind speed at larger heights.}
+
+\notebyalbert{We could quantify the anti-correlation between the AWSoM terminal speed and the DEMT electron density at the coronal base in the following fashion.
+We can set up starting points at, say, $20\,\mrsun$, every one degree, both in latitude and longitude.
+This would mean setting up $180\times 360$ starting points.
+We trace then the (open) field lines from each of those starting points down to $1.0\,\mrsun$ to find out the DEMT results at those lower heights for each field line.
+Now, to do this we need to develop some codes and have no time for this paper.
+We can postpone it for a next effort, or...
+Chip: do you think you could do this with your present tools?
+Do you think it is interesting?
+I think so.
+Our submission deadline is end-of-January.}
 
@@
 *In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI.
-In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, analyzed a single target using both instruments independently.
+In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
 They found that while the density product is essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e.
@@
 
-*Coronal magnetic structures for which the temperature increases/decreases with height in the range of heights covered by DEMT, $1.02–1.22\,\mrsun$, have been dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first observed their presence by means of DEMT.
-As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
-Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}.
-In a recent study by \citet{schiff_2016}, down and up loops have been successfully reproduced by a numerical implementation of a 1D steady-state model that considers time-averaged heating rates.
-
-We found down legs in the DEMT reconstructions mainly in the equatorial latitudes, being a greater quantity and better distribution along longitudes in CR-2082 than in CR-2208.
+*We found down legs in the DEMT reconstructions mainly in the equatorial latitudes, being a greater quantity and better distribution along longitudes in CR-2082 than in CR-2208.
 \citet{nuevo_2013} showed a decrease in the amount of down loops as the solar activity increases, which is consistent with the results shown in this article.
+
+*
 

### 2020-01-11 lloveras_2020_Albert_Section4.tex
..

--- 2020-01-11 lloveras_2020.tex
@@
 
-\subsection{DEMT reconstructions}\label{demt}
+\subsection{\albert{DEMT Reconstructions}}\label{demt}
 
@@
 
-\subsection{AWSoM simulations}\label{awsom}
+\subsection{\albert{AWSoM Simulations}}\label{awsom}
 
@@
 
-\subsection{Tracing of results along fieldlines}\label{trace}
-
-\noindent\notebyalbert{This section will explain how the AWSoM magnetic model is used to trace the thermodynamic products of both DEMT and AWSoM along the fieldlines of AWSoM.
+\subsection{\albert{Tracing Results Along Magnetic Fieldlines}}\label{trace}
+
+%\noindent\notebyalbert{This section will explain how the AWSoM magnetic model is used to trace the thermodynamic products of both DEMT and AWSoM along the fieldlines of AWSoM.
 This requires covering the following points:
-\begin{itemize}
-  \item A first paragraph qualitatively describing the process. This includes mentioning that the AWSoM products are first interpolated into the DEMT grid.
-  \item A short paragraph describing the numerical method used to trace field lines.
+%\begin{itemize}
+%  \item A first paragraph qualitatively describing the process. This includes mentioning that the AWSoM products are first interpolated into the DEMT grid.
+%  \item A short paragraph describing the numerical method used to trace field lines.
 We have a nice version of this in your previous paper.
 At this point the reader should understand that for each field line we have its geometry $\mathbf{r}(s)$ as a function of the distance $s$ along the loop, with $s(1\,\mrsun)\equiv 0$.
-  \item Explain very simply how then that for each voxel the middle point of the field line is selected and assigned the DEMT and AWSoM products of that cell.
+%  \item Explain very simply how then that for each voxel the middle point of the field line is selected and assigned the DEMT and AWSoM products of that cell.
 At this point the reader should understand that for each field line we have: $Q[r(s)]$, where $Q$ is any given quantity from either the DEMT model (specifically $\sqravgN$ and $\Tm$) or the AWSoM model (specifically $\Ne$ and $\Te$).
-  \item Explain fits to the DEMT results  $\sqravgN(r)$, $\Tm(r)$.
-  \item Explain then the classification of field lines.
-\end{itemize}
-}
-
-Aiming determination of the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid.
+%  \item Explain fits to the DEMT results  $\sqravgN(r)$, $\Tm(r)$.
+%  \item Explain then the classification of field lines.
+%\end{itemize}}
+
+\albert{To determine} the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid.
 Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = r{\rm d}\theta/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point.
 In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, for a total of $96,000$ starting points.
-Each traced field line is classified as ``open" if it intersects the source surface, set in this work at $r=6\,\mrsun$ (where lines become radial), or as ``closed" otherwise.
-In the case of closed magnetic lines, they are separated in two ``legs", from the base to the apex.
-
-%\diego{Of these legs, those whose size $L$ are smaller than the average lengths $\langle L \rangle$ are called small, and those with $L > \langle L \rangle$ ar called large.}
-\diego{
-In the case of closed magnetic field lines, legs {are} further classified as ``small" and ``large" upon their apex height being within or beyond the lenght average of the closed legs, respectively.
-}
-
-At this stage, all DEMT and AWSoM products, electron density and mean temperature in particular, can be traced along open and closed magnetic field lines.
+
+\albert{For analysis purposes, the geometry of all traced magnetic field lines is classified.
+They are first classified as open or closed according to their full geometry.
+Each closed magnetic field line is further classified as ``small" or ``large", according to its coronal length $L$ being smaller or larger than the median value ${\rm Md}(L)$ of the whole population, respectively.
+This median value is ${\rm Md}(L)=0.51$ and $0.46\,\mrsun$ for CR-2082 and CR-2208, respectively.
+Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e.
+their location at $r=1\,\mrsun$) to its apex (i.e., the location of maximum height).} \notebyalbert{Diego, aquí ordené y corregí mucho y creo que es un buen ejemplo de corrección de estilo de redacción, si querés comparar con como estaba antes.
+Nota: MHD no tiene source surface!
+Ahora bien, además informo ${\rm Md}(L)$.
+Para ello multipliqué por dos el valor mediano de las longitudes de las piernas (que recuerdo de memoria, por ahí la pifié).
+Vale la pena que le muestres estos histogramas a Fede y la pieza de código de donde sale, para confirmar la metodología y de paso los números.
+Es importante.}
+
+At this stage, all DEMT and AWSoM products, electron density and \albert{temperature} in particular, can be traced along open and closed magnetic field lines.
 Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one).
 To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it.
-As a result, for each field line one data point per tomographic cell is obtained.
-This allows to analyze how density and temperature, coming from both models, vary with height along each individual field line.
-This approach was firstly used by \citet{huang_2012} to study inverted temperature structures in the solar minimum corona, and later on applied by \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.
-
-For each open field line, and for each leg of the closed ones, an exponential fit was then applied to the electron density and a linear fit applied to the electron temperature.
-For DEMT results the data points used were $\sqravgN(r)$ and $\Tm(r)$, and in case of AWSoM the data points used were $\Ne(r)$ and $\Te(r)$.
+As a result, for each field line one data point per tomographic cell \albert{is obtained.
+This approach} was firstly used by \citet{huang_2012} to \albert{study temperature} structures in the solar minimum \albert{corona and by} \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.
+
+For each open field line and \albert{for each closed field leg}, an exponential fit \albert{was applied} to the electron density \albert{data points} and a linear fit applied to the electron temperature \albert{data points}.
+For \albert{the DEMT model} the data points used were $\sqravgN(r)$ and $\Tm(r)$, and in case of \albert{the AWSoM models} the data points used were $\Ne(r)$ and $\Te(r)$.
 The exponential and linear fit equations are described by
@@
 
-In the present work we focus on legs with increasing and decreasing temperatures in linear form.
-In other words, we selected those legs where the {Pearson correlation coefficient $\rho$ between temperature $T$ and radius $r$ meets $|\rhoTr| > 0.5$} {(with 95\% confidence level)}.
-In this way, those legs in which the DEMT results cannot ensure a noticeable change in temperature between the base and the apex, are discarded.
-
-The linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg.
-Both fits consider tomographic systematic uncertainty estimated in \citet{lloveras_2017}, i.e.
-$0.07$ MK for $\Tm$ and $4.0\,10^6 cm^{-3}$ for $\Ne$.
-
-To measure how good the quality of the fit are, a chi-square merit function was used (Section 15.2 \citet{recipes}).%, selecting only legs with 95\% confidence level.
-
-%el p-valor es un concepto estadístico, no veo xq deberia ser explicado. Lo que si, en el paper explicare bien las hipotesis nulas y de esa forma el p-valor queda bien claro.
-%El p-valor es una cuantificacion de con cuanta probabilidad de exito estas rechazando o aceptando una hipotesis en particular que se la suele denominar hipotesis nula.
-%En este caso, con 95$\%$ de seguridad estas rechazando las piernas que tienen un $pearson_x,y = 0$. Es decir te estarias quedando con aquellas que tienen una dependencia lineal entre x e y.
-%En el segundo caso, el test de hipotesis seria sobre la hip nula de que los datos provienen una funcion distribucion donde la recta fiteada de esos datos es el valor esperado de la distribucion.
-Con lo cual hacerle un test chi cuadrado te da una idea de cuan acertado o no es el ajuste.
-En este caso la hipotesis nula es que los datos provienen de esa distrib, con lo cual el chi deberia dar bajo y descartas los que dan valores altos con un 95$\%$ de seguridad.
-Eso es lo que representa el p-valor =0.05 en este caso (el area bajo la funcion distribucion, es decir, probabilidad).
-
-{To be selected a leg must meet all following conditions.}
-
-\diego{
+\notebyalbert{Este párrafo debe ser movido al menos aquí (estaba más abajo), pues el siguiente párrafo ya utiliza el concepto up/down.
+Además está corregido.} \albert{Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies.
+As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
+Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}.
+In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}
+
+\notebyalbert{Reordené y corregí mucho el siguiente párrafo.
+Lo que see lee es correcto en cada detalle y palabra?
+Está bien explicado todo lo que concierne a chi-suqared?
+La jerga estadística es precisa y correcta (no confundir confidence level con confidence interval, está bien?}
+\albert{To determine if a traced filed line leg is of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points.
+We then select field lines for which the temperature increases or decreases significantly with height by requiring $|\rhoTr| > 0.5$.
+We then measure the quality of the linear fit to the temperature-height data by means of a chi-squared test \citep{recipes}, and select legs for which the fit has a 90\% confidence level.
+In this way, legs for which the DEMT temperature does not show a significant variation with height, or the linear fit to temperature is good enough, are not considered in this analysis.
+Finally, selected legs are then classified as up or down according to if $\rhoTr > +0.5$ or $\rhoTr < -0.5$, respectively.
+The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg.
+Both fits consider tomographic systematic uncertainty of the electron temeprature and density, respectively estimated to be $\Delta(\Tm) \approx 0.07\,\MK$ and $\Delta(N_e)\approx 4.0\times 10^6\,\cm^{-3}$ by \citet{lloveras_2017}.
+\notebyalbert{No comprendo bien si esta última linea está bien ubicada aquí, de todas formas lo corregí un poco.
+Precisaría que discutamos los tres estos tres párrafos en naranja el lunes.} In summary, to be selected a leg must meet all three following conditions:}
+
 \begin{enumerate}
@@
 The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg.
+\albert{This requirement is set to ensure a reasonably spread sample of heights along the leg.}
 \item 
-The {value of the Pearson correlation coefficient meets $|\rhoTr| > 0.5$.}
+The \albert{DEMT temperature and height data points must meet} $|\rhoTr| > 0.5$.
 \item 
-The coefficient level of both the exponential and linear fit must be grater than \%90.
+\albert{The condifence level of both the exponential and linear fits must be larger than 90\%.} \notebyalbert{Aquí corregí, está bien expresado?}
 \end{enumerate}
-}
-
-{Coronal magnetic structures for which their temperature increases/decreases with height (in the inner corona) have been dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies.
-As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
-Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}.
-In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}
 
 {To characterize the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model.
-Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types in this work:}
-
-\diego{
+Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types in this work:} \notebyalbert{Simplifiqué mucho esto.}
+
+\albert{
 \begin{itemize}
-\item Type 0 - Small legs (coming from closed field) in the latitudes range $[-50\mdeg,+50\mdeg]$, and $\rhoTr < -0.5$. 
- %This class thoroughly populates the equator of the Streamer belt during a minimum solar rotation.
-\item Type I - Small legs (coming from closed field) in the latitudes range $[-50\mdeg,+50\mdeg]$, and $\rhoTr > 0.5$. 
-%This class thoroughly populates the inner of the Streamer belt.
-\item Type II - Large legs (coming from closed field) in the latitudes range $[-90\mdeg,-40\mdeg] \cup [+40\mdeg,+90\mdeg]$, and $\rhoTr > 0.5$. 
-%This class is mostly populated by very large trans-equatorial field lines forming the envelope of the Streamer belt. 
-\item Type III - Open field lines in the latitudes range $[-90\mdeg,-60\mdeg] \cup [+60\mdeg,+90\mdeg]$, and $\rhoTr > 0.5$.
+\item Type 0: closed-small-down with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
+\item Type I: closed-small-up with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
+\item Type II: closed-large-up with footpoints in the range $|{\rm latitude}|>40\mdeg$. 
+\item Type III: open with footpoint in the range $|{\rm latitude}|>60\mdeg$.
 \end{itemize}
 }
-{In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed.}
-
-\subsection{{Energy input flux}}\label{energia}
-
-\noindent\notebyalbert{This section will summarize how loop integrated energy quantities are computed from the DEMT products and the AWSoM magetic model alone.
+
+In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed.
+\albert{As shown below, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}
+
+\subsection{\albert{Energy Input Flux}}\label{energia}
+
+%\noindent\notebyalbert{This section will summarize how loop integrated energy quantities are computed from the DEMT products and the AWSoM magetic model alone.
 The summary will not include any derivation and will refer to Cecilia's paper.
@@
 At the end the reader should understand that their sum is the enery input flux required at the coronal base to maintain the loop stable.
-This should be a very short section, as it is a summary of one previous paper alone.}
-
-%correcciones a hacer! DIEGO
-%Los términos de la Eq (10) requieren ser explicados.
-La explicación a conituación no es clara, y de hecho está mal escrita.
-La Eq.
-(7) se integra en el VOLUMEN CORONAL COMPLETO de cada tubo de flujo y se divide por el área basal del mismo.
-Utilizando la condición solenoidal de B se llega a la Eq.
-(7), dónde...
-y ahí deberían darse las expresiones de Phir y Phic porque no pertenecen a la literatura estandard, y explicar a continuación como todos los elementos de esas dos expresiones surgen de los fits de DEMT y del modelo magnético de AWSoM.
-Donde si se puede ahorrar mucho espacio es en lo previo, la Eq (8) podría no incluirse por ejemplo.
-Creo que ahora lo mejor es que trates de completar la explicación dando las expresiones de Phir y Phic, y luego vemos de como limarla, probablemente eliminando la ec.
-(8).
-y además el texto puede compactarse, corregirse y reordenarse mucho.
-Poné las unidades de las cantidades Phi entre paréntesis a continuación de $\Phi_{h,r,c}$.
-
-Due the difference between temperatures of transition region and solar corona, there must to be a heating mechanism that compensate all the losses present in the atmosphere and maintain stable the plasma temperature.
-Previous works have studied this mechanism by observations and modeling, but mostly for active regions.
-\citet{maccormack_2017} have developed a technique that estimate the heating injected into the loops during a period of minima activity.
-Using DEMT combined with an extrapolation of magnetic field, as we detailed before, they obtain the different plasma parameters along each magnetic loop, and therefore, compute the energy input flux required to maintain them stable.
-The model assume a simple energy balance for each magnetic flux tube, where the losses by radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated by some coronal heating power($E_h$) \citep{aschwanden_2004}:
+This should be a very short section, as it is a summary of a single previous paper.}
+
+\albert{The high temperature of the corona requires heating mechanisms to compensate for the the losses.
+While the vast majority of the existing literature on coronal heating focuses on ARs, some studies have been dedicated to the heating of quiet-Sun regions.
+In particular,  \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to mantain them stable.
+The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in the previous Section \ref{trace}.}
+
+\albert{Consider} a simple energy balance for each magnetic flux tube, \albert{in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated \albert{by a} coronal heating power($E_h$) \citep{aschwanden_2004}:
 
@@
 \noindent
-where $s$ is the position along each magnetic flux tube and the powers are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.
-
-\noindent\notebyalbert{Trabajé todo lo naranja.
-Primero decidí que es mejor no numerar $E_c$ sino $F_c$.
-Eso te quedará claro cuando agregues las ecuaciones (11) y (12) que te indico más abajo y leas el último párrafo naranja de abajo, ahí cierra todo.
-Además describí que son los $\phi$ en forma correcta.
-El texto previo estaba muy flojón, entre otras cosas se hablaba de una (inexistente) ``conductive loss function" y de una (incorrectamente denominada) ``area along the loop".
-Obviamente luego de chequear este texto naranja borrá esta nota azul en particular.}
+where $s$ is the position along \albert{the flux tube} and the \albert{power quntities} are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.
 
@@
 
-\noindent\notebyalbert{This section will show first the DEMT products in the form of Carrington maps at three heights, for the two target rotations.
+%\noindent\notebyalbert{This section will show first the DEMT products in the form of Carrington maps at three heights, for the two target rotations.
 It will then show the latitude/longitude location of the four types of  magnetic loops (defined in Section 2.3) at a sample height.
@@
 Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} \diego{Of the 48000 legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III.
+Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the 48000 legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III.
 On the other hand, of the 57000 legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III.
-(NOTA: Estos numeros estan actualizados,  pensaba en ponerlos solo porque en ningun momento hablamos de la proporcion, solo se muestran los histos de gradT)}
+\notebyalbert{Luego de des-ralear, las piernas seleccionadas en Figura 4 eran del orden de 100 mil, para  ambas rotaciones.
+Algo no está consistente aquí.}
 
@@
 \hline
-0    & 1&24 &(\Mi&19\%)  &   7&4 &(\Pl&~3\%) &   1&09 &(\Pl&24\%) \\
+0    & 1&24 &(\Mi&19\%)  &   \albert{\bf 7}&\albert{\bf 1} &(\Pl&~3\%) &   1&09 &(\Pl&24\%) \\
 I    & 1&15 &(\Mi&10\%)  &   7&5 &(\Pl&29\%) &   1&25 &(\Pl&24\%) \\
@@
 \caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
-For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.
-\notebyalbert{Propongo que para todas las cantidades absolutas de la Tabla 1 informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
-Doy dos ejemplos para no dejar dudas.
-Para $\NCB$ de Type-II: $1.0\,(-21\%)$.
-Para $\aTm$ de Type-III: $1.0\,(+6\%)$.}\diego{Si aca redondeo, Ncb de type 0 y I toman el mismo valor 1.2, y si no redondeo la temp en type III se ve lindo que sea sub-MK.
-}}
+For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
 \label{tabla_demt}
@@
 
-\diego{A comparison of the results between the two rotations shows that, compared to CR-2082, target rotation CR-2208 was characterized by $\approx 15-20\%$ lower values of the electron density at the coronal base, $\approx 5-30\%$ larger values of density scale height, and $\approx 10-25\%$ larger values of the electron temperature.}
+{A comparison of the results between the two rotations shows that, compared to CR-2082, target rotation CR-2208 was characterized by \albert{$\approx 10-20\%$} lower values of the electron density at the coronal base, $\approx 5-30\%$ larger values of density scale height, and \albert{$\approx 5-25\%$} larger values of the electron temperature.}
 
@@
 Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range.
-As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized} by $\phi_c<0$.}
-
-\subsection{Tomography and Models}\label{awsom_res}
+As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, \albert{being characterized by $\phi_c<0$.
+\vfill}} % NOTA el vfill
+
+\subsection{\albert{Comparison of the DEMT and AWSoM Models}}\label{awsom_res}
 
@@
 
-\notebyalbert{Diego: debés estar seguro que sacaste ARs y low-latitude CHs de los promedios en longitud.
-Cuando más te esmeres la comparación es más justa, y podés revelar algo que de otra manera no se vería.
-Si promediaste longitudes con ARs o CHs, rehacelo, vale la pena.
-Por supuesto debes promediar idéntidas longitudes en DEMT, AWSoM y en la O/C.}\\
-\diego{NOTA: Saqué todo desde un principio, incluso las selcciones donde hay regiones abiertas dentro del streamer.}
-
 \begin{figure}[h!]
@@
 
-{To characterize the results of the AWSoM model in distinct magnetic structures, its results for electron density and temperature were traced along its magnetic field lines.
-For each field line leg, the results were then fit to Equations (\ref{Nfit}) and (\ref{Tfit}).
-\diego{In case of AWSoM, only data above $1.055\,\mrsun$ were fitted.} In its current implementation, the AWSoM model can not simulate down loops, a point we will discuss in the next section.
-We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.}
-
 \begin{figure}[h!]
@@
 
-{For both target rotations, the top panels of Figure \ref{rpoint_awsom} show the latitude-longitude location (at heliocentric height $1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
-That criterion is adapted here, requiring that at least five voxels of the tomographic grid are threaded by the leg.
-Open legs are indicated in gray color and closed ones in black color.
-For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit} and \ref{Tfit}.
-Considering the AWSoM data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_awsom} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a three-color code, type I, II and III legs are shown in red, magenta and cyan color, respectively.
-This figure is to be compared with the corresponding Figure \ref{rpoint_demt} for DEMT results.
-It is readily seen that the AWSoM maps are more populated than those of DEMT.
-This is due to the 3D MHD model having electron density and temperature fields spatially smoother than those of DEMT.}
-
-{For target rotation CR-2082, Figure \ref{histos_2082} shows the statistical distribution of the results of the DEMT (solid line-style) and AWSoM (dashed line-style) models traced along legs of type I, II and III (from top to bottom), as defined in Section \ref{trace}.
-From left to right: electron density at the lowest coronal height of the AWSoM model $\NCB\equiv\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
-In each panel the median values $m$ are indicated.
-Figure \ref{histos_2208} shows the same analysis for target rotation CR-2208.}
+To characterize the results of the AWSoM model in distinct magnetic structures, its results for electron density and temperature were traced along its magnetic field lines.
+For each field line leg, the results were then fit to Equations (\ref{Nfit}) and (\ref{Tfit})\albert{, considering only data points above heliocentric height $1.055\,\mrsun$.
+We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.
+Legs of type 0 are not included for AWSoM, as in its current implementation it can not simulate down loops, a point we will discuss in the next section.}
 
@@
 
-{For the two target rotations, Table \ref{tabla_comp} summarizes a quantitative comparative analysis between the results of the DEMT and AWSoM models.
-The DEMT results are expressed as absolute values, while the ASWSoM results are informed as a percentual variation relative to the corresponding result for DEMT.
-The following major results can be drawn.}
+{For both target rotations, the top panels of Figure \ref{rpoint_awsom} show the latitude-longitude location (at heliocentric height $1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
+That criterion is adapted here, requiring that at least five voxels of the tomographic grid are threaded by the leg.
+Open legs are indicated in gray color and closed ones in black color.
+For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit} and \ref{Tfit}.
+Considering the AWSoM data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_awsom} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
+Using a three-color code, type I, II and III legs are shown in red, magenta and cyan color, respectively.
+This figure is to be compared with the corresponding Figure \ref{rpoint_demt} for DEMT results.
+It is readily seen that the AWSoM maps are more populated than those of DEMT.
+This is due to the 3D MHD model having electron density and temperature fields spatially smoother than those of DEMT.}
+
+{For target rotation CR-2082, Figure \ref{histos_2082} shows the statistical distribution of the results of the DEMT (solid line-style) and AWSoM (dashed line-style) models traced along legs of type I, II and III (from top to bottom), as defined in Section \ref{trace}.
+From left to right: electron density at the lowest coronal height of the AWSoM model $\NCB\equiv\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
+In each panel the median values $m$ are indicated.
+Figure \ref{histos_2208} shows the same analysis for target rotation CR-2208.}
 
@@
 
+{For the two target rotations, Table \ref{tabla_comp} summarizes a quantitative comparative analysis between the results of the DEMT and AWSoM models \albert{based on the results shown in Figures \ref{histos_2082} and \ref{histos_2208}}.
+The DEMT results are expressed as absolute values, while the ASWSoM results are informed as a percentual variation relative to the corresponding result for DEMT.
+The following major results can be drawn.}
+
 {For target rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, depending of the type of leg, while the median value of the scale height $\lN$ agree within $\approx 10\%$.
@@
 CR-2082\\
-I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&~9\%) \\
-II   & 0&99 &(\Mi&25\%)  &   8&9 &(\Mi&~2\%) &   1&36 &(\Mi&~2\%) \\
+I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&\albert{\bf 10}\%) \\
+II   & 0&99 &(\Mi&25\%)  &   \albert{\bf 9}&9 &(\Mi&~2\%) &   1&36 &(\Mi&~2\%) \\
 III  & 0&65 &(\Mi&15\%)  &   7&6 &(\Mi&~8\%) &   0&97 &(\Mi&~9\%) \\
@@
 II   & 0&79 &(\Pl&~9\%)  &  11&8 &(\Mi&14\%) &   1&58 &(\Mi&~8\%) \\
-III  & 0&55 &(\Pl&~1\%)  &   8&6 &(\Mi&16\%) &   1&04 &(\Mi&11\%) \\
+III  & 0&55 &(\Pl&~\albert{\bf 2}\%)  &   8&6 &(\Mi&16\%) &   1&04 &(\Mi&11\%) \\
 \end{tabular}
 \caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
-DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.
-\albert{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
-Ejemplo para CR-2082 $\NCB$ de Type-II: $1.0\,(-23\%)$.
-Ejemplo para CR-2208 $\lambda_N$ de Type-II: $12.0\,(-17\%)$.
-Ejemplo para CR-2208 $\aTm$ de Type-II: $1.6\,(-10\%)$.} \diego{Hay 6 valores que terminan en 5, con lo cual al redondearlos se pierde bastante informacion, lo dejé así como lo vez por eso.
-Si aún asi te parece buena idea redondearlo, lo hacemos.}}
+DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
 \label{tabla_comp}
@@
 
-\section{Discussion}\label{discu}
-
-\noindent\notebyalbert{(by Albert) This section will discuss and summarize some main conclusions, possibly in three groups: a) DEMT analysis alone (including thermodynamical structure, up/down loops, energy considerations, etc.), b) Comparison AWSoM/DEMT (longitude-averaged latitudinal profiles, height-dependence profiles in different magnetic structures, etc), and c) Correlation betweem AWSoM terminal wind speed and DEMT basal density, I will expand on this later this week as this may require help from Michigan).}
-
-\diego{NOTE: Here is a paragraph describing the empirical successes in the reconstruction of both rotations.}
-
-*In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI.
+\section{\albert{Discussion and Conclusions}}\label{discu}
+
+\notebyalbert{Propongo que Diego escriba una primer sección limpia, ordenada.
+Lo que vos mandarías al Solar Physics, sin asteriscos ni nada raro.
+Expresate con párrafos limpios.
+Si querés destacar algo para discutir ponelo como una nota en rojo al final del párrafo correspondiente, no en el medio de los mismos.
+Yo creo que esto debe estructurarse así:
+\begin{enumerate}
+\item Un párrafo (breve) de que se hizo, esto contextualiza. 
+\item Dos o tres párrafos sobre los resultados 3.1.
+Esto es: resultados per se de cada rotación y como comparan (mencionando el tema incertezas).
+Estructura 3D del streamer en CAPAS, revelada observacionalmente en forma global por DEMT, esto incluye UP/DOWN loops.
+Explicar que con AIA no andamos bien en CHs.
+O sí?
+Energía.
+\item Uno o dos párrafos sobre los resultados 3.2. Como compara AWSoM con DEMT. En forma breve. Vale la pena explicar que DOWN loops no se puede.
+\item Luego un párrafo sobre next steps. Esto puede incluir nuevas cosas con AIA-4, el Eclipse, otras rotaciones de mayor intensidad.
+\end{enumerate}
+}
+
+\notebyalbert{Este párrafo que sigue es de Albert.
+Algo así debe ir incluído dentro de la parte que refiere a 3.1.
+Creo que hay que corregir números a la luz de los análisis finales.
+Creo que los números de cuanto más frío o caliente, etc, deben ser corregidos a la luz de la nueva Tabla 1.}
+
+In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI.
 In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
@@
 These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\lesssim 5\%$ and $\approx 2\%$ for the electron temperature and density, respectively.
+\notebyalbert{son estos errores compatibles con los informados en la Sección 2?}
+
+\notebyalbert{El texto hasta el final son de Diego. Algunos se pueden ir, otros pueden servir de semilla para construir las distintas partes de la Sección.}
 
@@
 \citet{nuevo_2013} showed a decrease in the amount of down loops as the solar activity increases, which is consistent with the results shown in this article.
-
-*
 

### 2020-01-13 lloveras_2020_Albert_Section4.tex
mergeo nuevo

@@
 
-\subsection{\albert{DEMT Reconstructions}}\label{demt}
+\subsection{{DEMT Reconstructions}}\label{demt}
 
@@
 
-\subsection{\albert{AWSoM Simulations}}\label{awsom}
+\subsection{{AWSoM Simulations}}\label{awsom}
 
@@
 
-\subsection{\albert{Tracing Results Along Magnetic Fieldlines}}\label{trace}
+\subsection{{Tracing Results Along Magnetic Fieldlines}}\label{trace}
 
@@
 
-\albert{To determine} the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid.
+{To determine} the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid.
 Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = r{\rm d}\theta/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point.
@@
 
-\albert{For analysis purposes, the geometry of all traced magnetic field lines is classified.
+{For analysis purposes, the geometry of all traced magnetic field lines is classified.
 They are first classified as open or closed according to their full geometry.
 Each closed magnetic field line is further classified as ``small" or ``large", according to its coronal length $L$ being smaller or larger than the median value ${\rm Md}(L)$ of the whole population, respectively.
-This median value is ${\rm Md}(L)=0.51$ and $0.46\,\mrsun$ for CR-2082 and CR-2208, respectively.
+This median value is \diego{${\rm Md}(L)=0.50$} and $0.46\,\mrsun$ for CR-2082 and CR-2208, respectively.
 Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e.
@@
 
-At this stage, all DEMT and AWSoM products, electron density and \albert{temperature} in particular, can be traced along open and closed magnetic field lines.
+At this stage, all DEMT and AWSoM products, electron density and {temperature} in particular, can be traced along open and closed magnetic field lines.
 Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one).
 To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it.
-As a result, for each field line one data point per tomographic cell \albert{is obtained.
-This approach} was firstly used by \citet{huang_2012} to \albert{study temperature} structures in the solar minimum \albert{corona and by} \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.
-
-For each open field line and \albert{for each closed field leg}, an exponential fit \albert{was applied} to the electron density \albert{data points} and a linear fit applied to the electron temperature \albert{data points}.
-For \albert{the DEMT model} the data points used were $\sqravgN(r)$ and $\Tm(r)$, and in case of \albert{the AWSoM models} the data points used were $\Ne(r)$ and $\Te(r)$.
+As a result, for each field line one data point per tomographic cell {is obtained.
+This approach} was firstly used by \citet{huang_2012} to {study temperature} structures in the solar minimum {corona and by} \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.
+
+For each open field line and {for each closed field leg}, an exponential fit {was applied} to the electron density {data points} and a linear fit applied to the electron temperature {data points}.
+For {the DEMT model} the data points used were $\sqravgN(r)$ and $\Tm(r)$, and in case of {the AWSoM models} the data points used were $\Ne(r)$ and $\Te(r)$.
 The exponential and linear fit equations are described by
@@
 \notebyalbert{Este párrafo debe ser movido al menos aquí (estaba más abajo), pues el siguiente párrafo ya utiliza el concepto up/down.
-Además está corregido.} \albert{Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies.
+Además está corregido.} {Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies.
 As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
@@
 La jerga estadística es precisa y correcta (no confundir confidence level con confidence interval, está bien?}
-\albert{To determine if a traced filed line leg is of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points.
+{To determine if a traced filed line leg is of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points.
 We then select field lines for which the temperature increases or decreases significantly with height by requiring $|\rhoTr| > 0.5$.
-We then measure the quality of the linear fit to the temperature-height data by means of a chi-squared test \citep{recipes}, and select legs for which the fit has a 90\% confidence level.
+\diego{hablemos sobre esta frase} We then measure the quality of the linear fit to the temperature-height data by means of a chi-squared test \citep{recipes}, and select legs for which the fit has a 90\% confidence level.
 In this way, legs for which the DEMT temperature does not show a significant variation with height, or the linear fit to temperature is good enough, are not considered in this analysis.
@@
 The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg.
-\albert{This requirement is set to ensure a reasonably spread sample of heights along the leg.}
+{This requirement is set to ensure a reasonably spread sample of heights along the leg.}
 \item 
-The \albert{DEMT temperature and height data points must meet} $|\rhoTr| > 0.5$.
+The {DEMT temperature and height data points must meet} $|\rhoTr| > 0.5$.
 \item 
-\albert{The condifence level of both the exponential and linear fits must be larger than 90\%.} \notebyalbert{Aquí corregí, está bien expresado?}
+{The condifence level of both the exponential and linear fits must be larger than 90\%.} \notebyalbert{Aquí corregí, está bien expresado?}\diego{si!}
 \end{enumerate}
@@
 
-\albert{
+{
 \begin{itemize}
@@
 In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed.
-\albert{As shown below, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}
-
-\subsection{\albert{Energy Input Flux}}\label{energia}
+{As shown below, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}
+
+\subsection{{Energy Input Flux}}\label{energia}
 
@@
 
-\albert{The high temperature of the corona requires heating mechanisms to compensate for the the losses.
+{The high temperature of the corona requires heating mechanisms to compensate for the the losses.
 While the vast majority of the existing literature on coronal heating focuses on ARs, some studies have been dedicated to the heating of quiet-Sun regions.
@@
 
-\albert{Consider} a simple energy balance for each magnetic flux tube, \albert{in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated \albert{by a} coronal heating power($E_h$) \citep{aschwanden_2004}:
+{Consider} a simple energy balance for each magnetic flux tube, {in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated {by a} coronal heating power($E_h$) \citep{aschwanden_2004}:
 
@@
 \noindent
-where $s$ is the position along \albert{the flux tube} and the \albert{power quntities} are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.
+where $s$ is the position along {the flux tube} and the {power quntities} are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.
 
@@
 \notebyalbert{Luego de des-ralear, las piernas seleccionadas en Figura 4 eran del orden de 100 mil, para  ambas rotaciones.
-Algo no está consistente aquí.}
+Algo no está consistente aquí.}\diego{Statloop 6 alturas noda algo asi como 150k piernas, algunas no se trazan (entre 30 y 40k) lo cual nos deja aprox 110k.
+SUpongo que te quedaste con ese numero.
+Pero elimino los cuasi isotermicos, perdemos 30k en el streamer y 10k en CH.
+Luego hacemos una seleccion qie involucra footpoints y ahi perdemos lo que falta!
+Es decir, el numero del draft ya es des-raleado.}
 
@@
 \hline
-0    & 1&24 &(\Mi&19\%)  &   \albert{\bf 7}&\albert{\bf 1} &(\Pl&~3\%) &   1&09 &(\Pl&24\%) \\
+0    & 1&24 &(\Mi&19\%)  &   {\bf 7}&{\bf 1} &(\Pl&~3\%) &   1&09 &(\Pl&24\%) \\
 I    & 1&15 &(\Mi&10\%)  &   7&5 &(\Pl&29\%) &   1&25 &(\Pl&24\%) \\
@@
 
-{A comparison of the results between the two rotations shows that, compared to CR-2082, target rotation CR-2208 was characterized by \albert{$\approx 10-20\%$} lower values of the electron density at the coronal base, $\approx 5-30\%$ larger values of density scale height, and \albert{$\approx 5-25\%$} larger values of the electron temperature.}
+{A comparison of the results between the two rotations shows that, compared to CR-2082, target rotation CR-2208 was characterized by {$\approx 10-20\%$} lower values of the electron density at the coronal base, $\approx 5-30\%$ larger values of density scale height, and {$\approx 5-25\%$} larger values of the electron temperature.}
 
@@
 Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range.
-As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, \albert{being characterized by $\phi_c<0$.
+As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized by $\phi_c<0$.
 \vfill}} % NOTA el vfill
 
-\subsection{\albert{Comparison of the DEMT and AWSoM Models}}\label{awsom_res}
+\subsection{{Comparison of the DEMT and AWSoM Models}}\label{awsom_res}
 
@@
 To characterize the results of the AWSoM model in distinct magnetic structures, its results for electron density and temperature were traced along its magnetic field lines.
-For each field line leg, the results were then fit to Equations (\ref{Nfit}) and (\ref{Tfit})\albert{, considering only data points above heliocentric height $1.055\,\mrsun$.
+For each field line leg, the results were then fit to Equations (\ref{Nfit}) and (\ref{Tfit}){, considering only data points above heliocentric height $1.055\,\mrsun$.
 We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.
@@
 
-{For the two target rotations, Table \ref{tabla_comp} summarizes a quantitative comparative analysis between the results of the DEMT and AWSoM models \albert{based on the results shown in Figures \ref{histos_2082} and \ref{histos_2208}}.
+{For the two target rotations, Table \ref{tabla_comp} summarizes a quantitative comparative analysis between the results of the DEMT and AWSoM models {based on the results shown in Figures \ref{histos_2082} and \ref{histos_2208}}.
 The DEMT results are expressed as absolute values, while the ASWSoM results are informed as a percentual variation relative to the corresponding result for DEMT.
@@
 CR-2082\\
-I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&\albert{\bf 10}\%) \\
-II   & 0&99 &(\Mi&25\%)  &   \albert{\bf 9}&9 &(\Mi&~2\%) &   1&36 &(\Mi&~2\%) \\
+I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&{\bf 10}\%) \\
+II   & 0&99 &(\Mi&25\%)  &   {\bf 9}&9 &(\Mi&~2\%) &   1&36 &(\Mi&~2\%) \\
 III  & 0&65 &(\Mi&15\%)  &   7&6 &(\Mi&~8\%) &   0&97 &(\Mi&~9\%) \\
@@
 II   & 0&79 &(\Pl&~9\%)  &  11&8 &(\Mi&14\%) &   1&58 &(\Mi&~8\%) \\
-III  & 0&55 &(\Pl&~\albert{\bf 2}\%)  &   8&6 &(\Mi&16\%) &   1&04 &(\Mi&11\%) \\
+III  & 0&55 &(\Pl&~{\bf 2}\%)  &   8&6 &(\Mi&16\%) &   1&04 &(\Mi&11\%) \\
 \end{tabular}
@@
 
-\section{\albert{Discussion and Conclusions}}\label{discu}
+\section{{Discussion and Conclusions}}\label{discu}
 

### 2020-01-14 lloveras_2020.tex
nuevas imag

@@
 
-\subsection{DEMT reconstructions}\label{demt}
+\subsection{{DEMT Reconstructions}}\label{demt}
 
@@
 
-\subsection{AWSoM simulations}\label{awsom}
+\subsection{{AWSoM Simulations}}\label{awsom}
 
@@
 
-\subsection{Tracing of results along fieldlines}\label{trace}
-
-\noindent\notebyalbert{This section will explain how the AWSoM magnetic model is used to trace the thermodynamic products of both DEMT and AWSoM along the fieldlines of AWSoM.
+\subsection{{Tracing Results Along Magnetic Fieldlines}}\label{trace}
+
+%\noindent\notebyalbert{This section will explain how the AWSoM magnetic model is used to trace the thermodynamic products of both DEMT and AWSoM along the fieldlines of AWSoM.
 This requires covering the following points:
-\begin{itemize}
-  \item A first paragraph qualitatively describing the process. This includes mentioning that the AWSoM products are first interpolated into the DEMT grid.
-  \item A short paragraph describing the numerical method used to trace field lines.
+%\begin{itemize}
+%  \item A first paragraph qualitatively describing the process. This includes mentioning that the AWSoM products are first interpolated into the DEMT grid.
+%  \item A short paragraph describing the numerical method used to trace field lines.
 We have a nice version of this in your previous paper.
 At this point the reader should understand that for each field line we have its geometry $\mathbf{r}(s)$ as a function of the distance $s$ along the loop, with $s(1\,\mrsun)\equiv 0$.
-  \item Explain very simply how then that for each voxel the middle point of the field line is selected and assigned the DEMT and AWSoM products of that cell.
+%  \item Explain very simply how then that for each voxel the middle point of the field line is selected and assigned the DEMT and AWSoM products of that cell.
 At this point the reader should understand that for each field line we have: $Q[r(s)]$, where $Q$ is any given quantity from either the DEMT model (specifically $\sqravgN$ and $\Tm$) or the AWSoM model (specifically $\Ne$ and $\Te$).
-  \item Explain fits to the DEMT results  $\sqravgN(r)$, $\Tm(r)$.
-  \item Explain then the classification of field lines.
-\end{itemize}
-}
-
-Aiming determination of the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid.
+%  \item Explain fits to the DEMT results  $\sqravgN(r)$, $\Tm(r)$.
+%  \item Explain then the classification of field lines.
+%\end{itemize}}
+
+{To determine} the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid.
 Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = r{\rm d}\theta/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point.
 In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, for a total of $96,000$ starting points.
-Each traced field line is classified as ``open" if it intersects the source surface, set in this work at $r=6\,\mrsun$ (where lines become radial), or as ``closed" otherwise.
-In the case of closed magnetic lines, they are separated in two ``legs", from the base to the apex.
-
-%\diego{Of these legs, those whose size $L$ are smaller than the average lengths $\langle L \rangle$ are called small, and those with $L > \langle L \rangle$ ar called large.}
-\diego{
-In the case of closed magnetic field lines, legs {are} further classified as ``small" and ``large" upon their apex height being within or beyond the lenght average of the closed legs, respectively.
-}
-
-At this stage, all DEMT and AWSoM products, electron density and mean temperature in particular, can be traced along open and closed magnetic field lines.
+
+{For analysis purposes, the geometry of all traced magnetic field lines is classified.
+They are first classified as open or closed according to their full geometry.
+Each closed magnetic field line is further classified as ``small" or ``large", according to its coronal length $L$ being smaller or larger than the median value ${\rm Md}(L)$ of the whole population, respectively.
+This median value is \diego{${\rm Md}(L)=0.50$} and $0.46\,\mrsun$ for CR-2082 and CR-2208, respectively.
+Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e.
+their location at $r=1\,\mrsun$) to its apex (i.e., the location of maximum height).} \notebyalbert{Diego, aquí ordené y corregí mucho y creo que es un buen ejemplo de corrección de estilo de redacción, si querés comparar con como estaba antes.
+Nota: MHD no tiene source surface!
+Ahora bien, además informo ${\rm Md}(L)$.
+Para ello multipliqué por dos el valor mediano de las longitudes de las piernas (que recuerdo de memoria, por ahí la pifié).
+Vale la pena que le muestres estos histogramas a Fede y la pieza de código de donde sale, para confirmar la metodología y de paso los números.
+Es importante.}
+
+At this stage, all DEMT and AWSoM products, electron density and {temperature} in particular, can be traced along open and closed magnetic field lines.
 Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one).
 To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it.
-As a result, for each field line one data point per tomographic cell is obtained.
-This allows to analyze how density and temperature, coming from both models, vary with height along each individual field line.
-This approach was firstly used by \citet{huang_2012} to study inverted temperature structures in the solar minimum corona, and later on applied by \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.
-
-For each open field line, and for each leg of the closed ones, an exponential fit was then applied to the electron density and a linear fit applied to the electron temperature.
-For DEMT results the data points used were $\sqravgN(r)$ and $\Tm(r)$, and in case of AWSoM the data points used were $\Ne(r)$ and $\Te(r)$.
+As a result, for each field line one data point per tomographic cell {is obtained.
+This approach} was firstly used by \citet{huang_2012} to {study temperature} structures in the solar minimum {corona and by} \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.
+
+For each open field line and {for each closed field leg}, an exponential fit {was applied} to the electron density {data points} and a linear fit applied to the electron temperature {data points}.
+For {the DEMT model} the data points used were $\sqravgN(r)$ and $\Tm(r)$, and in case of {the AWSoM models} the data points used were $\Ne(r)$ and $\Te(r)$.
 The exponential and linear fit equations are described by
@@
 
-In the present work we focus on legs with increasing and decreasing temperatures in linear form.
-In other words, we selected those legs where the {Pearson correlation coefficient $\rho$ between temperature $T$ and radius $r$ meets $|\rhoTr| > 0.5$} {(with 95\% confidence level)}.
-In this way, those legs in which the DEMT results cannot ensure a noticeable change in temperature between the base and the apex, are discarded.
-
-The linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg.
-Both fits consider tomographic systematic uncertainty estimated in \citet{lloveras_2017}, i.e.
-$0.07$ MK for $\Tm$ and $4.0\,10^6 cm^{-3}$ for $\Ne$.
-
-To measure how good the quality of the fit are, a chi-square merit function was used (Section 15.2 \citet{recipes}).%, selecting only legs with 95\% confidence level.
-
-%el p-valor es un concepto estadístico, no veo xq deberia ser explicado. Lo que si, en el paper explicare bien las hipotesis nulas y de esa forma el p-valor queda bien claro.
-%El p-valor es una cuantificacion de con cuanta probabilidad de exito estas rechazando o aceptando una hipotesis en particular que se la suele denominar hipotesis nula.
-%En este caso, con 95$\%$ de seguridad estas rechazando las piernas que tienen un $pearson_x,y = 0$. Es decir te estarias quedando con aquellas que tienen una dependencia lineal entre x e y.
-%En el segundo caso, el test de hipotesis seria sobre la hip nula de que los datos provienen una funcion distribucion donde la recta fiteada de esos datos es el valor esperado de la distribucion.
-Con lo cual hacerle un test chi cuadrado te da una idea de cuan acertado o no es el ajuste.
-En este caso la hipotesis nula es que los datos provienen de esa distrib, con lo cual el chi deberia dar bajo y descartas los que dan valores altos con un 95$\%$ de seguridad.
-Eso es lo que representa el p-valor =0.05 en este caso (el area bajo la funcion distribucion, es decir, probabilidad).
-
-{To be selected a leg must meet all following conditions.}
-
-\diego{
+\notebyalbert{Este párrafo debe ser movido al menos aquí (estaba más abajo), pues el siguiente párrafo ya utiliza el concepto up/down.
+Además está corregido.} {Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies.
+As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
+Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}.
+In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}
+
+\notebyalbert{Reordené y corregí mucho el siguiente párrafo.
+Lo que see lee es correcto en cada detalle y palabra?
+Está bien explicado todo lo que concierne a chi-suqared?
+La jerga estadística es precisa y correcta (no confundir confidence level con confidence interval, está bien?}
+{To determine if a traced filed line leg is of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points.
+We then select field lines for which the temperature increases or decreases significantly with height by requiring $|\rhoTr| > 0.5$.
+\diego{hablemos sobre esta frase} We then measure the quality of the linear fit to the temperature-height data by means of a chi-squared test \citep{recipes}, and select legs for which the fit has a 90\% confidence level.
+In this way, legs for which the DEMT temperature does not show a significant variation with height, or the linear fit to temperature is good enough, are not considered in this analysis.
+Finally, selected legs are then classified as up or down according to if $\rhoTr > +0.5$ or $\rhoTr < -0.5$, respectively.
+The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg.
+Both fits consider tomographic systematic uncertainty of the electron temeprature and density, respectively estimated to be $\Delta(\Tm) \approx 0.07\,\MK$ and $\Delta(N_e)\approx 4.0\times 10^6\,\cm^{-3}$ by \citet{lloveras_2017}.
+\notebyalbert{No comprendo bien si esta última linea está bien ubicada aquí, de todas formas lo corregí un poco.
+Precisaría que discutamos los tres estos tres párrafos en naranja el lunes.} In summary, to be selected a leg must meet all three following conditions:}
+
 \begin{enumerate}
@@
 The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg.
+{This requirement is set to ensure a reasonably spread sample of heights along the leg.}
 \item 
-The {value of the Pearson correlation coefficient meets $|\rhoTr| > 0.5$.}
+The {DEMT temperature and height data points must meet} $|\rhoTr| > 0.5$.
 \item 
-The coefficient level of both the exponential and linear fit must be grater than \%90.
+{The condifence level of both the exponential and linear fits must be larger than 90\%.} \notebyalbert{Aquí corregí, está bien expresado?}\diego{si!}
 \end{enumerate}
-}
-
-{Coronal magnetic structures for which their temperature increases/decreases with height (in the inner corona) have been dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies.
-As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
-Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}.
-In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}
 
 {To characterize the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model.
-Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types in this work:}
-
-\diego{
+Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types in this work:} \notebyalbert{Simplifiqué mucho esto.}
+
+{
 \begin{itemize}
-\item Type 0 - Small legs (coming from closed field) in the latitudes range $[-50\mdeg,+50\mdeg]$, and $\rhoTr < -0.5$. 
- %This class thoroughly populates the equator of the Streamer belt during a minimum solar rotation.
-\item Type I - Small legs (coming from closed field) in the latitudes range $[-50\mdeg,+50\mdeg]$, and $\rhoTr > 0.5$. 
-%This class thoroughly populates the inner of the Streamer belt.
-\item Type II - Large legs (coming from closed field) in the latitudes range $[-90\mdeg,-40\mdeg] \cup [+40\mdeg,+90\mdeg]$, and $\rhoTr > 0.5$. 
-%This class is mostly populated by very large trans-equatorial field lines forming the envelope of the Streamer belt. 
-\item Type III - Open field lines in the latitudes range $[-90\mdeg,-60\mdeg] \cup [+60\mdeg,+90\mdeg]$, and $\rhoTr > 0.5$.
+\item Type 0: closed-small-down with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
+\item Type I: closed-small-up with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
+\item Type II: closed-large-up with footpoints in the range $|{\rm latitude}|>40\mdeg$. 
+\item Type III: open with footpoint in the range $|{\rm latitude}|>60\mdeg$.
 \end{itemize}
 }
-{In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed.}
-
-\subsection{{Energy input flux}}\label{energia}
-
-\noindent\notebyalbert{This section will summarize how loop integrated energy quantities are computed from the DEMT products and the AWSoM magetic model alone.
+
+In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed.
+{As shown below, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}
+
+\subsection{{Energy Input Flux}}\label{energia}
+
+%\noindent\notebyalbert{This section will summarize how loop integrated energy quantities are computed from the DEMT products and the AWSoM magetic model alone.
 The summary will not include any derivation and will refer to Cecilia's paper.
@@
 At the end the reader should understand that their sum is the enery input flux required at the coronal base to maintain the loop stable.
-This should be a very short section, as it is a summary of one previous paper alone.}
-
-%correcciones a hacer! DIEGO
-%Los términos de la Eq (10) requieren ser explicados.
-La explicación a conituación no es clara, y de hecho está mal escrita.
-La Eq.
-(7) se integra en el VOLUMEN CORONAL COMPLETO de cada tubo de flujo y se divide por el área basal del mismo.
-Utilizando la condición solenoidal de B se llega a la Eq.
-(7), dónde...
-y ahí deberían darse las expresiones de Phir y Phic porque no pertenecen a la literatura estandard, y explicar a continuación como todos los elementos de esas dos expresiones surgen de los fits de DEMT y del modelo magnético de AWSoM.
-Donde si se puede ahorrar mucho espacio es en lo previo, la Eq (8) podría no incluirse por ejemplo.
-Creo que ahora lo mejor es que trates de completar la explicación dando las expresiones de Phir y Phic, y luego vemos de como limarla, probablemente eliminando la ec.
-(8).
-y además el texto puede compactarse, corregirse y reordenarse mucho.
-Poné las unidades de las cantidades Phi entre paréntesis a continuación de $\Phi_{h,r,c}$.
-
-Due the difference between temperatures of transition region and solar corona, there must to be a heating mechanism that compensate all the losses present in the atmosphere and maintain stable the plasma temperature.
-Previous works have studied this mechanism by observations and modeling, but mostly for active regions.
-\citet{maccormack_2017} have developed a technique that estimate the heating injected into the loops during a period of minima activity.
-Using DEMT combined with an extrapolation of magnetic field, as we detailed before, they obtain the different plasma parameters along each magnetic loop, and therefore, compute the energy input flux required to maintain them stable.
-The model assume a simple energy balance for each magnetic flux tube, where the losses by radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated by some coronal heating power($E_h$) \citep{aschwanden_2004}:
+This should be a very short section, as it is a summary of a single previous paper.}
+
+{The high temperature of the corona requires heating mechanisms to compensate for the the losses.
+While the vast majority of the existing literature on coronal heating focuses on ARs, some studies have been dedicated to the heating of quiet-Sun regions.
+In particular,  \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to mantain them stable.
+The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in the previous Section \ref{trace}.}
+
+{Consider} a simple energy balance for each magnetic flux tube, {in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated {by a} coronal heating power($E_h$) \citep{aschwanden_2004}:
 
@@
 \noindent
-where $s$ is the position along each magnetic flux tube and the powers are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.
-
-\noindent\notebyalbert{Trabajé todo lo naranja.
-Primero decidí que es mejor no numerar $E_c$ sino $F_c$.
-Eso te quedará claro cuando agregues las ecuaciones (11) y (12) que te indico más abajo y leas el último párrafo naranja de abajo, ahí cierra todo.
-Además describí que son los $\phi$ en forma correcta.
-El texto previo estaba muy flojón, entre otras cosas se hablaba de una (inexistente) ``conductive loss function" y de una (incorrectamente denominada) ``area along the loop".
-Obviamente luego de chequear este texto naranja borrá esta nota azul en particular.}
+where $s$ is the position along {the flux tube} and the {power quntities} are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.
 
@@
 Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} \diego{Of the 48000 legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III.
+Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the 48000 legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III.
 On the other hand, of the 57000 legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III.
-(NOTA: Estos numeros estan actualizados,  pensaba en ponerlos solo porque en ningun momento hablamos de la proporcion, solo se muestran los histos de gradT)}
+\notebyalbert{Luego de des-ralear, las piernas seleccionadas en Figura 4 eran del orden de 100 mil, para  ambas rotaciones.
+Algo no está consistente aquí.}\diego{Statloop 6 alturas noda algo asi como 150k piernas, algunas no se trazan (entre 30 y 40k) lo cual nos deja aprox 110k.
+SUpongo que te quedaste con ese numero.
+Pero elimino los cuasi isotermicos, perdemos 30k en el streamer y 10k en CH.
+Luego hacemos una seleccion qie involucra footpoints y ahi perdemos lo que falta!
+Es decir, el numero del draft ya es des-raleado.}
 
@@
 \hline
-0    & 1&24 &(\Mi&19\%)  &   7&4 &(\Pl&~3\%) &   1&09 &(\Pl&24\%) \\
+0    & 1&24 &(\Mi&19\%)  &   7&1 &(\Pl&~3\%) &   1&09 &(\Pl&24\%) \\
 I    & 1&15 &(\Mi&10\%)  &   7&5 &(\Pl&29\%) &   1&25 &(\Pl&24\%) \\
 II   & 0&98 &(\Mi&20\%)  &   9&9 &(\Pl&19\%) &   1&36 &(\Pl&16\%) \\
-III  & 0&65 &(\Mi&15\%)  &   7&6 &(\Pl&12\%) &   0&97 &(\Pl&~7\%) \\
+III  & 0&66 &(\Mi&12\%)  &   7&7 &(\Pl&15\%) &   0&97 &(\Pl&18\%) \\
 \hline          
@@
 
-\diego{A comparison of the results between the two rotations shows that, compared to CR-2082, target rotation CR-2208 was characterized by $\approx 15-20\%$ lower values of the electron density at the coronal base, $\approx 5-30\%$ larger values of density scale height, and $\approx 10-25\%$ larger values of the electron temperature.}
+{A comparison of the results between the two rotations shows that, compared to CR-2082, target rotation CR-2208 was characterized by {$\approx 10-20\%$} lower values of the electron density at the coronal base, $\approx 5-30\%$ larger values of density scale height, and {$\approx 5-25\%$} larger values of the electron temperature.}
 
@@
 Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range.
-As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized} by $\phi_c<0$.}
-
-\subsection{Tomography and Models}\label{awsom_res}
+As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized by $\phi_c<0$.
+\vfill}} % NOTA el vfill
+
+\subsection{{Comparison of the DEMT and AWSoM Models}}\label{awsom_res}
 
@@
 
-{For both target rotations, the top panels of Figure \ref{rpoint_awsom} show the latitude-longitude location (at heliocentric height $1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
-That criterion is adapted here, requiring that at least five voxels of the tomographic grid are threaded by the leg.
-Open legs are indicated in gray color and closed ones in black color.
-For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit} and \ref{Tfit}.
-Considering the AWSoM data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_awsom} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a three-color code, type I, II and III legs are shown in red, magenta and cyan color, respectively.
-This figure is to be compared with the corresponding Figure \ref{rpoint_demt} for DEMT results.
-It is readily seen that the AWSoM maps are more populated than those of DEMT.
-This is due to the 3D MHD model having electron density and temperature fields spatially smoother than those of DEMT.}
-
-{For target rotation CR-2082, Figure \ref{histos_2082} shows the statistical distribution of the results of the DEMT (solid line-style) and AWSoM (dashed line-style) models traced along legs of type I, II and III (from top to bottom), as defined in Section \ref{trace}.
-From left to right: electron density at the lowest coronal height of the AWSoM model $\NCB\equiv\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
-In each panel the median values $m$ are indicated.
-Figure \ref{histos_2208} shows the same analysis for target rotation CR-2208.}
+To characterize the results of the AWSoM model in distinct magnetic structures, its results for electron density and temperature were traced along its magnetic field lines.
+For each field line leg, the results were then fit to Equations (\ref{Nfit}) and (\ref{Tfit}){, considering only data points above heliocentric height $1.055\,\mrsun$.
+We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.
+Legs of type 0 are not included for AWSoM, as in its current implementation it can not simulate down loops, a point we will discuss in the next section.}
 
@@
 
+{For the two target rotations, Table \ref{tabla_comp} summarizes a quantitative comparative analysis between the results of the DEMT and AWSoM models {based on the results shown in Figures \ref{histos_2082} and \ref{histos_2208}}.
+The DEMT results are expressed as absolute values, while the ASWSoM results are informed as a percentual variation relative to the corresponding result for DEMT.
+The following major results can be drawn.}
+
 {For target rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, depending of the type of leg, while the median value of the scale height $\lN$ agree within $\approx 10\%$.
@@
 CR-2082\\
-I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&~9\%) \\
-II   & 0&99 &(\Mi&25\%)  &   8&9 &(\Mi&~2\%) &   1&36 &(\Mi&~2\%) \\
-III  & 0&65 &(\Mi&15\%)  &   7&6 &(\Mi&~8\%) &   0&97 &(\Mi&~9\%) \\
+I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&10\%) \\
+II   & 0&99 &(\Mi&25\%)  &   9&9 &(\Mi&~2\%) &   1&36 &(\Mi&~2\%) \\
+III  & 0&66 &(\Mi&17\%)  &   7&0 &(\Mi&~9\%) &   0&97 &(\Mi&~9\%) \\
 \hline          
@@
 II   & 0&79 &(\Pl&~9\%)  &  11&8 &(\Mi&14\%) &   1&58 &(\Mi&~8\%) \\
-III  & 0&55 &(\Pl&~1\%)  &   8&6 &(\Mi&16\%) &   1&04 &(\Mi&11\%) \\
+III  & 0&58 &(\Mi&~3\%)  &   8&9 &(\Mi&18\%) &   1&14 &(\Mi&18\%) \\
 \end{tabular}
 \caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
-DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.
-\albert{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
-Ejemplo para CR-2082 $\NCB$ de Type-II: $1.0\,(-23\%)$.
-Ejemplo para CR-2208 $\lambda_N$ de Type-II: $12.0\,(-17\%)$.
-Ejemplo para CR-2208 $\aTm$ de Type-II: $1.6\,(-10\%)$.} \diego{Hay 6 valores que terminan en 5, con lo cual al redondearlos se pierde bastante informacion, lo dejé así como lo vez por eso.
-Si aún asi te parece buena idea redondearlo, lo hacemos.}}
+DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
 \label{tabla_comp}
@@
 
-\section{Discussion}\label{discu}
-
-\noindent\notebyalbert{(by Albert) This section will discuss and summarize some main conclusions, possibly in three groups: a) DEMT analysis alone (including thermodynamical structure, up/down loops, energy considerations, etc.), b) Comparison AWSoM/DEMT (longitude-averaged latitudinal profiles, height-dependence profiles in different magnetic structures, etc), and c) Correlation betweem AWSoM terminal wind speed and DEMT basal density, I will expand on this later this week as this may require help from Michigan).}
-
-\diego{NOTE: Here is a paragraph describing the empirical successes in the reconstruction of both rotations.}
-
-*In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI.
+\section{{Discussion and Conclusions}}\label{discu}
+
+\notebyalbert{Propongo que Diego escriba una primer sección limpia, ordenada.
+Lo que vos mandarías al Solar Physics, sin asteriscos ni nada raro.
+Expresate con párrafos limpios.
+Si querés destacar algo para discutir ponelo como una nota en rojo al final del párrafo correspondiente, no en el medio de los mismos.
+Yo creo que esto debe estructurarse así:
+\begin{enumerate}
+\item Un párrafo (breve) de que se hizo, esto contextualiza. 
+\item Dos o tres párrafos sobre los resultados 3.1.
+Esto es: resultados per se de cada rotación y como comparan (mencionando el tema incertezas).
+Estructura 3D del streamer en CAPAS, revelada observacionalmente en forma global por DEMT, esto incluye UP/DOWN loops.
+Explicar que con AIA no andamos bien en CHs.
+O sí?
+Energía.
+\item Uno o dos párrafos sobre los resultados 3.2. Como compara AWSoM con DEMT. En forma breve. Vale la pena explicar que DOWN loops no se puede.
+\item Luego un párrafo sobre next steps. Esto puede incluir nuevas cosas con AIA-4, el Eclipse, otras rotaciones de mayor intensidad.
+\end{enumerate}
+}
+
+\notebyalbert{Este párrafo que sigue es de Albert.
+Algo así debe ir incluído dentro de la parte que refiere a 3.1.
+Creo que hay que corregir números a la luz de los análisis finales.
+Creo que los números de cuanto más frío o caliente, etc, deben ser corregidos a la luz de la nueva Tabla 1.}
+
+In this work the combination of DEMT reconstructions and PFSS models has been used to perform a comparative study of the 3D thermodynamical state of the low solar corona ($1.02-1.23\,\mrsun$) {for two rotations sampling} the last two solar minima.
+Specifically the study compares rotations CR-1915 and CR-2081, {respectively sampling} the SC 22/23 and SC 23/24 minima.
+The SC 22/23 minimum was shorter, more active and intermittent.
+The SC 23/24 minimum {was remarkably} characterized by a $\approx 1$ year period {showing virtually} no sunspots.
+Being CR-2081 near the end of that extremely quiet period, it was one of the most axisymmetric and quiet rotations on record from that period \citep{nuevo_2013}.
+
+In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI.
 In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.

### 2020-01-14 lloveras_2020_Albert_Section4.tex

@@
 
+\albert{Based on time-series of EUV images, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the solar corona.
+The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}.
+In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid.
+The size of the tomographic cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions.
+The cadence of the data time-series is set to 6\,hr.
+The main product of the technique is the local DEM (LDEM), a measure of the temperature distribution of the plasma contained in each voxel of the tomographic grid.
+A recent review by \citet{vasquez_2016} summarizes the DEMT works up until then.
+More recently \citet{lloveras_2017} applied DEMT to study the last two solar minima, and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona.}
+
 \section{Methodology}\label{meto}
@@
 
-\noindent\notebyalbert{This section will summarize DEMT's main aspects and equations, only those needed to understand the paper.
+%\noindent\notebyalbert{This section will summarize DEMT's main aspects and equations, only those needed to understand the paper.
 Nothing not needed to read this paper is provided.
@@
 Points to cover are:
-\begin{itemize}
-  \item Selected targets, instruments used. One paragraph.
-  \item Characteristics of the data (specific time series, dates, bands, etc.), SolarSoft software version used for their processing. One paragraph.
-  \item Technical aspects of DEMT (grid, regularization, off-limb data is only used) and how these differ from previous versions (rereferences). One paragraph.
-  \item What is FBE, what is LDEM, what is R.
+%\begin{itemize}
+%  \item Selected targets, instruments used. One paragraph.
+%  \item Characteristics of the data (specific time series, dates, bands, etc.), SolarSoft software version used %for their processing. One paragraph.
+%  \item Technical aspects of DEMT (grid, regularization, off-limb data is only used) and how these differ from previous versions (rereferences). One paragraph.
+%  \item What is FBE, what is LDEM, what is R.
 Why we care about these three quantities and what is their physical meaning should be clear.
 Then the final products $\Nm$ and $\Tm$, and what is their physical meaning.
-\end{itemize}
-}
-
-To perform the comparison two specific rotations were selected, CR-2082 (2009, 05 April through 03 May), a deep minimum period between solar cycles (SCs) 23 and 24 characterized by virtually no ARs, and CR-2208 (2018, 02 September through 29 September), a rotation during the early declining fase of SC 24.
-
-To determine the thermodynamical structure of both rotations, the DEMT technique was applied to respective time series of EUV images covering each first half rotation.
-To study CR-2082 and CR-2208 data taken by the EUVI-B/STEREO and AIA/SDO instruments was used, respectively.
-
-In DEMT, the low corona in the height range $1.0$ to $1.25\,\mrsun$ is discretized in a spherical computational grid.
-The size of the tomographic cell (or voxel) is set to 0.01 \rsun \ in the radial direction, while is set 2\deg\ in both the latitudinal and longitudinal directions.
-We carried out a reconstruction using half of a solar rotation blocking the lines-of-sight comming from the disk (i.e.
-only using off-limb data).
-
-Using the high cadence of data available, one image every 10 minutes were used.
-The selected images were averaged in 6-hour intervals which, given the angular resolution, is the cadence needed to fully constrain the inversion problem, for a total of about 55 images to cover a half solar rotation.
-For both rotations, the first 14 days of data were used.
-
-EUV images are affected by instrumental stray light contamination, which can be corrected by deconvolution of the point spread function (PSF).
-While in the case of AIA images there is no reliable determination of its PSF, it has been well determined for EUVI-B by \citet{shearer_2012}.
-For this article, all EUVI images were stray-light corrected.
-For the details of impact in $\Nm$ and $\Tm$, refer to \citet{lloveras_ba2017}.
-
-\diego{
-Unlike in previous works, a 3D regularization scheme was applied, thus spurious artifacts (nduced by the previous longitude latitude regularization schemei) were minimized in the first two heights of the tomographic grid.}
-
-We refer the reader to \citet{frazin_2009} for a detailed description of the technique, and to \citet{vasquez_2016} for a recent review on all published work based on it.
-Here we summarize the key points.
-The technique involves two consecutive procedures.
+%\end{itemize}
+%}
+
+\albert{We carried out the 3D DEMT reconstruction and MHD modeling of two target Carrington rotations (CR).
+We selected CR-2082 (2009, 05 April through 03 May), a deep minimum rotation between solar cycles (SC) 23 and 24, and CR-2208 (2018, 02 September through 29 September), a rotation during the early declining fase of SC 24.
+To study CR-2082 and CR-2208 data taken by the STEREO/EUVI-B/STEREO and SDO/AIA instruments was used, respectively.
+The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package.
+For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.}
+
+\albert{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we opted to only use off-limb data.
+In this way, the smallest scale and brighter coronal features seen on disk (most typically in the 171\AA\ band) are not included.
+This has two implications.
+Fistly, the fast dynamics that typically characterizes those structures is abscent from the data.
+Sencondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume.
+As a result, coronal dynamics induced artifacts are reduced compared to previous DEMT reconstructions.}
+.
+\albert{The solution of the tomographic problem involves a very large sparse matrix.
+Such type of inversion problems are characterized by spurious high-frequency artifacts in the solution, which can be mitigated through \emph{regularization} techniques \citep{frazin_2000}.
+In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude.
+Also new to the present work, is the implementation of an expanded 3D regularization scheme, which adds to the previous scheme a finite difference matrix operator to approximate radial derivatives.
+In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions.
+As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.}
+
+\albert{We summarize next the main aspects of DEMT required for the analysis of this work. We refer the reader to \citet{frazin_2009} for a full description of the technique.}
 
 In a first step, the time series of EUV images is used to solve a solar rotational tomography (SRT) problem, for each EUV band independently.
-As a result, the 3D distribution of the so called {filter band emissivity} (FBE) is determined for each band separately.
+As a result, the 3D distribution of the so called \emph{filter band emissivity} (FBE) is determined for each band separately.
 The FBE, {an emissivity-type quantity}, is defined as the wavelength integral of the coronal EUV spectral emissivity and the telescope's passband function of each EUV channel.
 Line-of-sight (LOS) integration of the FBE provides synthetic images that can be quantitatively compared to the real data in the time series.
-To find the FBE, the tomographic problem is posed a global optimization problem in which the quadratic norm of the difference between all pairs of synthetic and real images is minimized.
-Spatial regularization terms are also included in the objective function as to minimize high frequency spurious artifacts that are due to the specific characteristics of the SRT sparse projection matrix \citep{frazin_2009,frazin_2000}.
-{Due to optical depth issues that may affect LOSs} passing very close to the limb, and to the decay of intensity with radii, the 3D maps produced by DEMT analysis typically cover the height range 1.02 to 1.23 \rsun \ \citep{frazin_2009}.
-
-\diego{COMO INTRODUZCO EL NIVEL DE REGULARIZACION? For each instrument, the DEMT analysis involves a cross-validation study to determine the optimal level of regularization.}
-
-{In a second step, the FBE values obtained for all bands in each voxel are used to constrain the determination of a {local differential emission measure} (LDEM) distribution, which describes the temperature distribution of the electron plasma contained in each individual tomographic grid voxel.
-Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}
+To find the FBE, the tomographic problem is posed a global optimization problem in which the quadratic norm of the difference between all \albert{pairs of synthetic and real images is minimized.}
+
+{In a second step, the FBE values obtained for all bands in each voxel \albert{of the tomographic grid are used to constrain the determination of the LDEM which, as described in Section \ref{intro}, describes the temperature distribution of the plasma within the individual voxel.} Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}
 
@@
 
-{
+\noindent
+\albert{where $K$ is the number EUV bands, and $\TRF^{(k)}$ is the \emph{temperature response function} of the $j$-th detector.
+The TRFs are here computed based on the (known) channel’s passband times the coronal emissivity at that temperature (normalized by the squared electron density).
+The emissivity model used here is provided by the latest version of the CHIANTI atomic database and plasma emission model \citep{delzanna_2015,landi_2013}.}
+
 Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}.
 These non-reconstructed voxels are indicated as black voxels in the Carrington maps of the reconstructed DEMT reults in Section \ref{resu}.
-}
-
-Once the LDEM is determined at each voxel, the average squared electron density $\langle \Ne^2 \rangle$ and the electron mean temperature $\Tm$ in the voxel can be computed by taking its zeroth and first moments over temperature.
+
+Once the LDEM is determined at each voxel, \albert{the LDEM-averaged squared electron density $\Nm^2$ and electron temperature $\Tm$} in the voxel can be computed by taking its zeroth and first moments over temperature.
 More specifically, at the $i$-th voxel,
@@
 
-being the average relative difference between the tomographic and the synthetic FBEs.
+\noindent 
+\albert{being the} average relative difference between the tomographic and the synthetic FBEs.
 The final product of DEMT is in the form of 3D maps of the electron density and mean temperature.
@@
 
-{For analysis purposes, the geometry of all traced magnetic field lines is classified.
-They are first classified as open or closed according to their full geometry.
-Each closed magnetic field line is further classified as ``small" or ``large", according to its coronal length $L$ being smaller or larger than the median value ${\rm Md}(L)$ of the whole population, respectively.
-This median value is \diego{${\rm Md}(L)=0.50$} and $0.46\,\mrsun$ for CR-2082 and CR-2208, respectively.
-Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e.
-their location at $r=1\,\mrsun$) to its apex (i.e., the location of maximum height).} \notebyalbert{Diego, aquí ordené y corregí mucho y creo que es un buen ejemplo de corrección de estilo de redacción, si querés comparar con como estaba antes.
-Nota: MHD no tiene source surface!
-Ahora bien, además informo ${\rm Md}(L)$.
-Para ello multipliqué por dos el valor mediano de las longitudes de las piernas (que recuerdo de memoria, por ahí la pifié).
-Vale la pena que le muestres estos histogramas a Fede y la pieza de código de donde sale, para confirmar la metodología y de paso los números.
-Es importante.}
-
-At this stage, all DEMT and AWSoM products, electron density and {temperature} in particular, can be traced along open and closed magnetic field lines.
+{For analysis purposes, \albert{the traced magnetic field lines are classified as open or closed according to their full geometry.
+Each closed field} line is further classified as ``small" or ``large", according to its coronal length $L$ being \albert{respectively smaller or larger than the median value of the whole population, which is ${\rm Md}(L)\approx 0.5\,\mrsun$ for both rotations.} Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e.
+their location at $r=1\,\mrsun$) to its apex (i.e., the location of maximum height).}
+
+At this \albert{stage, DEMT and AWSoM products} can be traced along open and closed magnetic field lines.
 Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one).
@@
 
-\notebyalbert{Este párrafo debe ser movido al menos aquí (estaba más abajo), pues el siguiente párrafo ya utiliza el concepto up/down.
-Además está corregido.} {Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies.
+{Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies.
 As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
@@
 
-\notebyalbert{Reordené y corregí mucho el siguiente párrafo.
-Lo que see lee es correcto en cada detalle y palabra?
-Está bien explicado todo lo que concierne a chi-suqared?
-La jerga estadística es precisa y correcta (no confundir confidence level con confidence interval, está bien?}
+\noindent\notebyalbert{El párrafo que sigue describe un algoritmo para identificar y seleccionar piernas up/down.
+Es correcta la jerga de "confidence level'' y el como se describe chi-squared test?
+Están bien mencionadas ambas cosas?
+Por ejemplo: confidence-level y conficence-interval, son dos cosas diferentes.
+Otro tema es: si entiendo bien el chi-squared utiliza los errores, correcto?
+Noten que modifiqué a errores porcentuales (mucho más claro) tal como se describen en las conclusiones (los corregí un poco, aquí y allá), que los saqué de la Tabla 7, y re-escribí toda la frase (ver nuevo texto naranja), es correcta?.
+Ahora bien, son errores muy pequeños para cada celda, es poner demasiada fé en la tomografía :) Estos son los errores del valor mediano de $\Tm$.
+Podemos discutirlo, pero creo que los errores por punto (es decir, la $\Tm$ de cada voxel) deben adjudicarse valores mayores.
+Quizá esto de paso hace que el chi-squared ralee menos?}
+
 {To determine if a traced filed line leg is of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points.
 We then select field lines for which the temperature increases or decreases significantly with height by requiring $|\rhoTr| > 0.5$.
-\diego{hablemos sobre esta frase} We then measure the quality of the linear fit to the temperature-height data by means of a chi-squared test \citep{recipes}, and select legs for which the fit has a 90\% confidence level.
+We then measure the quality of the linear fit to the temperature-height data by means of a chi-squared test \citep{recipes}, and select legs for which the fit has a 90\% confidence level.
 In this way, legs for which the DEMT temperature does not show a significant variation with height, or the linear fit to temperature is good enough, are not considered in this analysis.
@@
 The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg.
-Both fits consider tomographic systematic uncertainty of the electron temeprature and density, respectively estimated to be $\Delta(\Tm) \approx 0.07\,\MK$ and $\Delta(N_e)\approx 4.0\times 10^6\,\cm^{-3}$ by \citet{lloveras_2017}.
-\notebyalbert{No comprendo bien si esta última linea está bien ubicada aquí, de todas formas lo corregí un poco.
-Precisaría que discutamos los tres estos tres párrafos en naranja el lunes.} In summary, to be selected a leg must meet all three following conditions:}
+\albert{The chi-squared test to evaluate the quality of the fits considers the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\Delta\Tm\approx 6\%$ and $\Delta\sqravgN\approx 3\%$.} In summary, to be selected a leg must meet all three following conditions:}
 
@@
 \item 
-{The condifence level of both the exponential and linear fits must be larger than 90\%.} \notebyalbert{Aquí corregí, está bien expresado?}\diego{si!}
+{The condifence level of both the exponential and linear fits must be larger than 90\%.}
 \end{enumerate}
@@
 {To characterize the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model.
-Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types in this work:} \notebyalbert{Simplifiqué mucho esto.}
+Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types in this work:}
 
@@
 In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed.
-{As shown below, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}
+{As shown \albert{in Section \ref{demt_res}} below, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}
 
@@
 Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the 48000 legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III.
-On the other hand, of the 57000 legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III.
-\notebyalbert{Luego de des-ralear, las piernas seleccionadas en Figura 4 eran del orden de 100 mil, para  ambas rotaciones.
-Algo no está consistente aquí.}\diego{Statloop 6 alturas noda algo asi como 150k piernas, algunas no se trazan (entre 30 y 40k) lo cual nos deja aprox 110k.
-SUpongo que te quedaste con ese numero.
-Pero elimino los cuasi isotermicos, perdemos 30k en el streamer y 10k en CH.
-Luego hacemos una seleccion qie involucra footpoints y ahi perdemos lo que falta!
-Es decir, el numero del draft ya es des-raleado.}
+Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the \albert{$\approx 48000$} legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III.
+On the other hand, of the \albert{$\approx 57000$} legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III.
 
@@
 As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region.
-These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\lesssim 5\%$ and $\approx 2\%$ for the electron temperature and density, respectively.
-\notebyalbert{son estos errores compatibles con los informados en la Sección 2?}
+These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} \albert{estimated to be $\Delta\Tm\approx 6\%$ and $\Delta\sqravgN\approx 3\%$}.
 

### 2020-01-14 lloveras_2020.tex
mergeando a lloveras_2020

@@
 We should mention the instruments and missions we use as data for DEMT, and define their accronyms too.
-Also, a couple of paragraphs on the AWSoM model and the SWMF, including references and defining the accronyms in the process.}
+Also one paragraph on the SWMF/AWSoM model, including references and defining the accronyms on the way.}
+
+{Based on time-series of EUV images, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the solar corona.
+The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}.
+In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid.
+The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions.
+The cadence of the data time-series is set to 6\,hr.
+The main product of the technique is the local DEM (LDEM) at each volxel, a measure of the temperature distribution of the plasma contained in it.
+A recent review by \citet{vasquez_2016} summarizes the DEMT works up until then.
+More recently \citet{lloveras_2017} applied DEMT to study the last two solar minima, and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona.}
 
@@
 Points to cover are:
-\begin{itemize}
-  \item Selected targets, instruments used. One paragraph.
-  \item Characteristics of the data (specific time series, dates, bands, etc.), SolarSoft software version used for their processing. One paragraph.
-  \item Technical aspects of DEMT (grid, regularization, off-limb data is only used) and how these differ from previous versions (rereferences). One paragraph.
-  \item What is FBE, what is LDEM, what is R.
+%\begin{itemize}
+%  \item Selected targets, instruments used. One paragraph.
+%  \item Characteristics of the data (specific time series, dates, bands, etc.), SolarSoft software version used for their processing. One paragraph.
+%  \item Technical aspects of DEMT (grid, regularization, off-limb data is only used) and how these differ from previous versions (rereferences). One paragraph.
+%  \item What is FBE, what is LDEM, what is R.
 Why we care about these three quantities and what is their physical meaning should be clear.
 Then the final products $\Nm$ and $\Tm$, and what is their physical meaning.
-\end{itemize}
-}
-
-To perform the comparison two specific rotations were selected, CR-2082 (2009, 05 April through 03 May), a deep minimum period between solar cycles (SCs) 23 and 24 characterized by virtually no ARs, and CR-2208 (2018, 02 September through 29 September), a rotation during the early declining fase of SC 24.
-
-To determine the thermodynamical structure of both rotations, the DEMT technique was applied to respective time series of EUV images covering each first half rotation.
-To study CR-2082 and CR-2208 data taken by the EUVI-B/STEREO and AIA/SDO instruments was used, respectively.
-
-In DEMT, the low corona in the height range $1.0$ to $1.25\,\mrsun$ is discretized in a spherical computational grid.
-The size of the tomographic cell (or voxel) is set to 0.01 \rsun \ in the radial direction, while is set 2\deg\ in both the latitudinal and longitudinal directions.
-We carried out a reconstruction using half of a solar rotation blocking the lines-of-sight comming from the disk (i.e.
-only using off-limb data).
-
-Using the high cadence of data available, one image every 10 minutes were used.
-The selected images were averaged in 6-hour intervals which, given the angular resolution, is the cadence needed to fully constrain the inversion problem, for a total of about 55 images to cover a half solar rotation.
-For both rotations, the first 14 days of data were used.
-
-EUV images are affected by instrumental stray light contamination, which can be corrected by deconvolution of the point spread function (PSF).
-While in the case of AIA images there is no reliable determination of its PSF, it has been well determined for EUVI-B by \citet{shearer_2012}.
-For this article, all EUVI images were stray-light corrected.
-For the details of impact in $\Nm$ and $\Tm$, refer to \citet{lloveras_ba2017}.
-
-\diego{
-Unlike in previous works, a 3D regularization scheme was applied, thus spurious artifacts (nduced by the previous longitude latitude regularization schemei) were minimized in the first two heights of the tomographic grid.}
-
-We refer the reader to \citet{frazin_2009} for a detailed description of the technique, and to \citet{vasquez_2016} for a recent review on all published work based on it.
-Here we summarize the key points.
-The technique involves two consecutive procedures.
+%\end{itemize}
+%}
+
+{We carried out the 3D DEMT reconstruction and MHD modeling of two target Carrington rotations (CR).
+We selected CR-2082 (2009, 05 April through 03 May), a deep minimum rotation between solar cycles (SC) 23 and 24, and CR-2208 (2018, 02 September through 29 September), a rotation during the early declining fase of SC 24.
+To study CR-2082 and CR-2208 data taken by the STEREO/EUVI-B and SDO/AIA instruments was used, respectively.
+The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package.
+For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.}
+
+{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we opted to only use off-limb data.
+In this way, the smallest scale and brighter coronal features seen on disk (most typically in the 171\AA\ band) are not included.
+This has two implications.
+Fistly, the fast dynamics that typically characterizes those structures is abscent from the data.
+Sencondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume.
+As a result, coronal dynamics induced artifacts are reduced compared to previous DEMT reconstructions.}
+.
+{The solution of the tomographic problem involves a very large sparse matrix.
+Such type of inversion problems are characterized by spurious high-frequency artifacts in the solution, which can be mitigated through \emph{regularization} techniques \citep{frazin_2000}.
+In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude.
+Also new to the present work, is the implementation of an expanded 3D regularization scheme, which adds to the previous scheme a finite difference matrix operator to approximate radial derivatives.
+In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions.
+As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.}
+
+{We summarize next the main aspects of DEMT required for the analysis of this work. We refer the reader to \citet{frazin_2009} for a full description of the technique.}
 
 In a first step, the time series of EUV images is used to solve a solar rotational tomography (SRT) problem, for each EUV band independently.
-As a result, the 3D distribution of the so called {filter band emissivity} (FBE) is determined for each band separately.
+As a result, the 3D distribution of the so called \emph{filter band emissivity} (FBE) is determined for each band separately.
 The FBE, {an emissivity-type quantity}, is defined as the wavelength integral of the coronal EUV spectral emissivity and the telescope's passband function of each EUV channel.
 Line-of-sight (LOS) integration of the FBE provides synthetic images that can be quantitatively compared to the real data in the time series.
-To find the FBE, the tomographic problem is posed a global optimization problem in which the quadratic norm of the difference between all pairs of synthetic and real images is minimized.
-Spatial regularization terms are also included in the objective function as to minimize high frequency spurious artifacts that are due to the specific characteristics of the SRT sparse projection matrix \citep{frazin_2009,frazin_2000}.
-{Due to optical depth issues that may affect LOSs} passing very close to the limb, and to the decay of intensity with radii, the 3D maps produced by DEMT analysis typically cover the height range 1.02 to 1.23 \rsun \ \citep{frazin_2009}.
-
-\diego{COMO INTRODUZCO EL NIVEL DE REGULARIZACION? For each instrument, the DEMT analysis involves a cross-validation study to determine the optimal level of regularization.}
-
-{In a second step, the FBE values obtained for all bands in each voxel are used to constrain the determination of a {local differential emission measure} (LDEM) distribution, which describes the temperature distribution of the electron plasma contained in each individual tomographic grid voxel.
-Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}
+To find the FBE, the tomographic problem is posed a global optimization problem in which the quadratic norm of the difference between all {pairs of synthetic and real images is minimized.}
+
+{In a second step, the FBE values obtained for all bands in each voxel {of the tomographic grid are used to constrain the determination of the LDEM which, as described in Section \ref{intro}, describes the temperature distribution of the plasma within the individual voxel.} Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}
 
@@
 
-{
+\noindent
+{where $K$ is the number EUV bands, and $\TRF^{(k)}$ is the \emph{temperature response function} of the $j$-th detector.
+The TRFs are here computed based on the (known) channel’s passband times the coronal emissivity at that temperature (normalized by the squared electron density).
+The emissivity model used here is provided by the latest version of the CHIANTI atomic database and plasma emission model \citep{delzanna_2015,landi_2013}.}
+
 Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}.
-These non-reconstructed voxels are indicated as black voxels in the Carrington maps of the reconstructed DEMT reults in Section \ref{resu}.
-}
-
-Once the LDEM is determined at each voxel, the average squared electron density $\langle \Ne^2 \rangle$ and the electron mean temperature $\Tm$ in the voxel can be computed by taking its zeroth and first moments over temperature.
+These non-reconstructed voxels are indicated {in black color in the latitude-longitude (Carrington) maps of DEMT} reults in Section \ref{resu}.
+
+Once the LDEM is determined at each voxel, {the LDEM-averaged squared electron density $\Nm^2$ and electron temperature $\Tm$} in the voxel can be computed by taking its zeroth and first moments over temperature.
 More specifically, at the $i$-th voxel,
-
 {
@@
 
-being the average relative difference between the tomographic and the synthetic FBEs.
-The final product of DEMT is in the form of 3D maps of the electron density and mean temperature.
-These relationships {were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
-%\temp{Aclarar que consideramos Ne como $\sqrt{<\Ne ^2>}$.} {ALBERT: Yo creo que es mejor hablar de $\sqravgN$}
-
-%\temp{DEMT has been improved since the previously published work.
-We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.} \notebyalbert{NOTA de Albert: Explicá que hacés sin justificarte.
-Luego aclará como se hizo eso en trabajos previos, y cual es el impacto esperado.
-Puedo proveer un párrafo de ejemplo, pero creo que será mejor que vos escribas como te salga y yo luego edito.
-Algo muy importante para todo el paper: proponete escribir ``párrafos modulares".
-Es decir que, con las razonables limitaciones, puedan moverse de lugar, de orden, y sigan funcionando.
-No definiría hollow-tomography, es un término coloquial interno nuestro.
-Lo correcto es que al hablar de datos mucho más arribas expliques que los datos del disco no se utilizan, pero no le des un nombre a la tomografía.}
+\noindent 
+{being the} average relative difference between the tomographic and the synthetic FBEs.
+{The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.}\\
 
@@
 
-\noindent\notebyalbert{This section will summarize the AWSoM model. After a first version is written we will surely require some input from the Michigan friends. Points to cover:
+\noindent\notebyalbert{This section will summarize the AWSoM model. Chip, Nishtha, do you think you could provide 2 or 3 paragraphs? We believe the points to cover are:
 \begin{itemize}
@@
   \item Explain the artificially extended TR. One paragraph.
-  \item What are the products of the model we care about in this paper. One paragraph.
+  \item What are the products of the model we care about in this paper ($N_e$, $T_e$, $B$, $V$, as of now). One paragraph.
 \end{itemize}
@@
 
-{For analysis purposes, the geometry of all traced magnetic field lines is classified.
-They are first classified as open or closed according to their full geometry.
-Each closed magnetic field line is further classified as ``small" or ``large", according to its coronal length $L$ being smaller or larger than the median value ${\rm Md}(L)$ of the whole population, respectively.
-This median value is \diego{${\rm Md}(L)=0.50$} and $0.46\,\mrsun$ for CR-2082 and CR-2208, respectively.
-Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e.
-their location at $r=1\,\mrsun$) to its apex (i.e., the location of maximum height).} \notebyalbert{Diego, aquí ordené y corregí mucho y creo que es un buen ejemplo de corrección de estilo de redacción, si querés comparar con como estaba antes.
-Nota: MHD no tiene source surface!
-Ahora bien, además informo ${\rm Md}(L)$.
-Para ello multipliqué por dos el valor mediano de las longitudes de las piernas (que recuerdo de memoria, por ahí la pifié).
-Vale la pena que le muestres estos histogramas a Fede y la pieza de código de donde sale, para confirmar la metodología y de paso los números.
-Es importante.}
-
-At this stage, all DEMT and AWSoM products, electron density and {temperature} in particular, can be traced along open and closed magnetic field lines.
+{For analysis purposes, {the traced magnetic field lines are classified as open or closed according to their full geometry.
+Each closed field} line is further classified as ``small" or ``large", according to its coronal length $L$ being {respectively smaller or larger than the median value of the whole population, which is ${\rm Md}(L)\approx 0.5\,\mrsun$ for both rotations.} Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e.
+their location at $r=1\,\mrsun$) to its apex (i.e., the location of maximum height).}
+
+At this {stage, DEMT and AWSoM products} can be traced along open and closed magnetic field lines.
 Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one).
@@
 
-\notebyalbert{Este párrafo debe ser movido al menos aquí (estaba más abajo), pues el siguiente párrafo ya utiliza el concepto up/down.
-Además está corregido.} {Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies.
+{Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies.
 As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
 Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}.
-In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}
-
-\notebyalbert{Reordené y corregí mucho el siguiente párrafo.
-Lo que see lee es correcto en cada detalle y palabra?
-Está bien explicado todo lo que concierne a chi-suqared?
-La jerga estadística es precisa y correcta (no confundir confidence level con confidence interval, está bien?}
-{To determine if a traced filed line leg is of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points.
-We then select field lines for which the temperature increases or decreases significantly with height by requiring $|\rhoTr| > 0.5$.
-\diego{hablemos sobre esta frase} We then measure the quality of the linear fit to the temperature-height data by means of a chi-squared test \citep{recipes}, and select legs for which the fit has a 90\% confidence level.
-In this way, legs for which the DEMT temperature does not show a significant variation with height, or the linear fit to temperature is good enough, are not considered in this analysis.
-Finally, selected legs are then classified as up or down according to if $\rhoTr > +0.5$ or $\rhoTr < -0.5$, respectively.
+In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and {considering time-averaged heating rates.}}
+\noindent
+\notebyalbert{Modifiqué la descripción del test estadístico en el próximo párrafo .
+Estuve leyendo un poco y hay que asegurarse que esto quede escrito bien.
+Yo busqué la frase más vaga que me parece tiene un sentido científico claro.
+Aquí hay una versión de divulgación:\\
+{\tt www.statisticshowto.datasciencecentral.com/confidence-level/}\\
+pero tener cuidado con esto: busquen ``Statistical Significance" en la Wikipedia, y lea la breve sección ``Redefining significance" al final del artículo.}
+
+{To determine if the leg of a traced field line is} of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points.
+We then select field lines for which the temperature {is significantly correlated with height} by requiring $|\rhoTr| > 0.5$.
+{To test the goodness of the fit to the temperature-height data we perform a chi-squared test \citep{recipes} considering the uncertainty of the DEMT data points, selecting legs for which the fit matches the data with a 90\% confidence level.} In this way, legs for which the DEMT temperature does not show a significant {correlation} with height, or the linear fit to temperature is {not} good enough, are {excluded from the} analysis.
+{The test is also applied to the density-height data points, to ensure the trend is reasonably represented by the exponential fit.} Finally, selected legs are then classified as up or down according to if $\dr\Tm > 0$ or $\dr\Tm < 0$, respectively.
 The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg.
-Both fits consider tomographic systematic uncertainty of the electron temeprature and density, respectively estimated to be $\Delta(\Tm) \approx 0.07\,\MK$ and $\Delta(N_e)\approx 4.0\times 10^6\,\cm^{-3}$ by \citet{lloveras_2017}.
-\notebyalbert{No comprendo bien si esta última linea está bien ubicada aquí, de todas formas lo corregí un poco.
-Precisaría que discutamos los tres estos tres párrafos en naranja el lunes.} In summary, to be selected a leg must meet all three following conditions:}
+{The chi-squared test to evaluate the quality of the fits considers the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$.} In summary, to be selected a leg must meet all three following conditions:
 
@@
 \item 
-{The condifence level of both the exponential and linear fits must be larger than 90\%.} \notebyalbert{Aquí corregí, está bien expresado?}\diego{si!}
+{The condifence level of both the exponential and linear fits must be larger than 90\%.} 
 \end{enumerate}
@@
 In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed.
-{As shown below, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}
+{As shown in Section \ref{demt_res}, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}
 
@@
 
-{As described in Section \ref{demt}, we carried out DEMT reconstructions of the coronal structure for target rotations CR-2082 and CR-2208 using STEREO/EUVI and SDO/AIA data, respectively.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared $\sqravgN$ and the electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}{, and the measure $R$ was calculated by means of Equation (\ref{R}).}}
+{As described in Section \ref{demt}, we carried out DEMT reconstructions of the coronal structure for target rotations CR-2082 and CR-2208 using STEREO/EUVI and SDO/AIA data, respectively.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared ($\sqravgN$) and the electron mean temperature ($\Tm$) were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}{, and the measure $R$ was calculated by means of Equation \ref{R}.}}
 
 {As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations.
-Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic results ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
+Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic \diego{grid} ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
 Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}).
@@
 characterized by a high azymuthal symmetry.
-Rotation CR-2082} showed two {small} ARs (active {regions), both near latitude} $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg${, respectively}.
+Rotation CR-2082} showed two {small} active regions (ARs), both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg${, respectively}.
 {Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$, respectively.}
 
-{The magnetically open and closed regions of the AWSoM model are associated to CHs and the equatorial streamer belt, respectively.
-Consistently with that, the {location of the} open/closed boundaries derived from the respective AWSoM model quite accurately match {the regions of the DEMT maps which exhibit the strongest latitudinal gradient of both the electron density and temperature.}}
+{The magnetically open and closed regions of the AWSoM model are associated to Coronal holes (CHs) and the equatorial streamer belt, respectively.
+Consistently with that, the {location of the} open/closed boundaries derived from the respective AWSoM model quite accurately matchs {the regions of the DEMT maps which exhibit the strongest latitudinal gradient of both the electron density and temperature.}}
 
@@
 {To characterize the DEMT results in different magnetic structures, we traced} $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.
-For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected.
-For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.
+For both rotations, all legss that meet the criteria listed in Section \ref{trace} were selected.
+For each leg, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.
 {As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}
@@
 Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the 48000 legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III.
-On the other hand, of the 57000 legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III.
-\notebyalbert{Luego de des-ralear, las piernas seleccionadas en Figura 4 eran del orden de 100 mil, para  ambas rotaciones.
-Algo no está consistente aquí.}\diego{Statloop 6 alturas noda algo asi como 150k piernas, algunas no se trazan (entre 30 y 40k) lo cual nos deja aprox 110k.
-SUpongo que te quedaste con ese numero.
-Pero elimino los cuasi isotermicos, perdemos 30k en el streamer y 10k en CH.
-Luego hacemos una seleccion qie involucra footpoints y ahi perdemos lo que falta!
-Es decir, el numero del draft ya es des-raleado.}
+Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the {$\approx 48000$} legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III.
+On the other hand, of the {$\approx 57000$} legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III.
 
@@
 Here, we verify the existence of this type of structure for the two target rotations.
-The relatively smaller population of down loops seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}.
+The relatively smaller population of down legs seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}.
 Type I (small up) mainly populate the mid-latitudes, while type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt.
-Finally, type III (open) legs populate of course the CHs.}
+Finally, type III (open) legs populate the CHs.}
 
@@
 
-Figure \ref{gradt_demt} shows frequency histograms (normalized to the total amount of selected field lines ) of the temperature radial gradient ($\dr\Tm$) for legs of type 0, I, II and III.
+Figure \ref{gradt_demt} shows frequency histograms \diego{$\dr\Tm$} for legs of type 0, I, II and III.
 The lack of population around values close to zero is due to the requirement $|\rhoTr| > 0.5$ which discards quasi-isothermal legs.
@@
 
-{For both rotations, Figure \ref{histos_fulldemt} shows, in a statistical fashion, the DEMT results traced along field lines discriminated by field line type}.
-From top to bottom {results are shown for} type 0 to type III {field lines}{, respectively}.
+{For both rotations, Figure \ref{histos_fulldemt} shows, in a statistical fashion, the DEMT results traced along field lines discriminated by leg type}.
+From top to bottom {results are shown for} type 0 to type III {legs}{, respectively}.
 From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$ {(the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.
@@
 \end{tabular}
-\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
+\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of legs defined in Section \ref{trace}.
 For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
@@
 {Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer regions of the equatorial streamer belt, progressively exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature.
-In both rotations also, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.}
+In both rotations also, type III legs in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I legs in the core of the equatorial streamer.}
 
@@
 In these longitude-averaged profiles, longitudes containing ARs or low latitude CHs were excluded.
-In each panel the averaged latitudinal variation for the DEMT model is shown in solid-linestyle, while the result for the AWSoM model is shown in dashed-linesyle.
+In each panel the averaged latitudinal variation for the DEMT model is shown in solid-line style, while the result for the AWSoM model is shown in dashed-linesyle.
 Left panels show the comparison for CR-2082 (in blue) and right panels for CR-2208 (in red).
@@
 The left (right) panels correspond to CR-2082 (CR2208).
-The vertical black line indicates the longitude-averaged latitudes of the open/close magnetic boundary in both hemispheres.}
+The vertical black line indicates the longitude-averaged latitudes of the open/closed magnetic boundary in both hemispheres.}
 \label{perf_lat}
@@
 Secondly, for both target rotations, and for both models, these plots clearly show the relatively lower temperatures characterising the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
-Thirdly, for both target rotations, the latitude of the open/close magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density.
+Thirdly, for both target rotations, the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density.
 Note this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
-Last, note that the DEMT electron density decreases from the open/close boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend.}
+Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend.}
 
@@
 \includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
-\caption{{Statistical distribution {of the results of the DEMT (solid line-style) and AWSoM (dashed-linestyle) models} traced along legs of type I, II and III (from top to bottom), as defined in {Section \ref{trace}.} From left to right: electron density at the lowest coronal height of the AWSoM model $\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
+\caption{{Statistical distribution {of the results of the DEMT (solid line-style) and AWSoM (dashed-line style) models} traced along legs of type I, II and III (from top to bottom), as defined in {Section \ref{trace}.} From left to right: electron density at the lowest coronal height of the AWSoM model $\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
 In each panel the median {values $m$ are} indicated.}}
@@
 \end{tabular}
-\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
+\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of leg defined in Section \ref{trace}.
 DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
@@
 {Finally, to provide a graphical comparison of both models across the full range of heliocentric heights covered by the DEMT results, Figure \ref{perfiles_promedio} shows the average fits of $\Ne(r)$ and $T_e(r)$ for legs of type I (red), II (magenta), and III (cyan) for both target rotations.
-In each panel the DEMT and AWSoM results are plotted in solid and dashed linestyles, respectively.}
+In each panel the DEMT and AWSoM results are plotted in solid and dashed line styles, respectively.}
 

### 2020-01-15 lloveras_2020_Albert_Section4_and_Abstract.tex
..

--- 2020-01-14 lloveras_2020_Albert_Section4.tex
@@
 %\usepackage{epsfig}                     % For eps figures, old commands
-\usepackage{graphicx}                    % For eps figures, newer & more powerfull
+\usepackage{graphicx}                    % For eps figuresascs, newer & more powerfull
 %\usepackage{courier}                    % Change the \texttt command to courier style
@@
 \begin{abstract}
-Observational {techniques} play an essential role in advancing our understanding of the physics of the solar corona.
-They provide validation data {for} three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, {key to improve} their space weather forecasting capabilities.
+Observational techniques play an essential role in advancing our understanding of the physics of the solar corona.
+They provide validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, key to improve their space weather forecasting capabilities.
 Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale.
-Based on EUV data of space borne instruments, SRT allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun.
-We carry out a study of the corona combining tomographic reconstructions with MHD simulations {using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF).
-Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24.
-Tomographic reconstructions and results of the model are {analysed} in distinct coronal magnetic structures.
-We study magnetically closed structures associated with the equatorial streamer belt, as well as magnetically open regions enclosing it.
-We report on the tomographic results in the different structures, their implications for the physics of the solar corona, and the {current} capability of the AWSoM model to reproduce the tomographic reconstructions in different regions.
-
+Based on EUV data of space borne instruments, \albert{differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun.
+We carry out a study of the corona combining \albert{DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF).
+Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the declining} phase of SC 24.
+The 3D tomographic and MHD models are analysed and compared in distinct coronal magnetic structures.
+\albert{We report in quantitative detail on the 3D termodinamic structure of the inner corona as revealed by the DEMT analysis.
+We show in particular the existence of diverse types of temperature structures in the low and mid latitudes of the streamer belt, and that the heating energy required to keep them stable may be accounted for by Alfvén waves.
+We show that the latest version of the AWSoM model results agree with DEMT reconstructions to within a $\approx 20\%$ accuracy or better.
+We report on aspects of the AWSoM model that could be improved to better reproduce the DEMT results, in particular concerning the source region of the fast/slow solar winds.}
 \end{abstract}
@@
 
-\noindent\notebyalbert{Here we will put in a couple of paragraphs summarizing what SRT and DEMT are, including references and defining the accronyms in the process.
-We should refer to minima in particular.
+\noindent\notebyalbert{This section is not finished.
+We will put here in a couple of paragraphs summarizing what SRT and DEMT are, including references and defining the accronyms in the process.
+We should refer to minima in particular (cite all relevant references here).
 We should mention the instruments and missions we use as data for DEMT, and define their accronyms too.
-Also, a couple of paragraphs on the AWSoM model and the SWMF, including references and defining the accronyms in the process.}
+Also one paragraph on the SWMF/AWSoM model, including references and defining the accronyms on the way.}
 
-\albert{Based on time-series of EUV images, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the solar corona.
+{Based on time-series of EUV images, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the solar corona.
 The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}.
 In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid.
-The size of the tomographic cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions.
+The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions.
 The cadence of the data time-series is set to 6\,hr.
-The main product of the technique is the local DEM (LDEM), a measure of the temperature distribution of the plasma contained in each voxel of the tomographic grid.
+The main product of the technique is the local DEM (LDEM) at each volxel, a measure of the temperature distribution of the plasma contained in it.
 A recent review by \citet{vasquez_2016} summarizes the DEMT works up until then.
@@
 
-\albert{We carried out the 3D DEMT reconstruction and MHD modeling of two target Carrington rotations (CR).
+{We carried out the 3D DEMT reconstruction and MHD modeling of two target Carrington rotations (CR).
 We selected CR-2082 (2009, 05 April through 03 May), a deep minimum rotation between solar cycles (SC) 23 and 24, and CR-2208 (2018, 02 September through 29 September), a rotation during the early declining fase of SC 24.
@@
 
-\albert{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we opted to only use off-limb data.
+{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we opted to only use off-limb data.
 In this way, the smallest scale and brighter coronal features seen on disk (most typically in the 171\AA\ band) are not included.
@@
 .
-\albert{The solution of the tomographic problem involves a very large sparse matrix.
+{The solution of the tomographic problem involves a very large sparse matrix.
 Such type of inversion problems are characterized by spurious high-frequency artifacts in the solution, which can be mitigated through \emph{regularization} techniques \citep{frazin_2000}.
@@
 
-\albert{We summarize next the main aspects of DEMT required for the analysis of this work. We refer the reader to \citet{frazin_2009} for a full description of the technique.}
+{We summarize next the main aspects of DEMT required for the analysis of this work. We refer the reader to \citet{frazin_2009} for a full description of the technique.}
 
@@
 Line-of-sight (LOS) integration of the FBE provides synthetic images that can be quantitatively compared to the real data in the time series.
-To find the FBE, the tomographic problem is posed a global optimization problem in which the quadratic norm of the difference between all \albert{pairs of synthetic and real images is minimized.}
+To find the FBE, the tomographic problem is posed a global optimization problem in which the quadratic norm of the difference between all {pairs of synthetic and real images is minimized.}
 
-{In a second step, the FBE values obtained for all bands in each voxel \albert{of the tomographic grid are used to constrain the determination of the LDEM which, as described in Section \ref{intro}, describes the temperature distribution of the plasma within the individual voxel.} Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}
+{In a second step, the FBE values obtained for all bands in each voxel {of the tomographic grid are used to constrain the determination of the LDEM which, as described in Section \ref{intro}, describes the temperature distribution of the plasma within the individual voxel.} Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}
 
@@
 \noindent
-\albert{where $K$ is the number EUV bands, and $\TRF^{(k)}$ is the \emph{temperature response function} of the $j$-th detector.
+{where $K$ is the number EUV bands, and $\TRF^{(k)}$ is the \emph{temperature response function} of the $j$-th detector.
 The TRFs are here computed based on the (known) channel’s passband times the coronal emissivity at that temperature (normalized by the squared electron density).
@@
 Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}.
-These non-reconstructed voxels are indicated as black voxels in the Carrington maps of the reconstructed DEMT reults in Section \ref{resu}.
+These non-reconstructed voxels are indicated {in black color in the latitude-longitude (Carrington) maps of DEMT} reults in Section \ref{resu}.
 
-Once the LDEM is determined at each voxel, \albert{the LDEM-averaged squared electron density $\Nm^2$ and electron temperature $\Tm$} in the voxel can be computed by taking its zeroth and first moments over temperature.
+Once the LDEM is determined at each voxel, {the LDEM-averaged squared electron density $\Nm^2$ and electron temperature $\Tm$} in the voxel can be computed by taking its zeroth and first moments over temperature.
 More specifically, at the $i$-th voxel,
@@
 \noindent 
-\albert{being the} average relative difference between the tomographic and the synthetic FBEs.
-The final product of DEMT is in the form of 3D maps of the electron density and mean temperature.
-These relationships {were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
-%\temp{Aclarar que consideramos Ne como $\sqrt{<\Ne ^2>}$.} {ALBERT: Yo creo que es mejor hablar de $\sqravgN$}
-
-%\temp{DEMT has been improved since the previously published work.
-We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.} \notebyalbert{NOTA de Albert: Explicá que hacés sin justificarte.
-Luego aclará como se hizo eso en trabajos previos, y cual es el impacto esperado.
-Puedo proveer un párrafo de ejemplo, pero creo que será mejor que vos escribas como te salga y yo luego edito.
-Algo muy importante para todo el paper: proponete escribir ``párrafos modulares".
-Es decir que, con las razonables limitaciones, puedan moverse de lugar, de orden, y sigan funcionando.
-No definiría hollow-tomography, es un término coloquial interno nuestro.
-Lo correcto es que al hablar de datos mucho más arribas expliques que los datos del disco no se utilizan, pero no le des un nombre a la tomografía.}
+{being the} average relative difference between the tomographic and the synthetic FBEs.
+{The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.}\\
 
@@
 
-{For analysis purposes, \albert{the traced magnetic field lines are classified as open or closed according to their full geometry.
-Each closed field} line is further classified as ``small" or ``large", according to its coronal length $L$ being \albert{respectively smaller or larger than the median value of the whole population, which is ${\rm Md}(L)\approx 0.5\,\mrsun$ for both rotations.} Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e.
+{For analysis purposes, {the traced magnetic field lines are classified as open or closed according to their full geometry.
+Each closed field} line is further classified as ``small" or ``large", according to its coronal length $L$ being {respectively smaller or larger than the median value of the whole population, which is ${\rm Md}(L)\approx 0.5\,\mrsun$ for both rotations.} Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e.
 their location at $r=1\,\mrsun$) to its apex (i.e., the location of maximum height).}
 
-At this \albert{stage, DEMT and AWSoM products} can be traced along open and closed magnetic field lines.
+At this {stage, DEMT and AWSoM products} can be traced along open and closed magnetic field lines.
 Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one).
@@
 Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}.
-In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}
+In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and {considering time-averaged heating rates.}
 
-\noindent\notebyalbert{El párrafo que sigue describe un algoritmo para identificar y seleccionar piernas up/down.
-Es correcta la jerga de "confidence level'' y el como se describe chi-squared test?
-Están bien mencionadas ambas cosas?
-Por ejemplo: confidence-level y conficence-interval, son dos cosas diferentes.
-Otro tema es: si entiendo bien el chi-squared utiliza los errores, correcto?
-Noten que modifiqué a errores porcentuales (mucho más claro) tal como se describen en las conclusiones (los corregí un poco, aquí y allá), que los saqué de la Tabla 7, y re-escribí toda la frase (ver nuevo texto naranja), es correcta?.
-Ahora bien, son errores muy pequeños para cada celda, es poner demasiada fé en la tomografía :) Estos son los errores del valor mediano de $\Tm$.
-Podemos discutirlo, pero creo que los errores por punto (es decir, la $\Tm$ de cada voxel) deben adjudicarse valores mayores.
-Quizá esto de paso hace que el chi-squared ralee menos?}
+\noindent
+\notebyalbert{Aseguarse que la explicación estadística en el próximo párrafo es precisa y correcta.}
 
-{To determine if a traced filed line leg is of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points.
-We then select field lines for which the temperature increases or decreases significantly with height by requiring $|\rhoTr| > 0.5$.
-We then measure the quality of the linear fit to the temperature-height data by means of a chi-squared test \citep{recipes}, and select legs for which the fit has a 90\% confidence level.
-In this way, legs for which the DEMT temperature does not show a significant variation with height, or the linear fit to temperature is good enough, are not considered in this analysis.
-Finally, selected legs are then classified as up or down according to if $\rhoTr > +0.5$ or $\rhoTr < -0.5$, respectively.
+{To determine if the leg of a traced field line is} of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points.
+We then select field lines for which the temperature {is significantly correlated with height} by requiring $|\rhoTr| > 0.5$.
+{To test the goodness of the fit to the temperature-height data we perform a chi-squared test \citep{recipes} considering the uncertainty of the DEMT data points, selecting legs for which the fit matches the data with a 90\% confidence level.} In this way, legs for which the DEMT temperature does not show a significant {correlation} with height, or the linear fit to temperature is {not} good enough, are {excluded from the} analysis.
+{The test is also applied to the density-height data points, to ensure the trend is reasonably represented by the exponential fit.} Finally, selected legs are then classified as up or down according to if $\dr\Tm > 0$ or $\dr\Tm < 0$, respectively.
 The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg.
-\albert{The chi-squared test to evaluate the quality of the fits considers the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\Delta\Tm\approx 6\%$ and $\Delta\sqravgN\approx 3\%$.} In summary, to be selected a leg must meet all three following conditions:}
+{The chi-squared test to evaluate the quality of the fits considers the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$.} In summary, to be selected a leg must meet all three following conditions:}
 
@@
 
+\albert{Legs of type down turn out to have a significant population only for closed-small loops.
+In the case of closed-large loops and open field lines, there are very few cases of type down.
+Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population in each case}.
 In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed.
-{As shown \albert{in Section \ref{demt_res}} below, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}
+{As shown {in Section \ref{demt_res}} below, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}
 
@@
 
-{Consider} a simple energy balance for each magnetic flux tube, {in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated {by a} coronal heating power($E_h$) \citep{aschwanden_2004}:
+{Consider} a simple energy balance for each magnetic flux tube, {in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated {by a} coronal heating power($E_h$) \citep{aschwanden_2004}: \notebyalbert{Algo está saliendo mal en la lista de referencias, aparecen unos signos de preguntas, vas a tener que resolverlo.
+Sugiero rebusques en ADS el bib code.}
 
@@
 Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the \albert{$\approx 48000$} legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III.
-On the other hand, of the \albert{$\approx 57000$} legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III.
+Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the {$\approx 48000$} legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III.
+On the other hand, of the {$\approx 57000$} legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III.
+\notebyalbert{Posiblemente quieras actualizar estos números.}
 
@@
 
-{The notable difference between both rotations is the characteristic {value ${\rm Md}\left(\dr\Tm\right)\approx +4.5\,\MK/\mrsun$} for legs of type III for CR-2208.
+{The single notable difference between both rotations is to be found in the histograms for legs of type III in the open region.
+For those, the characteristic value is ${\rm Md}\left(\dr\Tm\right)\approx {\bf +X.X}$ and ${\bf Y.Y}\,\MK/\mrsun$ for CR-2208 and CR-2082, respectively}.
 This is related to the much larger $R$ score for the DEMT results along CH legs for CR-2208.
 In this case, DEMT performs poorly in modeling a LDEM that predicts the tomographic FBEs with reasonable accuracy.
-Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, {reveals that in most of the CH region the result for $\Tm$ below height $1.105\,\mrsun$ is quite uniform and artificially low}.
-As it turns out, around and above height this height the score $R$ is lower and the temperature results are more reliable.
-As a result, the temperature gradient along these legs is artificially larger, with the linear fit trying to simultaneously fit the artificially low values of $\Tm$ at lower heights.
-In general, the DEMT results in the CH region based on AIA data are thus much less reliable than in the rest of the analysis.
-We will return to this point in the conclusion section.}
+Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, reveals that in most of the CH region the result for $\Tm$ below height $1.105\,\mrsun$ is {artificially uniform and low.
+Such results, mostly excluded of the analysis by the selection algorithm explained in Section \ref{trace}, imply the presence of some artificially large radial gradients of the DEMT temperature.} In general, the DEMT results in the CH region based on AIA data are thus much less reliable than in the rest of the analysis.
+We will return to this point in the conclusion section.
 
@@
 
-{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer regions of the equatorial streamer belt, progressively exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature.
+{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer regions of the equatorial streamer belt, \albert{exhibit progressively} decreasing coronal base density, increasing density scale height, and increasing electron temperature.
 In both rotations also, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.}
@@
 
-\notebyalbert{Propongo que Diego escriba una primer sección limpia, ordenada.
-Lo que vos mandarías al Solar Physics, sin asteriscos ni nada raro.
-Expresate con párrafos limpios.
-Si querés destacar algo para discutir ponelo como una nota en rojo al final del párrafo correspondiente, no en el medio de los mismos.
-Yo creo que esto debe estructurarse así:
-\begin{enumerate}
-\item Un párrafo (breve) de que se hizo, esto contextualiza. 
-\item Dos o tres párrafos sobre los resultados 3.1.
-Esto es: resultados per se de cada rotación y como comparan (mencionando el tema incertezas).
-Estructura 3D del streamer en CAPAS, revelada observacionalmente en forma global por DEMT, esto incluye UP/DOWN loops.
-Explicar que con AIA no andamos bien en CHs.
-O sí?
-Energía.
-\item Uno o dos párrafos sobre los resultados 3.2. Como compara AWSoM con DEMT. En forma breve. Vale la pena explicar que DOWN loops no se puede.
-\item Luego un párrafo sobre next steps. Esto puede incluir nuevas cosas con AIA-4, el Eclipse, otras rotaciones de mayor intensidad.
-\end{enumerate}
-}
+\albert{We carried out the 3D DEMT reconstruction and MHD modeling of the inner solar corona for two target rotations, CR-2082 and CR-2208.
+The first target belongs to the deep minimum epoch between SCs 23 and 24, while the latter belongs to the end of the declinig phase of SC 24.
+The present work introduces two improvements in the implementation of DEMT, namely the use of only off-limb data in the EUV images, and the inclusion of a 3D regularization scheme.
+As a result of the former, artifacts introduced by coronal dynamics are mitigated, and as a result of the latter, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.
+The MHD model used is here the latest version of the AWSoM component of the SWMF suite.}
 
-\notebyalbert{Este párrafo que sigue es de Albert.
-Algo así debe ir incluído dentro de la parte que refiere a 3.1.
-Creo que hay que corregir números a la luz de los análisis finales.
-Creo que los números de cuanto más frío o caliente, etc, deben ser corregidos a la luz de la nueva Tabla 1.}
+\albert{Based on the magnetic field model of AWSoM model and the results of the DEMT model for electron density and temeprature, we classified coronal structures in four different types.
+Smaller loops in the core of the streamer belt are classified in down/up types according to their temperature decreasing/increasing with height (dubbed type 0/I loops).
+Larger closed loops of type up that form the envelope of the streamer belt (dubbed type II loops), and open field lines of type up popuating the CHs (dubbed type III loops).}
 
-In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI.
-In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
-They found that while the density product is essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e.
+\albert{Concerning the DEMT reconstructions, throughout the magnetically closed region of both rotations, we find that type 0, I and II legs are associated to increasingly outer regions of the equatorial streamer belt, and exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
+For both target rotations we find that down loops populate the low latitudes of the streamer belt, while up loops dominate its mid-latitudes.
+Also, in the case of CR-2082 the fraction of down loops is significabtly larger than for CR-2208.
+These findings are consistent with previous studies by \citet{huang_2012} and \citet{nuevo_2013}.
+In the case of the latter, they include in their analysis target CR-2081, which is a rotation almost identical to our target CR-2082.
+Our results for target CR-2082 compare very well with those of \citet{nuevo_2015} for target CR-2081.
+As our study uses the improved version of the DEMT techinque, such comparison provided a consistency check for the changes implemented in the DEMT techique.}
+
+\albert{In both rotations also, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.
+In the case of the AIA based DEMT reconstruction, we show that in a substantial fraction of the CHs region the technique performs poorly in modeling LDEMs that predict the tomographic emissivitiy in each EUV band with reasonable accuracy.
+As a result, DEMT results based on AIA data are currently less reliable in the CH region.
+This was already found by the existing two previous DEMT works based on AIA data \citep{nuevo_2015,maccormack_2017}.
+The source of this distinct performance of DEMT when applied to EUVI or AIA data is related to the TRFs of the respective filter sets.
+We are currenlty implementing an improved LDEM determination alogrithm to to deal with this issue that will be used in a follow up article.}
+
+In comparing the DEMT results obtained for the two selected targets, \albert{we highlight here that} they rely on data provided by two different instruments, \albert{namely EUVI and AIA for CR-2082 and CR-2208, respectively.} In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
+They found that while the density \albert{products are} essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e.
 $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$.
-Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was $\approx 10-15\%$ hotter than CR-2082 throughout the streamer belt region.
+Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was \albert{characterized by temperatures $\approx 10-15\%$ larger relative to CR-2082} throughout the streamer belt region.
 As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region.
-These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} \albert{estimated to be $\Delta\Tm\approx 6\%$ and $\Delta\sqravgN\approx 3\%$}.
+These systematic differences are \albert{around or beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} {estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$}.}
 
-\notebyalbert{El texto hasta el final son de Diego. Algunos se pueden ir, otros pueden servir de semilla para construir las distintas partes de la Sección.}
+\albert{In the streamer belt region we combined the DEMT results and the AWSoM magnetic model to infer the energy input flux $\phi_h$ at the coronal base required to mantain stable coronal loops.
+To this end, we applied the technique developed by \citet{maccormack_2017}.
+We found characteristic values in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}.
+Based on spectroscopic data of the EIS instrument in quiet-Sun regions \citet{hahn_2014} showed that, if the observed non-thermal broadenings are assigned to Alfvén waves, their energy flux at the coronal base is estimated to be in the range $\approx 1.5-2.5\times 10^5\,\erg\,\cminvs\,\s^{-1}$.
+A large fraction of the coronal base energy input flux $\phi_h$ estimated in this work, or even its totality, could then be accounted for by Alfvén waves.}
 
-*We found down legs in the DEMT reconstructions mainly in the equatorial latitudes, being a greater quantity and better distribution along longitudes in CR-2082 than in CR-2208.
-\citet{nuevo_2013} showed a decrease in the amount of down loops as the solar activity increases, which is consistent with the results shown in this article.
+\albert{Results of the AWSoM model are compared to those of the DEMT reconstructions in the range of coronal heights $\approx 1.05-1.20\,\mrsun$ simultaneously covered by both models.
+In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines.
+The detailed comparison shown in this work can be summarized as follows.
+For CR-2082, the electron density of both models agree within $\approx 20\%$ in all regions, while for CR-2208 the agreement is within $\approx 5\%$.
+In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations.
+This level of agreement between both models is considerably better than that reported in previous works.
+\citet{oran_2015} and \citet{jin_2012} reported electron density values of the AWsOM model typically 50\% larger than those of the DEMT reconstructions.} \notebyalbert{Chip, if Section 2.2 explains the most significant imporvements of AWSoM since the version used in those references, we can comment on the reason for the improvement here.}
 
-*We can see, on type 0 loops, a median value of energy input flux ($\phi_h$) for CR-2082 twice bigger than CR-2208.
-In both rotations this magnitude has negative values, this can refer to some loops where loop-integrated radiative flux $\phi_r$) is too small in comparison with the larger gradients of negative conductive flux $\phi_c$), resulting in negative energy input flux.
+\albert{Within the quantitative match summarized in the previous paragraph, there are some qualitative agreements and dissagreements bewteen both models worth noticing.
+For both target rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterise the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
+On the other hand, while the latitude of the open/close magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
+Also, while the DEMT electron density decreases from the open/close boundary towards the poles (in both hemispheres of the two target rotations), the AWSoM model shows the opposite trend.
+This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the ope/close boubdary towards the poles.} \notebyalbert{Chip: Even if the match AWSoM/DEMT is quantitatively pretty good, this qualitative opposite behavior is off putting.
+Do you think there is room for improvement in the AWSoM model here?
+Maybe worth mentioning?}
 
-This effect can be due a subestimation of the density present in the loop or the limited range of temperature used to reconstruct tomographic parameters, that can affect the compute of radiative power.
-Nevertheless, this population represent lower than the \diego{ALGÚN PORCENTAJE$\%$} of total population in both cases.
+\notebyalbert{Chip: In relation to the previous comment, if the anlaysis proposed in Figure 15 is carried out we should say something about that here.}
 
-Consistent that the density in CR-2082 was higher, the $\phi_r$ was also higher.
-In both rotations the magnitudes in the temperature gradients are similar, but the temperatures in CR-2208 were consistently higher at all heights, resulting in a larger $\phi_c$ in module.
-This results are in agree with the observations of \citet{maccormack_2017}.
+\albert{A detailed empirical description of the 3D termodynamic structure of the inner corona at a global scale is curently only possible with tomographic techniques, such as DEMT.
+Using tomographic results for continuous validation of 3D MHD models is of high relevance for the continued improvement of models.
+In a follow up article we will analyse whit DMET and 3D MHD modeling new target rotations of the current solar minimum between SCs 24 and 25, in particular the rotations conrresponding to the 2019 and 2020 total solar eclipses.}
 
-\diego{THE AR of CR-2082 wasn't well modeled by AWSoM.}
+\noindent
+\notebyalbert{Diego, agregá las sección de agradecimientos, fijándote como lo hicimos para tu paper anterior.
+Vos seguro debes agradecer a la beca, Ceci tambien (fijate en su paper), y todos los de aqui deberemos agraecer grants.
+Armalo como puedas y luego lo revisamos.}
 
-In both rotations, AWSoM and DEMT resutls shows same termodynamic structures along latitude and longitude with very comparable values between $1.055 - 1.25\,\mrsun$
-
-Figure \ref{histos_2082} and Table \ref{tabla_comp} indicate that AWSoM reconstruction of CR-2082 was found to be less dense $\approx 11-22\%$ and colder $\approx 5-10\%$.
-
-Both reconstructions of CR-2208 reconstructed the ARs with very similare values and in almost the same latitude-longitude location.
-Figure \ref{histos_2208} and Table \ref{tabla_comp} indicate that AWSoM reconstruction of CR-2208 was found to be denser $\approx 0-10\%$ and colder $\approx 10-15\%$.
-
-CR-2208 was $\approx 10-15\%$ hotter than CR-2082 throughout the streamer belt region.
-As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region.
-These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\lesssim 5\%$ and $\approx 2\%$ for the electron temperature and density, respectively.
-
-\diego{I would like to say something about FIgure 10. Maybe the weird tale in AWSoM Ne in the poles. Ideas?}\\
-
-%\diego{We could say something about the anti correlation between speed and density and not get into the trace because issues do always appear and we don't have much time, and we all want to be happy in january.
-Unless the collaborators find easy to make this part.}
-
-%% Figure 
-%
-% \begin{figure} 
-% \centerline{\includegraphics[width=0.5\textwidth,clip=]{<fig.eps>}}
-% \caption{}%\label{fig:?}
-% \end{figure}
-
-%% Table
-%
-% \begin{table}
-% \caption{}%\label{tbl:?}
-% \begin{tabular}{}     
-% \hline
-% \multicolumn{2}{c}{<>}
-% <data>
-% \hline
-% \end{tabular}
-% \end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Appendix
-%
-% \appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Acknowledgements
-%
-% \begin{acks}
-%
-% \end{acks}
-
-%%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Bibliography
-%
-% Using BibTeX
-%
 \bibliographystyle{spr-mp-sola}
 \bibliography{solphys_dglloveras}
-%
-% Without BibTeX 
-% \begin{thebibliography}{}
-% \bibitem[\protect\citeauthoryear{Author}{Year}]{key}
-%   <bibliographical entry>
-%
-% \bibitem[\protect\citeauthoryear{}{}]{}
-%   
-%  
-% \end{thebibliography}
 

### 2020-01-15 lloveras_2020.tex
version mergeada con conclusiones

@@
 \begin{abstract}
-Observational {techniques} play an essential role in advancing our understanding of the physics of the solar corona.
-They provide validation data {for} three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, {key to improve} their space weather forecasting capabilities.
+Observational techniques play an essential role in advancing our understanding of the physics of the solar corona.
+They provide validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, key to improve their space weather forecasting capabilities.
 Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale.
-Based on EUV data of space borne instruments, SRT allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun.
-We carry out a study of the corona combining tomographic reconstructions with MHD simulations {using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF).
-Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24.
-Tomographic reconstructions and results of the model are {analysed} in distinct coronal magnetic structures.
-We study magnetically closed structures associated with the equatorial streamer belt, as well as magnetically open regions enclosing it.
-We report on the tomographic results in the different structures, their implications for the physics of the solar corona, and the {current} capability of the AWSoM model to reproduce the tomographic reconstructions in different regions.
-
+Based on EUV data of space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun.
+We carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF).
+Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the declining} phase of SC 24.
+The 3D tomographic and MHD models are analysed and compared in distinct coronal magnetic structures.
+{We report in quantitative detail on the 3D termodinamic structure of the inner corona as revealed by the DEMT analysis.
+We show in particular the existence of diverse types of temperature structures in the low and mid latitudes of the streamer belt, and that the heating energy required to keep them stable may be accounted for by Alfvén waves.
+We show that the latest version of the AWSoM model results agree with DEMT reconstructions to within a $\approx 20\%$ accuracy or better.
+We report on aspects of the AWSoM model that could be improved to better reproduce the DEMT results, in particular concerning the source region of the fast/slow solar winds.}
 \end{abstract}
@@
 
+In the present work, data from 3 EUV bands was used.
+171, 193 and 211 \AA \ in case of AIA, and 171, 195 and 284 \AA \ bands in case of EUVI.
+When using data from 3 EUV bands, a Gaussian model for the LDEM is able to accurately predict the tomographic emissivities \citep{frazin_2009,nuevo_2015}.
+In each tomographic voxel the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that allow to best reproduce the three tomographically reconstructed values of FBE in that voxel.
+
 Once the LDEM is determined at each voxel, {the LDEM-averaged squared electron density $\Nm^2$ and electron temperature $\Tm$} in the voxel can be computed by taking its zeroth and first moments over temperature.
@@
 }
-
+{Legs of type down turn out to have a significant population only for closed-small loops.
+In the case of closed-large loops and open field lines, there are very few cases of type down.
+Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population in each case}.
+\\
 In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed.
@@
 Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the {$\approx 48000$} legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III.
-On the other hand, of the {$\approx 57000$} legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III.
+Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the {$\approx 44000$} legs selected for CR-2082, 20\% are type 0, 31\% are type I, 23\% are type II and 26\% type III.
+On the other hand, of the {$\approx 44000$} legs selected for CR-2208, 10\% are type 0, 43\% are type I, 30\% are type II and 17\% type III.
 
@@
 
-{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer regions of the equatorial streamer belt, progressively exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature.
+{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer regions of the equatorial streamer belt, exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
 In both rotations also, type III legs in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I legs in the core of the equatorial streamer.}
@@
 I think so.
-Our submission deadline is end-of-January.}
+Our submission deadline is 24 January.}
 
@@
 
-\notebyalbert{Propongo que Diego escriba una primer sección limpia, ordenada.
+%\notebyalbert{Propongo que Diego escriba una primer sección limpia, ordenada.
 Lo que vos mandarías al Solar Physics, sin asteriscos ni nada raro.
@@
 Yo creo que esto debe estructurarse así:
-\begin{enumerate}
-\item Un párrafo (breve) de que se hizo, esto contextualiza. 
-\item Dos o tres párrafos sobre los resultados 3.1.
+%\begin{enumerate}
+%\item Un párrafo (breve) de que se hizo, esto contextualiza. 
+%\item Dos o tres párrafos sobre los resultados 3.1.
 Esto es: resultados per se de cada rotación y como comparan (mencionando el tema incertezas).
@@
 Energía.
-\item Uno o dos párrafos sobre los resultados 3.2. Como compara AWSoM con DEMT. En forma breve. Vale la pena explicar que DOWN loops no se puede.
-\item Luego un párrafo sobre next steps. Esto puede incluir nuevas cosas con AIA-4, el Eclipse, otras rotaciones de mayor intensidad.
-\end{enumerate}
-}
-
-\notebyalbert{Este párrafo que sigue es de Albert.
-Algo así debe ir incluído dentro de la parte que refiere a 3.1.
-Creo que hay que corregir números a la luz de los análisis finales.
-Creo que los números de cuanto más frío o caliente, etc, deben ser corregidos a la luz de la nueva Tabla 1.}
-
-In this work the combination of DEMT reconstructions and PFSS models has been used to perform a comparative study of the 3D thermodynamical state of the low solar corona ($1.02-1.23\,\mrsun$) {for two rotations sampling} the last two solar minima.
-Specifically the study compares rotations CR-1915 and CR-2081, {respectively sampling} the SC 22/23 and SC 23/24 minima.
-The SC 22/23 minimum was shorter, more active and intermittent.
-The SC 23/24 minimum {was remarkably} characterized by a $\approx 1$ year period {showing virtually} no sunspots.
-Being CR-2081 near the end of that extremely quiet period, it was one of the most axisymmetric and quiet rotations on record from that period \citep{nuevo_2013}.
-
-In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI.
-In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
-They found that while the density product is essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e.
+%\item Uno o dos párrafos sobre los resultados 3.2. Como compara AWSoM con DEMT. En forma breve. Vale la pena explicar que DOWN loops no se puede.
+%\item Luego un párrafo sobre next steps. Esto puede incluir nuevas cosas con AIA-4, el Eclipse, otras rotaciones de mayor intensidad.
+%\end{enumerate}
+%}
+
+{We carried out the 3D DEMT reconstruction and MHD modeling of the inner solar corona for two target rotations, CR-2082 and CR-2208.
+The first target belongs to the deep minimum epoch between SCs 23 and 24, while the latter belongs to the end of the declining phase of SC 24.
+The present work introduces two improvements in the implementation of DEMT, namely the use of only off-limb data in the EUV images, and the inclusion of a 3D regularization scheme.
+As a result of the former, artifacts introduced by coronal dynamics are mitigated, and as a result of the latter, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.
+The MHD model used is here the latest version of the AWSoM component of the SWMF suite.}
+
+{Based on the magnetic field model of AWSoM model and the results of the DEMT model for electron density and temperature, we classified coronal structures in four different types.
+Smaller legs in the core of the streamer belt are classified in down/up types according to their temperature decreasing/increasing with height (dubbed type 0/I).
+Larger closed legs of type up that form the envelope of the streamer belt (dubbed type II), and open field lines of type up populating the CHs (dubbed type III).}
+
+{Concerning the DEMT reconstructions, throughout the magnetically closed region of both rotations, we find that type 0, I and II legs are associated to increasingly outer regions of the equatorial streamer belt, and exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
+For both target rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes.
+Also, in the case of CR-2082 the fraction of down legs is significantly larger than for CR-2208.
+These findings are consistent with previous studies by \citet{huang_2012} and \citet{nuevo_2013}.
+In the case of the latter, they include in their analysis target CR-2081, which is a rotation almost identical to our target CR-2082.
+Our results for target CR-2082 compare very well with those of \citet{nuevo_2015} and \citet{lloveras_2017} for target CR-2081.
+As our study uses the improved version of the DEMT technique, such comparison provided a consistency check for the changes implemented in the DEMT technique.}
+
+{In both rotations also, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.
+In the case of the AIA based DEMT reconstruction, we show that in a substantial fraction of the CHs region the technique performs poorly in modeling LDEMs that predict the tomographic emissivitiy in each EUV band with reasonable accuracy.
+As a result, DEMT results based on AIA data are currently less reliable in the CH region.
+This was already found by the existing two previous DEMT works based on AIA data \citep{nuevo_2015,maccormack_2017}.
+The source of this distinct performance of DEMT when applied to EUVI or AIA data is related to the TRFs of the respective filter sets.
+We are currently implementing an improved LDEM determination algorithm to to deal with this issue that will be used in a follow up article.}
+
+In comparing the DEMT results obtained for the two selected targets, {we highlight here that} they rely on data provided by two different instruments, {namely EUVI and AIA for CR-2082 and CR-2208, respectively.} In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
+They found that while the density {products are} essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e.
 $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$.
-Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was $\approx 10-15\%$ hotter than CR-2082 throughout the streamer belt region.
+Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was {characterized by temperatures $\approx 10-15\%$ larger relative to CR-2082} throughout the streamer belt region.
 As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region.
-These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\lesssim 5\%$ and $\approx 2\%$ for the electron temperature and density, respectively.
-\notebyalbert{son estos errores compatibles con los informados en la Sección 2?}
-
-\notebyalbert{El texto hasta el final son de Diego. Algunos se pueden ir, otros pueden servir de semilla para construir las distintas partes de la Sección.}
-
-*We found down legs in the DEMT reconstructions mainly in the equatorial latitudes, being a greater quantity and better distribution along longitudes in CR-2082 than in CR-2208.
-\citet{nuevo_2013} showed a decrease in the amount of down loops as the solar activity increases, which is consistent with the results shown in this article.
-
-*We can see, on type 0 loops, a median value of energy input flux ($\phi_h$) for CR-2082 twice bigger than CR-2208.
-In both rotations this magnitude has negative values, this can refer to some loops where loop-integrated radiative flux $\phi_r$) is too small in comparison with the larger gradients of negative conductive flux $\phi_c$), resulting in negative energy input flux.
-
-This effect can be due a subestimation of the density present in the loop or the limited range of temperature used to reconstruct tomographic parameters, that can affect the compute of radiative power.
-Nevertheless, this population represent lower than the \diego{ALGÚN PORCENTAJE$\%$} of total population in both cases.
-
-Consistent that the density in CR-2082 was higher, the $\phi_r$ was also higher.
-In both rotations the magnitudes in the temperature gradients are similar, but the temperatures in CR-2208 were consistently higher at all heights, resulting in a larger $\phi_c$ in module.
-This results are in agree with the observations of \citet{maccormack_2017}.
-
-\diego{THE AR of CR-2082 wasn't well modeled by AWSoM.}
-
-In both rotations, AWSoM and DEMT resutls shows same termodynamic structures along latitude and longitude with very comparable values between $1.055 - 1.25\,\mrsun$
-
-Figure \ref{histos_2082} and Table \ref{tabla_comp} indicate that AWSoM reconstruction of CR-2082 was found to be less dense $\approx 11-22\%$ and colder $\approx 5-10\%$.
-
-Both reconstructions of CR-2208 reconstructed the ARs with very similare values and in almost the same latitude-longitude location.
-Figure \ref{histos_2208} and Table \ref{tabla_comp} indicate that AWSoM reconstruction of CR-2208 was found to be denser $\approx 0-10\%$ and colder $\approx 10-15\%$.
-
-CR-2208 was $\approx 10-15\%$ hotter than CR-2082 throughout the streamer belt region.
-As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region.
-These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\lesssim 5\%$ and $\approx 2\%$ for the electron temperature and density, respectively.
-
-\diego{I would like to say something about FIgure 10. Maybe the weird tale in AWSoM Ne in the poles. Ideas?}\\
-
-%\diego{We could say something about the anti correlation between speed and density and not get into the trace because issues do always appear and we don't have much time, and we all want to be happy in january.
-Unless the collaborators find easy to make this part.}
+These systematic differences are {around or beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} {estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$}.}
+
+{In the streamer belt region we combined the DEMT results and the AWSoM magnetic model to infer the energy input flux $\phi_h$ at the coronal base required to maintain stable coronal loops.
+To this end, we applied the technique developed by \citet{maccormack_2017}.
+We found characteristic values in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}.
+Based on spectroscopic data of the EIS instrument in quiet-Sun regions \citet{hahn_2014} showed that, if the observed non-thermal broadening are assigned to Alfvén waves, their energy flux at the coronal base is estimated to be in the range $\approx 1.5-2.5\times 10^5\,\erg\,\cminvs\,\s^{-1}$.
+A large fraction of the coronal base energy input flux $\phi_h$ estimated in this work, or even its totality, could then be accounted for by Alfvén waves.}
+
+{Results of the AWSoM model are compared to those of the DEMT reconstructions in the range of coronal heights $\approx 1.05-1.20\,\mrsun$ simultaneously covered by both models.
+In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines.
+The detailed comparison shown in this work can be summarized as follows.
+For CR-2082, the electron density of both models agree within $\approx 20\%$ in all regions, while for CR-2208 the agreement is within $\approx 5\%$.
+In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations.
+This level of agreement between both models is considerably better than that reported in previous works.
+\citet{oran_2015} and \citet{jin_2012} reported electron density values of the AWSoM model typically 50\% larger than those of the DEMT reconstructions.} \notebyalbert{Chip, if Section 2.2 explains the most significant improvements of AWSoM since the version used in those references, we can comment on the reason for the improvement here.}
+
+{Within the quantitative match summarized in the previous paragraph, there are some qualitative agreements and disagreements between both models worth noticing.
+For both target rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
+On the other hand, while the latitude of the open/close magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
+Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), the AWSoM model shows the opposite trend.
+This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.} \notebyalbert{Chip: Even if the match AWSoM/DEMT is quantitatively pretty good, this qualitative opposite behavior is off putting.
+Do you think there is room for improvement in the AWSoM model here?
+Maybe worth mentioning?}
+
+\notebyalbert{Chip: In relation to the previous comment, if the anlaysis proposed in Figure 15 is carried out we should say something about that here.}
+
+{A detailed empirical description of the 3D termodynamic structure of the inner corona at a global scale is curently only possible with tomographic techniques, such as DEMT.
+Using tomographic results for continuous validation of 3D MHD models is of high relevance for the continued improvement of models.
+In a follow up article we will analyse whit DEMT and 3D MHD modeling new target rotations of the current solar minimum between SCs 24 and 25, in particular the rotations conrresponding to the 2019 and 2020 total solar eclipses.}
+
+\noindent
+\notebyalbert{Diego, agregá las sección de agradecimientos, fijándote como lo hicimos para tu paper anterior.
+Vos seguro debes agradecer a la beca, Ceci tambien (fijate en su paper), y todos los de aqui deberemos agraecer grants.
+Armalo como puedas y luego lo revisamos.}
 
@@
 %
-% \begin{acks}
-%
-% \end{acks}
+ \begin{acks}
+D.G.Ll. and C.M.C. acknowledges CONICET doctoral fellowship (Res. Nr. 4870) to IAFE that supported his participation in this research.
+The authors acknowledge \diego{ANPCyT grant 2012/0973 and CONICET grant PIP \# 11220120100403 estos son viejos?} to IAFE that partially supported their participation in this research
+ \end{acks}
 

### 2020-01-15 lloveras_2020.tex
Subido por ALbert

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Affilations 
-%% id shold be the same with \author addressref value.
-%\address[id={}]{}
 \address[id=aff1]{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (IAFE), CONICET-UBA, CC 67 - Suc 28,  (C1428ZAA) Ciudad Aut\'onoma de Buenos Aires, Argentina}
@@
 
-%\noindent\notebyalbert{This section will summarize DEMT's main aspects and equations, only those needed to understand the paper.
-Nothing not needed to read this paper is provided.
-Also, no derivation of equations are provided.
-References are given so that the reader can dig deeper if so desires.
-Points to cover are:
-%\begin{itemize}
-%  \item Selected targets, instruments used. One paragraph.
-%  \item Characteristics of the data (specific time series, dates, bands, etc.), SolarSoft software version used for their processing. One paragraph.
-%  \item Technical aspects of DEMT (grid, regularization, off-limb data is only used) and how these differ from previous versions (rereferences). One paragraph.
-%  \item What is FBE, what is LDEM, what is R.
-Why we care about these three quantities and what is their physical meaning should be clear.
-Then the final products $\Nm$ and $\Tm$, and what is their physical meaning.
-%\end{itemize}
-%}
-
 {We carried out the 3D DEMT reconstruction and MHD modeling of two target Carrington rotations (CR).
@@
 
-In the present work, data from 3 EUV bands was used.
-171, 193 and 211 \AA \ in case of AIA, and 171, 195 and 284 \AA \ bands in case of EUVI.
-When using data from 3 EUV bands, a Gaussian model for the LDEM is able to accurately predict the tomographic emissivities \citep{frazin_2009,nuevo_2015}.
+\albert{In this work,} data from thre EUV bands was \albert{used:} 171, 193 and 211 \AA \ in \albert{the} case of AIA, and 171, 195 and 284 \AA \ bands in \albert{the} case of EUVI.
+When using data from \albert{three bands}, a Gaussian model for the LDEM is able to accurately predict the tomographic emissivities \citep{frazin_2009,nuevo_2015}.
 In each tomographic voxel the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that allow to best reproduce the three tomographically reconstructed values of FBE in that voxel.
@@
 {being the} average relative difference between the tomographic and the synthetic FBEs.
-{The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.}\\
+{The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.}
 
@@
 \subsection{{Tracing Results Along Magnetic Fieldlines}}\label{trace}
-
-%\noindent\notebyalbert{This section will explain how the AWSoM magnetic model is used to trace the thermodynamic products of both DEMT and AWSoM along the fieldlines of AWSoM.
-This requires covering the following points:
-%\begin{itemize}
-%  \item A first paragraph qualitatively describing the process. This includes mentioning that the AWSoM products are first interpolated into the DEMT grid.
-%  \item A short paragraph describing the numerical method used to trace field lines.
-We have a nice version of this in your previous paper.
-At this point the reader should understand that for each field line we have its geometry $\mathbf{r}(s)$ as a function of the distance $s$ along the loop, with $s(1\,\mrsun)\equiv 0$.
-%  \item Explain very simply how then that for each voxel the middle point of the field line is selected and assigned the DEMT and AWSoM products of that cell.
-At this point the reader should understand that for each field line we have: $Q[r(s)]$, where $Q$ is any given quantity from either the DEMT model (specifically $\sqravgN$ and $\Tm$) or the AWSoM model (specifically $\Ne$ and $\Te$).
-%  \item Explain fits to the DEMT results  $\sqravgN(r)$, $\Tm(r)$.
-%  \item Explain then the classification of field lines.
-%\end{itemize}}
 
@@
 \end{eqnarray}
+
 \noindent
@@
 In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and {considering time-averaged heating rates.}}
-\noindent
-\notebyalbert{Modifiqué la descripción del test estadístico en el próximo párrafo .
-Estuve leyendo un poco y hay que asegurarse que esto quede escrito bien.
-Yo busqué la frase más vaga que me parece tiene un sentido científico claro.
-Aquí hay una versión de divulgación:\\
-{\tt www.statisticshowto.datasciencecentral.com/confidence-level/}\\
-pero tener cuidado con esto: busquen ``Statistical Significance" en la Wikipedia, y lea la breve sección ``Redefining significance" al final del artículo.}
 
@@
 
-{
 \begin{itemize}
@@
 \end{itemize}
-}
+
 {Legs of type down turn out to have a significant population only for closed-small loops.
@@
 \subsection{{Energy Input Flux}}\label{energia}
-
-%\noindent\notebyalbert{This section will summarize how loop integrated energy quantities are computed from the DEMT products and the AWSoM magetic model alone.
-The summary will not include any derivation and will refer to Cecilia's paper.
-Only the results that are relevant are to be explicited.
-Start by explaining the model and assumptions, and end up summarizing the loop-integrated products (radiative and conductive fluxes).
-At the end the reader should understand that their sum is the enery input flux required at the coronal base to maintain the loop stable.
-This should be a very short section, as it is a summary of a single previous paper.}
 
@@
 
-%\noindent\notebyalbert{This section will show first the DEMT products in the form of Carrington maps at three heights, for the two target rotations.
-It will then show the latitude/longitude location of the four types of  magnetic loops (defined in Section 2.3) at a sample height.
-Then, for the each type of loop, we will show histograms of the values of different DEMT products traced along them, charerizing in a quantitative fashion the DEMT results in distinct magnetic structures.
-It will also include a quantitative comparison between the two target rotations of the median values of the DEMT products in each type of loop.}
-
 {As described in Section \ref{demt}, we carried out DEMT reconstructions of the coronal structure for target rotations CR-2082 and CR-2208 using STEREO/EUVI and SDO/AIA data, respectively.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared ($\sqravgN$) and the electron mean temperature ($\Tm$) were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}{, and the measure $R$ was calculated by means of Equation \ref{R}.}}
@@
 {As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations.
-Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic \diego{grid} ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
+Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of \albert{the} tomographic grid ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
 Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}).
@@
 
-Figure \ref{gradt_demt} shows frequency histograms \diego{$\dr\Tm$} for legs of type 0, I, II and III.
+Figure \ref{gradt_demt} shows frequency histograms \albert{of $\dr\Tm$} for legs of type 0, I, II and III.
 The lack of population around values close to zero is due to the requirement $|\rhoTr| > 0.5$ which discards quasi-isothermal legs.
@@
 Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range.
-As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized by $\phi_c<0$.
-\vfill}} % NOTA el vfill
+As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized by $\phi_c<0$.}}
 
 \subsection{{Comparison of the DEMT and AWSoM Models}}\label{awsom_res}
-
-%\noindent\notebyalbert{This section will show the results of AWSoM for $N_e$ and $T_e$, and how they compare with the corresponding results of DEMT ($\sqravgN$ and $\Tm$).
-It will first show the Carrington maps of $N_e$ and $T_e$ at the same three heights we showed the same maps for the DEMT results.
-As the two targets are highly axis-symmetric, a first quantitative comparison between AWSoM and DEMT will be shown as longitude-averaged latitudinal profiles of the results of both models at a sample height.
-Then we will show the lat/lon location of loops of type I, II and III at a middle height, just loke for DEMT results.
-To make comparisons in distinct magnetic structures, we will show the average radial dependence of results for loops of type I, II and III, overplotting the AWSoM and the DEMT results.
-For the tree types of loops we will show histograms of the DEMT and AWSoM products along field lines.
-This is a LOT of information from which and we need to pull out a few clear conclusions.}
 
@@
 
-%\notebyalbert{Propongo que Diego escriba una primer sección limpia, ordenada.
-Lo que vos mandarías al Solar Physics, sin asteriscos ni nada raro.
-Expresate con párrafos limpios.
-Si querés destacar algo para discutir ponelo como una nota en rojo al final del párrafo correspondiente, no en el medio de los mismos.
-Yo creo que esto debe estructurarse así:
-%\begin{enumerate}
-%\item Un párrafo (breve) de que se hizo, esto contextualiza. 
-%\item Dos o tres párrafos sobre los resultados 3.1.
-Esto es: resultados per se de cada rotación y como comparan (mencionando el tema incertezas).
-Estructura 3D del streamer en CAPAS, revelada observacionalmente en forma global por DEMT, esto incluye UP/DOWN loops.
-Explicar que con AIA no andamos bien en CHs.
-O sí?
-Energía.
-%\item Uno o dos párrafos sobre los resultados 3.2. Como compara AWSoM con DEMT. En forma breve. Vale la pena explicar que DOWN loops no se puede.
-%\item Luego un párrafo sobre next steps. Esto puede incluir nuevas cosas con AIA-4, el Eclipse, otras rotaciones de mayor intensidad.
-%\end{enumerate}
-%}
-
 {We carried out the 3D DEMT reconstruction and MHD modeling of the inner solar corona for two target rotations, CR-2082 and CR-2208.
@@
 
-\noindent
-\notebyalbert{Diego, agregá las sección de agradecimientos, fijándote como lo hicimos para tu paper anterior.
-Vos seguro debes agradecer a la beca, Ceci tambien (fijate en su paper), y todos los de aqui deberemos agraecer grants.
-Armalo como puedas y luego lo revisamos.}
-
-%% Figure 
-%
-% \begin{figure} 
-% \centerline{\includegraphics[width=0.5\textwidth,clip=]{<fig.eps>}}
-% \caption{}%\label{fig:?}
-% \end{figure}
-
-%% Table
-%
-% \begin{table}
-% \caption{}%\label{tbl:?}
-% \begin{tabular}{}     
-% \hline
-% \multicolumn{2}{c}{<>}
-% <data>
-% \hline
-% \end{tabular}
-% \end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Appendix
-%
-% \appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Acknowledgements
-%
 \begin{acks}
-D.G.Ll. and C.M.C. acknowledges CONICET doctoral fellowship (Res. Nr. 4870) to IAFE that supported his participation in this research.
-The authors acknowledge \diego{ANPCyT grant 2012/0973 and CONICET grant PIP \# 11220120100403 estos son viejos?} to IAFE that partially supported their participation in this research
+D.G.Ll.
+and C.M.C.
+\albert{acknowledge} CONICET doctoral \albert{fellowships} (Res.
+Nr.
+4870) to IAFE that supported \albert{their} participation in this research.
+\albert{D.G.Ll, A.M.V., F.A.N.
+and C.M.C.
+acknowledge ANPCyT grant 2016/0221 to IAFE that partially supported their participation in this research.
+A.M.V.
+also acknowledges UBACyT grant XXXX to FCEyN-UBA and IAFE that partially supported his participation in this research.}
 \end{acks}
 
-%%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Bibliography
-%
-% Using BibTeX
-%
 \bibliographystyle{spr-mp-sola}
 \bibliography{solphys_dglloveras}
-%
-% Without BibTeX 
-% \begin{thebibliography}{}
-% \bibitem[\protect\citeauthoryear{Author}{Year}]{key}
-%   <bibliographical entry>
-%
-% \bibitem[\protect\citeauthoryear{}{}]{}
-%   
-%  
-% \end{thebibliography}
 

### 2020-01-15 lloveras_2020.tex
trabajando en la intro

@@
 They provide validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, key to improve their space weather forecasting capabilities.
-Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale.
-Based on EUV data of space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun.
-We carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF).
+Solar rotational tomography is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale.
+Based on \diego{extreme ultraviolet} data of space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun.
+We carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework.
 Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the declining} phase of SC 24.
@@
 
-{Based on time-series of EUV images, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the solar corona.
-The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}.
+To study the global coronal 3D structure, solar rotational tomography (SRT) proved to be a powerful tool.
+Based on solar rotation, allow instruments to compile a time series of images that cover the entire corona.
+
+{Based on time-series of \diego{extreme ultraviolet (EUV)} images, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the \diego{quiet-Sun low corona at a global scale.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}.
+Using solar rotation time series of EUV images taken in channels sensitive to different temperatures, the technique allows calculation of 3D maps of electron density and temperature in the heliocentric height range $1.0\,\mrsun$ to $1.2\,\mrsun$ as summarized in Section \ref{demt}.
+
+\diego{
+A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona.
+For the first time we combined DEMT with coronal magnetic field modeled by a magnetohydrodynamic (MHD) model.
+Using the latest version of the Alfvén Wave Solar Model (AWSoM) of the Space Weather Modeling Framework, which provides a global magnetohydrodynamic (MHD) model coronal magnetic field and coronal thermodynamics,a combination of DEMT and AWSoM results
+}
+We carry out a quantitatively detailed comparative DEMT analysis of the Carrington Rotation (CR)-2082 during the Solar Cycle (SC) 23/24 minimum and CR-2208 during the declining fase of SC 24.
+To study CR-2082 data taken by the \textit{Extreme UltraViolet Imager Behind} (EUVI-B) on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) was used, while data taken by the \textit{Atmospheric Imaging Assembly instrument} (AIA), on board the \textit{Solar Dynamics Observatory} (SDO) mission was used to study CR-2208.
+
+\diego{
+Complementary to this, the coronal magnetic field of the global corona can be modeled
+by means of potential field source surface (PFSS) or even magnetohydrodynamics (MHD)
+models. A combination of the DEMT and global magnetic models has provided useful in-
+sight into the 3D thermodynamical structure of the global quiet-Sun corona
+}
+
+\diego{El parrafo de abajo lo pondria en la seccion 2.1}
 In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid.
@@
 
-\albert{In this work,} data from thre EUV bands was \albert{used:} 171, 193 and 211 \AA \ in \albert{the} case of AIA, and 171, 195 and 284 \AA \ bands in \albert{the} case of EUVI.
-When using data from \albert{three bands}, a Gaussian model for the LDEM is able to accurately predict the tomographic emissivities \citep{frazin_2009,nuevo_2015}.
+{In this work,} data from thre EUV bands was {used:} 171, 193 and 211 \AA \ in {the} case of AIA, and 171, 195 and 284 \AA \ bands in {the} case of EUVI.
+When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict the tomographic emissivities \citep{frazin_2009,nuevo_2015}.
 In each tomographic voxel the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that allow to best reproduce the three tomographically reconstructed values of FBE in that voxel.
@@
 {As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations.
-Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of \albert{the} tomographic grid ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
+Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of {the} tomographic grid ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
 Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}).
@@
 
-Figure \ref{gradt_demt} shows frequency histograms \albert{of $\dr\Tm$} for legs of type 0, I, II and III.
+Figure \ref{gradt_demt} shows frequency histograms {of $\dr\Tm$} for legs of type 0, I, II and III.
 The lack of population around values close to zero is due to the requirement $|\rhoTr| > 0.5$ which discards quasi-isothermal legs.
@@
 and C.M.C.
-\albert{acknowledge} CONICET doctoral \albert{fellowships} (Res.
+{acknowledge} CONICET doctoral {fellowships} (Res.
 Nr.
-4870) to IAFE that supported \albert{their} participation in this research.
-\albert{D.G.Ll, A.M.V., F.A.N.
+4870) to IAFE that supported {their} participation in this research.
+{D.G.Ll, A.M.V., F.A.N.
 and C.M.C.
@@
 A.M.V.
-also acknowledges UBACyT grant XXXX to FCEyN-UBA and IAFE that partially supported his participation in this research.}
+also acknowledges UBACyT grant \diego{XXXX} to FCEyN-UBA and IAFE that partially supported his participation in this research.}
 \end{acks}
-
+\\
+\\
+\begin{footnotesize}
+ Disclosure of Potential Conflicts of Interest: The authors declare that they have no conflicts of interest.
+\end{footnotesize}
 \bibliographystyle{spr-mp-sola}

### 2020-01-15 lloveras_2020_Albert_Section1.tex

--- 2020-01-15 lloveras_2020.tex
@@
 \label{momento2}
- \Tmi  = \langle \Te \rangle_i &=& \frac{1}{\langle \Ne^2 \rangle_i}\,\int\,\textrm{d}T\,T\,\LDEM_i(T),\label{Tm} 
+ \Tmi  = \langle \Te \rangle_i &=& \frac{1}{\langle \Ne^2 \rangle_i}\,\int\,\textrm{d}T\,T\,\albert{\LDEM_i(T).}\label{Tm} 
 \end{eqnarray}
@@
 
-{The energy balance given by Equation (\ref{Balance}) is then integrated in the volume of any given coronal magnetic flux tube.
+The energy balance given by Equation (\ref{Balance}) is then integrated in the volume of any given coronal magnetic flux tube.
 Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a field-line integrated version of that energy balance is found,
+
 \begin{equation}\label{FluxBalance}
-\phi_h = \phi_r + \phi_c.
+\phi_h = \phi_r + \albert{\phi_c,}
 \end{equation}
+
 \noindent
-where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\
+where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},
 
@@
 
-{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer regions of the equatorial streamer belt, exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
+{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer \albert{layers} of the equatorial streamer belt, exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
 In both rotations also, type III legs in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I legs in the core of the equatorial streamer.}
@@
 
-{Concerning the DEMT reconstructions, throughout the magnetically closed region of both rotations, we find that type 0, I and II legs are associated to increasingly outer regions of the equatorial streamer belt, and exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
+{Concerning the DEMT reconstructions, throughout the magnetically closed region of both rotations, we find that type 0, I and II legs are associated to increasingly outer \albert{layers} of the equatorial streamer belt, and exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
 For both target rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes.
@@
 
-{A detailed empirical description of the 3D termodynamic structure of the inner corona at a global scale is curently only possible with tomographic techniques, such as DEMT.
+A detailed empirical description of the 3D termodynamic structure of the inner corona at a global scale is curently only possible with tomographic techniques, such as DEMT.
 Using tomographic results for continuous validation of 3D MHD models is of high relevance for the continued improvement of models.
-In a follow up article we will analyse whit DEMT and 3D MHD modeling new target rotations of the current solar minimum between SCs 24 and 25, in particular the rotations conrresponding to the 2019 and 2020 total solar eclipses.}
+In \albert{follow up articles} we will \albert{carry out the 3D DEMT reconstruction and MHD modeling of} new target rotations \albert{selected from} the current solar minimum \albert{epoch} between SCs 24 and 25, \albert{as well as rotation CR-2219 corresponding to the July 2nd 2019 total solar eclipse.}
 
@@
 A.M.V.
-also acknowledges UBACyT grant XXXX to FCEyN-UBA and IAFE that partially supported his participation in this research.}
+also acknowledges UBACyT grant \albert{XXXX} to FCEyN-UBA and IAFE that partially supported his participation in this research.}
 \end{acks}

### 2020-01-17 lloveras_2020.tex
metiendo carne en la intro

@@
 \begin{abstract}
-Observational techniques play an essential role in advancing our understanding of the physics of the solar corona.
-They provide validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, key to improve their space weather forecasting capabilities.
-Solar rotational tomography is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale.
-Based on \diego{extreme ultraviolet} data of space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun.
+Observational techniques play an essential role in advancing our understanding of the physics of the solar corona, providing in particular validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere.
+Solar rotational tomography is currently the sole observational technique that provides a 3D quantitative description of the solar corona at a global scale.
+Based on \diego{extreme ultraviolet} data of space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$.
 We carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework.
@@
 To advance our knowledge of the physics of the solar corona, as well as to improve its three-dimensional (3D) models, information derived from observational data plays a key role.
-Solar rotational tomography is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar corona at a global scale.
+Solar rotational tomography (SRT) is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar corona at a global scale.
 
@@
 
-To study the global coronal 3D structure, solar rotational tomography (SRT) proved to be a powerful tool.
-Based on solar rotation, allow instruments to compile a time series of images that cover the entire corona.
+To study the global coronal 3D structure, SRT proved to be a powerful tool. Based on solar rotation, allow instruments to compile a time series of images that cover the entire corona.
 
@@
 Using solar rotation time series of EUV images taken in channels sensitive to different temperatures, the technique allows calculation of 3D maps of electron density and temperature in the heliocentric height range $1.0\,\mrsun$ to $1.2\,\mrsun$ as summarized in Section \ref{demt}.
+The reader may refer to the recent review by \citet{vasquez_2016} that summarizes the DEMT technique.
 
@@
 A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona.
-For the first time we combined DEMT with coronal magnetic field modeled by a magnetohydrodynamic (MHD) model.
-Using the latest version of the Alfvén Wave Solar Model (AWSoM) of the Space Weather Modeling Framework, which provides a global magnetohydrodynamic (MHD) model coronal magnetic field and coronal thermodynamics,a combination of DEMT and AWSoM results
+Recently \citet{lloveras_2017} combined DEMT whit coronal magnetic field of the global corona modeled by means of potential field source surface to study the last two solar minima.
+ More recently, \citet{sachdeva_2019} compared the results of the latest version of the Alfvén Wave Solar Model (AWSoM) of the Space Weather Modeling Framework model with observations for the same rotations as this article in a globally fashion, obtaining good agreement up to 1 AU.
+We used AWSoM results with two purposes.
+On the one hand to provide thermodynamic results to be contrasted with DEMT, and on the other hand to provide magnetohydrodynamic (MHD) coronal magnetic field model that is used to study thermodynamics along field lines.
 }
-We carry out a quantitatively detailed comparative DEMT analysis of the Carrington Rotation (CR)-2082 during the Solar Cycle (SC) 23/24 minimum and CR-2208 during the declining fase of SC 24.
+We carry out a quantitatively detailed comparative \diego{DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 during the Solar Cycle (SC) 23/24 minimum and CR-2208 during the declining fase of SC 24.
 To study CR-2082 data taken by the \textit{Extreme UltraViolet Imager Behind} (EUVI-B) on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) was used, while data taken by the \textit{Atmospheric Imaging Assembly instrument} (AIA), on board the \textit{Solar Dynamics Observatory} (SDO) mission was used to study CR-2208.
@@
 \diego{
-Complementary to this, the coronal magnetic field of the global corona can be modeled
-by means of potential field source surface (PFSS) or even magnetohydrodynamics (MHD)
-models. A combination of the DEMT and global magnetic models has provided useful in-
-sight into the 3D thermodynamical structure of the global quiet-Sun corona
+Section \ref{demt} and \ref{awsom} summarizes DEMT technique, AWSoM model, instruments, and datasets we used.
+Section \ref{trace} explains the technique that is used to trace the thermodynamic results along the field lines.
+Section \ref{energia} details the energy model and the loop integrated quantities that are part of the comparative analysis.
+In Section \ref{demt_res} the quantitative comparative analysis of both rotations using DEMT is described and in Section \ref{awsom_res} AWSoM results are related to the one of DEMT.
+Finally in Section \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.
 }
-
-\diego{El parrafo de abajo lo pondria en la seccion 2.1}
+\\
+\diego{El parrafo de abajo lo pondria en la seccion 2.1}\\
 In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid.
@@
 The main product of the technique is the local DEM (LDEM) at each volxel, a measure of the temperature distribution of the plasma contained in it.
-A recent review by \citet{vasquez_2016} summarizes the DEMT works up until then.
-More recently \citet{lloveras_2017} applied DEMT to study the last two solar minima, and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona.}
+
+\citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona.}
 
@@
 \label{momento2}
- \Tmi  = \langle \Te \rangle_i &=& \frac{1}{\langle \Ne^2 \rangle_i}\,\int\,\textrm{d}T\,T\,\LDEM_i(T),\label{Tm} 
+ \Tmi  = \langle \Te \rangle_i &=& \frac{1}{\langle \Ne^2 \rangle_i}\,\int\,\textrm{d}T\,T\,\LDEM_i(T).\label{Tm} 
 \end{eqnarray}
@@
 \begin{equation}\label{FluxBalance}
-\phi_h = \phi_r + \phi_c.
+\phi_h = \phi_r + \phi_c,
 \end{equation}
@@
 
-{Note that, for any given field line, all quantities in these two expresions can be computed from the DEMT and AWSoM models through Equations (\ref{Fc})-(\ref{Er}).
+{Note that, for any given field line, all quantities in these two expresions can be computed from the DEMT and AWSoM models through Equations \ref{Fc}-\ref{Er}.
 Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to mantain a stable coronal structure.}
+\diego{si vamos a hablar de awsom aca, deberiamos explicar xq no lo analizamos.}
 
@@
 
-{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer regions of the equatorial streamer belt, exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
+{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer layers of the equatorial streamer belt, exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
 In both rotations also, type III legs in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I legs in the core of the equatorial streamer.}
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105.eps}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2082_1005.eps}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2208_1005.eps}
 \caption{Longitude-averaged latitudinal dependence of the electron density (top) and temperature (bottom) for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$.
@@
 
-{Concerning the DEMT reconstructions, throughout the magnetically closed region of both rotations, we find that type 0, I and II legs are associated to increasingly outer regions of the equatorial streamer belt, and exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
+Concerning the DEMT reconstructions, Figure \ref{rpoint_demt} shows that, for both target rotations, magnetic field lines of type 0, I and II are associated to increasingly outer {layers} of the equatorial streamer belt.
+Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} report in 3D quantitative detail how these progressively outer magnetic structures exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
 For both target rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes.
@@
 Our results for target CR-2082 compare very well with those of \citet{nuevo_2015} and \citet{lloveras_2017} for target CR-2081.
-As our study uses the improved version of the DEMT technique, such comparison provided a consistency check for the changes implemented in the DEMT technique.}
+As our study uses the improved version of the DEMT technique, such comparison provided a consistency check for the changes implemented in the DEMT technique.
 
-{In both rotations also, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.
+{{For both target rotations}, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.
 In the case of the AIA based DEMT reconstruction, we show that in a substantial fraction of the CHs region the technique performs poorly in modeling LDEMs that predict the tomographic emissivitiy in each EUV band with reasonable accuracy.
@@
 
-{Results of the AWSoM model are compared to those of the DEMT reconstructions in the range of coronal heights $\approx 1.05-1.20\,\mrsun$ simultaneously covered by both models.
+Results of the AWSoM model are compared to those of the DEMT reconstructions in the range of coronal heights $\approx 1.05-1.20\,\mrsun$ simultaneously covered by both models.
 In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines.
@@
 This level of agreement between both models is considerably better than that reported in previous works.
-\citet{oran_2015} and \citet{jin_2012} reported electron density values of the AWSoM model typically 50\% larger than those of the DEMT reconstructions.} \notebyalbert{Chip, if Section 2.2 explains the most significant improvements of AWSoM since the version used in those references, we can comment on the reason for the improvement here.}
+\citet{oran_2015} and \citet{jin_2012} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.} \notebyalbert{Chip, if Section 2.2 explains the most significant improvements of AWSoM since the version used in those references, we can comment on the reason for the improvement here.}
 
@@
 
-\notebyalbert{Chip: In relation to the previous comment, if the anlaysis proposed in Figure 15 is carried out we should say something about that here.}
+\notebyalbert{Chip: In relation to the previous comment, if the analysis proposed in Figure 15 is carried out we should say something about that here.}
 
-{A detailed empirical description of the 3D termodynamic structure of the inner corona at a global scale is curently only possible with tomographic techniques, such as DEMT.
+A detailed empirical description of the 3D termodynamic structure of the inner corona at a global scale is currently only possible with tomographic techniques, such as DEMT.
 Using tomographic results for continuous validation of 3D MHD models is of high relevance for the continued improvement of models.
-In a follow up article we will analyse whit DEMT and 3D MHD modeling new target rotations of the current solar minimum between SCs 24 and 25, in particular the rotations conrresponding to the 2019 and 2020 total solar eclipses.}
-
+In {follow up articles} we will {carry out the 3D DEMT reconstruction and MHD modeling of} new target rotations {selected from} the current solar minimum {epoch} between SCs 24 and 25, {as well as rotation CR-2219 corresponding to the July 2nd 2019 total solar eclipse.}
 \begin{acks}
@@
 A.M.V.
-also acknowledges UBACyT grant \diego{XXXX} to FCEyN-UBA and IAFE that partially supported his participation in this research.}
+also acknowledges UBACyT grant 20020160100072BA to DCAO-UBA to FCEyN-UBA and IAFE that partially supported his participation in this research.}
 \end{acks}

### 2020-01-17 lloveras_2020_Albert.tex

@@
 \begin{abstract}
-Observational {techniques} play an essential role in advancing our understanding of the physics of the solar corona.
-They provide validation data {for} three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, {key to improve} their space weather forecasting capabilities.
-Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale.
-Based on EUV data of space borne instruments, SRT allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun.
-We carry out a study of the corona combining tomographic reconstructions with MHD simulations {using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF).
-Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24.
-Tomographic reconstructions and results of the model are \albert{analysed} in distinct coronal magnetic structures.
-We study magnetically closed structures associated with the equatorial streamer belt, as well as magnetically open regions enclosing it.
-We report on the tomographic results in the different structures, their implications for the physics of the solar corona, and the {current} capability of the AWSoM model to reproduce the tomographic reconstructions in different regions.
-
+Observational techniques play an essential role in advancing our understanding of the physics of the solar {corona, providing in particular validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere.
+Solar rotational tomography is currently the sole observational technique that provides a 3D quantitative description of the solar corona at a global scale.} Based on EUV data of space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights {below $\approx 1.25\,\mrsun$.
+We} carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling {Framework}.
+Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the declining} phase of SC 24.
+The 3D tomographic and MHD models are analysed and compared in distinct coronal magnetic structures.
+{We report in quantitative detail on the 3D thermodinamic structure of the inner corona as revealed by the DEMT analysis.
+We show in particular the existence of diverse types of temperature structures in the low and mid latitudes of the streamer belt, and that the heating energy required to keep them stable may be accounted for by Alfvén waves.
+We show that the latest version of the AWSoM model results agree with DEMT reconstructions to within a $\approx 20\%$ accuracy or better.
+We report on aspects of the AWSoM model that could be improved to better reproduce the DEMT results, in particular concerning the source region of the fast/slow solar winds.}
 \end{abstract}
@@
 
-\subsection{DEMT reconstructions}\label{demt}
+\subsection{{DEMT Reconstructions}}\label{demt}
 
-\noindent\notebyalbert{This section will summarize DEMT's main aspects and equations, only those needed to understand the paper.
-Nothing not needed to read this paper is provided.
-Also, no derivation of equations are provided.
-References are given so that the reader can dig deeper if so desires.
-Points to cover are:
-\begin{itemize}
-  \item Selected targets, instruments used. One paragraph.
-  \item Characteristics of the data (specific time series, dates, bands, etc.), SolarSoft software version used for their processing. One paragraph.
-  \item Technical aspects of DEMT (grid, regularization, off-limb data is only used) and how these differ from previous versions (rereferences). One paragraph.
-  \item What is FBE, what is LDEM, what is R.
-Why we care about these three quantities and what is their physical meaning should be clear.
-Then the final products $\Nm$ and $\Tm$, and what is their physical meaning.
-\end{itemize}
-}
+{We carried out the 3D DEMT reconstruction and MHD modeling of two target Carrington rotations (CR).
+We selected CR-2082 (2009, 05 April through 03 May), a deep minimum rotation between solar cycles (SC) 23 and 24, and CR-2208 (2018, 02 September through 29 September), a rotation during the early declining fase of SC 24.
+To study CR-2082 and CR-2208 data taken by the STEREO/EUVI-B and SDO/AIA instruments was used, respectively.
+The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package.
+For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.}
 
-To perform the comparison two specific rotations were selected, CR-2082 (2009, 05 April through 03 May), a deep minimum period between solar cycles (SCs) 23 and 24 characterized by virtually no ARs, and CR-2208 (2018, 02 September through 29 September), a rotation during the early declining fase of SC 24.
+{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we opted to only use off-limb data.
+In this way, the smallest scale and brighter coronal features seen on disk (most typically in the 171\AA\ band) are not included.
+This has two implications.
+Fistly, the fast dynamics that typically characterizes those structures is abscent from the data.
+Sencondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume.
+As a result, coronal dynamics induced artifacts are reduced compared to previous DEMT reconstructions.}
+.
+{The solution of the tomographic problem involves a very large sparse matrix.
+Such type of inversion problems are characterized by spurious high-frequency artifacts in the solution, which can be mitigated through \emph{regularization} techniques \citep{frazin_2000}.
+In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude.
+Also new to the present work, is the implementation of an expanded 3D regularization scheme, which adds to the previous scheme a finite difference matrix operator to approximate radial derivatives.
+In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions.
+As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.}
 
-To determine the thermodynamical structure of both rotations, the DEMT technique was applied to respective time series of EUV images covering each first half rotation.
-To study CR-2082 and CR-2208 data taken by the EUVI-B/STEREO and AIA/SDO instruments was used, respectively.
+{We summarize next the main aspects of DEMT required for the analysis of this work. We refer the reader to \citet{frazin_2009} for a full description of the technique.}
 
-EUV images are affected by instrumental stray light contamination, which can be corrected by deconvolution of the point spread function (PSF).
-While in the case of AIA images there is no reliable determination of its PSF, it has been well determined for EUVI-B by \citet{shearer_2012}.
-For this article, all EUVI images were stray-light corrected.
-For the details of impact in $\Nm$ and $\Tm$, refer to \citet{lloveras_ba2017}.
-
-In DEMT, the low corona in the height range $1.0$ to $1.25\,\mrsun$ is discretized in a spherical computational grid.
-The size of the tomographic cell (or voxel) is set to 0.01 \rsun \ in the radial direction, while is set 2\deg\ in both the latitudinal and longitudinal directions.
-We carried out a reconstruction using half of a solar rotation blocking the lines-of-sight comming from the disk (i.e.
-only using off-limb data).
-
-Using the high cadence of data available, one image every 10 minutes were used.
-The selected images were averaged in 6-hour intervals which, given the angular resolution, is the cadence needed to fully constrain the inversion problem, for a total of about 55 images to cover a half solar rotation.
-For both rotations, the first 14 days of data were used.
-
-\diego{ DONDE QUEDA MEJOR COMENTAR ESTA MEJORA?
-Unlike in previous works, a 3D regularization scheme was applied, thus spurious artifacts (nduced by the previous longitude latitude regularization schemei) were minimized in the first two heights of the tomographic grid.}
-
-We refer the reader to \citet{frazin_2009} for a detailed description of the technique, and to \citet{vasquez_2016} for a recent review on all published work based on it.
-Here we summarize the key points.
-The technique involves two consecutive procedures.
-
-In a first step, the time series of EUV images is used to solve a SRT problem, for each EUV band independently.
-As a result, the 3D distribution of the so called {filter band emissivity} (FBE) is determined for each band separately.
+In a first step, the time series of EUV images is used to solve a solar rotational tomography (SRT) problem, for each EUV band independently.
+As a result, the 3D distribution of the so called \emph{filter band emissivity} (FBE) is determined for each band separately.
 The FBE, {an emissivity-type quantity}, is defined as the wavelength integral of the coronal EUV spectral emissivity and the telescope's passband function of each EUV channel.
 Line-of-sight (LOS) integration of the FBE provides synthetic images that can be quantitatively compared to the real data in the time series.
-To find the FBE, the tomographic problem is posed a global optimization problem in which the quadratic norm of the difference between all pairs of synthetic and real images is minimized.
-Spatial regularization terms are also included in the objective function as to minimize high frequency spurious artifacts that are due to the specific characteristics of the SRT sparse projection matrix \citep{frazin_2009,frazin_2000}.
-{Due to optical depth issues that may affect LOSs} passing very close to the limb, and to the decay of intensity with radii, the 3D maps produced by DEMT analysis typically cover the height range 1.02 to 1.23 \rsun \ \citep{frazin_2009}.
+To find the FBE, the tomographic problem is posed a global optimization problem in which the quadratic norm of the difference between all {pairs of synthetic and real images is minimized.}
 
-\diego{COMO INTRODUZCO EL NIVEL DE REGULARIZACION? For each instrument, the DEMT analysis involves a cross-validation study to determine the optimal level of regularization.}
-
-{In a second step, the FBE values obtained for all bands in each voxel are used to constrain the determination of a {local differential emission measure} (LDEM) distribution, which describes the temperature distribution of the electron plasma contained in each individual tomographic grid voxel.
-Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}
+{In a second step, the FBE values obtained for all bands in each voxel {of the tomographic grid are used to constrain the determination of the LDEM which, as described in Section \ref{intro}, describes the temperature distribution of the plasma within the individual voxel.} Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}
 
@@
 
-{
+\noindent
+{where $K$ is the number EUV bands, and $\TRF^{(k)}$ is the \emph{temperature response function} of the $j$-th detector.
+The TRFs are here computed based on the (known) channel’s passband times the coronal emissivity at that temperature (normalized by the squared electron density).
+The emissivity model used here is provided by the latest version of the CHIANTI atomic database and plasma emission model \citep{delzanna_2015,landi_2013}.}
+
 Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}.
-These non-reconstructed voxels are indicated as black voxels in the Carrington maps of the reconstructed DEMT reults in Section \ref{resu}.
-}
+These non-reconstructed voxels are indicated {in black color in the latitude-longitude (Carrington) maps of DEMT} reults in Section \ref{resu}.
 
-Once the LDEM is determined at each voxel, the average squared electron density $\langle \Ne^2 \rangle$ and the electron mean temperature $\Tm$ in the voxel can be computed by taking its zeroth and first moments over temperature.
+{In this work,} data from thre EUV bands was {used:} 171, 193 and 211 \AA \ in {the} case of AIA, and 171, 195 and 284 \AA \ bands in {the} case of EUVI.
+When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict the tomographic emissivities \citep{frazin_2009,nuevo_2015}.
+In each tomographic voxel the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that allow to best reproduce the three tomographically reconstructed values of FBE in that voxel.
+
+Once the LDEM is determined at each voxel, {the LDEM-averaged squared electron density $\Nm^2$ and electron temperature $\Tm$} in the voxel can be computed by taking its zeroth and first moments over temperature.
 More specifically, at the $i$-th voxel,
-
 {
@@
 \label{momento2}
- \Tmi  = \langle \Te \rangle_i &=& \frac{1}{\langle \Ne^2 \rangle_i}\,\int\,\textrm{d}T\,T\,\LDEM_i(T),\label{Tm} 
+ \Tmi  = \langle \Te \rangle_i &=& \frac{1}{\langle \Ne^2 \rangle_i}\,\int\,\textrm{d}T\,T\,{\LDEM_i(T).}\label{Tm} 
 \end{eqnarray}
@@
 
-being the average relative difference between the tomographic and the synthetic FBEs.
-The final product of DEMT is in the form of 3D maps of the electron density and mean temperature.
-These relationships {were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
-%\temp{Aclarar que consideramos Ne como $\sqrt{<\Ne ^2>}$.} {ALBERT: Yo creo que es mejor hablar de $\sqravgN$}
+\noindent 
+{being the} average relative difference between the tomographic and the synthetic FBEs.
+{The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.}
 
-%\temp{DEMT has been improved since the previously published work.
-We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.} \notebyalbert{NOTA de Albert: Explicá que hacés sin justificarte.
-Luego aclará como se hizo eso en trabajos previos, y cual es el impacto esperado.
-Puedo proveer un párrafo de ejemplo, pero creo que será mejor que vos escribas como te salga y yo luego edito.
-Algo muy importante para todo el paper: proponete escribir ``párrafos modulares".
-Es decir que, con las razonables limitaciones, puedan moverse de lugar, de orden, y sigan funcionando.
-No definiría hollow-tomography, es un término coloquial interno nuestro.
-Lo correcto es que al hablar de datos mucho más arribas expliques que los datos del disco no se utilizan, pero no le des un nombre a la tomografía.}
+\subsection{{AWSoM Simulations}}\label{awsom}
 
-\subsection{AWSoM simulations}\label{awsom}
-
-\noindent\notebyalbert{This section will summarize the AWSoM model. After a first version is written we will surely require some input from the Michigan friends. Points to cover:
+\noindent\notebyalbert{This section will summarize the AWSoM model. Chip, Nishtha, do you think you could provide 2 or 3 paragraphs? We believe the points to cover are:
 \begin{itemize}
@@
 
-\subsection{Tracing of results along fieldlines}\label{trace}
+\subsection{{Tracing Results Along Magnetic Fieldlines}}\label{trace}
 
-\noindent\notebyalbert{This section will explain how the AWSoM magnetic model is used to trace the thermodynamic products of both DEMT and AWSoM along the fieldlines of AWSoM.
-This requires covering the following points:
-\begin{itemize}
-  \item A first paragraph qualitatively describing the process. This includes mentioning that the AWSoM products are first interpolated into the DEMT grid.
-  \item A short paragraph describing the numerical method used to trace field lines.
-We have a nice version of this in your previous paper.
-At this point the reader should understand that for each field line we have its geometry $\mathbf{r}(s)$ as a function of the distance $s$ along the loop, with $s(1\,\mrsun)\equiv 0$.
-  \item Explain very simply how then that for each voxel the middle point of the field line is selected and assigned the DEMT and AWSoM products of that cell.
-At this point the reader should understand that for each field line we have: $Q[r(s)]$, where $Q$ is any given quantity from either the DEMT model (specifically $\sqravgN$ and $\Tm$) or the AWSoM model (specifically $\Ne$ and $\Te$).
-  \item Explain fits to the DEMT results  $\sqravgN(r)$, $\Tm(r)$.
-  \item Explain then the classification of field lines.
-\end{itemize}
-}
-
-Aiming determination of the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid.
+{To determine} the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid.
 Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = r{\rm d}\theta/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point.
 In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, for a total of $96,000$ starting points.
-Each traced field line is classified as ``open" if it intersects the source surface, set in this work at $r=6\,\mrsun$ (where lines become radial), or as ``closed" otherwise.
-In the case of closed magnetic field lines, loops {are} further classified as ``small" and ``large" upon their apex height being within or beyond the range of heights studied by DEMT, respectively.
 
-At this stage, all DEMT and AWSoM products, electron density and mean temperature in particular, can be traced along open and closed magnetic field lines.
+{For analysis purposes, {the traced magnetic field lines are classified as open or closed according to their full geometry.
+Each closed field} line is further classified as ``small" or ``large", according to its coronal length $L$ being {respectively smaller or larger than the median value of the whole population, which is ${\rm Md}(L)\approx 0.5\,\mrsun$ for both rotations.} Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e.
+their location at $r=1\,\mrsun$) to its apex (i.e., the location of maximum height).}
+
+At this {stage, DEMT and AWSoM products} can be traced along open and closed magnetic field lines.
 Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one).
 To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it.
-As a result, for each field line one data point per tomographic cell is obtained.
-This allows to analyze how density and temperature, comming from both models, vary with height along each individual field line.
-This approach was firstly used by \citet{huang_2012} to study inverted temperature structures in the solar minimum corona, and later on applied by \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.
+As a result, for each field line one data point per tomographic cell {is obtained.
+This approach} was firstly used by \citet{huang_2012} to {study temperature} structures in the solar minimum {corona and by} \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.
 
-\diego{aca estoy haciendo la distincion entre la densidad y temp obtenida por demt y awsom}
-For each open field line, and for each leg of the closed ones, an exponential fit was then applied to the electron density and a linear fit applied to the electron temperature.
-For DEMT results, the data points used were $\sqravgN(r)$ and $\Tm(r)$, in case of AWSoM the data points were $\Ne(r)$ and $\Te(r)$.
+For each open field line and {for each closed field leg}, an exponential fit {was applied} to the electron density {data points} and a linear fit applied to the electron temperature {data points}.
+For {the DEMT model} the data points used were $\sqravgN(r)$ and $\Tm(r)$, and in case of {the AWSoM models} the data points used were $\Ne(r)$ and $\Te(r)$.
 The exponential and linear fit equations are described by
@@
 
-%La temperatura en funcion de la altura a lo largo de lineas muestra comportamientos lineales.
-En el presente trabajo nos focalizamos en lineas con temperaturas crecientes y decrecientes en foma lineal.
-Es decir nos quedamos con aquellas piernas donde el coeficiente de pearson entre la temperatura y la altura (rho) cumple rho mayor 0.5 (con p-value 0.05) y de esta forma se descartan aquellas piernas en las que los resultados DEMT no pueden asegurar un cambio notable de temperatura entre la base y el apice (asi no uso la palabra isotermico y evado ese problema)
+{Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies.
+As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
+Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}.
+In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and {considering time-averaged heating rates.}}
 
-%The temperature as a function of height along legs shows linear behaviors. 
-In the present work we focus on lines with increasing and decreasing temperatures in linear form.
-In other words, we selected those legs where the {Pearson correlation coefficient $\rho$ between temperature $T$ and radius $r$ meets $|\rhoTr| > 0.5$}.
-\temp{(with p-value less than 0.05)}.
-In this way, those legs in which the DEMT results cannot ensure a noticeable change in temperature between the base and the apex, are discarded.
-
-The linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg.
-\diego{En realidad esta regresion lineal utiliza de por si los errores, pero luego tmb los uso para el test de hipotesis, quizas vale la pena ponerlo solo ahi.}
-
-To measure how good the quality of the exponential fit to the electron density and the linear fit to the temperature data are, a chi-square merit function was used (see Section 15.2 \citet{recipes}).
-The errors were estimated in \citet{lloveras_2017}, $0.07$ MK for $\Tm$ and $4.0\,10^6 cm^{-3}$ for $\Ne$ and legs with p-value $>0.005$ were rejected.
-
-%el p-valor es un concepto estadístico, no veo xq deberia ser explicado. Lo que si, en el paper explicare bien las hipotesis nulas y de esa forma el p-valor queda bien claro.
-%El p-valor es una cuantificacion de con cuanta probabilidad de exito estas rechazando o aceptando una hipotesis en particular que se la suele denominar hipotesis nula.
-%En este caso, con 95$\%$ de seguridad estas rechazando las piernas que tienen un $pearson_x,y = 0$. Es decir te estarias quedando con aquellas que tienen una dependencia lineal entre x e y.
-%En el segundo caso, el test de hipotesis seria sobre la hip nula de que los datos provienen una funcion distribucion donde la recta fiteada de esos datos es el valor esperado de la distribucion.
-Con lo cual hacerle un test chi cuadrado te da una idea de cuan acertado o no es el ajuste.
-En este caso la hipotesis nula es que los datos provienen de esa distrib, con lo cual el chi deberia dar bajo y descartas los que dan valores altos con un 95$\%$ de seguridad.
-Eso es lo que representa el p-valor =0.05 en este caso (el area bajo la funcion distribucion, es decir, probabilidad).
-
-{To be selected a leg must meet all following conditions.}
+{To determine if the leg of a traced field line is} of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points.
+We then select field lines for which the temperature {is significantly correlated with height} by requiring $|\rhoTr| > 0.5$.
+{To test the goodness of the fit to the temperature-height data we perform a chi-squared test \citep{recipes} considering the uncertainty of the DEMT data points, selecting legs for which the fit matches the data with a 90\% confidence level.} In this way, legs for which the DEMT temperature does not show a significant {correlation} with height, or the linear fit to temperature is {not} good enough, are {excluded from the} analysis.
+{The test is also applied to the density-height data points, to ensure the trend is reasonably represented by the exponential fit.} Finally, selected legs are then classified as up or down according to if $\dr\Tm > 0$ or $\dr\Tm < 0$, respectively.
+The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg.
+{The chi-squared test to evaluate the quality of the fits considers the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$.} In summary, to be selected a leg must meet all three following conditions:
 
 \begin{enumerate}
-
 \item 
 The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg.
-
+{This requirement is set to ensure a reasonably spread sample of heights along the leg.}
 \item 
-The {value of the Pearson correlation coefficient meets $|\rhoTr| > 0.5$.}
-
+The {DEMT temperature and height data points must meet} $|\rhoTr| > 0.5$.
 \item 
-The p-value of both the exponential and linear fit must be less than 0.05.
-
+{The condifence level of both the exponential and linear fits must be larger than 90\%.} 
 \end{enumerate}
 
-\albert{Coronal magnetic structures for which their temperature increases/decreases with height (in the inner corona) have been dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies.
-As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
-Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}.
-In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}
-
-\albert{To characterize the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model.
+{To characterize the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model.
 Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types in this work:}
 
-\diego{Hice las definiciones con gradiente de temperatura para que quede mas claro, pero en realidad uso el pearson.} \notebyalbert{Charlemos los tres en persona de esto.}
-
 \begin{itemize}
- \item Type 0 - Small (meaning with apex within the DEMT range of heights) closed field lines in the latitudes range $[-30\mdeg,+30\mdeg]$ and $\dr \Tm < 0$.
-%This class thoroughly populates the equator of the Streamer belt during a minimum solar rotation.
-
-\item  Type I - Small closed field lines in all latitudes, with $\dr \Tm > 0$. %This class thoroughly populates the inner of the Streamer belt.
-
-\item  Type II - Large closed field lines (meaning their apex surpasses the DEMT range of heights) in the latitudes range $[-90\mdeg,-30\mdeg] \cup [+30\mdeg,+90\mdeg]$ and $\dr \Tm > 0$.
-%This class is mostly populated by very large trans-equatorial field lines forming the envelope of the Streamer belt.
-
-\item Type III - Open field lines (meaning with apex out the DEMT range of heights) in the latitudes range $[-90\mdeg,-60\mdeg] \cup [+60\mdeg,+90\mdeg]$ and $\dr \Tm > 0$.
-
+\item Type 0: closed-small-down with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
+\item Type I: closed-small-up with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
+\item Type II: closed-large-up with footpoints in the range $|{\rm latitude}|>40\mdeg$. 
+\item Type III: open with footpoint in the range $|{\rm latitude}|>60\mdeg$.
 \end{itemize}
 
-\albert{In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed.}
+{Legs of type down turn out to have a significant population only for closed-small loops.
+In the case of closed-large loops and open field lines, there are very few cases of type down.
+Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population in each case}.
+\\
+In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed.
+{As shown in Section \ref{demt_res}, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}
 
-\subsection{{Energy input flux}}\label{energia}
+\subsection{{Energy Input Flux}}\label{energia}
 
-\noindent\notebyalbert{This section will summarize how loop integrated energy quantities are computed from the DEMT products and the AWSoM magetic model alone.
-The summary will not include any derivation and will refer to Cecilia's paper.
-Only the results that are relevant are to be explicited.
-Start by explaining the model and assumptions, and end up summarizing the loop-integrated products (radiative and conductive fluxes).
-At the end the reader should understand that their sum is the enery input flux required at the coronal base to maintain the loop stable.
-This should be a very short section, as it is a summary of one previous paper alone.}
+{The high temperature of the corona requires heating mechanisms to compensate for the the losses.
+While the vast majority of the existing literature on coronal heating focuses on ARs, some studies have been dedicated to the heating of quiet-Sun regions.
+In particular,  \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to mantain them stable.
+The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in the previous Section \ref{trace}.}
 
-%correcciones a hacer! DIEGO
-%Los términos de la Eq (10) requieren ser explicados.
-La explicación a conituación no es clara, y de hecho está mal escrita.
-La Eq.
-(7) se integra en el VOLUMEN CORONAL COMPLETO de cada tubo de flujo y se divide por el área basal del mismo.
-Utilizando la condición solenoidal de B se llega a la Eq.
-(7), dónde...
-y ahí deberían darse las expresiones de Phir y Phic porque no pertenecen a la literatura estandard, y explicar a continuación como todos los elementos de esas dos expresiones surgen de los fits de DEMT y del modelo magnético de AWSoM.
-Donde si se puede ahorrar mucho espacio es en lo previo, la Eq (8) podría no incluirse por ejemplo.
-Creo que ahora lo mejor es que trates de completar la explicación dando las expresiones de Phir y Phic, y luego vemos de como limarla, probablemente eliminando la ec.
-(8).
-y además el texto puede compactarse, corregirse y reordenarse mucho.
-Poné las unidades de las cantidades Phi entre paréntesis a continuación de $\Phi_{h,r,c}$.
-
-Due the difference between temperatures of transition region and solar corona, there must to be a heating mechanism that compensate all the losses present in the atmosphere and maintain stable the plasma temperature.
-Previous works have studied this mechanism by observations and modeling, but mostly for active regions.
-\citet{maccormack_2017} have developed a technique that estimate the heating injected into the loops during a period of minima activity.
-Using DEMT combined with an extrapolation of magnetic field, as we detailed before, they obtain the different plasma parameters along each magnetic loop, and therefore, compute the energy input flux required to maintain them stable.
-The model assume a simple energy balance for each magnetic flux tube, where the losses by radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated by some coronal heating power($E_h$) \citep{aschwanden_2004}:
+{Consider} a simple energy balance for each magnetic flux tube, {in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated {by a} coronal heating power($E_h$) \citep{aschwanden_2004}:
 
@@
 
-{The energy balance given by Equation (\ref{Balance}) is then integrated in the volume of any given coronal magnetic flux tube.
+The energy balance given by Equation (\ref{Balance}) is then integrated in the volume of any given coronal magnetic flux tube.
 Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a field-line integrated version of that energy balance is found,
+
 \begin{equation}\label{FluxBalance}
-\phi_h = \phi_r + \phi_c.
+\phi_h = \phi_r + {\phi_c,}
 \end{equation}
+
 \noindent
-where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\
+where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},
 
@@
 
-\noindent\notebyalbert{This section will show first the DEMT products in the form of Carrington maps at three heights, for the two target rotations.
-It will then show the latitude/longitude location of the four types of  magnetic loops (defined in Section 2.3) at a sample height.
-Then, for the each type of loop, we will show histograms of the values of different DEMT products traced along them, charerizing in a quantitative fashion the DEMT results in distinct magnetic structures.
-It will also include a quantitative comparison between the two target rotations of the median values of the DEMT products in each type of loop.}
-
-{As described in Section \ref{demt}, we carried out DEMT reconstructions of the coronal structure for target rotations CR-2082 and CR-2208 using STEREO/EUVI and SDO/AIA data, respectively.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared $\sqravgN$ and the electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}{, and the measure $R$ was calculated by means of Equation (\ref{R}).}}
+{As described in Section \ref{demt}, we carried out DEMT reconstructions of the coronal structure for target rotations CR-2082 and CR-2208 using STEREO/EUVI and SDO/AIA data, respectively.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared ($\sqravgN$) and the electron mean temperature ($\Tm$) were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}{, and the measure $R$ was calculated by means of Equation \ref{R}.}}
 
 {As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations.
-Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic results ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
+Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of {the} tomographic grid ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
 Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}).
@@
 
-\albert{Both target rotations are highly axisymmetric, i.e.
+{Both target rotations are highly axisymmetric, i.e.
 characterized by a high azymuthal symmetry.
-Rotation CR-2082} showed two {small} ARs (active {regions), both near latitude} $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg${, respectively}.
-\albert{Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$, respectively.}
+Rotation CR-2082} showed two {small} active regions (ARs), both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg${, respectively}.
+{Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$, respectively.}
 
-{The magnetically open and closed regions of the AWSoM model are associated to CHs and the the equatorial streamer belt, respectively.
-Consistently with that, the \albert{location of the} open/closed boundaries derived from the respective AWSoM model quite accurately match \albert{the regions of the DEMT maps which exhibit the strongest latitudinal gradient of both the electron density and temperature.}}
+{The magnetically open and closed regions of the AWSoM model are associated to Coronal holes (CHs) and the equatorial streamer belt, respectively.
+Consistently with that, the {location of the} open/closed boundaries derived from the respective AWSoM model quite accurately matchs {the regions of the DEMT maps which exhibit the strongest latitudinal gradient of both the electron density and temperature.}}
 
@@
 
-{\albert{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively larger values of density and temperature in comparison to the CHs.
-They also that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 24 and 25}, the \albert{the low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behaviour is seen in CR-2208, belonging to the declining phase of {SC 25, but having a \albert{somewhat less axisymmetric} structure this characteristic is not so obvious.
+{{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively larger values of density and temperature in comparison to the CHs.
+They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 24 and 25}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the declining phase of {SC 25, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious.
 This thermodynamic structure} of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
 
-{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of \albert{the DEMT} measure $R$ defined by Equation (\ref{R}), at the same three heighs shown in Figures \ref{momento1} and \ref{momento2}.
+{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of {the DEMT} measure $R$ defined by Equation (\ref{R}), at the same three heights shown in Figures \ref{momento1} and \ref{momento2}.
 In most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$.
-The notable exception is to be found in the CHs of the target rotation \albert{analysed} based on AIA data.
+The notable exception is to be found in the CHs of the target rotation {analysed} based on AIA data.
 A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}.
@@
 \emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-\albert{The location of} type 0, I, II and III legs \albert{is shown} in blue, red, \albert{magenta and cyan} color, respectively.}}
+{The location of} type 0, I, II and III legs {is shown} in blue, red, {magenta and cyan} color, respectively.}}
 \label{rpoint_demt}
@@
 {For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
-Open legs are indicated in grey color and closed ones in black color.
+Open legs are indicated in gray color and closed ones in black color.
 For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}).
 Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} {Of the 45000 legs selected for CR-2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III.
-On the other hand, of the 59000 legs selected for CR-2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.} \notebyalbert{Los números deben ser actualizados, o la frase eliminada.}
+Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the {$\approx 44000$} legs selected for CR-2082, 20\% are type 0, 31\% are type I, 23\% are type II and 26\% type III.
+On the other hand, of the {$\approx 44000$} legs selected for CR-2208, 10\% are type 0, 43\% are type I, 30\% are type II and 17\% type III.
 
 {Type 0 (small down) legs mainly populate the equatorial latitudes.
-This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level {around the solar minimum beween SCs 24 and 25} by \citet{nuevo_2013}.
+This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level {around the solar minimum between SCs 24 and 25} by \citet{nuevo_2013}.
 Later on, \citet{lloveras_2017} showed {that} equatorial down loops in streamers were also to be found in the deep minimum between SCs {23 and 24}.
 Here, we verify the existence of this type of structure for the two target rotations.
-The relatively smaller population of down loops seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}.
+The relatively smaller population of down legs seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}.
 Type I (small up) mainly populate the mid-latitudes, while type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt.
-Finally, type III (open) legs populate of course the CHs.}
+Finally, type III (open) legs populate the CHs.}
 
@@
 \includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
-\caption{Frequency histograms of the temperature radial gradient for \albert{the four types of legs} in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
+\caption{Frequency histograms of the temperature radial gradient for {the four types of legs} in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
 \label{gradt_demt}
@@
 
-Figure \ref{gradt_demt} shows frequency histograms (normalized to the total amount of selected field lines ) of the temperature radial gradient ($\dr\Tm$) for legs of type 0, I, II and III.
-The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs.
+Figure \ref{gradt_demt} shows frequency histograms {of $\dr\Tm$} for legs of type 0, I, II and III.
+The lack of population around values close to zero is due to the requirement $|\rhoTr| > 0.5$ which discards quasi-isothermal legs.
 For both rotations, {the median value of the temperature radial gradient is ${\rm Md}\left(\dr\Tm\right) \approx -2.5$, $+2.3$ and $+2.4\,\MK/\mrsun$} for legs of type 0, I and II, respectively.
@@
 In this case, DEMT performs poorly in modeling a LDEM that predicts the tomographic FBEs with reasonable accuracy.
-Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, \albert{reveals that in most of the CH region the result for $\Tm$ below height $1.105\,\mrsun$ is quite uniform and artificially low}.
+Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, {reveals that in most of the CH region the result for $\Tm$ below height $1.105\,\mrsun$ is quite uniform and artificially low}.
 As it turns out, around and above height this height the score $R$ is lower and the temperature results are more reliable.
@@
 \includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
-\caption{{Statistical distribution of \albert{DEMT results for rotations CR-2082 (blue) and CR-2208 (red)} traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}.
-From left to right: \albert{electron density $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$,} electron density scale height $\lN$, \albert{and loop-averaged temperature $\aTm$.
+\caption{{Statistical distribution of {DEMT results for rotations CR-2082 (blue) and CR-2208 (red)} traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}.
+From left to right: {electron density $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$,} electron density scale height $\lN$, {and loop-averaged temperature $\aTm$.
 In each panel} the median value $m$ is indicated.} }
@@
 \begin{table}[h!]
-\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
-% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
+\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
 \hline
-Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
-       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
+Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
+        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
 \hline
-0    & 1&26 &(\Mi&17&4\%)  &   7&3 &(\Pl&13&6\%) &   1&09 &(\Pl&24&7\%) \\
-I    & 1&13 &(\Mi&14&1\%)  &   8&3 &(\Pl&18&1\%) &   1&29 &(\Pl&20&1\%) \\
-II   & 0&97 &(\Mi&20&6\%)  &   8&9 &(\Pl&29&1\%) &   1&33 &(\Pl&16&5\%) \\
-III  & 0&66 &(\Mi&16&2\%)  &   7&7 &(\Pl&11&4\%) &   0&98 &(\Pl&~6&1\%) \\
+0    & 1&24 &(\Mi&19\%)  &   7&1 &(\Pl&~3\%) &   1&09 &(\Pl&24\%) \\
+I    & 1&15 &(\Mi&10\%)  &   7&5 &(\Pl&29\%) &   1&25 &(\Pl&24\%) \\
+II   & 0&98 &(\Mi&20\%)  &   9&9 &(\Pl&19\%) &   1&36 &(\Pl&16\%) \\
+III  & 0&66 &(\Mi&12\%)  &   7&7 &(\Pl&15\%) &   0&97 &(\Pl&18\%) \\
 \hline          
 \end{tabular}
-\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
-For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.
-\notebyalbert{Propongo que para todas las cantidades absolutas de la Tabla 1 informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
-Doy dos ejemplos para no dejar dudas.
-Para $\NCB$ de Type-II: $1.0\,(-21\%)$.
-Para $\aTm$ de Type-III: $1.0\,(+6\%)$.}}
+\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of legs defined in Section \ref{trace}.
+For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
 \label{tabla_demt}
@@
 
-{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer regions of the equatorial streamer belt, progressively exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature.
-In both rotations also, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.}
+{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer {layers} of the equatorial streamer belt, exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
+In both rotations also, type III legs in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I legs in the core of the equatorial streamer.}
 
-{A comparison of the results between the two rotations shows that, compared to CR-2082, target rotation CR-2208 was characterized by $\approx 15-20\%$ lower values of the electron density at the coronal base, $\approx 10-30\%$ larger values of density scale height, and $\approx 15-25\%$ larger values of the electron temperature.} \notebyalbert{Los números de esta frase deben ser consistentes con los que finalmente informe la Table 1, redondeando los rangos característicos observados para los diversos tipos de línea (consultame!).
-La Table 1 debe a su vez resumir lo que muestra la Figure 6.
-Destacalo en tu color cuando lo hayas hecho así le presto atención.}
+{A comparison of the results between the two rotations shows that, compared to CR-2082, target rotation CR-2208 was characterized by {$\approx 10-20\%$} lower values of the electron density at the coronal base, $\approx 5-30\%$ larger values of density scale height, and {$\approx 5-25\%$} larger values of the electron temperature.}
 
-{To analyze the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the clasification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).
+{To analyze the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the classification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).
 {For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.}
@@
 
-{For both rotations, the value of the \albert{loop-integrated} radiative power $E_r$, measured by the quantity $\phi_r$, is largest for loops of type 0.
+{For both rotations, the value of the {loop-integrated} radiative power $E_r$, measured by the quantity $\phi_r$, is largest for loops of type 0.
 This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors contributing to maximize $E_r$ for loops of type 0.
-As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0 are characterised by \albert{the largest} values of electron density.
+As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0 are characterized by {the largest} values of electron density.
 Also, in the range of sensitivity of the EUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$.
-According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterised by {values of temperature that are progressively larger and farther} from the value $\Tc$, for both rotations.}
+According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterized by {values of temperature that are progressively larger and farther} from the value $\Tc$, for both rotations.}
 
-{\albert{The sign of the quantity $\phi_c$ depends on that of the conductive flux $F_c$.
-Equations (\ref{Fc}) and (\ref{phi_c}) imply that } down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, \albert{as verified} in Figure \ref{energia_demt}.}
+{{The sign of the quantity $\phi_c$ depends on that of the conductive flux $F_c$.
+Equations (\ref{Fc}) and (\ref{phi_c}) imply that } down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, {as verified} in Figure \ref{energia_demt}.}
 
-{\albert{Adding the} radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of \albert{loop, matching the values reported by} \citet{maccormack_2017}.
+{{Adding the} radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}.
 Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$.
-As shown by \citet{maccormack_2017}, \albert{this affects only the smallest sized loops of the type 0}, and it is \albert{most probably} due to the limited temperature sensitivity of the instrumental passbands.
-The radiative loss term is \albert{here calculated based on plasma emission detected by three coronal bands of EUVI or AIA.
+As shown by \citet{maccormack_2017}, {this affects only the smallest sized loops of the type 0}, and it is {most probably} due to the limited temperature sensitivity of the instrumental passbands.
+The radiative loss term is {here calculated based on plasma emission detected by three coronal bands of EUVI or AIA.
 Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range.
-As a result,} the positive term $\phi_r$ is most likely understimated, leading to values $\phi_h<0$ in loops of type 0, \albert{being characterized} by $\phi_c<0$.}
+As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized by $\phi_c<0$.}}
 
-\subsection{Tomography and Models}\label{awsom_res}
+\subsection{{Comparison of the DEMT and AWSoM Models}}\label{awsom_res}
 
-%\noindent\notebyalbert{This section will show the results of AWSoM for $N_e$ and $T_e$, and how they compare with the corresponding results of DEMT ($\sqravgN$ and $\Tm$).
-It will first show the Carrington maps of $N_e$ and $T_e$ at the same three heights we showed the same maps for the DEMT results.
-As the two targets are highly axis-symmetric, a first quantitative comparison between AWSoM and DEMT will be shown as longitude-averaged latitudinal profiles of the results of both models at a sample height.
-Then we will show the lat/lon location of loops of type I, II and III at a middle height, just loke for DEMT results.
-To make comparisons in distinct magnetic structures, we will show the average radial dependence of results for loops of type I, II and III, overplotting the AWSoM and the DEMT results.
-For the tree types of loops we will show histograms of the DEMT and AWSoM products along field lines.
-This is a LOT of information from which and we need to pull out a few clear conclusions.}
-
-\albert{For both target rotations,} Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature.
-\albert{Maps are shown} at the same three heights selected for visualisation of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}.
-\albert{Thick-black curves} indicate the magnetic open/closed boundaries based on the magnetic field of the AWSoM model.
-Visual inspection of these maps shows that the AWSoM model for both rotations is highly \albert{axisymetric}, as the tomographic model.
+{For both target rotations,} Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature.
+{Maps are shown} at the same three heights selected for visualization of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}.
+{Thick-black curves} indicate the magnetic open/closed boundaries based on the magnetic field of the AWSoM model.
+Visual inspection of these maps shows that the AWSoM model for both rotations is highly {axisymetric}, as the tomographic model.
 
@@
 
-\albert{As described in Section \ref{awsom}, the AWSoM model includes an artificially thick TR, achieving coronal conditions above height $\approx 1.06\,\mrsun$.
-Indeed, the top panels in Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208}, at height $1.025\,\mrsun$, clearly do not represent coronal conditions (altough we include them here for completness).
+{As described in Section \ref{awsom}, the AWSoM model includes an artificially thick TR, achieving coronal conditions above height $\approx 1.06\,\mrsun$.
+Indeed, the top panels in Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208}, at height $1.025\,\mrsun$, clearly do not represent coronal conditions (although we include them here for completeness).
 When compared to DEMT results (Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}), the latitude-longitude maps of the AWSoM model for heights $1.065$ and $1.105\,\mrsun$ capture well the denser and hotter equatorial streamer belt surrounded by the less dense and colder CHs.
-Furthermore, for both target rotations, the temperature maps show the low latitudes of the equatorial streamer belt to be characterised by lower temperatures than its mid-latitudes, as also seen in the DEMT results.
+Furthermore, for both target rotations, the temperature maps show the low latitudes of the equatorial streamer belt to be characterized by lower temperatures than its mid-latitudes, as also seen in the DEMT results.
 The latitude-longitude maps of the AWSoM and DEMT results are shown in the same units and scales, so that a visual comparison among them already reveals similar values of electron density and temperature in both models.}
@@
 
-\albert{Being highly axisymmtric target rotations, the longitude-averaged latitudinal variation of the results of both models is an informative way to compare their large-scale structure.
-Such comprison is shown in Figure \ref{perf_lat} at height $1.105\,\mrsun$, with top panels comparing electron density and lower panels electron temperature.
+{Being highly axisymmtric target rotations, the longitude-averaged latitudinal variation of the results of both models is an informative way to compare their large-scale structure.
+Such comparison is shown in Figure \ref{perf_lat} at height $1.105\,\mrsun$, with top panels comparing electron density and lower panels electron temperature.
 In these longitude-averaged profiles, longitudes containing ARs or low latitude CHs were excluded.
-In each panel the averaged latitudinal variation for the DEMT model is shown in solid-linestyle, while the result for the AWSoM model is shown in dashed-linesyle.
+In each panel the averaged latitudinal variation for the DEMT model is shown in solid-line style, while the result for the AWSoM model is shown in dashed-linesyle.
 Left panels show the comparison for CR-2082 (in blue) and right panels for CR-2208 (in red).
 In each panel the vertical black lines denote the corresponding longitude-averaged latitude of the open-close boundary in both hemispheres.}
-
-\notebyalbert{Diego: debés estar seguro que sacaste ARs y low-latitude CHs de los promedios en longitud.
-Cuando más te esmeres la comparación es más justa, y podés revelar algo que de otra manera no se vería.
-Si promediaste longitudes con ARs o CHs, rehacelo, vale la pena.
-Por supuesto debes promediar idéntidas longitudes en DEMT, AWSoM y en la O/C.}
 
@@
 
-\albert{Several details from Figure \ref{perf_lat} are worth being highlighted.
-Firstly, for CR-2082 the electron density of both models agree within $\approx 20\%$ at all latitudes, and for CR-2208 the agreement is within $\approx5\%$.
-In the case of the electron temperature both models agree within $\approx 10-15\%$ at all latitudes for both target rotations.
-Secondly, for both target rotations, and for both models, these plots clearly show the relatively lower temperatures characterising the low-latitudes of the equatorial streamel belt compared to its mid-latitudes.
-Thirdly, for both target rotations, the latitude of the open/close magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density.
-Note this is not the case for the AWSoM model, that shows a minimum densityat the open/closed boundary.
-Last, note that the DEMT electron density decreases from the open/close boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend.}
-
-\albert{To characterize the results of the AWSoM model in distinct magnetic structures, its results for electron density and temperature were traced along its magnetic field lines.
-For each field line leg, the results were then fit to Equations (\ref{Nfit}) and (\ref{Tfit}).
-In its current implementation, the AWSoM model can not simulate down loops, a point we will discuss in the next section.
-We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.}
+{\albert{Several details from Figure \ref{perf_lat} are worth being highlighted.
+Firstly, at most latitudes the overal agreement of the electron density of both models is within $\approx 20\%$ for CR-2082, and $\approx 5\%$ for CR-2208.
+The noticeable exception is to be found near the open/close boundaries of both target rotations, where the disagreement between both models can be up to twice as much.
+In the case of the electron temperature, for both target rotations the models agree within $\approx 15\%$ at all latitudes of the streamer belt, showing larger discrepancies in the CHs.} Secondly, for both target rotations, and for both models, these plots clearly show the relatively lower temperatures characterising the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
+Thirdly, for both target rotations, the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density.
+Note this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
+Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend.}
 
@@
 
-\albert{For both target rotations, the top panels of Figure \ref{rpoint_awsom} show the latitude-longitude location (at heliocentric height $1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
-That criterion is adapted here, requiring that at least five voxels of the tomographic grid are threaded by the leg.
-Open legs are indicated in grey color and closed ones in black color.
-For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit} and \ref{Tfit}.
-Considering the AWSoM data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_awsom} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a three-color code, type I, II and III legs are shown in red, magenta and cyan color, respectively.
-This figure is to be compared with the corresponding Figure \ref{rpoint_demt} for DEMT results.
-It is readily seen that the AWSoM maps are more populated than those of DEMT.
-This is due to the 3D MHD model having electron density and temperature fields spatially smoother than those of DEMT.}
-
-\albert{For target rotation CR-2082, Figure \ref{histos_2082} shows the statistical distribution of the results of the DEMT (solid line-style) and AWSoM (dashed line-style) models traced along legs of type I, II and III (from top to bottom), as defined in Section \ref{trace}.
-From left to right: electron density at the lowest coronal height of the AWSoM model $\NCB\equiv\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
-In each panel the median values $m$ are indicated.
-Figure \ref{histos_2208} shows the same analysis for target rotation CR-2208.}
+To characterize the results of the AWSoM model in distinct magnetic structures, its results for electron density and temperature were traced along its magnetic field lines.
+For each field line leg, the results were then fit to Equations (\ref{Nfit}) and (\ref{Tfit}){, considering only data points above heliocentric height $1.055\,\mrsun$.
+We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.
+Legs of type 0 are not included for AWSoM, as in its current implementation it can not simulate down loops, a point we will discuss in the next section.}
 
@@
 \includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
-\caption{{Statistical distribution \albert{of the results of the DEMT (solid line-style) and AWSoM (dashed-linestyle) models} traced along legs of type I, II and III (from top to bottom), as defined in \albert{Section \ref{trace}.} From left to right: electron density at the lowest coronal height of the AWSoM model $\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
-In each panel the median \albert{values $m$ are} indicated.}}
+\caption{{Statistical distribution {of the results of the DEMT (solid line-style) and AWSoM (dashed-line style) models} traced along legs of type I, II and III (from top to bottom), as defined in {Section \ref{trace}.} From left to right: electron density at the lowest coronal height of the AWSoM model $\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
+In each panel the median {values $m$ are} indicated.}}
 \label{histos_2082}
@@
 
-\albert{For the two target rotations, Table \ref{tabla_comp} summarizes a quantitative comparative analysis between the results of the DEMT and AWSoM models.
-The DEMT results are expressed as absolute values, while the ASWSoM results are informed as a percentual variation relative to the corresponding result for DEMT.
-the following major results can be drawn.}
+{For both target rotations, the top panels of Figure \ref{rpoint_awsom} show the latitude-longitude location (at heliocentric height $1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
+That criterion is adapted here, requiring that at least five voxels of the tomographic grid are threaded by the leg.
+Open legs are indicated in gray color and closed ones in black color.
+For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit} and \ref{Tfit}.
+Considering the AWSoM data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_awsom} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
+Using a three-color code, type I, II and III legs are shown in red, magenta and cyan color, respectively.
+This figure is to be compared with the corresponding Figure \ref{rpoint_demt} for DEMT results.
+It is readily seen that the AWSoM maps are more populated than those of DEMT.
+This is due to the 3D MHD model having electron density and temperature fields spatially smoother than those of DEMT.}
+
+{For target rotation CR-2082, Figure \ref{histos_2082} shows the statistical distribution of the results of the DEMT (solid line-style) and AWSoM (dashed line-style) models traced along legs of type I, II and III (from top to bottom), as defined in Section \ref{trace}.
+From left to right: electron density at the lowest coronal height of the AWSoM model $\NCB\equiv\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
+In each panel the median values $m$ are indicated.
+Figure \ref{histos_2208} shows the same analysis for target rotation CR-2208.}
 
@@
 
-\albert{For target rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, depending of the type of leg, while the median value of the scale height $\lN$ agree within $\approx 10\%$.
-The leg-averaged electron temperature $\aTm$ of both models also agree within $10\%$.
-For target rotation CR-2208 the agreement of the median value of $\NCB$ and $\lN$ of both models is within $5\%$, while median values of $\aTm$ agree within $15\%$.
-These detailed results informed per magnetic structure are fully consistent with the large-scale comparison provided in Figure \ref{perf_lat}.}
+{For the two target rotations, Table \ref{tabla_comp} summarizes a quantitative comparative analysis between the results of the DEMT and AWSoM models {based on the results shown in Figures \ref{histos_2082} and \ref{histos_2208}}.
+The DEMT results are expressed as absolute values, while the ASWSoM results are informed as a percentual variation relative to the corresponding result for DEMT.
+The following major results can be drawn.}
+
+{For target rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, \albert{depending of the type of leg, with the largest discrepancy foud for legs of type II (near the open/close boundary).
+The} median value of the scale height $\lN$ agree \albert{within $\approx 10\%$ in all regions}.
+The leg-averaged electron temperature $\aTm$ of both models also agree \albert{within $10\%$ in all regions}.
+For target rotation CR-2208 the agreement of the median value of $\NCB$ and $\lN$ of both models \albert{is within $10\%$, while} median values of $\aTm$ agree within $15\%$.
+\albert{These detailed results, being consistent with the large-scale comparison provided in Figure \ref{perf_lat}, show in detail how the AWSoM model performs compard to DEMT in different magetic strucures.}}
 
 \begin{table}
-\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
-% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
+\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
 \hline
-Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
-       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
+Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
+        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
 \hline
 CR-2082\\
-I  & 1&13 &(\Mi&11&9\%)  &   8&3 &(\Mi&~2&4\%) &   1&29 &(\Mi&10&8\%) \\
-II  & 0&97 &(\Mi&22&5\%)  &   8&9 &(\Pl&~2&2\%) &   1&33 &(\Mi&~4&5\%) \\
-III  & 0&66 &(\Mi&16&8\%)  &   7&7 &(\Mi&~9&1\%) &   0&98 &(\Mi&~9&2\%) \\
+I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&10\%) \\
+II   & 0&99 &(\Mi&25\%)  &   9&9 &(\Mi&~2\%) &   1&36 &(\Mi&~2\%) \\
+III  & 0&66 &(\Mi&17\%)  &   7&0 &(\Mi&~9\%) &   0&97 &(\Mi&~9\%) \\
 \hline          
 CR-2208\\
-I  & 0&97 &(\Pl&~9&3\%)  &   9&8 &(\Mi&~7&1\%) &   1&55 &(\Mi&14&2\%) \\
-II  & 0&77 &(\Pl&11&7\%)  &  11&6 &(\Mi&17&2\%) &   1&55 &(\Mi&~9&7\%) \\
-III  & 0&56 &(\Mi&~1&9\%)  &   8&6 &(\Mi&16&3\%) &   1&04 &(\Mi&~9&6\%) \\
+I    & 1&03 &(\Pl&~6\%)  &   9&7 &(\Mi&~8\%) &   1&55 &(\Mi&17\%) \\
+II   & 0&79 &(\Pl&~9\%)  &  11&8 &(\Mi&14\%) &   1&58 &(\Mi&~8\%) \\
+III  & 0&58 &(\Mi&~3\%)  &   8&9 &(\Mi&18\%) &   1&14 &(\Mi&18\%) \\
 \end{tabular}
-\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
-DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.
-{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca.
-Ejemplo para CR-2082 $\NCB$ de Type-II: $1.0\,(-23\%)$.
-Ejemplo para CR-2208 $\lambda_N$ de Type-II: $12.0\,(-17\%)$.
-Ejemplo para CR-2208 $\aTm$ de Type-II: $1.6\,(-10\%)$.}}
+\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of leg defined in Section \ref{trace}.
+DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
 \label{tabla_comp}
@@
 
-\albert{Finally, to provide a graphical comparison of both models accross the full range of heliocentric heights covered by the DEMT results, Figure \ref{perfiles_promedio} shows the average fits of $\Ne(r)$ and $T_e(r)$ for legs of type I (red), II (magenta), and III (cyan) for both target rotations.
-In each panel the DEMT and AWSoM results are plotted in solid and dashed linestyles, respectively.}
+{Finally, to provide a graphical comparison of both models across the full range of heliocentric heights covered by the DEMT results, Figure \ref{perfiles_promedio} shows the average fits of $\Ne(r)$ and $T_e(r)$ for legs of type I (red), II (magenta), and III (cyan) for both target rotations.
+In each panel the DEMT and AWSoM results are plotted in solid and dashed line styles, respectively.}
 
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
-\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of \albert{type I (red), II (magenta), and III (cyan)}, for CR-2082 (top panels) and CR-2208 (bottom panels).
+\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of {type I (red), II (magenta), and III (cyan)}, for CR-2082 (top panels) and CR-2208 (bottom panels).
 Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
@@
 
-\albert{As discusssed above, Figure \ref{perf_lat} shows that the logitude-averaged latitudinal profile of the DEMT electron density in the CHs decreases towards the poles.
+{As discussed above, Figure \ref{perf_lat} shows that the logitude-averaged latitudinal profile of the DEMT electron density in the CHs decreases towards the poles.
 Figure \ref{perf_lon_vr} below shows the longitude-averaged AWSoM radial wind speed $V_r$ at $6\,\mrsun$, where all field lines are open.
@@
 Similarly, all velocity data points to the north of the HCS position map down to the northern CH in Figures \ref{perf_lat}.
-This clearly shows an anti-correlation between the DEMT electron density at low heights and the AWSoM wind speed at larger heghts.}
+This clearly shows an anti-correlation between the DEMT electron density at low heights and the AWSoM wind speed at larger heights.}
 
@@
 We can set up starting points at, say, $20\,\mrsun$, every one degree, both in latitude and longitude.
-This would mean setting up $180\times 360$ strating points.
+This would mean setting up $180\times 360$ starting points.
 We trace then the (open) field lines from each of those starting points down to $1.0\,\mrsun$ to find out the DEMT results at those lower heights for each field line.
@@
 Chip: do you think you could do this with your present tools?
-Do you think it is intersting?
+Do you think it is interesting?
 I think so.
-Our submission deadline is end-of-January.}
+Our submission deadline is 24 January.}
 
@@
 
-\section{Discussion}\label{discu}
+\section{{Discussion and Conclusions}}\label{discu}
 
-\noindent\notebyalbert{(by Albert) This section will discuss and summarize some main conclusions, possibly in three groups: a) DEMT analysis alone (including thermodynamical structure, up/down loops, energy considerations, etc.), b) Comparison AWSoM/DEMT (longitude-averaged latitudinal profiles, height-dependence profiles in different magnetic structures, etc), and c) Correlation betweem AWSoM terminal wind speed and DEMT basal density, I will expand on this later this week as this may require help from Michigan).}
+{We carried out the 3D DEMT reconstruction and MHD modeling of the inner solar corona for two target rotations, CR-2082 and CR-2208.
+The first target belongs to the deep minimum epoch between SCs 23 and 24, while the latter belongs to the end of the declining phase of SC 24.
+The present work introduces two improvements in the implementation of DEMT, namely the use of only off-limb data in the EUV images, and the inclusion of a 3D regularization scheme.
+As a result of the former, artifacts introduced by coronal dynamics are mitigated, and as a result of the latter, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.
+The MHD model used is here the latest version of the AWSoM component of the SWMF suite.}
 
-\diego{NOTE: Here is a paragraph describing the empirical successes in the reconstruction of both rotations.}
+{Based on the magnetic field model of AWSoM model and the results of the DEMT model for electron density and temperature, we classified coronal structures in four different types.
+Smaller legs in the core of the streamer belt are classified in down/up types according to their temperature decreasing/increasing with height (dubbed type 0/I).
+Larger closed legs of type up that form the envelope of the streamer belt (dubbed type II), and open field lines of type up populating the CHs (dubbed type III).}
 
-*In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI.
-In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, \albert{analysed} a single target using both instruments independently.
-They found that while the density product is essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e.
+{Concerning the DEMT reconstructions, Figure \ref{rpoint_demt} shows that, for both taget rotations, magnetic field lines of type 0, I and II are associated to increasingly outer {layers} of the equatorial streamer belt.
+Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} report in 3D quantitative detail how these progressively outer magnetic structures exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.} For both target rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes.
+Also, in the case of CR-2082 the fraction of down legs is significantly larger than for CR-2208.
+These findings are consistent with previous studies by \citet{huang_2012} and \citet{nuevo_2013}.
+In the case of the latter, they include in their analysis target CR-2081, which is a rotation almost identical to our target CR-2082.
+Our results for target CR-2082 compare very well with those of \citet{nuevo_2015} and \citet{lloveras_2017} for target CR-2081.
+As our study uses the improved version of the DEMT technique, such comparison provided a consistency check for the changes implemented in the DEMT technique.
+
+{{For both target rotations}, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.
+In the case of the AIA based DEMT reconstruction, we show that in a substantial fraction of the CHs region the technique performs poorly in modeling LDEMs that predict the tomographic emissivitiy in each EUV band with reasonable accuracy.
+As a result, DEMT results based on AIA data are currently less reliable in the CH region.
+This was already found by the existing two previous DEMT works based on AIA data \citep{nuevo_2015,maccormack_2017}.
+The source of this distinct performance of DEMT when applied to EUVI or AIA data is related to the TRFs of the respective filter sets.
+We are currently implementing an improved LDEM determination algorithm to to deal with this issue that will be used in a follow up article.}
+
+In comparing the DEMT results obtained for the two selected targets, {we highlight here that} they rely on data provided by two different instruments, {namely EUVI and AIA for CR-2082 and CR-2208, respectively.} In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
+They found that while the density {products are} essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e.
 $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$.
-Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was $\approx 10-15\%$ hotter than CR-2082 throughout the streamer belt region.
+Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was {characterized by temperatures $\approx 10-15\%$ larger relative to CR-2082} throughout the streamer belt region.
 As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region.
-These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\lesssim 5\%$ and $\approx 2\%$ for the electron temperature and density, respectively.
+These systematic differences are {around or beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} {estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$}.}
 
-We found down legs in the DEMT reconstructions mainly in the equatorial latitudes, being a greater quantity and better distribution along longitudes in CR-2082 than in CR-2208.
-\citet{nuevo_2013} showed a decrease in the amount of down loops as the solar activity increases, which is consistent with the results shown in this article.
+{In the streamer belt region we combined the DEMT results and the AWSoM magnetic model to infer the energy input flux $\phi_h$ at the coronal base required to maintain stable coronal loops.
+To this end, we applied the technique developed by \citet{maccormack_2017}.
+We found characteristic values in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}.
+Based on spectroscopic data of the EIS instrument in quiet-Sun regions \citet{hahn_2014} showed that, if the observed non-thermal broadening are assigned to Alfvén waves, their energy flux at the coronal base is estimated to be in the range $\approx 1.5-2.5\times 10^5\,\erg\,\cminvs\,\s^{-1}$.
+A large fraction of the coronal base energy input flux $\phi_h$ estimated in this work, or even its totality, could then be accounted for by Alfvén waves.}
 
-*We can see, on type 0 loops, a median value of energy input flux ($\phi_h$) for CR-2082 twice bigger than CR-2208.
-In both rotations this magnitude has negative values, this can refer to some loops where loop-integrated radiative flux $\phi_r$) is too small in comparison with the larger gradients of negative conductive flux $\phi_c$), resulting in negative energy input flux.
+Results of the AWSoM model are compared to those of the DEMT reconstructions in the range of coronal heights $\approx 1.05-1.20\,\mrsun$ simultaneously covered by both models.
+In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines.
+The detailed comparison shown in this work can be summarized as follows.
+For CR-2082, the electron density of both models agree within $\approx 20\%$ \albert{in most regions}, while for CR-2208 the agreement is within $\approx 5\%$.
+\albert{The noticeable exception is to be found near the open/close boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations\albert{, with larger discrepancies in the CHs.} This level of agreement between both models is considerably better than that reported in previous works.
+\citet{oran_2015} and \citet{jin_2012} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.} \notebyalbert{Chip, if Section 2.2 explains the most significant improvements of AWSoM since the version used in those references, we can comment on the reason for the improvement here.}
 
-This effect can be due a subestimation of the density present in the loop or the limited range of temperature used to reconstruct tomographic parameters, that can affect the compute of radiative power.
-Nevertheless, this population represent lower than the \diego{ALGÚN PORCENTAJE$\%$} of total population in both cases.
+{Within the quantitative match summarized in the previous paragraph, there are some qualitative agreements and disagreements between both models worth noticing.
+For both target rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
+On the other hand, while the latitude of the open/close magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
+Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), the AWSoM model shows the opposite trend.
+This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.} \notebyalbert{Chip: Even if the match AWSoM/DEMT is quantitatively pretty good, this qualitative opposite behavior is off putting.
+Do you think there is room for improvement in the AWSoM model here?
+Maybe worth mentioning?}
 
-Consistent that the density in CR-2082 was higher, the $\phi_r$ was also higher.
-In both rotations the magnitudes in the temperature gradients are similar, but the temperatures in CR-2208 were consistently higher at all heights, resulting in a larger $\phi_c$ in module.
-This results are in agree with the observations of \citet{maccormack_2017}.
+\notebyalbert{Chip: In relation to the previous comment, if the anlaysis proposed in Figure 15 is carried out we should say something about that here.}
 
-\diego{THE AR of CR-2082 wasn't well modeled by AWSoM.}
+A detailed empirical description of the 3D termodynamic structure of the inner corona at a global scale is curently only possible with tomographic techniques, such as DEMT.
+Using tomographic results for continuous validation of 3D MHD models is of high relevance for the continued improvement of models.
+In {follow up articles} we will {carry out the 3D DEMT reconstruction and MHD modeling of} new target rotations {selected from} the current solar minimum {epoch} between SCs 24 and 25, {as well as rotation CR-2219 corresponding to the July 2nd 2019 total solar eclipse.}
 
-In both rotations, AWSoM and DEMT resutls shows same termodynamic structures along latitude and longitude with very comparable values between $1.055 - 1.25\,\mrsun$
+\begin{acks}
+D.G.Ll.
+and C.M.C.
+{acknowledge} CONICET doctoral {fellowships} (Res.
+Nr.
+4870) to IAFE that supported {their} participation in this research.
+{D.G.Ll, A.M.V., F.A.N.
+and C.M.C.
+acknowledge ANPCyT grant 2016/0221 to IAFE that partially supported their participation in this research.
+A.M.V.
+also acknowledges UBACyT grant {20020160100072BA to DCAO-UBA} and IAFE that partially supported his participation in this research.}
+\end{acks}
 
-Figure \ref{histos_2082} and Table \ref{tabla_comp} indicate that AWSoM reconstruction of CR-2082 was found to be less dense $\approx 11-22\%$ and colder $\approx 5-10\%$.
-
-Both reconstructions of CR-2208 reconstructed the ARs with very similare values and in almost the same latitude-longitude location.
-Figure \ref{histos_2208} and Table \ref{tabla_comp} indicate that AWSoM reconstruction of CR-2208 was found to be denser $\approx 0-10\%$ and colder $\approx 10-15\%$.
-
-CR-2208 was $\approx 10-15\%$ hotter than CR-2082 throughout the streamer belt region.
-As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region.
-These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\lesssim 5\%$ and $\approx 2\%$ for the electron temperature and density, respectively.
-
-\diego{I would like to say something about FIgure 10. Maybe the weird tale in AWSoM Ne in the poles. Ideas?}\\
-
-%\diego{We could say something about the anti correlation between speed and density and not get into the trace because issues do always appear and we don't have much time, and we all want to be happy in january.
-Unless the collaborators find easy to make this part.}
-
-%% Figure 
-%
-% \begin{figure} 
-% \centerline{\includegraphics[width=0.5\textwidth,clip=]{<fig.eps>}}
-% \caption{}%\label{fig:?}
-% \end{figure}
-
-%% Table
-%
-% \begin{table}
-% \caption{}%\label{tbl:?}
-% \begin{tabular}{}     
-% \hline
-% \multicolumn{2}{c}{<>}
-% <data>
-% \hline
-% \end{tabular}
-% \end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Appendix
-%
-% \appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Acknowledgements
-%
-% \begin{acks}
-%
-% \end{acks}
-
-%%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Bibliography
-%
-% Using BibTeX
-%
 \bibliographystyle{spr-mp-sola}
 \bibliography{solphys_dglloveras}
-%
-% Without BibTeX 
-% \begin{thebibliography}{}
-% \bibitem[\protect\citeauthoryear{Author}{Year}]{key}
-%   <bibliographical entry>
-%
-% \bibitem[\protect\citeauthoryear{}{}]{}
-%   
-%  
-% \end{thebibliography}
 

### 2020-01-17 lloveras_2020.tex
alguna pabada
avanzando

@@
 \runningauthor{D.G.~Lloveras~\etal}
-%\runningtitle{}
+\runningtitle{Comparative Coronal Study of CR-2082 and CR-2208}
 
@@
 
-To study the global coronal 3D structure, SRT proved to be a powerful tool. Based on solar rotation, allow instruments to compile a time series of images that cover the entire corona.
+\diego{To study the global coronal 3D structure, SRT proved to be a powerful tool.
+Based on solar rotation, allow instruments to compile a time series of images that cover the entire corona collecting data from all lines of sight.}
 
@@
 Recently \citet{lloveras_2017} combined DEMT whit coronal magnetic field of the global corona modeled by means of potential field source surface to study the last two solar minima.
+}
+
+\diego{DECIR ALGO DEL DESARROLLO DE AWSOM
 More recently, \citet{sachdeva_2019} compared the results of the latest version of the Alfvén Wave Solar Model (AWSoM) of the Space Weather Modeling Framework model with observations for the same rotations as this article in a globally fashion, obtaining good agreement up to 1 AU.
@@
 
-{Several details from Figure \ref{perf_lat} are worth being highlighted.
-Firstly, for CR-2082 the electron density of both models agree within $\approx 20\%$ at all latitudes, and for CR-2208 the agreement is within $\approx5\%$.
-In the case of the electron temperature both models agree within $\approx 10-15\%$ at all latitudes for both target rotations.
-Secondly, for both target rotations, and for both models, these plots clearly show the relatively lower temperatures characterising the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
+{{Several details from Figure \ref{perf_lat} are worth being highlighted.
+Firstly, at most latitudes the overal agreement of the electron density of both models is within $\approx 20\%$ for CR-2082, and $\approx 5\%$ for CR-2208.
+The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.
+In the case of the electron temperature, for both target rotations the models agree within $\approx 15\%$ at all latitudes of the streamer belt, showing larger discrepancies in the CHs.} Secondly, for both target rotations, and for both models, these plots clearly show the relatively lower temperatures characterising the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
 Thirdly, for both target rotations, the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density.
@@
 
-{For target rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, depending of the type of leg, while the median value of the scale height $\lN$ agree within $\approx 10\%$.
-The leg-averaged electron temperature $\aTm$ of both models also agree within $10\%$.
-For target rotation CR-2208 the agreement of the median value of $\NCB$ and $\lN$ of both models is within $5\%$, while median values of $\aTm$ agree within $15\%$.
-These detailed results informed per magnetic structure are fully consistent with the large-scale comparison provided in Figure \ref{perf_lat}.}
+{For target rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, {depending of the type of leg, with the largest discrepancy foud for legs of type II (near the open/closed boundary).
+The} median value of the scale height $\lN$ agree {within $\approx 10\%$ in all regions}.
+The leg-averaged electron temperature $\aTm$ of both models also agree {within $10\%$ in all regions}.
+For target rotation CR-2208 the agreement of the median value of $\NCB$ and $\lN$ of both models {is within $10\%$, while} median values of $\aTm$ agree within $15\%$.
+{These detailed results, being consistent with the large-scale comparison provided in Figure \ref{perf_lat}, show in detail how the AWSoM model performs compard to DEMT in different magetic strucures.}}
 
@@
 The detailed comparison shown in this work can be summarized as follows.
-For CR-2082, the electron density of both models agree within $\approx 20\%$ in all regions, while for CR-2208 the agreement is within $\approx 5\%$.
-In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations.
-This level of agreement between both models is considerably better than that reported in previous works.
+For CR-2082, the electron density of both models agree within $\approx 20\%$ {in most regions}, while for CR-2208 the agreement is within $\approx 5\%$.
+{The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations{, with larger discrepancies in the CHs.} This level of agreement between both models is considerably better than that reported in previous works.
 \citet{oran_2015} and \citet{jin_2012} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.} \notebyalbert{Chip, if Section 2.2 explains the most significant improvements of AWSoM since the version used in those references, we can comment on the reason for the improvement here.}
@@
 For both target rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
-On the other hand, while the latitude of the open/close magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
+On the other hand, while the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
 Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), the AWSoM model shows the opposite trend.

### 2020-01-20 lloveras_2020.tex
mejoras seccion1

@@
 
-Being the place where the solar atmosphere is heated and the solar wind accelerated, and where impulsive events such as solar flares and coronal mass ejections are energized, observation and modeling of the solar corona are tasks of great relevance to improve our understanding of the Sun-Earth environment.
+Being the \diego{region} where the solar atmosphere is \diego{heated, solar wind accelerated}, and where impulsive events such as solar flares and coronal mass ejections are energized, observation and modeling of the solar corona are tasks of great relevance to improve our understanding of the Sun-Earth environment.
 To advance our knowledge of the physics of the solar corona, as well as to improve its three-dimensional (3D) models, information derived from observational data plays a key role.
@@
 \diego{To study the global coronal 3D structure, SRT proved to be a powerful tool.
-Based on solar rotation, allow instruments to compile a time series of images that cover the entire corona collecting data from all lines of sight.}
-
-{Based on time-series of \diego{extreme ultraviolet (EUV)} images, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the \diego{quiet-Sun low corona at a global scale.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}.
+Based on solar rotation, allow instruments to compile a time series of images that cover the entire corona collecting data from all lines of sight.} In particular, differential emission measure tomography (DEMT), based on time-series of extreme ultraviolet (EUV) images, allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the \diego{quiet-Sun low corona at a global scale.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}.
 Using solar rotation time series of EUV images taken in channels sensitive to different temperatures, the technique allows calculation of 3D maps of electron density and temperature in the heliocentric height range $1.0\,\mrsun$ to $1.2\,\mrsun$ as summarized in Section \ref{demt}.
@@
 A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona.
-Recently \citet{lloveras_2017} combined DEMT whit coronal magnetic field of the global corona modeled by means of potential field source surface to study the last two solar minima.
-}
+In previous work, DEMT has been combined with a potential field source surface (PFSS) model such as \citet{huang_2012}, \citet{nuevo_2013} and \citet{nuevo_2015}.
+Recently, \citet{lloveras_2017} combined DEMT whit PFSS to study the thermodynamic of the last two solar minima along magnetic field lines and selecting different magnetic structures and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona throgh PFSS magnetic lines.}
 
-\diego{DECIR ALGO DEL DESARROLLO DE AWSOM
-More recently, \citet{sachdeva_2019} compared the results of the latest version of the Alfvén Wave Solar Model (AWSoM) of the Space Weather Modeling Framework model with observations for the same rotations as this article in a globally fashion, obtaining good agreement up to 1 AU.
+\diego{The Alfvén Wave Solar Model (AWSoM) of the Space Weather Modeling Framework model is constantly validated with observations as new improvements are implemented, in particular, \citet{oran_2015} used DEMT to validate the model in the low corona.
+More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT resutls in a globally fashion, obtaining an agreement within 20\%.
 We used AWSoM results with two purposes.
 On the one hand to provide thermodynamic results to be contrasted with DEMT, and on the other hand to provide magnetohydrodynamic (MHD) coronal magnetic field model that is used to study thermodynamics along field lines.
-}
+}\\
 We carry out a quantitatively detailed comparative \diego{DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 during the Solar Cycle (SC) 23/24 minimum and CR-2208 during the declining fase of SC 24.
-To study CR-2082 data taken by the \textit{Extreme UltraViolet Imager Behind} (EUVI-B) on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) was used, while data taken by the \textit{Atmospheric Imaging Assembly instrument} (AIA), on board the \textit{Solar Dynamics Observatory} (SDO) mission was used to study CR-2208.
+To study CR-2082 data taken by the \textit{Extreme UltraViolet Imager Behind} (EUVI-B) on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) was used \diego{for DEMT, and Global Oscillation Network Group (GONG) magnetogram as the only input for AWSoM}, while data taken by the \textit{Atmospheric Imaging Assembly instrument} (AIA), on board the \textit{Solar Dynamics Observatory} (SDO) mission was used to study CR-2208 \diego{for DEMT, and Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG magnetograms for AWSoM}.
 
@@
 \\
-\diego{El parrafo de abajo lo pondria en la seccion 2.1}\\
-In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid.
+%\diego{El parrafo de abajo lo pondria en la seccion 2.1}\\
+%In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid.
 The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions.
@@
 The main product of the technique is the local DEM (LDEM) at each volxel, a measure of the temperature distribution of the plasma contained in it.
-
-\citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona.}
 
@@
 As a result, coronal dynamics induced artifacts are reduced compared to previous DEMT reconstructions.}
-.
+
 {The solution of the tomographic problem involves a very large sparse matrix.
@@
 As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.}
+\diego{The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction (covering the height range $1.0-1.25\,\mrsun$) and 2\deg\ in both the latitudinal and longitudinal directions.
+}
 
@@
 
-{In this work,} data from thre EUV bands was {used:} 171, 193 and 211 \AA \ in {the} case of AIA, and 171, 195 and 284 \AA \ bands in {the} case of EUVI.
+The cadence of the data time-series is set to 6\,hr.
+
+\diego{In this work the cadence of the data time-series was set to 6\,hr and} data from three EUV bands were {used:} 171, 193 and 211 \AA \ in {the} case of AIA, and 171, 195 and 284 \AA \ bands in {the} case of EUVI.
 When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict the tomographic emissivities \citep{frazin_2009,nuevo_2015}.

### 2020-01-20 lloveras_2020.tex
agregado de texto de nishtha

@@
 \newcommand{\ssr}{    {\it Space Sci. Rev.}} 
+\newcommand{\procspie}{{\it Proc. SPIE}}
 
@@
 A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona.
-In previous work, DEMT has been combined with a potential field source surface (PFSS) model such as \citet{huang_2012}, \citet{nuevo_2013} and \citet{nuevo_2015}.
-Recently, \citet{lloveras_2017} combined DEMT whit PFSS to study the thermodynamic of the last two solar minima along magnetic field lines and selecting different magnetic structures and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona throgh PFSS magnetic lines.}
+In previous works, DEMT has been combined with a potential field source surface (PFSS) model such as \citet{huang_2012}, \citet{nuevo_2013} and \citet{nuevo_2015}.
+Recently, \citet{lloveras_2017} combined DEMT with PFSS to study the thermodynamic of the last two solar minima along magnetic field lines and selecting different magnetic structures and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona throgh PFSS magnetic lines.}
 
@@
 We carry out a quantitatively detailed comparative \diego{DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 during the Solar Cycle (SC) 23/24 minimum and CR-2208 during the declining fase of SC 24.
-To study CR-2082 data taken by the \textit{Extreme UltraViolet Imager Behind} (EUVI-B) on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) was used \diego{for DEMT, and Global Oscillation Network Group (GONG) magnetogram as the only input for AWSoM}, while data taken by the \textit{Atmospheric Imaging Assembly instrument} (AIA), on board the \textit{Solar Dynamics Observatory} (SDO) mission was used to study CR-2208 \diego{for DEMT, and Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG magnetograms for AWSoM}.
+To study CR-2082 data taken by the \textit{Extreme UltraViolet Imager Behind} \diego{(EUVI-B \citep{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) was used \diego{for DEMT, and Global Oscillation Network Group (GONG) magnetogram as the only input for AWSoM}, while data taken by the \textit{Atmospheric Imaging Assembly instrument} \diego{(AIA \citep{lemen_2012})}, on board the \textit{Solar Dynamics Observatory} (SDO) mission was used to study CR-2208 \diego{for DEMT, and Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG magnetograms for AWSoM}.
 
@@
 For this {reason,} the model uses {an artificially} extended {TR about $\approx 0.05\,\mrsun$ thick, as well as artificially large values for the electronic density and temperature as boundary conditions in $r=1\,\mrsun$.} Consequently, model results below {$\approx 1.05\,\mrsun$} were not taken into account in this article.
+
+The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) is a three-dimensional (3D) physics-based, data-driven model extending from the upper chromosphere, into the solar corona upto 1 AU (and beyond) \citep{vander_2010, Van2014}.
+AWSoM addresses coronal heating by including the non-linear interaction of forward propagating and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
+The model accounts for anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature.
+The dissipated turbulent energy is distributed over these three temperatures based on the theories of linear wave damping and stochastic heating.
+AWSoM does not use ad-hoc heating functions and accounts for both collisional and collision-less electron heat conduction.
+The Alfv\'{e}n wave number associated with the damping rate is determined by the critical balance condition which uses the cascade time of the minor wave \citep{Lit2007} instead of the previously used cascade time of the major wave \citep{Cha2011, Van2014}.
+This energy partitioning, in the improved version of AWSoM, leads to more electron heating and less solar wind acceleration \diego{falta cita}%\citep{Van2019b}.
+To solve anisotropic MHD equations with radiative cooling, heat conduction and wave turbulence, AWSoM uses the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme.
+MHD equations employed within the AWSoM model are detailed in \citet{Van2014}.
+Recently, \citet{sachdeva_2019} validated the AWSoM simulation results with a suite of observations from near the Sun upto 1 AU for solar minimum conditions.
+
+Global maps of the observed photospheric magnetic field are essential for accurate modeling of the solar corona and are the primary input for AWSoM.
+We use the Global Oscillation Network Group (GONG) synoptic map as input for CR2082 (2009-04-05 - 2009-05-03) and the Air Force Data Assimilation Photospheric Flux Transport (ADAPT)-GONG global magnetic field map for CR2208 (2018-09-02 to 2018-09-29).
+ADAPT-GONG maps are unavailable for CR2082.
+GONG provides synoptic full disk line-of-sight surface map of the radial magnetic field component.
+The unobserved polar fields in GONG are estimated by fitting a polynomial to neighboring observed fields.
+An improvement over these maps is provided by the ADAPT model \citep{Wor2000} which creates synchronic-synoptic maps that uses supergranulation, meridional circulation, flux-transport and differential rotation to evolve the magnetic field on the Sun for better estimates of the unobserved photospheric field \citep{Arg2010, Hen2012}.
+In AWSoM, the 2D radial photospheric field is converted to 3D magnetic field using the Potential Field Source Surface (PFSS) model which specifies the initial condition.
+We take the source surface to be at 2.5 \rsun and the magnetic field is radial at this height.
+The radial component specifies the boundary condition.
+%ADAPT-GONG maps have multiple realizations based on how the polar fields are filled. We use realization 5 for CR2208.
+ Based on \citet{Cha2011} the stochastic heating exponent is taken to be 0.21 and amplitude is 0.18 to account for energy partioning between electrons and protons.
+The Alfv\'{e}n wave energy boundary condition is given by the poynting flux (S$_{A}$) of the outgoing wave $(\frac{S_{A}}{B})_{\odot} = 1.0\times 10^{6}$ Wm$^{-2}$T$^{-1}$ and the correlation length of the Alfv\'{e}n waves is set to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$ m$\sqrt{T}$.
+
+The base of the transition region forms the inner boundary of the model (at $\approx$1.0\,\rsun).
+To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot}=2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K.
+The upper chromosphere is required to extend radially for the density to fall rapidly to correct (lower) values \citep{Lio2009}.
+In reality, the thin transition has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses.
+To resolve these gradients excessive numerical resources are required.
+As described in \citet{Lio2009,Sok2013} we artificially broaden the transition region to resolve with our finest grid resolution of $\approx$ 0.001\,\rsun.This results in pushing the corona outwards.
+At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region.
+The computational domain for solar corona (SC) extends from 1 to 24 R$_{\odot}$.
+The spherical grid in SC is radially stretched (with a maximum resolution of 0.001 R$_{\odot}$ near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates.
+The Adaptive Mesh Refinement (AMR) resolves the angular size to 1.4$^\circ$ between 1 - 1.7 \rsun and 2.8 \rsun outside.
+The SC component uses about 3 million cells on a $6 \times 8 \times 8$ grid block.
+Local time stepping is used to speed up the steady state convergence.
+AWSoM simulation results provide the 3D distribution of density and temperature in addition to the 3D magnetic structure and velocity of the solar wind.
 
@@
 
-\notebyalbert{Chip: In relation to the previous comment, if the analysis proposed in Figure 15 is carried out we should say something about that here.}
+\notebyalbert{Chip: In relation to the previous comment, if the analysis proposed in Figure 15 is carried out we should say something about that here.} d
 
@@
 In {follow up articles} we will {carry out the 3D DEMT reconstruction and MHD modeling of} new target rotations {selected from} the current solar minimum {epoch} between SCs 24 and 25, {as well as rotation CR-2219 corresponding to the July 2nd 2019 total solar eclipse.}
+
 \begin{acks}

### 2020-01-21 lloveras_2020.tex
Version 1.0

@@
 Solar rotational tomography is currently the sole observational technique that provides a 3D quantitative description of the solar corona at a global scale.
-Based on \diego{extreme ultraviolet} data of space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$.
+Based on {extreme ultraviolet} data of space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$.
 We carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework.
@@
 
-Being the \diego{region} where the solar atmosphere is \diego{heated, solar wind accelerated}, and where impulsive events such as solar flares and coronal mass ejections are energized, observation and modeling of the solar corona are tasks of great relevance to improve our understanding of the Sun-Earth environment.
+Being the {region} where the solar atmosphere is {heated, solar wind accelerated}, and where impulsive events such as solar flares and coronal mass ejections are energized, observation and modeling of the solar corona are tasks of great relevance to improve our understanding of the Sun-Earth environment.
 To advance our knowledge of the physics of the solar corona, as well as to improve its three-dimensional (3D) models, information derived from observational data plays a key role.
@@
 
-\noindent\notebyalbert{Here we will put in a couple of paragraphs summarizing what SRT and DEMT are, including references and defining the accronyms in the process.
+%\noindent\notebyalbert{Here we will put in a couple of paragraphs summarizing what SRT and DEMT are, including references and defining the accronyms in the process.
 We should refer to minima in particular.
@@
 
-\diego{To study the global coronal 3D structure, SRT proved to be a powerful tool.
-Based on solar rotation, allow instruments to compile a time series of images that cover the entire corona collecting data from all lines of sight.} In particular, differential emission measure tomography (DEMT), based on time-series of extreme ultraviolet (EUV) images, allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the \diego{quiet-Sun low corona at a global scale.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}.
+{To study the global coronal 3D structure, SRT proved to be a powerful tool.
+Based on solar rotation, allow instruments to compile a time series of images that cover the entire corona collecting data from all lines of sight.} In particular, differential emission measure tomography (DEMT), based on time-series of extreme ultraviolet (EUV) images, allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the {quiet-Sun low corona at a global scale.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}.
 Using solar rotation time series of EUV images taken in channels sensitive to different temperatures, the technique allows calculation of 3D maps of electron density and temperature in the heliocentric height range $1.0\,\mrsun$ to $1.2\,\mrsun$ as summarized in Section \ref{demt}.
@@
 
-\diego{
+{
 A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona.
@@
 
-\diego{The Alfvén Wave Solar Model (AWSoM) of the Space Weather Modeling Framework model is constantly validated with observations as new improvements are implemented, in particular, \citet{oran_2015} used DEMT to validate the model in the low corona.
-More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT resutls in a globally fashion, obtaining an agreement within 20\%.
+{The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) is a three-dimensional (3D) physics-based, data-driven model extending from the upper chromosphere, into the solar corona upto 1 AU (and beyond) \citep{vander_2010, Van2014} and is constantly validated with observations as new improvements are implemented.
+DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona.
+More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a globally fashion, obtaining an agreement within 20\%.
 We used AWSoM results with two purposes.
 On the one hand to provide thermodynamic results to be contrasted with DEMT, and on the other hand to provide magnetohydrodynamic (MHD) coronal magnetic field model that is used to study thermodynamics along field lines.
-}\\
-We carry out a quantitatively detailed comparative \diego{DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 during the Solar Cycle (SC) 23/24 minimum and CR-2208 during the declining fase of SC 24.
-To study CR-2082 data taken by the \textit{Extreme UltraViolet Imager Behind} \diego{(EUVI-B \citep{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) was used \diego{for DEMT, and Global Oscillation Network Group (GONG) magnetogram as the only input for AWSoM}, while data taken by the \textit{Atmospheric Imaging Assembly instrument} \diego{(AIA \citep{lemen_2012})}, on board the \textit{Solar Dynamics Observatory} (SDO) mission was used to study CR-2208 \diego{for DEMT, and Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG magnetograms for AWSoM}.
+}
 
-\diego{
+We carry out a quantitatively detailed comparative {DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 during the Solar Cycle (SC) 23/24 minimum and CR-2208 during the declining fase of SC 24.
+To study CR-2082 data taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B \citep{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) was used {for DEMT, and Global Oscillation Network Group (GONG) magnetogram as the only input for AWSoM}, while data taken by the \textit{Atmospheric Imaging Assembly instrument} {(AIA \citep{lemen_2012})}, on board the \textit{Solar Dynamics Observatory} (SDO) mission was used to study CR-2208 {for DEMT, and Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG magnetograms for AWSoM}.
+
+{
 Section \ref{demt} and \ref{awsom} summarizes DEMT technique, AWSoM model, instruments, and datasets we used.
@@
 \\
-%\diego{El parrafo de abajo lo pondria en la seccion 2.1}\\
+%{El parrafo de abajo lo pondria en la seccion 2.1}\\
 %In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid.
@@
 As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.}
-\diego{The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction (covering the height range $1.0-1.25\,\mrsun$) and 2\deg\ in both the latitudinal and longitudinal directions.
+{The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction (covering the height range $1.0-1.25\,\mrsun$) and 2\deg\ in both the latitudinal and longitudinal directions.
 }
@@
 
-\diego{In this work the cadence of the data time-series was set to 6\,hr and} data from three EUV bands were {used:} 171, 193 and 211 \AA \ in {the} case of AIA, and 171, 195 and 284 \AA \ bands in {the} case of EUVI.
+{In this work the cadence of the data time-series was set to 6\,hr and} data from three EUV bands were {used:} 171, 193 and 211 \AA \ in {the} case of AIA, and 171, 195 and 284 \AA \ bands in {the} case of EUVI.
 When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict the tomographic emissivities \citep{frazin_2009,nuevo_2015}.
@@
 
-\noindent\notebyalbert{This section will summarize the AWSoM model. Chip, Nishtha, do you think you could provide 2 or 3 paragraphs? We believe the points to cover are:
-\begin{itemize}
-  \item Data input. Link with the data input for DEMT in terms of dates, etc. One paragraph.
-  \item Main physical and technical aspects (grid in particular) of the model.  One paragraph. 
-  \item Explain the artificially extended TR. One paragraph.
-  \item What are the products of the model we care about in this paper ($N_e$, $T_e$, $B$, $V$, as of now). One paragraph.
-\end{itemize}
-}
+%\noindent\notebyalbert{This section will summarize the AWSoM model. Chip, Nishtha, do you think you could provide 2 or 3 paragraphs? We believe the points to cover are:
+%\begin{itemize}
+%  \item Data input. Link with the data input for DEMT in terms of dates, etc. One paragraph.
+%  \item Main physical and technical aspects (grid in particular) of the model.  One paragraph. 
+%  \item Explain the artificially extended TR. One paragraph.
+%  \item What are the products of the model we care about in this paper ($N_e$, $T_e$, $B$, $V$, as of now). One paragraph.
+%\end{itemize}
+%}
 
-In the transition region {(TR)}, the plasma heats up and becomes less dense {by} several orders of magnitude {over} a short distance.
+%In the transition region {(TR)}, the plasma heats up and becomes less dense {by} several orders of magnitude {over} a short distance.
 Modeling this region {realistically has a very high computational cost}.
@@
 
-The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) is a three-dimensional (3D) physics-based, data-driven model extending from the upper chromosphere, into the solar corona upto 1 AU (and beyond) \citep{vander_2010, Van2014}.
+%The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) is a three-dimensional (3D) physics-based, data-driven model extending from the upper chromosphere, into the solar corona upto 1 AU (and beyond) \citep{vander_2010, Van2014}.
+
 AWSoM addresses coronal heating by including the non-linear interaction of forward propagating and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
@@
 The Alfv\'{e}n wave number associated with the damping rate is determined by the critical balance condition which uses the cascade time of the minor wave \citep{Lit2007} instead of the previously used cascade time of the major wave \citep{Cha2011, Van2014}.
-This energy partitioning, in the improved version of AWSoM, leads to more electron heating and less solar wind acceleration \diego{falta cita}%\citep{Van2019b}.
+This energy partitioning, in the improved version of AWSoM, leads to more electron heating and less solar wind acceleration.% \diego{falta cita}%\citep{Van2019b}.
 To solve anisotropic MHD equations with radiative cooling, heat conduction and wave turbulence, AWSoM uses the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme.
@@
 Global maps of the observed photospheric magnetic field are essential for accurate modeling of the solar corona and are the primary input for AWSoM.
-We use the Global Oscillation Network Group (GONG) synoptic map as input for CR2082 (2009-04-05 - 2009-05-03) and the Air Force Data Assimilation Photospheric Flux Transport (ADAPT)-GONG global magnetic field map for CR2208 (2018-09-02 to 2018-09-29).
-ADAPT-GONG maps are unavailable for CR2082.
+The model use GONG synoptic map as input for CR-2082 (2009-04-05 - 2009-05-03) and ADAPT-GONG global magnetic field map for CR-2208 (2018-09-02 to 2018-09-29).
+ADAPT-GONG maps are unavailable for CR-2082.
 GONG provides synoptic full disk line-of-sight surface map of the radial magnetic field component.
@@
 An improvement over these maps is provided by the ADAPT model \citep{Wor2000} which creates synchronic-synoptic maps that uses supergranulation, meridional circulation, flux-transport and differential rotation to evolve the magnetic field on the Sun for better estimates of the unobserved photospheric field \citep{Arg2010, Hen2012}.
-In AWSoM, the 2D radial photospheric field is converted to 3D magnetic field using the Potential Field Source Surface (PFSS) model which specifies the initial condition.
-We take the source surface to be at 2.5 \rsun and the magnetic field is radial at this height.
+In AWSoM, the 2D radial photospheric field is converted to 3D magnetic field using the PFSS model which specifies the initial condition.
+We take the source surface to be at $2.5 \, \mrsun$ and the magnetic field is radial at this height.
 The radial component specifies the boundary condition.
@@
 
-The base of the transition region forms the inner boundary of the model (at $\approx$1.0\,\rsun).
+The base of the transition region (TR) forms the inner boundary of the model (at $\approx$1.0\,\rsun).
 To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot}=2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K.
@@
 To resolve these gradients excessive numerical resources are required.
-As described in \citet{Lio2009,Sok2013} we artificially broaden the transition region to resolve with our finest grid resolution of $\approx$ 0.001\,\rsun.This results in pushing the corona outwards.
+As described in \citet{Lio2009,Sok2013} we artificially broaden the transition region to resolve with our finest grid resolution of $\approx$ 0.001\,\rsun.
+This results in pushing the corona outwards.
 At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region.
-The computational domain for solar corona (SC) extends from 1 to 24 R$_{\odot}$.
-The spherical grid in SC is radially stretched (with a maximum resolution of 0.001 R$_{\odot}$ near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates.
-The Adaptive Mesh Refinement (AMR) resolves the angular size to 1.4$^\circ$ between 1 - 1.7 \rsun and 2.8 \rsun outside.
-The SC component uses about 3 million cells on a $6 \times 8 \times 8$ grid block.
+Consequently, AWSoM results below {$\approx 1.05\,\mrsun$} were not taken into account in this article.
+\\
+The computational domain for solar corona extends from 1 to 24 R$_{\odot}$.
+The spherical grid is radially stretched (with a maximum resolution of $0.001 \, \mrsun$ near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates.
+The Adaptive Mesh Refinement resolves the angular size to 1.4$^\circ$ between $1 - 1.7 \, \mrsun$ and $2.8 \, \mrsun$ outside.
+The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid block.
 Local time stepping is used to speed up the steady state convergence.
@@
 
-{The energy balance given by Equation (\ref{Balance}) is then integrated in the volume of any given coronal magnetic flux tube.
+{The energy balance given by Equation \ref{Balance} is then integrated in the volume of any given coronal magnetic flux tube.
 Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a field-line integrated version of that energy balance is found,
@@
 
-{Note that, for any given field line, all quantities in these two expresions can be computed from the DEMT and AWSoM models through Equations \ref{Fc}-\ref{Er}.
+{Note that, for any given field line, all quantities in these two expresions can be computed {from DEMT model} through Equations \ref{Fc}-\ref{Er}.
 Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to mantain a stable coronal structure.}
-\diego{si vamos a hablar de awsom aca, deberiamos explicar xq no lo analizamos.}
 
@@
 
-{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of {the DEMT} measure $R$ defined by Equation (\ref{R}), at the same three heights shown in Figures \ref{momento1} and \ref{momento2}.
+{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of {the DEMT} measure $R$ defined by Equation \ref{R}, at the same three heights shown in Figures \ref{momento1} and \ref{momento2}.
 In most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$.
@@
 \includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
-\caption{{Carrington maps of the measure $R$ defined by Equation (\ref{R}), for CR-2082 (left panels) and CR-2208 (right panels), at heights $1.025$, $1.065$ and $1.105\,\mrsun$, from top to bottom}.
-}
+\caption{{Carrington maps of the measure $R$ defined by Equation \ref{R}, for CR-2082 (left panels) and CR-2208 (right panels), at heights $1.025$, $1.065$ and $1.105\,\mrsun$, from top to bottom}. }
 \label{carmaps_R_2082_2208}
@@
 
+Figure 1 shows the ADAPT-GONG and GONG global
+maps for CR2208. The two maps show significant dif-
+ferences, especially in the polar regions. We find that
+using ADAPT-GONG maps as input to the AWSoM
+model produces significantly better results in compar-
+ison to using GONG maps. Therefore, in this work
+we use ADAPT-GONG global magnetic maps for both
+CR2208 and CR
+
+Figure \ref{Br} shows carrington maps of radial magnetic field ($Br$) for both rotations at $1.005\, \mrsun$.
+Both maps show a clear dipole.
+The main difference is observed in the polar region and is due to the different types of approaches that use GONG (CR-2082) and ADAPT-GONG (CR-2208.)
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{figs/map_Br_awsom_2082_185_extend_1005_Rsun.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/map_Br_awsom_2208_185_extend_1005_Rsun.pdf}
+\caption{Carrington maps of radial magnetic field obtained with AWSoM at $1.005 \, \mrsun$ for CR-2082 (left) and CR-2208 (right). }
+\label{Br}
+\end{center}
+\end{figure}
+
 {To characterize the DEMT results in different magnetic structures, we traced} $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.
-For both rotations, all legss that meet the criteria listed in Section \ref{trace} were selected.
+For both rotations, all legs that meet the criteria listed in Section \ref{trace} were selected.
 For each leg, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.
@@
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
-\caption{\emph{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR2082 (left) and CR2208 (right).
+\caption{\emph{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR-2082 (left) and CR-2208 (right).
 \emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
@@
 Open legs are indicated in gray color and closed ones in black color.
-For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}).
+For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit}-\ref{Tfit}.
 Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
@@
 {{The sign of the quantity $\phi_c$ depends on that of the conductive flux $F_c$.
-Equations (\ref{Fc}) and (\ref{phi_c}) imply that } down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, {as verified} in Figure \ref{energia_demt}.}
+Equations \ref{Fc} and \ref{phi_c} imply that } down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, {as verified} in Figure \ref{energia_demt}.}
 
@@
 {Being highly axisymmtric target rotations, the longitude-averaged latitudinal variation of the results of both models is an informative way to compare their large-scale structure.
-Such comparison is shown in Figure \ref{perf_lat} at height $1.105\,\mrsun$, with top panels comparing electron density and lower panels electron temperature.
-In these longitude-averaged profiles, longitudes containing ARs or low latitude CHs were excluded.
+Such comparison is shown in Figure \ref{perf_lat} at height $1.105\,\mrsun$, with top panels comparing electron density and mid panels electron temperature.
+\diego{For completeness the variation of $Br$ is added in the lower panels.} In these longitude-averaged profiles, longitudes containing ARs or low latitude CHs were excluded.
 In each panel the averaged latitudinal variation for the DEMT model is shown in solid-line style, while the result for the AWSoM model is shown in dashed-linesyle.
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105.eps}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2082_1005.eps}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2208_1005.eps}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2082_1105.eps}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2208_1105.eps}
 \caption{Longitude-averaged latitudinal dependence of the electron density (top) and temperature (bottom) for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$.
-The left (right) panels correspond to CR-2082 (CR2208).
+The left (right) panels correspond to CR-2082 (CR-2208).
 The vertical black line indicates the longitude-averaged latitudes of the open/closed magnetic boundary in both hemispheres.}
@@
 Note this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
-Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend.}
+Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend.} \diego{With regard to $Br$, it is worth pointing the plateau in the coronal hole region of CR-2082 and the decreasing tendency in the case of CR-2208.}
 
@@
 To characterize the results of the AWSoM model in distinct magnetic structures, its results for electron density and temperature were traced along its magnetic field lines.
-For each field line leg, the results were then fit to Equations (\ref{Nfit}) and (\ref{Tfit}){, considering only data points above heliocentric height $1.055\,\mrsun$.
+For each field line leg, the results were then fit to Equations \ref{Nfit} and \ref{Tfit}{, considering only data points above heliocentric height $1.055\,\mrsun$.
 We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.
@@
 
-\notebyalbert{We could quantify the anti-correlation between the AWSoM terminal speed and the DEMT electron density at the coronal base in the following fashion.
+%\notebyalbert{We could quantify the anti-correlation between the AWSoM terminal speed and the DEMT electron density at the coronal base in the following fashion.
 We can set up starting points at, say, $20\,\mrsun$, every one degree, both in latitude and longitude.
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
-\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6.0\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).} \notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the absolute minimum indicates the location of the HCS at this height.
+\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6.0\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).} %\notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the absolute minimum indicates the location of the HCS at this height.
 I believe it is interesting to compare these two curves with Figure 10.
@@
 In order to quantify this anti-correlation we need to trace the terminal speed and the DEMT $N_e$, which we may need to do with the help of Chip and Nishtha.
-Chip, we can discuss this idea over Skype after Xmas if you are around.}}
+Chip, we can discuss this idea over Skype after Xmas if you are around.}
+}
 \label{perf_lon_vr}
@@
 
-{Based on the magnetic field model of AWSoM model and the results of the DEMT model for electron density and temperature, we classified coronal structures in four different types.
+{Based on the magnetic field of AWSoM model and the results of the DEMT model for electron density and temperature, we classified coronal structures in four different types.
 Smaller legs in the core of the streamer belt are classified in down/up types according to their temperature decreasing/increasing with height (dubbed type 0/I).
@@
 \citet{oran_2015} and \citet{jin_2012} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.} \notebyalbert{Chip, if Section 2.2 explains the most significant improvements of AWSoM since the version used in those references, we can comment on the reason for the improvement here.}
+\diego{Note by Diego: Chip, Nishtha, if you think we can relate some differences or observed trends of AWSoM with the magnetic field, this could be a good place, but I need your insight here.}
 
@@
 Maybe worth mentioning?}
-
-\notebyalbert{Chip: In relation to the previous comment, if the analysis proposed in Figure 15 is carried out we should say something about that here.} d
 

### 2020-01-22 lloveras_2020.tex
figuras retocadas con inkscape añadidas

@@
 
-{
 A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona.
-In previous works, DEMT has been combined with a potential field source surface (PFSS) model such as \citet{huang_2012}, \citet{nuevo_2013} and \citet{nuevo_2015}.
-Recently, \citet{lloveras_2017} combined DEMT with PFSS to study the thermodynamic of the last two solar minima along magnetic field lines and selecting different magnetic structures and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona throgh PFSS magnetic lines.}
+In previous works, DEMT has been combined with a potential field source surface (PFSS) model  (\citet{huang_2012}, \citet{nuevo_2013}).
+Recently, \citet{lloveras_2017} combined DEMT with PFSS to study the thermodynamic of the last two solar minima along magnetic field lines and selecting different magnetic structures and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona throgh PFSS magnetic lines.
+In this article, for first time, we combined the DEMT reconstruction with the magnetic field of a MHD model, as explained in the next paragraph.
 
-{The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) is a three-dimensional (3D) physics-based, data-driven model extending from the upper chromosphere, into the solar corona upto 1 AU (and beyond) \citep{vander_2010, Van2014} and is constantly validated with observations as new improvements are implemented.
+{The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) \diego{within the Space Weather Modeling Framework (SWMF)} is a three-dimensional (3D) physics-based, data-driven model extending from the upper chromosphere, into the solar corona upto 1 AU (and beyond) \citep{vander_2010, Van2014} and is constantly validated with observations as new improvements are implemented.
 DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona.
@@
 
-We carry out a quantitatively detailed comparative {DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 during the Solar Cycle (SC) 23/24 minimum and CR-2208 during the declining fase of SC 24.
-To study CR-2082 data taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B \citep{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) was used {for DEMT, and Global Oscillation Network Group (GONG) magnetogram as the only input for AWSoM}, while data taken by the \textit{Atmospheric Imaging Assembly instrument} {(AIA \citep{lemen_2012})}, on board the \textit{Solar Dynamics Observatory} (SDO) mission was used to study CR-2208 {for DEMT, and Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG magnetograms for AWSoM}.
+We carry out a quantitatively detailed comparative {DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum and CR-2208 (2018, 02 September through 29 September) during the declining fase of SC 24.
+To study CR-2082 with DEMT technique, data taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) were used, and Global Oscillation Network Group (GONG) magnetogram as the only input for AWSoM, while data taken by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} (SDO) mission were used to study CR-2208 {for DEMT, and Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG magnetograms for AWSoM}.
 
-{
-Section \ref{demt} and \ref{awsom} summarizes DEMT technique, AWSoM model, instruments, and datasets we used.
-Section \ref{trace} explains the technique that is used to trace the thermodynamic results along the field lines.
-Section \ref{energia} details the energy model and the loop integrated quantities that are part of the comparative analysis.
+%We carry out a quantitatively detailed comparative DEMT/AWSoM analysis of the Carrington Rotation (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum and CR-2208 (2018, 02 September through 29 September) during the declining fase of SC 24.
+To study CR-2082 with DEMT technique data taken by the Extreme UltraViolet Imager Behind (EUVI-B (Wuelser et al.,2004)) on board the Solar TErrestrial RElations Observatory (STEREO) was used, while data taken by the Atmospheric Imaging Assembly instrument (AIA (Lemen et al., 2012)), on board the Solar Dynamics Observatory (SDO) mission was used to study.
+Global Oscillation Network Group (GONG) synoptic magnetogram was used as the only input for AWSoM model to the same two target rotations.
+In the case of CR-2208 Air Force Data Assimilation Photosph eric flux Transport (ADAPT)-GONG magnetogram map was used as input of the model.
+
+Section \ref{demt} and \ref{awsom} summarizes DEMT technique, and  AWSoM model respectively.
+Section \ref{trace} explains the method that is used to trace the thermodynamic results along the field lines of the magnetic model.
+Section \ref{energia} details the energy model and the loop integrated quantities.
 In Section \ref{demt_res} the quantitative comparative analysis of both rotations using DEMT is described and in Section \ref{awsom_res} AWSoM results are related to the one of DEMT.
 Finally in Section \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.
-}
-\\
+
 %{El parrafo de abajo lo pondria en la seccion 2.1}\\
@@
 
-{We carried out the 3D DEMT reconstruction and MHD modeling of two target Carrington rotations (CR).
-We selected CR-2082 (2009, 05 April through 03 May), a deep minimum rotation between solar cycles (SC) 23 and 24, and CR-2208 (2018, 02 September through 29 September), a rotation during the early declining fase of SC 24.
+{We carried out the 3D DEMT reconstruction of two target Carrington rotations (CR).
+We selected CR-2082, a deep minimum rotation between solar cycles (SC) 23 and 24, and CR-2208, a rotation during the early declining fase of SC 24.
 To study CR-2082 and CR-2208 data taken by the STEREO/EUVI-B and SDO/AIA instruments was used, respectively.
@@
 {The solution of the tomographic problem involves a very large sparse matrix.
-Such type of inversion problems are characterized by spurious high-frequency artifacts in the solution, which can be mitigated through \emph{regularization} techniques \citep{frazin_2000}.
+Such type of inversion problems are characterized by spurious high-frequency artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}.
 In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude.
@@
 
-AWSoM addresses coronal heating by including the non-linear interaction of forward propagating and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
+We perform a MHD modeling of the two target rotations studied with DEMT.
+For this propose we use the MHD coronal model AWSOM which addresses coronal heating by including the non-linear interaction of forward propagating and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
 The model accounts for anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature.
@@
 {For analysis purposes, {the traced magnetic field lines are classified as open or closed according to their full geometry.
-Each closed field} line is further classified as ``small" or ``large", according to its coronal length $L$ being {respectively smaller or larger than the median value of the whole population, which is ${\rm Md}(L)\approx 0.5\,\mrsun$ for both rotations.} Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e.
-their location at $r=1\,\mrsun$) to its apex (i.e., the location of maximum height).}
+Each closed field} line is further classified as ``small" or ``large", according to its coronal length $L$ being {respectively smaller or larger than the median value of the whole population, which is ${\rm Md}(L)\approx 0.5\,\mrsun$ for both rotations.} Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (\textit{i.e.} their location at $r=1\,\mrsun$) to its apex (\textit{i.e.}, the location of maximum height).}
 
@@
 
-{Consider} a simple energy balance for each magnetic flux tube, {in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated {by a} coronal heating power($E_h$) \citep{aschwanden_2004}:
+{Consider} a simple energy balance for each magnetic flux tube, {in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated {by a} coronal heating power ($E_h$) \citep{aschwanden_2004}:
 
@@
 
-{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, i.e.
-$E_c(s)=[1/A(s)]\,{\rm d}[A(s)\,F_c(s)]/{\rm d}s$, where $A(s)$ is the transversal area of the magnetic flux tube at position $s$.
+{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, \textit{i.e.} $E_c(s)=[1/A(s)]\,{\rm d}[A(s)\,F_c(s)]/{\rm d}s$, where $A(s)$ is the transversal area of the magnetic flux tube at position $s$.
 Under a quiescent solar corona plasma regime, the conductive flux is assumed to be dominated by the electron thermal conduction, described by the usual Spitzer model \citep{spitzer_1962}
@@
 
-{Both target rotations are highly axisymmetric, i.e.
-characterized by a high azymuthal symmetry.
+{Both target rotations are highly axisymmetric, \textit{i.e.} characterized by a high azymuthal symmetry.
 Rotation CR-2082} showed two {small} active regions (ARs), both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg${, respectively}.
@@
 \end{figure}
-
-Figure 1 shows the ADAPT-GONG and GONG global
-maps for CR2208. The two maps show significant dif-
-ferences, especially in the polar regions. We find that
-using ADAPT-GONG maps as input to the AWSoM
-model produces significantly better results in compar-
-ison to using GONG maps. Therefore, in this work
-we use ADAPT-GONG global magnetic maps for both
-CR2208 and CR
 
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105.eps}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105.eps}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105.eps}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2082_1105.eps}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2208_1105.eps}
-\caption{Longitude-averaged latitudinal dependence of the electron density (top) and temperature (bottom) for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$.
-The left (right) panels correspond to CR-2082 (CR-2208).
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105_2.pdf}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105_2.pdf}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105_2.pdf}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105_2.pdf}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2082_1105_2.pdf}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2208_1105_2.pdf}
+\caption{Longitude-averaged latitudinal dependence of the electron density (top), temperature (mid) and $Br$ for CR-2082 (blue) and CR-2208 (red) results at $1.105\,\mrsun$.
+Dashed lines correspond to AWSoM results while solid line to DEMT.
 The vertical black line indicates the longitude-averaged latitudes of the open/closed magnetic boundary in both hemispheres.}
@@
 III  & 0&58 &(\Mi&~3\%)  &   8&9 &(\Mi&18\%) &   1&14 &(\Mi&18\%) \\
+\hline   
 \end{tabular}
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995.eps}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995_2.pdf}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995_2.pdf}
 \caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6.0\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).} %\notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the absolute minimum indicates the location of the HCS at this height.
@@
 In comparing the DEMT results obtained for the two selected targets, {we highlight here that} they rely on data provided by two different instruments, {namely EUVI and AIA for CR-2082 and CR-2208, respectively.} In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
-They found that while the density {products are} essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e.
-$\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$.
+They found that while the density {products are} essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, \textit{i.e.} $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$.
 Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was {characterized by temperatures $\approx 10-15\%$ larger relative to CR-2082} throughout the streamer belt region.
@@
 These systematic differences are {around or beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} {estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$}.}
+
+%\diego{As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region.
+The uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), was estimated {at $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$ by \citet{lloveras_2017}}.
+Considering uncertainty levels CR-2208 is characterized by slightly larger temperatures and definitely lower densities.}
 
@@
 For CR-2082, the electron density of both models agree within $\approx 20\%$ {in most regions}, while for CR-2208 the agreement is within $\approx 5\%$.
-{The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations{, with larger discrepancies in the CHs.} This level of agreement between both models is considerably better than that reported in previous works.
-\citet{oran_2015} and \citet{jin_2012} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.} \notebyalbert{Chip, if Section 2.2 explains the most significant improvements of AWSoM since the version used in those references, we can comment on the reason for the improvement here.}
+{The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations{, with larger discrepancies in the CHs.} This level of agreement between both models \diego{(within or slightly above the uncertainty)} is considerably better than that reported in previous works.
+\citet{jin_2012} and \citet{oran_2015} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.} \notebyalbert{Chip, if Section 2.2 explains the most significant improvements of AWSoM since the version used in those references, we can comment on the reason for the improvement here.}
 \diego{Note by Diego: Chip, Nishtha, if you think we can relate some differences or observed trends of AWSoM with the magnetic field, this could be a good place, but I need your insight here.}

### 2020-01-24 lloveras_2020.tex
modificaciones fede

@@
 
-\author[addressref={aff1,aff2},corref,email={albert@iafe.uba.ar}]{\inits{A.M.}\fnm{Alberto M.}~\lnm{V\'asquez}\orcid{0000-0003-3401-6409}}
+\author[addressref={aff1,aff2},email={albert@iafe.uba.ar}]{\inits{A.M.}\fnm{Alberto M.}~\lnm{V\'asquez}\orcid{0000-0003-3401-6409}}
 
-\author[addressref={aff1,aff3},corref,email={federico@iafe.uba.ar}]{\inits{F.A.}\fnm{Federico A.}~\lnm{Nuevo}\orcid{0000-0003-2355-5853}}
+\author[addressref={aff1,aff3},email={federico@iafe.uba.ar}]{\inits{F.A.}\fnm{Federico A.}~\lnm{Nuevo}\orcid{0000-0003-2355-5853}}
 
-\author[addressref={aff1,aff2},corref,email={cmaccormack@iafe.uba.ar}]{\inits{C.}\fnm{Cecilia}~\lnm{Mac Cormack}\orcid{0000-0003-1173-503X}}
+\author[addressref={aff1,aff2},email={cmaccormack@iafe.uba.ar}]{\inits{C.}\fnm{Cecilia}~\lnm{Mac Cormack}\orcid{0000-0003-1173-503X}}
 
-\author[addressref={aff4},corref,email={nishthas@umich.edu}]{\inits{N.}\fnm{Nishtha}~\lnm{Sachdeva}\orcid{0000-0001-9114-6133}}
+\author[addressref={aff4},email={nishthas@umich.edu}]{\inits{N.}\fnm{Nishtha}~\lnm{Sachdeva}\orcid{0000-0001-9114-6133}}
 
-\author[addressref={aff4},corref,email={chipm@umich.edu}]{\inits{W.}\fnm{Ward}~\lnm{Manchester IV}\orcid{0000-0003-0472-9408}}
+\author[addressref={aff4},email={chipm@umich.edu}]{\inits{W.}\fnm{Ward}~\lnm{Manchester IV}\orcid{0000-0003-0472-9408}}
 
-\author[addressref={aff4},corref,email={bartvand@umich.edu}]{\inits{B.}\fnm{Bartholomeus}~\lnm{Van der Holst}\orcid{0000-0001-5260-3944}}
+\author[addressref={aff4},email={bartvand@umich.edu}]{\inits{B.}\fnm{Bartholomeus}~\lnm{Van der Holst}\orcid{0000-0001-5260-3944}}
 
-\author[addressref={aff4},corref,email={rfrazin@umich.edu}]{\inits{R.A.}\fnm{Richard A.}~\lnm{Frazin}\orcid{0000-0002-0281-7677}}
+\author[addressref={aff4},email={rfrazin@umich.edu}]{\inits{R.A.}\fnm{Richard A.}~\lnm{Frazin}\orcid{0000-0002-0281-7677}}
 
@@
 Using solar rotation time series of EUV images taken in channels sensitive to different temperatures, the technique allows calculation of 3D maps of electron density and temperature in the heliocentric height range $1.0\,\mrsun$ to $1.2\,\mrsun$ as summarized in Section \ref{demt}.
-The reader may refer to the recent review by \citet{vasquez_2016} that summarizes the DEMT technique.
+The reader may refer to the review by \citet{vasquez_2016} that describes the DEMT technique and summarizes the principal publications based on it.
 
 A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona.
-In previous works, DEMT has been combined with a potential field source surface (PFSS) model  (\citet{huang_2012}, \citet{nuevo_2013}).
-Recently, \citet{lloveras_2017} combined DEMT with PFSS to study the thermodynamic of the last two solar minima along magnetic field lines and selecting different magnetic structures and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona throgh PFSS magnetic lines.
-In this article, for first time, we combined the DEMT reconstruction with the magnetic field of a MHD model, as explained in the next paragraph.
+In previous works, DEMT has been combined with a potential field source surface (PFSS) model  (\citealt{huang_2012}, \citealt{nuevo_2013}).
+Recently, \citet{lloveras_2017} combined DEMT with PFSS to study the thermodynamic variables along different magnetic structure of the last two solar minima, and selecting different magnetic structures and \citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux at the coronal base that is required to maintain stable the coronal loop structures represented by the PFSS field lines.
+In this article, for first time, we combined the DEMT reconstruction with the magnetic field of a magnetohydrodynamic (MHD) model, as explained in the next paragraph.
 
-{The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) \diego{within the Space Weather Modeling Framework (SWMF)} is a three-dimensional (3D) physics-based, data-driven model extending from the upper chromosphere, into the solar corona upto 1 AU (and beyond) \citep{vander_2010, Van2014} and is constantly validated with observations as new improvements are implemented.
+{The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) \diego{within the Space Weather Modeling Framework (SWMF)} is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, into the solar corona upto 1 AU (and beyond) \citep{vander_2010, Van2014} and is constantly validated with observations as new improvements are implemented.
 DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona.
@@
 We used AWSoM results with two purposes.
-On the one hand to provide thermodynamic results to be contrasted with DEMT, and on the other hand to provide magnetohydrodynamic (MHD) coronal magnetic field model that is used to study thermodynamics along field lines.
+On the one hand to provide thermodynamic results to be compared with those reconstructed by DEMT, and on the other hand to provide MHD coronal magnetic field model that is used to study thermodynamic variables along field lines.
 }
@@
 
-Section \ref{demt} and \ref{awsom} summarizes DEMT technique, and  AWSoM model respectively.
-Section \ref{trace} explains the method that is used to trace the thermodynamic results along the field lines of the magnetic model.
+Section \ref{demt} and \ref{awsom} summarizes DEMT technique and AWSoM model respectively.
+Section \ref{trace} explains the method used to trace the thermodynamic results along the field lines of the magnetic model.
 Section \ref{energia} details the energy model and the loop integrated quantities.
@@
 
-{We carried out the 3D DEMT reconstruction of two target Carrington rotations (CR).
-We selected CR-2082, a deep minimum rotation between solar cycles (SC) 23 and 24, and CR-2208, a rotation during the early declining fase of SC 24.
-To study CR-2082 and CR-2208 data taken by the STEREO/EUVI-B and SDO/AIA instruments was used, respectively.
+{We carried out the 3D DEMT reconstruction of two target CR.
+We selected CR-2082, a deep minimum rotation between SCs 23 and 24, and CR-2208, a rotation during the early declining fase of SC 24.
+To study CR-2082 and CR-2208, as mentioned in Section \ref{intro}, data taken by the STEREO/EUVI-B and SDO/AIA instruments was used, respectively.
 The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package.
@@
 
-In a first step, the time series of EUV images is used to solve a solar rotational tomography (SRT) problem, for each EUV band independently.
+In a first step, the time series of EUV images is used to solve a solar SRT problem, for each EUV band independently.
 As a result, the 3D distribution of the so called \emph{filter band emissivity} (FBE) is determined for each band separately.
@@
 
-{In a second step, the FBE values obtained for all bands in each voxel {of the tomographic grid are used to constrain the determination of the LDEM which, as described in Section \ref{intro}, describes the temperature distribution of the plasma within the individual voxel.} Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}
+{In a second step, the FBE values obtained for all bands in each voxel {of the tomographic grid are used to constrain the determination of the local-DEM (LDEM) which, as described in Section \ref{intro}, describes the temperature distribution of the plasma within the individual voxel.} Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}
 
@@
 \noindent
-{where $K$ is the number EUV bands, and $\TRF^{(k)}$ is the \emph{temperature response function} of the $j$-th detector.
-The TRFs are here computed based on the (known) channel’s passband times the coronal emissivity at that temperature (normalized by the squared electron density).
+{where $K$ is the number EUV bands, and $\TRF^{(k)}$ is the \emph{temperature response function} of the $k$-th detector.
+In this work, the TRFs are computed based on the (known) channel’s passband times the coronal emissivity at that temperature (normalized by the squared electron density).
 The emissivity model used here is provided by the latest version of the CHIANTI atomic database and plasma emission model \citep{delzanna_2015,landi_2013}.}
@@
 Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}.
-These non-reconstructed voxels are indicated {in black color in the latitude-longitude (Carrington) maps of DEMT} reults in Section \ref{resu}.
-
-The cadence of the data time-series is set to 6\,hr.
+These non-reconstructed voxels are indicated {in black color in the latitude-longitude (Carrington) maps of DEMT} results in Section \ref{resu}.
 
 {In this work the cadence of the data time-series was set to 6\,hr and} data from three EUV bands were {used:} 171, 193 and 211 \AA \ in {the} case of AIA, and 171, 195 and 284 \AA \ bands in {the} case of EUVI.
-When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict the tomographic emissivities \citep{frazin_2009,nuevo_2015}.
+When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict the FBEs \citep{frazin_2009,nuevo_2015}.
 In each tomographic voxel the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that allow to best reproduce the three tomographically reconstructed values of FBE in that voxel.
@@
 
-We define next a measure of the accuracy of the LDEM model to predict the tomographic FBEs in each voxel, as
+Next, we define a measure of the accuracy of the LDEM model to predict the tomographic FBEs in each voxel, as
 
@@
 Global maps of the observed photospheric magnetic field are essential for accurate modeling of the solar corona and are the primary input for AWSoM.
-The model use GONG synoptic map as input for CR-2082 (2009-04-05 - 2009-05-03) and ADAPT-GONG global magnetic field map for CR-2208 (2018-09-02 to 2018-09-29).
+The model use GONG synoptic map as input for CR-2082 and ADAPT-GONG global magnetic field map for CR-2208.
 ADAPT-GONG maps are unavailable for CR-2082.
@@
 
-\subsection{{Tracing Results Along Magnetic Fieldlines}}\label{trace}
+\subsection{{Tracing Results Along Magnetic Field lines}}\label{trace}
 
@@
 In the electron temperature fit, $m\,[\MK/\mrsun]$ is the slope and $T_0\,[\MK]$ is the electron temperature at the footpoint of the loop.
-The slope $m$ is the radial gradient of the electron temperature along the loop, which we denote as $m = \dr\Tm$ hereafter, being $\dr\equiv\er\cdot\nabla$ the radial derivative operator, where $\er$ is the heliocentric radial unit vector.
+The slope $m$ estimates the radial gradient of the electron temperature along the loop, which we denote as $m = \dr\Tm$ hereafter, being $\dr\equiv\er\cdot\nabla$ the radial derivative operator, where $\er$ is the heliocentric radial unit vector.
 
@@
 
-{The high temperature of the corona requires heating mechanisms to compensate for the the losses.
-While the vast majority of the existing literature on coronal heating focuses on ARs, some studies have been dedicated to the heating of quiet-Sun regions.
+{The high temperature of the corona requires heating mechanisms to compensate for the energy losses.
+While the vast majority of the existing literature on coronal heating focuses on active regions (ARs), some studies have been dedicated to the heating of quiet-Sun regions.
 In particular,  \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to mantain them stable.
-The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in the previous Section \ref{trace}.}
+The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in Section \ref{trace}.}
 
-{Consider} a simple energy balance for each magnetic flux tube, {in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated {by a} coronal heating power ($E_h$) \citep{aschwanden_2004}:
+{Consider} a static energy balance for each magnetic flux tube, {in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated {by a} coronal heating power ($E_h$) \citep{aschwanden_2004}:
 
@@
 \begin{equation}\label{Er}
-E_r = \int\,\textrm{d}T\,\LDEM(T)\,\Lambda(T)
+E_r = \int\,\textrm{d}T\,\LDEM(T)\,\Lambda(T),
 \end{equation}
@@
 \begin{equation}\label{phi_r}
-\phi_r = \left( \frac{B_0 \ B_L}{B_0 + B_L} \right) \int_{0}^{L} ds \ \frac{E_r(s)}{B(s)}
+\phi_r = \left( \frac{B_0 \ B_L}{B_0 + B_L} \right) \int_{0}^{L} ds \ \frac{E_r(s)}{B(s)},
 \end{equation}
@@
 \begin{equation}\label{phi_c}
-\phi_c = \left( \frac{B_0 \ F_{c,L} - B_L \ F_{c,0}}{B_0 + B_L} \right) 
+\phi_c = \left( \frac{B_0 \ F_{c,L} - B_L \ F_{c,0}}{B_0 + B_L} \right) ,
 \end{equation}
@@
 {Both target rotations are highly axisymmetric, \textit{i.e.} characterized by a high azymuthal symmetry.
-Rotation CR-2082} showed two {small} active regions (ARs), both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg${, respectively}.
+Rotation CR-2082} showed two {small} ARs, both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg${, respectively}.
 {Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$, respectively.}
@@
 \subsection{{Comparison of the DEMT and AWSoM Models}}\label{awsom_res}
+
+To develop a validation of the AWSoM model described in Section \ref{awsom} with the DEMT technique explained in Section \ref{demt}, we perform the AWSoM model to the same two target rotations shown in the previous section.
 

### 2020-01-24 lloveras_2020.tex
agregadas correcciones de Chip

@@
 \begin{abstract}
-Observational techniques play an essential role in advancing our understanding of the physics of the solar corona, providing in particular validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere.
+Observational techniques play an essential role in advancing our understanding of the physical processes governing the solar corona, providing in particular, validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere.
 Solar rotational tomography is currently the sole observational technique that provides a 3D quantitative description of the solar corona at a global scale.
-Based on {extreme ultraviolet} data of space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$.
-We carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework.
+Based on {extreme ultraviolet} images gathered by space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$.
+We carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) developed at the University of Michigan as a component of the Space Weather Modeling Framework.
 Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the declining} phase of SC 24.
 The 3D tomographic and MHD models are analysed and compared in distinct coronal magnetic structures.
-{We report in quantitative detail on the 3D termodinamic structure of the inner corona as revealed by the DEMT analysis.
+{We report in quantitative detail on the 3D thermodynamic structure of the inner corona as revealed by the DEMT analysis.
 We show in particular the existence of diverse types of temperature structures in the low and mid latitudes of the streamer belt, and that the heating energy required to keep them stable may be accounted for by Alfvén waves.
@@
 
-Being the {region} where the solar atmosphere is {heated, solar wind accelerated}, and where impulsive events such as solar flares and coronal mass ejections are energized, observation and modeling of the solar corona are tasks of great relevance to improve our understanding of the Sun-Earth environment.
-To advance our knowledge of the physics of the solar corona, as well as to improve its three-dimensional (3D) models, information derived from observational data plays a key role.
-Solar rotational tomography (SRT) is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar corona at a global scale.
+Being the {region} where the solar atmosphere is {heated, the solar wind accelerated}, and where impulsive events such as solar flares and coronal mass ejections are energized, observing and modeling of the solar corona are of great relevance to improving our understanding of the Sun-Earth environment.
+To advance our knowledge of the physics of the solar corona, as well as to improve and validate three-dimensional (3D) models, information derived from observational data plays a key role.
+Solar rotational tomography (SRT) is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar corona on a global scale.
 
@@
 
-{To study the global coronal 3D structure, SRT proved to be a powerful tool.
-Based on solar rotation, allow instruments to compile a time series of images that cover the entire corona collecting data from all lines of sight.} In particular, differential emission measure tomography (DEMT), based on time-series of extreme ultraviolet (EUV) images, allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the {quiet-Sun low corona at a global scale.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}.
+{To study the global coronal 3D structure, SRT has proven to be a powerful tool.
+Solar rotations allows instruments to compile a time series of images that cover the entire corona collecting data from many lines of sight.} In particular, differential emission measure tomography (DEMT), based on time-series of extreme ultraviolet (EUV) images, allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the {quiet-Sun low corona at a global scale.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}.
 Using solar rotation time series of EUV images taken in channels sensitive to different temperatures, the technique allows calculation of 3D maps of electron density and temperature in the heliocentric height range $1.0\,\mrsun$ to $1.2\,\mrsun$ as summarized in Section \ref{demt}.
 The reader may refer to the review by \citet{vasquez_2016} that describes the DEMT technique and summarizes the principal publications based on it.
+\diego{chip propuso eliminar la cita de frazin 2009, no se si se confundio, xq la cita de abajo es muy similar.}
 
@@
 In previous works, DEMT has been combined with a potential field source surface (PFSS) model  (\citealt{huang_2012}, \citealt{nuevo_2013}).
-Recently, \citet{lloveras_2017} combined DEMT with PFSS to study the thermodynamic variables along different magnetic structure of the last two solar minima, and selecting different magnetic structures and \citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux at the coronal base that is required to maintain stable the coronal loop structures represented by the PFSS field lines.
+Recently, \citet{lloveras_2017} combined DEMT with PFSS to study the thermodynamics of different magnetic structures along field lines found in the last two solar cycles.
+\citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux at the coronal base that is required to maintain stable the coronal loop structures represented by the PFSS field lines.
 In this article, for first time, we combined the DEMT reconstruction with the magnetic field of a magnetohydrodynamic (MHD) model, as explained in the next paragraph.
 
-{The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) \diego{within the Space Weather Modeling Framework (SWMF)} is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, into the solar corona upto 1 AU (and beyond) \citep{vander_2010, Van2014} and is constantly validated with observations as new improvements are implemented.
+{The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) \diego{within the Space Weather Modeling Framework (SWMF)} is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to 1 AU (and beyond) \citep{vander_2010, Van2014}.
+Is constantly being validated with observations as new improvements are implemented.
 DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona.
 More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a globally fashion, obtaining an agreement within 20\%.
-We used AWSoM results with two purposes.
-On the one hand to provide thermodynamic results to be compared with those reconstructed by DEMT, and on the other hand to provide MHD coronal magnetic field model that is used to study thermodynamic variables along field lines.
+here, we use AWSoM results with two purposes: On the one hand to provide thermodynamic results to be compared with those reconstructed by DEMT, and on the other hand to provide a MHD coronal magnetic field model that is used to study thermodynamic variables along field lines.
 }
 
-We carry out a quantitatively detailed comparative {DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum and CR-2208 (2018, 02 September through 29 September) during the declining fase of SC 24.
-To study CR-2082 with DEMT technique, data taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) were used, and Global Oscillation Network Group (GONG) magnetogram as the only input for AWSoM, while data taken by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} (SDO) mission were used to study CR-2208 {for DEMT, and Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG magnetograms for AWSoM}.
+We carry out a quantitatively detailed comparative {DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum and CR-2208 (2018, 02 September through 29 September) during the declining phase of SC 24.
+To study CR-2082 with the DEMT technique, data taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) are used, and Global Oscillation Network Group (GONG) magnetogram are used as the only input for AWSoM.
+For CR-2208 data for DEMT are taken by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} (SDO) mission while Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG magnetograms are used for AWSoM.
 
@@
 Section \ref{energia} details the energy model and the loop integrated quantities.
-In Section \ref{demt_res} the quantitative comparative analysis of both rotations using DEMT is described and in Section \ref{awsom_res} AWSoM results are related to the one of DEMT.
+In Section \ref{demt_res}, the quantitative comparative analysis of both rotations using DEMT is described and in Section \ref{awsom_res} AWSoM and DEMT results are compared.
 Finally in Section \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.
@@
 
-{We carried out the 3D DEMT reconstruction of two target CR.
-We selected CR-2082, a deep minimum rotation between SCs 23 and 24, and CR-2208, a rotation during the early declining fase of SC 24.
-To study CR-2082 and CR-2208, as mentioned in Section \ref{intro}, data taken by the STEREO/EUVI-B and SDO/AIA instruments was used, respectively.
+{We carry out the 3D DEMT reconstruction of two target CRs.
+We select CR-2082, a deep minimum rotation between SCs 23 and 24, and CR-2208, a rotation during the early declining fase of SC 24.
+To study CR-2082 and CR-2208, as mentioned in Section \ref{intro}, data taken by the STEREO/EUVI-B and SDO/AIA instruments are used, respectively.
 The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package.
@@
 
-{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we opted to only use off-limb data.
+{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we \diego{opt} to only use off-limb data.
 In this way, the smallest scale and brighter coronal features seen on disk (most typically in the 171\AA\ band) are not included.
@@
 Sencondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume.
-As a result, coronal dynamics induced artifacts are reduced compared to previous DEMT reconstructions.}
+As a result, coronal dynamics \diego{induce} artifacts are reduced compared to previous DEMT reconstructions.}
 
-{The solution of the tomographic problem involves a very large sparse matrix.
-Such type of inversion problems are characterized by spurious high-frequency artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}.
+{The solution of the tomographic problem involves \diego{inversion of} a very large sparse matrix.
+Such inversion problems are characterized by spurious high-frequency artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}.
 In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude.
@@
 
-{We summarize next the main aspects of DEMT required for the analysis of this work. We refer the reader to \citet{frazin_2009} for a full description of the technique.}
-
-In a first step, the time series of EUV images is used to solve a solar SRT problem, for each EUV band independently.
+\diego{We summarize next the main aspects of DEMT required for the analysis of this work.} In a first step, the time series of EUV images is used to solve a solar SRT problem, for each EUV band independently.
 As a result, the 3D distribution of the so called \emph{filter band emissivity} (FBE) is determined for each band separately.
@@
 Line-of-sight (LOS) integration of the FBE provides synthetic images that can be quantitatively compared to the real data in the time series.
-To find the FBE, the tomographic problem is posed a global optimization problem in which the quadratic norm of the difference between all {pairs of synthetic and real images is minimized.}
+To find the FBE, the tomographic problem is posed as a global optimization problem in which the quadratic norm of the difference between all {pairs of synthetic and real images is minimized.}
+
+Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}.
+These non-reconstructed voxels are indicated {in black color in the latitude-longitude (Carrington) maps of DEMT} results in Section \ref{resu}.
 
@@
 
-Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}.
-These non-reconstructed voxels are indicated {in black color in the latitude-longitude (Carrington) maps of DEMT} results in Section \ref{resu}.
-
 {In this work the cadence of the data time-series was set to 6\,hr and} data from three EUV bands were {used:} 171, 193 and 211 \AA \ in {the} case of AIA, and 171, 195 and 284 \AA \ bands in {the} case of EUVI.
 When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict the FBEs \citep{frazin_2009,nuevo_2015}.
-In each tomographic voxel the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that allow to best reproduce the three tomographically reconstructed values of FBE in that voxel.
+In each tomographic voxel, the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that best reproduce the three tomographically reconstructed values of FBE in that voxel.
 
@@
 {being the} average relative difference between the tomographic and the synthetic FBEs.
-{The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.}
+{The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.} \diego{For a full description of the technique we refer the reader to \citet{frazin_2009}.}
 
@@
 
-We perform a MHD modeling of the two target rotations studied with DEMT.
-For this propose we use the MHD coronal model AWSOM which addresses coronal heating by including the non-linear interaction of forward propagating and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
+We perform MHD modeling of the two target rotations studied with DEMT.
+For this propose we use the MHD coronal model AWSOM which addresses coronal heating by including the non-linear interaction of forward and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
 The model accounts for anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature.
@@
 The unobserved polar fields in GONG are estimated by fitting a polynomial to neighboring observed fields.
-An improvement over these maps is provided by the ADAPT model \citep{Wor2000} which creates synchronic-synoptic maps that uses supergranulation, meridional circulation, flux-transport and differential rotation to evolve the magnetic field on the Sun for better estimates of the unobserved photospheric field \citep{Arg2010, Hen2012}.
-In AWSoM, the 2D radial photospheric field is converted to 3D magnetic field using the PFSS model which specifies the initial condition.
+An improvement over these maps is provided by the ADAPT model \citep{Wor2000}, which creates synchronic-synoptic maps by incorporating supergranulation, meridional circulation, and differential rotation to evolve the magnetic field.
+These maps provide a physics based description of the unobserved polar fields \citep{Arg2010, Hen2012}.
+In AWSoM, the 2D radial photospheric field is used as a boundary condition for the 3D PFSS model which, in turn is used to specify the initial condition.
 We take the source surface to be at $2.5 \, \mrsun$ and the magnetic field is radial at this height.
@@
 To resolve these gradients excessive numerical resources are required.
-As described in \citet{Lio2009,Sok2013} we artificially broaden the transition region to resolve with our finest grid resolution of $\approx$ 0.001\,\rsun.
-This results in pushing the corona outwards.
+As described in \citet{Lio2009} and \citet{Sok2013}, we artificially broaden the transition region to resolve with our finest grid resolution of $\le$ 0.001\,\rsun.
+This broadening pushes the corona outwards.
 At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region.
@@
 In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, for a total of $96,000$ starting points.
+\diego{tecnicamente 97,200 = 90*180*6 como indica Chip, pero hay lineas que no son ni 0 ni 1 ni 2 y esas son las aprox 1200 que faltan!.
+yo pondria 97200 y evitaria aclarar.}
 
@@
 Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one).
-To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it.
+%To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it.
  As a result, for each field line one data point per tomographic cell {is obtained.
@@
 While the vast majority of the existing literature on coronal heating focuses on active regions (ARs), some studies have been dedicated to the heating of quiet-Sun regions.
-In particular,  \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to mantain them stable.
+In particular,  \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to mantain stability.
 The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in Section \ref{trace}.}
@@
 Radiative power depends on the amount of plasma in certain temperatures that can radiate.
-The model estimate it by integrating the squared density multiplied by a radiative loss function $\Lambda(T)$.
+
+\diego{The electrons collide with ionized metals, completely dominating the EUV radiation.
+Therefore the radiative power depends on the electronic density.} The flux tube model estimates by integrating the squared density multiplied by a radiative loss function $\Lambda(T)$.
 This function depends on plasma temperature and is calculated by the atomic database and the plasma emission model from CHIANTI \citep{delzanna_2015}.
@@
 \begin{equation}\label{Er}
-E_r = \int\,\textrm{d}T\,\LDEM(T)\,\Lambda(T),
+E_r = \int\,\textrm{d}T\,\LDEM(T)\,\Lambda(T).
 \end{equation}
@@
 
-{Note that, for any given field line, all quantities in these two expresions can be computed {from DEMT model} through Equations \ref{Fc}-\ref{Er}.
+\diego{where $B_0$ and $B_L$ are the values of the magnetic field at the footpoints of the loop in the coronal base.} {Note that, for any given field line, all quantities in these two expresions can be computed {from DEMT model} through Equations \ref{Fc}-\ref{Er}.
 Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to mantain a stable coronal structure.}
@@
 
-{The magnetically open and closed regions of the AWSoM model are associated to Coronal holes (CHs) and the equatorial streamer belt, respectively.
-Consistently with that, the {location of the} open/closed boundaries derived from the respective AWSoM model quite accurately matchs {the regions of the DEMT maps which exhibit the strongest latitudinal gradient of both the electron density and temperature.}}
+{The magnetically open and closed regions of the AWSoM model are associated with Coronal holes (CHs) and the equatorial streamer belt, respectively.
+The {location of the} open/closed boundaries derived from the respective AWSoM model quite accurately matchs {the regions of the DEMT maps, which exhibit the strongest latitudinal gradient of both the electron density and temperature.}}
 
@@
 
-{{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively larger values of density and temperature in comparison to the CHs.
+{{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively higher densities and temperatures in comparison to the CHs.
 They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 24 and 25}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the declining phase of {SC 25, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious.

### 2020-01-25 lloveras_2020.tex
cambios de nishtha

@@
 
-We perform MHD modeling of the two target rotations studied with DEMT.
-For this propose we use the MHD coronal model AWSOM which addresses coronal heating by including the non-linear interaction of forward and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
-The model accounts for anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature.
-The dissipated turbulent energy is distributed over these three temperatures based on the theories of linear wave damping and stochastic heating.
-AWSoM does not use ad-hoc heating functions and accounts for both collisional and collision-less electron heat conduction.
-The Alfv\'{e}n wave number associated with the damping rate is determined by the critical balance condition which uses the cascade time of the minor wave \citep{Lit2007} instead of the previously used cascade time of the major wave \citep{Cha2011, Van2014}.
-This energy partitioning, in the improved version of AWSoM, leads to more electron heating and less solar wind acceleration.% \diego{falta cita}%\citep{Van2019b}.
-To solve anisotropic MHD equations with radiative cooling, heat conduction and wave turbulence, AWSoM uses the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme.
-MHD equations employed within the AWSoM model are detailed in \citet{Van2014}.
-Recently, \citet{sachdeva_2019} validated the AWSoM simulation results with a suite of observations from near the Sun upto 1 AU for solar minimum conditions.
-
-Global maps of the observed photospheric magnetic field are essential for accurate modeling of the solar corona and are the primary input for AWSoM.
-The model use GONG synoptic map as input for CR-2082 and ADAPT-GONG global magnetic field map for CR-2208.
-ADAPT-GONG maps are unavailable for CR-2082.
-GONG provides synoptic full disk line-of-sight surface map of the radial magnetic field component.
-The unobserved polar fields in GONG are estimated by fitting a polynomial to neighboring observed fields.
-An improvement over these maps is provided by the ADAPT model \citep{Wor2000}, which creates synchronic-synoptic maps by incorporating supergranulation, meridional circulation, and differential rotation to evolve the magnetic field.
-These maps provide a physics based description of the unobserved polar fields \citep{Arg2010, Hen2012}.
-In AWSoM, the 2D radial photospheric field is used as a boundary condition for the 3D PFSS model which, in turn is used to specify the initial condition.
-We take the source surface to be at $2.5 \, \mrsun$ and the magnetic field is radial at this height.
-The radial component specifies the boundary condition.
-%ADAPT-GONG maps have multiple realizations based on how the polar fields are filled. We use realization 5 for CR2208.
-Based on \citet{Cha2011} the stochastic heating exponent is taken to be 0.21 and amplitude is 0.18 to account for energy partioning between electrons and protons.
-The Alfv\'{e}n wave energy boundary condition is given by the poynting flux (S$_{A}$) of the outgoing wave $(\frac{S_{A}}{B})_{\odot} = 1.0\times 10^{6}$ Wm$^{-2}$T$^{-1}$ and the correlation length of the Alfv\'{e}n waves is set to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$ m$\sqrt{T}$.
-
-The base of the transition region (TR) forms the inner boundary of the model (at $\approx$1.0\,\rsun).
-To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot}=2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K.
+We compare the DEMT analysis of the two Carrington rotations with the MHD model simulations results from the Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the SWMF. 
+AWSoM is a three-temperature, MHD model of the solar corona and inner heliosphere which provides the 3D distribution of density and temperatures as well as the 3D magnetic structure and velocity of the solar wind.
+In this work, we use AWSoM model simulated results below 1.25 $\mrsun$ to correspond to the DEMT analysis region.
+AWsoM addresses the heating of the solar corona by including the non-linear interaction of forward and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
+This dissipated turbulent energy is distributed over anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature using theories of linear wave damping and stochastic heating.
+AWSoM accounts for both collisional and collision-less electron heat conduction and does not use ad-hoc heating functions.
+The extended MHD equations including radiative cooling, heat conduction and wave turbulence within AWSoM \citep{Van2014} are solved using the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme.
+In the previous version of the model, the cascade time of the major wave was used to determine the wave damping rate \citep{Cha2011, Van2014}.
+However, we improve the energy partitioning by using the Alfv\'{e}n wave number associated with the damping rate as determined by the critical balance condition, which uses the cascade time of the minor wave \citep{Lit2007}.
+This leads to more electron heating and less solar wind acceleration \citep{Van2019b}.
+
+The inner boundary of AWSoM is located at the base of the transition region (at $\approx$1.0\,$\mrsun$).
+In reality, the thin transition region has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses.
+To resolve these gradients in a global model would require excessive numerical resources.
+As described in \citet{Lio2009} and \citet{Sok2013} we artificially broaden the transition region to resolve with our finest grid resolution of 0.001\,$\mrsun$.
+To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot} =2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K.
 The upper chromosphere is required to extend radially for the density to fall rapidly to correct (lower) values \citep{Lio2009}.
-In reality, the thin transition has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses.
-To resolve these gradients excessive numerical resources are required.
-As described in \citet{Lio2009} and \citet{Sok2013}, we artificially broaden the transition region to resolve with our finest grid resolution of $\le$ 0.001\,\rsun.
-This broadening pushes the corona outwards.
 At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region.
-Consequently, AWSoM results below {$\approx 1.05\,\mrsun$} were not taken into account in this article.
-\\
+Since the broadening of the transition region pushes the corona outwards, AWSoM results below 1.05 $\mrsun$ were not taken into account in this article.
+
+To drive our solar corona model, accurate estimates of the photospheric magnetic field of the Sun form the primary input.
+Synoptic magnetograms are used to specify the initial and the boundary conditions of the magnetic field in AWSoM.
+We use the PFSS model to extrapolate the 3D magnetic field (from the 2D photospheric magnetic field maps) using spherical harmonics.
+The source surface is taken to be at 2.5 $\mrsun$.
+The Global Oscillation Network Group (GONG) provides synoptic full-disk surface maps of the radial magnetic field component of the Sun.
+However, since the polar regions are not well observed from the ecliptic, GONG estimates the polar fields by fitting a polynomial to neighboring observed latitudes, which might lead to inaccuracies.
+An improvement over these maps is provided by the Air Force Data Assimilation Photospheric Flux Transport (ADAPT) model \citep{Wor2000}, which creates synchronic-synoptic maps by incorporating supergranulation, meridional circulation, and differential rotation.
+These maps provide a physics-based description of the unobserved polar magnetic fields \citep{Arg2010, Hen2012}.
+In this work, we use the GONG synoptic map as input for CR-2082 (ADAPT-GONG maps are unavailable for CR-2082) and the ADAPT-GONG global magnetic field map for CR-2208.
+For CR-2082, the magnetic field from the GONG map is scaled up by a factor of 1.85 (for Br$<$5 G) while no modification is done for the ADAPT-GONG map for CR-2208.
+The AWSoM steady-state simulation set-up and input parameters for both rotations are described below.
+
+To account for the energy partitioning between electrons and protons, based on \citet{Cha2011}, we set the stochastic heating exponent to be 0.21 and the amplitude equal to 0.18 for both rotations.
+The boundary condition for Alfv\'{e}n wave energy is given by the poynting flux (S$_{A}$) of the outgoing wave.
+$(\frac{S_{A}}{B})_{\odot} = 1.1\times 10^{6}$ Wm$^{-2}$T$^{-1}$ and  $1.0\times 10^{6}$ Wm$^{-2}$T$^{-1}$ for CR-2082 and CR-2208 respectively.
+$B_{\odot}$ is the filed strength at the inner boundary.
+The correlation length of the Alfv\'{e}n waves is set to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$ m$\sqrt{T}$.
+%ADAPT-GONG maps have multiple realizations based on how the polar fields are filled. We use realization 5 for CR-2208.
 The computational domain for solar corona extends from 1 to 24 R$_{\odot}$.
-The spherical grid is radially stretched (with a maximum resolution of $0.001 \, \mrsun$ near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates.
-The Adaptive Mesh Refinement resolves the angular size to 1.4$^\circ$ between $1 - 1.7 \, \mrsun$ and $2.8 \, \mrsun$ outside.
-The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid block.
+The spherical grid in the solar corona is radially stretched (with a maximum resolution of 0.001 R$_{\odot}$ near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates.
+The Adaptive Mesh Refinement (AMR) resolves the angular cell size to 1.4$^\circ$ between 1 - 1.7 $\mrsun$ and 2.8 $\mrsun$ outside.
+The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082.
 Local time stepping is used to speed up the steady state convergence.
-AWSoM simulation results provide the 3D distribution of density and temperature in addition to the 3D magnetic structure and velocity of the solar wind.
+The AWSoM simulation results of the structure of the solar corona for solar minimum conditions represented by CR-2082 and CR-2208 are compared to the DEMT as described in the results section.
 
@@
 {Both target rotations are highly axisymmetric, \textit{i.e.} characterized by a high azymuthal symmetry.
-Rotation CR-2082} showed two {small} ARs, both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg${, respectively}.
-{Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$, respectively.}
+Rotation CR-2082} showed two {small} ARs, both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg$  \diego{(too smal to be registered)}.
+{Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$ \diego{(NOAA 12722, 12721)}.}
 
@@
 {{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively higher densities and temperatures in comparison to the CHs.
-They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 24 and 25}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the declining phase of {SC 25, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious.
-This thermodynamic structure} of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
+They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between \diego{SCs 23 and 24}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the declining phase of \diego{SC 24}, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious.
+This thermodynamic structure of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
 
@@
 {Type 0 (small down) legs mainly populate the equatorial latitudes.
-This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level {around the solar minimum between SCs 24 and 25} by \citet{nuevo_2013}.
+This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the solar minimum between \diego{SCs 23 and 24} by \citet{nuevo_2013}.
 Later on, \citet{lloveras_2017} showed {that} equatorial down loops in streamers were also to be found in the deep minimum between SCs {23 and 24}.

### 2020-01-27 lloveras_2020.tex
Version Albert Jan26-2020-21:19

@@
 \begin{abstract}
-Observational techniques play an essential role in advancing our understanding of the physical processes governing the solar corona, providing in particular, validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere.
-Solar rotational tomography is currently the sole observational technique that provides a 3D quantitative description of the solar corona at a global scale.
-Based on {extreme ultraviolet} images gathered by space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$.
-We carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) developed at the University of Michigan as a component of the Space Weather Modeling Framework.
-Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the declining} phase of SC 24.
-The 3D tomographic and MHD models are analysed and compared in distinct coronal magnetic structures.
+Observational techniques play an essential role in advancing our understanding of the physical processes governing the solar corona, providing in \albert{particular validation} data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere.
+Solar rotational tomography is currently the sole observational technique \albert{able to provide} a 3D quantitative description of the solar corona at a global scale.
+Based on {extreme ultraviolet} images \albert{of space} borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$.
+We carry out a study of the corona \albert{through DEMT} reconstructions \albert{and MHD simulations, using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) developed at the University of Michigan as a component of the Space Weather Modeling Framework.
+\albert{Two target} rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the \albert{end of the} declining} phase of SC 24.
+The 3D \albert{DEMT} and MHD models are analysed and compared in distinct coronal magnetic structures.
 {We report in quantitative detail on the 3D thermodynamic structure of the inner corona as revealed by the DEMT analysis.
-We show in particular the existence of diverse types of temperature structures in the low and mid latitudes of the streamer belt, and that the heating energy required to keep them stable may be accounted for by Alfvén waves.
-We show that the latest version of the AWSoM model results agree with DEMT reconstructions to within a $\approx 20\%$ accuracy or better.
-We report on aspects of the AWSoM model that could be improved to better reproduce the DEMT results, in particular concerning the source region of the fast/slow solar winds.}
+We \albert{show the} existence of diverse types of temperature structures in the low and mid latitudes of the \albert{streamer belt.
+We estimate} the heating energy required to keep them \albert{stable, which we argue may} be accounted for by Alfvén waves.
+\albert{We also show that results of the latest version of the AWSoM model overal} agree with DEMT \albert{reconstructions within a $\approx 20\%$ accuracy.
+We highlight some details of the AWSoM model that should} be improved to better reproduce \albert{tomographic} results, in particular concerning the source region of the \albert{fast and slow components of the solar wind.}}
 \end{abstract}
@@
 Being the {region} where the solar atmosphere is {heated, the solar wind accelerated}, and where impulsive events such as solar flares and coronal mass ejections are energized, observing and modeling of the solar corona are of great relevance to improving our understanding of the Sun-Earth environment.
-To advance our knowledge of the physics of the solar corona, as well as to improve and validate three-dimensional (3D) models, information derived from observational data plays a key role.
-Solar rotational tomography (SRT) is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar corona on a global scale.
+To advance our knowledge of the physics of the solar corona, as well as \albert{to enhance} and validate three-dimensional (3D) models, information derived from observational data plays a key role.
+Solar rotational tomography (SRT) is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar \albert{corona at a global} scale.
 
-%\noindent\notebyalbert{Here we will put in a couple of paragraphs summarizing what SRT and DEMT are, including references and defining the accronyms in the process.
-We should refer to minima in particular.
-We should mention the instruments and missions we use as data for DEMT, and define their accronyms too.
-Also one paragraph on the SWMF/AWSoM model, including references and defining the accronyms on the way.}
+To study the \albert{3D structure of the quiet-Sun global corona,} SRT has proven to be a powerful tool.
+\albert{In SRT, solar rotation is taken advantage of, so that instruments gather time series of images covering all viewing angles of the solar corona.
+This allows posing an inversion problem to solve for the uncknown 3D distribution of specific quantities of the solar corona.
+Based on extreme ultraviolet EUV images, taken in several channels sensitive to different temperatures, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM).
+The final product of DEMT is in the form of 3D maps of electron density and temperature, covering the range of heliocentric heights $\lesssim 1.25\,\mrsun$.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}.
+\albert{A recent review on DEMT was published by \citet{vasquez_2016}.
+The technique is summarized in Section \ref{demt}.}
 
-{To study the global coronal 3D structure, SRT has proven to be a powerful tool.
-Solar rotations allows instruments to compile a time series of images that cover the entire corona collecting data from many lines of sight.} In particular, differential emission measure tomography (DEMT), based on time-series of extreme ultraviolet (EUV) images, allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the {quiet-Sun low corona at a global scale.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}.
-Using solar rotation time series of EUV images taken in channels sensitive to different temperatures, the technique allows calculation of 3D maps of electron density and temperature in the heliocentric height range $1.0\,\mrsun$ to $1.2\,\mrsun$ as summarized in Section \ref{demt}.
-The reader may refer to the review by \citet{vasquez_2016} that describes the DEMT technique and summarizes the principal publications based on it.
-\diego{chip propuso eliminar la cita de frazin 2009, no se si se confundio, xq la cita de abajo es muy similar.}
+\albert{The combination of DEMT with global magnetic models provides insight} into the 3D thermodynamical structure of the global quiet-Sun corona.
+\albert{DEMT was first combined with a potential field source surface (PFSS) model by \citet{huang_2012} and \citet{nuevo_2013}.
+More recently,} \citet{lloveras_2017} combined DEMT with PFSS \albert{models to study the thermodynamics of the global solar corona in specific magnetic structures for two target rotations selected from the last two solar minimum epochs.
+Also combining DEMT with a PFSS model,} \citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux \albert{required at the coronal base in order to maintain stable coronal loops}.
+In this article, \albert{DEMT is first combined with the magnetic field of a magnetohydrodynamic (MHD) model.}
 
-A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona.
-In previous works, DEMT has been combined with a potential field source surface (PFSS) model  (\citealt{huang_2012}, \citealt{nuevo_2013}).
-Recently, \citet{lloveras_2017} combined DEMT with PFSS to study the thermodynamics of different magnetic structures along field lines found in the last two solar cycles.
-\citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux at the coronal base that is required to maintain stable the coronal loop structures represented by the PFSS field lines.
-In this article, for first time, we combined the DEMT reconstruction with the magnetic field of a magnetohydrodynamic (MHD) model, as explained in the next paragraph.
+The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space \albert{Wea\-ther} Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to \albert{1 AU and beyond} \citep{vander_2010, Van2014}.
+\albert{The single data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation.
+As new improvements are implemented, the model is continuously being validated with observations.} DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona.
+More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a globally fashion, obtaining an agreement within 20\%.
 
-{The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) \diego{within the Space Weather Modeling Framework (SWMF)} is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to 1 AU (and beyond) \citep{vander_2010, Van2014}.
-Is constantly being validated with observations as new improvements are implemented.
-DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona.
-More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a globally fashion, obtaining an agreement within 20\%.
-here, we use AWSoM results with two purposes: On the one hand to provide thermodynamic results to be compared with those reconstructed by DEMT, and on the other hand to provide a MHD coronal magnetic field model that is used to study thermodynamic variables along field lines.
-}
+\albert{In this work, the AWSoM model is used with two purposes.
+Firstly, to provide an MHD model of the coronal magnetic field to be used to study the DEMT results along magnetic field lines.
+Secondly, to provide thermodynamic results to be compared with those reconstructed by DEMT.}
 
-We carry out a quantitatively detailed comparative {DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum and CR-2208 (2018, 02 September through 29 September) during the declining phase of SC 24.
-To study CR-2082 with the DEMT technique, data taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) are used, and Global Oscillation Network Group (GONG) magnetogram are used as the only input for AWSoM.
-For CR-2208 data for DEMT are taken by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} (SDO) mission while Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG magnetograms are used for AWSoM.
+\albert{Combining the DEMT and AWSoM models, we carry out a detailed quantitatively analysis of two target rotations.
+We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during \albert{the end of the declining} phase of SC 24.
+\albert{In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} \albert{(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG).
+In the case of CR-2208, the DEMT analysis is based in data taken} by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} \albert{(SDO), while the AWSoM model uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}
 
-%We carry out a quantitatively detailed comparative DEMT/AWSoM analysis of the Carrington Rotation (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum and CR-2208 (2018, 02 September through 29 September) during the declining fase of SC 24.
-To study CR-2082 with DEMT technique data taken by the Extreme UltraViolet Imager Behind (EUVI-B (Wuelser et al.,2004)) on board the Solar TErrestrial RElations Observatory (STEREO) was used, while data taken by the Atmospheric Imaging Assembly instrument (AIA (Lemen et al., 2012)), on board the Solar Dynamics Observatory (SDO) mission was used to study.
-Global Oscillation Network Group (GONG) synoptic magnetogram was used as the only input for AWSoM model to the same two target rotations.
-In the case of CR-2208 Air Force Data Assimilation Photosph eric flux Transport (ADAPT)-GONG magnetogram map was used as input of the model.
-
-Section \ref{demt} and \ref{awsom} summarizes DEMT technique and AWSoM model respectively.
-Section \ref{trace} explains the method used to trace the thermodynamic results along the field lines of the magnetic model.
-Section \ref{energia} details the energy model and the loop integrated quantities.
-In Section \ref{demt_res}, the quantitative comparative analysis of both rotations using DEMT is described and in Section \ref{awsom_res} AWSoM and DEMT results are compared.
-Finally in Section \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.
-
-%{El parrafo de abajo lo pondria en la seccion 2.1}\\
-%In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid.
-The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions.
-The cadence of the data time-series is set to 6\,hr.
-The main product of the technique is the local DEM (LDEM) at each volxel, a measure of the temperature distribution of the plasma contained in it.
+Section \ref{demt} and \ref{awsom} \albert{summarize the DEMT technique and the AWSoM model, respectively.} Section \ref{trace} \albert{details} the method used to trace \albert{the DEMT} results along the field lines of the magnetic model.
+Section \ref{energia} details \albert{the method that allows determination of the energy input flux at the coronal base.} In Section \ref{demt_res} the quantitative \albert{detailed DEMT analysis of both target rotations is shown,} and in Section \ref{awsom_res} the AWSoM and DEMT results are compared.
+\albert{Finally, Section} \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.
 
@@
 
-{We carry out the 3D DEMT reconstruction of two target CRs.
-We select CR-2082, a deep minimum rotation between SCs 23 and 24, and CR-2208, a rotation during the early declining fase of SC 24.
-To study CR-2082 and CR-2208, as mentioned in Section \ref{intro}, data taken by the STEREO/EUVI-B and SDO/AIA instruments are used, respectively.
-The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package.
-For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.}
+\albert{As detailed in Section \ref{intro}, target rotations CR-2082 and CR-2208 were selected to carry out DEMT reconstructions, based on data taken by the STEREO/EUVI-B and SDO/AIA instruments, respectively.} The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package.
+For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.
 
-{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we \diego{opt} to only use off-limb data.
+{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we {opt} to only use off-limb data.
 In this way, the smallest scale and brighter coronal features seen on disk (most typically in the 171\AA\ band) are not included.
@@
 Sencondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume.
-As a result, coronal dynamics \diego{induce} artifacts are reduced compared to previous DEMT reconstructions.}
+As a result, \albert{artifacts induced by coronal dynamics} are reduced compared to previous DEMT reconstructions.}
 
-{The solution of the tomographic problem involves \diego{inversion of} a very large sparse matrix.
-Such inversion problems are characterized by spurious high-frequency artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}.
+{The solution of the tomographic problem involves {inversion of} a very large sparse matrix.
+Such inversion problems are characterized by spurious \albert{high-fre\-quen\-cy} artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}.
 In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude.
@@
 In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions.
-As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.}
-{The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction (covering the height range $1.0-1.25\,\mrsun$) and 2\deg\ in both the latitudinal and longitudinal directions.
-}
+As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid \albert{when compared to previous reconstructions.}}
 
-\diego{We summarize next the main aspects of DEMT required for the analysis of this work.} In a first step, the time series of EUV images is used to solve a solar SRT problem, for each EUV band independently.
+\albert{In DEMT, the inner corona in the range of heliocentric heights $\lesssim 1.25\,\mrsun$ is discretized in a spherical computational grid.
+The size of the tomographic grid cell (or voxel) is typically set to $0.01\,\mrsun$ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions.
+The cadence of the data time-series is set to 6\,hr.
+The main product of the technique is the local DEM (LDEM) at each voxel, a measure of the temperature distribution of the plasma contained in it.
+We summarize next the main aspects of DEMT required for the analysis of this work.}
+
+In a first step, the time series of EUV images is used to solve a solar SRT problem, for each EUV band independently.
 As a result, the 3D distribution of the so called \emph{filter band emissivity} (FBE) is determined for each band separately.
@@
 
-{In this work the cadence of the data time-series was set to 6\,hr and} data from three EUV bands were {used:} 171, 193 and 211 \AA \ in {the} case of AIA, and 171, 195 and 284 \AA \ bands in {the} case of EUVI.
-When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict the FBEs \citep{frazin_2009,nuevo_2015}.
+\albert{In this work,} data from three EUV bands \albert{was used:} 171, 193 and \albert{211 \AA\ in} {the} case of AIA, and 171, 195 and \albert{284 \AA\ bands} in {the} case of EUVI.
+When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict \albert{the FBEs \citep{nuevo_2015}}.
 In each tomographic voxel, the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that best reproduce the three tomographically reconstructed values of FBE in that voxel.
@@
 {being the} average relative difference between the tomographic and the synthetic FBEs.
-{The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.} \diego{For a full description of the technique we refer the reader to \citet{frazin_2009}.}
+{The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.} {For a full description of the \albert{DEMT technique} we refer the reader to \citet{frazin_2009}.}
 
@@
 
-%\noindent\notebyalbert{This section will summarize the AWSoM model. Chip, Nishtha, do you think you could provide 2 or 3 paragraphs? We believe the points to cover are:
-%\begin{itemize}
-%  \item Data input. Link with the data input for DEMT in terms of dates, etc. One paragraph.
-%  \item Main physical and technical aspects (grid in particular) of the model.  One paragraph. 
-%  \item Explain the artificially extended TR. One paragraph.
-%  \item What are the products of the model we care about in this paper ($N_e$, $T_e$, $B$, $V$, as of now). One paragraph.
-%\end{itemize}
-%}
+\albert{AWSoM is a three-temperature}, MHD model of the solar corona and inner heliosphere which provides the 3D distribution of density and temperatures as well as the 3D magnetic structure and velocity of the solar wind.
+In this work, we use AWSoM model simulated results below 1.25 $\mrsun$ to correspond to the DEMT analysis region.
 
-%In the transition region {(TR)}, the plasma heats up and becomes less dense {by} several orders of magnitude {over} a short distance.
-Modeling this region {realistically has a very high computational cost}.
-For this {reason,} the model uses {an artificially} extended {TR about $\approx 0.05\,\mrsun$ thick, as well as artificially large values for the electronic density and temperature as boundary conditions in $r=1\,\mrsun$.} Consequently, model results below {$\approx 1.05\,\mrsun$} were not taken into account in this article.
+\albert{Heating of the solar corona is addressed} by including the non-linear interaction of forward and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
+This dissipated turbulent energy is distributed over anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature using theories of linear wave damping and stochastic heating.
 
-%The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) is a three-dimensional (3D) physics-based, data-driven model extending from the upper chromosphere, into the solar corona upto 1 AU (and beyond) \citep{vander_2010, Van2014}.
+\albert{The model accounts} for both collisional and collision-less electron heat conduction and does not use ad-hoc heating functions.
+The extended MHD equations including radiative cooling, heat conduction and wave turbulence within AWSoM \citep{Van2014} are solved using the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme.
 
-We compare the DEMT analysis of the two Carrington rotations with the MHD model simulations results from the Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the SWMF. 
-AWSoM is a three-temperature, MHD model of the solar corona and inner heliosphere which provides the 3D distribution of density and temperatures as well as the 3D magnetic structure and velocity of the solar wind.
-In this work, we use AWSoM model simulated results below 1.25 $\mrsun$ to correspond to the DEMT analysis region.
-AWsoM addresses the heating of the solar corona by including the non-linear interaction of forward and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
-This dissipated turbulent energy is distributed over anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature using theories of linear wave damping and stochastic heating.
-AWSoM accounts for both collisional and collision-less electron heat conduction and does not use ad-hoc heating functions.
-The extended MHD equations including radiative cooling, heat conduction and wave turbulence within AWSoM \citep{Van2014} are solved using the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme.
-In the previous version of the model, the cascade time of the major wave was used to determine the wave damping rate \citep{Cha2011, Van2014}.
-However, we improve the energy partitioning by using the Alfv\'{e}n wave number associated with the damping rate as determined by the critical balance condition, which uses the cascade time of the minor wave \citep{Lit2007}.
+\albert{In a previous} version of the model, the cascade time of the major wave was used to determine the wave damping rate \citep{Cha2011, Van2014}.
+\albert{In its present version, the energy partitioning  improved} by using the Alfv\'{e}n wave number associated with the damping rate as determined by the critical balance condition, which uses the cascade time of the minor wave \citep{Lit2007}.
 This leads to more electron heating and less solar wind acceleration \citep{Van2019b}.
@@
 The inner boundary of AWSoM is located at the base of the transition region (at $\approx$1.0\,$\mrsun$).
-In reality, the thin transition region has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses.
+In reality, the thin \albert{transition region (TR)} has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses.
 To resolve these gradients in a global model would require excessive numerical resources.
-As described in \citet{Lio2009} and \citet{Sok2013} we artificially broaden the transition region to resolve with our finest grid resolution of 0.001\,$\mrsun$.
+As described in \citet{Lio2009} and \citet{Sok2013}\albert{, the TR is artificially broaden to be resolved with a} finest grid resolution of 0.001\,$\mrsun$.
 To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot} =2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K.
@@
 At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region.
-Since the broadening of the transition region pushes the corona outwards, AWSoM results below 1.05 $\mrsun$ were not taken into account in this article.
+Since the broadening of the transition region pushes the corona outwards, \albert{the AWSoM model achieves coronal conditions at height $\approx 1.05\,\mrsun$, below which results can not then be compared to coronal tomographic reconstructions.}
 
-To drive our solar corona model, accurate estimates of the photospheric magnetic field of the Sun form the primary input.
-Synoptic magnetograms are used to specify the initial and the boundary conditions of the magnetic field in AWSoM.
-We use the PFSS model to extrapolate the 3D magnetic field (from the 2D photospheric magnetic field maps) using spherical harmonics.
+To drive \albert{the AWSoM model, estimates} of the photospheric magnetic field of the Sun \albert{are the main} input.
+Synoptic magnetograms are used to specify the initial and the boundary conditions of the \albert{magnetic field.} We use the PFSS model to extrapolate the 3D magnetic field (from the 2D photospheric magnetic field maps) using spherical harmonics.
 The source surface is taken to be at 2.5 $\mrsun$.
@@
 In this work, we use the GONG synoptic map as input for CR-2082 (ADAPT-GONG maps are unavailable for CR-2082) and the ADAPT-GONG global magnetic field map for CR-2208.
-For CR-2082, the magnetic field from the GONG map is scaled up by a factor of 1.85 (for Br$<$5 G) while no modification is done for the ADAPT-GONG map for CR-2208.
+\albert{Based on results from previous efforts, for CR-2082} the magnetic field from the GONG map is scaled up by a factor of 1.85 \albert{for weak fields ($B_r< 5\,\rm{G}$), while no modification is applied in the case of} the ADAPT-GONG map for CR-2208.
 The AWSoM steady-state simulation set-up and input parameters for both rotations are described below.
 
-To account for the energy partitioning between electrons and protons, based on \citet{Cha2011}, we set the stochastic heating exponent to be 0.21 and the amplitude equal to 0.18 for both rotations.
-The boundary condition for Alfv\'{e}n wave energy is given by the poynting flux (S$_{A}$) of the outgoing wave.
-$(\frac{S_{A}}{B})_{\odot} = 1.1\times 10^{6}$ Wm$^{-2}$T$^{-1}$ and  $1.0\times 10^{6}$ Wm$^{-2}$T$^{-1}$ for CR-2082 and CR-2208 respectively.
-$B_{\odot}$ is the filed strength at the inner boundary.
-The correlation length of the Alfv\'{e}n waves is set to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$ m$\sqrt{T}$.
-%ADAPT-GONG maps have multiple realizations based on how the polar fields are filled. We use realization 5 for CR-2208.
-The computational domain for solar corona extends from 1 to 24 R$_{\odot}$.
-The spherical grid in the solar corona is radially stretched (with a maximum resolution of 0.001 R$_{\odot}$ near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates.
-The Adaptive Mesh Refinement (AMR) resolves the angular cell size to 1.4$^\circ$ between 1 - 1.7 $\mrsun$ and 2.8 $\mrsun$ outside.
-The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082.
+To account for the energy partitioning between electrons and protons, based on \citet{Cha2011}, we set the stochastic heating exponent \albert{equal to} 0.21 and the amplitude equal to \albert{0.18, for both} rotations.
+The boundary condition for Alfv\'{e}n wave energy is given by the \albert{poynting flux ($S_{A}$)} of the outgoing \albert{wave, $({S_{A}/}{B})_{\odot} = 1.1\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ and $1.0\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ for CR-2082 and CR-2208, respectively, whith $B_{\odot}$ being the field} strength at the inner boundary.
+The correlation length of the Alfv\'{e}n waves is set \albert{to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$m\,$\sqrt{T}$.}
+
+\albert{The computational domain of the solar corona} extends from 1 to \albert{$24\,\mrsun$}.
+The spherical grid in the solar corona is radially stretched (with a maximum resolution \albert{of $0.001\,\mrsun$} near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates.
+The Adaptive Mesh Refinement (AMR) resolves the angular cell \albert{size to $1.4\mdeg$ in the range of heights $1-1.7\,\mrsun$ and beyond $2.8\,\mrsun$}.
+\notebyalbert{(by Albert) does this make sense?} The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082.
 Local time stepping is used to speed up the steady state convergence.
@@
 {To determine} the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid.
-Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = r{\rm d}\theta/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point.
-In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, for a total of $96,000$ starting points.
-\diego{tecnicamente 97,200 = 90*180*6 como indica Chip, pero hay lineas que no son ni 0 ni 1 ni 2 y esas son las aprox 1200 que faltan!.
-yo pondria 97200 y evitaria aclarar.}
+Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = \albert{r\,{\rm d}\theta}/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point.
+In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, \albert{for a total of $97,200$ starting points.}
 
@@
 
-\diego{The electrons collide with ionized metals, completely dominating the EUV radiation.
-Therefore the radiative power depends on the electronic density.} The flux tube model estimates by integrating the squared density multiplied by a radiative loss function $\Lambda(T)$.
-This function depends on plasma temperature and is calculated by the atomic database and the plasma emission model from CHIANTI \citep{delzanna_2015}.
-Then, the expression for radiative power obtained is:
+\albert{In the corona, EUV emission is dominated by collisions of the emitting ions with free electrons, so that the radiative power scales as $N_e^2$.
+The radiative power of an isothermal plasma at temperature $T$ is then computed as $E_r=N_e^2\,\Lambda(T)$, where the radiative loss function $\Lambda(T)$ is calculated by means of an emission model.
+In this work we used the latest version of the atomic database and plasma emission model CHIANTI \citep{delzanna_2015}.
+The radiative power in terms of the LDEM is then given by:}
 
@@
 {The energy balance given by Equation \ref{Balance} is then integrated in the volume of any given coronal magnetic flux tube.
-Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a field-line integrated version of that energy balance is found,
+Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a \albert{field line integrated} version of that energy balance is found,
 \begin{equation}\label{FluxBalance}
@@
 \noindent
-where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\
+where the \albert{line-integrated} flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\
 
@@
 
-\diego{where $B_0$ and $B_L$ are the values of the magnetic field at the footpoints of the loop in the coronal base.} {Note that, for any given field line, all quantities in these two expresions can be computed {from DEMT model} through Equations \ref{Fc}-\ref{Er}.
+\noindent \albert{where $L$ is the length of the loop, and $B_0$ and $B_L$ are the values of the magnetic field at the footpoint locations of the loop in the coronal base, namely $s=0$ and $s=L$.} {Note that, for any given field line, all quantities in these two expresions can be computed \albert{from the DEMT results traced along field lines, and the AWSoM magnetic field model,} through Equations \ref{Fc}-\ref{Er}.
 Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to mantain a stable coronal structure.}
@@
 {Both target rotations are highly axisymmetric, \textit{i.e.} characterized by a high azymuthal symmetry.
-Rotation CR-2082} showed two {small} ARs, both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg$  \diego{(too smal to be registered)}.
-{Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$ \diego{(NOAA 12722, 12721)}.}
+Rotation CR-2082} showed two {small} ARs, both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg$  \albert{(not identified in the NOAA catalog)}.
+{Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$ {(NOAA 12722, 12721)}.}
 
@@
 {{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively higher densities and temperatures in comparison to the CHs.
-They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between \diego{SCs 23 and 24}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the declining phase of \diego{SC 24}, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious.
+They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 23 and 24}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the \albert{end of the declining} phase of {SC 24}, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious.
 This thermodynamic structure of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
@@
 
-Figure \ref{Br} shows carrington maps of radial magnetic field ($Br$) for both rotations at $1.005\, \mrsun$.
-Both maps show a clear dipole.
-The main difference is observed in the polar region and is due to the different types of approaches that use GONG (CR-2082) and ADAPT-GONG (CR-2208.)
+Figure \ref{Br} shows carrington maps of \albert{the radial} magnetic \albert{field ($B_r$)} for both rotations at $1.005\, \mrsun$.
+\albert{Both maps clearly show the large-scale dipolar field, characteristic of solar minimum conditions.
+Differences between both maps are observed in the sub-polar latitudes, due to the different treatments applied there by the GONG (CR-2082) and the ADAPT-GONG (CR-2208) maps.}
 
@@
 \end{figure}
-
 {To characterize the DEMT results in different magnetic structures, we traced} $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.
@@
 {Type 0 (small down) legs mainly populate the equatorial latitudes.
-This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the solar minimum between \diego{SCs 23 and 24} by \citet{nuevo_2013}.
+This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the solar minimum between {SCs 23 and 24} by \citet{nuevo_2013}.
 Later on, \citet{lloveras_2017} showed {that} equatorial down loops in streamers were also to be found in the deep minimum between SCs {23 and 24}.
@@
 
-To develop a validation of the AWSoM model described in Section \ref{awsom} with the DEMT technique explained in Section \ref{demt}, we perform the AWSoM model to the same two target rotations shown in the previous section.
-
-{For both target rotations,} Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature.
+\albert{For both target rotations,} Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature.
 {Maps are shown} at the same three heights selected for visualization of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}.
@@
 
-{Being highly axisymmtric target rotations, the longitude-averaged latitudinal variation of the results of both models is an informative way to compare their large-scale structure.
+{Being highly axisymmtric target rotations, the longitude-averaged latitudinal \albert{profile} of the results of both models is an informative way to compare their large-scale structure.
 Such comparison is shown in Figure \ref{perf_lat} at height $1.105\,\mrsun$, with top panels comparing electron density and mid panels electron temperature.
-\diego{For completeness the variation of $Br$ is added in the lower panels.} In these longitude-averaged profiles, longitudes containing ARs or low latitude CHs were excluded.
+\albert{The longitude-averaged latitudinal profile of $B_r$ is shown in the bottom panels.} In these longitude-averaged profiles, longitudes containing ARs or low latitude CHs were excluded.
 In each panel the averaged latitudinal variation for the DEMT model is shown in solid-line style, while the result for the AWSoM model is shown in dashed-linesyle.
@@
 Note this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
-Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend.} \diego{With regard to $Br$, it is worth pointing the plateau in the coronal hole region of CR-2082 and the decreasing tendency in the case of CR-2208.}
+Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend.
+\albert{For comparison, note the beahavior of $B_r$ in the CHs, increasing from the open/closed boudary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}
 
@@
 
-%\diego{As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region.
-The uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), was estimated {at $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$ by \citet{lloveras_2017}}.
-Considering uncertainty levels CR-2208 is characterized by slightly larger temperatures and definitely lower densities.}
-
 {In the streamer belt region we combined the DEMT results and the AWSoM magnetic model to infer the energy input flux $\phi_h$ at the coronal base required to maintain stable coronal loops.
@@
 For CR-2082, the electron density of both models agree within $\approx 20\%$ {in most regions}, while for CR-2208 the agreement is within $\approx 5\%$.
-{The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations{, with larger discrepancies in the CHs.} This level of agreement between both models \diego{(within or slightly above the uncertainty)} is considerably better than that reported in previous works.
+{The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations{, with larger discrepancies in the CHs.} This level of agreement between both models \albert{(within or slightly beyond the uncertainty level of DEMT results)} is considerably better than that reported in previous works.
 \citet{jin_2012} and \citet{oran_2015} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.} \notebyalbert{Chip, if Section 2.2 explains the most significant improvements of AWSoM since the version used in those references, we can comment on the reason for the improvement here.}
@@
 
-{Within the quantitative match summarized in the previous paragraph, there are some qualitative agreements and disagreements between both models worth noticing.
+{Within the \albert{excellent quantitative match between both models,} summarized in the previous paragraph, there are some qualitative agreements and \albert{disagreements worth noticing}.
 For both target rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.

### 2020-01-27 lloveras_2020_Albert.tex
Version Albert Jan26-2020-21:31

@@
 \begin{abstract}
-Observational techniques play an essential role in advancing our understanding of the physics of the solar {corona, providing in particular validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere.
-Solar rotational tomography is currently the sole observational technique that provides a 3D quantitative description of the solar corona at a global scale.} Based on EUV data of space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights {below $\approx 1.25\,\mrsun$.
-We} carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling {Framework}.
-Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the declining} phase of SC 24.
-The 3D tomographic and MHD models are analysed and compared in distinct coronal magnetic structures.
-{We report in quantitative detail on the 3D thermodinamic structure of the inner corona as revealed by the DEMT analysis.
-We show in particular the existence of diverse types of temperature structures in the low and mid latitudes of the streamer belt, and that the heating energy required to keep them stable may be accounted for by Alfvén waves.
-We show that the latest version of the AWSoM model results agree with DEMT reconstructions to within a $\approx 20\%$ accuracy or better.
-We report on aspects of the AWSoM model that could be improved to better reproduce the DEMT results, in particular concerning the source region of the fast/slow solar winds.}
+Observational techniques play an essential role in advancing our understanding of the physical processes governing the solar corona, providing in \albert{particular validation} data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere.
+Solar rotational tomography is currently the sole observational technique \albert{able to provide} a 3D quantitative description of the solar corona at a global scale.
+Based on {extreme ultraviolet} images \albert{of space} borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$.
+We carry out a study of the corona \albert{through DEMT} reconstructions \albert{and MHD simulations, using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) developed at the University of Michigan as a component of the Space Weather Modeling Framework.
+\albert{Two target} rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the \albert{end of the} declining} phase of SC 24.
+The 3D \albert{DEMT} and MHD models are analysed and compared in distinct coronal magnetic structures.
+{We report in quantitative detail on the 3D thermodynamic structure of the inner corona as revealed by the DEMT analysis.
+We \albert{show the} existence of diverse types of temperature structures in the low and mid latitudes of the \albert{streamer belt.
+We estimate} the heating energy required to keep them \albert{stable, which we argue may} be accounted for by Alfvén waves.
+\albert{We also show that results of the latest version of the AWSoM model overal} agree with DEMT \albert{reconstructions within a $\approx 20\%$ accuracy.
+We highlight some details of the AWSoM model that should} be improved to better reproduce \albert{tomographic} results, in particular concerning the source region of the \albert{fast and slow components of the solar wind.}}
 \end{abstract}
@@
 
-Being the place where the solar atmosphere is heated and the solar wind accelerated, and where impulsive events such as solar flares and coronal mass ejections are energized, observation and modeling of the solar corona are tasks of great relevance to improve our understanding of the Sun-Earth environment.
-To advance our knowledge of the physics of the solar corona, as well as to improve its three-dimensional (3D) models, information derived from observational data plays a key role.
-Solar rotational tomography is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar corona at a global scale.
+Being the {region} where the solar atmosphere is {heated, the solar wind accelerated}, and where impulsive events such as solar flares and coronal mass ejections are energized, observing and modeling of the solar corona are of great relevance to improving our understanding of the Sun-Earth environment.
+To advance our knowledge of the physics of the solar corona, as well as \albert{to enhance} and validate three-dimensional (3D) models, information derived from observational data plays a key role.
+Solar rotational tomography (SRT) is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar \albert{corona at a global} scale.
 
-\noindent\notebyalbert{Here we will put in a couple of paragraphs summarizing what SRT and DEMT are, including references and defining the accronyms in the process.
-We should refer to minima in particular.
-We should mention the instruments and missions we use as data for DEMT, and define their accronyms too.
-Also one paragraph on the SWMF/AWSoM model, including references and defining the accronyms on the way.}
+To study the \albert{3D structure of the quiet-Sun global corona,} SRT has proven to be a powerful tool.
+\albert{In SRT, solar rotation is taken advantage of, so that instruments gather time series of images covering all viewing angles of the solar corona.
+This allows posing an inversion problem to solve for the uncknown 3D distribution of specific quantities of the solar corona.
+Based on extreme ultraviolet EUV images, taken in several channels sensitive to different temperatures, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM).
+The final product of DEMT is in the form of 3D maps of electron density and temperature, covering the range of heliocentric heights $\lesssim 1.25\,\mrsun$.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}.
+\albert{A recent review on DEMT was published by \citet{vasquez_2016}.
+The technique is summarized in Section \ref{demt}.}
 
-{Based on time-series of EUV images, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the solar corona.
-The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}.
-In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid.
-The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions.
-The cadence of the data time-series is set to 6\,hr.
-The main product of the technique is the local DEM (LDEM) at each volxel, a measure of the temperature distribution of the plasma contained in it.
-A recent review by \citet{vasquez_2016} summarizes the DEMT works up until then.
-More recently \citet{lloveras_2017} applied DEMT to study the last two solar minima, and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona.}
+\albert{The combination of DEMT with global magnetic models provides insight} into the 3D thermodynamical structure of the global quiet-Sun corona.
+\albert{DEMT was first combined with a potential field source surface (PFSS) model by \citet{huang_2012} and \citet{nuevo_2013}.
+More recently,} \citet{lloveras_2017} combined DEMT with PFSS \albert{models to study the thermodynamics of the global solar corona in specific magnetic structures for two target rotations selected from the last two solar minimum epochs.
+Also combining DEMT with a PFSS model,} \citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux \albert{required at the coronal base in order to maintain stable coronal loops}.
+In this article, \albert{DEMT is first combined with the magnetic field of a magnetohydrodynamic (MHD) model.}
+
+The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space \albert{Wea\-ther} Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to \albert{1 AU and beyond} \citep{vander_2010, Van2014}.
+\albert{The single data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation.
+As new improvements are implemented, the model is continuously being validated with observations.} DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona.
+More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a globally fashion, obtaining an agreement within 20\%.
+
+\albert{In this work, the AWSoM model is used with two purposes.
+Firstly, to provide an MHD model of the coronal magnetic field to be used to study the DEMT results along magnetic field lines.
+Secondly, to provide thermodynamic results to be compared with those reconstructed by DEMT.}
+
+\albert{Combining the DEMT and AWSoM models, we carry out a detailed quantitatively analysis of two target rotations.
+We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during \albert{the end of the declining} phase of SC 24.
+\albert{In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} \albert{(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG).
+In the case of CR-2208, the DEMT analysis is based in data taken} by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} \albert{(SDO), while the AWSoM model uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}
+
+Section \ref{demt} and \ref{awsom} \albert{summarize the DEMT technique and the AWSoM model, respectively.} Section \ref{trace} \albert{details} the method used to trace \albert{the DEMT} results along the field lines of the magnetic model.
+Section \ref{energia} details \albert{the method that allows determination of the energy input flux at the coronal base.} In Section \ref{demt_res} the quantitative \albert{detailed DEMT analysis of both target rotations is shown,} and in Section \ref{awsom_res} the AWSoM and DEMT results are compared.
+\albert{Finally, Section} \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.
 
@@
 
-{We carried out the 3D DEMT reconstruction and MHD modeling of two target Carrington rotations (CR).
-We selected CR-2082 (2009, 05 April through 03 May), a deep minimum rotation between solar cycles (SC) 23 and 24, and CR-2208 (2018, 02 September through 29 September), a rotation during the early declining fase of SC 24.
-To study CR-2082 and CR-2208 data taken by the STEREO/EUVI-B and SDO/AIA instruments was used, respectively.
-The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package.
-For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.}
+\albert{As detailed in Section \ref{intro}, target rotations CR-2082 and CR-2208 were selected to carry out DEMT reconstructions, based on data taken by the STEREO/EUVI-B and SDO/AIA instruments, respectively.} The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package.
+For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.
 
-{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we opted to only use off-limb data.
+{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we {opt} to only use off-limb data.
 In this way, the smallest scale and brighter coronal features seen on disk (most typically in the 171\AA\ band) are not included.
@@
 Sencondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume.
-As a result, coronal dynamics induced artifacts are reduced compared to previous DEMT reconstructions.}
-.
-{The solution of the tomographic problem involves a very large sparse matrix.
-Such type of inversion problems are characterized by spurious high-frequency artifacts in the solution, which can be mitigated through \emph{regularization} techniques \citep{frazin_2000}.
+As a result, \albert{artifacts induced by coronal dynamics} are reduced compared to previous DEMT reconstructions.}
+
+{The solution of the tomographic problem involves {inversion of} a very large sparse matrix.
+Such inversion problems are characterized by spurious \albert{high-fre\-quen\-cy} artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}.
 In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude.
@@
 In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions.
-As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.}
+As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid \albert{when compared to previous reconstructions.}}
 
-{We summarize next the main aspects of DEMT required for the analysis of this work. We refer the reader to \citet{frazin_2009} for a full description of the technique.}
+\albert{In DEMT, the inner corona in the range of heliocentric heights $\lesssim 1.25\,\mrsun$ is discretized in a spherical computational grid.
+The size of the tomographic grid cell (or voxel) is typically set to $0.01\,\mrsun$ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions.
+The cadence of the data time-series is set to 6\,hr.
+The main product of the technique is the local DEM (LDEM) at each voxel, a measure of the temperature distribution of the plasma contained in it.
+We summarize next the main aspects of DEMT required for the analysis of this work.}
 
-In a first step, the time series of EUV images is used to solve a solar rotational tomography (SRT) problem, for each EUV band independently.
+In a first step, the time series of EUV images is used to solve a solar SRT problem, for each EUV band independently.
 As a result, the 3D distribution of the so called \emph{filter band emissivity} (FBE) is determined for each band separately.
@@
 Line-of-sight (LOS) integration of the FBE provides synthetic images that can be quantitatively compared to the real data in the time series.
-To find the FBE, the tomographic problem is posed a global optimization problem in which the quadratic norm of the difference between all {pairs of synthetic and real images is minimized.}
+To find the FBE, the tomographic problem is posed as a global optimization problem in which the quadratic norm of the difference between all {pairs of synthetic and real images is minimized.}
 
-{In a second step, the FBE values obtained for all bands in each voxel {of the tomographic grid are used to constrain the determination of the LDEM which, as described in Section \ref{intro}, describes the temperature distribution of the plasma within the individual voxel.} Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}
+Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}.
+These non-reconstructed voxels are indicated {in black color in the latitude-longitude (Carrington) maps of DEMT} results in Section \ref{resu}.
+
+{In a second step, the FBE values obtained for all bands in each voxel {of the tomographic grid are used to constrain the determination of the local-DEM (LDEM) which, as described in Section \ref{intro}, describes the temperature distribution of the plasma within the individual voxel.} Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}
 
@@
 \noindent
-{where $K$ is the number EUV bands, and $\TRF^{(k)}$ is the \emph{temperature response function} of the $j$-th detector.
-The TRFs are here computed based on the (known) channel’s passband times the coronal emissivity at that temperature (normalized by the squared electron density).
+{where $K$ is the number EUV bands, and $\TRF^{(k)}$ is the \emph{temperature response function} of the $k$-th detector.
+In this work, the TRFs are computed based on the (known) channel’s passband times the coronal emissivity at that temperature (normalized by the squared electron density).
 The emissivity model used here is provided by the latest version of the CHIANTI atomic database and plasma emission model \citep{delzanna_2015,landi_2013}.}
 
-Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}.
-These non-reconstructed voxels are indicated {in black color in the latitude-longitude (Carrington) maps of DEMT} reults in Section \ref{resu}.
-
-{In this work,} data from thre EUV bands was {used:} 171, 193 and 211 \AA \ in {the} case of AIA, and 171, 195 and 284 \AA \ bands in {the} case of EUVI.
-When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict the tomographic emissivities \citep{frazin_2009,nuevo_2015}.
-In each tomographic voxel the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that allow to best reproduce the three tomographically reconstructed values of FBE in that voxel.
+\albert{In this work,} data from three EUV bands \albert{was used:} 171, 193 and \albert{211 \AA\ in} {the} case of AIA, and 171, 195 and \albert{284 \AA\ bands} in {the} case of EUVI.
+When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict \albert{the FBEs \citep{nuevo_2015}}.
+In each tomographic voxel, the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that best reproduce the three tomographically reconstructed values of FBE in that voxel.
 
@@
 \label{momento2}
- \Tmi  = \langle \Te \rangle_i &=& \frac{1}{\langle \Ne^2 \rangle_i}\,\int\,\textrm{d}T\,T\,{\LDEM_i(T).}\label{Tm} 
+ \Tmi  = \langle \Te \rangle_i &=& \frac{1}{\langle \Ne^2 \rangle_i}\,\int\,\textrm{d}T\,T\,\LDEM_i(T).\label{Tm} 
 \end{eqnarray}
@@
 {being the} average relative difference between the tomographic and the synthetic FBEs.
-{The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.}
+{The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.} {For a full description of the \albert{DEMT technique} we refer the reader to \citet{frazin_2009}.}
 
@@
 
-\noindent\notebyalbert{This section will summarize the AWSoM model. Chip, Nishtha, do you think you could provide 2 or 3 paragraphs? We believe the points to cover are:
-\begin{itemize}
-  \item Data input. Link with the data input for DEMT in terms of dates, etc. One paragraph.
-  \item Main physical and technical aspects (grid in particular) of the model.  One paragraph. 
-  \item Explain the artificially extended TR. One paragraph.
-  \item What are the products of the model we care about in this paper ($N_e$, $T_e$, $B$, $V$, as of now). One paragraph.
-\end{itemize}
-}
+\albert{AWSoM is a three-temperature}, MHD model of the solar corona and inner heliosphere which provides the 3D distribution of density and temperatures as well as the 3D magnetic structure and velocity of the solar wind.
+In this work, we use AWSoM model simulated results below 1.25 $\mrsun$ to correspond to the DEMT analysis region.
 
-In the transition region {(TR)}, the plasma heats up and becomes less dense {by} several orders of magnitude {over} a short distance.
-Modeling this region {realistically has a very high computational cost}.
-For this {reason,} the model uses {an artificially} extended {TR about $\approx 0.05\,\mrsun$ thick, as well as artificially large values for the electronic density and temperature as boundary conditions in $r=1\,\mrsun$.} Consequently, model results below {$\approx 1.05\,\mrsun$} were not taken into account in this article.
+\albert{Heating of the solar corona is addressed} by including the non-linear interaction of forward and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
+This dissipated turbulent energy is distributed over anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature using theories of linear wave damping and stochastic heating.
 
-\subsection{{Tracing Results Along Magnetic Fieldlines}}\label{trace}
+\albert{The model accounts} for both collisional and collision-less electron heat conduction and does not use ad-hoc heating functions.
+The extended MHD equations including radiative cooling, heat conduction and wave turbulence within AWSoM \citep{Van2014} are solved using the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme.
+
+\albert{In a previous} version of the model, the cascade time of the major wave was used to determine the wave damping rate \citep{Cha2011, Van2014}.
+\albert{In its present version, the energy partitioning  improved} by using the Alfv\'{e}n wave number associated with the damping rate as determined by the critical balance condition, which uses the cascade time of the minor wave \citep{Lit2007}.
+This leads to more electron heating and less solar wind acceleration \citep{Van2019b}.
+
+The inner boundary of AWSoM is located at the base of the transition region (at $\approx$1.0\,$\mrsun$).
+In reality, the thin \albert{transition region (TR)} has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses.
+To resolve these gradients in a global model would require excessive numerical resources.
+As described in \citet{Lio2009} and \citet{Sok2013}\albert{, the TR is artificially broaden to be resolved with a} finest grid resolution of 0.001\,$\mrsun$.
+To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot} =2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K.
+The upper chromosphere is required to extend radially for the density to fall rapidly to correct (lower) values \citep{Lio2009}.
+At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region.
+Since the broadening of the transition region pushes the corona outwards, \albert{the AWSoM model achieves coronal conditions at height $\approx 1.05\,\mrsun$, below which results can not then be compared to coronal tomographic reconstructions.}
+
+To drive \albert{the AWSoM model, estimates} of the photospheric magnetic field of the Sun \albert{are the main} input.
+Synoptic magnetograms are used to specify the initial and the boundary conditions of the \albert{magnetic field.} We use the PFSS model to extrapolate the 3D magnetic field (from the 2D photospheric magnetic field maps) using spherical harmonics.
+The source surface is taken to be at 2.5 $\mrsun$.
+The Global Oscillation Network Group (GONG) provides synoptic full-disk surface maps of the radial magnetic field component of the Sun.
+However, since the polar regions are not well observed from the ecliptic, GONG estimates the polar fields by fitting a polynomial to neighboring observed latitudes, which might lead to inaccuracies.
+An improvement over these maps is provided by the Air Force Data Assimilation Photospheric Flux Transport (ADAPT) model \citep{Wor2000}, which creates synchronic-synoptic maps by incorporating supergranulation, meridional circulation, and differential rotation.
+These maps provide a physics-based description of the unobserved polar magnetic fields \citep{Arg2010, Hen2012}.
+In this work, we use the GONG synoptic map as input for CR-2082 (ADAPT-GONG maps are unavailable for CR-2082) and the ADAPT-GONG global magnetic field map for CR-2208.
+\albert{Based on results from previous efforts, for CR-2082} the magnetic field from the GONG map is scaled up by a factor of 1.85 \albert{for weak fields ($B_r< 5\,\rm{G}$), while no modification is applied in the case of} the ADAPT-GONG map for CR-2208.
+The AWSoM steady-state simulation set-up and input parameters for both rotations are described below.
+
+To account for the energy partitioning between electrons and protons, based on \citet{Cha2011}, we set the stochastic heating exponent \albert{equal to} 0.21 and the amplitude equal to \albert{0.18, for both} rotations.
+The boundary condition for Alfv\'{e}n wave energy is given by the \albert{poynting flux ($S_{A}$)} of the outgoing \albert{wave, $({S_{A}/}{B})_{\odot} = 1.1\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ and $1.0\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ for CR-2082 and CR-2208, respectively, whith $B_{\odot}$ being the field} strength at the inner boundary.
+The correlation length of the Alfv\'{e}n waves is set \albert{to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$m\,$\sqrt{T}$.}
+
+\albert{The computational domain of the solar corona} extends from 1 to \albert{$24\,\mrsun$}.
+The spherical grid in the solar corona is radially stretched (with a maximum resolution \albert{of $0.001\,\mrsun$} near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates.
+The Adaptive Mesh Refinement (AMR) resolves the angular cell \albert{size to $1.4\mdeg$ in the range of heights $1-1.7\,\mrsun$ and beyond $2.8\,\mrsun$}.
+\notebyalbert{(by Albert) does this make sense?} The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082.
+Local time stepping is used to speed up the steady state convergence.
+The AWSoM simulation results of the structure of the solar corona for solar minimum conditions represented by CR-2082 and CR-2208 are compared to the DEMT as described in the results section.
+
+\subsection{{Tracing Results Along Magnetic Field lines}}\label{trace}
 
 {To determine} the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid.
-Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = r{\rm d}\theta/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point.
-In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, for a total of $96,000$ starting points.
+Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = \albert{r\,{\rm d}\theta}/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point.
+In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, \albert{for a total of $97,200$ starting points.}
 
 {For analysis purposes, {the traced magnetic field lines are classified as open or closed according to their full geometry.
-Each closed field} line is further classified as ``small" or ``large", according to its coronal length $L$ being {respectively smaller or larger than the median value of the whole population, which is ${\rm Md}(L)\approx 0.5\,\mrsun$ for both rotations.} Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e.
-their location at $r=1\,\mrsun$) to its apex (i.e., the location of maximum height).}
+Each closed field} line is further classified as ``small" or ``large", according to its coronal length $L$ being {respectively smaller or larger than the median value of the whole population, which is ${\rm Md}(L)\approx 0.5\,\mrsun$ for both rotations.} Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (\textit{i.e.} their location at $r=1\,\mrsun$) to its apex (\textit{i.e.}, the location of maximum height).}
 
@@
 
-{The high temperature of the corona requires heating mechanisms to compensate for the the losses.
-While the vast majority of the existing literature on coronal heating focuses on ARs, some studies have been dedicated to the heating of quiet-Sun regions.
-In particular,  \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to mantain them stable.
-The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in the previous Section \ref{trace}.}
+{The high temperature of the corona requires heating mechanisms to compensate for the energy losses.
+While the vast majority of the existing literature on coronal heating focuses on active regions (ARs), some studies have been dedicated to the heating of quiet-Sun regions.
+In particular,  \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to mantain stability.
+The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in Section \ref{trace}.}
 
-{Consider} a simple energy balance for each magnetic flux tube, {in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated {by a} coronal heating power($E_h$) \citep{aschwanden_2004}:
+{Consider} a static energy balance for each magnetic flux tube, {in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated {by a} coronal heating power ($E_h$) \citep{aschwanden_2004}:
 
@@
 Radiative power depends on the amount of plasma in certain temperatures that can radiate.
-The model estimate it by integrating the squared density multiplied by a radiative loss function $\Lambda(T)$.
-This function depends on plasma temperature and is calculated by the atomic database and the plasma emission model from CHIANTI \citep{delzanna_2015}.
-Then, the expression for radiative power obtained is:
+
+\albert{In the corona, EUV emission is dominated by collisions of the emitting ions with free electrons, so that the radiative power scales as $N_e^2$.
+The radiative power of an isothermal plasma at temperature $T$ is then computed as $E_r=N_e^2\,\Lambda(T)$, where the radiative loss function $\Lambda(T)$ is calculated by means of an emission model.
+In this work we used the latest version of the atomic database and plasma emission model CHIANTI \citep{delzanna_2015}.
+The radiative power in terms of the LDEM is then given by:}
 
 \begin{equation}\label{Er}
-E_r = \int\,\textrm{d}T\,\LDEM(T)\,\Lambda(T)
+E_r = \int\,\textrm{d}T\,\LDEM(T)\,\Lambda(T).
 \end{equation}
 
-The energy balance given by Equation (\ref{Balance}) is then integrated in the volume of any given coronal magnetic flux tube.
-Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a field-line integrated version of that energy balance is found,
-
+{The energy balance given by Equation \ref{Balance} is then integrated in the volume of any given coronal magnetic flux tube.
+Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a \albert{field line integrated} version of that energy balance is found,
 \begin{equation}\label{FluxBalance}
-\phi_h = \phi_r + {\phi_c,}
+\phi_h = \phi_r + \phi_c,
 \end{equation}
-
 \noindent
-where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},
+where the \albert{line-integrated} flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\
 
 \begin{equation}\label{phi_r}
-\phi_r = \left( \frac{B_0 \ B_L}{B_0 + B_L} \right) \int_{0}^{L} ds \ \frac{E_r(s)}{B(s)}
+\phi_r = \left( \frac{B_0 \ B_L}{B_0 + B_L} \right) \int_{0}^{L} ds \ \frac{E_r(s)}{B(s)},
 \end{equation}
@@
 \begin{equation}\label{phi_c}
-\phi_c = \left( \frac{B_0 \ F_{c,L} - B_L \ F_{c,0}}{B_0 + B_L} \right) 
+\phi_c = \left( \frac{B_0 \ F_{c,L} - B_L \ F_{c,0}}{B_0 + B_L} \right) ,
 \end{equation}
 
-{Note that, for any given field line, all quantities in these two expresions can be computed from the DEMT and AWSoM models through Equations (\ref{Fc})-(\ref{Er}).
+\noindent \albert{where $L$ is the length of the loop, and $B_0$ and $B_L$ are the values of the magnetic field at the footpoint locations of the loop in the coronal base, namely $s=0$ and $s=L$.} {Note that, for any given field line, all quantities in these two expresions can be computed \albert{from the DEMT results traced along field lines, and the AWSoM magnetic field model,} through Equations \ref{Fc}-\ref{Er}.
 Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to mantain a stable coronal structure.}
@@
 
-{Both target rotations are highly axisymmetric, i.e.
-characterized by a high azymuthal symmetry.
-Rotation CR-2082} showed two {small} active regions (ARs), both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg${, respectively}.
-{Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$, respectively.}
+{Both target rotations are highly axisymmetric, \textit{i.e.} characterized by a high azymuthal symmetry.
+Rotation CR-2082} showed two {small} ARs, both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg$  \albert{(not identified in the NOAA catalog)}.
+{Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$ {(NOAA 12722, 12721)}.}
 
-{The magnetically open and closed regions of the AWSoM model are associated to Coronal holes (CHs) and the equatorial streamer belt, respectively.
-Consistently with that, the {location of the} open/closed boundaries derived from the respective AWSoM model quite accurately matchs {the regions of the DEMT maps which exhibit the strongest latitudinal gradient of both the electron density and temperature.}}
+{The magnetically open and closed regions of the AWSoM model are associated with Coronal holes (CHs) and the equatorial streamer belt, respectively.
+The {location of the} open/closed boundaries derived from the respective AWSoM model quite accurately matchs {the regions of the DEMT maps, which exhibit the strongest latitudinal gradient of both the electron density and temperature.}}
 
@@
 
-{{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively larger values of density and temperature in comparison to the CHs.
-They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 24 and 25}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the declining phase of {SC 25, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious.
-This thermodynamic structure} of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
+{{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively higher densities and temperatures in comparison to the CHs.
+They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 23 and 24}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the \albert{end of the declining} phase of {SC 24}, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious.
+This thermodynamic structure of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
 
-{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of {the DEMT} measure $R$ defined by Equation (\ref{R}), at the same three heights shown in Figures \ref{momento1} and \ref{momento2}.
+{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of {the DEMT} measure $R$ defined by Equation \ref{R}, at the same three heights shown in Figures \ref{momento1} and \ref{momento2}.
 In most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$.
@@
 
+Figure \ref{Br} shows carrington maps of \albert{the radial} magnetic \albert{field ($B_r$)} for both rotations at $1.005\, \mrsun$.
+\albert{Both maps clearly show the large-scale dipolar field, characteristic of solar minimum conditions.
+Differences between both maps are observed in the sub-polar latitudes, due to the different treatments applied there by the GONG (CR-2082) and the ADAPT-GONG (CR-2208) maps.}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{figs/map_Br_awsom_2082_185_extend_1005_Rsun.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/map_Br_awsom_2208_185_extend_1005_Rsun.pdf}
+\caption{Carrington maps of \albert{the radial magnetic field $B_r$ of the AWSoM model} at $1.005 \, \mrsun$ for CR-2082 (left) and CR-2208 (right). }
+\label{Br}
+\end{center}
+\end{figure}
 {To characterize the DEMT results in different magnetic structures, we traced} $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.
-For both rotations, all legss that meet the criteria listed in Section \ref{trace} were selected.
+For both rotations, all legs that meet the criteria listed in Section \ref{trace} were selected.
 For each leg, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.
@@
 {Type 0 (small down) legs mainly populate the equatorial latitudes.
-This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level {around the solar minimum between SCs 24 and 25} by \citet{nuevo_2013}.
+This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the solar minimum between {SCs 23 and 24} by \citet{nuevo_2013}.
 Later on, \citet{lloveras_2017} showed {that} equatorial down loops in streamers were also to be found in the deep minimum between SCs {23 and 24}.
@@
 
-{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer {layers} of the equatorial streamer belt, exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
+{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer layers of the equatorial streamer belt, exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
 In both rotations also, type III legs in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I legs in the core of the equatorial streamer.}
@@
 
-{For both target rotations,} Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature.
+\albert{For both target rotations,} Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature.
 {Maps are shown} at the same three heights selected for visualization of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}.
@@
 
-{Being highly axisymmtric target rotations, the longitude-averaged latitudinal variation of the results of both models is an informative way to compare their large-scale structure.
-Such comparison is shown in Figure \ref{perf_lat} at height $1.105\,\mrsun$, with top panels comparing electron density and lower panels electron temperature.
-In these longitude-averaged profiles, longitudes containing ARs or low latitude CHs were excluded.
+{Being highly axisymmtric target rotations, the longitude-averaged latitudinal \albert{profile} of the results of both models is an informative way to compare their large-scale structure.
+Such comparison is shown in Figure \ref{perf_lat} at height $1.105\,\mrsun$, with top panels comparing electron density and mid panels electron temperature.
+\albert{The longitude-averaged latitudinal profile of $B_r$ is shown in the bottom panels.} In these longitude-averaged profiles, longitudes containing ARs or low latitude CHs were excluded.
 In each panel the averaged latitudinal variation for the DEMT model is shown in solid-line style, while the result for the AWSoM model is shown in dashed-linesyle.
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105.eps}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105.eps}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105.eps}
-\caption{Longitude-averaged latitudinal dependence of the electron density (top) and temperature (bottom) for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$.
-The left (right) panels correspond to CR-2082 (CR2208).
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105_2.pdf}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105_2.pdf}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105_2.pdf}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105_2.pdf}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2082_1105_2.pdf}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2208_1105_2.pdf}
+\caption{Longitude-averaged latitudinal dependence of the electron density (\albert{top panels}), \albert{electron temperature (\albert{middle panels})} and \albert{radial magnetic field $B_r$ (bottom panels), for target rotations} CR-2082 (\albert{blue color, left panels}) and CR-2208 (\albert{red color, right panels) at} $1.105\,\mrsun$.
+Dashed lines correspond to AWSoM results while solid line to DEMT.
 The vertical black line indicates the longitude-averaged latitudes of the open/closed magnetic boundary in both hemispheres.}
@@
 
-{\albert{Several details from Figure \ref{perf_lat} are worth being highlighted.
+{{Several details from Figure \ref{perf_lat} are worth being highlighted.
 Firstly, at most latitudes the overal agreement of the electron density of both models is within $\approx 20\%$ for CR-2082, and $\approx 5\%$ for CR-2208.
-The noticeable exception is to be found near the open/close boundaries of both target rotations, where the disagreement between both models can be up to twice as much.
+The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.
 In the case of the electron temperature, for both target rotations the models agree within $\approx 15\%$ at all latitudes of the streamer belt, showing larger discrepancies in the CHs.} Secondly, for both target rotations, and for both models, these plots clearly show the relatively lower temperatures characterising the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
@@
 Note this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
-Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend.}
+Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend.
+\albert{For comparison, note the beahavior of $B_r$ in the CHs, increasing from the open/closed boudary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}
 
@@
 
-{For target rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, \albert{depending of the type of leg, with the largest discrepancy foud for legs of type II (near the open/close boundary).
-The} median value of the scale height $\lN$ agree \albert{within $\approx 10\%$ in all regions}.
-The leg-averaged electron temperature $\aTm$ of both models also agree \albert{within $10\%$ in all regions}.
-For target rotation CR-2208 the agreement of the median value of $\NCB$ and $\lN$ of both models \albert{is within $10\%$, while} median values of $\aTm$ agree within $15\%$.
-\albert{These detailed results, being consistent with the large-scale comparison provided in Figure \ref{perf_lat}, show in detail how the AWSoM model performs compard to DEMT in different magetic strucures.}}
+{For target rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, {depending of the type of leg, with the largest discrepancy foud for legs of type II (near the open/closed boundary).
+The} median value of the scale height $\lN$ agree {within $\approx 10\%$ in all regions}.
+The leg-averaged electron temperature $\aTm$ of both models also agree {within $10\%$ in all regions}.
+For target rotation CR-2208 the agreement of the median value of $\NCB$ and $\lN$ of both models {is within $10\%$, while} median values of $\aTm$ agree within $15\%$.
+{These detailed results, being consistent with the large-scale comparison provided in Figure \ref{perf_lat}, show in detail how the AWSoM model performs compard to DEMT in different magetic strucures.}}
 
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995.eps}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
-\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6.0\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).} \notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the absolute minimum indicates the location of the HCS at this height.
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995_2.pdf}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995_2.pdf}
+\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6.0\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).} %\notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the absolute minimum indicates the location of the HCS at this height.
 I believe it is interesting to compare these two curves with Figure 10.
@@
 
-{Concerning the DEMT reconstructions, Figure \ref{rpoint_demt} shows that, for both taget rotations, magnetic field lines of type 0, I and II are associated to increasingly outer {layers} of the equatorial streamer belt.
-Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} report in 3D quantitative detail how these progressively outer magnetic structures exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.} For both target rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes.
+Concerning the DEMT reconstructions, Figure \ref{rpoint_demt} shows that, for both target rotations, magnetic field lines of type 0, I and II are associated to increasingly outer {layers} of the equatorial streamer belt.
+Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} report in 3D quantitative detail how these progressively outer magnetic structures exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
+For both target rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes.
 Also, in the case of CR-2082 the fraction of down legs is significantly larger than for CR-2208.
@@
 The detailed comparison shown in this work can be summarized as follows.
-For CR-2082, the electron density of both models agree within $\approx 20\%$ \albert{in most regions}, while for CR-2208 the agreement is within $\approx 5\%$.
-\albert{The noticeable exception is to be found near the open/close boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations\albert{, with larger discrepancies in the CHs.} This level of agreement between both models is considerably better than that reported in previous works.
-\citet{oran_2015} and \citet{jin_2012} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.} \notebyalbert{Chip, if Section 2.2 explains the most significant improvements of AWSoM since the version used in those references, we can comment on the reason for the improvement here.}
+For CR-2082, the electron density of both models agree within $\approx 20\%$ {in most regions}, while for CR-2208 the agreement is within $\approx 5\%$.
+{The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations{, with larger discrepancies in the CHs.} This level of agreement between both models \albert{(within or slightly beyond the uncertainty level of DEMT results)} is considerably better than that reported in previous works.
+\citet{jin_2012} and \citet{oran_2015} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.} \notebyalbert{Chip, if Section 2.2 explains the most significant improvements of AWSoM since the version used in those references, we can comment on the reason for the improvement here.}
+\diego{Note by Diego: Chip, Nishtha, if you think we can relate some differences or observed trends of AWSoM with the magnetic field, this could be a good place, but I need your insight here.}
 
-{Within the quantitative match summarized in the previous paragraph, there are some qualitative agreements and disagreements between both models worth noticing.
+{Within the \albert{excellent quantitative match between both models,} summarized in the previous paragraph, there are some qualitative agreements and \albert{disagreements worth noticing}.
 For both target rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
-On the other hand, while the latitude of the open/close magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
+On the other hand, while the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
 Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), the AWSoM model shows the opposite trend.
@@
 
-\notebyalbert{Chip: In relation to the previous comment, if the anlaysis proposed in Figure 15 is carried out we should say something about that here.}
-
-A detailed empirical description of the 3D termodynamic structure of the inner corona at a global scale is curently only possible with tomographic techniques, such as DEMT.
+A detailed empirical description of the 3D termodynamic structure of the inner corona at a global scale is currently only possible with tomographic techniques, such as DEMT.
 Using tomographic results for continuous validation of 3D MHD models is of high relevance for the continued improvement of models.
@@
 A.M.V.
-also acknowledges UBACyT grant {20020160100072BA to DCAO-UBA} and IAFE that partially supported his participation in this research.}
+also acknowledges UBACyT grant 20020160100072BA to DCAO-UBA to FCEyN-UBA and IAFE that partially supported his participation in this research.}
 \end{acks}
-
+\\
+\\
+\begin{footnotesize}
+ Disclosure of Potential Conflicts of Interest: The authors declare that they have no conflicts of interest.
+\end{footnotesize}
 \bibliographystyle{spr-mp-sola}

### 2020-01-27 lloveras_2020.tex
Version Albert 27-Jan-2020 14:05

@@
-%% Template.tex; Solar Physics
-%% 
 \documentclass[namedreferences]{solarphysics}
-%
-% spr-sola-addons available options:
-%  hyperref      -- loads hyperref.sty with options (pdfborder={0 0 0 },urlcolor=blue,breaklinks)
-%  nonatbib      -- do not load natbib.sty (style loads it by default)
-%  solaromanenum -- makes enumerated list with roman numerals and a single right-bracket
-%  linksfromyear -- puts a link on a year citation (hyperref must be loaded). Loaded by default
-%  nolinksfromyear -- suppress  linksfromyear
-%  optionalrh    -- for optional running title/author
-%  showbiblabels -- to show bibitem label at end of bibitem (via \endbibitem command)
-%
+
 \usepackage[hyperref,optionalrh,solaromanenum]{spr-sola-addons} % For Solar Physics 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Runningheads
-%
 \runningauthor{D.G.~Lloveras~\etal}
@@
 \begin{abstract}
-Observational techniques play an essential role in advancing our understanding of the physical processes governing the solar corona, providing in \albert{particular validation} data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere.
-Solar rotational tomography is currently the sole observational technique \albert{able to provide} a 3D quantitative description of the solar corona at a global scale.
-Based on {extreme ultraviolet} images \albert{of space} borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$.
-We carry out a study of the corona \albert{through DEMT} reconstructions \albert{and MHD simulations, using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) developed at the University of Michigan as a component of the Space Weather Modeling Framework.
-\albert{Two target} rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the \albert{end of the} declining} phase of SC 24.
-The 3D \albert{DEMT} and MHD models are analysed and compared in distinct coronal magnetic structures.
+Observational techniques play an essential role in advancing our understanding of the physical processes governing the solar corona, providing in {particular validation} data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere.
+Solar rotational tomography is currently the sole observational technique {able to provide} a 3D quantitative description of the solar corona at a global scale.
+Based on {extreme ultraviolet} images {of space} borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$.
+We carry out a study of the corona {through DEMT} reconstructions {and MHD simulations, using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) developed at the University of Michigan as a component of the Space Weather Modeling Framework.
+{Two target} rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the {end of the} declining} phase of SC 24.
+The 3D {DEMT} and MHD models are analysed and compared in distinct coronal magnetic structures.
 {We report in quantitative detail on the 3D thermodynamic structure of the inner corona as revealed by the DEMT analysis.
-We \albert{show the} existence of diverse types of temperature structures in the low and mid latitudes of the \albert{streamer belt.
-We estimate} the heating energy required to keep them \albert{stable, which we argue may} be accounted for by Alfvén waves.
-\albert{We also show that results of the latest version of the AWSoM model overal} agree with DEMT \albert{reconstructions within a $\approx 20\%$ accuracy.
-We highlight some details of the AWSoM model that should} be improved to better reproduce \albert{tomographic} results, in particular concerning the source region of the \albert{fast and slow components of the solar wind.}}
+We {show the} existence of diverse types of temperature structures in the low and mid latitudes of the {streamer belt.
+We estimate} the heating energy required to keep them {stable, which we argue may} be accounted for by Alfvén waves.
+{We also show that results of the latest version of the AWSoM model overal} agree with DEMT {reconstructions within a $\approx 20\%$ accuracy.
+We highlight some details of the AWSoM model that should} be improved to better reproduce {tomographic} results, in particular concerning the source region of the {fast and slow components of the solar wind.}}
 \end{abstract}
@@
 Being the {region} where the solar atmosphere is {heated, the solar wind accelerated}, and where impulsive events such as solar flares and coronal mass ejections are energized, observing and modeling of the solar corona are of great relevance to improving our understanding of the Sun-Earth environment.
-To advance our knowledge of the physics of the solar corona, as well as \albert{to enhance} and validate three-dimensional (3D) models, information derived from observational data plays a key role.
-Solar rotational tomography (SRT) is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar \albert{corona at a global} scale.
+To advance our knowledge of the physics of the solar corona, as well as {to enhance} and validate three-dimensional (3D) models, information derived from observational data plays a key role.
+Solar rotational tomography (SRT) is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar {corona at a global} scale.
 
-To study the \albert{3D structure of the quiet-Sun global corona,} SRT has proven to be a powerful tool.
-\albert{In SRT, solar rotation is taken advantage of, so that instruments gather time series of images covering all viewing angles of the solar corona.
+To study the {3D structure of the quiet-Sun global corona,} SRT has proven to be a powerful tool.
+{In SRT, solar rotation is taken advantage of, so that instruments gather time series of images covering all viewing angles of the solar corona.
 This allows posing an inversion problem to solve for the uncknown 3D distribution of specific quantities of the solar corona.
@@
 The final product of DEMT is in the form of 3D maps of electron density and temperature, covering the range of heliocentric heights $\lesssim 1.25\,\mrsun$.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}.
-\albert{A recent review on DEMT was published by \citet{vasquez_2016}.
+{A recent review on DEMT was published by \citet{vasquez_2016}.
 The technique is summarized in Section \ref{demt}.}
 
-\albert{The combination of DEMT with global magnetic models provides insight} into the 3D thermodynamical structure of the global quiet-Sun corona.
-\albert{DEMT was first combined with a potential field source surface (PFSS) model by \citet{huang_2012} and \citet{nuevo_2013}.
-More recently,} \citet{lloveras_2017} combined DEMT with PFSS \albert{models to study the thermodynamics of the global solar corona in specific magnetic structures for two target rotations selected from the last two solar minimum epochs.
-Also combining DEMT with a PFSS model,} \citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux \albert{required at the coronal base in order to maintain stable coronal loops}.
-In this article, \albert{DEMT is first combined with the magnetic field of a magnetohydrodynamic (MHD) model.}
+{The combination of DEMT with global magnetic models provides insight} into the 3D thermodynamical structure of the global quiet-Sun corona.
+{DEMT was first combined with a potential field source surface (PFSS) model by \citet{huang_2012} and \citet{nuevo_2013}.
+More recently,} \citet{lloveras_2017} combined DEMT with PFSS {models to study the thermodynamics of the global solar corona in specific magnetic structures for two target rotations selected from the last two solar minimum epochs.
+Also combining DEMT with a PFSS model,} \citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux {required at the coronal base in order to maintain stable coronal loops}.
+In this article, {DEMT is first combined with the magnetic field of a magnetohydrodynamic (MHD) model.}
 
-The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space \albert{Wea\-ther} Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to \albert{1 AU and beyond} \citep{vander_2010, Van2014}.
-\albert{The single data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation.
+The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space {Wea\-ther} Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to {1 AU and beyond} \citep{vander_2010, Van2014}.
+{The single data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation.
 As new improvements are implemented, the model is continuously being validated with observations.} DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona.
@@
 
-\albert{In this work, the AWSoM model is used with two purposes.
+{In this work, the AWSoM model is used with two purposes.
 Firstly, to provide an MHD model of the coronal magnetic field to be used to study the DEMT results along magnetic field lines.
@@
 
-\albert{Combining the DEMT and AWSoM models, we carry out a detailed quantitatively analysis of two target rotations.
-We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during \albert{the end of the declining} phase of SC 24.
-\albert{In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} \albert{(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG).
-In the case of CR-2208, the DEMT analysis is based in data taken} by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} \albert{(SDO), while the AWSoM model uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}
+{Combining the DEMT and AWSoM models, we carry out a detailed quantitatively analysis of two target rotations.
+We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during {the end of the declining} phase of SC 24.
+{In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} {(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG).
+In the case of CR-2208, the DEMT analysis is based in data taken} by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} {(SDO), while the AWSoM model uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}
 
-Section \ref{demt} and \ref{awsom} \albert{summarize the DEMT technique and the AWSoM model, respectively.} Section \ref{trace} \albert{details} the method used to trace \albert{the DEMT} results along the field lines of the magnetic model.
-Section \ref{energia} details \albert{the method that allows determination of the energy input flux at the coronal base.} In Section \ref{demt_res} the quantitative \albert{detailed DEMT analysis of both target rotations is shown,} and in Section \ref{awsom_res} the AWSoM and DEMT results are compared.
-\albert{Finally, Section} \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.
+Section \ref{demt} and \ref{awsom} {summarize the DEMT technique and the AWSoM model, respectively.} Section \ref{trace} {details} the method used to trace {the DEMT} results along the field lines of the magnetic model.
+Section \ref{energia} details {the method that allows determination of the energy input flux at the coronal base.} In Section \ref{demt_res} the quantitative {detailed DEMT analysis of both target rotations is shown,} and in Section \ref{awsom_res} the AWSoM and DEMT results are compared.
+{Finally, Section} \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.
 
@@
 
-\albert{As detailed in Section \ref{intro}, target rotations CR-2082 and CR-2208 were selected to carry out DEMT reconstructions, based on data taken by the STEREO/EUVI-B and SDO/AIA instruments, respectively.} The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package.
+{As detailed in Section \ref{intro}, target rotations CR-2082 and CR-2208 were selected to carry out DEMT reconstructions, based on data taken by the STEREO/EUVI-B and SDO/AIA instruments, respectively.} The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package.
 For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.
@@
 Sencondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume.
-As a result, \albert{artifacts induced by coronal dynamics} are reduced compared to previous DEMT reconstructions.}
+As a result, {artifacts induced by coronal dynamics} are reduced compared to previous DEMT reconstructions.}
 
 {The solution of the tomographic problem involves {inversion of} a very large sparse matrix.
-Such inversion problems are characterized by spurious \albert{high-fre\-quen\-cy} artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}.
+Such inversion problems are characterized by spurious {high-fre\-quen\-cy} artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}.
 In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude.
@@
 In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions.
-As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid \albert{when compared to previous reconstructions.}}
+As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid {when compared to previous reconstructions.}}
 
-\albert{In DEMT, the inner corona in the range of heliocentric heights $\lesssim 1.25\,\mrsun$ is discretized in a spherical computational grid.
+{In DEMT, the inner corona in the range of heliocentric heights $\lesssim 1.25\,\mrsun$ is discretized in a spherical computational grid.
 The size of the tomographic grid cell (or voxel) is typically set to $0.01\,\mrsun$ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions.
@@
 
-\albert{In this work,} data from three EUV bands \albert{was used:} 171, 193 and \albert{211 \AA\ in} {the} case of AIA, and 171, 195 and \albert{284 \AA\ bands} in {the} case of EUVI.
-When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict \albert{the FBEs \citep{nuevo_2015}}.
+{In this work,} data from three EUV bands {was used:} 171, 193 and {211 \AA\ in} {the} case of AIA, and 171, 195 and {284 \AA\ bands} in {the} case of EUVI.
+When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict {the FBEs \citep{nuevo_2015}}.
 In each tomographic voxel, the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that best reproduce the three tomographically reconstructed values of FBE in that voxel.
@@
 {being the} average relative difference between the tomographic and the synthetic FBEs.
-{The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.} {For a full description of the \albert{DEMT technique} we refer the reader to \citet{frazin_2009}.}
+{The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.} {For a full description of the {DEMT technique} we refer the reader to \citet{frazin_2009}.}
 
@@
 
-\albert{AWSoM is a three-temperature}, MHD model of the solar corona and inner heliosphere which provides the 3D distribution of density and temperatures as well as the 3D magnetic structure and velocity of the solar wind.
+{AWSoM is a three-temperature}, MHD model of the solar corona and inner heliosphere which provides the 3D distribution of density and temperatures as well as the 3D magnetic structure and velocity of the solar wind.
 In this work, we use AWSoM model simulated results below 1.25 $\mrsun$ to correspond to the DEMT analysis region.
 
-\albert{Heating of the solar corona is addressed} by including the non-linear interaction of forward and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
+{Heating of the solar corona is addressed} by including the non-linear interaction of forward and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
 This dissipated turbulent energy is distributed over anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature using theories of linear wave damping and stochastic heating.
 
-\albert{The model accounts} for both collisional and collision-less electron heat conduction and does not use ad-hoc heating functions.
+{The model accounts} for both collisional and collision-less electron heat conduction and does not use ad-hoc heating functions.
 The extended MHD equations including radiative cooling, heat conduction and wave turbulence within AWSoM \citep{Van2014} are solved using the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme.
 
-\albert{In a previous} version of the model, the cascade time of the major wave was used to determine the wave damping rate \citep{Cha2011, Van2014}.
-\albert{In its present version, the energy partitioning  improved} by using the Alfv\'{e}n wave number associated with the damping rate as determined by the critical balance condition, which uses the cascade time of the minor wave \citep{Lit2007}.
+{In a previous} version of the model, the cascade time of the major wave was used to determine the wave damping rate \citep{Cha2011, Van2014}.
+{In its present version, the energy partitioning  improved} by using the Alfv\'{e}n wave number associated with the damping rate as determined by the critical balance condition, which uses the cascade time of the minor wave \citep{Lit2007}.
 This leads to more electron heating and less solar wind acceleration \citep{Van2019b}.
@@
 The inner boundary of AWSoM is located at the base of the transition region (at $\approx$1.0\,$\mrsun$).
-In reality, the thin \albert{transition region (TR)} has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses.
+In reality, the thin {transition region (TR)} has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses.
 To resolve these gradients in a global model would require excessive numerical resources.
-As described in \citet{Lio2009} and \citet{Sok2013}\albert{, the TR is artificially broaden to be resolved with a} finest grid resolution of 0.001\,$\mrsun$.
+As described in \citet{Lio2009} and \citet{Sok2013}{, the TR is artificially broaden to be resolved with a} finest grid resolution of 0.001\,$\mrsun$.
 To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot} =2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K.
@@
 At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region.
-Since the broadening of the transition region pushes the corona outwards, \albert{the AWSoM model achieves coronal conditions at height $\approx 1.05\,\mrsun$, below which results can not then be compared to coronal tomographic reconstructions.}
+Since the broadening of the transition region pushes the corona outwards, {the AWSoM model achieves coronal conditions at height $\approx 1.05\,\mrsun$, below which results can not then be compared to coronal tomographic reconstructions.}
 
-To drive \albert{the AWSoM model, estimates} of the photospheric magnetic field of the Sun \albert{are the main} input.
-Synoptic magnetograms are used to specify the initial and the boundary conditions of the \albert{magnetic field.} We use the PFSS model to extrapolate the 3D magnetic field (from the 2D photospheric magnetic field maps) using spherical harmonics.
+To drive {the AWSoM model, estimates} of the photospheric magnetic field of the Sun {are the main} input.
+Synoptic magnetograms are used to specify the initial and the boundary conditions of the {magnetic field.} We use the PFSS model to extrapolate the 3D magnetic field (from the 2D photospheric magnetic field maps) using spherical harmonics.
 The source surface is taken to be at 2.5 $\mrsun$.
@@
 In this work, we use the GONG synoptic map as input for CR-2082 (ADAPT-GONG maps are unavailable for CR-2082) and the ADAPT-GONG global magnetic field map for CR-2208.
-\albert{Based on results from previous efforts, for CR-2082} the magnetic field from the GONG map is scaled up by a factor of 1.85 \albert{for weak fields ($B_r< 5\,\rm{G}$), while no modification is applied in the case of} the ADAPT-GONG map for CR-2208.
+{Based on results from previous efforts, for CR-2082} the magnetic field from the GONG map is scaled up by a factor of 1.85 {for weak fields ($B_r< 5\,\rm{G}$), while no modification is applied in the case of} the ADAPT-GONG map for CR-2208.
 The AWSoM steady-state simulation set-up and input parameters for both rotations are described below.
 
-To account for the energy partitioning between electrons and protons, based on \citet{Cha2011}, we set the stochastic heating exponent \albert{equal to} 0.21 and the amplitude equal to \albert{0.18, for both} rotations.
-The boundary condition for Alfv\'{e}n wave energy is given by the \albert{poynting flux ($S_{A}$)} of the outgoing \albert{wave, $({S_{A}/}{B})_{\odot} = 1.1\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ and $1.0\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ for CR-2082 and CR-2208, respectively, whith $B_{\odot}$ being the field} strength at the inner boundary.
-The correlation length of the Alfv\'{e}n waves is set \albert{to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$m\,$\sqrt{T}$.}
+To account for the energy partitioning between electrons and protons, based on \citet{Cha2011}, we set the stochastic heating exponent {equal to} 0.21 and the amplitude equal to {0.18, for both} rotations.
+The boundary condition for Alfv\'{e}n wave energy is given by the {poynting flux ($S_{A}$)} of the outgoing {wave, $({S_{A}/}{B})_{\odot} = 1.1\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ and $1.0\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ for CR-2082 and CR-2208, respectively, whith $B_{\odot}$ being the field} strength at the inner boundary.
+The correlation length of the Alfv\'{e}n waves is set {to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$m\,$\sqrt{T}$.}
 
-\albert{The computational domain of the solar corona} extends from 1 to \albert{$24\,\mrsun$}.
-The spherical grid in the solar corona is radially stretched (with a maximum resolution \albert{of $0.001\,\mrsun$} near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates.
-The Adaptive Mesh Refinement (AMR) resolves the angular cell \albert{size to $1.4\mdeg$ in the range of heights $1-1.7\,\mrsun$ and beyond $2.8\,\mrsun$}.
+{The computational domain of the solar corona} extends from 1 to {$24\,\mrsun$}.
+The spherical grid in the solar corona is radially stretched (with a maximum resolution {of $0.001\,\mrsun$} near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates.
+The Adaptive Mesh Refinement (AMR) resolves the angular cell {size to $1.4\mdeg$ in the range of heights $1-1.7\,\mrsun$ and beyond $2.8\,\mrsun$}.
 \notebyalbert{(by Albert) does this make sense?} The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082.
@@
 {To determine} the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid.
-Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = \albert{r\,{\rm d}\theta}/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point.
-In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, \albert{for a total of $97,200$ starting points.}
+Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = {r\,{\rm d}\theta}/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point.
+In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, {for a total of $97,200$ starting points.}
 
@@
 
-\albert{In the corona, EUV emission is dominated by collisions of the emitting ions with free electrons, so that the radiative power scales as $N_e^2$.
+{In the corona, EUV emission is dominated by collisions of the emitting ions with free electrons, so that the radiative power scales as $N_e^2$.
 The radiative power of an isothermal plasma at temperature $T$ is then computed as $E_r=N_e^2\,\Lambda(T)$, where the radiative loss function $\Lambda(T)$ is calculated by means of an emission model.
@@
 {The energy balance given by Equation \ref{Balance} is then integrated in the volume of any given coronal magnetic flux tube.
-Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a \albert{field line integrated} version of that energy balance is found,
+Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a {field line integrated} version of that energy balance is found,
 \begin{equation}\label{FluxBalance}
@@
 \noindent
-where the \albert{line-integrated} flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\
+where the {line-integrated} flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\
 
@@
 
-\noindent \albert{where $L$ is the length of the loop, and $B_0$ and $B_L$ are the values of the magnetic field at the footpoint locations of the loop in the coronal base, namely $s=0$ and $s=L$.} {Note that, for any given field line, all quantities in these two expresions can be computed \albert{from the DEMT results traced along field lines, and the AWSoM magnetic field model,} through Equations \ref{Fc}-\ref{Er}.
+\noindent {where $L$ is the length of the loop, and $B_0$ and $B_L$ are the values of the magnetic field at the footpoint locations of the loop in the coronal base, namely $s=0$ and $s=L$.} {Note that, for any given field line, all quantities in these two expresions can be computed {from the DEMT results traced along field lines, and the AWSoM magnetic field model,} through Equations \ref{Fc}-\ref{Er}.
 Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to mantain a stable coronal structure.}
@@
 Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}).
-Thick-black {curves indicate} the {open/closed boundaries of the magnetic field of the} AWSoM model.
+Thick-black {curves indicate} the {open/closed boundaries of the magnetic field of the} AWSoM model\albert{, detailed in Section \ref{awsom}.}
 
@@
 {Both target rotations are highly axisymmetric, \textit{i.e.} characterized by a high azymuthal symmetry.
-Rotation CR-2082} showed two {small} ARs, both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg$  \albert{(not identified in the NOAA catalog)}.
+Rotation CR-2082} showed two {small} ARs, both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg$  {(not identified in the NOAA catalog)}.
 {Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$ {(NOAA 12722, 12721)}.}
@@
 {{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively higher densities and temperatures in comparison to the CHs.
-They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 23 and 24}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the \albert{end of the declining} phase of {SC 24}, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious.
+They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 23 and 24}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the {end of the declining} phase of {SC 24}, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious.
 This thermodynamic structure of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
@@
 
-Figure \ref{Br} shows carrington maps of \albert{the radial} magnetic \albert{field ($B_r$)} for both rotations at $1.005\, \mrsun$.
-\albert{Both maps clearly show the large-scale dipolar field, characteristic of solar minimum conditions.
-Differences between both maps are observed in the sub-polar latitudes, due to the different treatments applied there by the GONG (CR-2082) and the ADAPT-GONG (CR-2208) maps.}
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/map_Br_awsom_2082_185_extend_1005_Rsun.pdf}
-\includegraphics[width=0.495\textwidth,clip=]{figs/map_Br_awsom_2208_185_extend_1005_Rsun.pdf}
-\caption{Carrington maps of radial magnetic field obtained with AWSoM at $1.005 \, \mrsun$ for CR-2082 (left) and CR-2208 (right). }
-\label{Br}
-\end{center}
-\end{figure}
 {To characterize the DEMT results in different magnetic structures, we traced} $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.
@@
 
-\albert{For both target rotations,} Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature.
+\albert{Figure \ref{Br} shows carrington maps of {the radial} magnetic {field ($B_r$)} for both rotations at $1.005\, \mrsun$.
+{Both maps clearly show the large-scale dipolar field, characteristic of solar minimum conditions.
+Differences between both maps are observed in the sub-polar latitudes, due to the different treatments applied there by the GONG (CR-2082) and the ADAPT-GONG (CR-2208) maps.}}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{figs/map_Br_awsom_2082_185_extend_1005_Rsun.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/map_Br_awsom_2208_185_extend_1005_Rsun.pdf}
+\caption{Carrington maps of {the radial magnetic field $B_r$ of the AWSoM model} at $1.005 \, \mrsun$ for CR-2082 (left) and CR-2208 (right). }
+\label{Br}
+\end{center}
+\end{figure}
+
+{For both target rotations,} Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature.
 {Maps are shown} at the same three heights selected for visualization of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}.
@@
 
-{Being highly axisymmtric target rotations, the longitude-averaged latitudinal \albert{profile} of the results of both models is an informative way to compare their large-scale structure.
+{Being highly axisymmtric target rotations, the longitude-averaged latitudinal {profile} of the results of both models is an informative way to compare their large-scale structure.
 Such comparison is shown in Figure \ref{perf_lat} at height $1.105\,\mrsun$, with top panels comparing electron density and mid panels electron temperature.
-\albert{The longitude-averaged latitudinal profile of $B_r$ is shown in the bottom panels.} In these longitude-averaged profiles, longitudes containing ARs or low latitude CHs were excluded.
+{The longitude-averaged latitudinal profile of $B_r$ is shown in the bottom panels.} In these longitude-averaged profiles, longitudes containing ARs or low latitude CHs were excluded.
 In each panel the averaged latitudinal variation for the DEMT model is shown in solid-line style, while the result for the AWSoM model is shown in dashed-linesyle.
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2208_1105_2.pdf}
-\caption{Longitude-averaged latitudinal dependence of the electron density (top), temperature (mid) and $Br$ for CR-2082 (blue) and CR-2208 (red) results at $1.105\,\mrsun$.
+\caption{Longitude-averaged latitudinal dependence of the electron density ({top panels}), {electron temperature ({middle panels})} and {radial magnetic field $B_r$ (bottom panels), for target rotations} CR-2082 ({blue color, left panels}) and CR-2208 ({red color, right panels) at} $1.105\,\mrsun$.
 Dashed lines correspond to AWSoM results while solid line to DEMT.
@@
 Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend.
-\albert{For comparison, note the beahavior of $B_r$ in the CHs, increasing from the open/closed boudary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}
+{For comparison, note the beahavior of $B_r$ in the CHs, increasing from the open/closed boudary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}
 
@@
 
-%\notebyalbert{We could quantify the anti-correlation between the AWSoM terminal speed and the DEMT electron density at the coronal base in the following fashion.
-We can set up starting points at, say, $20\,\mrsun$, every one degree, both in latitude and longitude.
-This would mean setting up $180\times 360$ starting points.
-We trace then the (open) field lines from each of those starting points down to $1.0\,\mrsun$ to find out the DEMT results at those lower heights for each field line.
-Now, to do this we need to develop some codes and have no time for this paper.
-We can postpone it for a next effort, or...
-Chip: do you think you could do this with your present tools?
-Do you think it is interesting?
-I think so.
-Our submission deadline is 24 January.}
-
 \begin{figure}[h!]
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995_2.pdf}
-\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6.0\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).} %\notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the absolute minimum indicates the location of the HCS at this height.
-I believe it is interesting to compare these two curves with Figure 10.
-Note that while in this Figure all latitudes are magnetically open, in Figure 10 only the part at latitudes larger than the vertical black lines are open.
-Note that DEMT shows that in the open low corona $N_e$ decreases from the O/C boundary towards the poles, anti-correlating with the AWSoM terminal speed, which is nice.
-In order to quantify this anti-correlation we need to trace the terminal speed and the DEMT $N_e$, which we may need to do with the help of Chip and Nishtha.
-Chip, we can discuss this idea over Skype after Xmas if you are around.}
-}
+\caption{{Longitude-averaged latitudinal dependence of the AWSoM model \albert{wind speed $V_r$} at $6.0\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).}}
 \label{perf_lon_vr}
@@
 {Based on the magnetic field of AWSoM model and the results of the DEMT model for electron density and temperature, we classified coronal structures in four different types.
-Smaller legs in the core of the streamer belt are classified in down/up types according to their temperature decreasing/increasing with height (dubbed type 0/I).
-Larger closed legs of type up that form the envelope of the streamer belt (dubbed type II), and open field lines of type up populating the CHs (dubbed type III).}
+\albert{Small loop legs} in the core of the streamer belt are classified in down/up types according to their temperature decreasing/increasing with height (dubbed type 0/I).
+\albert{Large closed legs} of type up that form the envelope of the streamer belt (dubbed type II), and open field lines of type up populating the CHs (dubbed type III).}
 
@@
 {{For both target rotations}, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.
-In the case of the AIA based DEMT reconstruction, we show that in a substantial fraction of the CHs region the technique performs poorly in modeling LDEMs that predict the tomographic emissivitiy in each EUV band with reasonable accuracy.
-As a result, DEMT results based on AIA data are currently less reliable in the CH region.
+In the case of the \albert{DEMT reconstruction based on AIA data we show that, in} a substantial fraction of the \albert{voxels of the CHs,} the technique performs poorly in modeling \albert{an LDEM that predicts} the tomographic emissivitiy in each EUV band with reasonable accuracy.
+As a result, DEMT results based on AIA data \albert{are less reliable CHs}.
 This was already found by the existing two previous DEMT works based on AIA data \citep{nuevo_2015,maccormack_2017}.
@@
 
-In comparing the DEMT results obtained for the two selected targets, {we highlight here that} they rely on data provided by two different instruments, {namely EUVI and AIA for CR-2082 and CR-2208, respectively.} In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
+In comparing the DEMT results obtained for the two selected targets, \albert{we highlight} they rely on data provided by two different instruments, {namely EUVI and AIA for CR-2082 and CR-2208, respectively.} In order to quantify the systematic difference of the DEMT products \albert{due to the different filter sets of} both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
 They found that while the density {products are} essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, \textit{i.e.} $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$.
@@
 
-Results of the AWSoM model are compared to those of the DEMT reconstructions in the range of coronal heights $\approx 1.05-1.20\,\mrsun$ simultaneously covered by both models.
-In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines.
+Results of the AWSoM model \albert{were compared} to those of the DEMT reconstructions \albert{in the range of coronal heights simultaneously covered by both models, namely $\approx 1.05-1.20\,\mrsun$.} In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines.
 The detailed comparison shown in this work can be summarized as follows.
 For CR-2082, the electron density of both models agree within $\approx 20\%$ {in most regions}, while for CR-2208 the agreement is within $\approx 5\%$.
-{The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations{, with larger discrepancies in the CHs.} This level of agreement between both models \albert{(within or slightly beyond the uncertainty level of DEMT results)} is considerably better than that reported in previous works.
-\citet{jin_2012} and \citet{oran_2015} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.} \notebyalbert{Chip, if Section 2.2 explains the most significant improvements of AWSoM since the version used in those references, we can comment on the reason for the improvement here.}
-\diego{Note by Diego: Chip, Nishtha, if you think we can relate some differences or observed trends of AWSoM with the magnetic field, this could be a good place, but I need your insight here.}
+{The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations{, with larger discrepancies in the CHs.} This level of agreement between both models {(within or slightly beyond the uncertainty level of DEMT results)} is considerably better than that reported in previous works.
+\citet{jin_2012} and \citet{oran_2015}\albert{, who used previous versions of the AWSoM model,} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.}
 
-{Within the \albert{excellent quantitative match between both models,} summarized in the previous paragraph, there are some qualitative agreements and \albert{disagreements worth noticing}.
+\albert{The overal better match of the results of the current version of the AWSoM model when compared to DEMT reconstructions is partly due to the improved energy partitioning scheme of the model, described in Section \ref{awsom}.
+Note also that the simulation of CR-2082 used GONG maps as boundary condition, while the simulation of CR-2208 used the improved ADAPT-GONG maps.
+This is most probably the cause that the results of the AWSoM model show a more accurate match to the DEMT reconstructions in the case of CR-2208.}
+
+Within the {excellent quantitative match between both \albert{models summarized} in the previous paragraph, there are some qualitative agreements and {disagreements worth noticing}.
 For both target rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
-On the other hand, while the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
-Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), the AWSoM model shows the opposite trend.
-This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.} \notebyalbert{Chip: Even if the match AWSoM/DEMT is quantitatively pretty good, this qualitative opposite behavior is off putting.
-Do you think there is room for improvement in the AWSoM model here?
-Maybe worth mentioning?}
+On the other hand, while the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density \albert{(physically expected in transitioning from magnetically closed to open regions)}, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
+Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), \albert{as expected in transitioning from the source region of the slow to the fast component of the solar wind}, the AWSoM model shows the opposite trend.
+This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.} \albert{These unphysical characteristics of the results of the AWSoM model in the rage of low heights analysed here ($r\lesssim 1.2\,\mrsun$), may be traced down to the less reliable values of $B_r$ provided by both the GONG and ADAPT-GONG maps at subpolar latitudes, rather than a limitation of the model itself.
+This will be further investigated in a follow up article focusing on the current deep minimum epoch, during which the large-scale corona shows the simplest possible structure.}
 

### 2020-01-27 lloveras_2020.tex
version final?

@@
 Solar rotational tomography is currently the sole observational technique {able to provide} a 3D quantitative description of the solar corona at a global scale.
-Based on {extreme ultraviolet} images {of space} borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$.
+Based on {extreme ultraviolet} images {of space} borne instruments, {differential emission measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$.
 We carry out a study of the corona {through DEMT} reconstructions {and MHD simulations, using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) developed at the University of Michigan as a component of the Space Weather Modeling Framework.
-{Two target} rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the {end of the} declining} phase of SC 24.
+{Two target} rotations were selected from the solar minimum between solar cycles (SCs) 23 and 24 and {the {end of the} declining} phase of SC 24.
 The 3D {DEMT} and MHD models are analysed and compared in distinct coronal magnetic structures.
@@
 {In SRT, solar rotation is taken advantage of, so that instruments gather time series of images covering all viewing angles of the solar corona.
-This allows posing an inversion problem to solve for the uncknown 3D distribution of specific quantities of the solar corona.
-Based on extreme ultraviolet EUV images, taken in several channels sensitive to different temperatures, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM).
+This allows posing an inversion problem to solve for the unknown 3D distribution of specific quantities of the solar corona.
+Based on extreme ultraviolet (EUV) images, taken in several channels sensitive to different temperatures, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM).
 The final product of DEMT is in the form of 3D maps of electron density and temperature, covering the range of heliocentric heights $\lesssim 1.25\,\mrsun$.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}.
@@
 
-The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space {Wea\-ther} Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to {1 AU and beyond} \citep{vander_2010, Van2014}.
+The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space {Weather} Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to {1 AU and beyond} \citep{vander_2010, Van2014}.
 {The single data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation.
@@
 We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during {the end of the declining} phase of SC 24.
-{In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} {(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG).
+{In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} {(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG: \citealt{gong}).
 In the case of CR-2208, the DEMT analysis is based in data taken} by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} {(SDO), while the AWSoM model uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}
@@
 This has two implications.
-Fistly, the fast dynamics that typically characterizes those structures is abscent from the data.
-Sencondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume.
+Firstly, the fast dynamics that typically characterizes those structures is absent from the data.
+Secondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume.
 As a result, {artifacts induced by coronal dynamics} are reduced compared to previous DEMT reconstructions.}
@@
 {The solution of the tomographic problem involves {inversion of} a very large sparse matrix.
-Such inversion problems are characterized by spurious {high-fre\-quen\-cy} artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}.
+Such inversion problems are characterized by spurious {high-frequency} artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}.
 In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude.
@@
 \begin{equation}\label{fbeldem}
-\FBE_i^{(k)}  = \int\,\textrm{d}T\,\LDEM_i(T)\,{\TRF}^{(k)}(T), \ \ \ {k=1,...,K}
+\FBE_i^{(k)}  = \int\,\textrm{d}T\,\LDEM_i(T)\,{\TRF}^{(k)}(T), \ \ \ {k=1,...,K} \,,
 \end{equation}
@@
 The source surface is taken to be at 2.5 $\mrsun$.
-The Global Oscillation Network Group (GONG) provides synoptic full-disk surface maps of the radial magnetic field component of the Sun.
+GONG provides synoptic full-disk surface maps of the radial magnetic field component of the Sun.
 However, since the polar regions are not well observed from the ecliptic, GONG estimates the polar fields by fitting a polynomial to neighboring observed latitudes, which might lead to inaccuracies.
@@
 To account for the energy partitioning between electrons and protons, based on \citet{Cha2011}, we set the stochastic heating exponent {equal to} 0.21 and the amplitude equal to {0.18, for both} rotations.
-The boundary condition for Alfv\'{e}n wave energy is given by the {poynting flux ($S_{A}$)} of the outgoing {wave, $({S_{A}/}{B})_{\odot} = 1.1\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ and $1.0\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ for CR-2082 and CR-2208, respectively, whith $B_{\odot}$ being the field} strength at the inner boundary.
+The boundary condition for Alfv\'{e}n wave energy is given by the {poynting flux ($S_{A}$)} of the outgoing {wave, $({S_{A}/}{B})_{\odot} = 1.1\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ and $1.0\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ for CR-2082 and CR-2208, respectively, with $B_{\odot}$ being the field} strength at the inner boundary.
 The correlation length of the Alfv\'{e}n waves is set {to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$m\,$\sqrt{T}$.}
@@
 The spherical grid in the solar corona is radially stretched (with a maximum resolution {of $0.001\,\mrsun$} near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates.
-The Adaptive Mesh Refinement (AMR) resolves the angular cell {size to $1.4\mdeg$ in the range of heights $1-1.7\,\mrsun$ and beyond $2.8\,\mrsun$}.
-\notebyalbert{(by Albert) does this make sense?} The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082.
+The Adaptive Mesh refinement (AMR) resolves the angular cell size to $1.4\mdeg$ between $1 - 1.7\,\mrsun$ and to $2.8\mdeg$ outside this radius range.
+The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082.
 Local time stepping is used to speed up the steady state convergence.
@@
 
-\subsection{{Tracing Results Along Magnetic Field lines}}\label{trace}
+\subsection{{Tracing Results Along Magnetic Field Lines}}\label{trace}
 
@@
 \begin{eqnarray}\label{Nfit}
-\sqravgN &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]}\\
+\sqravgN &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]} \,,\\
 \label{Tfit}
-\Tm &=& T_0\,+\,m\,h
+\Tm &=& T_0\,+\,m\,h \,,
 \end{eqnarray}
@@
 \item 
-{The condifence level of both the exponential and linear fits must be larger than 90\%.} 
+{The confidence level of both the exponential and linear fits must be larger than 90\%.} 
 \end{enumerate}
@@
 \\
-In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed.
+In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic structures are statistically analysed.
 {As shown in Section \ref{demt_res}, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}
@@
 While the vast majority of the existing literature on coronal heating focuses on active regions (ARs), some studies have been dedicated to the heating of quiet-Sun regions.
-In particular,  \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to mantain stability.
+In particular,  \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to maintain stability.
 The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in Section \ref{trace}.}
@@
 \noindent
-where $s$ is the position along {the flux tube} and the {power quntities} are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.
+where $s$ is the position along {the flux tube} and the {power quantities} are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.
 
@@
 {The energy balance given by Equation \ref{Balance} is then integrated in the volume of any given coronal magnetic flux tube.
-Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a {field line integrated} version of that energy balance is found,
+Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal condition of the magnetic field, a {field line integrated} version of that energy balance is found,
 \begin{equation}\label{FluxBalance}
@@
 \noindent
-where the {line-integrated} flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\
+where the {line-integrated} flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017}:} \\
 
@@
 
-\noindent {where $L$ is the length of the loop, and $B_0$ and $B_L$ are the values of the magnetic field at the footpoint locations of the loop in the coronal base, namely $s=0$ and $s=L$.} {Note that, for any given field line, all quantities in these two expresions can be computed {from the DEMT results traced along field lines, and the AWSoM magnetic field model,} through Equations \ref{Fc}-\ref{Er}.
-Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to mantain a stable coronal structure.}
+\noindent {where $L$ is the length of the loop, and $B_0$ and $B_L$ are the values of the magnetic field at the footpoint locations of the loop in the coronal base, namely $s=0$ and $s=L$.} {Note that, for any given field line, all quantities in these two expressions can be computed {from the DEMT results traced along field lines, and the AWSoM magnetic field model,} through Equations \ref{Fc}-\ref{Er}.
+Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to maintain a stable coronal structure.}
 
@@
 Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}).
-Thick-black {curves indicate} the {open/closed boundaries of the magnetic field of the} AWSoM model\albert{, detailed in Section \ref{awsom}.}
+Thick-black {curves indicate} the {open/closed boundaries of the magnetic field of the} AWSoM model{, detailed in Section \ref{awsom}.}
 
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2082_fulltriple_gradt.eps}
-\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
+\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2082_full_doble_errortriple_gradt.eps}
+\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_full_doble_errortriple_gradt.eps}
 \caption{Frequency histograms of the temperature radial gradient for {the four types of legs} in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
@@
 
-\albert{Figure \ref{Br} shows carrington maps of {the radial} magnetic {field ($B_r$)} for both rotations at $1.005\, \mrsun$.
+{Figure \ref{Br} shows carrington maps of {the radial} magnetic {field ($B_r$)} for both rotations at $1.005\, \mrsun$.
 {Both maps clearly show the large-scale dipolar field, characteristic of solar minimum conditions.
@@
 {{Several details from Figure \ref{perf_lat} are worth being highlighted.
-Firstly, at most latitudes the overal agreement of the electron density of both models is within $\approx 20\%$ for CR-2082, and $\approx 5\%$ for CR-2208.
+Firstly, at most latitudes the overall agreement of the electron density of both models is within $\approx 20\%$ for CR-2082, and $\approx 5\%$ for CR-2208.
 The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.
-In the case of the electron temperature, for both target rotations the models agree within $\approx 15\%$ at all latitudes of the streamer belt, showing larger discrepancies in the CHs.} Secondly, for both target rotations, and for both models, these plots clearly show the relatively lower temperatures characterising the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
+In the case of the electron temperature, for both target rotations the models agree within $\approx 15\%$ at all latitudes of the streamer belt, showing larger discrepancies in the CHs.} Secondly, for both target rotations, and for both models, these plots clearly show the relatively lower temperatures characterizing the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
 Thirdly, for both target rotations, the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density.
@@
 Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend.
-{For comparison, note the beahavior of $B_r$ in the CHs, increasing from the open/closed boudary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}
+{For comparison, note the behavior of $B_r$ in the CHs, increasing from the open/closed boundary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}
 
@@
 For target rotation CR-2208 the agreement of the median value of $\NCB$ and $\lN$ of both models {is within $10\%$, while} median values of $\aTm$ agree within $15\%$.
-{These detailed results, being consistent with the large-scale comparison provided in Figure \ref{perf_lat}, show in detail how the AWSoM model performs compard to DEMT in different magetic strucures.}}
+{These detailed results, being consistent with the large-scale comparison provided in Figure \ref{perf_lat}, show in detail how the AWSoM model performs compared to DEMT in different magnetic structures.}}
 
@@
 
-{As discussed above, Figure \ref{perf_lat} shows that the logitude-averaged latitudinal profile of the DEMT electron density in the CHs decreases towards the poles.
+{As discussed above, Figure \ref{perf_lat} shows that the longitude-averaged latitudinal profile of the DEMT electron density in the CHs decreases towards the poles.
 Figure \ref{perf_lon_vr} below shows the longitude-averaged AWSoM radial wind speed $V_r$ at $6\,\mrsun$, where all field lines are open.
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995_2.pdf}
-\caption{{Longitude-averaged latitudinal dependence of the AWSoM model \albert{wind speed $V_r$} at $6.0\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).}}
+\caption{{Longitude-averaged latitudinal dependence of the AWSoM model {wind speed $V_r$} at $6.0\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).}}
 \label{perf_lon_vr}
@@
 {Based on the magnetic field of AWSoM model and the results of the DEMT model for electron density and temperature, we classified coronal structures in four different types.
-\albert{Small loop legs} in the core of the streamer belt are classified in down/up types according to their temperature decreasing/increasing with height (dubbed type 0/I).
-\albert{Large closed legs} of type up that form the envelope of the streamer belt (dubbed type II), and open field lines of type up populating the CHs (dubbed type III).}
+{Small loop legs} in the core of the streamer belt are classified in down/up types according to their temperature decreasing/increasing with height (dubbed type 0/I).
+{Large closed legs} of type up that form the envelope of the streamer belt (dubbed type II), and open field lines of type up populating the CHs (dubbed type III).}
 
@@
 {{For both target rotations}, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.
-In the case of the \albert{DEMT reconstruction based on AIA data we show that, in} a substantial fraction of the \albert{voxels of the CHs,} the technique performs poorly in modeling \albert{an LDEM that predicts} the tomographic emissivitiy in each EUV band with reasonable accuracy.
-As a result, DEMT results based on AIA data \albert{are less reliable CHs}.
+In the case of the {DEMT reconstruction based on AIA data we show that, in} a substantial fraction of the {voxels of the CHs,} the technique performs poorly in modeling {an LDEM that predicts} the tomographic emissivity in each EUV band with reasonable accuracy.
+As a result, DEMT results based on AIA data {are less reliable CHs}.
 This was already found by the existing two previous DEMT works based on AIA data \citep{nuevo_2015,maccormack_2017}.
@@
 
-In comparing the DEMT results obtained for the two selected targets, \albert{we highlight} they rely on data provided by two different instruments, {namely EUVI and AIA for CR-2082 and CR-2208, respectively.} In order to quantify the systematic difference of the DEMT products \albert{due to the different filter sets of} both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
+In comparing the DEMT results obtained for the two selected targets, {we highlight} they rely on data provided by two different instruments, {namely EUVI and AIA for CR-2082 and CR-2208, respectively.} In order to quantify the systematic difference of the DEMT products {due to the different filter sets of} both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
 They found that while the density {products are} essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, \textit{i.e.} $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$.
@@
 
-Results of the AWSoM model \albert{were compared} to those of the DEMT reconstructions \albert{in the range of coronal heights simultaneously covered by both models, namely $\approx 1.05-1.20\,\mrsun$.} In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines.
+Results of the AWSoM model {were compared} to those of the DEMT reconstructions {in the range of coronal heights simultaneously covered by both models, namely $\approx 1.05-1.20\,\mrsun$.} In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines.
 The detailed comparison shown in this work can be summarized as follows.
@@
 {The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations{, with larger discrepancies in the CHs.} This level of agreement between both models {(within or slightly beyond the uncertainty level of DEMT results)} is considerably better than that reported in previous works.
-\citet{jin_2012} and \citet{oran_2015}\albert{, who used previous versions of the AWSoM model,} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.}
+\citet{jin_2012} and \citet{oran_2015}{, who used previous versions of the AWSoM model,} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.}
 
-\albert{The overal better match of the results of the current version of the AWSoM model when compared to DEMT reconstructions is partly due to the improved energy partitioning scheme of the model, described in Section \ref{awsom}.
+{The overall better match of the results of the current version of the AWSoM model when compared to DEMT reconstructions is partly due to the improved energy partitioning scheme of the model, described in Section \ref{awsom}.
 Note also that the simulation of CR-2082 used GONG maps as boundary condition, while the simulation of CR-2208 used the improved ADAPT-GONG maps.
@@
 
-Within the {excellent quantitative match between both \albert{models summarized} in the previous paragraph, there are some qualitative agreements and {disagreements worth noticing}.
+Within the {excellent quantitative match between both {models summarized} in the previous paragraph, there are some qualitative agreements and {disagreements worth noticing}.
 For both target rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
-On the other hand, while the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density \albert{(physically expected in transitioning from magnetically closed to open regions)}, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
-Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), \albert{as expected in transitioning from the source region of the slow to the fast component of the solar wind}, the AWSoM model shows the opposite trend.
-This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.} \albert{These unphysical characteristics of the results of the AWSoM model in the rage of low heights analysed here ($r\lesssim 1.2\,\mrsun$), may be traced down to the less reliable values of $B_r$ provided by both the GONG and ADAPT-GONG maps at subpolar latitudes, rather than a limitation of the model itself.
+On the other hand, while the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density {(physically expected in transitioning from magnetically closed to open regions)}, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
+Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), {as expected in transitioning from the source region of the slow to the fast component of the solar wind}, the AWSoM model shows the opposite trend.
+This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.} {These unphysical characteristics of the results of the AWSoM model in the rage of low heights analysed here ($r\lesssim 1.2\,\mrsun$), may be traced down to the less reliable values of $B_r$ provided by both the GONG and ADAPT-GONG maps at subpolar latitudes, rather than a limitation of the model itself.
 This will be further investigated in a follow up article focusing on the current deep minimum epoch, during which the large-scale corona shows the simplest possible structure.}
 
-A detailed empirical description of the 3D termodynamic structure of the inner corona at a global scale is currently only possible with tomographic techniques, such as DEMT.
+A detailed empirical description of the 3D thermodynamic structure of the inner corona at a global scale is currently only possible with tomographic techniques, such as DEMT.
 Using tomographic results for continuous validation of 3D MHD models is of high relevance for the continued improvement of models.

### 2020-01-29 lloveras_2020.tex

@@
 
-\keywords{Solar Cycle, Observations; Corona,E; Corona, Structures}
+%\keywords{Solar Cycle, Observations; Corona,E; Corona, Structures}
+\keywords{Solar Cycle, Observations; Corona, E; Corona, Structures; Corona, Models; Magnetohydrodynamics}
 
@@
 Based on spectroscopic data of the EIS instrument in quiet-Sun regions \citet{hahn_2014} showed that, if the observed non-thermal broadening are assigned to Alfvén waves, their energy flux at the coronal base is estimated to be in the range $\approx 1.5-2.5\times 10^5\,\erg\,\cminvs\,\s^{-1}$.
-A large fraction of the coronal base energy input flux $\phi_h$ estimated in this work, or even its totality, could then be accounted for by Alfvén waves.}
+A large fraction of the coronal base energy input flux $\phi_h$ estimated in this work, or even its totality, could then be accounted for by Alfvén waves (see the discussion in \citealt{maccormack_2017}).}
 

### 2020-01-29 lloveras_2020.tex
alguna que otra modificacion del rich

@@
 
-{The combination of DEMT with global magnetic models provides insight} into the 3D thermodynamical structure of the global quiet-Sun corona.
+{The combination of DEMT with global magnetic models provides insight} into the 3D thermodynamical structure of the global corona.
 {DEMT was first combined with a potential field source surface (PFSS) model by \citet{huang_2012} and \citet{nuevo_2013}.
@@
 The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space {Weather} Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to {1 AU and beyond} \citep{vander_2010, Van2014}.
-{The single data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation.
+{The only data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation.
 As new improvements are implemented, the model is continuously being validated with observations.} DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona.
@@
 
-{Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies.
-As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
+{Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported the presence of down loops.
+As speculated by the authors of those works, down loops can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
 Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}.
@@
 
-{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, \textit{i.e.} $E_c(s)=[1/A(s)]\,{\rm d}[A(s)\,F_c(s)]/{\rm d}s$, where $A(s)$ is the transversal area of the magnetic flux tube at position $s$.
+{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, \textit{i.e.} $E_c(s)=[1/A(s)]\,{\rm d}[A(s)\,F_c(s)]/{\rm d}s$, where $A(s)$ is the transverse area of the magnetic flux tube at position $s$.
 Under a quiescent solar corona plasma regime, the conductive flux is assumed to be dominated by the electron thermal conduction, described by the usual Spitzer model \citep{spitzer_1962}
@@
 where $\kappa_0 = 9.2 \times 10^{-7}  {\rm erg\,sec^{-1}\,K^{-7/2}}$ is the Spitzer thermal conductivity.}
-
-Radiative power depends on the amount of plasma in certain temperatures that can radiate.
 
@@
 {The magnetically open and closed regions of the AWSoM model are associated with Coronal holes (CHs) and the equatorial streamer belt, respectively.
-The {location of the} open/closed boundaries derived from the respective AWSoM model quite accurately matchs {the regions of the DEMT maps, which exhibit the strongest latitudinal gradient of both the electron density and temperature.}}
+The {location of the} open/closed boundaries derived from the respective AWSoM model quite accurately matches {the regions of the DEMT maps, which exhibit the strongest latitudinal gradient of both the electron density and temperature.}}
 
@@
 They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 23 and 24}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the {end of the declining} phase of {SC 24}, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious.
-This thermodynamic structure of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
+This thermodynamic structure of the streamer has been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
 

### 2020-01-29 agregados_albert.tex
..

* Un párrafo para poner al discutir la Figura 5 en las conclusiones. Tenés que agregar a tu BIB el ApJ 2015 de Nuevo et al.

In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI. In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, analyzed a single target using both instruments independently. They found that while the density product is essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e. $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$. Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR2208 was $\approx 10-15\%$ hotter than CR2082 throughout the streamer belt region. As for the electron density products, CR2208 was found to be $\approx 15-20\%$ less dense than CR2082 throughout the streamer belt region. These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\lesssim 5\%$ and $\approx 2\%$ for the electron temperature and density, respectively.

Aquí indico como estimé estas diferencias basado en los valores MEDIANOS informados en los paneles de la Figura 5 (no en la Tabla), y usando los factores de corrección 1.08 y 0.98 para Sqrt(Nm) y Tm del paper de Fede del 2015. Las incertezas las extraje de la Tabla 7 del SolPhys de Diego del 2017, usando los valores Sigma/Mu

IDL> print,( [1.36,1.55,1.55]/1.08 - [1.09,1.29,1.33] ) / [1.09,1.29,1.33]
     0.155284     0.112547    0.0790865
IDL> 
IDL> print,( [1.04,0.97,0.77]/0.98 - [1.26,1.13,0.98] ) / [1.26,1.13,0.98]
    -0.157758    -0.124074    -0.198251

### 2020-01-29 lloveras_2020_Albert.tex
..

@@
 \begin{abstract}
-Observational techniques play an essential role in advancing our understanding of the physical processes governing the solar corona, providing in \albert{particular validation} data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere.
-Solar rotational tomography is currently the sole observational technique \albert{able to provide} a 3D quantitative description of the solar corona at a global scale.
-Based on {extreme ultraviolet} images \albert{of space} borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$.
-We carry out a study of the corona \albert{through DEMT} reconstructions \albert{and MHD simulations, using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) developed at the University of Michigan as a component of the Space Weather Modeling Framework.
-\albert{Two target} rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the \albert{end of the} declining} phase of SC 24.
-The 3D \albert{DEMT} and MHD models are analysed and compared in distinct coronal magnetic structures.
+Observational techniques play an essential role in advancing our understanding of the physical processes governing the solar corona, providing in {particular validation} data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere.
+Solar rotational tomography is currently the sole observational technique {able to provide} a 3D quantitative description of the solar corona at a global scale.
+Based on {extreme ultraviolet} images {of space} borne instruments, {differential emission measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$.
+We carry out a study of the corona {through DEMT} reconstructions {and MHD simulations, using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) developed at the University of Michigan as a component of the Space Weather Modeling Framework.
+{Two target} rotations were selected from the solar minimum between solar cycles (SCs) 23 and 24 and {the {end of the} declining} phase of SC 24.
+The 3D {DEMT} and MHD models are analysed and compared in distinct coronal magnetic structures.
 {We report in quantitative detail on the 3D thermodynamic structure of the inner corona as revealed by the DEMT analysis.
-We \albert{show the} existence of diverse types of temperature structures in the low and mid latitudes of the \albert{streamer belt.
-We estimate} the heating energy required to keep them \albert{stable, which we argue may} be accounted for by Alfvén waves.
-\albert{We also show that results of the latest version of the AWSoM model overal} agree with DEMT \albert{reconstructions within a $\approx 20\%$ accuracy.
-We highlight some details of the AWSoM model that should} be improved to better reproduce \albert{tomographic} results, in particular concerning the source region of the \albert{fast and slow components of the solar wind.}}
+We {show the} existence of diverse types of temperature structures in the low and mid latitudes of the {streamer belt.
+We estimate} the heating energy required to keep them {stable, which we argue may} be accounted for by Alfvén waves.
+{We also show that results of the latest version of the AWSoM model overal} agree with DEMT {reconstructions within a $\approx 20\%$ accuracy.
+We highlight some details of the AWSoM model that should} be improved to better reproduce {tomographic} results, in particular concerning the source region of the {fast and slow components of the solar wind.}}
 \end{abstract}
 
-\keywords{Solar Cycle, Observations; Corona,E; Corona, Structures}
+\keywords{\albert{Solar Cycle, Observations; Corona, E; Corona, Structures; Corona, Models; Magnetohydrodynamics}}
 
@@
 Being the {region} where the solar atmosphere is {heated, the solar wind accelerated}, and where impulsive events such as solar flares and coronal mass ejections are energized, observing and modeling of the solar corona are of great relevance to improving our understanding of the Sun-Earth environment.
-To advance our knowledge of the physics of the solar corona, as well as \albert{to enhance} and validate three-dimensional (3D) models, information derived from observational data plays a key role.
-Solar rotational tomography (SRT) is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar \albert{corona at a global} scale.
+To advance our knowledge of the physics of the solar corona, as well as {to enhance} and validate three-dimensional (3D) models, information derived from observational data plays a key role.
+Solar rotational tomography (SRT) is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar {corona at a global} scale.
 
-To study the \albert{3D structure of the quiet-Sun global corona,} SRT has proven to be a powerful tool.
-\albert{In SRT, solar rotation is taken advantage of, so that instruments gather time series of images covering all viewing angles of the solar corona.
-This allows posing an inversion problem to solve for the uncknown 3D distribution of specific quantities of the solar corona.
-Based on extreme ultraviolet EUV images, taken in several channels sensitive to different temperatures, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM).
+To study the {3D structure of the quiet-Sun global corona,} SRT has proven to be a powerful tool.
+{In SRT, solar rotation is taken advantage of, so that instruments gather time series of images covering all viewing angles of the solar corona.
+This allows posing an inversion problem to solve for the unknown 3D distribution of specific quantities of the solar corona.
+Based on extreme ultraviolet (EUV) images, taken in several channels sensitive to different temperatures, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM).
 The final product of DEMT is in the form of 3D maps of electron density and temperature, covering the range of heliocentric heights $\lesssim 1.25\,\mrsun$.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}.
-\albert{A recent review on DEMT was published by \citet{vasquez_2016}.
+{A recent review on DEMT was published by \citet{vasquez_2016}.
 The technique is summarized in Section \ref{demt}.}
 
-\albert{The combination of DEMT with global magnetic models provides insight} into the 3D thermodynamical structure of the global quiet-Sun corona.
-\albert{DEMT was first combined with a potential field source surface (PFSS) model by \citet{huang_2012} and \citet{nuevo_2013}.
-More recently,} \citet{lloveras_2017} combined DEMT with PFSS \albert{models to study the thermodynamics of the global solar corona in specific magnetic structures for two target rotations selected from the last two solar minimum epochs.
-Also combining DEMT with a PFSS model,} \citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux \albert{required at the coronal base in order to maintain stable coronal loops}.
-In this article, \albert{DEMT is first combined with the magnetic field of a magnetohydrodynamic (MHD) model.}
+{The combination of DEMT with global magnetic models provides insight} into the 3D thermodynamical structure of the global quiet-Sun corona.
+{DEMT was first combined with a potential field source surface (PFSS) model by \citet{huang_2012} and \citet{nuevo_2013}.
+More recently,} \citet{lloveras_2017} combined DEMT with PFSS {models to study the thermodynamics of the global solar corona in specific magnetic structures for two target rotations selected from the last two solar minimum epochs.
+Also combining DEMT with a PFSS model,} \citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux {required at the coronal base in order to maintain stable coronal loops}.
+In this article, {DEMT is first combined with the magnetic field of a magnetohydrodynamic (MHD) model.}
 
-The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space \albert{Wea\-ther} Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to \albert{1 AU and beyond} \citep{vander_2010, Van2014}.
-\albert{The single data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation.
+The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space {Weather} Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to {1 AU and beyond} \citep{vander_2010, Van2014}.
+{The single data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation.
 As new improvements are implemented, the model is continuously being validated with observations.} DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona.
@@
 
-\albert{Combining the DEMT and AWSoM models, we carry out a detailed quantitatively analysis of two target rotations.
-We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during \albert{the end of the declining} phase of SC 24.
-\albert{In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} \albert{(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG).
-In the case of CR-2208, the DEMT analysis is based in data taken} by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} \albert{(SDO), while the AWSoM model uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}
+{Combining the DEMT and AWSoM models, we carry out a detailed quantitatively analysis of two target rotations.
+We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during {the end of the declining} phase of SC 24.
+{In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} {(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG: \citealt{gong}).
+In the case of CR-2208, the DEMT analysis is based in data taken} by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} {(SDO), while the AWSoM model uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}
 
-Section \ref{demt} and \ref{awsom} \albert{summarize the DEMT technique and the AWSoM model, respectively.} Section \ref{trace} \albert{details} the method used to trace \albert{the DEMT} results along the field lines of the magnetic model.
-Section \ref{energia} details \albert{the method that allows determination of the energy input flux at the coronal base.} In Section \ref{demt_res} the quantitative \albert{detailed DEMT analysis of both target rotations is shown,} and in Section \ref{awsom_res} the AWSoM and DEMT results are compared.
-\albert{Finally, Section} \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.
+Section \ref{demt} and \ref{awsom} {summarize the DEMT technique and the AWSoM model, respectively.} Section \ref{trace} {details} the method used to trace {the DEMT} results along the field lines of the magnetic model.
+Section \ref{energia} details {the method that allows determination of the energy input flux at the coronal base.} In Section \ref{demt_res} the quantitative {detailed DEMT analysis of both target rotations is shown,} and in Section \ref{awsom_res} the AWSoM and DEMT results are compared.
+{Finally, Section} \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.
 
@@
 This has two implications.
-Fistly, the fast dynamics that typically characterizes those structures is abscent from the data.
-Sencondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume.
-As a result, \albert{artifacts induced by coronal dynamics} are reduced compared to previous DEMT reconstructions.}
+Firstly, the fast dynamics that typically characterizes those structures is absent from the data.
+Secondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume.
+As a result, {artifacts induced by coronal dynamics} are reduced compared to previous DEMT reconstructions.}
 
 {The solution of the tomographic problem involves {inversion of} a very large sparse matrix.
-Such inversion problems are characterized by spurious \albert{high-fre\-quen\-cy} artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}.
+Such inversion problems are characterized by spurious {high-frequency} artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}.
 In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude.
@@
 At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region.
-Since the broadening of the transition region pushes the corona outwards, \albert{the AWSoM model achieves coronal conditions at height $\approx 1.05\,\mrsun$, below which results can not then be compared to coronal tomographic reconstructions.}
+Since the broadening of the transition region pushes the corona outwards, {the AWSoM model achieves coronal conditions at height $\approx 1.05\,\mrsun$, below which results can not then be compared to coronal tomographic reconstructions.}
 
-To drive \albert{the AWSoM model, estimates} of the photospheric magnetic field of the Sun \albert{are the main} input.
-Synoptic magnetograms are used to specify the initial and the boundary conditions of the \albert{magnetic field.} We use the PFSS model to extrapolate the 3D magnetic field (from the 2D photospheric magnetic field maps) using spherical harmonics.
+To drive {the AWSoM model, estimates} of the photospheric magnetic field of the Sun {are the main} input.
+Synoptic magnetograms are used to specify the initial and the boundary conditions of the {magnetic field.} We use the PFSS model to extrapolate the 3D magnetic field (from the 2D photospheric magnetic field maps) using spherical harmonics.
 The source surface is taken to be at 2.5 $\mrsun$.
-The Global Oscillation Network Group (GONG) provides synoptic full-disk surface maps of the radial magnetic field component of the Sun.
+GONG provides synoptic full-disk surface maps of the radial magnetic field component of the Sun.
 However, since the polar regions are not well observed from the ecliptic, GONG estimates the polar fields by fitting a polynomial to neighboring observed latitudes, which might lead to inaccuracies.
@@
 In this work, we use the GONG synoptic map as input for CR-2082 (ADAPT-GONG maps are unavailable for CR-2082) and the ADAPT-GONG global magnetic field map for CR-2208.
-\albert{Based on results from previous efforts, for CR-2082} the magnetic field from the GONG map is scaled up by a factor of 1.85 \albert{for weak fields ($B_r< 5\,\rm{G}$), while no modification is applied in the case of} the ADAPT-GONG map for CR-2208.
+{Based on results from previous efforts, for CR-2082} the magnetic field from the GONG map is scaled up by a factor of 1.85 {for weak fields ($B_r< 5\,\rm{G}$), while no modification is applied in the case of} the ADAPT-GONG map for CR-2208.
 The AWSoM steady-state simulation set-up and input parameters for both rotations are described below.
 
-To account for the energy partitioning between electrons and protons, based on \citet{Cha2011}, we set the stochastic heating exponent \albert{equal to} 0.21 and the amplitude equal to \albert{0.18, for both} rotations.
-The boundary condition for Alfv\'{e}n wave energy is given by the \albert{poynting flux ($S_{A}$)} of the outgoing \albert{wave, $({S_{A}/}{B})_{\odot} = 1.1\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ and $1.0\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ for CR-2082 and CR-2208, respectively, whith $B_{\odot}$ being the field} strength at the inner boundary.
-The correlation length of the Alfv\'{e}n waves is set \albert{to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$m\,$\sqrt{T}$.}
+To account for the energy partitioning between electrons and protons, based on \citet{Cha2011}, we set the stochastic heating exponent {equal to} 0.21 and the amplitude equal to {0.18, for both} rotations.
+The boundary condition for Alfv\'{e}n wave energy is given by the {poynting flux ($S_{A}$)} of the outgoing {wave, $({S_{A}/}{B})_{\odot} = 1.1\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ and $1.0\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ for CR-2082 and CR-2208, respectively, with $B_{\odot}$ being the field} strength at the inner boundary.
+The correlation length of the Alfv\'{e}n waves is set {to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$m\,$\sqrt{T}$.}
 
-\albert{The computational domain of the solar corona} extends from 1 to \albert{$24\,\mrsun$}.
-The spherical grid in the solar corona is radially stretched (with a maximum resolution \albert{of $0.001\,\mrsun$} near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates.
-The Adaptive Mesh Refinement (AMR) resolves the angular cell \albert{size to $1.4\mdeg$ in the range of heights $1-1.7\,\mrsun$ and beyond $2.8\,\mrsun$}.
-\notebyalbert{(by Albert) does this make sense?} The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082.
+{The computational domain of the solar corona} extends from 1 to {$24\,\mrsun$}.
+The spherical grid in the solar corona is radially stretched (with a maximum resolution {of $0.001\,\mrsun$} near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates.
+The Adaptive Mesh refinement (AMR) resolves the angular cell size to $1.4\mdeg$ between $1 - 1.7\,\mrsun$ and to $2.8\mdeg$ outside this radius range.
+The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082.
 Local time stepping is used to speed up the steady state convergence.
@@
 
-\subsection{{Tracing Results Along Magnetic Field lines}}\label{trace}
+\subsection{{Tracing Results Along Magnetic Field Lines}}\label{trace}
 
 {To determine} the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid.
-Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = \albert{r\,{\rm d}\theta}/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point.
-In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, \albert{for a total of $97,200$ starting points.}
+Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = {r\,{\rm d}\theta}/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point.
+In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, {for a total of $97,200$ starting points.}
 
@@
 {The energy balance given by Equation \ref{Balance} is then integrated in the volume of any given coronal magnetic flux tube.
-Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a \albert{field line integrated} version of that energy balance is found,
+Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal condition of the magnetic field, a {field line integrated} version of that energy balance is found,
 \begin{equation}\label{FluxBalance}
@@
 \noindent
-where the \albert{line-integrated} flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\
+where the {line-integrated} flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017}:} \\
 
@@
 
-\noindent \albert{where $L$ is the length of the loop, and $B_0$ and $B_L$ are the values of the magnetic field at the footpoint locations of the loop in the coronal base, namely $s=0$ and $s=L$.} {Note that, for any given field line, all quantities in these two expresions can be computed \albert{from the DEMT results traced along field lines, and the AWSoM magnetic field model,} through Equations \ref{Fc}-\ref{Er}.
-Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to mantain a stable coronal structure.}
+\noindent {where $L$ is the length of the loop, and $B_0$ and $B_L$ are the values of the magnetic field at the footpoint locations of the loop in the coronal base, namely $s=0$ and $s=L$.} {Note that, for any given field line, all quantities in these two expressions can be computed {from the DEMT results traced along field lines, and the AWSoM magnetic field model,} through Equations \ref{Fc}-\ref{Er}.
+Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to maintain a stable coronal structure.}
 
@@
 Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}).
-Thick-black {curves indicate} the {open/closed boundaries of the magnetic field of the} AWSoM model.
+Thick-black {curves indicate} the {open/closed boundaries of the magnetic field of the} AWSoM model{, detailed in Section \ref{awsom}.}
 
@@
 
-Figure \ref{Br} shows carrington maps of \albert{the radial} magnetic \albert{field ($B_r$)} for both rotations at $1.005\, \mrsun$.
-\albert{Both maps clearly show the large-scale dipolar field, characteristic of solar minimum conditions.
-Differences between both maps are observed in the sub-polar latitudes, due to the different treatments applied there by the GONG (CR-2082) and the ADAPT-GONG (CR-2208) maps.}
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/map_Br_awsom_2082_185_extend_1005_Rsun.pdf}
-\includegraphics[width=0.495\textwidth,clip=]{figs/map_Br_awsom_2208_185_extend_1005_Rsun.pdf}
-\caption{Carrington maps of \albert{the radial magnetic field $B_r$ of the AWSoM model} at $1.005 \, \mrsun$ for CR-2082 (left) and CR-2208 (right). }
-\label{Br}
-\end{center}
-\end{figure}
 {To characterize the DEMT results in different magnetic structures, we traced} $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.
@@
 
-\albert{For both target rotations,} Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature.
+{Figure \ref{Br} shows carrington maps of {the radial} magnetic {field ($B_r$)} for both rotations at $1.005\, \mrsun$.
+{Both maps clearly show the large-scale dipolar field, characteristic of solar minimum conditions.
+Differences between both maps are observed in the sub-polar latitudes, due to the different treatments applied there by the GONG (CR-2082) and the ADAPT-GONG (CR-2208) maps.}}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.495\textwidth,clip=]{figs/map_Br_awsom_2082_185_extend_1005_Rsun.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/map_Br_awsom_2208_185_extend_1005_Rsun.pdf}
+\caption{Carrington maps of {the radial magnetic field $B_r$ of the AWSoM model} at $1.005 \, \mrsun$ for CR-2082 (left) and CR-2208 (right). }
+\label{Br}
+\end{center}
+\end{figure}
+
+{For both target rotations,} Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature.
 {Maps are shown} at the same three heights selected for visualization of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}.
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2208_1105_2.pdf}
-\caption{Longitude-averaged latitudinal dependence of the electron density (\albert{top panels}), \albert{electron temperature (\albert{middle panels})} and \albert{radial magnetic field $B_r$ (bottom panels), for target rotations} CR-2082 (\albert{blue color, left panels}) and CR-2208 (\albert{red color, right panels) at} $1.105\,\mrsun$.
+\caption{Longitude-averaged latitudinal dependence of the electron density ({top panels}), {electron temperature ({middle panels})} and {radial magnetic field $B_r$ (bottom panels), for target rotations} CR-2082 ({blue color, left panels}) and CR-2208 ({red color, right panels) at} $1.105\,\mrsun$.
 Dashed lines correspond to AWSoM results while solid line to DEMT.
@@
 Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend.
-\albert{For comparison, note the beahavior of $B_r$ in the CHs, increasing from the open/closed boudary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}
+{For comparison, note the behavior of $B_r$ in the CHs, increasing from the open/closed boundary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}
 
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995_2.pdf}
-\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6.0\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).} %\notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the absolute minimum indicates the location of the HCS at this height.
-I believe it is interesting to compare these two curves with Figure 10.
-Note that while in this Figure all latitudes are magnetically open, in Figure 10 only the part at latitudes larger than the vertical black lines are open.
-Note that DEMT shows that in the open low corona $N_e$ decreases from the O/C boundary towards the poles, anti-correlating with the AWSoM terminal speed, which is nice.
-In order to quantify this anti-correlation we need to trace the terminal speed and the DEMT $N_e$, which we may need to do with the help of Chip and Nishtha.
-Chip, we can discuss this idea over Skype after Xmas if you are around.}
-}
+\caption{{Longitude-averaged latitudinal dependence of the AWSoM model {wind speed $V_r$} at $6.0\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).}}
 \label{perf_lon_vr}
@@
 {Based on the magnetic field of AWSoM model and the results of the DEMT model for electron density and temperature, we classified coronal structures in four different types.
-Smaller legs in the core of the streamer belt are classified in down/up types according to their temperature decreasing/increasing with height (dubbed type 0/I).
-Larger closed legs of type up that form the envelope of the streamer belt (dubbed type II), and open field lines of type up populating the CHs (dubbed type III).}
+{Small loop legs} in the core of the streamer belt are classified in down/up types according to their temperature decreasing/increasing with height (dubbed type 0/I).
+{Large closed legs} of type up that form the envelope of the streamer belt (dubbed type II), and open field lines of type up populating the CHs (dubbed type III).}
 
@@
 {{For both target rotations}, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.
-In the case of the AIA based DEMT reconstruction, we show that in a substantial fraction of the CHs region the technique performs poorly in modeling LDEMs that predict the tomographic emissivitiy in each EUV band with reasonable accuracy.
-As a result, DEMT results based on AIA data are currently less reliable in the CH region.
+In the case of the {DEMT reconstruction based on AIA data we show that, in} a substantial fraction of the {voxels of the CHs,} the technique performs poorly in modeling {an LDEM that predicts} the tomographic emissivity in each EUV band with reasonable accuracy.
+As a result, DEMT results based on AIA data {are less reliable CHs}.
 This was already found by the existing two previous DEMT works based on AIA data \citep{nuevo_2015,maccormack_2017}.
@@
 
-In comparing the DEMT results obtained for the two selected targets, {we highlight here that} they rely on data provided by two different instruments, {namely EUVI and AIA for CR-2082 and CR-2208, respectively.} In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
+In comparing the DEMT results obtained for the two selected targets, {we highlight} they rely on data provided by two different instruments, {namely EUVI and AIA for CR-2082 and CR-2208, respectively.} In order to quantify the systematic difference of the DEMT products {due to the different filter sets of} both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
 They found that while the density {products are} essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, \textit{i.e.} $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$.
@@
 Based on spectroscopic data of the EIS instrument in quiet-Sun regions \citet{hahn_2014} showed that, if the observed non-thermal broadening are assigned to Alfvén waves, their energy flux at the coronal base is estimated to be in the range $\approx 1.5-2.5\times 10^5\,\erg\,\cminvs\,\s^{-1}$.
-A large fraction of the coronal base energy input flux $\phi_h$ estimated in this work, or even its totality, could then be accounted for by Alfvén waves.}
+A large fraction of the coronal base energy input flux $\phi_h$ estimated in this work, or even its totality, could then be accounted for by Alfvén waves \albert{(see the discussion in \citealt{maccormack_2017})}.}
 
-Results of the AWSoM model are compared to those of the DEMT reconstructions in the range of coronal heights $\approx 1.05-1.20\,\mrsun$ simultaneously covered by both models.
-In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines.
+Results of the AWSoM model {were compared} to those of the DEMT reconstructions {in the range of coronal heights simultaneously covered by both models, namely $\approx 1.05-1.20\,\mrsun$.} In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines.
 The detailed comparison shown in this work can be summarized as follows.
 For CR-2082, the electron density of both models agree within $\approx 20\%$ {in most regions}, while for CR-2208 the agreement is within $\approx 5\%$.
-{The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations{, with larger discrepancies in the CHs.} This level of agreement between both models \albert{(within or slightly beyond the uncertainty level of DEMT results)} is considerably better than that reported in previous works.
-\citet{jin_2012} and \citet{oran_2015} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.} \notebyalbert{Chip, if Section 2.2 explains the most significant improvements of AWSoM since the version used in those references, we can comment on the reason for the improvement here.}
-\diego{Note by Diego: Chip, Nishtha, if you think we can relate some differences or observed trends of AWSoM with the magnetic field, this could be a good place, but I need your insight here.}
+{The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations{, with larger discrepancies in the CHs.} This level of agreement between both models {(within or slightly beyond the uncertainty level of DEMT results)} is considerably better than that reported in previous works.
+\citet{jin_2012} and \citet{oran_2015}{, who used previous versions of the AWSoM model,} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.}
 
-{Within the \albert{excellent quantitative match between both models,} summarized in the previous paragraph, there are some qualitative agreements and \albert{disagreements worth noticing}.
+{The overall better match of the results of the current version of the AWSoM model when compared to DEMT reconstructions is partly due to the improved energy partitioning scheme of the model, described in Section \ref{awsom}.
+Note also that the simulation of CR-2082 used GONG maps as boundary condition, while the simulation of CR-2208 used the improved ADAPT-GONG maps.
+This is most probably the cause that the results of the AWSoM model show a more accurate match to the DEMT reconstructions in the case of CR-2208.}
+
+Within the {excellent quantitative match between both {models summarized} in the previous paragraph, there are some qualitative agreements and {disagreements worth noticing}.
 For both target rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
-On the other hand, while the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
-Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), the AWSoM model shows the opposite trend.
-This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.} \notebyalbert{Chip: Even if the match AWSoM/DEMT is quantitatively pretty good, this qualitative opposite behavior is off putting.
-Do you think there is room for improvement in the AWSoM model here?
-Maybe worth mentioning?}
+On the other hand, while the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density {(physically expected in transitioning from magnetically closed to open regions)}, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
+Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), {as expected in transitioning from the source region of the slow to the fast component of the solar wind}, the AWSoM model shows the opposite trend.
+This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.} {These unphysical characteristics of the results of the AWSoM model in the rage of low heights analysed here ($r\lesssim 1.2\,\mrsun$), may be traced down to the less reliable values of $B_r$ provided by both the GONG and ADAPT-GONG maps at subpolar latitudes, rather than a limitation of the model itself.
+This will be further investigated in a follow up article focusing on the current deep minimum epoch, during which the large-scale corona shows the simplest possible structure.}
 
-A detailed empirical description of the 3D termodynamic structure of the inner corona at a global scale is currently only possible with tomographic techniques, such as DEMT.
+A detailed empirical description of the 3D thermodynamic structure of the inner corona at a global scale is currently only possible with tomographic techniques, such as DEMT.
 Using tomographic results for continuous validation of 3D MHD models is of high relevance for the continued improvement of models.

### 2020-01-29 lloveras_2020_Albert_Section4_CON-TestHipotesis-Error2-V1.tex
..

--- 2020-01-14 lloveras_2020_Albert_Section4.tex
@@
 We carry out a study of the corona combining tomographic reconstructions with MHD simulations {using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF).
-Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24.
-Tomographic reconstructions and results of the model are {analysed} in distinct coronal magnetic structures.
-We study magnetically closed structures associated with the equatorial streamer belt, as well as magnetically open regions enclosing it.
-We report on the tomographic results in the different structures, their implications for the physics of the solar corona, and the {current} capability of the AWSoM model to reproduce the tomographic reconstructions in different regions.
+Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and \albert{the declining} phase of \albert{SC 24 }.
+\albert{The 3D tomographic and MHD models} are analysed and compared in distinct coronal magnetic \albert{structures.} \notebyalbert{Aquí faltan dos frases de conclusiones a escribir cuando esté hecha la Section 4.}
 
@@
 
+\noindent\albert{Diego: Esta nota en azul que sigue está modificada, inlcuíla así en la versión que mandes a Michigan, y borrá esta frase naranja :)}
+
 \noindent\notebyalbert{Here we will put in a couple of paragraphs summarizing what SRT and DEMT are, including references and defining the accronyms in the process.
@@
 We should mention the instruments and missions we use as data for DEMT, and define their accronyms too.
-Also, a couple of paragraphs on the AWSoM model and the SWMF, including references and defining the accronyms in the process.}
+Also one paragraph on the SWMF/AWSoM model, including references and defining the accronyms on the way.}
 
@@
 In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid.
-The size of the tomographic cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions.
+The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions.
 The cadence of the data time-series is set to 6\,hr.
-The main product of the technique is the local DEM (LDEM), a measure of the temperature distribution of the plasma contained in each voxel of the tomographic grid.
+The main product of the technique is the local DEM (LDEM) at each volxel, a measure of the temperature distribution of the plasma contained in it.
 A recent review by \citet{vasquez_2016} summarizes the DEMT works up until then.
@@
 Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}.
-These non-reconstructed voxels are indicated as black voxels in the Carrington maps of the reconstructed DEMT reults in Section \ref{resu}.
+These non-reconstructed voxels are indicated \albert{in black color in the latitude-longitude (Carrington) maps of DEMT} reults in Section \ref{resu}.
 
@@
 \albert{being the} average relative difference between the tomographic and the synthetic FBEs.
-The final product of DEMT is in the form of 3D maps of the electron density and mean temperature.
-These relationships {were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
-%\temp{Aclarar que consideramos Ne como $\sqrt{<\Ne ^2>}$.} {ALBERT: Yo creo que es mejor hablar de $\sqravgN$}
-
-%\temp{DEMT has been improved since the previously published work.
-We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.} \notebyalbert{NOTA de Albert: Explicá que hacés sin justificarte.
-Luego aclará como se hizo eso en trabajos previos, y cual es el impacto esperado.
-Puedo proveer un párrafo de ejemplo, pero creo que será mejor que vos escribas como te salga y yo luego edito.
-Algo muy importante para todo el paper: proponete escribir ``párrafos modulares".
-Es decir que, con las razonables limitaciones, puedan moverse de lugar, de orden, y sigan funcionando.
-No definiría hollow-tomography, es un término coloquial interno nuestro.
-Lo correcto es que al hablar de datos mucho más arribas expliques que los datos del disco no se utilizan, pero no le des un nombre a la tomografía.}
+\albert{The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.}\\
 
@@
 
-\noindent\notebyalbert{This section will summarize the AWSoM model. After a first version is written we will surely require some input from the Michigan friends. Points to cover:
+\noindent\albert{Diego: Esta nota en azul que sigue está modificada, inlcuíla así en la versión que mandes a Michigan, y borrá esta frase naranja :)}
+
+\noindent\notebyalbert{This section will summarize the AWSoM model. Chip, Nishtha, do you think you could provide 2 or 3 paragraphs? We believe the points to cover are:
 \begin{itemize}
@@
 Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}.
-In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}
-
-\noindent\notebyalbert{El párrafo que sigue describe un algoritmo para identificar y seleccionar piernas up/down.
-Es correcta la jerga de "confidence level'' y el como se describe chi-squared test?
-Están bien mencionadas ambas cosas?
-Por ejemplo: confidence-level y conficence-interval, son dos cosas diferentes.
-Otro tema es: si entiendo bien el chi-squared utiliza los errores, correcto?
-Noten que modifiqué a errores porcentuales (mucho más claro) tal como se describen en las conclusiones (los corregí un poco, aquí y allá), que los saqué de la Tabla 7, y re-escribí toda la frase (ver nuevo texto naranja), es correcta?.
-Ahora bien, son errores muy pequeños para cada celda, es poner demasiada fé en la tomografía :) Estos son los errores del valor mediano de $\Tm$.
-Podemos discutirlo, pero creo que los errores por punto (es decir, la $\Tm$ de cada voxel) deben adjudicarse valores mayores.
-Quizá esto de paso hace que el chi-squared ralee menos?}
-
-{To determine if a traced filed line leg is of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points.
-We then select field lines for which the temperature increases or decreases significantly with height by requiring $|\rhoTr| > 0.5$.
-We then measure the quality of the linear fit to the temperature-height data by means of a chi-squared test \citep{recipes}, and select legs for which the fit has a 90\% confidence level.
-In this way, legs for which the DEMT temperature does not show a significant variation with height, or the linear fit to temperature is good enough, are not considered in this analysis.
-Finally, selected legs are then classified as up or down according to if $\rhoTr > +0.5$ or $\rhoTr < -0.5$, respectively.
+In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and \albert{considering time-averaged heating rates.}
+
+\noindent
+\notebyalbert{Modifiqué la descripción del test estadístico en el próximo párrafo .
+Estuve leyendo un poco y hay que asegurarse que esto quede escrito bien.
+Yo busqué la frase más vaga que me parece tiene un sentido científico claro.
+Aquí hay una versión de divulgación:\\
+{\tt www.statisticshowto.datasciencecentral.com/confidence-level/}\\
+pero tener cuidado con esto: busquen ``Statistical Significance" en la Wikipedia, y lea la breve sección ``Redefining significance" al final del artículo.}
+
+\albert{To determine if the leg of a traced field line is} of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points.
+We then select field lines for which the temperature \albert{is significantly correlated with height} by requiring $|\rhoTr| > 0.5$.
+\albert{To test the goodness of the fit to the temperature-height data we perform a chi-squared test \citep{recipes} considering the uncertainty of the DEMT data points, selecting legs for which the fit matches the data with a 90\% confidence level.} In this way, legs for which the DEMT temperature does not show a significant \albert{correlation} with height, or the linear fit to temperature is \albert{not} good enough, are \albert{excluded from the} analysis.
+\albert{The test is also applied to the density-height data points, to ensure the trend is reasonably represented by the exponential fit.} Finally, selected legs are then classified as up or down according to if $\dr\Tm > 0$ or $\dr\Tm < 0$, respectively.
 The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg.
-\albert{The chi-squared test to evaluate the quality of the fits considers the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\Delta\Tm\approx 6\%$ and $\Delta\sqravgN\approx 3\%$.} In summary, to be selected a leg must meet all three following conditions:}
+\albert{The chi-squared test to evaluate the quality of the fits considers the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$.} In summary, to be selected a leg must meet all three following conditions:}
 
@@
 On the other hand, of the \albert{$\approx 57000$} legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III.
+\notebyalbert{Posiblemente quieras actualizar estos números.}
 
@@
 
-{The notable difference between both rotations is the characteristic {value ${\rm Md}\left(\dr\Tm\right)\approx +4.5\,\MK/\mrsun$} for legs of type III for CR-2208.
+\albert{The single notable difference between both rotations is to be found in the histograms for legs of type III in the open region.
+For those, the characteristic value is ${\rm Md}\left(\dr\Tm\right)\approx {\bf +X.X}$ and ${\bf Y.Y}\,\MK/\mrsun$ for CR-2208 and CR-2082, respectively}.
 This is related to the much larger $R$ score for the DEMT results along CH legs for CR-2208.
 In this case, DEMT performs poorly in modeling a LDEM that predicts the tomographic FBEs with reasonable accuracy.
-Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, {reveals that in most of the CH region the result for $\Tm$ below height $1.105\,\mrsun$ is quite uniform and artificially low}.
-As it turns out, around and above height this height the score $R$ is lower and the temperature results are more reliable.
-As a result, the temperature gradient along these legs is artificially larger, with the linear fit trying to simultaneously fit the artificially low values of $\Tm$ at lower heights.
-In general, the DEMT results in the CH region based on AIA data are thus much less reliable than in the rest of the analysis.
-We will return to this point in the conclusion section.}
+Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, reveals that in most of the CH region the result for $\Tm$ below height $1.105\,\mrsun$ is \albert{artificially uniform and low.
+Such results, mostly excluded of the analysis by the selection algorithm explained in Section \ref{trace}, imply the presence of some artificially large radial gradients of the DEMT temperature.} In general, the DEMT results in the CH region based on AIA data are thus much less reliable than in the rest of the analysis.
+We will return to this point in the conclusion section.
 
@@
 \caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}.
-For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
+For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.\notebyalbert{Notá que tenés un número en NEGRITA, y en la Tabla 2 tenés 3.
+Esos son números que yo había corregido, destacando en naranje y negrita, sacales la negrita.
+Quizá hay actualización de números para los Type III?}}
 \label{tabla_demt}
@@
 As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region.
-These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} \albert{estimated to be $\Delta\Tm\approx 6\%$ and $\Delta\sqravgN\approx 3\%$}.
+These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} \albert{estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$}.
 

### 2020-01-29 lloveras_2020.tex
..

@@
 \newcommand{\Nqi}{N_{\rm QI}}
-
 \newcommand{\dr}{\triangledown_r}
@@
 \newcommand{\Tc}{T_{\rm c}}
-
 \newcommand{\BibTeX}{\textsc{Bib}\TeX}
 \newcommand{\etal}{{\it et al.}}
-
 \newcommand{\Pl}{\texttt{+}}
@@
 \newcommand{\procspie}{{\it Proc. SPIE}}
-
-%---------REMOVE THESE OPTIONS AND DEFs BEFORE SUMBISSION---------------------------------------
-\usepackage[usenames,dvipsnames]{xcolor} % Las opciones: [USENAMES,DVIPSNAMES] 
-                                         % ponen a disposición los colores ejemplificados aquí:
-                                         % https://en.wikibooks.org/wiki/LaTeX/Colors
-\def\diego#1{\textcolor{red}{#1}}
-\def\albert#1{\textcolor{orange}{#1}}
-\def\fede#1{\textcolor{ForestGreen}{#1}}
-\def\temp#1{\textcolor{gray}{#1}}
-\def\notebyalbert#1{\textcolor{blue}{NOTE: #1}}
-%-----------------------------------------------------------------------------------------------
 
@@
 We estimate} the heating energy required to keep them {stable, which we argue may} be accounted for by Alfvén waves.
-{We also show that results of the latest version of the AWSoM model overal} agree with DEMT {reconstructions within a $\approx 20\%$ accuracy.
+{We also show that results of the latest version of the AWSoM model overall} agree with DEMT {reconstructions within a $\approx 20\%$ accuracy.
 We highlight some details of the AWSoM model that should} be improved to better reproduce {tomographic} results, in particular concerning the source region of the {fast and slow components of the solar wind.}}
@@
 
-%\keywords{Solar Cycle, Observations; Corona,E; Corona, Structures}
 \keywords{Solar Cycle, Observations; Corona, E; Corona, Structures; Corona, Models; Magnetohydrodynamics}
@@
 
-Being the {region} where the solar atmosphere is {heated, the solar wind accelerated}, and where impulsive events such as solar flares and coronal mass ejections are energized, observing and modeling of the solar corona are of great relevance to improving our understanding of the Sun-Earth environment.
+Being the {region} where the solar atmosphere plasma is {heated to million degree temperatures, the solar wind accelerated}, and where impulsive events such as solar flares and coronal mass ejections are energized, observing and modeling of the solar corona are of great relevance to improving our understanding of the Sun-Earth environment.
 To advance our knowledge of the physics of the solar corona, as well as {to enhance} and validate three-dimensional (3D) models, information derived from observational data plays a key role.
@@
 
-The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space {Weather} Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to {1 AU and beyond} \citep{vander_2010, Van2014}.
+The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space Wea\-ther Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to {1 AU and beyond} \citep{vander_2010, Van2014}.
 {The only data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation.
 As new improvements are implemented, the model is continuously being validated with observations.} DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona.
-More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a globally fashion, obtaining an agreement within 20\%.
+More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a global fashion.
 
@@
 
-{As detailed in Section \ref{intro}, target rotations CR-2082 and CR-2208 were selected to carry out DEMT reconstructions, based on data taken by the STEREO/EUVI-B and SDO/AIA instruments, respectively.} The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package.
+{As detailed in Section \ref{intro}, rotations CR-2082 and CR-2208 were selected to carry out DEMT reconstructions, based on data taken by the STEREO/EUVI-B and SDO/AIA instruments, respectively.} The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package.
 For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.
@@
 {The solution of the tomographic problem involves {inversion of} a very large sparse matrix.
-Such inversion problems are characterized by spurious {high-frequency} artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}.
+Such inversion problems are characterized by spurious {high-fre\-quen\-cy} artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}.
 In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude.
@@
 Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one).
-%To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it.
 As a result, for each field line one data point per tomographic cell {is obtained.
-This approach} was firstly used by \citet{huang_2012} to {study temperature} structures in the solar minimum {corona and by} \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.
+This approach} was first used by \citet{huang_2012} to {study temperature} structures in the solar minimum {corona and by} \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.
 
@@
 \label{Tfit}
-\Tm &=& T_0\,+\,m\,h \,,
+\Tm &=& T_0\,+\,a\,h\,,
 \end{eqnarray}
@@
 In the electron density fit, $\l\,[\mrsun]$ is the density scale height and $N_0\,[\cminvc]$ is the electron density at the footpoint ($h=0$) of the loop.
-In the electron temperature fit, $m\,[\MK/\mrsun]$ is the slope and $T_0\,[\MK]$ is the electron temperature at the footpoint of the loop.
-The slope $m$ estimates the radial gradient of the electron temperature along the loop, which we denote as $m = \dr\Tm$ hereafter, being $\dr\equiv\er\cdot\nabla$ the radial derivative operator, where $\er$ is the heliocentric radial unit vector.
+In the electron temperature fit, $a\,[\MK/\mrsun]$ is the slope and $T_0\,[\MK]$ is the electron temperature at the footpoint of the loop.
+The slope $a$ estimates the radial gradient of the electron temperature along the loop, which we denote as $a = \dr\Tm$ hereafter, being $\dr\equiv\er\cdot\nabla$ the radial derivative operator, where $\er$ is the heliocentric radial unit vector.
 
@@
 \begin{equation}\label{Balance}
-E_h(s) = E_r(s)+ E_c(s),
+E_h(s) = E_r(s) + E_c(s),
 \end{equation}
@@
 Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal condition of the magnetic field, a {field line integrated} version of that energy balance is found,
+
 \begin{equation}\label{FluxBalance}
@@
 \end{equation}
+
 \noindent
-where the {line-integrated} flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017}:} \\
+where the {line-integrated} flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017}:}
 
@@
 
-\noindent {where $L$ is the length of the loop, and $B_0$ and $B_L$ are the values of the magnetic field at the footpoint locations of the loop in the coronal base, namely $s=0$ and $s=L$.} {Note that, for any given field line, all quantities in these two expressions can be computed {from the DEMT results traced along field lines, and the AWSoM magnetic field model,} through Equations \ref{Fc}-\ref{Er}.
+\noindent 
+{where $L$ is the length of the loop, and $B_0$ and $B_L$ are the values of the magnetic field at the footpoint locations of the loop in the coronal base, namely $s=0$ and $s=L$.} {Note that, for any given field line, all quantities in these two expressions can be computed {from the DEMT results traced along field lines, and the AWSoM magnetic field model,} through Equations \ref{Fc}-\ref{Er}.
 Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to maintain a stable coronal structure.}
@@
 
-{As described in Section \ref{demt}, we carried out DEMT reconstructions of the coronal structure for target rotations CR-2082 and CR-2208 using STEREO/EUVI and SDO/AIA data, respectively.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared ($\sqravgN$) and the electron mean temperature ($\Tm$) were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}{, and the measure $R$ was calculated by means of Equation \ref{R}.}}
+{As described in Section \ref{demt}, we carried out DEMT reconstructions of the coronal structure for rotations CR-2082 and CR-2208 using STEREO/EUVI and SDO/AIA data, respectively.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared ($\sqravgN$) and the electron mean temperature ($\Tm$) were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}{, and the measure $R$ was calculated by means of Equation \ref{R}.}}
 
@@
 
-{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of {the DEMT} measure $R$ defined by Equation \ref{R}, at the same three heights shown in Figures \ref{momento1} and \ref{momento2}.
-In most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$.
-The notable exception is to be found in the CHs of the target rotation {analysed} based on AIA data.
+Latitude-longitude maps of the score $R$ defined by Equation \ref{R} show that in most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$.
+The notable exception is to be found only in the CHs of the rotation {analysed} based on AIA data.
 A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}.
-This point is further discussed below.}
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
-\caption{{Carrington maps of the measure $R$ defined by Equation \ref{R}, for CR-2082 (left panels) and CR-2208 (right panels), at heights $1.025$, $1.065$ and $1.105\,\mrsun$, from top to bottom}. }
-\label{carmaps_R_2082_2208}
-\end{center}
-\end{figure}
+This point is further discussed below in this section.
 
@@
 
-{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
+{For both rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
 Open legs are indicated in gray color and closed ones in black color.
@@
 Later on, \citet{lloveras_2017} showed {that} equatorial down loops in streamers were also to be found in the deep minimum between SCs {23 and 24}.
-Here, we verify the existence of this type of structure for the two target rotations.
+Here, we verify the existence of this type of structure for the two rotations.
 The relatively smaller population of down legs seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}.
@@
 {The notable difference between both rotations is the characteristic {value ${\rm Md}\left(\dr\Tm\right)\approx +4.5\,\MK/\mrsun$} for legs of type III for CR-2208.
-This is related to the much larger $R$ score for the DEMT results along CH legs for CR-2208.
-In this case, DEMT performs poorly in modeling a LDEM that predicts the tomographic FBEs with reasonable accuracy.
-Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, {reveals that in most of the CH region the result for $\Tm$ below height $1.105\,\mrsun$ is quite uniform and artificially low}.
-As it turns out, around and above height this height the score $R$ is lower and the temperature results are more reliable.
-As a result, the temperature gradient along these legs is artificially larger, with the linear fit trying to simultaneously fit the artificially low values of $\Tm$ at lower heights.
-In general, the DEMT results in the CH region based on AIA data are thus much less reliable than in the rest of the analysis.
+This is related to the relatively larger values of the score $R$ for the CH of CR-2208, making the DEMT results based on AIA data less reliable in the CHs.
 We will return to this point in the conclusion section.}
@@
 From top to bottom {results are shown for} type 0 to type III {legs}{, respectively}.
-From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$ {(the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.
-
-{Table \ref{tabla_demt} summarizes a} quantitative comparative analysis between the results of the two {target rotations}.
-For CR-2082 quantities are expressed as absolute values, {while} for CR-2208 they are informed {as a percentual variation} relative to the corresponding results for CR-2082.
-{The following major results, both concerning the structure of each rotation individually as well as their comparison, can be drawn.}
+From left to right the panels show the statistical distribution of the electron density value $\NCB \equiv \sqravgN(r=1.055)$ {(at the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.
 
@@
 
+{Table \ref{tabla_demt} summarizes a} quantitative comparative analysis between the results of the two {target rotations}.
+For CR-2082 quantities are expressed as absolute values, {while} for CR-2208 they are expressed relative to the corresponding results for CR-2082.
+
 {Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer layers of the equatorial streamer belt, exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
-In both rotations also, type III legs in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I legs in the core of the equatorial streamer.}
+In both rotations also, type III legs in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I legs in the core of the equatorial streamer.} {A comparison of the results between the two rotations shows that, compared to CR-2082, rotation CR-2208 was characterized by {$\approx 10-20\%$} lower values of the electron density at the coronal base, $\approx 5-30\%$ larger values of density scale height, and {$\approx 15-25\%$} larger values of the electron temperature.}
 
-{A comparison of the results between the two rotations shows that, compared to CR-2082, target rotation CR-2208 was characterized by {$\approx 10-20\%$} lower values of the electron density at the coronal base, $\approx 5-30\%$ larger values of density scale height, and {$\approx 5-25\%$} larger values of the electron temperature.}
-
-{To analyze the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the classification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).
-{For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.}
-
-\begin{figure}[ht]
+\begin{figure}[h!]
 \begin{center}
@@
 
+In comparing the DEMT results obtained for the two selected targets, {we highlight} they rely on data provided by two different instruments, {namely EUVI and AIA for CR-2082 and CR-2208, respectively.} To quantify the systematic difference of the DEMT products {due to the different filter sets of} both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
+They found that while the density {products are} essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, \textit{i.e.} $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$.
+Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was {characterized by temperatures $\approx 10-15\%$ larger relative to CR-2082} throughout the streamer belt region.
+As for the electron density products, CR-2208 was found to be $\approx 10-20\%$ less dense than CR-2082 throughout the streamer belt region.
+These systematic differences are {around or beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} {estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$}.}
+
+{To analyse the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the classification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).
+{For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.}
+
 {For both rotations, the value of the {loop-integrated} radiative power $E_r$, measured by the quantity $\phi_r$, is largest for loops of type 0.
@@
 
-{{The sign of the quantity $\phi_c$ depends on that of the conductive flux $F_c$.
-Equations \ref{Fc} and \ref{phi_c} imply that } down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, {as verified} in Figure \ref{energia_demt}.}
+The sign of the quantity $\phi_c$ depends on that of the conductive flux $F_c$.
+Equations \ref{Fc} and \ref{phi_c} imply that, by definition, down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, {as verified} in Figure \ref{energia_demt}.
 
@@
 Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$.
-As shown by \citet{maccormack_2017}, {this affects only the smallest sized loops of the type 0}, and it is {most probably} due to the limited temperature sensitivity of the instrumental passbands.
-The radiative loss term is {here calculated based on plasma emission detected by three coronal bands of EUVI or AIA.
+As shown by \citet{maccormack_2017}, {this affects only the smallest sized loops of the type 0}, and it is likely due to measurement errors.
 Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range.
-As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized by $\phi_c<0$.}}
+As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized by $\phi_c<0$.}
 
@@
 
-{For both target rotations,} Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature.
-{Maps are shown} at the same three heights selected for visualization of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}.
+{As described in Section \ref{awsom}, the AWSoM model includes an artificially thick TR, achieving coronal conditions above height $\approx 1.06\,\mrsun$.
+Results for the AWSoM model are shown here above that height.
+For both target rotations,} Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature.
+{Maps are shown} at the two largest heights selected for visualization of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}.
 {Thick-black curves} indicate the magnetic open/closed boundaries based on the magnetic field of the AWSoM model.
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1025_Rsun.pdf}
 \includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1065_Rsun.pdf}
@@
 \includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1105_Rsun.pdf}
-\caption{Carrington maps of density (left panels) and temperature (right panels) obtained with AWSoM model for the same three heights shown in Figure \ref{carmaps_demt_2082}.}
+\caption{Carrington maps of density (left panels) and temperature (right panels) obtained with AWSoM model at heliocentric heights $1.065$ (top panels) and $1.105\,\mrsun$ (bottom panels).}
 \label{carmaps_awsom_2082}
@@
 
-{As described in Section \ref{awsom}, the AWSoM model includes an artificially thick TR, achieving coronal conditions above height $\approx 1.06\,\mrsun$.
-Indeed, the top panels in Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208}, at height $1.025\,\mrsun$, clearly do not represent coronal conditions (although we include them here for completeness).
-When compared to DEMT results (Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}), the latitude-longitude maps of the AWSoM model for heights $1.065$ and $1.105\,\mrsun$ capture well the denser and hotter equatorial streamer belt surrounded by the less dense and colder CHs.
-Furthermore, for both target rotations, the temperature maps show the low latitudes of the equatorial streamer belt to be characterized by lower temperatures than its mid-latitudes, as also seen in the DEMT results.
+{When compared to DEMT results (Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}), the latitude-longitude maps of the AWSoM model for heights $1.065$ and $1.105\,\mrsun$ capture well the denser and hotter equatorial streamer belt surrounded by the less dense and colder CHs.
+Furthermore, for both rotations, the temperature maps show the low latitudes of the equatorial streamer belt to be characterized by lower temperatures than its mid-latitudes, as also seen in the DEMT results.
 The latitude-longitude maps of the AWSoM and DEMT results are shown in the same units and scales, so that a visual comparison among them already reveals similar values of electron density and temperature in both models.}
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1025_Rsun.pdf}
 \includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1065_Rsun.pdf}
@@
 \includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1105_Rsun.pdf}
-\caption{Same as Figure \ref{carmaps_awsom_2208} for CR-2208.}
+\caption{Same as Figure \ref{carmaps_awsom_2082} for CR-2208.}
 \label{carmaps_awsom_2208}
@@
 
-{Being highly axisymmtric target rotations, the longitude-averaged latitudinal {profile} of the results of both models is an informative way to compare their large-scale structure.
+{Being highly axisymmtric rotations, the longitude-averaged latitudinal {profile} of the results of both models is an informative way to compare their large-scale structure.
 Such comparison is shown in Figure \ref{perf_lat} at height $1.105\,\mrsun$, with top panels comparing electron density and mid panels electron temperature.
@@
 Left panels show the comparison for CR-2082 (in blue) and right panels for CR-2208 (in red).
-In each panel the vertical black lines denote the corresponding longitude-averaged latitude of the open-close boundary in both hemispheres.}
+In each panel the vertical black lines denote the corresponding longitude-averaged latitude of the open-closed boundary in both hemispheres.}
 
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2208_1105_2.pdf}
-\caption{Longitude-averaged latitudinal dependence of the electron density ({top panels}), {electron temperature ({middle panels})} and {radial magnetic field $B_r$ (bottom panels), for target rotations} CR-2082 ({blue color, left panels}) and CR-2208 ({red color, right panels) at} $1.105\,\mrsun$.
-Dashed lines correspond to AWSoM results while solid line to DEMT.
-The vertical black line indicates the longitude-averaged latitudes of the open/closed magnetic boundary in both hemispheres.}
+\caption{Longitude-averaged latitudinal variation of the electron density ({top panels}), {electron temperature ({middle panels})} and {radial magnetic field $B_r$ (bottom panels), for rotations} CR-2082 ({blue color, left panels}) and CR-2208 ({red color, right panels) at} $1.105\,\mrsun$.
+Dashed and solid lines indicate AWSoM and DEMT results, respectively.
+Vertical black lines indicate the longitude-averaged latitude of the open/closed magnetic boundary in both hemispheres.}
 \label{perf_lat}
@@
 The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.
-In the case of the electron temperature, for both target rotations the models agree within $\approx 15\%$ at all latitudes of the streamer belt, showing larger discrepancies in the CHs.} Secondly, for both target rotations, and for both models, these plots clearly show the relatively lower temperatures characterizing the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
-Thirdly, for both target rotations, the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density.
+In the case of the electron temperature, for both rotations the models agree within $\approx 15\%$ at all latitudes of the streamer belt, showing larger discrepancies in the CHs.} Secondly, for both rotations, and for both models, these plots clearly show the relatively lower temperatures characterizing the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
+Thirdly, for both rotations, the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density.
 Note this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
-Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend.
+Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two rotations), while the AWSoM model shows the opposite trend.
 {For comparison, note the behavior of $B_r$ in the CHs, increasing from the open/closed boundary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}
@@
 
-{For target rotation CR-2082, Figure \ref{histos_2082} shows the statistical distribution of the results of the DEMT (solid line-style) and AWSoM (dashed line-style) models traced along legs of type I, II and III (from top to bottom), as defined in Section \ref{trace}.
-From left to right: electron density at the lowest coronal height of the AWSoM model $\NCB\equiv\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
-In each panel the median values $m$ are indicated.
-Figure \ref{histos_2208} shows the same analysis for target rotation CR-2208.}
-
 \begin{figure}[h!]
@@
 
+{For rotation CR-2082, Figure \ref{histos_2082} shows the statistical distribution of the results of the DEMT (solid line-style) and AWSoM (dashed line-style) models traced along legs of type I, II and III (from top to bottom), as defined in Section \ref{trace}.
+From left to right: electron density at the lowest coronal height of the AWSoM model $\NCB\equiv\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
+In each panel the median values $m$ are indicated.
+Figure \ref{histos_2208} shows the same analysis for rotation CR-2208.}
+
 {For the two target rotations, Table \ref{tabla_comp} summarizes a quantitative comparative analysis between the results of the DEMT and AWSoM models {based on the results shown in Figures \ref{histos_2082} and \ref{histos_2208}}.
@@
 The following major results can be drawn.}
-
-{For target rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, {depending of the type of leg, with the largest discrepancy foud for legs of type II (near the open/closed boundary).
-The} median value of the scale height $\lN$ agree {within $\approx 10\%$ in all regions}.
-The leg-averaged electron temperature $\aTm$ of both models also agree {within $10\%$ in all regions}.
-For target rotation CR-2208 the agreement of the median value of $\NCB$ and $\lN$ of both models {is within $10\%$, while} median values of $\aTm$ agree within $15\%$.
-{These detailed results, being consistent with the large-scale comparison provided in Figure \ref{perf_lat}, show in detail how the AWSoM model performs compared to DEMT in different magnetic structures.}}
 
@@
 \caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of leg defined in Section \ref{trace}.
-DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
+DEMT values are expressed in absolute terms, while AWSoM results are expressed relative to the corresponding DEMT value.}
 \label{tabla_comp}
 \end{table}
+
+{For rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, {depending of the type of leg, with the largest discrepancy foud for legs of type II (near the open/closed boundary).
+The} median value of the scale height $\lN$ agree {within $\approx 10\%$ in all regions}.
+The leg-averaged electron temperature $\aTm$ of both models also agree {within $10\%$ in all regions}.
+For rotation CR-2208 the agreement of the median value of $\NCB$ and $\lN$ of both models {is within $10\%$, while} median values of $\aTm$ agree within $15\%$.
+{These detailed results, being consistent with the large-scale comparison provided in Figure \ref{perf_lat}, show in detail how the AWSoM model performs compared to DEMT in different magnetic structures.}}
 
@@
 
-{We carried out the 3D DEMT reconstruction and MHD modeling of the inner solar corona for two target rotations, CR-2082 and CR-2208.
-The first target belongs to the deep minimum epoch between SCs 23 and 24, while the latter belongs to the end of the declining phase of SC 24.
-The present work introduces two improvements in the implementation of DEMT, namely the use of only off-limb data in the EUV images, and the inclusion of a 3D regularization scheme.
-As a result of the former, artifacts introduced by coronal dynamics are mitigated, and as a result of the latter, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.
-The MHD model used is here the latest version of the AWSoM component of the SWMF suite.}
+We carried out the 3D DEMT reconstruction and MHD modeling of the inner solar corona for two target rotations, CR-2082 and CR-2208.
+The former belongs to the deep minimum epoch between SCs 23 and 24, while the latter belongs to the end of the declining phase of SC 24.
+The present work introduces two improvements in the implementation of DEMT, namely the use of only off-limb data in the EUV images, and the inclusion of a 3D regularization scheme (Section \ref{demt}).
+The MHD model used is here the latest version of the AWSoM component of the SWMF suite  (Section \ref{awsom}).
 
@@
 
-Concerning the DEMT reconstructions, Figure \ref{rpoint_demt} shows that, for both target rotations, magnetic field lines of type 0, I and II are associated to increasingly outer {layers} of the equatorial streamer belt.
-Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} report in 3D quantitative detail how these progressively outer magnetic structures exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
-For both target rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes.
+Concerning the DEMT reconstructions, Figure \ref{rpoint_demt} shows that, for both rotations, magnetic field lines of type 0, I and II are associated with increasingly outer {layers} of the equatorial streamer belt.
+Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} show in 3D quantitative detail how these progressively outer magnetic structures exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature.
+For both rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes.
 Also, in the case of CR-2082 the fraction of down legs is significantly larger than for CR-2208.
@@
 
-{{For both target rotations}, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.
+{{For both rotations}, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.
 In the case of the {DEMT reconstruction based on AIA data we show that, in} a substantial fraction of the {voxels of the CHs,} the technique performs poorly in modeling {an LDEM that predicts} the tomographic emissivity in each EUV band with reasonable accuracy.
@@
 
-In comparing the DEMT results obtained for the two selected targets, {we highlight} they rely on data provided by two different instruments, {namely EUVI and AIA for CR-2082 and CR-2208, respectively.} In order to quantify the systematic difference of the DEMT products {due to the different filter sets of} both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
-They found that while the density {products are} essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, \textit{i.e.} $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$.
-Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was {characterized by temperatures $\approx 10-15\%$ larger relative to CR-2082} throughout the streamer belt region.
-As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region.
-These systematic differences are {around or beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} {estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$}.}
-
 {In the streamer belt region we combined the DEMT results and the AWSoM magnetic model to infer the energy input flux $\phi_h$ at the coronal base required to maintain stable coronal loops.
-To this end, we applied the technique developed by \citet{maccormack_2017}.
 We found characteristic values in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}.
@@
 For CR-2082, the electron density of both models agree within $\approx 20\%$ {in most regions}, while for CR-2208 the agreement is within $\approx 5\%$.
-{The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations{, with larger discrepancies in the CHs.} This level of agreement between both models {(within or slightly beyond the uncertainty level of DEMT results)} is considerably better than that reported in previous works.
+{The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both rotations{, with larger discrepancies in the CHs.} This level of agreement between both models {(within or slightly beyond the uncertainty level of DEMT results)} is considerably better than that reported in previous works.
 \citet{jin_2012} and \citet{oran_2015}{, who used previous versions of the AWSoM model,} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.}
 
-{The overall better match of the results of the current version of the AWSoM model when compared to DEMT reconstructions is partly due to the improved energy partitioning scheme of the model, described in Section \ref{awsom}.
+{The overall better match of the results of the current version of the AWSoM model compared to DEMT reconstructions is partly due to the improved energy partitioning scheme of the model, described in Section \ref{awsom}.
 Note also that the simulation of CR-2082 used GONG maps as boundary condition, while the simulation of CR-2208 used the improved ADAPT-GONG maps.
-This is most probably the cause that the results of the AWSoM model show a more accurate match to the DEMT reconstructions in the case of CR-2208.}
+This is likely the cause that the results of the AWSoM model show a more accurate match to the DEMT reconstructions in the case of CR-2208.}
 
-Within the {excellent quantitative match between both {models summarized} in the previous paragraph, there are some qualitative agreements and {disagreements worth noticing}.
-For both target rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
+Within the {quantitative match between both {models summarized} in the previous paragraph, there are some qualitative agreements and {disagreements worth noticing}.
+For both rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
 On the other hand, while the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density {(physically expected in transitioning from magnetically closed to open regions)}, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
-Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), {as expected in transitioning from the source region of the slow to the fast component of the solar wind}, the AWSoM model shows the opposite trend.
-This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.} {These unphysical characteristics of the results of the AWSoM model in the rage of low heights analysed here ($r\lesssim 1.2\,\mrsun$), may be traced down to the less reliable values of $B_r$ provided by both the GONG and ADAPT-GONG maps at subpolar latitudes, rather than a limitation of the model itself.
+Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two rotations), {as expected in transitioning from the source region of the slow to the fast component of the solar wind}, the AWSoM model shows the opposite trend.
+This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.} {These unphysical characteristics of the results of the AWSoM model in the rage of low heights analysed here ($r\lesssim 1.2\,\mrsun$), may be attributed to the less reliable values of $B_r$ provided by both the GONG and ADAPT-GONG maps at subpolar latitudes.
 This will be further investigated in a follow up article focusing on the current deep minimum epoch, during which the large-scale corona shows the simplest possible structure.}
@@
 \end{acks}
-\\
-\\
+
 \begin{footnotesize}
@@
 \end{footnotesize}
+
 \bibliographystyle{spr-mp-sola}

### 2020-01-30 lloveras_2020_Albert.tex
..

@@
 
-%---------REMOVE THESE OPTIONS AND DEFs BEFORE SUMBISSION---------------------------------------
+%-------------remove these two lines before submision--------------------------
 \usepackage[usenames,dvipsnames]{xcolor} % Las opciones: [USENAMES,DVIPSNAMES] 
-                                         % ponen a disposición los colores ejemplificados aquí:
-                                         % https://en.wikibooks.org/wiki/LaTeX/Colors
-\def\diego#1{\textcolor{red}{#1}}
 \def\albert#1{\textcolor{orange}{#1}}
-\def\fede#1{\textcolor{ForestGreen}{#1}}
-\def\temp#1{\textcolor{gray}{#1}}
-\def\notebyalbert#1{\textcolor{blue}{NOTE: #1}}
-%-----------------------------------------------------------------------------------------------
+%------------------------------------------------------------------------------
 
 \begin{document}
-
 \begin{article}
@@
 
-\keywords{\albert{Solar Cycle, Observations; Corona, E; Corona, Structures; Corona, Models; Magnetohydrodynamics}}
+\keywords{Solar Cycle, Observations; Corona, E; Corona, Structures; Corona, Models; Magnetohydrodynamics}
 
@@
 
-The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space {Weather} Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to {1 AU and beyond} \citep{vander_2010, Van2014}.
-{The single data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation.
+The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space Wea\-ther Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to {1 AU and beyond} \citep{vander_2010, Van2014}.
+{The only data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation.
 As new improvements are implemented, the model is continuously being validated with observations.} DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona.
-More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a globally fashion, obtaining an agreement within 20\%.
+More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a global fashion.
 
@@
 
-{Legs of type down turn out to have a significant population only for closed-small loops.
+Legs of type down turn out to have a significant population only for closed-small loops.
 In the case of closed-large loops and open field lines, there are very few cases of type down.
-Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population in each case}.
-\\
-In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic structures are statistically analysed.
-{As shown in Section \ref{demt_res}, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}
+Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population \albert{in each case.
+In Section} \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic structures are statistically analysed.
+As shown in Section \ref{demt_res}, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.
 
@@
 They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 23 and 24}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the {end of the declining} phase of {SC 24}, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious.
-This thermodynamic structure of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
+This thermodynamic structure of the streamer has been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
 
-{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of {the DEMT} measure $R$ defined by Equation \ref{R}, at the same three heights shown in Figures \ref{momento1} and \ref{momento2}.
-In most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$.
-The notable exception is to be found in the CHs of the target rotation {analysed} based on AIA data.
+Latitude-longitude maps of the score $R$ defined by Equation \ref{R} show that in most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$.
+The notable exception is to be found only in the CHs of the rotation {analysed} based on AIA data.
 A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}.
-This point is further discussed below.}
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
-\caption{{Carrington maps of the measure $R$ defined by Equation \ref{R}, for CR-2082 (left panels) and CR-2208 (right panels), at heights $1.025$, $1.065$ and $1.105\,\mrsun$, from top to bottom}. }
-\label{carmaps_R_2082_2208}
-\end{center}
-\end{figure}
+This point is further discussed below in this section.
 
@@
 We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.
-Legs of type 0 are not included for AWSoM, as in its current implementation it can not simulate down loops, a point we will discuss in the next section.}
+Legs of type 0 are not included for AWSoM \albert{as it currently can not simulate down loops, as discussed in Section \ref{discu}.}}
 
@@
 
-In comparing the DEMT results obtained for the two selected targets, {we highlight} they rely on data provided by two different instruments, {namely EUVI and AIA for CR-2082 and CR-2208, respectively.} In order to quantify the systematic difference of the DEMT products {due to the different filter sets of} both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
-They found that while the density {products are} essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, \textit{i.e.} $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$.
-Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was {characterized by temperatures $\approx 10-15\%$ larger relative to CR-2082} throughout the streamer belt region.
-As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region.
-These systematic differences are {around or beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} {estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$}.}
-
 {In the streamer belt region we combined the DEMT results and the AWSoM magnetic model to infer the energy input flux $\phi_h$ at the coronal base required to maintain stable coronal loops.
-To this end, we applied the technique developed by \citet{maccormack_2017}.
 We found characteristic values in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}.
 Based on spectroscopic data of the EIS instrument in quiet-Sun regions \citet{hahn_2014} showed that, if the observed non-thermal broadening are assigned to Alfvén waves, their energy flux at the coronal base is estimated to be in the range $\approx 1.5-2.5\times 10^5\,\erg\,\cminvs\,\s^{-1}$.
-A large fraction of the coronal base energy input flux $\phi_h$ estimated in this work, or even its totality, could then be accounted for by Alfvén waves \albert{(see the discussion in \citealt{maccormack_2017})}.}
+A large fraction of the coronal base energy input flux $\phi_h$ estimated in this work, or even its totality, could then be accounted for by Alfvén waves (see the discussion in \citealt{maccormack_2017}).}
 
@@
 For CR-2082, the electron density of both models agree within $\approx 20\%$ {in most regions}, while for CR-2208 the agreement is within $\approx 5\%$.
-{The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations{, with larger discrepancies in the CHs.} This level of agreement between both models {(within or slightly beyond the uncertainty level of DEMT results)} is considerably better than that reported in previous works.
+{The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both rotations{, with larger discrepancies in the CHs.} This level of agreement between both models {(within or slightly beyond the uncertainty level of DEMT results)} is considerably better than that reported in previous works.
 \citet{jin_2012} and \citet{oran_2015}{, who used previous versions of the AWSoM model,} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.}
 
-{The overall better match of the results of the current version of the AWSoM model when compared to DEMT reconstructions is partly due to the improved energy partitioning scheme of the model, described in Section \ref{awsom}.
+{The overall better match of the results of the current version of the AWSoM model compared to DEMT reconstructions is partly due to the improved energy partitioning scheme of the model, described in Section \ref{awsom}.
 Note also that the simulation of CR-2082 used GONG maps as boundary condition, while the simulation of CR-2208 used the improved ADAPT-GONG maps.
-This is most probably the cause that the results of the AWSoM model show a more accurate match to the DEMT reconstructions in the case of CR-2208.}
+This is likely the cause that the results of the AWSoM model show a more accurate match to the DEMT reconstructions in the case of CR-2208.}
 
-Within the {excellent quantitative match between both {models summarized} in the previous paragraph, there are some qualitative agreements and {disagreements worth noticing}.
-For both target rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
+Within the {quantitative match between both {models summarized} in the previous paragraph, there are some qualitative agreements and {disagreements worth noticing}.
+For both rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
 On the other hand, while the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density {(physically expected in transitioning from magnetically closed to open regions)}, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
-Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), {as expected in transitioning from the source region of the slow to the fast component of the solar wind}, the AWSoM model shows the opposite trend.
-This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.} {These unphysical characteristics of the results of the AWSoM model in the rage of low heights analysed here ($r\lesssim 1.2\,\mrsun$), may be traced down to the less reliable values of $B_r$ provided by both the GONG and ADAPT-GONG maps at subpolar latitudes, rather than a limitation of the model itself.
+Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two rotations), {as expected in transitioning from the source region of the slow to the fast component of the solar wind}, the AWSoM model shows the opposite trend.
+This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.} {These unphysical characteristics of the results of the AWSoM model in the rage of low heights analysed here ($r\lesssim 1.2\,\mrsun$), may be attributed to the less reliable values of $B_r$ provided by both the GONG and ADAPT-GONG maps at subpolar latitudes.
 This will be further investigated in a follow up article focusing on the current deep minimum epoch, during which the large-scale corona shows the simplest possible structure.}
+
+\albert{Down loops are to be expected if heating is enhanced at the footpoints of coronal structures.
+\citet{schiff_2016} numerically simulated stable down loops by means of a 1D steady-state model, requiring that the initial population of Alfvén waves is efficiently converted into compressive modes.
+Mode conversion is favored by the $\beta\gtrsim 1 $ condition found to characterize the regions where down loops are observed in DEMT analysis \citep{nuevo_2013}.
+In the AWSoM model, heating is controlled by two key parameters, namely, the Alfvén wave dissipation length, and its reflection coefficient.
+So far, attempts to reproduce observed down loops in AWSoM simulations by increasing the reflection coefficient have not been successful.}
 

### 2020-01-30 lloveras_2020.tex
Version Final

@@
 Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population in each case}.
-\\
 In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic structures are statistically analysed.
@@
 We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.
-Legs of type 0 are not included for AWSoM, as in its current implementation it can not simulate down loops, a point we will discuss in the next section.}
+Legs of type 0 are not included for AWSoM as it currently can not simulate down loops, as discussed in Section \ref{discu}.}
 
@@
 
+Down loops are to be expected if heating is enhanced at the footpoints of coronal structures.
+\citet{schiff_2016} numerically simulated stable down loops by means of a 1D steady-state model, requiring that the initial population of Alfvén waves is efficiently converted into compressive modes.
+Mode conversion is favored by the $\beta\gtrsim 1 $ condition found to characterize the regions where down loops are observed in DEMT analysis \citep{nuevo_2013}.
+In the AWSoM model, heating is controlled by two key parameters, namely, the Alfvén wave dissipation length, and its reflection coefficient.
+So far, attempts to reproduce observed down loops in AWSoM simulations by increasing the reflection coefficient have not been successful.
+
 A detailed empirical description of the 3D thermodynamic structure of the inner corona at a global scale is currently only possible with tomographic techniques, such as DEMT.
@@
 \begin{acks}
-D.G.Ll.
+D.G.L.
 and C.M.C.
@@
 4870) to IAFE that supported {their} participation in this research.
-{D.G.Ll, A.M.V., F.A.N.
+{D.G.L, A.M.V., F.A.N.
 and C.M.C.
@@
 A.M.V.
-also acknowledges UBACyT grant 20020160100072BA to DCAO-UBA to FCEyN-UBA and IAFE that partially supported his participation in this research.}
+also acknowledges UBACyT grant 20020160100072BA to DCAO-UBA to FCEyN-UBA and IAFE that partially supported his participation in this research.} W.M.
+and B.v.H acknowledge NSF grant 1663800 that partially supported his participation in this research.
+W.M.
+also acknowledges NASA grants NNX16AL12G and 80NSSC17K0686.
 \end{acks}

### 2020-01-30 lloveras_2020_Albert.tex
Version Final

@@
 \albert{Down loops are to be expected if heating is enhanced at the footpoints of coronal structures.
-\citet{schiff_2016} numerically simulated stable down loops by means of a 1D steady-state model, requiring that the initial population of Alfvén waves is efficiently converted into compressive modes.
-Mode conversion is favored by the $\beta\gtrsim 1 $ condition found to characterize the regions where down loops are observed in DEMT analysis \citep{nuevo_2013}.
+\citet{schiff_2016} reproduced down loops by means of numerical simulations based on a 1D steady-state model, by requiring that the initial population of Alfvén waves is efficiently converted into compressive modes.
+Mode conversion is favored by the $\beta\gtrsim 1 $ condition found to characterize the regions where down loops are observed in DEMT \citep{nuevo_2013}.
 In the AWSoM model, heating is controlled by two key parameters, namely, the Alfvén wave dissipation length, and its reflection coefficient.
-So far, attempts to reproduce observed down loops in AWSoM simulations by increasing the reflection coefficient have not been successful.}
+So far, attempts to reproduce down loops within AWSoM simulations by increasing the reflection coefficient have not been successful.}
 

### 2020-02-17 response_to_review_SOLA-D-20-00015_v1.txt
Review y Respuesta

Dear Editor,

Thank you very much for you email with the report on the first version of our manuscript SOLA-D-20-00015, titled "Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling".

We deeply acknowledge the reviewer, whose report not only reflects how carefully he/she read it, but which also contains a series highly relevant, useful, and very constructive criticisms and suggestions. It is the opinion of the authors that this review ranks among the very best they ever read.

Below, we paste the full review. Following each query we include a response, highlighting the changes in the manuscript, where all edited/new text is marked in RED COLOR fonts.

Looking forward to your response. Sincerely,
The Authors.

------------------------------begin of response------------------------------------------
COMMENTS FOR THE AUTHOR:

Review of Thermodynamic Structure of the Solar corona: tomographic reconstructions and MHD modeling

This is a well-structured and clearly-written paper, presenting a detailed comparison of tomographic reconstructions of the low solar corona (which gives density and temperature), and a global MHD model. The work is important and valuable to the field, and is suitable for publication in Solar Physics. There are no major scientific concerns. The paper should be ready for publication if the following, mostly minor, concerns are addressed:

Medium concerns
-----------------------------------------------------------------------------------------
1. All of the multi-panel figures that show longitude-latitude maps (e.g. figure 1, 2, 3 etc) are too small, it is very difficult to see any details. There is a lot of white space between the panels that can be removed, and this would be one way to instantly make the maps larger.

We fully  agree. We improved the use of space in Figures 1 through 3. We also changed colors in the latter (see also query #2 below). Let us know.

(ESTO ES TRABAJO PARA DIEGO & ALBERT).

-----------------------------------------------------------------------------------------
2. Figure 3 and 11, bottom panels. I find it difficult to distinguish between the red and magenta colours. Can you replace magenta with a different colour, maybe green?

We fully agree. Actually this affects more figures: Figures 3, 4, 11, and 14. In all of these we made the changes: RED->ORANGE and MAGENTA->DarkRed. These changes emulate our previous choice of colors in Nuevo et al. 82013) and Lloveras et al. (2017). We like to keep all "up" structures in "warm" palette. We edited text accordingly all along the manuscript.

(ESTO ES TRABAJO PARA DIEGO & ALBERT, CON LA ASESORIA ARTISTICA DE FEDE).

-----------------------------------------------------------------------------------------
3. Page 14, paragraph starting at line 34. You discuss the latitudinal distribution of short and long loops, and state that the small legs mainly populate the equatorial latitudes, and longer legs at higher latitudes. But this is a skewed result - their spatial positioning was a criteria for their categorisation, so this should not be presented as a scientific result.

(ESTO REQUIERE NO SOLO DISCUTIRLO, SINO QUE REVISEMOS CON DIEGO QUE MAPAS PODEMOS PRODUCIR SIN CONDICIONAR LOS FOOTPOINTS, SOLO DISTINGUIENDO TAMAÑOS. SI MAYORITARIAMENTE QUEDAN COMO AHORA YO HARÍA ESO Y EDITARIA EN FORMA ACORDE. SINO HAY QUE REPARAFRASEAR COSAS. ESTE ES UN PUNTO SUPER INTERESANTE PARA MI.)

-----------------------------------------------------------------------------------------
4. Table 2 summarises the differences of the median values of the DEMT and MHD model. This is OK. However, there is an opportunity here to present a more detailed comparison, including in particular the mean (or median) absolute deviation (MAD) of values between DEMT and MHD. The MAD is a more stringent, voxel-by-voxel test of the comparison, which cannot be seen from the histogram comparisons (e.g. figure 12/13) nor the median values of Table 2.

(CREO QUE NO ES BUENA IDEA. ESTO ESTA HECHO EN EL PAPER DE NISCHTHA. DEBEMOS DISCUTIRLO LOS TRES Y DAR UNA EXPLICACION CLARA AL REFEREE. COMO MINIMO LA PREGUNTA DEL REFEREE INDICA UNA DEFICIENCIA DEL PAPER: ESTO NO ESTA CLARO.)

-----------------------------------------------------------------------------------------
5. You discuss the less reliable results from AIA in coronal holes. The very recent paper by Saqri et al (Solar Physics 295, 2020) is relevant here, and should be referenced.

(DEBEMOS TODOS MIRAR ESE PAPER Y LUEGO DISCUTIR DONDE ESTAMOS CON ESTE TEMA. TENEMOS QUE VER LAS CORRIDAS DE FEFE. TERMINAREMOS PONIENDO ALGÚN DETALLE MÁS DEL TEMA EN EL DRAFT. )

-----------------------------------------------------------------------------------------
6. The abstract can be shortened somewhat, reducing the number of introductory sentences and with a little less emphasis on the method and future improvements, and more on the science results. In particular: the results of the energy balance analysis and the estimate of energy flux at the coronal base, which are important.

(TOTALMENTE, HAGAMOS ESTO LUEGO DE EDITAR TODO).

-----------------------------------------------------------------------------------------
7. Page 5, paragraph beginning line 34. You briefly describe fitting the DEM to a Gaussian. I know this approach is covered in detail in Nuevo 2015, but I would like a little more detail here. You should mention that, in general, DEMs do not necessarily have a clean Gaussian profile and that more complicated inversions are needed (reference https://ui.adsabs.harvard.edu/abs/2012A%26A...539A.146H/abstract , https://ui.adsabs.harvard.edu/abs/2019SoPh..294..135M/abstract , https://ui.adsabs.harvard.edu/abs/2019SoPh..294..136P/abstract ). Then explain briefly why DEMT leads to cleaner, non-multithermal profiles (due to the 3D spatial reconstruction of the line of sight). I assume that this is why you can use a straightforward Gaussian fit? Also efficiency?

(A DISCUTIR ENTRE LOS TRES. HABRÁ FRASES NUEVAS EN EL DRAFT COMO CONSECUENCIA DE ESTO).

-----------------------------------------------------------------------------------------
8. The introduction does not have many references to works beyond DEMT and AWSoM. The 2nd paragraph of the introduction offers a chance to remedy this, where you discuss the quiet-Sun corona. I know there are very few works that address the quiet corona in the context of DEM analysis, but you can reference https://www.aanda.org/articles/aa/full_html/2014/04/aa23054-13/aa23054-13.html. You can also mention https://iopscience.iop.org/article/10.1088/0004-637X/795/2/111 here (although you do reference this paper in more detail in the discussion). Another relevant paper which can be referenced, with DEM analysis of a large amount of quiet coronal data over long time periods, is https://advances.sciencemag.org/content/3/7/e1602056 .

(CREO QUE DEBEMOS HACER ESTO AL FINAL DE TODO, Y LUEGO EDITAR EL ABSTRACT).

LO QUE SIGUE DEBE SER TODO HECHO POR DIEGO, CONSULTANDOME SOLO A MI (ALBERT). TODO CAMBIO DEBERÁ ESTAR DESTACADO CON \EDIT{} EN ROJO.
-----------------------------------------------------------------------------------------
9. Some sections can benefit from weeding out of repetitions. You tend to repeat statements regarding the method a lot. For example:
- Paragraph starting page 13, line 41. This has already been said in the method.
- Sentence Page 14, line 25 'For each leg…
- statement in parenthesis at page 15, line 24.
- Section 4, first two paragraphs.
- Page 26, line 26:
 'In the streamer belt region we combined the DEMT results and the AWSom magnetic model to infer the energy input phi at the coronal base required to maintain stable coronal loops. We found characteristic values in the range…'
Shorten to: 'The energy input phi at the coronal base, required to maintain stable coronal loops, is in the range…'
- Page 26, lines 38-43, between 'Results of the AWSoM….summarized as follows.' can be omitted.

-----------------------------------------------------------------------------------------
Minor grammatical improvements, typos, and removal of redundant statements
Page number, line number: 
3,36: quantitive analysis
3, 44: based on data
4, 25: absent => is this the right choice of word? I would think that the effect of fast dynamics is reduced, rather than being completely absent?
Equation 1 (and subsequent). You use LDEM and TRF. Is it more correct to use Greek symbols rather than acronyms in the equations? However, if you have used these acronyms in equations in previous studies, please leave as is.
6, 9: average absolute relative difference
6, 35: energy partitioning is improved
6, 46: broadened
6, 50 and 51: explain the subscripts for N and T
7, 39: waves is set to L
7, 41: radially stretched => is there a better description? 
7, 41: The spherical grid… has an adaptive grid that has fine resolution near the Sun, and increases…
7, 46: million cells on 6 x 
7, 49: The AWSoM simulation of the solar corona for…to the DEMT in the results section.
8, 23: products are traced
8, 33: For DEMT the data points used are 
8, 48: hereafter, with del_r=e_r.del being the radial derivative operator, and e_r is the 
9, 2: to directly compare the observed
9, 11: , and later by Aschwanden
9, 17: and the heliocentric height r. We then
9, 19: the goodness of fit  we perform
9, 21: uncertainty of the DEMT, selecting legs
9, 24: linear fit to temperature is weak, are excluded
9, 28: according to del_r
9, 31: quality of the fit considers
9, 33: In summary, a selected leg must meet three conditions:
9, 40: temperature and height points must meet
9, 48: four different types:
10, 12: type 0 to II allows a study of the streamer belt in three distinct layers at increasing height.
10, 25: model, as described
10, 35: transverse => cross-sectional?
11, 44: Figures 1 and 2 show …. (omit 'As an example', not needed)
12, 35: Rotation CR-2082 has two small… (and same in following sentence)
13: 34: by Equation 4 show that the agreement… (omit 'in most of the coronal volume of the DEMT grid', not needed)
13: 36: A similar result was
15, 19: to this point in the Conclusions.
15, 28: Caption to table 1. Informed => given? Also explain that the CR-2208 values are given in parenthesis.
15, 42: Table 1 summarises the results of the…
16, 51: , the temperature based on AIA data
17, 45: Considering this error, Figure 5
18, 8: legs, each loop was
18, 20: characterised    by temperatures that are are progressively larger, and farther from T_c, for both rotations.
18, 33: smallest sized loops of type 0, and it is likely due to emission out of the instrumental sensitivity range.
19, 17: axisymmetric, similar to the tomographic results. (In fact, you should avoid using 'tomographic model' since it is not a model, this happens a few times in the text).
19, 45: a visual comparison reveals similar
19, 50: Such a comparison…, with the top
20, 30: are worth highlighting.
20, 43: boundary. Lastly, the DEMT… ('note that' is usually not needed, you use quite a lot in text)
20, 47: For comparison, B_r in the CHs increases from
22, 42: tomografic => tomographic
22, 48: This figure can be compared
22, 49: …DEMT results. The AWSoM maps are more densely populated
22, 50: having spatially smoother distributions of electron density and temperature than those of DEMT.
23, 38: variation relative to the DEMT. (Then omit 'The following major results can be drawn', not needed).
25, 47: Omit 'Concerning the DEMT reconstructions, Figure 3 shows that, for both rotations, …'  Start paragraph with 'Magnetic field lines of type…'
25, 50: Omit 'Figure 5 and Table 1 show in 3D quantitive detail how…', and start sentence with 'These progressively outer'
26, 12: such comparison provided a consistency check. (And omit 'for the changes implemented in the DEMT technique.')
26, 20: less reliable for CHs.
26, 24: algorithm to deal
27, 12: This is likely the cause of a more accurate match to the…
27, 14: Omit first sentence of paragraph, not needed.
27, 30: in the range of
27, 33: This will be investigated in

-----------------------------------------------end of response---------------------------

### 2020-02-18 response_to_review_SOLA-D-20-00015_v1.txt
..

@@
 
-We deeply acknowledge the reviewer, whose report not only reflects how carefully he/she read it, but which also contains a series highly relevant, useful, and very constructive criticisms and suggestions.
-It is the opinion of the authors that this review ranks among the very best they ever read.
+We deeply acknowledge the reviewer, whose report reflects her/his very careful and interested read, containing a series of highly relevant, useful, and very constructive comments, criticisms, and suggestions.
 
@@
 
-(ESTO ES TRABAJO PARA DIEGO & ALBERT).
+(ESTO ES TRABAJO PARA DIEGO & ALBERT, XTOOLS).
 
@@
 
-(ESTO ES TRABAJO PARA DIEGO & ALBERT, CON LA ASESORIA ARTISTICA DE FEDE).
+(ESTO ES TRABAJO PARA DIEGO, CON LA ASESORIA ARTISTICA DE FEDE y ALBERT).
 
@@
 DEBEMOS DISCUTIRLO LOS TRES Y DAR UNA EXPLICACION CLARA AL REFEREE.
-COMO MINIMO LA PREGUNTA DEL REFEREE INDICA UNA DEFICIENCIA DEL PAPER: ESTO NO ESTA CLARO.)
+COMO MINIMO LA PREGUNTA DEL REFEREE INDICA UNA DEFICIENCIA DEL PAPER: ESTO NO ESTA CLARO.
+O YO NO ESTY ENTENDIENDO AÚN EL COMENTARIO.)
 
@@
 
-LO QUE SIGUE DEBE SER TODO HECHO POR DIEGO, CONSULTANDOME SOLO A MI (ALBERT). TODO CAMBIO DEBERÁ ESTAR DESTACADO CON \EDIT{} EN ROJO.
+LO QUE SIGUE DEBE SER TODO HECHO POR DIEGO, CONSULTANDO PRINCIPALMENTE A ALBERT. TODO CAMBIO DEBERÁ ESTAR DESTACADO CON \EDIT{} EN ROJO.
 -----------------------------------------------------------------------------------------

### 2020-02-18 response_to_review_SOLA-D-20-00015_v1.txt
..

@@
 
-Thank you very much for you email with the report on the first version of our manuscript SOLA-D-20-00015, titled "Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling".
+Thank you very much for your email with the report on the first version of our manuscript SOLA-D-20-00015, titled "Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling".
 

### 2020-02-21 response_to_review_SOLA-D-20-00015_v1.txt
..

@@
 
-We deeply acknowledge the reviewer, whose report reflects her/his very careful and interested read, containing a series of highly relevant, useful, and very constructive comments, criticisms, and suggestions.
+We deeply acknowledge the reviewer, whose report reflects her/his very careful and interested read, containing a series of relevant, useful, and constructive criticisms and suggestions.
 
@@
 
-(ESTO REQUIERE NO SOLO DISCUTIRLO, SINO QUE REVISEMOS CON DIEGO QUE MAPAS PODEMOS PRODUCIR SIN CONDICIONAR LOS FOOTPOINTS, SOLO DISTINGUIENDO TAMAÑOS.
-SI MAYORITARIAMENTE QUEDAN COMO AHORA YO HARÍA ESO Y EDITARIA EN FORMA ACORDE.
-SINO HAY QUE REPARAFRASEAR COSAS.
-ESTE ES UN PUNTO SUPER INTERESANTE PARA MI.)
+DIEGO, SUGERIMOS CON FEDE QUE REHAGAS COMO EXPERIMENTO LOS PANELES INFERIORES DE LA FIGURAS 3 CON OTRA DEFINICION DE TYPE 0, I Y II.
+SE QUE LO HICIMOS, PERO LO REVISITARIA Y SUGERIMOS AGREGAR UN GRAFICO DE HISTOGRAMA DE FOOTPOINT DE LAS CUATRO CLASES.
+FIJATE:
+
+* TYPE-0:   CLOSED-SMALL-DOWN
+* TYPE-I:   CLOSED-SMALL-UP
+* TYPE-II:  CLOSED-LARGE-UP
+* TYPE-III: TAL COMO ESTÁ (PARA QUE NO NOS ENSUCIE LA ESTADISTICA DE RESULTADOS DEMT LOS CHs DE LAT BAJA)
+
+SI VEMOS QUE NO ES TAN SUCIO EL RESULTADO, PODEMOS DEJAR ESA SELEECCION YE INCLUIR QUIZA UN NUEVO GRAFICO: HISTOGRAMA DE FOOTPOINT DE LOS 4 TIPPOS.
+(UNA SOLA FIURA DE 4 COLORES) QUE SEAN LOS NUEVOS DOS PANELES INFERIORES DE LA fIGURA 3, QUE TENDRIA 6 PANELES EN TOTAL.
+LUEGO DECIDAMOS SI QUEDA COMO ESTA O USAMOS UNA NUEVA VERSION, Y EN CUALQUIERA DE AMBOS CASOS RETOCAMOS UN POCO EL TEXTO DE PAG 14 QUE QUEDO "MISSLEADING".
 
@@
 
-(CREO QUE NO ES BUENA IDEA.
-ESTO ESTA HECHO EN EL PAPER DE NISCHTHA.
-DEBEMOS DISCUTIRLO LOS TRES Y DAR UNA EXPLICACION CLARA AL REFEREE.
-COMO MINIMO LA PREGUNTA DEL REFEREE INDICA UNA DEFICIENCIA DEL PAPER: ESTO NO ESTA CLARO.
-O YO NO ESTY ENTENDIENDO AÚN EL COMENTARIO.)
+REFERENCIA: https://en.wikipedia.org/wiki/Median_absolute_deviation
+
+DIEGO, PROPONEMOS HACER ESTO CON FEDE.
+
+DEFINAMOS EL CAMPO ESCALAR Xi = (X_MHD - X_tom) / X_tom, DONDE "X" ES CUALQUIER RESULTADO A LO LARGO DE LOOP (Ncb, LAMDA_n, ó <Tm>).
+LA TABLA 2 INFORMA LOS VALORES: "[Med(X_MHD) - Med(X_tom)]/Med(X_tom)".
+
+PROPONEMOS DEJAR LOS HISTOGRAMAS DE LAS FIGS 12 Y 13 COMO ESTÁN, PERO EXPANDIR LA TABLA 2 A QUE INCLUYA DOS COLUMNAS MÁS INDICANDO ESTOS DOS INDICADORES DE CADA CAMPO "Xi":
+* Med(Xi)  (debería aproximarse a los porcentuales y signos entre paréntesis que actualmente informa la Tabla 2).
+* MAD = Med(Abs(Xi-Med(Xi))).
+
+LUEGO EDITAMOS TABLA Y TEXTO DEL PAPER.
 
@@
 
-(DEBEMOS TODOS MIRAR ESE PAPER Y LUEGO DISCUTIR DONDE ESTAMOS CON ESTE TEMA. TENEMOS QUE VER LAS CORRIDAS DE FEFE. TERMINAREMOS PONIENDO ALGÚN DETALLE MÁS DEL TEMA EN EL DRAFT. )
+YO PROPONGO HACER DOS O TRES EXPERIMENTOS DE CARACRTERIZACION Y RESOLUCION DEL PROBLEMA TESTEANDOLO A LAS TRES ALTURAS DEL PAPER. SI VEMOS QUE SALIO, POR QUE NO MEJORAR EL PAPER.
 

### 2020-02-21 lloveras_2020_Albert.tex
..

--- 2020-01-30 lloveras_2020_Albert.tex
@@
 
-%-------------remove these two lines before submision--------------------------
+%---------REMOVE THESE OPTIONS AND DEFs BEFORE SUMBISSION---------------------------------------
 \usepackage[usenames,dvipsnames]{xcolor} % Las opciones: [USENAMES,DVIPSNAMES] 
+                                         % ponen a disposición los colores ejemplificados aquí:
+                                         % https://en.wikibooks.org/wiki/LaTeX/Colors
+\def\note#1{\textcolor{blue}{NOTE: #1}}
+\def\diego#1{\textcolor{red}{#1}}
 \def\albert#1{\textcolor{orange}{#1}}
-%------------------------------------------------------------------------------
+\def\fede#1{\textcolor{ForestGreen}{#1}}
+\def\temp#1{\textcolor{gray}{#1}}
+%-----------------------------------------------------------------------------------------------
 
 \begin{document}
+
 \begin{article}
@@
 
-Legs of type down turn out to have a significant population only for closed-small loops.
+{Legs of type down turn out to have a significant population only for closed-small loops.
 In the case of closed-large loops and open field lines, there are very few cases of type down.
-Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population \albert{in each case.
-In Section} \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic structures are statistically analysed.
-As shown in Section \ref{demt_res}, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.
+Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population in each case}.
+In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic structures are statistically analysed.
+{As shown in Section \ref{demt_res}, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}
 
@@
 We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.
-Legs of type 0 are not included for AWSoM \albert{as it currently can not simulate down loops, as discussed in Section \ref{discu}.}}
+Legs of type 0 are not included for AWSoM as it currently can not simulate down loops, as discussed in Section \ref{discu}.}
 
@@
 
-\albert{Down loops are to be expected if heating is enhanced at the footpoints of coronal structures.
+Down loops are to be expected if heating is enhanced at the footpoints of coronal structures.
 \citet{schiff_2016} numerically simulated stable down loops by means of a 1D steady-state model, requiring that the initial population of Alfvén waves is efficiently converted into compressive modes.
@@
 In the AWSoM model, heating is controlled by two key parameters, namely, the Alfvén wave dissipation length, and its reflection coefficient.
-So far, attempts to reproduce observed down loops in AWSoM simulations by increasing the reflection coefficient have not been successful.}
+So far, attempts to reproduce observed down loops in AWSoM simulations by increasing the reflection coefficient have not been successful.
 

### 2020-02-21 response_to_review_SOLA-D-20-00015_v1.txt
..

@@
 
-(A DISCUTIR ENTRE LOS TRES. HABRÁ FRASES NUEVAS EN EL DRAFT COMO CONSECUENCIA DE ESTO).
+Thanks for this comment and the references.
+As the LDEM describes the temeprature distribution of the plasma in a specific voxel it does not deal with different large scale structures, as it usually it may be the case for the DEM describing the plasma alog a full line-of.sight (LOS).
+In that sense one can expect as you say, cleaner, profiles than those observed by DEM studies.
+Still, if one adds tbhe 335 A channel, which adds two sensitivity poits at ~ 1.0 MK and ~ 2.5 MK, one finds that a a bi-Gaussian LDEM model best predics all the tomographic emissivities.
+That is the main conclusion of Nuevo et.
+al.
+(2015).
+The interpretation in that case is that the unresolved independent strands threading the voxel can have two different characteristic temperatures.
+Nuevo et al.
+(2015).
+So in this sense, the plasma within the voxel can be multi-thermal.
+As for efficiency, the parametric technique is comparably efficient independently of the chosen model.
+We did read the  We expanded this discussion in the text.
 
@@
 
-(CREO QUE DEBEMOS HACER ESTO AL FINAL DE TODO, Y LUEGO EDITAR EL ABSTRACT).
+ALBERT VA A ESCRIBIR UN POCO DE TEXTO.
 

### 2020-03-04 lloveras_2020.tex
nuevas figuras

@@
 \begin{center}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1105_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1105_Rsun.pdf}
 \caption{Same as Figure \ref{carmaps_demt_2082} but for CR-2208.}
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
+%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
 %\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
+%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_conajuste_doble_error_Rpoint-map.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_conajuste_doble_error_Rpoint-map.pdf}
 %\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_full_conajuste_doble_errorhighpoints.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_full_conajuste_doble_errorhighpoints.eps}
+
 \caption{\emph{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR-2082 (left) and CR-2208 (right).
@@
 \includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_conajustene_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_conajustelambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_conajusteTm.eps}
 \caption{{Statistical distribution of {DEMT results for rotations CR-2082 (blue) and CR-2208 (red)} traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}.
@@
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105_2.pdf}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105_2.pdf}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_multistart2_1105.pdf}
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105_2.pdf}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105_2.pdf}
+\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_multistart2_1105.pdf}
 \includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2082_1105_2.pdf}
@@
 \includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_Tm.eps}\\
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_Tm.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_conajuste_ne_1055.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_conajuste_lambda_n.eps}
+\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_conajuste_Tm.eps}
 \caption{Same as Figure \ref{histos_2082} for CR-2208.}
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up_conajuste.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_conajuste.eps}
 \caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of {type I (red), II (magenta), and III (cyan)}, for CR-2082 (top panels) and CR-2208 (bottom panels).

### 2020-03-05 response_to_review_SOLA-D-20-00015_v1.txt
..

@@
 
-We fully  agree. We improved the use of space in Figures 1 through 3. We also changed colors in the latter (see also query #2 below). Let us know.
-
-(ESTO ES TRABAJO PARA DIEGO & ALBERT, XTOOLS).
+We fully  agree. We improved the use of space in Figures 1 through 3. We also changed colors in the latter (see also query #2 below).
 
@@
 We fully agree.
-Actually this affects more figures: Figures 3, 4, 11, and 14.
-In all of these we made the changes: RED->ORANGE and MAGENTA->DarkRed.
-These changes emulate our previous choice of colors in Nuevo et al.
-82013) and Lloveras et al.
+Actually this affects all following Figures #: 3, 4, 11, and 14.
+In those, we applied the following changes: Red->Orange and Magenta->Red.
+These emulate our previous choice of colors in Nuevo et al.
+(2013) and Lloveras et al.
 (2017).
-We like to keep all "up" structures in "warm" palette.
+We like to keep all "up" structures in a "warm" palette.
 We edited text accordingly all along the manuscript.
-
-(ESTO ES TRABAJO PARA DIEGO, CON LA ASESORIA ARTISTICA DE FEDE y ALBERT).
+We believe the colors are now clearly distinguishable in all figures.
 
@@
 
-DIEGO, SUGERIMOS CON FEDE QUE REHAGAS COMO EXPERIMENTO LOS PANELES INFERIORES DE LA FIGURAS 3 CON OTRA DEFINICION DE TYPE 0, I Y II.
-SE QUE LO HICIMOS, PERO LO REVISITARIA Y SUGERIMOS AGREGAR UN GRAFICO DE HISTOGRAMA DE FOOTPOINT DE LAS CUATRO CLASES.
-FIJATE:
-
-* TYPE-0:   CLOSED-SMALL-DOWN
-* TYPE-I:   CLOSED-SMALL-UP
-* TYPE-II:  CLOSED-LARGE-UP
-* TYPE-III: TAL COMO ESTÁ (PARA QUE NO NOS ENSUCIE LA ESTADISTICA DE RESULTADOS DEMT LOS CHs DE LAT BAJA)
-
-SI VEMOS QUE NO ES TAN SUCIO EL RESULTADO, PODEMOS DEJAR ESA SELEECCION YE INCLUIR QUIZA UN NUEVO GRAFICO: HISTOGRAMA DE FOOTPOINT DE LOS 4 TIPPOS.
-(UNA SOLA FIURA DE 4 COLORES) QUE SEAN LOS NUEVOS DOS PANELES INFERIORES DE LA fIGURA 3, QUE TENDRIA 6 PANELES EN TOTAL.
-LUEGO DECIDAMOS SI QUEDA COMO ESTA O USAMOS UNA NUEVA VERSION, Y EN CUALQUIERA DE AMBOS CASOS RETOCAMOS UN POCO EL TEXTO DE PAG 14 QUE QUEDO "MISSLEADING".
+Thanks for pointing this out....
+ESTO REQUIERE CAMBIOS EN EL PAPER JUSTIFICANDO CON CLARIDAD LA ELECCION DE LOS LIMITES LATITUDINALES Y LA SELECCION DE SOLO UP EN TYPE II Y III.
+Y UNA RESPUESTA ACORDE.
 
@@
 
-YO PROPONGO HACER DOS O TRES EXPERIMENTOS DE CARACRTERIZACION Y RESOLUCION DEL PROBLEMA TESTEANDOLO A LAS TRES ALTURAS DEL PAPER. SI VEMOS QUE SALIO, POR QUE NO MEJORAR EL PAPER.
+ESTO FUE SOLUCIONADO.
+EL ORIGEN DEL PROBLEMA NO RADICA EN STRAY-LIGHT DECON.
+EL EFECTO DE ESTO EN TOM, APLICADO A DATOS EUVI, FUE EXPLORADO EN LLOVERAS ET AL.
+(2017).
+CIERTAMENTE NOS INTERESA INCORPORAR ESTO AL PIPELINE DE AIA SI LA PFS ESTÁ BIEN CARACTERIZADA, PERO ES UN TEMA QUE DEBEMOS INVESTIGAR.
+EXPLICAR COMO SE SOLUCIONÓ Y REMOVER TODO LO NO NECESARIO EN EL PAPER (AZUL) Y AGREGAR COSAS NUEVAS (ROJO).
 
@@
 Thanks for this comment and the references.
-As the LDEM describes the temeprature distribution of the plasma in a specific voxel it does not deal with different large scale structures, as it usually it may be the case for the DEM describing the plasma alog a full line-of.sight (LOS).
+As the LDEM describes the temperature distribution of the plasma in a specific voxel it does not deal with different large scale structures, as it usually it may be the case for the DEM describing the plasma alog a full line-of.sight (LOS).
 In that sense one can expect as you say, cleaner, profiles than those observed by DEM studies.

### 2020-03-05 lloveras_2020_v2.tex
tablas con numeros acomodados en type III
lloveras_2020_v2.tex ahora tiene los nombres de las figuras correctas y ademas se mejorarons estilos de varias figuras

--- 2020-02-21 lloveras_2020_Albert.tex
@@
 \usepackage[utf8]{inputenc}
+\usepackage[usenames,dvipsnames]{xcolor}
 
@@
 %% \renewcommand{}{} if it is already defined in LaTeX
+
+\def\edit#1{\textcolor{Red}{#1}}
+\def\del#1{\textcolor{Blue}{#1}}
+
 \renewcommand{\deg}{$^\circ$}
@@
 \newcommand{\procspie}{{\it Proc. SPIE}}
-
-%---------REMOVE THESE OPTIONS AND DEFs BEFORE SUMBISSION---------------------------------------
-\usepackage[usenames,dvipsnames]{xcolor} % Las opciones: [USENAMES,DVIPSNAMES] 
-                                         % ponen a disposición los colores ejemplificados aquí:
-                                         % https://en.wikibooks.org/wiki/LaTeX/Colors
-\def\note#1{\textcolor{blue}{NOTE: #1}}
-\def\diego#1{\textcolor{red}{#1}}
-\def\albert#1{\textcolor{orange}{#1}}
-\def\fede#1{\textcolor{ForestGreen}{#1}}
-\def\temp#1{\textcolor{gray}{#1}}
-%-----------------------------------------------------------------------------------------------
 
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
+%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
 %\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
+%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_conajuste_doble_error_Rpoint-map.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_conajuste_doble_error_Rpoint-map.pdf}
 %\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
 %\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_full_conajuste_doble_errorhighpoints.eps}
+\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_full_conajuste_doble_errorhighpoints.eps}
 \caption{\emph{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR-2082 (left) and CR-2208 (right).
@@
 II   & 0&98 &(\Mi&20\%)  &   9&9 &(\Pl&19\%) &   1&36 &(\Pl&16\%) \\
-III  & 0&66 &(\Mi&12\%)  &   7&7 &(\Pl&15\%) &   0&97 &(\Pl&18\%) \\
+III  & 0&66 &(\Mi&\edit{21}\%)  &   7&7 &(\Pl&15\%) &   0&97 &(\Pl&\edit{17}\%) \\
 \hline          
@@
 II   & 0&79 &(\Pl&~9\%)  &  11&8 &(\Mi&14\%) &   1&58 &(\Mi&~8\%) \\
-III  & 0&58 &(\Mi&~3\%)  &   8&9 &(\Mi&18\%) &   1&14 &(\Mi&18\%) \\
+III  & 0&\edit{52} &(\edit{\Pl}&~\edit{8}\%)  &   8&9 &(\Mi&18\%) &   1&\edit{13} &(\Mi&18\%) \\
 \hline   

### 2020-03-06 lloveras_2020_v2.tex
ediciones gramaticales y typos en V2.tex

@@
 
-{Combining the DEMT and AWSoM models, we carry out a detailed quantitatively analysis of two target rotations.
+{Combining the DEMT and AWSoM models, we carry out a detailed \edit{quantitative} analysis of two target rotations.
 We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during {the end of the declining} phase of SC 24.
 {In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} {(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG: \citealt{gong}).
-In the case of CR-2208, the DEMT analysis is based in data taken} by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} {(SDO), while the AWSoM model uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}
+In the case of CR-2208, the DEMT analysis is based \edit{on} data taken} by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} {(SDO), while the AWSoM model uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}
 
@@
 This has two implications.
-Firstly, the fast dynamics that typically characterizes those structures is absent from the data.
+Firstly, the fast dynamics that typically characterizes those structures is \edit{absent/reduced} from the data.
 Secondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume.
@@
 \noindent 
-{being the} average relative difference between the tomographic and the synthetic FBEs.
+{being the} \edit{average absolute relative difference} between the tomographic and the synthetic FBEs.
 {The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.} {For a full description of the {DEMT technique} we refer the reader to \citet{frazin_2009}.}
@@
 {In a previous} version of the model, the cascade time of the major wave was used to determine the wave damping rate \citep{Cha2011, Van2014}.
-{In its present version, the energy partitioning  improved} by using the Alfv\'{e}n wave number associated with the damping rate as determined by the critical balance condition, which uses the cascade time of the minor wave \citep{Lit2007}.
+{In its present version, the \edit{energy partitioning is improved}} by using the Alfv\'{e}n wave number associated with the damping rate as determined by the critical balance condition, which uses the cascade time of the minor wave \citep{Lit2007}.
 This leads to more electron heating and less solar wind acceleration \citep{Van2019b}.
@@
 To resolve these gradients in a global model would require excessive numerical resources.
-As described in \citet{Lio2009} and \citet{Sok2013}{, the TR is artificially broaden to be resolved with a} finest grid resolution of 0.001\,$\mrsun$.
-To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot} =2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K.
+As described in \citet{Lio2009} and \citet{Sok2013}{, the TR is artificially \edit{broadened} to be resolved with a} finest grid resolution of 0.001\,$\mrsun$.
+To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot} =2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K\edit{, where the subscripts represents electrons and ions}.
 The upper chromosphere is required to extend radially for the density to fall rapidly to correct (lower) values \citep{Lio2009}.
@@
 The boundary condition for Alfv\'{e}n wave energy is given by the {poynting flux ($S_{A}$)} of the outgoing {wave, $({S_{A}/}{B})_{\odot} = 1.1\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ and $1.0\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ for CR-2082 and CR-2208, respectively, with $B_{\odot}$ being the field} strength at the inner boundary.
-The correlation length of the Alfv\'{e}n waves is set {to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$m\,$\sqrt{T}$.}
+The correlation length of the Alfv\'{e}n waves is set {to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$m\,$\sqrt{T}$}\edit{, where $L_{\perp}$ is transverse to the magnetic field direction.}
 
 {The computational domain of the solar corona} extends from 1 to {$24\,\mrsun$}.
-The spherical grid in the solar corona is radially stretched (with a maximum resolution {of $0.001\,\mrsun$} near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates.
+\del{The spherical grid in the solar corona is radially stretched (with a maximum resolution {of $0.001\,\mrsun$} near the Sun)} \edit{The spherical grid has an adaptive grid that has fine resolution near the Sun, and increases outward} with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates.
 The Adaptive Mesh refinement (AMR) resolves the angular cell size to $1.4\mdeg$ between $1 - 1.7\,\mrsun$ and to $2.8\mdeg$ outside this radius range.
-The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082.
+The solar corona component uses about 3 million cells on $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082.
 Local time stepping is used to speed up the steady state convergence.
-The AWSoM simulation results of the structure of the solar corona for solar minimum conditions represented by CR-2082 and CR-2208 are compared to the DEMT as described in the results section.
+\edit{The AWSoM simulation of the solar corona for solar minimum conditions represented by CR-2082 and CR-2208 are compared to the DEMT in the results section.}
 
@@
 
-At this {stage, DEMT and AWSoM products} can be traced along open and closed magnetic field lines.
+At this {stage, DEMT and AWSoM products} \edit{are} traced along open and closed magnetic field lines.
 Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one).
@@
 For each open field line and {for each closed field leg}, an exponential fit {was applied} to the electron density {data points} and a linear fit applied to the electron temperature {data points}.
-For {the DEMT model} the data points used were $\sqravgN(r)$ and $\Tm(r)$, and in case of {the AWSoM models} the data points used were $\Ne(r)$ and $\Te(r)$.
+\edit{For DEMT the data points used are} $\sqravgN(r)$ and $\Tm(r)$, and in case of {the AWSoM models} the data points used \edit{are} $\Ne(r)$ and $\Te(r)$.
 The exponential and linear fit equations are described by
@@
 In the electron temperature fit, $a\,[\MK/\mrsun]$ is the slope and $T_0\,[\MK]$ is the electron temperature at the footpoint of the loop.
-The slope $a$ estimates the radial gradient of the electron temperature along the loop, which we denote as $a = \dr\Tm$ hereafter, being $\dr\equiv\er\cdot\nabla$ the radial derivative operator, where $\er$ is the heliocentric radial unit vector.
+The slope $a$ estimates the radial gradient of the electron temperature along the loop, which we denote as $a = \dr\Tm$ hereafter, \edit{with} $\dr\equiv\er\cdot\nabla$ \edit{being} the radial derivative operator \edit{and} $\er$ is the heliocentric radial unit vector.
 
 In the case of the electron density, the fitted function corresponds to the isothermal hydrostatic equilibrium solution, allowing for variation of the solar gravitational acceleration with height.
-This choice of function provides a straightforward means to directly evaluate how compatible is the observed coronal thermodynamical state with the hydrostatic solution.
+This choice of function provides a straightforward means to directly \edit{compare the observed} coronal thermodynamical state with the hydrostatic solution.
 
@@
 As speculated by the authors of those works, down loops can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
-Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}.
+Down loops were first predicted by \citet{serio_1981}, and later by \citet{aschwanden_2002}.
 In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and {considering time-averaged heating rates.}}
 
-{To determine if the leg of a traced field line is} of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points.
+{To determine if the leg of a traced field line is} of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$.
 We then select field lines for which the temperature {is significantly correlated with height} by requiring $|\rhoTr| > 0.5$.
-{To test the goodness of the fit to the temperature-height data we perform a chi-squared test \citep{recipes} considering the uncertainty of the DEMT data points, selecting legs for which the fit matches the data with a 90\% confidence level.} In this way, legs for which the DEMT temperature does not show a significant {correlation} with height, or the linear fit to temperature is {not} good enough, are {excluded from the} analysis.
-{The test is also applied to the density-height data points, to ensure the trend is reasonably represented by the exponential fit.} Finally, selected legs are then classified as up or down according to if $\dr\Tm > 0$ or $\dr\Tm < 0$, respectively.
+{To test the goodness of the fit \del{to the temperature-height data} we perform a chi-squared test \citep{recipes} considering the uncertainty of the DEMT data, selecting legs for which the fit matches the data with a 90\% confidence level.} In this way, legs for which the DEMT temperature does not show a significant {correlation} with height, or the linear fit to temperature is \edit{weak}, are {excluded from the} analysis.
+{The test is also applied to the density-height data points, to ensure the trend is reasonably represented by the exponential fit.} Finally, selected legs are then classified as up or down according to $\dr\Tm > 0$ or $\dr\Tm < 0$, respectively.
 The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg.
-{The chi-squared test to evaluate the quality of the fits considers the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$.} In summary, to be selected a leg must meet all three following conditions:
+{The chi-squared test to evaluate the quality of the \edit{fit} considers the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$.} In summary, \edit{a selected leg must meet three conditions:}
 
@@
 \item 
-The {DEMT temperature and height data points must meet} $|\rhoTr| > 0.5$.
+The {DEMT temperature and height points must meet} $|\rhoTr| > 0.5$.
 \item 
@@
 {To characterize the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model.
-Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types in this work:}
+Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types:}
 
@@
 In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic structures are statistically analysed.
-{As shown in Section \ref{demt_res}, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}
+{As shown in Section \ref{demt_res}, classification of legs from type \edit{type 0 to II allows a study of the streamer belt in three distinct layers at increasing height.}}
 
@@
 In particular, \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to maintain stability.
-The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in Section \ref{trace}.}
+The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, as described in Section \ref{trace}.}
 
@@
 
-{As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations.
+Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations.
 Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of {the} tomographic grid ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}.
@@
 {Both target rotations are highly axisymmetric, \textit{i.e.} characterized by a high azymuthal symmetry.
-Rotation CR-2082} showed two {small} ARs, both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg$  {(not identified in the NOAA catalog)}.
-{Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$ {(NOAA 12722, 12721)}.}
+Rotation CR-2082} \edit{has} two {small} ARs, both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg$  {(not identified in the NOAA catalog)}.
+{Rotation CR-2208} \edit{has} two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$ {(NOAA 12722, 12721)}.}
 
@@
 
-Latitude-longitude maps of the score $R$ defined by Equation \ref{R} show that in most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$.
+Latitude-longitude maps of the score $R$ defined by Equation \ref{R} show that \edit{the agreement between the tomographic} and synthetic FBEs is $\lesssim 1\%$.
 The notable exception is to be found only in the CHs of the rotation {analysed} based on AIA data.
@@
 This is related to the relatively larger values of the score $R$ for the CH of CR-2208, making the DEMT results based on AIA data less reliable in the CHs.
-We will return to this point in the conclusion section.}
+We will return to this point in the \edit{Conclusions}.}
 
@@
 \caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of legs defined in Section \ref{trace}.
-For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
+For CR-2082 values are expressed in absolute terms, while for CR-2208 they are \edit{given} as a percentual variation relative to the CR-2082 value \edit{in the parentheses.}}
 \label{tabla_demt}
@@
 
-{Table \ref{tabla_demt} summarizes a} quantitative comparative analysis between the results of the two {target rotations}.
+Table \ref{tabla_demt} summarizes \edit{the results of the quantitative comparative analysis between the two {target rotations}}.
 For CR-2082 quantities are expressed as absolute values, {while} for CR-2208 they are expressed relative to the corresponding results for CR-2082.
@@
 In comparing the DEMT results obtained for the two selected targets, {we highlight} they rely on data provided by two different instruments, {namely EUVI and AIA for CR-2082 and CR-2208, respectively.} To quantify the systematic difference of the DEMT products {due to the different filter sets of} both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
-They found that while the density {products are} essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, \textit{i.e.} $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$.
-Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was {characterized by temperatures $\approx 10-15\%$ larger relative to CR-2082} throughout the streamer belt region.
+They found that while the density {products are} essentially equal, the temperature \edit{based on AIA data} is systematically 8\% larger than the one based on EUVI data, \textit{i.e.} $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$.
+Considering \edit{this error}, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was {characterized by temperatures $\approx 10-15\%$ larger relative to CR-2082} throughout the streamer belt region.
 As for the electron density products, CR-2208 was found to be $\approx 10-20\%$ less dense than CR-2082 throughout the streamer belt region.
@@
 
-{To analyse the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the classification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).
+{To analyse the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the classification of both its legs, each loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).
 {For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.}
@@
 This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors contributing to maximize $E_r$ for loops of type 0.
-As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0 are characterized by {the largest} values of electron density.
+As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0 are \edit{characterised} by {the largest} values of electron density.
 Also, in the range of sensitivity of the EUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$.
-According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterized by {values of temperature that are progressively larger and farther} from the value $\Tc$, for both rotations.}
+According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are \edit{characterised by temperatures that are are progressively larger, and farther from $\Tc$, for both rotations.}}
 
@@
 Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$.
-As shown by \citet{maccormack_2017}, {this affects only the smallest sized loops of the type 0}, and it is likely due to measurement errors.
+As shown by \citet{maccormack_2017}, this affects only the smallest sized loops of the type 0, and it is likely due \edit{to emission out of the instrumental sensitivity range}.
 Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range.
@@
 {Thick-black curves} indicate the magnetic open/closed boundaries based on the magnetic field of the AWSoM model.
-Visual inspection of these maps shows that the AWSoM model for both rotations is highly {axisymetric}, as the tomographic model.
+Visual inspection of these maps shows that the AWSoM model for both rotations is highly {axisymetric}, as the tomographic \edit{results}.
 
@@
 Furthermore, for both rotations, the temperature maps show the low latitudes of the equatorial streamer belt to be characterized by lower temperatures than its mid-latitudes, as also seen in the DEMT results.
-The latitude-longitude maps of the AWSoM and DEMT results are shown in the same units and scales, so that a visual comparison among them already reveals similar values of electron density and temperature in both models.}
+The latitude-longitude maps of the AWSoM and DEMT results are shown in the same units and scales, so that a \edit{visual comparison reveals} similar values of electron density and temperature in both models.}
 
@@
 {Being highly axisymmtric rotations, the longitude-averaged latitudinal {profile} of the results of both models is an informative way to compare their large-scale structure.
-Such comparison is shown in Figure \ref{perf_lat} at height $1.105\,\mrsun$, with top panels comparing electron density and mid panels electron temperature.
+\edit{Such a comparison} is shown in Figure \ref{perf_lat} at height $1.105\,\mrsun$, \edit{with the top} panels comparing electron density and mid panels electron temperature.
 {The longitude-averaged latitudinal profile of $B_r$ is shown in the bottom panels.} In these longitude-averaged profiles, longitudes containing ARs or low latitude CHs were excluded.
@@
 
-{{Several details from Figure \ref{perf_lat} are worth being highlighted.
+{{Several details from Figure \ref{perf_lat} are \edit{worth highlighted}.
 Firstly, at most latitudes the overall agreement of the electron density of both models is within $\approx 20\%$ for CR-2082, and $\approx 5\%$ for CR-2208.
@@
 Note this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
-Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two rotations), while the AWSoM model shows the opposite trend.
-{For comparison, note the behavior of $B_r$ in the CHs, increasing from the open/closed boundary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}
+\edit{Lastly, the DEMT} electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two rotations), while the AWSoM model shows the opposite trend.
+{For comparison,\edit{$B_r$ in the CHs increases} from the open/closed boundary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}
 
@@
 Open legs are indicated in gray color and closed ones in black color.
-For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit} and \ref{Tfit}.
+For each leg, the fits to tomographic temperature and density were applied, as given by Equations \ref{Nfit} and \ref{Tfit}.
 Considering the AWSoM data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_awsom} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
 Using a three-color code, type I, II and III legs are shown in red, magenta and cyan color, respectively.
-This figure is to be compared with the corresponding Figure \ref{rpoint_demt} for DEMT results.
-It is readily seen that the AWSoM maps are more populated than those of DEMT.
-This is due to the 3D MHD model having electron density and temperature fields spatially smoother than those of DEMT.}
+This figure \edit{can be compaed} with the corresponding Figure \ref{rpoint_demt} for DEMT results.
+\edit{The AWSoM maps are more densely populated} than those of DEMT.
+This is due to the 3D MHD model having \edit{having spatially smoother distributions of electron density and temperature than those of DEMT}.}
 
@@
 The DEMT results are expressed as absolute values, while the ASWSoM results are informed as a percentual variation relative to the corresponding result for DEMT.
-The following major results can be drawn.}
+\del{The following major results can be drawn.}}
 
@@
 
-Concerning the DEMT reconstructions, Figure \ref{rpoint_demt} shows that, for both rotations, magnetic field lines of type 0, I and II are associated with increasingly outer {layers} of the equatorial streamer belt.
-Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} show in 3D quantitative detail how these progressively outer magnetic structures exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature.
+\del{Concerning the DEMT reconstructions, Figure \ref{rpoint_demt} shows that, for both rotations,} \edit{Magnetic} field lines of type 0, I and II are associated with increasingly outer {layers} of the equatorial streamer belt.
+\del{Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} show in 3D quantitative detail how} \edit{These progressively} outer magnetic structures exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature.
 For both rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes.
@@
 Our results for target CR-2082 compare very well with those of \citet{nuevo_2015} and \citet{lloveras_2017} for target CR-2081.
-As our study uses the improved version of the DEMT technique, such comparison provided a consistency check for the changes implemented in the DEMT technique.
+As our study uses the improved version of the DEMT technique, such comparison provided a consistency \edit{check.} \del{for the changes implemented in the DEMT technique.}
 
@@
 In the case of the {DEMT reconstruction based on AIA data we show that, in} a substantial fraction of the {voxels of the CHs,} the technique performs poorly in modeling {an LDEM that predicts} the tomographic emissivity in each EUV band with reasonable accuracy.
-As a result, DEMT results based on AIA data {are less reliable CHs}.
+As a result, DEMT results based on AIA data {are less reliable \edit{for} CHs}.
 This was already found by the existing two previous DEMT works based on AIA data \citep{nuevo_2015,maccormack_2017}.
 The source of this distinct performance of DEMT when applied to EUVI or AIA data is related to the TRFs of the respective filter sets.
-We are currently implementing an improved LDEM determination algorithm to to deal with this issue that will be used in a follow up article.}
+We are currently implementing an improved LDEM determination algorithm to deal with this issue that will be used in a follow up article.}
 
@@
 Note also that the simulation of CR-2082 used GONG maps as boundary condition, while the simulation of CR-2208 used the improved ADAPT-GONG maps.
-This is likely the cause that the results of the AWSoM model show a more accurate match to the DEMT reconstructions in the case of CR-2208.}
+This is likely the cause \edit{of a more accurate match} to the DEMT reconstructions in the case of CR-2208.}
 
-Within the {quantitative match between both {models summarized} in the previous paragraph, there are some qualitative agreements and {disagreements worth noticing}.
-For both rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
+\del{Within the {quantitative match between both {models summarized} in the previous paragraph, there are some qualitative agreements and {disagreements worth noticing}.
+}For both rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
 On the other hand, while the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density {(physically expected in transitioning from magnetically closed to open regions)}, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
 Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two rotations), {as expected in transitioning from the source region of the slow to the fast component of the solar wind}, the AWSoM model shows the opposite trend.
-This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.} {These unphysical characteristics of the results of the AWSoM model in the rage of low heights analysed here ($r\lesssim 1.2\,\mrsun$), may be attributed to the less reliable values of $B_r$ provided by both the GONG and ADAPT-GONG maps at subpolar latitudes.
-This will be further investigated in a follow up article focusing on the current deep minimum epoch, during which the large-scale corona shows the simplest possible structure.}
+This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.} {These unphysical characteristics of the results of the AWSoM model in the \edit{range} of low heights analysed here ($r\lesssim 1.2\,\mrsun$), may be attributed to the less reliable values of $B_r$ provided by both the GONG and ADAPT-GONG maps at subpolar latitudes.
+This will \edit{be investigated} in a follow up article focusing on the current deep minimum epoch, during which the large-scale corona shows the simplest possible structure.}
 

### 2020-03-06 lloveras_2020_v2.tex
nuevos ajustes del referi

@@
 \noindent 
-{where $L$ is the length of the loop, and $B_0$ and $B_L$ are the values of the magnetic field at the footpoint locations of the loop in the coronal base, namely $s=0$ and $s=L$.} {Note that, for any given field line, all quantities in these two expressions can be computed {from the DEMT results traced along field lines, and the AWSoM magnetic field model,} through Equations \ref{Fc}-\ref{Er}.
+{where $L$ is the length of the loop, and $B_0$ and $B_L$ are the values of the magnetic field at the footpoint locations of the loop in the coronal base, namely $s=0$ and $s=L$.} {\edit{For} any given field line, all quantities in these two expressions can be computed {from the DEMT results traced along field lines, and the AWSoM magnetic field model,} through Equations \ref{Fc}-\ref{Er}.
 Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to maintain a stable coronal structure.}
@@
 
-{To characterize the DEMT results in different magnetic structures, we traced} $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.
+\del{To characterize the DEMT results in different magnetic structures, we traced $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.
 For both rotations, all legs that meet the criteria listed in Section \ref{trace} were selected.
 For each leg, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.
-{As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}
+{As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}}
 
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_full_conajuste_doble_errorhighpoints.eps}
-\caption{\emph{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR-2082 (left) and CR-2208 (right).
-\emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-{The location of} type 0, I, II and III legs {is shown} in blue, red, {magenta and cyan} color, respectively.}}
+\caption{{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR-2082 (left) and CR-2208 (right).
+{Mid panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
+{The location of} type 0, I, II and III legs {is shown} in blue, \edit{orange, red and cyan} color, respectively.}\edit{Bottom panels: histograms of the latitudinal distribution at $r=1.105\,\mrsun$ of the selected legs.}}
 \label{rpoint_demt}
@@
 Open legs are indicated in gray color and closed ones in black color.
-For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit}-\ref{Tfit}.
-Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
+\del{For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit}-\ref{Tfit}.} Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
 Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the {$\approx 44000$} legs selected for CR-2082, 20\% are type 0, 31\% are type I, 23\% are type II and 26\% type III.
-On the other hand, of the {$\approx 44000$} legs selected for CR-2208, 10\% are type 0, 43\% are type I, 30\% are type II and 17\% type III.
+On the other hand, of the \edit{$\approx 50000$} legs selected for CR-2208, 10\% are type 0, \edit{38}\% are type I, \edit{27}\% are type II and \edit{25}\% type III.
 
@@
 
-Figure \ref{gradt_demt} shows frequency histograms {of $\dr\Tm$} for legs of type 0, I, II and III.
+Figure \ref{gradt_demt} shows frequency histograms of $\dr\Tm$ for legs of type 0, I, II and III.
 The lack of population around values close to zero is due to the requirement $|\rhoTr| > 0.5$ which discards quasi-isothermal legs.
-For both rotations, {the median value of the temperature radial gradient is ${\rm Md}\left(\dr\Tm\right) \approx -2.5$, $+2.3$ and $+2.4\,\MK/\mrsun$} for legs of type 0, I and II, respectively.
-
+For both rotations, the median value of the temperature radial gradient is \edit{${\rm Md}\left(\dr\Tm\right) \approx -2.2$, $+2.3$, $+2.4$ and $+2.3\,\MK/\mrsun$ for legs of type 0, I, II and III, respectively.}
+\del{
 {The notable difference between both rotations is the characteristic {value ${\rm Md}\left(\dr\Tm\right)\approx +4.5\,\MK/\mrsun$} for legs of type III for CR-2208.
 This is related to the relatively larger values of the score $R$ for the CH of CR-2208, making the DEMT results based on AIA data less reliable in the CHs.
-We will return to this point in the \edit{Conclusions}.}
+We will return to this point in the {Conclusions}.}
+}
 
@@
 From top to bottom {results are shown for} type 0 to type III {legs}{, respectively}.
-From left to right the panels show the statistical distribution of the electron density value $\NCB \equiv \sqravgN(r=1.055)$ {(at the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.
+From left to right the panels show the statistical distribution of the electron density value $\NCB \equiv \sqravgN(r=1.055)$ \del{(at the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.
 
@@
 {{Adding the} radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}.
-Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$.
+\edit{For} type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$.
 As shown by \citet{maccormack_2017}, this affects only the smallest sized loops of the type 0, and it is likely due \edit{to emission out of the instrumental sensitivity range}.
@@
 
-{{Several details from Figure \ref{perf_lat} are \edit{worth highlighted}.
+{Several details from Figure \ref{perf_lat} are \edit{worth highlighted}.
 Firstly, at most latitudes the overall agreement of the electron density of both models is within $\approx 20\%$ for CR-2082, and $\approx 5\%$ for CR-2208.
 The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.
-In the case of the electron temperature, for both rotations the models agree within $\approx 15\%$ at all latitudes of the streamer belt, showing larger discrepancies in the CHs.} Secondly, for both rotations, and for both models, these plots clearly show the relatively lower temperatures characterizing the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
+In the case of the electron temperature, for both rotations the models agree within $\approx 15\%$ at all latitudes \del{of the streamer belt, showing larger discrepancies in the CHs}.
+Secondly, for both rotations, and for both models, these plots clearly show the relatively lower temperatures characterizing the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
 Thirdly, for both rotations, the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density.
@@
 \includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_conajuste.eps}
-\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of {type I (red), II (magenta), and III (cyan)}, for CR-2082 (top panels) and CR-2208 (bottom panels).
+\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of {type I (\edit{orange}), II (\edit{red}), and III (cyan)}, for CR-2082 (top panels) and CR-2208 (bottom panels).
 Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
@@
 \section{{Discussion and Conclusions}}\label{discu} 
-
+\del{
 We carried out the 3D DEMT reconstruction and MHD modeling of the inner solar corona for two target rotations, CR-2082 and CR-2208.
@@
 The MHD model used is here the latest version of the AWSoM component of the SWMF suite  (Section \ref{awsom}).
-
-{Based on the magnetic field of AWSoM model and the results of the DEMT model for electron density and temperature, we classified coronal structures in four different types.
+Based on the magnetic field of AWSoM model and the results of the DEMT model for electron density and temperature, we classified coronal structures in four different types.
 {Small loop legs} in the core of the streamer belt are classified in down/up types according to their temperature decreasing/increasing with height (dubbed type 0/I).
@@
 For both rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes.
-Also, in the case of CR-2082 the fraction of down legs is significantly larger than for CR-2208.
+\del{DIEGO: esto no es cierto, es nuestra definicion y no un resultado.} Also, in the case of CR-2082 the fraction of down legs is significantly larger than for CR-2208.
 These findings are consistent with previous studies by \citet{huang_2012} and \citet{nuevo_2013}.
@@
 
-{In the streamer belt region we combined the DEMT results and the AWSoM magnetic model to infer the energy input flux $\phi_h$ at the coronal base required to maintain stable coronal loops.
-We found characteristic values in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}.
+{\del{In the streamer belt region we combined the DEMT results and the AWSoM magnetic model to infer the energy input flux $\phi_h$ at the coronal base required to maintain stable coronal loops.
+We found characteristic values in the range \\}
+\edit{The energy input flux $\phi_h$ at the coronal base, required to maintain stable coronal loops, is in the range} $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}.
 Based on spectroscopic data of the EIS instrument in quiet-Sun regions \citet{hahn_2014} showed that, if the observed non-thermal broadening are assigned to Alfvén waves, their energy flux at the coronal base is estimated to be in the range $\approx 1.5-2.5\times 10^5\,\erg\,\cminvs\,\s^{-1}$.
@@
 
-Results of the AWSoM model {were compared} to those of the DEMT reconstructions {in the range of coronal heights simultaneously covered by both models, namely $\approx 1.05-1.20\,\mrsun$.} In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines.
-The detailed comparison shown in this work can be summarized as follows.
+\del{
+Results of the AWSoM model {were compared} to those of the DEMT reconstructions {in the range of coronal heights simultaneously covered by both models, namely $\approx 1.05-1.20\,\mrsun$.} In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines.} The detailed comparison shown in this work can be summarized as follows.
 For CR-2082, the electron density of both models agree within $\approx 20\%$ {in most regions}, while for CR-2208 the agreement is within $\approx 5\%$.
-{The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both rotations{, with larger discrepancies in the CHs.} This level of agreement between both models {(within or slightly beyond the uncertainty level of DEMT results)} is considerably better than that reported in previous works.
+{The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both rotations\del{, with larger discrepancies in the CHs.} This level of agreement between both models {(within or slightly beyond the uncertainty level of DEMT results)} is considerably better than that reported in previous works.
 \citet{jin_2012} and \citet{oran_2015}{, who used previous versions of the AWSoM model,} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.}
@@
 {The overall better match of the results of the current version of the AWSoM model compared to DEMT reconstructions is partly due to the improved energy partitioning scheme of the model, described in Section \ref{awsom}.
-Note also that the simulation of CR-2082 used GONG maps as boundary condition, while the simulation of CR-2208 used the improved ADAPT-GONG maps.
+\edit{The} simulation of CR-2082 used GONG maps as boundary condition, while the simulation of CR-2208 used the improved ADAPT-GONG maps.
 This is likely the cause \edit{of a more accurate match} to the DEMT reconstructions in the case of CR-2208.}
 
-\del{Within the {quantitative match between both {models summarized} in the previous paragraph, there are some qualitative agreements and {disagreements worth noticing}.
+\del{Within the quantitative match between both models summarized in the previous paragraph, there are some qualitative agreements and {disagreements worth noticing}.
 }For both rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
@@
 Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two rotations), {as expected in transitioning from the source region of the slow to the fast component of the solar wind}, the AWSoM model shows the opposite trend.
-This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.} {These unphysical characteristics of the results of the AWSoM model in the \edit{range} of low heights analysed here ($r\lesssim 1.2\,\mrsun$), may be attributed to the less reliable values of $B_r$ provided by both the GONG and ADAPT-GONG maps at subpolar latitudes.
-This will \edit{be investigated} in a follow up article focusing on the current deep minimum epoch, during which the large-scale corona shows the simplest possible structure.}
+This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.
+These unphysical characteristics of the results of the AWSoM model in the \edit{range} of low heights analysed here ($r\lesssim 1.2\,\mrsun$), may be attributed to the less reliable values of $B_r$ provided by both the GONG and ADAPT-GONG maps at subpolar latitudes.
+This will \edit{be investigated} in a follow up article focusing on the current deep minimum epoch, during which the large-scale corona shows the simplest possible structure.
 

### 2020-03-08 response_to_review_SOLA-D-20-00015_v1.txt
retoques del referi

@@
 
-We fully  agree. We improved the use of space in Figures 1 through 3. We also changed colors in the latter (see also query #2 below).
+We agree. We improved the use of space in Figures 1,2,8 and 9.
 
@@
 
-We fully agree.
+We agree.
 Actually this affects all following Figures #: 3, 4, 11, and 14.
@@
 Y UNA RESPUESTA ACORDE.
+
+That's right, we used it as a criterion of selection aiming to distinguish different layers. we changed the text avoiding confusion
 
@@
 
+The populations shown in the histograms are about types of legs associated with different latitudinal regions.
+The selection of these legs is not the same for AWSoM and DEMT.
+This is why calculating the MAD a on the relationship of the populations of the histograms reported is not simple.
+In the future we plan to make a comparative analysis leg-to-leg between AWSoM and DEMT and in that case we will undoubtedly report some statistics associated with the standard deviation such as being the MAD.
+
 -----------------------------------------------------------------------------------------
@@
 EXPLICAR COMO SE SOLUCIONÓ Y REMOVER TODO LO NO NECESARIO EN EL PAPER (AZUL) Y AGREGAR COSAS NUEVAS (ROJO).
+
+The problem in the magnetically open AIA region was actually because the minimization in the voxels used to converge to a local minimum.
+This was resolved by modifying the starting values of the minimization.
+Now the voxels takes correct values of density and temperature.
+This affects the figures that report type III legs for CR2208.
+Therefore, figures 4, 5, 10, 13 and 14 were modified.
+Now the temperature gradients are correct and the temperature profile reported in Figure 10 is improved.
 

### 2020-03-08 lloveras_2020_v2.tex
retoques del referi

@@
 
-{For both rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
+For both rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
 Open legs are indicated in gray color and closed ones in black color.
-\del{For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit}-\ref{Tfit}.} Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the {$\approx 44000$} legs selected for CR-2082, 20\% are type 0, 31\% are type I, 23\% are type II and 26\% type III.
+\del{For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit}-\ref{Tfit}.} Considering the DEMT data points and the resulting fits along each leg, the \edit{mid} panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
+Using a four-color code, type 0, I, II and III legs are shown in blue, \edit{orange, red and cyan} color, respectively.
+\edit{The bottom panels of same figure shows histograms of the latitudinal distribution of the legs using same color code.} Of the {$\approx 44000$} legs selected for CR-2082, 20\% are type 0, 31\% are type I, 23\% are type II and 26\% type III.
 On the other hand, of the \edit{$\approx 50000$} legs selected for CR-2208, 10\% are type 0, \edit{38}\% are type I, \edit{27}\% are type II and \edit{25}\% type III.
@@
 \edit{Lastly, the DEMT} electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two rotations), while the AWSoM model shows the opposite trend.
-{For comparison,\edit{$B_r$ in the CHs increases} from the open/closed boundary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}
+{For comparison, \edit{$B_r$ in the CHs increases} from the open/closed boundary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}
 
@@
 
-\del{Concerning the DEMT reconstructions, Figure \ref{rpoint_demt} shows that, for both rotations,} \edit{Magnetic} field lines of type 0, I and II are associated with increasingly outer {layers} of the equatorial streamer belt.
+\del{Concerning the DEMT reconstructions, Figure \ref{rpoint_demt} shows that, for both rotations,} \edit{Magnetic} field lines of type 0, I and II \edit{were selected to be associated} with increasingly outer {layers} of the equatorial streamer belt.
 \del{Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} show in 3D quantitative detail how} \edit{These progressively} outer magnetic structures exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature.
 For both rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes.
-\del{DIEGO: esto no es cierto, es nuestra definicion y no un resultado.} Also, in the case of CR-2082 the fraction of down legs is significantly larger than for CR-2208.
+Also, in the case of CR-2082 the fraction of down legs is significantly larger than for CR-2208.
 These findings are consistent with previous studies by \citet{huang_2012} and \citet{nuevo_2013}.

### 2020-03-10 response_to_review_SOLA-D-20-00015_v1.txt
Albert está trabajando en esto, no tocar todavía, gracias.

--- 2020-03-05 response_to_review_SOLA-D-20-00015_v1.txt
@@
 
-Thank you very much for your email with the report on the first version of our manuscript SOLA-D-20-00015, titled "Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling".
+Thank you very much for your email with the report on the first version of our manuscript ID SOLA-D-20-00015, titled "Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling".
 
-We deeply acknowledge the reviewer, whose report reflects her/his very careful and interested read, containing a series of relevant, useful, and constructive criticisms and suggestions.
+We deeply acknowledge the reviewer, whose report reflects her/his very careful and interested read.
+We found all queries very relevant, with useful and constructive criticisms and suggestions.
+We believe we addressed all points, as a result of which we believe the manuscript has gained in both content and clarity.
 
-Below, we paste the full review. Following each query we include a response, highlighting the changes in the manuscript, where all edited/new text is marked in RED COLOR fonts.
+Below, we copy/paste all queries (Q) of the review.
+Following each query we include an answer (A), commenting the changes in the manuscript, in which all edited/new text is highlighted in red color font.
 
@@
 
-------------------------------begin of response------------------------------------------
+------------------------------beginning of review and response---------------------------
 COMMENTS FOR THE AUTHOR:
@@
 -----------------------------------------------------------------------------------------
-1.
+Q1.
 All of the multi-panel figures that show longitude-latitude maps (e.g.
@@
 
-We fully  agree. We improved the use of space in Figures 1 through 3. We also changed colors in the latter (see also query #2 below).
+A1. We agree. We improved the use of space in the long-lat maps in Figures 1, 2, 8 and 9, while the one in Figure 3 remains the same (we believe those are fine).
 
 -----------------------------------------------------------------------------------------
-2. Figure 3 and 11, bottom panels. I find it difficult to distinguish between the red and magenta colours. Can you replace magenta with a different colour, maybe green?
+Q2. Figure 3 and 11, bottom panels. I find it difficult to distinguish between the red and magenta colours. Can you replace magenta with a different colour, maybe green?
 
-We fully agree.
-Actually this affects all following Figures #: 3, 4, 11, and 14.
+A2.
+We agree.
+Actually this affects all following Figures: 3, 4, 11, and 14.
 In those, we applied the following changes: Red->Orange and Magenta->Red.
@@
 -----------------------------------------------------------------------------------------
-3.
+Q3.
 Page 14, paragraph starting at line 34.
@@
 
-Thanks for pointing this out....
-ESTO REQUIERE CAMBIOS EN EL PAPER JUSTIFICANDO CON CLARIDAD LA ELECCION DE LOS LIMITES LATITUDINALES Y LA SELECCION DE SOLO UP EN TYPE II Y III.
-Y UNA RESPUESTA ACORDE.
+A3.
+Several aspects are involved here, the discussion in the paragraph you indicate heavily depends on that in the final paragraph of Section 2.3.
+Both were confusing as they were, specially the latter, so we edited both.
+Actually, we do not say that *small* legs populate the equatorial latitudes and *large* ones the mid latitudes.
+We say that if one classifies the *small-closed* loops in DOWN and UP, the former peak near the equator and the latter peak near mid latitudes (at least for the deep minimum rotation CR-2082).
+The classification of legs in four classes in Section 2.3 includes limits for the latitude of their footpoints, to distinguish different layers of the streamer belt (legs of type 0, I and II), as well as to separate field lines of the high latitude CHs (legs of type III).
+We included two new panels in Figure 3, showing frequency histograms of the latitude of the four types of legs at 1.105 Rsun.
+Within the range Abs(latitude) < 50 deg, and for the solar minimum target CR-2082, down-legs are peaked near the equator while up-legs peak at mid-latitudes.
+This is less obvious for CR-2208, although it is clear that down-legs peak in the core of the streamer belt.
+Now, it turns out that down-legs are scarce for Abs(latitude) > 50 deg.
+Should have we not included the limit of Abs(latitude) < 50 deg for closed-small down and up legs (i.e., legs of type 0 and I), their histograms would still peak at around the same latitudes.
+As our main objective here is to be able to analyze progressively outer layers of the streamer belt, we include these limits in the latitude of the footpoints.
+We edited in full the final paragraph of Section 2.3, as well as parts of the paragraph of Section 3.1 you point out.
+We trust the new graphs and discussions are clear now.
+Let us know.
 
 -----------------------------------------------------------------------------------------
-4.
+Q4.
 Table 2 summarises the differences of the median values of the DEMT and MHD model.
@@
 
-REFERENCIA: https://en.wikipedia.org/wiki/Median_absolute_deviation
-
-DIEGO, PROPONEMOS HACER ESTO CON FEDE.
-
-DEFINAMOS EL CAMPO ESCALAR Xi = (X_MHD - X_tom) / X_tom, DONDE "X" ES CUALQUIER RESULTADO A LO LARGO DE LOOP (Ncb, LAMDA_n, ó <Tm>).
-LA TABLA 2 INFORMA LOS VALORES: "[Med(X_MHD) - Med(X_tom)]/Med(X_tom)".
-
-PROPONEMOS DEJAR LOS HISTOGRAMAS DE LAS FIGS 12 Y 13 COMO ESTÁN, PERO EXPANDIR LA TABLA 2 A QUE INCLUYA DOS COLUMNAS MÁS INDICANDO ESTOS DOS INDICADORES DE CADA CAMPO "Xi":
-* Med(Xi)  (debería aproximarse a los porcentuales y signos entre paréntesis que actualmente informa la Tabla 2).
-* MAD = Med(Abs(Xi-Med(Xi))).
-
-LUEGO EDITAMOS TABLA Y TEXTO DEL PAPER.
+A4.
+The populations shown in the histograms are about types of legs associated with different latitudinal regions.
+The selection of these legs is not the same for AWSoM and DEMT.
+This is why calculating the MAD a on the relationship of the populations of the histograms reported is not simple.
+In the future we plan to make a comparative analysis leg-to-leg between AWSoM and DEMT and in that case we will undoubtedly report some statistics associated with the standard deviation such as being the MAD.
 
 -----------------------------------------------------------------------------------------
-5. You discuss the less reliable results from AIA in coronal holes. The very recent paper by Saqri et al (Solar Physics 295, 2020) is relevant here, and should be referenced.
+Q5. You discuss the less reliable results from AIA in coronal holes. The very recent paper by Saqri et al (Solar Physics 295, 2020) is relevant here, and should be referenced.
 
-ESTO FUE SOLUCIONADO.
-EL ORIGEN DEL PROBLEMA NO RADICA EN STRAY-LIGHT DECON.
-EL EFECTO DE ESTO EN TOM, APLICADO A DATOS EUVI, FUE EXPLORADO EN LLOVERAS ET AL.
-(2017).
-CIERTAMENTE NOS INTERESA INCORPORAR ESTO AL PIPELINE DE AIA SI LA PFS ESTÁ BIEN CARACTERIZADA, PERO ES UN TEMA QUE DEBEMOS INVESTIGAR.
-EXPLICAR COMO SE SOLUCIONÓ Y REMOVER TODO LO NO NECESARIO EN EL PAPER (AZUL) Y AGREGAR COSAS NUEVAS (ROJO).
+A5.
+Thanks for the refernce, certainly relevant and now mentioned in the paper (see below).
+As mentioned in the discussion section of v1: "The source of this distinct performance of DEMT when applied to EUVI or AIA data is related to the TRFs of the respective filter sets.
+We are currently implementing an improved LDEM determination algorithm to deal with this issue that will be used in a follow up article." We have successfully implemented the improved version of the code, as a result of which this problem has been solved.
+The issue was related to the algorithm that solves the optimization problem posed in each voxel to find the LDEM.
+When based on AIA data, the previous algorithm tended to converge to a non-optimal (local minimum of the objective function) in specific voxels located in the CHs.
+We addressed the problem by exploring multiple starting points when solving the optimization problem in cases where the initial solution was not good enough.
+In this draft, this improved algorithm affects results concerning type III legs for CR2208.
+As a result, the following Figures have been updated: 2, 3, 4, 5, 10, 13 and 14.
+You will notice all these Figures are just like the original ones, except the problem in the CHs of CR-2208 has been solved.
+Text throughout the manuscript was edited accordingly, in the following locations of v2 of the draft:
+ - Second paragraph after Figure 2.
+ - Paragraph following Figure 4.
+ - Numerical values concerning legs of type-III for CR-2208 in Tables 1 and 2.
+ - Most of the third paragraph of the Conclusion section in V1 was devoted to this solved issue, so it was eliminated.
+The remaining text is now the end of the second paragraph of that section (highlighted in red color).
 
 -----------------------------------------------------------------------------------------
-6.
+Q6.
 The abstract can be shortened somewhat, reducing the number of introductory sentences and with a little less emphasis on the method and future improvements, and more on the science results.
@@
 
-(TOTALMENTE, HAGAMOS ESTO LUEGO DE EDITAR TODO).
+A6. (TOTALMENTE, HAGAMOS ESTO LUEGO DE EDITAR TODO).
 
 -----------------------------------------------------------------------------------------
-7.
+Q7.
 Page 5, paragraph beginning line 34.
@@
 
+A7.
 Thanks for this comment and the references.
@@
 -----------------------------------------------------------------------------------------
-8.
+Q8.
 The introduction does not have many references to works beyond DEMT and AWSoM.
@@
 
+A8.
 ALBERT VA A ESCRIBIR UN POCO DE TEXTO.
@@
 LO QUE SIGUE DEBE SER TODO HECHO POR DIEGO, CONSULTANDO PRINCIPALMENTE A ALBERT. TODO CAMBIO DEBERÁ ESTAR DESTACADO CON \EDIT{} EN ROJO.
+
 -----------------------------------------------------------------------------------------
-9. Some sections can benefit from weeding out of repetitions. You tend to repeat statements regarding the method a lot. For example:
+Q9. Some sections can benefit from weeding out of repetitions. You tend to repeat statements regarding the method a lot. For example:
 - Paragraph starting page 13, line 41. This has already been said in the method.
@@
 
+A9. Thanks for pointing this out. We have improved the text in the following parts:
+
 -----------------------------------------------------------------------------------------
-Minor grammatical improvements, typos, and removal of redundant statements
+Q10. Minor grammatical improvements, typos, and removal of redundant statements
+
+A10. Thanks very much for this detailed corrections. We have addressed them all.
+
 Page number, line number: 

### 2020-03-10 lloveras_2020_v2.tex
Albert está trabajando en esto, no tocar todavía, gracias.

@@
 \def\del#1{\textcolor{Blue}{#1}}
+\def\comment#1{\textcolor{Blue}{#1}}
 
@@
 
-{Legs of type down turn out to have a significant population only for closed-small loops.
-In the case of closed-large loops and open field lines, there are very few cases of type down.
-Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population in each case}.
-In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic structures are statistically analysed.
-{As shown in Section \ref{demt_res}, classification of legs from type \edit{type 0 to II allows a study of the streamer belt in three distinct layers at increasing height.}}
+\edit{Legs of type down turn out to have a significant population only for closed-small field lines.
+Hence, we separate them into two complementary classes: legs of type 0 (down) and legs of type I (up).
+In the case of closed-large field lines, legs of type down are $\lesssim 15\%$ of the population.
+In the case of open field lines, legs of type down are $\lesssim 10\%$ of the population.
+Hence, the requirement of being up for legs of type II and III is included to select the vastly dominating population in each case.
+On the other hand, the inclusion of latitude limits for the footpoints in the classification of legs from type 0 through III is purposely set to study the streamer belt in three distinct, progressively outer layers, as well as to separate the field lines of the high latitude CHs (legs of type III).
+In Section \ref{resu}, the results of both the DEMT and AWSoM models in the four classes of legs are statistically analysed.}
 
@@
 Top, middle and bottom panels show the results at three heliocentric heights, $1.025$, $1.065$ and $1.105\,\mrsun$ respectively.
-Black voxels correspond to non-reconstructed regions (see text in Section \ref{demt_res}) and thick-black curves indicate the open/closed boundaries.}
+Black voxels correspond to non-reconstructed regions (see text in Section \ref{demt_res}) and thick-black curves indicate the open/closed boundaries.
+\comment{Por consistencia, creo que en los títulos de los CarrMaps de las Figuras 1 y 2 deberías usar la notación $\sqravgN$ y $\Tm$.
+Si esto lo hacés en LETITBE con el IDL 8.4, podrás usar los comandos de LaTeX dentro de las strings ``title", con lo cual no solo será simple sino que $\sqravgN$ no va a ocupar mucho más espacio y las chances son que salga todo lindo sin cambiar el tamaño de letra ni nada.}}
 \label{carmaps_demt_2082}
@@
 
-Latitude-longitude maps of the score $R$ defined by Equation \ref{R} show that \edit{the agreement between the tomographic} and synthetic FBEs is $\lesssim 1\%$.
+Latitude-longitude maps of the score $R$ defined by Equation \ref{R} show that \edit{the agreement between the tomographic and synthetic FBEs meets $R \lesssim 0.01$ in more than 90\% of the voxels where tomographic reconstruction is possible (i.e.
+where FBEs are non zero), and meets $R \lesssim 0.10$ in the rest.
+This implies that the LDEM found in each voxel accurately predicts the reconstructed FBEs.} \comment{Diego, evaluá que el valor que incluí es correcto.
+Simplemente fijate en que fracción de los voxels SIN ZDAs $R<0.01$ para CR-2208, yo estimo $90\%$.
+pra 2082 no hace falta.
+Comentame antes de enviar.}
+
+.
 The notable exception is to be found only in the CHs of the rotation {analysed} based on AIA data.
@@
 \caption{{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR-2082 (left) and CR-2208 (right).
-{Mid panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-{The location of} type 0, I, II and III legs {is shown} in blue, \edit{orange, red and cyan} color, respectively.}\edit{Bottom panels: histograms of the latitudinal distribution at $r=1.105\,\mrsun$ of the selected legs.}}
+\edit{Middle panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
+{The location of} type 0, I, II and III legs {is shown} in blue, \edit{orange, red, and cyan} color, respectively.} \edit{Bottom panels: frequency histograms of the latitude of the four types of legs of the middle panel.}}
 \label{rpoint_demt}
@@
 Open legs are indicated in gray color and closed ones in black color.
-\del{For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit}-\ref{Tfit}.} Considering the DEMT data points and the resulting fits along each leg, the \edit{mid} panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs are shown in blue, \edit{orange, red and cyan} color, respectively.
-\edit{The bottom panels of same figure shows histograms of the latitudinal distribution of the legs using same color code.} Of the {$\approx 44000$} legs selected for CR-2082, 20\% are type 0, 31\% are type I, 23\% are type II and 26\% type III.
+\del{For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit}-\ref{Tfit}.} Considering the DEMT data points and the resulting fits along each leg, the \edit{middle} panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
+Using a four-color code, type 0, I, II and III legs are shown in blue, \edit{orange, red, and cyan} color, respectively.
+\edit{The bottom panels show histograms of the latitude distribution of the legs of the middle panel, using the same color code.} Of the {$\approx 44000$} legs selected for CR-2082, 20\% are type 0, 31\% are type I, 23\% are type II and 26\% type III.
 On the other hand, of the \edit{$\approx 50000$} legs selected for CR-2208, 10\% are type 0, \edit{38}\% are type I, \edit{27}\% are type II and \edit{25}\% type III.
 
-{Type 0 (small down) legs mainly populate the equatorial latitudes.
-This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the solar minimum between {SCs 23 and 24} by \citet{nuevo_2013}.
+\edit{For both rotations, the population of type 0 (small-closed-down) legs population peaks in the core of the streamer belt, around the equator in the case of CR-2082, and towards the southern hemisphere in the case of CR-2208.} This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the solar minimum between {SCs 23 and 24} by \citet{nuevo_2013}.
 Later on, \citet{lloveras_2017} showed {that} equatorial down loops in streamers were also to be found in the deep minimum between SCs {23 and 24}.
@@
 The relatively smaller population of down legs seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}.
-Type I (small up) mainly populate the mid-latitudes, while type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt.
-Finally, type III (open) legs populate the CHs.}
+\edit{Type I (small-closed-up) legs are present at all latitudes in the streamer belt.
+Their population peaks in the mid-latitudes of both hemispheres for CR-2082, and in the mid-latitudes of the northern hemisphere for CR-2208.
+Type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt (the requirement of footpoints located beyond mid-latitudes was included precisely to select this kind of loop).
+Finally, type III (open) legs populate the high latitude CHs.}
 
@@
 The lack of population around values close to zero is due to the requirement $|\rhoTr| > 0.5$ which discards quasi-isothermal legs.
-For both rotations, the median value of the temperature radial gradient is \edit{${\rm Md}\left(\dr\Tm\right) \approx -2.2$, $+2.3$, $+2.4$ and $+2.3\,\MK/\mrsun$ for legs of type 0, I, II and III, respectively.}
-\del{
-{The notable difference between both rotations is the characteristic {value ${\rm Md}\left(\dr\Tm\right)\approx +4.5\,\MK/\mrsun$} for legs of type III for CR-2208.
-This is related to the relatively larger values of the score $R$ for the CH of CR-2208, making the DEMT results based on AIA data less reliable in the CHs.
-We will return to this point in the {Conclusions}.}
-}
+For both rotations, the median value of the temperature radial gradient is \edit{${\rm Md}\left(\dr\Tm\right) \approx -2.2$, $+2.3$, $+2.4$ and $+2.3\,\MK/\mrsun$, for legs of type 0, I, II and III, respectively.}
 
@@
 Our results for target CR-2082 compare very well with those of \citet{nuevo_2015} and \citet{lloveras_2017} for target CR-2081.
-As our study uses the improved version of the DEMT technique, such comparison provided a consistency \edit{check.} \del{for the changes implemented in the DEMT technique.}
-
-{{For both rotations}, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.
-In the case of the {DEMT reconstruction based on AIA data we show that, in} a substantial fraction of the {voxels of the CHs,} the technique performs poorly in modeling {an LDEM that predicts} the tomographic emissivity in each EUV band with reasonable accuracy.
-As a result, DEMT results based on AIA data {are less reliable \edit{for} CHs}.
-This was already found by the existing two previous DEMT works based on AIA data \citep{nuevo_2015,maccormack_2017}.
-The source of this distinct performance of DEMT when applied to EUVI or AIA data is related to the TRFs of the respective filter sets.
-We are currently implementing an improved LDEM determination algorithm to deal with this issue that will be used in a follow up article.}
+As our study uses the improved version of the DEMT technique, such comparison provided a consistency \edit{check.} \del{for the changes implemented in the DEMT technique.} \edit{For both rotations, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.}
 

### 2020-03-10 response_to_review_SOLA-D-20-00015_v1.txt
Albert está trabajando en esto, no tocar todavía, gracias.

@@
 We found all queries very relevant, with useful and constructive criticisms and suggestions.
-We believe we addressed all points, as a result of which we believe the manuscript has gained in both content and clarity.
+Below, we copy/paste the full review.
+Following each query (Q) we include a corresponding answer (A), commenting the changes in the manuscript, in which all edited/new text is highlighted in red color font.
 
-Below, we copy/paste all queries (Q) of the review.
-Following each query we include an answer (A), commenting the changes in the manuscript, in which all edited/new text is highlighted in red color font.
+We addressed all points, as a result of which we believe the manuscript improved in both content and clarity. In particular, a major improvement in this new version of the draft relates to Q5 below.
 
@@
 Medium concerns
+
 -----------------------------------------------------------------------------------------
@@
 A3.
-Several aspects are involved here, the discussion in the paragraph you indicate heavily depends on that in the final paragraph of Section 2.3.
-Both were confusing as they were, specially the latter, so we edited both.
+Several aspects are involved here, the discussion in the paragraph you indicate strongly relates on that in the final paragraph of Section 2.3.
+In reading them we find that these texts were confusing as they were, so we edited both.
 Actually, we do not say that *small* legs populate the equatorial latitudes and *large* ones the mid latitudes.
 We say that if one classifies the *small-closed* loops in DOWN and UP, the former peak near the equator and the latter peak near mid latitudes (at least for the deep minimum rotation CR-2082).
-The classification of legs in four classes in Section 2.3 includes limits for the latitude of their footpoints, to distinguish different layers of the streamer belt (legs of type 0, I and II), as well as to separate field lines of the high latitude CHs (legs of type III).
+The classification of legs in all four classes in Section 2.3 includes limits for the latitude of their footpoints, to distinguish different layers of the streamer belt (legs of type 0, I and II), as well as to separate field lines of the high latitude CHs (legs of type III).
 We included two new panels in Figure 3, showing frequency histograms of the latitude of the four types of legs at 1.105 Rsun.
@@
 This is less obvious for CR-2208, although it is clear that down-legs peak in the core of the streamer belt.
-Now, it turns out that down-legs are scarce for Abs(latitude) > 50 deg.
+If one analyses Abs(latitude) > 50 deg it turns out that small-down legs are scarce and there is an extra population of small-up legs (not nearly as much as in the peaks seen at mid lats.
 Should have we not included the limit of Abs(latitude) < 50 deg for closed-small down and up legs (i.e., legs of type 0 and I), their histograms would still peak at around the same latitudes.
+This can be seen in Figure 7 of Nuevo et al.
+92013), were they analyzed the small closed up and down loops for two rotations of solar minimum, without placing any limits in the latitude of the footpoints.
 As our main objective here is to be able to analyze progressively outer layers of the streamer belt, we include these limits in the latitude of the footpoints.
-We edited in full the final paragraph of Section 2.3, as well as parts of the paragraph of Section 3.1 you point out.
+We edited in full the final paragraph of Section 2.3, as well as the paragraph of Section 3.1 you point out (now split in two, shorter paragraphs).
 We trust the new graphs and discussions are clear now.
@@
 A4.
-The populations shown in the histograms are about types of legs associated with different latitudinal regions.
-The selection of these legs is not the same for AWSoM and DEMT.
-This is why calculating the MAD a on the relationship of the populations of the histograms reported is not simple.
-In the future we plan to make a comparative analysis leg-to-leg between AWSoM and DEMT and in that case we will undoubtedly report some statistics associated with the standard deviation such as being the MAD.
+First of all we note that, as a result of the discussion in Q5 below, a few numbers in Table 2 were updated (those corresponding to type-III legs for CR-2208).
+Now, when selecting field lines for analysis of both the DEMT and the AWSoM models, the classification of types of legs introduced in section 2.3 is used for each model separately.
+As a result, as shown by comparing the middle panels of Figure 3 and the bottom panels of Figure 11, and as discussed in the corresponding texts of the manuscript, the selection of field lines for DEMT is not the same.
+In comparing those Figures each color indicates comparable regions between the two analysis.
+It is so that Figures 12 and 13, and Table 2, which show DEMT-versus-AWSoM comparison for each rotation, are not done line-by-line but rather region-by-region (say: orange, red and cyan).
+The suggestion of calculating the MAD would require selecting the same field lines for both models, which is beyond the scope of the present comparative analysis.
+Informing the MAD is a good idea, being a precise measure of how the comparison between both models spreads.
+We will certainly implement such an analysis in a next effort.
+In the present draft, we trust the current comparison (Figures 12 and 13, and Table 2) provide are pretty informative summary of how both models compare.
+Let us know what you think.
 
@@
 A5.
-Thanks for the refernce, certainly relevant and now mentioned in the paper (see below).
-As mentioned in the discussion section of v1: "The source of this distinct performance of DEMT when applied to EUVI or AIA data is related to the TRFs of the respective filter sets.
+Thanks for the reference, which is certainly relevant and now mentioned in the paper, as discussed below.
+We are not sure stray light contamination was actually the reason of the reported issue, which is now solved.
+
+The discussion section of v1 of the draf include this sentence (now deleted): "The source of this distinct performance of DEMT when applied to EUVI or AIA data is related to the TRFs of the respective filter sets.
 We are currently implementing an improved LDEM determination algorithm to deal with this issue that will be used in a follow up article." We have successfully implemented the improved version of the code, as a result of which this problem has been solved.
@@
 Text throughout the manuscript was edited accordingly, in the following locations of v2 of the draft:
- - Second paragraph after Figure 2.
- - Paragraph following Figure 4.
+ - Red text in Pg 12 and Pg 13, and the red rext in Pg 15 informing characteristic values of Grad_r(Tm).
  - Numerical values concerning legs of type-III for CR-2208 in Tables 1 and 2.
- - Most of the third paragraph of the Conclusion section in V1 was devoted to this solved issue, so it was eliminated.
+ - Most of the third paragraph of the Conclusion section in V1 was devoted to this issue, so it was eliminated.
 The remaining text is now the end of the second paragraph of that section (highlighted in red color).
+
+Concerning the effect of stray-light contamination of EUV images on DEMT products, our current data processing pipeline for EUVI data includes the deconvolution of the PSF, carefully determined by Shearer et al.
+(ApJL, 2012).
+We have not yet included such a procedure for AIA data, as we were not aware of a reliable determination of their PSF.
+Shearer et al.
+(2012) showed that the signal in the core of CHs may be strongly affected by stray light.
+Now, the effect in tomography turns out to be milder, due to temporal and spatial binning of the images.
+In the case of EUVI data, Lloveras et al.
+(2017) performed a careful analysis of effect of stray-light removal in the resulting DEMT products.
+PSF deconvolution basically increases the contrast.
+As a result, the off-limb radial brightness in EUV images becomes somewhat steeper, which has an impact in tomographic reconstructions.
+Specifically, Lloveras et al.
+(2017) -see the end of their section 3.6- found that the coronal base density increases a bit (5-15%) and the density scale height decreases a bit (5-10%), while the electron temperature remains largely unchanged.
+We understand that stray light correction is less serious for AIA data.
+Again, it may be strong in specific pixels of AIA images and yet the final effect in tomographic products may be mild.
+Still, we do want to explore the effect in DEMT of stray light removal in AIA data.
+It will be in particular interesting to see if stray-light removal helps the algorithm that finds de LDEM in voxels of the CHs.
+We acknowledge the reference on AIA data, and will investigate this in the future.
+We included a comment on this topic, as well as the reference by Saqri et.al., at the beginning of Section 2.1 (red text).
 
@@
 
-A6. (TOTALMENTE, HAGAMOS ESTO LUEGO DE EDITAR TODO).
+A6. We agree. We edited the Abstract. Let us know what you think.
+
+-- FALTA ESTO --
 
@@
 I know this approach is covered in detail in Nuevo 2015, but I would like a little more detail here.
-You should mention that, in general, DEMs do not necessarily have a clean Gaussian profile and that more complicated inversions are needed (reference https://ui.adsabs.harvard.edu/abs/2012A%26A...539A.146H/abstract , https://ui.adsabs.harvard.edu/abs/2019SoPh..294..135M/abstract , https://ui.adsabs.harvard.edu/abs/2019SoPh..294..136P/abstract ).
+You should mention that, in general, DEMs do not necessarily have a clean Gaussian profile and that more complicated inversions are needed (reference https://ui.adsabs.harvard.edu/abs/2012A%26A...539A.146H/abstract , https://ui.adsabs.harvard.edu/abs/2019SoPh..294..135M/abstract , https://ui.adsabs.harvard.edu/abs/2019SoPh..294..136P/abstract).
 Then explain briefly why DEMT leads to cleaner, non-multithermal profiles (due to the 3D spatial reconstruction of the line of sight).
@@
 Thanks for this comment and the references.
-As the LDEM describes the temperature distribution of the plasma in a specific voxel it does not deal with different large scale structures, as it usually it may be the case for the DEM describing the plasma alog a full line-of.sight (LOS).
+We were aware of those, discussing the first one in Lloveras et.al.
+(2017).
+Concerning the other two, we are in fact interested in using the SITES code in the determination of the LDEM at each voxel, and make comparisons with those provide by our current parametric model code.
+As for the reason of LDEMs being "cleaner" than DEMs, you are right.
+As the LDEM describes the temperature distribution of the plasma in a specific voxel it does not deal with different large scale structures, as it may be the case for the DEM describing the plasma along a full line-of-sight (LOS).
 In that sense one can expect as you say, cleaner, profiles than those observed by DEM studies.
-Still, if one adds tbhe 335 A channel, which adds two sensitivity poits at ~ 1.0 MK and ~ 2.5 MK, one finds that a a bi-Gaussian LDEM model best predics all the tomographic emissivities.
+Even so, if one includes in the analysis data from the 335 A band, which adds two sensitivity points at ~ 1.0 MK and ~ 2.5 MK, one finds that a a bi-Gaussian LDEM model best predicts all the tomographic emissivities.
 That is the main conclusion of Nuevo et.
@@
 The interpretation in that case is that the unresolved independent strands threading the voxel can have two different characteristic temperatures.
-Nuevo et al.
-(2015).
-So in this sense, the plasma within the voxel can be multi-thermal.
+In this sense, the plasma within the voxel can be multi-thermal.
 As for efficiency, the parametric technique is comparably efficient independently of the chosen model.
-We did read the  We expanded this discussion in the text.
+We included a new paragraph (red text) between Equations (1) and (2), discussing this point and including the references above and others as well.
 
@@
 
-A8.
-ALBERT VA A ESCRIBIR UN POCO DE TEXTO.
+A8. ALBERT VA A ESCRIBIR UN POCO DE TEXTO. -- FALTA ESTO --
 

### 2020-03-10 lloveras_2020_v2.tex
Albert está trabajando en esto, no tocar todavía, gracias.

@@
 {As detailed in Section \ref{intro}, rotations CR-2082 and CR-2208 were selected to carry out DEMT reconstructions, based on data taken by the STEREO/EUVI-B and SDO/AIA instruments, respectively.} The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package.
-For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.
+\edit{In the case of EUVI data, stray-light contamination is removed by deconvolution of the point spread function (PSF), carefully determined for each detector by \citet{shearer_2012}.
+In the case of AIA data, we have not yet implemented such a procedure as we were not aware of reliable determinations of their PSF, and we also understand that stray light contamination is expected to be not so important for this instrument.
+A recent study by \citet{saqri_2020} indicates that the effect is noticeable in DEM analysis of coronal holes (CHs).
+That is also the case for DEM analysis of EUVI images.
+Nonetheless, as shown by \citet{lloveras_2017}, due to the temporal and spatial binning of the images used in tomography the effect of stray-light removal in DEMT products turns out to be mild, being $\lesssim 10\%$ for density products and negligible for temperature products.
+In the future, we will explore the effect of stray-light removal in AIA images on DEMT tomography, which we expect to be smaller than for EUVI images.} For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.
 
@@
 This has two implications.
-Firstly, the fast dynamics that typically characterizes those structures is \edit{absent/reduced} from the data.
+Firstly, the fast dynamics that typically characterizes those structures is absent from the data.
 Secondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume.
@@
 In each tomographic voxel, the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that best reproduce the three tomographically reconstructed values of FBE in that voxel.
+
+\edit{As the LDEM describes the temperature distribution of the plasma in a specific voxel, it does not deal with different large scale structures, as it may be the case for the DEM describing the plasma along a full LOS.
+As a result, LDEMs are usually successfully modeled with simpler profiles (such as Gaussian) than those returned by DEM studies constrained by LOS-integrated intensities.
+Parametric techniques are also used for DEM analysis of narrowband images, such as in the works by \citet{aschwanden_2011,plowman_2013,delzanna_2013}.
+Other methods applied to DEM analysis of narrow band images include Monte Carlo Markov Chain (MCMC) techniques \citep{schmeltz_2016}, regularized inversion techniques \citep{hannah_2012}, and iterative solvers \citep{pickering_2019,morgan_2019} that use the known TRFs of all filters as a functional base.
+The latter work in particular, introduces a fast iterative solver named SITES, which can easily be adapted for its use in DEMT.
+We will explore this in the future.}
 
@@
 
-\edit{Legs of type down turn out to have a significant population only for closed-small field lines.
-Hence, we separate them into two complementary classes: legs of type 0 (down) and legs of type I (up).
-In the case of closed-large field lines, legs of type down are $\lesssim 15\%$ of the population.
-In the case of open field lines, legs of type down are $\lesssim 10\%$ of the population.
+\edit{In the case of closed-small field lines, the population of down and up legs becomes comparable for CR-2082, so we classify them into the two complementary classes of legs of type 0 (down) and legs of type I (up).
+In the case of closed-large field lines, legs of type down are $\lesssim 15\%$ of the population for both rotations.
+In the case of open field lines, legs of type down are $\lesssim 10\%$ of the population for both rotations.
 Hence, the requirement of being up for legs of type II and III is included to select the vastly dominating population in each case.
-On the other hand, the inclusion of latitude limits for the footpoints in the classification of legs from type 0 through III is purposely set to study the streamer belt in three distinct, progressively outer layers, as well as to separate the field lines of the high latitude CHs (legs of type III).
+On the other hand, the inclusion of latitude limits for the footpoints in the classification of legs from type 0 through III is purposely set to study the streamer belt in progressively outer layers, as well as to separate the field lines of the high latitude CHs (legs of type III).
 In Section \ref{resu}, the results of both the DEMT and AWSoM models in the four classes of legs are statistically analysed.}
@@
 Top, middle and bottom panels show the results at three heliocentric heights, $1.025$, $1.065$ and $1.105\,\mrsun$ respectively.
-Black voxels correspond to non-reconstructed regions (see text in Section \ref{demt_res}) and thick-black curves indicate the open/closed boundaries.
-\comment{Por consistencia, creo que en los títulos de los CarrMaps de las Figuras 1 y 2 deberías usar la notación $\sqravgN$ y $\Tm$.
-Si esto lo hacés en LETITBE con el IDL 8.4, podrás usar los comandos de LaTeX dentro de las strings ``title", con lo cual no solo será simple sino que $\sqravgN$ no va a ocupar mucho más espacio y las chances son que salga todo lindo sin cambiar el tamaño de letra ni nada.}}
+Black voxels correspond to non-reconstructed regions (see text in Section \ref{demt_res}) and thick-black curves indicate the open/closed boundaries.}
 \label{carmaps_demt_2082}
@@
 
-{The magnetically open and closed regions of the AWSoM model are associated with Coronal holes (CHs) and the equatorial streamer belt, respectively.
+{The magnetically open and closed regions of the AWSoM model are associated \edit{with CHs} and the equatorial streamer belt, respectively.
 The {location of the} open/closed boundaries derived from the respective AWSoM model quite accurately matches {the regions of the DEMT maps, which exhibit the strongest latitudinal gradient of both the electron density and temperature.}}
@@
 
-Latitude-longitude maps of the score $R$ defined by Equation \ref{R} show that \edit{the agreement between the tomographic and synthetic FBEs meets $R \lesssim 0.01$ in more than 90\% of the voxels where tomographic reconstruction is possible (i.e.
-where FBEs are non zero), and meets $R \lesssim 0.10$ in the rest.
-This implies that the LDEM found in each voxel accurately predicts the reconstructed FBEs.} \comment{Diego, evaluá que el valor que incluí es correcto.
-Simplemente fijate en que fracción de los voxels SIN ZDAs $R<0.01$ para CR-2208, yo estimo $90\%$.
-pra 2082 no hace falta.
-Comentame antes de enviar.}
-
-.
-The notable exception is to be found only in the CHs of the rotation {analysed} based on AIA data.
-A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}.
-This point is further discussed below in this section.
+Latitude-longitude maps of the score $R$ defined by Equation \ref{R} show that \edit{the agreement between the tomographic and synthetic FBEs is 5\% or better in more than 90\% of the reconstructed coronal volume (i.e.
+where FBEs are non zero), and of order 10\% in the rest of the volume.
+This implies that the LDEM found in each voxel accurately predicts the reconstructed FBEs.}
 
@@
 
-\edit{For both rotations, the population of type 0 (small-closed-down) legs population peaks in the core of the streamer belt, around the equator in the case of CR-2082, and towards the southern hemisphere in the case of CR-2208.} This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the solar minimum between {SCs 23 and 24} by \citet{nuevo_2013}.
+\edit{For both rotations, the population of type 0 (small-closed-down) legs peaks at the core of the streamer belt, around the equator in the case of CR-2082, and towards the southern hemisphere in the case of CR-2208.} This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the solar minimum between {SCs 23 and 24} by \citet{nuevo_2013}.
 Later on, \citet{lloveras_2017} showed {that} equatorial down loops in streamers were also to be found in the deep minimum between SCs {23 and 24}.
@@
 The relatively smaller population of down legs seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}.
-\edit{Type I (small-closed-up) legs are present at all latitudes in the streamer belt.
+\edit{Type I (small-closed-up) legs are present at all latitudes within the streamer belt.
 Their population peaks in the mid-latitudes of both hemispheres for CR-2082, and in the mid-latitudes of the northern hemisphere for CR-2208.
-Type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt (the requirement of footpoints located beyond mid-latitudes was included precisely to select this kind of loop).
+The latitude distribution of legs of type 0 and I in CR-2082 is consistent to the distribution of down and up loops of CR-2081 in the analysis by \citet{nuevo_2013}, which did not place any limits on the latitude location of the analysed structures.}
+
+\edit{Type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt (the requirement of footpoints located beyond mid-latitudes was included precisely to select this kind of loop).
 Finally, type III (open) legs populate the high latitude CHs.}

### 2020-03-11 response_to_review_SOLA-D-20-00015_v1.txt
Albert está trabajando en esto, no tocar todavía, gracias.

@@
 
-A8. ALBERT VA A ESCRIBIR UN POCO DE TEXTO. -- FALTA ESTO --
-
-LO QUE SIGUE DEBE SER TODO HECHO POR DIEGO, CONSULTANDO PRINCIPALMENTE A ALBERT. TODO CAMBIO DEBERÁ ESTAR DESTACADO CON \EDIT{} EN ROJO.
+A8.
+We agree it is important to expand the references in the article to other studies of the quiet Sun.
+As you mention, we do refer to Hahn & Savin (2014) alreadyin the discussion.
+In the Introduction, we included now the other references you provided, as well as another one (new text in red).
 

### 2020-03-11 lloveras_2020_v2.tex
Albert está trabajando en esto, no tocar todavía, gracias.

@@
 
+\edit{Non-tomographic studies of localized regions of the quiet-Sun corona have been carried out by means of DEM analysis.
+\citet{mackovjak_2014} used regularized inversion techniques to study characteristic temperatures in the quiet-Sun.
+\citet{lopez_2019} used a parametric method to study EUV dimmings after coronal mass ejections (CMEs) in order to estimate the coronal mass evacuated by the events.
+At a global scale, DEM analysis has been used by \citet{morgan_2017} to characterize the evolution of the temperature of the quiet-Sun corona during most of solar cycle (SC) 24.}
+
 {The combination of DEMT with global magnetic models provides insight} into the 3D thermodynamical structure of the global corona.
@@
 {Combining the DEMT and AWSoM models, we carry out a detailed \edit{quantitative} analysis of two target rotations.
-We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during {the end of the declining} phase of SC 24.
+We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the SC 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during {the end of the declining} phase of SC 24.
 {In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} {(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG: \citealt{gong}).
@@
 Other methods applied to DEM analysis of narrow band images include Monte Carlo Markov Chain (MCMC) techniques \citep{schmeltz_2016}, regularized inversion techniques \citep{hannah_2012}, and iterative solvers \citep{pickering_2019,morgan_2019} that use the known TRFs of all filters as a functional base.
-The latter work in particular, introduces a fast iterative solver named SITES, which can easily be adapted for its use in DEMT.
-We will explore this in the future.}
+The latter work in particular, introduced a fast iterative solver named SITES, which can easily be adapted for its use in DEMT.
+We will explore this in the future and compare results with those provided by our parametric technique.}
 

### 2020-03-11 response_to_review_SOLA-D-20-00015_v1.txt
Albert está trabajando en esto, no tocar todavía, gracias.

@@
 We deeply acknowledge the reviewer, whose report reflects her/his very careful and interested read.
-We found all queries very relevant, with useful and constructive criticisms and suggestions.
+All queries very relevant, with useful and constructive criticisms and suggestions.
 Below, we copy/paste the full review.
@@
 
-We addressed all points, as a result of which we believe the manuscript improved in both content and clarity. In particular, a major improvement in this new version of the draft relates to Q5 below.
+We addressed all points, as a result of which we believe the manuscript has improved in both content and clarity.
+In particular, a major improvement in this new version of the draft relates to Q5 below.
 
@@
 A4.
-First of all we note that, as a result of the discussion in Q5 below, a few numbers in Table 2 were updated (those corresponding to type-III legs for CR-2208).
-Now, when selecting field lines for analysis of both the DEMT and the AWSoM models, the classification of types of legs introduced in section 2.3 is used for each model separately.
-As a result, as shown by comparing the middle panels of Figure 3 and the bottom panels of Figure 11, and as discussed in the corresponding texts of the manuscript, the selection of field lines for DEMT is not the same.
+When selecting field lines for analysis of both the DEMT and the AWSoM models, the classification of types of legs introduced in section 2.3 is applied to the DEMT reconstruction and the AWSoM model separately.
+As a result, as shown by comparing the middle panels of Figure 3 and the bottom panels of Figure 11, and as discussed in the corresponding texts of the manuscript, the selection of field lines for DEMT is not the same as the selection of field lines for the AWSoM model.
 In comparing those Figures each color indicates comparable regions between the two analysis.
-It is so that Figures 12 and 13, and Table 2, which show DEMT-versus-AWSoM comparison for each rotation, are not done line-by-line but rather region-by-region (say: orange, red and cyan).
+It is so that Figures 12 and 13, and Table 2, which show DEMT-versus-AWSoM comparison for each rotation, are not done line-by-line but rather region-by-region (orange, red and cyan).
 The suggestion of calculating the MAD would require selecting the same field lines for both models, which is beyond the scope of the present comparative analysis.
-Informing the MAD is a good idea, being a precise measure of how the comparison between both models spreads.
+Informing the MAD is a good idea, being a robust quantitative measure of how the comparison between both models spreads.
 We will certainly implement such an analysis in a next effort.
-In the present draft, we trust the current comparison (Figures 12 and 13, and Table 2) provide are pretty informative summary of how both models compare.
+In the present draft, we trust the current comparison (Figures 12 and 13, and Table 2) provide a pretty informative summary of how both models compare.
 Let us know what you think.
@@
 Thanks for the reference, which is certainly relevant and now mentioned in the paper, as discussed below.
-We are not sure stray light contamination was actually the reason of the reported issue, which is now solved.
+We are not sure stray light contamination is actually the fundamental reason of the reported issue, which is now solved, as described next.
 
-The discussion section of v1 of the draf include this sentence (now deleted): "The source of this distinct performance of DEMT when applied to EUVI or AIA data is related to the TRFs of the respective filter sets.
-We are currently implementing an improved LDEM determination algorithm to deal with this issue that will be used in a follow up article." We have successfully implemented the improved version of the code, as a result of which this problem has been solved.
+The discussion section of v1 of the draf includes this sentence (now deleted): "The source of this distinct performance of DEMT when applied to EUVI or AIA data is related to the TRFs of the respective filter sets.
+We are currently implementing an improved LDEM determination algorithm to deal with this issue that will be used in a follow up article." While waiting for your report and preparing V2 of the draft, we successfully implemented the improved version of the code, as a result of which this problem has been solved.
 The issue was related to the algorithm that solves the optimization problem posed in each voxel to find the LDEM.
@@
 We addressed the problem by exploring multiple starting points when solving the optimization problem in cases where the initial solution was not good enough.
-In this draft, this improved algorithm affects results concerning type III legs for CR2208.
+In this draft, the improved algorithm affects results concerning type III legs for CR2208.
 As a result, the following Figures have been updated: 2, 3, 4, 5, 10, 13 and 14.
-You will notice all these Figures are just like the original ones, except the problem in the CHs of CR-2208 has been solved.
-Text throughout the manuscript was edited accordingly, in the following locations of v2 of the draft:
- - Red text in Pg 12 and Pg 13, and the red rext in Pg 15 informing characteristic values of Grad_r(Tm).
+You will notice all these Figures are just like the original ones, except in the CHs of CR-2208, where the previous issue has been solved.
+The text throughout the manuscript was edited accordingly, in the following pages of V2 of the draft:
+ - Related text in Pgs. 12-15 (some of the red text in these pages relates to Q4 above).
  - Numerical values concerning legs of type-III for CR-2208 in Tables 1 and 2.
@@
 
-A6. We agree. We edited the Abstract. Let us know what you think.
-
--- FALTA ESTO --
+A6.
+We fully agree.
+We edited the Abstract, reducing the number of introductory lines from 12 down to 5, and greatly expanding the details in the results, and still keeping the full abstract 2 lines shorter than in V1.
+The presentation of results is better organized.
+We first summarize purely DEMT results.
+For this we were careful to mention which findings were first reported in previous DEMT studies.
+We still believe these are worth highlighting here as these were now found using the latest implementation of DEMT.
+Then we summarize how the results of the latest implementation of AWSoM compare with DEMT, highlighting the shortcomings as well.
 
@@
 A8.
-We agree it is important to expand the references in the article to other studies of the quiet Sun.
-As you mention, we do refer to Hahn & Savin (2014) alreadyin the discussion.
+We agree it is relevant to expand the references in the Introduction to other DEM studies of the quiet-Sun.
 In the Introduction, we included now the other references you provided, as well as another one (new text in red).
+We kept our reference to Hahn & Savin (2014) in the discussion.
 
@@
 Q9. Some sections can benefit from weeding out of repetitions. You tend to repeat statements regarding the method a lot. For example:
+
 - Paragraph starting page 13, line 41. This has already been said in the method.
@@
 
-A9. Thanks for pointing this out. We have improved the text in the following parts:
+A9. Thanks or the careful read. We have improved the text in those passages, and others similar that we found, with changes highlighted in red.
 
@@
 
-A10. Thanks very much for this detailed corrections. We have addressed them all.
+A10. Thanks very much for this detailed corrections. We believe we addressed them all. Changes highlighted in red.
 

### 2020-03-11 lloveras_2020_v2.tex
Albert está trabajando en esto, no tocar todavía, gracias.

@@
 \begin{abstract}
-Observational techniques play an essential role in advancing our understanding of the physical processes governing the solar corona, providing in {particular validation} data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere.
-Solar rotational tomography is currently the sole observational technique {able to provide} a 3D quantitative description of the solar corona at a global scale.
-Based on {extreme ultraviolet} images {of space} borne instruments, {differential emission measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$.
-We carry out a study of the corona {through DEMT} reconstructions {and MHD simulations, using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) developed at the University of Michigan as a component of the Space Weather Modeling Framework.
-{Two target} rotations were selected from the solar minimum between solar cycles (SCs) 23 and 24 and {the {end of the} declining} phase of SC 24.
-The 3D {DEMT} and MHD models are analysed and compared in distinct coronal magnetic structures.
-{We report in quantitative detail on the 3D thermodynamic structure of the inner corona as revealed by the DEMT analysis.
-We {show the} existence of diverse types of temperature structures in the low and mid latitudes of the {streamer belt.
-We estimate} the heating energy required to keep them {stable, which we argue may} be accounted for by Alfvén waves.
-{We also show that results of the latest version of the AWSoM model overall} agree with DEMT {reconstructions within a $\approx 20\%$ accuracy.
-We highlight some details of the AWSoM model that should} be improved to better reproduce {tomographic} results, in particular concerning the source region of the {fast and slow components of the solar wind.}}
+\edit{We carry out a study of the global three-dimensional (3D) structure of the electron density and temperature of the quiescent inner solar corona ($r<1.25\,\mrsun$) by means of tomographic reconstructions and magnetohydrodynamic simulations.
+We use differential emission measure tomography (DEMT) and the Alfv\'en Wave Solar Model (AWSoM), in their latest versions.
+Two target rotations were selected from the solar minimum between solar cycles (SCs) 23 and 24 and the declining phase of SC 24.
+We report in quantitative detail on the 3D thermodynamic structure of the core and outer layers of the streamer belt, and of the high latitude coronal holes (CH), as revealed by the DEMT analysis.
+We report on the presence of two types of structures within the streamer belt, loops with temperature decreasing/increasing with height (dubbed down/up loops), as reported first in previous DEMT studies.
+We also estimate the heating energy flux required at the coronal base to keep these structures stable, found to be or order $10^5\,\erg\,\cminvs\,\s^{-1}$, consistently with previous DEMT and spectroscopic studies.
+Our findings may explained by Alfvén wave dissipation.
+We also compare the 3D DEMT and AWSoM results in distinct magnetic structures.
+We show that the agreement between the products of both techniques is the best so far, with an overall agreement $\lesssim 20\%$, depending on the target rotation and the specific coronal region.
+Even so, in its current version the ASWsoM model can not reproduce down loops.
+Also, the model exhibits a latitude variation of the electron density in the source region of the fast and slow components of the solar wind that differs from that of the DEMT results.}
 \end{abstract}

### 2020-03-11 response_to_review_SOLA-D-20-00015_v1.txt
Albert está trabajando en esto, no tocar todavía, gracias.

@@
 We deeply acknowledge the reviewer, whose report reflects her/his very careful and interested read.
-All queries very relevant, with useful and constructive criticisms and suggestions.
+All queries are very relevant, with useful and constructive criticisms and suggestions.
 Below, we copy/paste the full review.
@@
 We fully agree.
-We edited the Abstract, reducing the number of introductory lines from 12 down to 5, and greatly expanding the details in the results, and still keeping the full abstract 2 lines shorter than in V1.
-The presentation of results is better organized.
+We edited the Abstract, reducing the number of introductory lines from 12 down to 5, and greatly expanding the details in the results, while keeping the full abstract 2 lines shorter than in V1.
+The presentation of results is better organized now.
 We first summarize purely DEMT results.
 For this we were careful to mention which findings were first reported in previous DEMT studies.
-We still believe these are worth highlighting here as these were now found using the latest implementation of DEMT.
-Then we summarize how the results of the latest implementation of AWSoM compare with DEMT, highlighting the shortcomings as well.
+We still believe these are worth highlighting here as these were now found using the latest implementation of DEMT, in which we implemented here substantial improvements, as discussed in the draft.
+We close the abstract summarizing how the results of the latest implementation of AWSoM compare with DEMT, highlighting its shortcomings as well.
 

### 2020-03-11 lloveras_2020_v2.tex
Albert está trabajando en esto, no tocar todavía, gracias.

@@
 We also estimate the heating energy flux required at the coronal base to keep these structures stable, found to be or order $10^5\,\erg\,\cminvs\,\s^{-1}$, consistently with previous DEMT and spectroscopic studies.
-Our findings may explained by Alfvén wave dissipation.
-We also compare the 3D DEMT and AWSoM results in distinct magnetic structures.
+We discuss how these findings are consistent with coronal dissipation of Alfvén waves.
+We compare the 3D results of DEMT and AWSoM in distinct magnetic structures.
 We show that the agreement between the products of both techniques is the best so far, with an overall agreement $\lesssim 20\%$, depending on the target rotation and the specific coronal region.
-Even so, in its current version the ASWsoM model can not reproduce down loops.
-Also, the model exhibits a latitude variation of the electron density in the source region of the fast and slow components of the solar wind that differs from that of the DEMT results.}
+In its current implementation the ASWsoM model can not reproduce down loops though.
+Also, in the source region of the fast and slow components of the solar wind, the electron density of the AWSoM model increases with latitude, opposite to the trend observed in DEMT reconstructions.}
 \end{abstract}
@@
 \citet{mackovjak_2014} used regularized inversion techniques to study characteristic temperatures in the quiet-Sun.
-\citet{lopez_2019} used a parametric method to study EUV dimmings after coronal mass ejections (CMEs) in order to estimate the coronal mass evacuated by the events.
+\citet{lopez_2019} used a parametric method to study EUV dimmings after coronal mass ejections (CMEs) to estimate the coronal mass evacuated by the events.
 At a global scale, DEM analysis has been used by \citet{morgan_2017} to characterize the evolution of the temperature of the quiet-Sun corona during most of solar cycle (SC) 24.}
@@
 More recently,} \citet{lloveras_2017} combined DEMT with PFSS {models to study the thermodynamics of the global solar corona in specific magnetic structures for two target rotations selected from the last two solar minimum epochs.
-Also combining DEMT with a PFSS model,} \citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux {required at the coronal base in order to maintain stable coronal loops}.
+Also combining DEMT with a PFSS model,} \citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux {required at the coronal base to maintain stable coronal loops}.
 In this article, {DEMT is first combined with the magnetic field of a magnetohydrodynamic (MHD) model.}

### 2020-03-11 response_to_review_SOLA-D-20-00015_v1.txt
Albert está trabajando en esto, no tocar todavía, gracias.

@@
 
+A9: We agree, and answer below point-by-point.
+
 - Paragraph starting page 13, line 41. This has already been said in the method.
+
+Agreed. We deleted that paragraph moved the detail on the leg-averaged temperature <Tm> right before Table 1 (text in red).
+
 - Sentence Page 14, line 25 'For each leg…
+
+Agreed, removed.
+
 - statement in parenthesis at page 15, line 24.
+
+Agreed, removed.
+
 - Section 4, first two paragraphs.
+
+Agreed, removed. We edited the new first paragraph in this section (red text) following also your suggestions in Q10 below, although we wanted to keep references to specific Figures and Tables here.
+
 - Page 26, line 26:
@@
 Shorten to: 'The energy input phi at the coronal base, required to maintain stable coronal loops, is in the range…'
+
+Agreed, done.
+
 - Page 26, lines 38-43, between 'Results of the AWSoM….summarized as follows.' can be omitted.
 
-A9. Thanks or the careful read. We have improved the text in those passages, and others similar that we found, with changes highlighted in red.
+Agreed, done. A little edit was introduced (red text) to start the paragraph.
 
@@
 
-A10. Thanks very much for this detailed corrections. We believe we addressed them all. Changes highlighted in red.
+A10. Thanks very much for this detailed corrections. We agreed with basically all of them and addressed them all. Changes highlighted in red.
 

### 2020-03-11 lloveras_2020_v2.tex
Albert está trabajando en esto, no tocar todavía, gracias.

@@
 {The computational domain of the solar corona} extends from 1 to {$24\,\mrsun$}.
-\del{The spherical grid in the solar corona is radially stretched (with a maximum resolution {of $0.001\,\mrsun$} near the Sun)} \edit{The spherical grid has an adaptive grid that has fine resolution near the Sun, and increases outward} with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates.
+\edit{The spherical grid has an adaptive grid that has fine resolution near the Sun, and increases outward} with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates.
 The Adaptive Mesh refinement (AMR) resolves the angular cell size to $1.4\mdeg$ between $1 - 1.7\,\mrsun$ and to $2.8\mdeg$ outside this radius range.
@@
 In the electron temperature fit, $a\,[\MK/\mrsun]$ is the slope and $T_0\,[\MK]$ is the electron temperature at the footpoint of the loop.
-The slope $a$ estimates the radial gradient of the electron temperature along the loop, which we denote as $a = \dr\Tm$ hereafter, \edit{with} $\dr\equiv\er\cdot\nabla$ \edit{being} the radial derivative operator \edit{and} $\er$ is the heliocentric radial unit vector.
+The slope $a$ estimates the radial gradient of the electron temperature along the loop, which we denote as $a = \dr\Tm$ hereafter, \edit{with} $\dr\equiv\er\cdot\nabla$ \edit{being} the radial derivative operator \edit{and} $\er$ the heliocentric radial unit vector.
 
@@
 We then select field lines for which the temperature {is significantly correlated with height} by requiring $|\rhoTr| > 0.5$.
-{To test the goodness of the fit \del{to the temperature-height data} we perform a chi-squared test \citep{recipes} considering the uncertainty of the DEMT data, selecting legs for which the fit matches the data with a 90\% confidence level.} In this way, legs for which the DEMT temperature does not show a significant {correlation} with height, or the linear fit to temperature is \edit{weak}, are {excluded from the} analysis.
+{To test the goodness of the fit we perform a chi-squared test \citep{recipes} considering the uncertainty of the DEMT data, selecting legs for which the fit matches the data with a 90\% confidence level.} In this way, legs for which the DEMT temperature does not show a significant {correlation} with height, or the linear fit to temperature is \edit{weak}, are {excluded from the} analysis.
 {The test is also applied to the density-height data points, to ensure the trend is reasonably represented by the exponential fit.} Finally, selected legs are then classified as up or down according to $\dr\Tm > 0$ or $\dr\Tm < 0$, respectively.
@@
 
-\del{To characterize the DEMT results in different magnetic structures, we traced $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.
-For both rotations, all legs that meet the criteria listed in Section \ref{trace} were selected.
-For each leg, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.
-{As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}}
-
 \begin{figure}[h!]
@@
 Open legs are indicated in gray color and closed ones in black color.
-\del{For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit}-\ref{Tfit}.} Considering the DEMT data points and the resulting fits along each leg, the \edit{middle} panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
+Considering the DEMT data points and the resulting fits along each leg, the \edit{middle} panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
 Using a four-color code, type 0, I, II and III legs are shown in blue, \edit{orange, red, and cyan} color, respectively.
@@
 From top to bottom {results are shown for} type 0 to type III {legs}{, respectively}.
-From left to right the panels show the statistical distribution of the electron density value $\NCB \equiv \sqravgN(r=1.055)$ \del{(at the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.
+From left to right the panels show the statistical distribution of the electron density value $\NCB \equiv \sqravgN(r=1.055)$, \edit{the scale height $\lN$, and the height-averaged (along the leg) electron temperature $\aTm$}, {with the median value $m$ indicated in each plot}.
 
@@
 The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.
-In the case of the electron temperature, for both rotations the models agree within $\approx 15\%$ at all latitudes \del{of the streamer belt, showing larger discrepancies in the CHs}.
+In the case of the electron temperature, for both rotations the models agree within $\approx 15\%$ at all latitudes.
 Secondly, for both rotations, and for both models, these plots clearly show the relatively lower temperatures characterizing the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
@@
 \section{{Discussion and Conclusions}}\label{discu}
-\del{
-We carried out the 3D DEMT reconstruction and MHD modeling of the inner solar corona for two target rotations, CR-2082 and CR-2208.
-The former belongs to the deep minimum epoch between SCs 23 and 24, while the latter belongs to the end of the declining phase of SC 24.
-The present work introduces two improvements in the implementation of DEMT, namely the use of only off-limb data in the EUV images, and the inclusion of a 3D regularization scheme (Section \ref{demt}).
-The MHD model used is here the latest version of the AWSoM component of the SWMF suite  (Section \ref{awsom}).
-Based on the magnetic field of AWSoM model and the results of the DEMT model for electron density and temperature, we classified coronal structures in four different types.
-{Small loop legs} in the core of the streamer belt are classified in down/up types according to their temperature decreasing/increasing with height (dubbed type 0/I).
-{Large closed legs} of type up that form the envelope of the streamer belt (dubbed type II), and open field lines of type up populating the CHs (dubbed type III).}
 
-\del{Concerning the DEMT reconstructions, Figure \ref{rpoint_demt} shows that, for both rotations,} \edit{Magnetic} field lines of type 0, I and II \edit{were selected to be associated} with increasingly outer {layers} of the equatorial streamer belt.
-\del{Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} show in 3D quantitative detail how} \edit{These progressively} outer magnetic structures exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature.
-For both rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes.
+\edit{Magnetic field lines of type 0, I and II were selected to be associated with increasingly outer layers of the equatorial streamer belt (Figure \ref{rpoint_demt}).
+These magnetic structures progressively exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature, as informed in 3D quantitative detail in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}.} For both rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes.
 Also, in the case of CR-2082 the fraction of down legs is significantly larger than for CR-2208.
@@
 Our results for target CR-2082 compare very well with those of \citet{nuevo_2015} and \citet{lloveras_2017} for target CR-2081.
-As our study uses the improved version of the DEMT technique, such comparison provided a consistency \edit{check.} \del{for the changes implemented in the DEMT technique.} \edit{For both rotations, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.}
+As our study uses the improved version of the DEMT technique, such comparison provided a consistency \edit{check.} \edit{For both rotations, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.}
 
-{\del{In the streamer belt region we combined the DEMT results and the AWSoM magnetic model to infer the energy input flux $\phi_h$ at the coronal base required to maintain stable coronal loops.
-We found characteristic values in the range \\}
 \edit{The energy input flux $\phi_h$ at the coronal base, required to maintain stable coronal loops, is in the range} $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}.
 Based on spectroscopic data of the EIS instrument in quiet-Sun regions \citet{hahn_2014} showed that, if the observed non-thermal broadening are assigned to Alfvén waves, their energy flux at the coronal base is estimated to be in the range $\approx 1.5-2.5\times 10^5\,\erg\,\cminvs\,\s^{-1}$.
-A large fraction of the coronal base energy input flux $\phi_h$ estimated in this work, or even its totality, could then be accounted for by Alfvén waves (see the discussion in \citealt{maccormack_2017}).}
+A large fraction of the coronal base energy input flux $\phi_h$ estimated in this work, or even its totality, could then be accounted for by Alfvén waves (see the discussion in \citealt{maccormack_2017}).
 
-\del{
-Results of the AWSoM model {were compared} to those of the DEMT reconstructions {in the range of coronal heights simultaneously covered by both models, namely $\approx 1.05-1.20\,\mrsun$.} In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines.} The detailed comparison shown in this work can be summarized as follows.
-For CR-2082, the electron density of both models agree within $\approx 20\%$ {in most regions}, while for CR-2208 the agreement is within $\approx 5\%$.
-{The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both rotations\del{, with larger discrepancies in the CHs.} This level of agreement between both models {(within or slightly beyond the uncertainty level of DEMT results)} is considerably better than that reported in previous works.
+\edit{The comparison of the results of the AWSoM model to the DEMT reconstructions can be summarized as follows.} For CR-2082, the electron density of both models agree within $\approx 20\%$ {in most regions}, while for CR-2208 the agreement is within $\approx 5\%$.
+{The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$.
+This level of agreement between both models {(within or slightly beyond the uncertainty level of DEMT results)} is considerably better than that reported in previous works.
 \citet{jin_2012} and \citet{oran_2015}{, who used previous versions of the AWSoM model,} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.}
@@
 
-\del{Within the quantitative match between both models summarized in the previous paragraph, there are some qualitative agreements and {disagreements worth noticing}.
-}For both rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
+For both rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
 On the other hand, while the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density {(physically expected in transitioning from magnetically closed to open regions)}, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.

### 2020-03-11 left_out_text.tex
Versión 2, ya procesada por Albert.

@@
+We carried out the 3D DEMT reconstruction and MHD modeling of the inner solar corona for two target rotations, CR-2082 and CR-2208.
+The former belongs to the deep minimum epoch between SCs 23 and 24, while the latter belongs to the end of the declining phase of SC 24.
+The present work introduces two improvements in the implementation of DEMT, namely the use of only off-limb data in the EUV images, and the inclusion of a 3D regularization scheme (Section \ref{demt}).
+The MHD model used is here the latest version of the AWSoM component of the SWMF suite  (Section \ref{awsom}).
+
+Based on the magnetic field of AWSoM model and the results of the DEMT model for electron density and temperature, we classified coronal structures in four different types.
+{Small loop legs} in the core of the streamer belt are classified in down/up types according to their temperature decreasing/increasing with height (dubbed type 0/I).
+{Large closed legs} of type up that form the envelope of the streamer belt (dubbed type II), and open field lines of type up populating the CHs (dubbed type III).
+
+%---------REMOVE THESE OPTIONS AND DEFs BEFORE SUMBISSION---------------------------------------
+\usepackage[usenames,dvipsnames]{xcolor} % Las opciones: [USENAMES,DVIPSNAMES] 
+                                         % ponen a disposición los colores ejemplificados aquí:
+                                         % https://en.wikibooks.org/wiki/LaTeX/Colors
+\def\diego#1{\textcolor{red}{#1}}
+\def\albert#1{\textcolor{orange}{#1}}
+\def\fede#1{\textcolor{ForestGreen}{#1}}
+\def\temp#1{\textcolor{gray}{#1}}
+\def\notebyalbert#1{\textcolor{blue}{NOTE: #1}}
+%-----------------------------------------------------------------------------------------------
+
+ Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, {reveals that in most of the CH region the result for $\Tm$ below height $1.105\,\mrsun$ is quite uniform and artificially low}.
+As it turns out, around and above height this height the score $R$ is lower and the temperature results are more reliable.
+As a result, the temperature gradient along these legs is artificially larger, with the linear fit trying to simultaneously fit the artificially low values of $\Tm$ at lower heights.
+In this case, DEMT performs poorly in modeling a LDEM that predicts the tomographic FBEs with reasonable accuracy.
+
+ to the limited temperature sensitivity of the instrumental passbands. The radiative loss term is {here calculated based on plasma emission detected by three coronal bands of EUVI or AIA.
+
+ Indeed, the top panels in Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208}, at height $1.025\,\mrsun$, clearly do not represent coronal conditions (although we include them here for completeness).
+
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1025_Rsun.pdf}
+
+\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1025_Rsun.pdf}
+
+As a result of the former, artifacts introduced by coronal dynamics are mitigated, and as a result of the latter, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
+\caption{{Carrington maps of the measure $R$ defined by Equation \ref{R}, for CR-2082 (left panels) and CR-2208 (right panels), at heights $1.025$, $1.065$ and $1.105\,\mrsun$, from top to bottom}. }
+\label{carmaps_R_2082_2208}
+\end{center}
+\end{figure}
+
+{For both rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of {the DEMT} measure $R$ defined by Equation \ref{R}, at the same three heights shown in Figures \ref{momento1} and \ref{momento2}.
+
 %\notebyalbert{No comprendo esta frase:} \emph{This classification of types of lines automatically leads to specific regions arranged along all longitudes associated with different thermodynamic, with good symmetry between both hemispheres in both rotations.}

### 2020-03-12 response_to_review_SOLA-D-20-00015_v1.txt
Versión 2, ya procesada por Albert.
minimas modificaciones

@@
 This can be seen in Figure 7 of Nuevo et al.
-92013), were they analyzed the small closed up and down loops for two rotations of solar minimum, without placing any limits in the latitude of the footpoints.
+2013), were they analyzed the small closed up and down loops for two rotations of solar minimum, without placing any limits in the latitude of the footpoints.
 As our main objective here is to be able to analyze progressively outer layers of the streamer belt, we include these limits in the latitude of the footpoints.
@@
 For this we were careful to mention which findings were first reported in previous DEMT studies.
-We still believe these are worth highlighting here as these were now found using the latest implementation of DEMT, in which we implemented here substantial improvements, as discussed in the draft.
+We still believe these are worth highlighted here as these were now found using the latest implementation of DEMT, in which we implemented here substantial improvements, as discussed in the draft.
 We close the abstract summarizing how the results of the latest implementation of AWSoM compare with DEMT, highlighting its shortcomings as well.
@@
 
-A10. Thanks very much for this detailed corrections. We agreed with basically all of them and addressed them all. Changes highlighted in red.
+A10. Thanks very much for this detailed corrections. We basically agreed with all of them and addressed them all. Changes highlighted in red.
 

### 2020-03-12 lloveras_2020_v2.tex
minimas modificaciones

@@
 \edit{In the case of EUVI data, stray-light contamination is removed by deconvolution of the point spread function (PSF), carefully determined for each detector by \citet{shearer_2012}.
-In the case of AIA data, we have not yet implemented such a procedure as we were not aware of reliable determinations of their PSF, and we also understand that stray light contamination is expected to be not so important for this instrument.
+In the case of AIA data, we have not yet implemented such a procedure as we were not aware of reliable determinations of their PSF, and we also understand that stray light contamination is expected to be less important for this instrument.
 A recent study by \citet{saqri_2020} indicates that the effect is noticeable in DEM analysis of coronal holes (CHs).
@@
 {The solution of the tomographic problem involves {inversion of} a very large sparse matrix.
-Such inversion problems are characterized by spurious {high-fre\-quen\-cy} artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}.
+Such inversion problems are characterised by spurious {high-fre\-quen\-cy} artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}.
 In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude.
@@
 \edit{In the case of closed-small field lines, the population of down and up legs becomes comparable for CR-2082, so we classify them into the two complementary classes of legs of type 0 (down) and legs of type I (up).
-In the case of closed-large field lines, legs of type down are $\lesssim 15\%$ of the population for both rotations.
-In the case of open field lines, legs of type down are $\lesssim 10\%$ of the population for both rotations.
+In the case of closed-large field lines, down legs are $\lesssim 15\%$ of the population for both rotations.
+In the case of open field lines, down legs are $\lesssim 10\%$ of the population for both rotations.
 Hence, the requirement of being up for legs of type II and III is included to select the vastly dominating population in each case.
@@
 
-{Both target rotations are highly axisymmetric, \textit{i.e.} characterized by a high azymuthal symmetry.
+{Both target rotations are highly axisymmetric, \textit{i.e.} characterised by a high azymuthal symmetry.
 Rotation CR-2082} \edit{has} two {small} ARs, both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg$  {(not identified in the NOAA catalog)}.
@@
 
-{{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively higher densities and temperatures in comparison to the CHs.
-They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 23 and 24}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the {end of the declining} phase of {SC 24}, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious.
+{{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterised by relatively higher densities and temperatures in comparison to the CHs.
+They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 23 and 24}, the {low latitudes of the streamer belt are characterised by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the {end of the declining} phase of {SC 24}, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious.
 This thermodynamic structure of the streamer has been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
@@
 {Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer layers of the equatorial streamer belt, exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
-In both rotations also, type III legs in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I legs in the core of the equatorial streamer.} {A comparison of the results between the two rotations shows that, compared to CR-2082, rotation CR-2208 was characterized by {$\approx 10-20\%$} lower values of the electron density at the coronal base, $\approx 5-30\%$ larger values of density scale height, and {$\approx 15-25\%$} larger values of the electron temperature.}
+In both rotations also, type III legs in the CHs are characterised by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I legs in the core of the equatorial streamer.} {A comparison of the results between the two rotations shows that, compared to CR-2082, rotation CR-2208 was characterised by {$\approx 10-20\%$} lower values of the electron density at the coronal base, $\approx 5-30\%$ larger values of density scale height, and {$\approx 15-25\%$} larger values of the electron temperature.}
 
@@
 They found that while the density {products are} essentially equal, the temperature \edit{based on AIA data} is systematically 8\% larger than the one based on EUVI data, \textit{i.e.} $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$.
-Considering \edit{this error}, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was {characterized by temperatures $\approx 10-15\%$ larger relative to CR-2082} throughout the streamer belt region.
+Considering \edit{this error}, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was {characterised by temperatures $\approx 10-15\%$ larger relative to CR-2082} throughout the streamer belt region.
 As for the electron density products, CR-2208 was found to be $\approx 10-20\%$ less dense than CR-2082 throughout the streamer belt region.
@@
 The sign of the quantity $\phi_c$ depends on that of the conductive flux $F_c$.
-Equations \ref{Fc} and \ref{phi_c} imply that, by definition, down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, {as verified} in Figure \ref{energia_demt}.
+Equations \ref{Fc} and \ref{phi_c} imply that, by definition, down loops (type 0) and up loops (type I and II) are characterised by $\phi_c<0$ and $\phi_c>0$, respectively, {as verified} in Figure \ref{energia_demt}.
 
 {{Adding the} radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}.
-\edit{For} type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$.
+\edit{For} type 0 loops there is a marginal population characterised by the unphysical result $\phi_h<0$.
 As shown by \citet{maccormack_2017}, this affects only the smallest sized loops of the type 0, and it is likely due \edit{to emission out of the instrumental sensitivity range}.
 Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range.
-As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized by $\phi_c<0$.}
+As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterised by $\phi_c<0$.}
 
@@
 {When compared to DEMT results (Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}), the latitude-longitude maps of the AWSoM model for heights $1.065$ and $1.105\,\mrsun$ capture well the denser and hotter equatorial streamer belt surrounded by the less dense and colder CHs.
-Furthermore, for both rotations, the temperature maps show the low latitudes of the equatorial streamer belt to be characterized by lower temperatures than its mid-latitudes, as also seen in the DEMT results.
+Furthermore, for both rotations, the temperature maps show the low latitudes of the equatorial streamer belt to be characterised by lower temperatures than its mid-latitudes, as also seen in the DEMT results.
 The latitude-longitude maps of the AWSoM and DEMT results are shown in the same units and scales, so that a \edit{visual comparison reveals} similar values of electron density and temperature in both models.}
@@
 Using a three-color code, type I, II and III legs are shown in red, magenta and cyan color, respectively.
-This figure \edit{can be compaed} with the corresponding Figure \ref{rpoint_demt} for DEMT results.
+This figure \edit{can be compared} with the corresponding Figure \ref{rpoint_demt} for DEMT results.
 \edit{The AWSoM maps are more densely populated} than those of DEMT.
@@
 {For the two target rotations, Table \ref{tabla_comp} summarizes a quantitative comparative analysis between the results of the DEMT and AWSoM models {based on the results shown in Figures \ref{histos_2082} and \ref{histos_2208}}.
-The DEMT results are expressed as absolute values, while the ASWSoM results are informed as a percentual variation relative to the corresponding result for DEMT.
-\del{The following major results can be drawn.}}
+The DEMT results are expressed as absolute values, while the ASWSoM results are informed as a percentual variation relative to the corresponding result for DEMT.}
 
@@
 Our results for target CR-2082 compare very well with those of \citet{nuevo_2015} and \citet{lloveras_2017} for target CR-2081.
-As our study uses the improved version of the DEMT technique, such comparison provided a consistency \edit{check.} \edit{For both rotations, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.}
+As our study uses the improved version of the DEMT technique, such comparison provided a consistency \edit{check.} \edit{For both rotations, type III field lines in the CHs are characterised by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.}
 

### 2020-03-12 response_to_review_SOLA-D-20-00015_v1.txt
version distribuida a los colaboradores con las correcciones del referi

@@
 This can be seen in Figure 7 of Nuevo et al.
-2013), were they analyzed the small closed up and down loops for two rotations of solar minimum, without placing any limits in the latitude of the footpoints.
-As our main objective here is to be able to analyze progressively outer layers of the streamer belt, we include these limits in the latitude of the footpoints.
+2013), were they analysed the small closed up and down loops for two rotations of solar minimum, without placing any limits in the latitude of the footpoints.
+As our main objective here is to be able to analyse progressively outer layers of the streamer belt, we include these limits in the latitude of the footpoints.
 We edited in full the final paragraph of Section 2.3, as well as the paragraph of Section 3.1 you point out (now split in two, shorter paragraphs).
@@
 
-The discussion section of v1 of the draf includes this sentence (now deleted): "The source of this distinct performance of DEMT when applied to EUVI or AIA data is related to the TRFs of the respective filter sets.
+The discussion section of v1 of the draft includes this sentence (now deleted): "The source of this distinct performance of DEMT when applied to EUVI or AIA data is related to the TRFs of the respective filter sets.
 We are currently implementing an improved LDEM determination algorithm to deal with this issue that will be used in a follow up article." While waiting for your report and preparing V2 of the draft, we successfully implemented the improved version of the code, as a result of which this problem has been solved.
@@
 - Page 26, line 26:
- 'In the streamer belt region we combined the DEMT results and the AWSom magnetic model to infer the energy input phi at the coronal base required to maintain stable coronal loops.
+ 'In the streamer belt region we combined the DEMT results and the AWSoM magnetic model to infer the energy input phi at the coronal base required to maintain stable coronal loops.
 We found characteristic values in the range…'

### 2020-03-12 lloveras_2020_v2.tex
version distribuida a los colaboradores con las correcciones del referi

@@
 
-{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, \textit{i.e.} $E_c(s)=[1/A(s)]\,{\rm d}[A(s)\,F_c(s)]/{\rm d}s$, where $A(s)$ is the transverse area of the magnetic flux tube at position $s$.
+{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, \textit{i.e.} $E_c(s)=[1/A(s)]\,{\rm d}[A(s)\,F_c(s)]/{\rm d}s$, where $A(s)$ is the \edit{cross-sectional} area of the magnetic flux tube at position $s$.
 Under a quiescent solar corona plasma regime, the conductive flux is assumed to be dominated by the electron thermal conduction, described by the usual Spitzer model \citep{spitzer_1962}

### 2020-05-13 R3_para_envio/SOLA-D-20-00015R3.tex
cambios finales del editor: mejoras en xlabel de muchas figuras y lenguaje british seleccionado + otras pequeñas mejoras sugeridas. todo lo subido al solphys en R3_*

--- 2020-03-12 lloveras_2020_v2.tex
@@
 \runningauthor{D.G.~Lloveras~\etal}
-\runningtitle{Comparative Coronal Study of CR-2082 and CR-2208}
+\runningtitle{Comparative Coronal Study of CR 2082 and CR 2208}
 
@@
 \begin{abstract}
-\edit{We carry out a study of the global three-dimensional (3D) structure of the electron density and temperature of the quiescent inner solar corona ($r<1.25\,\mrsun$) by means of tomographic reconstructions and magnetohydrodynamic simulations.
+{We carry out a study of the global three-dimensional (3D) structure of the electron density and temperature of the quiescent inner solar corona ($r<1.25\,\mrsun$) by means of tomographic reconstructions and magnetohydrodynamic simulations.
 We use differential emission measure tomography (DEMT) and the Alfv\'en Wave Solar Model (AWSoM), in their latest versions.
-Two target rotations were selected from the solar minimum between solar cycles (SCs) 23 and 24 and the declining phase of SC 24.
+Two target rotations were selected from the solar minimum between \edit{Solar Cycles} (SCs) 23 and 24 and the declining phase of SC 24.
 We report in quantitative detail on the 3D thermodynamic structure of the core and outer layers of the streamer belt, and of the high latitude coronal holes (CH), as revealed by the DEMT analysis.
 We report on the presence of two types of structures within the streamer belt, loops with temperature decreasing/increasing with height (dubbed down/up loops), as reported first in previous DEMT studies.
-We also estimate the heating energy flux required at the coronal base to keep these structures stable, found to be or order $10^5\,\erg\,\cminvs\,\s^{-1}$, consistently with previous DEMT and spectroscopic studies.
+We also estimate the heating energy flux required at the coronal base to keep these structures stable, found \edit{to be of order} $10^5\,\erg\,\cminvs\,\s^{-1}$, consistently with previous DEMT and spectroscopic studies.
 We discuss how these findings are consistent with coronal dissipation of Alfvén waves.
@@
 We show that the agreement between the products of both techniques is the best so far, with an overall agreement $\lesssim 20\%$, depending on the target rotation and the specific coronal region.
-In its current implementation the ASWsoM model can not reproduce down loops though.
+In its current implementation the ASWsoM model \edit{cannot} reproduce down loops though.
 Also, in the source region of the fast and slow components of the solar wind, the electron density of the AWSoM model increases with latitude, opposite to the trend observed in DEMT reconstructions.}
@@
 
-To study the {3D structure of the quiet-Sun global corona,} SRT has proven to be a powerful tool.
+To study the {3D structure of the quiet-Sun global corona,} \edit{the} SRT has proven to be a powerful tool.
 {In SRT, solar rotation is taken advantage of, so that instruments gather time series of images covering all viewing angles of the solar corona.
-This allows posing an inversion problem to solve for the unknown 3D distribution of specific quantities of the solar corona.
+\edit{This poses} an inversion problem to solve for the unknown 3D distribution of specific quantities of the solar corona.
 Based on extreme ultraviolet (EUV) images, taken in several channels sensitive to different temperatures, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM).
@@
 {A recent review on DEMT was published by \citet{vasquez_2016}.
-The technique is summarized in Section \ref{demt}.}
+The technique is \edit{summarised} in Section \ref{demt}.}
 
-\edit{Non-tomographic studies of localized regions of the quiet-Sun corona have been carried out by means of DEM analysis.
+{Non-tomographic studies of localized regions of the quiet-Sun corona have been carried out by means of DEM analysis.
 \citet{mackovjak_2014} used regularized inversion techniques to study characteristic temperatures in the quiet-Sun.
 \citet{lopez_2019} used a parametric method to study EUV dimmings after coronal mass ejections (CMEs) to estimate the coronal mass evacuated by the events.
-At a global scale, DEM analysis has been used by \citet{morgan_2017} to characterize the evolution of the temperature of the quiet-Sun corona during most of solar cycle (SC) 24.}
+At a global scale, DEM analysis has been used by \citet{morgan_2017} to \edit{characterise} the evolution of the temperature of the quiet-Sun corona during most of \edit{Solar Cycle 24}.}
 
@@
 
-The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space Wea\-ther Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to {1 AU and beyond} \citep{vander_2010, Van2014}.
+The Alfv\'{e}n Wave Solar \edit{Atmosphere} Model (AWSoM) within the Space Wea\-ther Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper \edit{chromosphere to the upper corona and reaching {1 AU and beyond}} \citep{vander_2010, Van2014}.
 {The only data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation.
@@
 
-{Combining the DEMT and AWSoM models, we carry out a detailed \edit{quantitative} analysis of two target rotations.
-We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the SC 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during {the end of the declining} phase of SC 24.
-{In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} {(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG: \citealt{gong}).
-In the case of CR-2208, the DEMT analysis is based \edit{on} data taken} by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} {(SDO), while the AWSoM model uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}
+{Combining the DEMT and AWSoM models, we carry out a detailed {quantitative} analysis of two target rotations.
+We selected Carrington rotation} \edit{(CR)2082} (2009, 05 April through 03 May) during \edit{the minimum between SCs 23 and 24 and CR 2208} (2018, 02 September through 29 September) during {the end of the declining} phase of SC 24.
+{In the case of \edit{CR 2082}, the DEMT analysis is based on data} taken by the {Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the {Solar TErrestrial RElations Observatory} {(STEREO), while \edit{AWSoM} uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG: \citealt{gong}).
+In the case of \edit{CR 2208}, the DEMT analysis is based {on} data taken} by the {Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the {Solar Dynamics Observatory} {(SDO), while \edit{AWSoM} uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}
 
-Section \ref{demt} and \ref{awsom} {summarize the DEMT technique and the AWSoM model, respectively.} Section \ref{trace} {details} the method used to trace {the DEMT} results along the field lines of the magnetic model.
+Section \ref{demt} and \ref{awsom} {\edit{summarise} the DEMT technique and the AWSoM model, respectively.} Section \ref{trace} {details} the method used to trace {the DEMT} results along the field lines of the magnetic model.
 Section \ref{energia} details {the method that allows determination of the energy input flux at the coronal base.} In Section \ref{demt_res} the quantitative {detailed DEMT analysis of both target rotations is shown,} and in Section \ref{awsom_res} the AWSoM and DEMT results are compared.
-{Finally, Section} \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.
+{Finally, Section} \ref{discu} \edit{summarises} and discusses the main conclusions of this analysis, and anticipates further planned work.
 
@@
 
-{As detailed in Section \ref{intro}, rotations CR-2082 and CR-2208 were selected to carry out DEMT reconstructions, based on data taken by the STEREO/EUVI-B and SDO/AIA instruments, respectively.} The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package.
-\edit{In the case of EUVI data, stray-light contamination is removed by deconvolution of the point spread function (PSF), carefully determined for each detector by \citet{shearer_2012}.
-In the case of AIA data, we have not yet implemented such a procedure as we were not aware of reliable determinations of their PSF, and we also understand that stray light contamination is expected to be less important for this instrument.
+{As detailed in Section \ref{intro}, rotations \edit{CR 2082} and \edit{CR 2208} were selected to carry out DEMT reconstructions, based on data taken by the STEREO/EUVI-B and SDO/AIA instruments, respectively.} The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the \edit{SolarSoftware} package.
+{In the case of EUVI data, stray-light contamination is removed by deconvolution of the point spread function (PSF), carefully determined for each detector by \citet{shearer_2012}.
+In the case of AIA data, we have not yet implemented such a procedure as we were not aware of reliable determinations of their PSF, and we also understand that \edit{stray-light} contamination is expected to be less important for this instrument.
 A recent study by \citet{saqri_2020} indicates that the effect is noticeable in DEM analysis of coronal holes (CHs).
@@
 
-{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we {opt} to only use off-limb data.
-In this way, the smallest scale and brighter coronal features seen on disk (most typically in the 171\AA\ band) are not included.
+{While in all previous DEMT studies \edit{full-disc data were used} to perform tomography, in this work we {opt} to only use off-limb data.
+In this way, the smallest scale and brighter coronal features seen on \edit{disc} (most typically in the 171\AA\ band) are not included.
 This has two implications.
-Firstly, the fast dynamics that typically characterizes those structures is absent from the data.
+Firstly, the fast dynamics that typically \edit{characterises} those structures is absent from the data.
 Secondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume.
@@
 In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude.
-Also new to the present work, is the implementation of an expanded 3D regularization scheme, which adds to the previous scheme a finite difference matrix operator to approximate radial derivatives.
+\edit{Also, new to the present work is} the implementation of an expanded 3D regularization scheme, which adds to the previous scheme a finite difference matrix operator to approximate radial derivatives.
 In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions.
@@
 The main product of the technique is the local DEM (LDEM) at each voxel, a measure of the temperature distribution of the plasma contained in it.
-We summarize next the main aspects of DEMT required for the analysis of this work.}
+We \edit{summarise} next the main aspects of DEMT required for the analysis of this work.}
 
@@
 As a result, the 3D distribution of the so called \emph{filter band emissivity} (FBE) is determined for each band separately.
-The FBE, {an emissivity-type quantity}, is defined as the wavelength integral of the coronal EUV spectral emissivity and the telescope's passband function of each EUV channel.
+The FBE, {an emissivity-type quantity}, is defined as the wavelength integral of the coronal EUV spectral emissivity and the \edit{telescope} passband function of each EUV channel.
 Line-of-sight (LOS) integration of the FBE provides synthetic images that can be quantitatively compared to the real data in the time series.
-To find the FBE, the tomographic problem is posed as a global optimization problem in which the quadratic norm of the difference between all {pairs of synthetic and real images is minimized.}
+To find the FBE, the tomographic problem is posed as a global \edit{optimisation} problem in which the quadratic norm of the difference between all {pairs of synthetic and real images is \edit{minimised}.}
 
 Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}.
-These non-reconstructed voxels are indicated {in black color in the latitude-longitude (Carrington) maps of DEMT} results in Section \ref{resu}.
+These non-reconstructed voxels are indicated {in black \edit{colour} in the latitude-longitude (Carrington) maps of DEMT} results in Section \ref{resu}.
 
-{In a second step, the FBE values obtained for all bands in each voxel {of the tomographic grid are used to constrain the determination of the local-DEM (LDEM) which, as described in Section \ref{intro}, describes the temperature distribution of the plasma within the individual voxel.} Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}
+{In a second step, the FBE values obtained for all bands in each voxel {of the tomographic grid are used to constrain the determination of the \edit{local DEM} (LDEM) which, as described in Section \ref{intro}, describes the temperature distribution of the plasma within the individual voxel.} Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}
 
@@
 {where $K$ is the number EUV bands, and $\TRF^{(k)}$ is the \emph{temperature response function} of the $k$-th detector.
-In this work, the TRFs are computed based on the (known) channel’s passband times the coronal emissivity at that temperature (normalized by the squared electron density).
+In this work, the TRFs are computed based on the (known) \edit{channel} passband times the coronal emissivity at that temperature (\edit{normalised} by the squared electron density).
 The emissivity model used here is provided by the latest version of the CHIANTI atomic database and plasma emission model \citep{delzanna_2015,landi_2013}.}
 
-{In this work,} data from three EUV bands {was used:} 171, 193 and {211 \AA\ in} {the} case of AIA, and 171, 195 and {284 \AA\ bands} in {the} case of EUVI.
+{In this work,} data from three EUV bands {\edit{were} used:} 171, 193 and {211 \AA\ in} {the} case of AIA, and 171, 195 and {284 \AA\ } in {the} case of EUVI.
 When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict {the FBEs \citep{nuevo_2015}}.
@@
 
-\edit{As the LDEM describes the temperature distribution of the plasma in a specific voxel, it does not deal with different large scale structures, as it may be the case for the DEM describing the plasma along a full LOS.
+{As the LDEM describes the temperature distribution of the plasma in a specific voxel, it does not deal with different large scale structures, as it may be the case for the DEM describing the plasma along a full LOS.
 As a result, LDEMs are usually successfully modeled with simpler profiles (such as Gaussian) than those returned by DEM studies constrained by LOS-integrated intensities.
 Parametric techniques are also used for DEM analysis of narrowband images, such as in the works by \citet{aschwanden_2011,plowman_2013,delzanna_2013}.
-Other methods applied to DEM analysis of narrow band images include Monte Carlo Markov Chain (MCMC) techniques \citep{schmeltz_2016}, regularized inversion techniques \citep{hannah_2012}, and iterative solvers \citep{pickering_2019,morgan_2019} that use the known TRFs of all filters as a functional base.
-The latter work in particular, introduced a fast iterative solver named SITES, which can easily be adapted for its use in DEMT.
+Other methods applied to DEM analysis of narrow band images include Monte Carlo Markov \edit{chain} (MCMC) techniques \citep{schmeltz_2016}, regularized inversion techniques \citep{hannah_2012}, and iterative solvers \citep{pickering_2019,morgan_2019} that use the known TRFs of all filters as a functional base.
+The latter work in particular, introduced a fast iterative solver named \edit{Solar Iterative Temperature Emission Solver}, which can easily be adapted for its use in DEMT.
 We will explore this in the future and compare results with those provided by our parametric technique.}
@@
 \noindent 
-{being the} \edit{average absolute relative difference} between the tomographic and the synthetic FBEs.
+{being the} \edit{absolute relative difference} between the tomographic and the synthetic FBEs.
 {The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.} {For a full description of the {DEMT technique} we refer the reader to \citet{frazin_2009}.}
@@
 
-{AWSoM is a three-temperature}, MHD model of the solar corona and inner heliosphere which provides the 3D distribution of density and temperatures as well as the 3D magnetic structure and velocity of the solar wind.
-In this work, we use AWSoM model simulated results below 1.25 $\mrsun$ to correspond to the DEMT analysis region.
+\edit{AWSoM is a three-temperature (accounts for anisotropic, parallel and perpendicular, proton temperatures and isotropic electron temperatures)}, MHD model of the solar corona and inner heliosphere which provides the 3D distribution of density \edit{and temperatures, as} well as the 3D magnetic structure and velocity of the solar wind.
+In this work, we use \edit{AWSoM} simulated results below 1.25 $\mrsun$ to correspond to the DEMT analysis region.
 
@@
 
-{The model accounts} for both collisional and collision-less electron heat conduction and does not use ad-hoc heating functions.
-The extended MHD equations including radiative cooling, heat conduction and wave turbulence within AWSoM \citep{Van2014} are solved using the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme.
+{The model accounts} for both collisional and \edit{collisionless} electron heat conduction and does not use ad-hoc heating functions.
+The extended MHD equations including radiative cooling, heat conduction and wave turbulence within AWSoM \citep{Van2014} are solved using the \edit{Block-Adaptive Tree Solarwind Roe-type Upwind Scheme} (BATS-R-US, \citealp{Pow1999, Tot2012}).
 
 {In a previous} version of the model, the cascade time of the major wave was used to determine the wave damping rate \citep{Cha2011, Van2014}.
-{In its present version, the \edit{energy partitioning is improved}} by using the Alfv\'{e}n wave number associated with the damping rate as determined by the critical balance condition, which uses the cascade time of the minor wave \citep{Lit2007}.
+{In its present version, the {energy partitioning is improved}} by using the Alfv\'{e}n wave number associated with the damping rate as determined by the critical balance condition, which uses the cascade time of the minor wave \citep{Lit2007}.
 This leads to more electron heating and less solar wind acceleration \citep{Van2019b}.
@@
 The inner boundary of AWSoM is located at the base of the transition region (at $\approx$1.0\,$\mrsun$).
-In reality, the thin {transition region (TR)} has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses.
+In reality, the thin {transition region (TR)} has steep gradients in temperature and density as a result of the balance between coronal heating, heat \edit{conduction, and radiative} losses.
 To resolve these gradients in a global model would require excessive numerical resources.
-As described in \citet{Lio2009} and \citet{Sok2013}{, the TR is artificially \edit{broadened} to be resolved with a} finest grid resolution of 0.001\,$\mrsun$.
-To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot} =2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K\edit{, where the subscripts represents electrons and ions}.
+As described in \citet{Lio2009} and \citet{Sok2013}{, the TR is artificially {broadened} to be resolved with a} finest grid resolution of 0.001\,$\mrsun$.
+To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot} =2\times10^{17}$\,m$^{-3}$\edit{, corresponding} to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K{, where the \edit{subscripts represent} electrons and ions}.
 The upper chromosphere is required to extend radially for the density to fall rapidly to correct (lower) values \citep{Lio2009}.
 At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region.
-Since the broadening of the transition region pushes the corona outwards, {the AWSoM model achieves coronal conditions at height $\approx 1.05\,\mrsun$, below which results can not then be compared to coronal tomographic reconstructions.}
+Since the broadening of the transition region pushes the corona outwards, {the AWSoM model achieves coronal conditions \edit{at a height} $\approx 1.05\,\mrsun$, below which results \edit{cannot} then be compared to coronal tomographic reconstructions.}
 
@@
 The source surface is taken to be at 2.5 $\mrsun$.
-GONG provides synoptic full-disk surface maps of the radial magnetic field component of the Sun.
+GONG provides synoptic \edit{full-disc} surface maps of the radial magnetic field component of the Sun.
 However, since the polar regions are not well observed from the ecliptic, GONG estimates the polar fields by fitting a polynomial to neighboring observed latitudes, which might lead to inaccuracies.
-An improvement over these maps is provided by the Air Force Data Assimilation Photospheric Flux Transport (ADAPT) model \citep{Wor2000}, which creates synchronic-synoptic maps by incorporating supergranulation, meridional circulation, and differential rotation.
+An improvement over these maps is provided by the \edit{ADAPT} model \citep{Wor2000}, which creates synchronic-synoptic maps by incorporating supergranulation, meridional circulation, and differential rotation.
 These maps provide a physics-based description of the unobserved polar magnetic fields \citep{Arg2010, Hen2012}.
-In this work, we use the GONG synoptic map as input for CR-2082 (ADAPT-GONG maps are unavailable for CR-2082) and the ADAPT-GONG global magnetic field map for CR-2208.
-{Based on results from previous efforts, for CR-2082} the magnetic field from the GONG map is scaled up by a factor of 1.85 {for weak fields ($B_r< 5\,\rm{G}$), while no modification is applied in the case of} the ADAPT-GONG map for CR-2208.
+In this work, we use the GONG synoptic map as input for \edit{CR 2082} (ADAPT-GONG maps are unavailable for \edit{CR 2082}) and the ADAPT-GONG global magnetic field map for \edit{CR 2208}.
+{Based on results from previous efforts, for \edit{CR 2082}} the magnetic field from the GONG map is scaled up by a factor of 1.85 {for weak fields ($B_r< 5\,\rm{G}$), while no modification is applied in the case of} the ADAPT-GONG map for \edit{CR 2208}.
 The AWSoM steady-state simulation set-up and input parameters for both rotations are described below.
@@
 To account for the energy partitioning between electrons and protons, based on \citet{Cha2011}, we set the stochastic heating exponent {equal to} 0.21 and the amplitude equal to {0.18, for both} rotations.
-The boundary condition for Alfv\'{e}n wave energy is given by the {poynting flux ($S_{A}$)} of the outgoing {wave, $({S_{A}/}{B})_{\odot} = 1.1\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ and $1.0\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ for CR-2082 and CR-2208, respectively, with $B_{\odot}$ being the field} strength at the inner boundary.
-The correlation length of the Alfv\'{e}n waves is set {to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$m\,$\sqrt{T}$}\edit{, where $L_{\perp}$ is transverse to the magnetic field direction.}
+The boundary condition for Alfv\'{e}n wave energy is given by the {poynting flux \edit{$S_{A}$}} of the outgoing {wave, $({S_{A}/}{B})_{\odot} = 1.1\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ and $1.0\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ for \edit{CR 2082} and \edit{CR 2208}, respectively, with $B_{\odot}$ being the field} strength at the inner boundary.
+The correlation length of the Alfv\'{e}n waves is set {to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$m\,$\sqrt{T}$}{, where $L_{\perp}$ is transverse to the magnetic field direction.}
 
 {The computational domain of the solar corona} extends from 1 to {$24\,\mrsun$}.
-\edit{The spherical grid has an adaptive grid that has fine resolution near the Sun, and increases outward} with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates.
-The Adaptive Mesh refinement (AMR) resolves the angular cell size to $1.4\mdeg$ between $1 - 1.7\,\mrsun$ and to $2.8\mdeg$ outside this radius range.
-The solar corona component uses about 3 million cells on $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082.
+\edit{The adaptive spherical grid has a finer resolution near the Sun}, and increases outward with the z-axis aligned with the rotation axis in \edit{heliographic rotation} coordinates.
+The \edit{adaptive mesh refinement} (AMR) resolves the angular cell size to $1.4\mdeg$ between $1 - 1.7\,\mrsun$ and to $2.8\mdeg$ outside this radius range.
+The solar corona component uses about 3 million cells on $6 \times 8 \times 8$ grid blocks (for \edit{CR 2208}) and $6 \times 4 \times 4$ grid blocks for \edit{CR 2082}.
 Local time stepping is used to speed up the steady state convergence.
-\edit{The AWSoM simulation of the solar corona for solar minimum conditions represented by CR-2082 and CR-2208 are compared to the DEMT in the results section.}
+{The AWSoM simulation of the solar corona for solar minimum conditions represented by \edit{CR 2082} and \edit{CR 2208} are compared to the DEMT in the results section.}
 
@@
 {For analysis purposes, {the traced magnetic field lines are classified as open or closed according to their full geometry.
-Each closed field} line is further classified as ``small" or ``large", according to its coronal length $L$ being {respectively smaller or larger than the median value of the whole population, which is ${\rm Md}(L)\approx 0.5\,\mrsun$ for both rotations.} Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (\textit{i.e.} their location at $r=1\,\mrsun$) to its apex (\textit{i.e.}, the location of maximum height).}
+Each closed field} line is further classified as ``small" or ``large", according to its coronal length $L$ being {respectively smaller or larger than the median value of the whole population, which is ${\rm Md}(L)\approx 0.5\,\mrsun$ for both rotations.} Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints ({i.e.} their location at $r=1\,\mrsun$) to its apex ({i.e.} the location of maximum height).}
 
-At this {stage, DEMT and AWSoM products} \edit{are} traced along open and closed magnetic field lines.
-Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one).
+At this {stage, DEMT and AWSoM products} {are} traced along open and closed magnetic field lines.
+Once the field line geometry is computed \edit{with} high spatial resolution, only one sample point per tomographic cell is kept (the median one).
 As a result, for each field line one data point per tomographic cell {is obtained.
@@
 For each open field line and {for each closed field leg}, an exponential fit {was applied} to the electron density {data points} and a linear fit applied to the electron temperature {data points}.
-\edit{For DEMT the data points used are} $\sqravgN(r)$ and $\Tm(r)$, and in case of {the AWSoM models} the data points used \edit{are} $\Ne(r)$ and $\Te(r)$.
+{For DEMT, the data points used are} $\sqravgN(r)$ and $\Tm(r)$, and in case of {the AWSoM models} the data points used {are} $\Ne(r)$ and $\Te(r)$.
 The exponential and linear fit equations are described by
@@
 In the electron temperature fit, $a\,[\MK/\mrsun]$ is the slope and $T_0\,[\MK]$ is the electron temperature at the footpoint of the loop.
-The slope $a$ estimates the radial gradient of the electron temperature along the loop, which we denote as $a = \dr\Tm$ hereafter, \edit{with} $\dr\equiv\er\cdot\nabla$ \edit{being} the radial derivative operator \edit{and} $\er$ the heliocentric radial unit vector.
+The slope $a$ estimates the radial gradient of the electron temperature along the loop, which we denote as $a = \dr\Tm$ hereafter, {with} $\dr\equiv\er\cdot\nabla$ {being} the radial derivative operator {and} $\er$ the heliocentric radial unit vector.
 
 In the case of the electron density, the fitted function corresponds to the isothermal hydrostatic equilibrium solution, allowing for variation of the solar gravitational acceleration with height.
-This choice of function provides a straightforward means to directly \edit{compare the observed} coronal thermodynamical state with the hydrostatic solution.
+This choice of function provides a straightforward means to directly {compare the observed} coronal thermodynamical state with the hydrostatic solution.
 
-{Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported the presence of down loops.
+{Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as up/down loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported the presence of down loops.
 As speculated by the authors of those works, down loops can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop.
@@
 We then select field lines for which the temperature {is significantly correlated with height} by requiring $|\rhoTr| > 0.5$.
-{To test the goodness of the fit we perform a chi-squared test \citep{recipes} considering the uncertainty of the DEMT data, selecting legs for which the fit matches the data with a 90\% confidence level.} In this way, legs for which the DEMT temperature does not show a significant {correlation} with height, or the linear fit to temperature is \edit{weak}, are {excluded from the} analysis.
+{To test the goodness of the fit we perform a chi-squared test \citep{recipes} considering the uncertainty of the DEMT data, selecting legs for which the fit matches the data with a 90\% confidence level.} In this way, legs for which the DEMT temperature does not show a significant {correlation} with height, or the linear fit to temperature is {weak}, are {excluded from the} analysis.
 {The test is also applied to the density-height data points, to ensure the trend is reasonably represented by the exponential fit.} Finally, selected legs are then classified as up or down according to $\dr\Tm > 0$ or $\dr\Tm < 0$, respectively.
 The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg.
-{The chi-squared test to evaluate the quality of the \edit{fit} considers the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$.} In summary, \edit{a selected leg must meet three conditions:}
+{The chi-squared test to evaluate the quality of the {fit} considers the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$.} In summary, {a selected leg must meet three conditions:}
 
@@
 
-{To characterize the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model.
+{To \edit{characterise} the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model.
 Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types:}
@@
 \begin{itemize}
-\item Type 0: closed-small-down with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
-\item Type I: closed-small-up with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
-\item Type II: closed-large-up with footpoints in the range $|{\rm latitude}|>40\mdeg$. 
+\item Type 0: \edit{closed-small down} with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
+\item Type I: \edit{closed-small up} with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
+\item Type II: \edit{closed-large up} with footpoints in the range $|{\rm latitude}|>40\mdeg$. 
 \item Type III: open with footpoint in the range $|{\rm latitude}|>60\mdeg$.
@@
 
-\edit{In the case of closed-small field lines, the population of down and up legs becomes comparable for CR-2082, so we classify them into the two complementary classes of legs of type 0 (down) and legs of type I (up).
+{In the case of closed-small field lines, the population of down and up legs becomes comparable for \edit{CR 2082}, so we classify them into the two complementary classes of legs of type 0 (down) and legs of type I (up).
 In the case of closed-large field lines, down legs are $\lesssim 15\%$ of the population for both rotations.
@@
 On the other hand, the inclusion of latitude limits for the footpoints in the classification of legs from type 0 through III is purposely set to study the streamer belt in progressively outer layers, as well as to separate the field lines of the high latitude CHs (legs of type III).
-In Section \ref{resu}, the results of both the DEMT and AWSoM models in the four classes of legs are statistically analysed.}
+In Section \ref{resu}, the results of both the \edit{DEMT reconstruction and AWSoM model} in the four classes of legs are statistically analysed.}
 
@@
 
-{Consider} a static energy balance for each magnetic flux tube, {in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated {by a} coronal heating power ($E_h$) \citep{aschwanden_2004}:
+{Consider} a static energy balance for each magnetic flux tube, {in which the dominating losses of} radiative power $E_r$ and thermal conduction power $E_c$ are compensated {by a} coronal heating power $E_h$ \citep{aschwanden_2004}:
 
@@
 \noindent
-where $s$ is the position along {the flux tube} and the {power quantities} are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.
+where $s$ is the position along {the flux tube} and \edit{these} quantities are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.
 
-{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, \textit{i.e.} $E_c(s)=[1/A(s)]\,{\rm d}[A(s)\,F_c(s)]/{\rm d}s$, where $A(s)$ is the transverse area of the magnetic flux tube at position $s$.
+{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, {i.e.} $E_c(s)=[1/A(s)]\,{\rm d}[A(s)\,F_c(s)]/{\rm d}s$, where $A(s)$ is the {cross-sectional} area of the magnetic flux tube at position $s$.
 Under a quiescent solar corona plasma regime, the conductive flux is assumed to be dominated by the electron thermal conduction, described by the usual Spitzer model \citep{spitzer_1962}
@@
 \noindent 
-{where $L$ is the length of the loop, and $B_0$ and $B_L$ are the values of the magnetic field at the footpoint locations of the loop in the coronal base, namely $s=0$ and $s=L$.} {\edit{For} any given field line, all quantities in these two expressions can be computed {from the DEMT results traced along field lines, and the AWSoM magnetic field model,} through Equations \ref{Fc}-\ref{Er}.
-Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to maintain a stable coronal structure.}
+{where $L$ is the length of the loop, and $B_0$ and $B_L$ are the values of the magnetic field at the \edit{footpoint} of the loop in the coronal base, namely $s=0$ and $s=L$.} {{For} any given field line, all quantities in these two expressions can be computed {from the DEMT results traced along field lines, \edit{of} the AWSoM magnetic field model,} through Equations \ref{Fc}-\ref{Er}.
+Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal \edit{field line} to maintain a stable coronal structure.}
 
@@
 
-{As described in Section \ref{demt}, we carried out DEMT reconstructions of the coronal structure for rotations CR-2082 and CR-2208 using STEREO/EUVI and SDO/AIA data, respectively.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared ($\sqravgN$) and the electron mean temperature ($\Tm$) were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}{, and the measure $R$ was calculated by means of Equation \ref{R}.}}
+{As described in Section \ref{demt}, we carried out DEMT reconstructions of the coronal structure for rotations \edit{CR 2082} and \edit{CR 2208} using STEREO/EUVI and SDO/AIA data, respectively.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared $\sqravgN$ and the electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid \edit{using} Equations \ref{momento1} and \ref{momento2}{, and the measure $R$ was calculated \edit{with} Equation \ref{R}.}}
 
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
-\caption{Carrington maps of DEMT {products $\sqravgN$} (left panels) and $\Tm$ (right panels) for CR-2082.
-Top, middle and bottom panels show the results at three heliocentric heights, $1.025$, $1.065$ and $1.105\,\mrsun$ respectively.
+\includegraphics[width=0.495\textwidth]{map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun2.pdf}
+\includegraphics[width=0.495\textwidth]{map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun2.pdf}
+\includegraphics[width=0.495\textwidth]{map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun2.pdf}
+\includegraphics[width=0.495\textwidth]{map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun2.pdf}
+\includegraphics[width=0.495\textwidth]{map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun2.pdf}
+\includegraphics[width=0.495\textwidth]{map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun2.pdf}
+\caption{Carrington maps of DEMT {products $\sqravgN$} (left panels) and $\Tm$ (right panels) for \edit{CR 2082}.
+Top, \edit{middle, and} bottom panels show the results at three heliocentric heights, $1.025$, \edit{$1.065$, and} $1.105\,\mrsun$ respectively.
 Black voxels correspond to non-reconstructed regions (see text in Section \ref{demt_res}) and thick-black curves indicate the open/closed boundaries.}
@@
 
-{Both target rotations are highly axisymmetric, \textit{i.e.} characterised by a high azymuthal symmetry.
-Rotation CR-2082} \edit{has} two {small} ARs, both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg$  {(not identified in the NOAA catalog)}.
-{Rotation CR-2208} \edit{has} two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$ {(NOAA 12722, 12721)}.}
+{Both target rotations are highly axisymmetric, {i.e.} characterised by a high azymuthal symmetry.
+Rotation \edit{CR 2082}} {has} two {small} ARs, both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg$  {(not identified in the NOAA catalog)}.
+{Rotation \edit{CR 2208}} {has} two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$ {(NOAA 12722, 12721)}.}
 
-{The magnetically open and closed regions of the AWSoM model are associated \edit{with CHs} and the equatorial streamer belt, respectively.
-The {location of the} open/closed boundaries derived from the respective AWSoM model quite accurately matches {the regions of the DEMT maps, which exhibit the strongest latitudinal gradient of both the electron density and temperature.}}
+{The magnetically open and closed regions of the AWSoM model are associated {with CHs} and the equatorial streamer belt, respectively.
+The {location of the} open/closed boundaries derived from \edit{the AWSoM} model quite accurately matches {the regions of the DEMT maps, which exhibit the strongest latitudinal gradient of both the electron density and temperature.}}
 
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1025_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1105_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1105_Rsun.pdf}
-\caption{Same as Figure \ref{carmaps_demt_2082} but for CR-2208.}
+\includegraphics[width=0.495\textwidth]{map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1025_Rsun2.pdf}
+\includegraphics[width=0.495\textwidth]{map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1025_Rsun2.pdf}
+\includegraphics[width=0.495\textwidth]{map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1065_Rsun2.pdf}
+\includegraphics[width=0.495\textwidth]{map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1065_Rsun2.pdf}
+\includegraphics[width=0.495\textwidth]{map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1105_Rsun2.pdf}
+\includegraphics[width=0.495\textwidth]{map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1105_Rsun2.pdf}
+\caption{Same as Figure \ref{carmaps_demt_2082} but for \edit{CR 2208}.}
 \label{carmaps_demt_2208}
@@
 {{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterised by relatively higher densities and temperatures in comparison to the CHs.
-They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 23 and 24}, the {low latitudes of the streamer belt are characterised by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the {end of the declining} phase of {SC 24}, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious.
+They also show that the streamer belt region of \edit{CR 2082} was denser and colder than  that of \edit{CR 2208}.} In the case of \edit{CR 2082}, which belongs to the deep minimum epoch between {SCs 23 and 24}, the {low latitudes of the streamer belt are characterised by \edit{an electron temperature lower} than in its mid-latitudes.} A similar \edit{behaviour} is seen in \edit{CR 2208}, belonging to the {end of the declining} phase of SC \edit{24 but, having a somewhat less axisymmetric structure, this} characteristic is not so obvious.
 This thermodynamic structure of the streamer has been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
 
-Latitude-longitude maps of the score $R$ defined by Equation \ref{R} show that \edit{the agreement between the tomographic and synthetic FBEs is 5\% or better in more than 90\% of the reconstructed coronal volume (i.e.
+Latitude-longitude maps of the score $R$ defined by Equation \ref{R} show that {the agreement between the tomographic and synthetic FBEs is 5\% or better in more than 90\% of the reconstructed coronal volume (i.e.
 where FBEs are non zero), and of order 10\% in the rest of the volume.
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
-%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
-%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
-%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
-%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_conajuste_doble_error_Rpoint-map.pdf}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_conajuste_doble_error_Rpoint-map.pdf}
-%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
-%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_full_conajuste_doble_errorhighpoints.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_full_conajuste_doble_errorhighpoints.eps}
-\caption{{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR-2082 (left) and CR-2208 (right).
-\edit{Middle panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-{The location of} type 0, I, II and III legs {is shown} in blue, \edit{orange, red, and cyan} color, respectively.} \edit{Bottom panels: frequency histograms of the latitude of the four types of legs of the middle panel.}}
+\includegraphics[width=0.495\textwidth,clip=]{Grispoint_2082_demt_paper_test_Rpoint-map222.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{Grispoint_2208_demt_paper_test_Rpoint-map222.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_doble_error_Rpoint-map222.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_doble_error_Rpoint-map222.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{histo_cr2082_full_conajuste_doble_errorhighpoints2.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{histo_cr2208_full_conajuste_doble_errorhighpoints2.pdf}
+\caption{{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey \edit{colour}) and closed (black \edit{colour}) traced field line legs for which criterion (i) of Section \ref{trace} is met, \edit{for} \edit{CR 2082} (left) and \edit{CR 2208} (right).
+{Middle panels}: latitude-longitude location of the subset for which \edit{both} criteria (ii) and (iii) of Section \ref{trace} are met.
+{The location of} type 0, I, II, and III legs {is shown} in blue, {orange, red, and cyan} \edit{colour}, respectively.} {Bottom panels: frequency histograms of the latitude of the four types of legs of the middle panel.}}
 \label{rpoint_demt}
@@
 For both rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met.
-Open legs are indicated in gray color and closed ones in black color.
-Considering the DEMT data points and the resulting fits along each leg, the \edit{middle} panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a four-color code, type 0, I, II and III legs are shown in blue, \edit{orange, red, and cyan} color, respectively.
-\edit{The bottom panels show histograms of the latitude distribution of the legs of the middle panel, using the same color code.} Of the {$\approx 44000$} legs selected for CR-2082, 20\% are type 0, 31\% are type I, 23\% are type II and 26\% type III.
-On the other hand, of the \edit{$\approx 50000$} legs selected for CR-2208, 10\% are type 0, \edit{38}\% are type I, \edit{27}\% are type II and \edit{25}\% type III.
+Open legs are indicated in \edit{grey} \edit{colour} and closed ones in black \edit{colour}.
+Considering the DEMT data points and the resulting fits along each leg, the {middle} panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
+Using a four-\edit{colour} code, type 0, I, II, and III legs are shown in blue, {orange, red, and cyan} \edit{colour}, respectively.
+{The bottom panels show histograms of the latitude distribution of the legs of the middle panel, using the same \edit{colour} code.} Of the {$\approx 44000$} legs selected for \edit{CR 2082}, 20\% are type 0, 31\% are type I, 23\% are type II, and 26\% type III.
+On the other hand, of the {$\approx 50000$} legs selected for \edit{CR 2208}, 10\% are type 0, {38}\% are type I, {27}\% are type II and {25}\% type III.
 
-\edit{For both rotations, the population of type 0 (small-closed-down) legs peaks at the core of the streamer belt, around the equator in the case of CR-2082, and towards the southern hemisphere in the case of CR-2208.} This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the solar minimum between {SCs 23 and 24} by \citet{nuevo_2013}.
+{For both rotations, the population of type 0 (\edit{small-closed down}) legs peaks at the core of the streamer belt, around the equator in the case of \edit{CR 2082}, and towards the southern hemisphere in the case of \edit{CR 2208}.} This kind of structure was originally found by \citet{huang_2012} and their existence was shown to be anti-correlated with the solar activity level around the solar minimum between {SCs 23 and 24} by \citet{nuevo_2013}.
 Later on, \citet{lloveras_2017} showed {that} equatorial down loops in streamers were also to be found in the deep minimum between SCs {23 and 24}.
 Here, we verify the existence of this type of structure for the two rotations.
-The relatively smaller population of down legs seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}.
-\edit{Type I (small-closed-up) legs are present at all latitudes within the streamer belt.
-Their population peaks in the mid-latitudes of both hemispheres for CR-2082, and in the mid-latitudes of the northern hemisphere for CR-2208.
-The latitude distribution of legs of type 0 and I in CR-2082 is consistent to the distribution of down and up loops of CR-2081 in the analysis by \citet{nuevo_2013}, which did not place any limits on the latitude location of the analysed structures.}
+The relatively smaller population of down legs seen in \edit{CR 2208}, as compared to \edit{CR 2082}, is consistent with the aforementioned results by \citet{nuevo_2013}.
+{Type I (small-closed-up) legs are present at all latitudes within the streamer belt.
+Their population peaks in the mid-latitudes of both hemispheres for \edit{CR 2082}, and in the mid-latitudes of the northern hemisphere for \edit{CR 2208}.
+The latitude distribution of legs of type 0 and I in \edit{CR 2082} is consistent to the distribution of down and up loops of CR 2081 in the analysis by \citet{nuevo_2013}, which did not place any limits on the latitude location of the analysed structures.}
 
-\edit{Type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt (the requirement of footpoints located beyond mid-latitudes was included precisely to select this kind of loop).
+{Type II (large up) legs are mostly very large \edit{transequatorial} field lines forming the envelope of the streamer belt (the requirement of footpoints located beyond mid-latitudes was included precisely to select this kind of loop).
 Finally, type III (open) legs populate the high latitude CHs.}
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2082_full_doble_errortriple_gradt.eps}
-\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_full_doble_errortriple_gradt.eps}
-\caption{Frequency histograms of the temperature radial gradient for {the four types of legs} in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
+\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{histo_cr2082_full_doble_errortriple_gradt.pdf}
+\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{histo_cr2208_full_doble_errortriple_gradt.pdf}
+\caption{Frequency histograms of the temperature radial gradient for {the four types of legs} in Figure \ref{rpoint_demt} (using the same \edit{colour} code) for \edit{CR 2082} (left panel) and \edit{CR 2208} (right panel).}
 \label{gradt_demt}
@@
 
-Figure \ref{gradt_demt} shows frequency histograms of $\dr\Tm$ for legs of type 0, I, II and III.
+Figure \ref{gradt_demt} shows frequency histograms of $\dr\Tm$ for legs of type 0, I, II, and III.
 The lack of population around values close to zero is due to the requirement $|\rhoTr| > 0.5$ which discards quasi-isothermal legs.
-For both rotations, the median value of the temperature radial gradient is \edit{${\rm Md}\left(\dr\Tm\right) \approx -2.2$, $+2.3$, $+2.4$ and $+2.3\,\MK/\mrsun$, for legs of type 0, I, II and III, respectively.}
+For both rotations, the median value of the temperature radial gradient is {${\rm Md}\left(\dr\Tm\right) \approx -2.2$, $+2.3$, $+2.4$, and $+2.3\,\MK/\mrsun$, for legs of type 0, I, II, and III, respectively.}
 
@@
 \begin{center}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_conajustene_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_conajustelambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_conajusteTm.eps}
-\caption{{Statistical distribution of {DEMT results for rotations CR-2082 (blue) and CR-2208 (red)} traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}.
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_2208_fulldemt_streamer_down_ne_1055_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_2208_fulldemt_streamer_down_lambda_n_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_2208_fulldemt_streamer_down_Tm_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_2208_fulldemt_streamer_up_ne_1055_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_2208_fulldemt_streamer_up_lambda_n_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_2208_fulldemt_streamer_up_Tm_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_2208_fulldemt_bound_up_ne_1055_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_2208_fulldemt_bound_up_lambda_n_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_2208_fulldemt_bound_up_Tm_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_2208_fulldemt_CH_up_conajustene_1055_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_2208_fulldemt_CH_up_conajustelambda_n_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_2208_fulldemt_CH_up_conajusteTm_2.pdf}
+\caption{{Statistical distribution of {DEMT results for rotations \edit{CR 2082} (blue) and \edit{CR 2208} (red)} traced along legs of type 0, I, II, and III (from top to bottom), as defined in Section \ref{trace}.
 From left to right: {electron density $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$,} electron density scale height $\lN$, {and loop-averaged temperature $\aTm$.
@@
 From top to bottom {results are shown for} type 0 to type III {legs}{, respectively}.
-From left to right the panels show the statistical distribution of the electron density value $\NCB \equiv \sqravgN(r=1.055)$, \edit{the scale height $\lN$, and the height-averaged (along the leg) electron temperature $\aTm$}, {with the median value $m$ indicated in each plot}.
+From left to right the panels show the statistical distribution of the electron density value $\NCB \equiv \sqravgN(r=1.055)\edit{[{\rm cm}^{-3}]}$, {the scale height $\lN$, and the height-averaged (along the leg) electron temperature $\aTm \edit{[{\rm MK}]}$}, {with the median value $m$ indicated in each plot}.
 
@@
 II   & 0&98 &(\Mi&20\%)  &   9&9 &(\Pl&19\%) &   1&36 &(\Pl&16\%) \\
-III  & 0&66 &(\Mi&\edit{21}\%)  &   7&7 &(\Pl&15\%) &   0&97 &(\Pl&\edit{17}\%) \\
+III  & 0&66 &(\Mi&{21}\%)  &   7&7 &(\Pl&15\%) &   0&97 &(\Pl&{17}\%) \\
 \hline          
 \end{tabular}
-\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of legs defined in Section \ref{trace}.
-For CR-2082 values are expressed in absolute terms, while for CR-2208 they are \edit{given} as a percentual variation relative to the CR-2082 value \edit{in the parentheses.}}
+\caption{Median value (indicated as Md) of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of legs defined in Section \ref{trace}.
+For \edit{CR 2082}, values are expressed in absolute terms, while for \edit{CR 2208} they are {given} as a percentual variation relative to the \edit{CR 2082} value {in the parentheses.}}
 \label{tabla_demt}
@@
 
-Table \ref{tabla_demt} summarizes \edit{the results of the quantitative comparative analysis between the two {target rotations}}.
-For CR-2082 quantities are expressed as absolute values, {while} for CR-2208 they are expressed relative to the corresponding results for CR-2082.
+Table \ref{tabla_demt} \edit{summarises} {the results of the quantitative comparative analysis between the two {target rotations}}.
+For \edit{CR 2082} quantities are expressed as absolute values, {while} for \edit{CR 2208} they are expressed relative to the corresponding results for \edit{CR 2082}.
 
-{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer layers of the equatorial streamer belt, exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
-In both rotations also, type III legs in the CHs are characterised by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I legs in the core of the equatorial streamer.} {A comparison of the results between the two rotations shows that, compared to CR-2082, rotation CR-2208 was characterised by {$\approx 10-20\%$} lower values of the electron density at the coronal base, $\approx 5-30\%$ larger values of density scale height, and {$\approx 15-25\%$} larger values of the electron temperature.}
+{Throughout the magnetically closed region of both rotations, type 0, I, and II legs, associated to  increasingly outer layers of the equatorial streamer belt, exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature.
+In both rotations also, type III legs in the CHs are characterised by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I legs in the core of the equatorial streamer.} {A comparison of the results between the two rotations shows that, compared to \edit{CR 2082}, rotation \edit{CR 2208} was characterised by {$\approx 10-20\%$} lower values of the electron density at the coronal base, $\approx 5-30\%$ larger values of density scale height, and {$\approx 15-25\%$} larger values of the electron temperature.}
 
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth]{figs/histocr2082_ccdownenergia.eps}
-\includegraphics[width=0.495\textwidth]{figs/histocr2208_ccdownenergia.eps}
-\includegraphics[width=0.495\textwidth]{figs/histocr2082_ccenergia.eps}
-\includegraphics[width=0.495\textwidth]{figs/histocr2208_ccenergia.eps}
-\includegraphics[width=0.495\textwidth]{figs/histocr2082_cgenergia.eps}
-\includegraphics[width=0.495\textwidth]{figs/histocr2208_cgenergia.eps}
-\caption{{Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right).
+\includegraphics[width=0.495\textwidth]{histocr2082_ccdownenergia.pdf}
+\includegraphics[width=0.495\textwidth]{histocr2208_ccdownenergia.pdf}
+\includegraphics[width=0.495\textwidth]{histocr2082_ccenergia.pdf}
+\includegraphics[width=0.495\textwidth]{histocr2208_ccenergia.pdf}
+\includegraphics[width=0.495\textwidth]{histocr2082_cgenergia.pdf}
+\includegraphics[width=0.495\textwidth]{histocr2208_cgenergia.pdf}
+\caption{{Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in \edit{colours} blue, red, and green, respectively for \edit{CR 2082} (left) and \edit{CR 2208} (right).
 From top to bottom, panels show the results for loops of type 0, I and II, which are loops for which both legs meet the criteria from Section \ref{trace}.}}
@@
 
-In comparing the DEMT results obtained for the two selected targets, {we highlight} they rely on data provided by two different instruments, {namely EUVI and AIA for CR-2082 and CR-2208, respectively.} To quantify the systematic difference of the DEMT products {due to the different filter sets of} both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
-They found that while the density {products are} essentially equal, the temperature \edit{based on AIA data} is systematically 8\% larger than the one based on EUVI data, \textit{i.e.} $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$.
-Considering \edit{this error}, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was {characterised by temperatures $\approx 10-15\%$ larger relative to CR-2082} throughout the streamer belt region.
-As for the electron density products, CR-2208 was found to be $\approx 10-20\%$ less dense than CR-2082 throughout the streamer belt region.
+In comparing the DEMT results obtained for the two selected targets, {we highlight} they rely on data provided by two different instruments, {namely EUVI and AIA for \edit{CR 2082} and \edit{CR 2208}, respectively.} To quantify the systematic difference of the DEMT products {due to the different filter sets of} both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently.
+They found that while the density {products are} essentially equal, the temperature {based on AIA data} is systematically 8\% larger than the one based on EUVI data, {i.e.} $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$.
+Considering {this error}, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that \edit{CR 2208} was {characterised by temperatures $\approx 10-15\%$ larger relative to \edit{CR 2082}} throughout the streamer belt region.
+As for the electron density products, \edit{CR 2208} was found to be $\approx 10-20\%$ less dense than \edit{CR 2082} throughout the streamer belt region.
 These systematic differences are {around or beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} {estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$}.}
 
-{To analyse the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the classification of both its legs, each loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).
-{For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.}
+{To analyse the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the classification of both legs, each loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).
+{For both target rotations, and for loops of type 0, I, and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$, and $\phi_h$ in blue, green, and red \edit{colour}}, respectively.}
 
-{For both rotations, the value of the {loop-integrated} radiative power $E_r$, measured by the quantity $\phi_r$, is largest for loops of type 0.
+{For both rotations, the value of the {loop-integrated} radiative power $E_r$, measured by the quantity $\phi_r$, is \edit{the} largest for loops of type 0.
 This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors contributing to maximize $E_r$ for loops of type 0.
-As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0 are \edit{characterised} by {the largest} values of electron density.
-Also, in the range of sensitivity of the EUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$.
-According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are \edit{characterised by temperatures that are are progressively larger, and farther from $\Tc$, for both rotations.}}
+As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0 are {characterised} by {the largest} values of electron density.
+Also, in the range of sensitivity of the EUVI and AIA instruments, namely \edit{$0.5\,-\,3.0$} MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$.
+According to Figure \ref{histos_fulldemt}, loops of type 0, I, and II are {characterised by temperatures that are are progressively larger, and farther from $\Tc$, for both rotations.}}
 
@@
 {{Adding the} radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}.
-\edit{For} type 0 loops there is a marginal population characterised by the unphysical result $\phi_h<0$.
-As shown by \citet{maccormack_2017}, this affects only the smallest sized loops of the type 0, and it is likely due \edit{to emission out of the instrumental sensitivity range}.
+{For} type 0 loops there is a marginal population characterised by the unphysical result $\phi_h<0$.
+As shown by \citet{maccormack_2017}, this affects only the smallest sized loops of the type 0, and it is likely due {to emission out of the instrumental sensitivity range}.
 Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range.
@@
 
-{Figure \ref{Br} shows carrington maps of {the radial} magnetic {field ($B_r$)} for both rotations at $1.005\, \mrsun$.
+{Figure \ref{Br} shows \edit{Carrington} maps of {the radial} magnetic {field $B_r$} for both rotations at $1.005\, \mrsun$.
 {Both maps clearly show the large-scale dipolar field, characteristic of solar minimum conditions.
-Differences between both maps are observed in the sub-polar latitudes, due to the different treatments applied there by the GONG (CR-2082) and the ADAPT-GONG (CR-2208) maps.}}
+Differences between both maps are observed in the sub-polar latitudes, due to the different treatments applied there by the GONG (\edit{CR 2082}) and the ADAPT-GONG (\edit{CR 2208}) maps.}}
 
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/map_Br_awsom_2082_185_extend_1005_Rsun.pdf}
-\includegraphics[width=0.495\textwidth,clip=]{figs/map_Br_awsom_2208_185_extend_1005_Rsun.pdf}
-\caption{Carrington maps of {the radial magnetic field $B_r$ of the AWSoM model} at $1.005 \, \mrsun$ for CR-2082 (left) and CR-2208 (right). }
+\includegraphics[width=0.495\textwidth,clip=]{map_Br_awsom_2082_185_extend_1005_Rsun2.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{map_Br_awsom_2208_185_extend_1005_Rsun2.pdf}
+\caption{Carrington maps of {the radial magnetic field $B_r$ of the AWSoM model} at $1.005 \, \mrsun$ for \edit{CR 2082} (left) and \edit{CR 2208} (right). }
 \label{Br}
@@
 {Thick-black curves} indicate the magnetic open/closed boundaries based on the magnetic field of the AWSoM model.
-Visual inspection of these maps shows that the AWSoM model for both rotations is highly {axisymetric}, as the tomographic \edit{results}.
+Visual inspection of these maps shows that the AWSoM model for both rotations is highly {axisymetric}, as the tomographic {results}.
 
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1105_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1105_Rsun.pdf}
+\includegraphics[width=0.495\textwidth]{map_Ne_awsom_2082_185_short_1065_Rsun2.pdf}
+\includegraphics[width=0.495\textwidth]{map_Te_awsom_2082_185_short_1065_Rsun2.pdf}
+\includegraphics[width=0.495\textwidth]{map_Ne_awsom_2082_185_short_1105_Rsun2.pdf}
+\includegraphics[width=0.495\textwidth]{map_Te_awsom_2082_185_short_1105_Rsun2.pdf}
 \caption{Carrington maps of density (left panels) and temperature (right panels) obtained with AWSoM model at heliocentric heights $1.065$ (top panels) and $1.105\,\mrsun$ (bottom panels).}
@@
 Furthermore, for both rotations, the temperature maps show the low latitudes of the equatorial streamer belt to be characterised by lower temperatures than its mid-latitudes, as also seen in the DEMT results.
-The latitude-longitude maps of the AWSoM and DEMT results are shown in the same units and scales, so that a \edit{visual comparison reveals} similar values of electron density and temperature in both models.}
+The latitude-longitude maps of the AWSoM and DEMT results are shown in the same units and scales, so that a {visual comparison reveals} similar values of electron density and temperature in both models.}
 
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1065_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1105_Rsun.pdf}
-\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1105_Rsun.pdf}
-\caption{Same as Figure \ref{carmaps_awsom_2082} for CR-2208.}
+\includegraphics[width=0.495\textwidth]{map_Ne_awsom_2208_185_short_1065_Rsun2.pdf}
+\includegraphics[width=0.495\textwidth]{map_Te_awsom_2208_185_short_1065_Rsun2.pdf}
+\includegraphics[width=0.495\textwidth]{map_Ne_awsom_2208_185_short_1105_Rsun2.pdf}
+\includegraphics[width=0.495\textwidth]{map_Te_awsom_2208_185_short_1105_Rsun2.pdf}
+\caption{Same as Figure \ref{carmaps_awsom_2082} for \edit{CR 2208}.}
 \label{carmaps_awsom_2208}
@@
 
-{Being highly axisymmtric rotations, the longitude-averaged latitudinal {profile} of the results of both models is an informative way to compare their large-scale structure.
-\edit{Such a comparison} is shown in Figure \ref{perf_lat} at height $1.105\,\mrsun$, \edit{with the top} panels comparing electron density and mid panels electron temperature.
+{Being highly \edit{axisymmetric} rotations, the longitude-averaged latitudinal {profile} of the results of both models is an informative way to compare their large-scale structure.
+{Such a comparison} is shown in Figure \ref{perf_lat} at height $1.105\,\mrsun$, {with the top} panels comparing electron density and \edit{middle panels the electron temperature}.
 {The longitude-averaged latitudinal profile of $B_r$ is shown in the bottom panels.} In these longitude-averaged profiles, longitudes containing ARs or low latitude CHs were excluded.
-In each panel the averaged latitudinal variation for the DEMT model is shown in solid-line style, while the result for the AWSoM model is shown in dashed-linesyle.
-Left panels show the comparison for CR-2082 (in blue) and right panels for CR-2208 (in red).
+In each panel the averaged latitudinal variation for the DEMT model is shown in solid-line style, while the result for the AWSoM model is shown in \edit{dashed-line syle}.
+Left panels show the comparison for \edit{CR 2082} (in blue) and right panels for \edit{CR 2208} (in red).
 In each panel the vertical black lines denote the corresponding longitude-averaged latitude of the open-closed boundary in both hemispheres.}
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105_2.pdf}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_multistart2_1105.pdf}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105_2.pdf}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_multistart2_1105.pdf}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2082_1105_2.pdf}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2208_1105_2.pdf}
-\caption{Longitude-averaged latitudinal variation of the electron density ({top panels}), {electron temperature ({middle panels})} and {radial magnetic field $B_r$ (bottom panels), for rotations} CR-2082 ({blue color, left panels}) and CR-2208 ({red color, right panels) at} $1.105\,\mrsun$.
+\includegraphics[width=0.495\textwidth]{Perfil_Ne_demt_awsom_2082_1105_2.pdf}
+\includegraphics[width=0.495\textwidth]{Perfil_Ne_demt_awsom_2208_multistart2_1105.pdf}
+\includegraphics[width=0.495\textwidth]{Perfil_Te_demt_awsom_2082_1105_2.pdf}
+\includegraphics[width=0.495\textwidth]{Perfil_Te_demt_awsom_2208_multistart2_1105.pdf}
+\includegraphics[width=0.495\textwidth]{Perfil_Br_2082_1105_2.pdf}
+\includegraphics[width=0.495\textwidth]{Perfil_Br_2208_1105_2.pdf}
+\caption{Longitude-averaged latitudinal variation of the electron density ({top panels}), {electron temperature ({middle panels})}, and {radial magnetic field $B_r$ (bottom panels), for rotations} \edit{CR 2082} ({blue \edit{colour}, left panels}) and \edit{CR 2208} ({red \edit{colour}, right panels) at} $1.105\,\mrsun$.
 Dashed and solid lines indicate AWSoM and DEMT results, respectively.
@@
 
-{Several details from Figure \ref{perf_lat} are \edit{worth highlighted}.
-Firstly, at most latitudes the overall agreement of the electron density of both models is within $\approx 20\%$ for CR-2082, and $\approx 5\%$ for CR-2208.
+\edit{It is worth highlighting several details from Figure \ref{perf_lat}}.
+Firstly, at most latitudes the overall agreement of the electron density of both models is within $\approx 20\%$ for \edit{CR 2082}, and $\approx 5\%$ for \edit{CR 2208}.
 The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.
 In the case of the electron temperature, for both rotations the models agree within $\approx 15\%$ at all latitudes.
-Secondly, for both rotations, and for both models, these plots clearly show the relatively lower temperatures characterizing the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
+Secondly, for both rotations, and for both models, these plots clearly show the relatively lower temperatures \edit{characterising} the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
 Thirdly, for both rotations, the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density.
 Note this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
-\edit{Lastly, the DEMT} electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two rotations), while the AWSoM model shows the opposite trend.
-{For comparison, \edit{$B_r$ in the CHs increases} from the open/closed boundary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}
+{Lastly, the DEMT} electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two rotations), while the AWSoM model shows the opposite trend.
+{For comparison, {$B_r$ in the CHs increases} from the open/closed boundary towards the poles for \edit{CR 2082}, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of \edit{CR 2208}.}
 
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_awsom_paper_test_Rpoint-map.pdf}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_awsom_paper_test_Rpoint-map.pdf}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.pdf}
-\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.pdf}
-\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its legs in types I, II and III. The model does not exhibit legs of type 0.}}
+\includegraphics[width=0.495\textwidth,clip=]{Grispoint_2082_awsom_paper_test_Rpoint-map2.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{Grispoint_2208_awsom_paper_test_Rpoint-map222.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map222.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map222.pdf}
+\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its legs in types I, II, and III. The model does not exhibit legs of type 0.}}
 \label{rpoint_awsom}
@@
 
-To characterize the results of the AWSoM model in distinct magnetic structures, its results for electron density and temperature were traced along its magnetic field lines.
+To \edit{characterise} the results of the AWSoM model in distinct magnetic structures, its results for electron density and temperature were traced along its magnetic field lines.
 For each field line leg, the results were then fit to Equations \ref{Nfit} and \ref{Tfit}{, considering only data points above heliocentric height $1.055\,\mrsun$.
-We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.
+We then classified the traced legs into types I, II, and III, according to the criteria described in Section \ref{trace}.
 Legs of type 0 are not included for AWSoM as it currently can not simulate down loops, as discussed in Section \ref{discu}.}
@@
 \begin{center}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
-\caption{{Statistical distribution {of the results of the DEMT (solid line-style) and AWSoM (dashed-line style) models} traced along legs of type I, II and III (from top to bottom), as defined in {Section \ref{trace}.} From left to right: electron density at the lowest coronal height of the AWSoM model $\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_demt_awsom_streamer_up_ne_1055_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_demt_awsom_streamer_up_lambda_n_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_demt_awsom_streamer_up_Tm_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_demt_awsom_bound_up_ne_1055_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_demt_awsom_bound_up_lambda_n_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_demt_awsom_bound_up_Tm_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_demt_awsom_CH_up_ne_1055_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_demt_awsom_CH_up_lambda_n_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2082_demt_awsom_CH_up_Tm_2.pdf}
+\caption{{Statistical distribution {of the results of the \edit{DEMT reconstruction} (solid line-style) and AWSoM (dashed-line style)} traced along legs of type I, II, and III (from top to bottom), as defined in {Section \ref{trace}.} From left to right: electron density at the lowest coronal height of the AWSoM model $\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
 In each panel the median {values $m$ are} indicated.}}
@@
 That criterion is adapted here, requiring that at least five voxels of the tomographic grid are threaded by the leg.
-Open legs are indicated in gray color and closed ones in black color.
+Open legs are indicated in \edit{grey} \edit{colour} and closed ones in black \edit{colour}.
 For each leg, the fits to tomographic temperature and density were applied, as given by Equations \ref{Nfit} and \ref{Tfit}.
 Considering the AWSoM data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_awsom} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met.
-Using a three-color code, type I, II and III legs are shown in red, magenta and cyan color, respectively.
-This figure \edit{can be compared} with the corresponding Figure \ref{rpoint_demt} for DEMT results.
-\edit{The AWSoM maps are more densely populated} than those of DEMT.
-This is due to the 3D MHD model having \edit{having spatially smoother distributions of electron density and temperature than those of DEMT}.}
+Using a three-\edit{colour} code, type I, II, and III legs are shown in red, magenta, and cyan \edit{colour}, respectively.
+This figure {can be compared} with the corresponding Figure \ref{rpoint_demt} for DEMT results.
+{The AWSoM maps are more densely populated} than those of \edit{the DEMT}.
+This is due to the 3D MHD model having {spatially smoother distributions of electron density and temperature than those of \edit{the DEMT}}.}
 
@@
 \begin{center}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_Tm.eps}\\
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_Tm.eps}\\
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_conajuste_ne_1055.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_conajuste_lambda_n.eps}
-\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_conajuste_Tm.eps}
-\caption{Same as Figure \ref{histos_2082} for CR-2208.}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2208_demt_awsom_streamer_up_ne_1055_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2208_demt_awsom_streamer_up_lambda_n_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2208_demt_awsom_streamer_up_Tm_2.pdf}\\
+\includegraphics[width=0.31\textwidth,clip=]{histo_2208_demt_awsom_bound_up_ne_1055_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2208_demt_awsom_bound_up_lambda_n_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2208_demt_awsom_bound_up_Tm_2.pdf}\\
+\includegraphics[width=0.31\textwidth,clip=]{histo_2208_demt_awsom_CH_up_conajuste_ne_1055_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2208_demt_awsom_CH_up_conajuste_lambda_n_2.pdf}
+\includegraphics[width=0.31\textwidth,clip=]{histo_2208_demt_awsom_CH_up_conajuste_Tm_2.pdf}
+\caption{Same as Figure \ref{histos_2082} for \edit{CR 2208}.}
 \label{histos_2208}
@@
 
-{For rotation CR-2082, Figure \ref{histos_2082} shows the statistical distribution of the results of the DEMT (solid line-style) and AWSoM (dashed line-style) models traced along legs of type I, II and III (from top to bottom), as defined in Section \ref{trace}.
-From left to right: electron density at the lowest coronal height of the AWSoM model $\NCB\equiv\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
+{For \edit{CR 2082}, Figure \ref{histos_2082} shows the statistical distribution of the results of the \edit{DEMT reconstruction} (solid line-style) and AWSoM (dashed line-style) model traced along legs of type I, II, and III (from top to bottom), as defined in Section \ref{trace}.
+Figure \ref{histos_2208} shows the same analysis for \edit{CR 2208}.} %From left to right: electron density at the lowest coronal height of the AWSoM model $\NCB\equiv\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$.
 In each panel the median values $m$ are indicated.
-Figure \ref{histos_2208} shows the same analysis for rotation CR-2208.}
+Figure \ref{histos_2208} shows the same analysis for rotation \edit{CR 2208}.}
 
-{For the two target rotations, Table \ref{tabla_comp} summarizes a quantitative comparative analysis between the results of the DEMT and AWSoM models {based on the results shown in Figures \ref{histos_2082} and \ref{histos_2208}}.
-The DEMT results are expressed as absolute values, while the ASWSoM results are informed as a percentual variation relative to the corresponding result for DEMT.}
+{For the two target rotations, Table \ref{tabla_comp} \edit{summarises the} quantitative comparative analysis between the results of the \edit{DEMT reconstruction and AWSoM model} {based on the results shown in Figures \ref{histos_2082} and \ref{histos_2208}}.
+The DEMT results are expressed as absolute values, while the AWSoM results are informed as a percentual variation relative to the corresponding result for \edit{the} DEMT.}
 
@@
 \hline
-CR-2082\\
+\edit{CR 2082}\\
 I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&10\%) \\
@@
 \hline          
-CR-2208\\
+\edit{CR 2208}\\
 I    & 1&03 &(\Pl&~6\%)  &   9&7 &(\Mi&~8\%) &   1&55 &(\Mi&17\%) \\
 II   & 0&79 &(\Pl&~9\%)  &  11&8 &(\Mi&14\%) &   1&58 &(\Mi&~8\%) \\
-III  & 0&\edit{52} &(\edit{\Pl}&~\edit{8}\%)  &   8&9 &(\Mi&18\%) &   1&\edit{13} &(\Mi&18\%) \\
+III  & 0&{52} &({\Pl}&~{8}\%)  &   8&9 &(\Mi&18\%) &   1&{13} &(\Mi&18\%) \\
 \hline   
 \end{tabular}
-\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of leg defined in Section \ref{trace}.
-DEMT values are expressed in absolute terms, while AWSoM results are expressed relative to the corresponding DEMT value.}
+\caption{Median value (indicated as Md) of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of leg defined in Section \ref{trace}.
+DEMT \edit{results} are expressed in absolute \edit{values}, while AWSoM results are expressed relative to the corresponding DEMT value.}
 \label{tabla_comp}
@@
 
-{For rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, {depending of the type of leg, with the largest discrepancy foud for legs of type II (near the open/closed boundary).
-The} median value of the scale height $\lN$ agree {within $\approx 10\%$ in all regions}.
+{For \edit{CR 2082}, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, {depending of the type of leg, with the largest discrepancy found for legs of type II (near the open/closed boundary).
+The} median value of the scale height $\lN$ agrees {within $\approx 10\%$ in all regions}.
 The leg-averaged electron temperature $\aTm$ of both models also agree {within $10\%$ in all regions}.
-For rotation CR-2208 the agreement of the median value of $\NCB$ and $\lN$ of both models {is within $10\%$, while} median values of $\aTm$ agree within $15\%$.
-{These detailed results, being consistent with the large-scale comparison provided in Figure \ref{perf_lat}, show in detail how the AWSoM model performs compared to DEMT in different magnetic structures.}}
+For \edit{CR 2208} the agreement of the median value of $\NCB$ and $\lN$ of both models {is within $10\%$, while} median values of $\aTm$ agree within $15\%$.
+{These detailed results, being consistent with the large-scale comparison provided in Figure \ref{perf_lat}, show in detail how the AWSoM model performs compared to \edit{the} DEMT in different magnetic structures.}}
 
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up_conajuste.eps}
-\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_conajuste.eps}
-\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of {type I (\edit{orange}), II (\edit{red}), and III (cyan)}, for CR-2082 (top panels) and CR-2208 (bottom panels).
+\includegraphics[width=0.495\textwidth,clip=]{perfil_paper_ne_cr2082_up.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{perfil_paper_te_cr2082_up.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{perfil_paper_ne_cr2208_up_conajuste.pdf}
+\includegraphics[width=0.495\textwidth,clip=]{perfil_paper_te_cr2208_up_conajuste.pdf}
+\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of {type I ({orange}), II ({red}), and III (cyan)}, for \edit{CR 2082} (top panels) and \edit{CR 2208} (bottom panels).
 Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
@@
 Similarly, all velocity data points to the north of the HCS position map down to the northern CH in Figures \ref{perf_lat}.
-This clearly shows an anti-correlation between the DEMT electron density at low heights and the AWSoM wind speed at larger heights.}
+This clearly shows an \edit{anticorrelation} between the DEMT electron density at low heights and the AWSoM wind speed at larger heights.}
 
@@
 \begin{center}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995_2.pdf}
-\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995_2.pdf}
-\caption{{Longitude-averaged latitudinal dependence of the AWSoM model {wind speed $V_r$} at $6.0\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).}}
+\includegraphics[width=0.495\textwidth]{Perfil_Vr_2082_5995_2.pdf}
+\includegraphics[width=0.495\textwidth]{Perfil_Vr_2208_5995_2.pdf}
+\caption{{Longitude-averaged latitudinal dependence of the AWSoM model {wind speed $V_r$} at $6.0\,\mrsun$ for \edit{CR 2082} (left panel) and \edit{CR 2208} (right panel).}}
 \label{perf_lon_vr}
@@
 
-\edit{Magnetic field lines of type 0, I and II were selected to be associated with increasingly outer layers of the equatorial streamer belt (Figure \ref{rpoint_demt}).
+{Magnetic field lines of type 0, I, and II were selected to be associated with increasingly outer layers of the equatorial streamer belt (Figure \ref{rpoint_demt}).
 These magnetic structures progressively exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature, as informed in 3D quantitative detail in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}.} For both rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes.
-Also, in the case of CR-2082 the fraction of down legs is significantly larger than for CR-2208.
+Also, in the case of \edit{CR 2082} the fraction of down legs is significantly larger than for \edit{CR 2208}.
 These findings are consistent with previous studies by \citet{huang_2012} and \citet{nuevo_2013}.
-In the case of the latter, they include in their analysis target CR-2081, which is a rotation almost identical to our target CR-2082.
-Our results for target CR-2082 compare very well with those of \citet{nuevo_2015} and \citet{lloveras_2017} for target CR-2081.
-As our study uses the improved version of the DEMT technique, such comparison provided a consistency \edit{check.} \edit{For both rotations, type III field lines in the CHs are characterised by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.}
+In the case of the latter, they include in their analysis CR 2081, which is a rotation almost identical to our target \edit{CR 2082}.
+Our results for \edit{CR 2082} compare very well with those of \citet{nuevo_2015} and \citet{lloveras_2017} for CR 2081.
+As our study uses the improved version of the DEMT technique, such comparison provided a consistency {check.} {For both rotations, type III field lines in the CHs are characterised by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.}
 
-\edit{The energy input flux $\phi_h$ at the coronal base, required to maintain stable coronal loops, is in the range} $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}.
-Based on spectroscopic data of the EIS instrument in quiet-Sun regions \citet{hahn_2014} showed that, if the observed non-thermal broadening are assigned to Alfvén waves, their energy flux at the coronal base is estimated to be in the range $\approx 1.5-2.5\times 10^5\,\erg\,\cminvs\,\s^{-1}$.
+{The energy input flux $\phi_h$ at the coronal base, required to maintain stable coronal loops, is in the range} $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}.
+Based on spectroscopic data of the EIS instrument in quiet-Sun regions \citet{hahn_2014} showed that, if the observed non-thermal \edit{broadenings} are assigned to Alfvén waves, their energy flux at the coronal base is estimated to be in the range $\approx 1.5-2.5\times 10^5\,\erg\,\cminvs\,\s^{-1}$.
 A large fraction of the coronal base energy input flux $\phi_h$ estimated in this work, or even its totality, could then be accounted for by Alfvén waves (see the discussion in \citealt{maccormack_2017}).
 
-\edit{The comparison of the results of the AWSoM model to the DEMT reconstructions can be summarized as follows.} For CR-2082, the electron density of both models agree within $\approx 20\%$ {in most regions}, while for CR-2208 the agreement is within $\approx 5\%$.
+{The comparison of the results of the AWSoM model to the DEMT reconstructions can be \edit{summarised} as follows.} For \edit{CR 2082}, the electron density of both models agree within $\approx 20\%$ {in most regions}, while for \edit{CR 2208} the agreement is within $\approx 5\%$.
 {The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$.
-This level of agreement between both models {(within or slightly beyond the uncertainty level of DEMT results)} is considerably better than that reported in previous works.
-\citet{jin_2012} and \citet{oran_2015}{, who used previous versions of the AWSoM model,} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.}
+This level of agreement between both models {(within or slightly beyond the uncertainty level of \edit{the} DEMT results)} is considerably better than that reported in previous works.
+\citet{jin_2012} and \citet{oran_2015}{, who used previous versions of the AWSoM model,} reported electron density values {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.}
 
 {The overall better match of the results of the current version of the AWSoM model compared to DEMT reconstructions is partly due to the improved energy partitioning scheme of the model, described in Section \ref{awsom}.
-\edit{The} simulation of CR-2082 used GONG maps as boundary condition, while the simulation of CR-2208 used the improved ADAPT-GONG maps.
-This is likely the cause \edit{of a more accurate match} to the DEMT reconstructions in the case of CR-2208.}
+{The} simulation of \edit{CR 2082} used GONG maps as boundary condition, while the simulation of \edit{CR 2208} used the improved ADAPT-GONG maps.
+This is likely the cause {of a more accurate match} to the DEMT reconstructions in the case of \edit{CR 2208}.}
 
-For both rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
+For both rotations, the AWSoM model reproduces the relatively lower temperatures found by \edit{the} DEMT to \edit{characterise} the low-latitudes of the equatorial streamer belt compared to its mid-latitudes.
 On the other hand, while the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density {(physically expected in transitioning from magnetically closed to open regions)}, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary.
 Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two rotations), {as expected in transitioning from the source region of the slow to the fast component of the solar wind}, the AWSoM model shows the opposite trend.
-This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.
-These unphysical characteristics of the results of the AWSoM model in the \edit{range} of low heights analysed here ($r\lesssim 1.2\,\mrsun$), may be attributed to the less reliable values of $B_r$ provided by both the GONG and ADAPT-GONG maps at subpolar latitudes.
-This will \edit{be investigated} in a follow up article focusing on the current deep minimum epoch, during which the large-scale corona shows the simplest possible structure.
+This \edit{behaviour} is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.
+These unphysical characteristics of the results of the AWSoM model in the {range} of low heights analysed here ($r\lesssim 1.2\,\mrsun$), may be attributed to the less reliable values of $B_r$ provided by both the GONG and ADAPT-GONG maps at subpolar latitudes.
+This will {be investigated} in a follow up article focusing on the current deep minimum epoch, during which the large-scale corona shows the simplest possible structure.
 
@@
 \citet{schiff_2016} numerically simulated stable down loops by means of a 1D steady-state model, requiring that the initial population of Alfvén waves is efficiently converted into compressive modes.
-Mode conversion is favored by the $\beta\gtrsim 1 $ condition found to characterize the regions where down loops are observed in DEMT analysis \citep{nuevo_2013}.
+Mode conversion is favored by the $\beta\gtrsim 1 $ condition found to \edit{characterise} the regions where down loops are observed in DEMT analysis \citep{nuevo_2013}.
 In the AWSoM model, heating is controlled by two key parameters, namely, the Alfvén wave dissipation length, and its reflection coefficient.
@@
 
-A detailed empirical description of the 3D thermodynamic structure of the inner corona at a global scale is currently only possible with tomographic techniques, such as DEMT.
+A detailed empirical description of the 3D thermodynamic structure of the inner corona at a global scale is currently only possible with tomographic techniques, such as \edit{the} DEMT.
 Using tomographic results for continuous validation of 3D MHD models is of high relevance for the continued improvement of models.
-In {follow up articles} we will {carry out the 3D DEMT reconstruction and MHD modeling of} new target rotations {selected from} the current solar minimum {epoch} between SCs 24 and 25, {as well as rotation CR-2219 corresponding to the July 2nd 2019 total solar eclipse.}
+In {follow up articles} we will {carry out the 3D DEMT reconstruction and MHD modeling of} new target rotations {selected from} the current solar minimum {epoch} between SCs 24 and 25, {as well as CR 2219 corresponding to the \edit{July 2, 2019} total solar eclipse.}
 
@@
 Nr.
-4870) to IAFE that supported {their} participation in this research.
-{D.G.L, A.M.V., F.A.N.
-and C.M.C.
-acknowledge ANPCyT grant 2016/0221 to IAFE that partially supported their participation in this research.
+4870) that supported {their} participation in this research.
+{D.G.L, A.M.V., F.A.N., and C.M.C.
+acknowledge ANPCyT grant 2016/0221 that partially supported their participation in this research.
 A.M.V.
-also acknowledges UBACyT grant 20020160100072BA to DCAO-UBA to FCEyN-UBA and IAFE that partially supported his participation in this research.} W.M.
+also acknowledges UBACyT grant 20020160100072BA that partially supported his participation in this research.} W.M.
 and B.v.H acknowledge NSF grant 1663800 that partially supported his participation in this research.
@@
 also acknowledges NASA grants NNX16AL12G and 80NSSC17K0686.
+\edit{The AIA/SDO data used in this study is courtesy of NASA/SDO and the AIA, EVE, and HMI science teams.}
 \end{acks}
